### 2020-02-20 paper.tex

\documentclass[12pt, a4paper]{article}
\usepackage[]{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[]{color}
\usepackage{alltt}

% Load graphicx package in your document's preamble
% Gandrud (2016), p.192

% turn page 90 degrees with lscape Gandrud (2016), p.185

% Create clickable hyperlinks with hyperref package, Gandrud (2016), p. 218

% Use natbib package for bibliography formatting, authoryear for Harvard style , Gandrud (2016), p. 227
% commands to change what information is included in the parentheses, Gandrud (2016), p. 228, table 11.2

% Using saveRDS and readRDS, following 
% https://csgillespie.github.io/efficientR/efficient-inputoutput.html#efficient-data-export-.rdata-or-.rds

\usepackage{lscape}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage{floatrow}
\usepackage[hidelinks]{hyperref}
% \usepackage[authoryear]{natbib}
% \bibliographystyle{apalike}
\usepackage{mathtools}
\usepackage[onehalfspacing]{setspace}
\usepackage[left = 72 pt, right = 72 pt]{geometry}

%\addbibresource{Main.bib}

%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

% Create list of packages used, Gandrud (2016), p 218/219

\title{Effects of CHILDREN's programs}
\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
\date{27th February 2020}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}

\begin{document}

\begin{titlepage}
\maketitle
\end{titlepage}

\tableofcontents
\listoftables
\listoffigures

% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}

\section{Introduction}

\section{Outline}
Descriptive statistics\\
- dynamics of selected outcomes\\
- dynamics of real subsidy per institution\\
- dynamics of real total subsidy\\
- dynamics of real subsidy per individual\\

Regressions\\

Questions:\\
- effect of healthy meals (DGE criterion) on healthy characteristics\\
- effect of real meals subsidy on number of meals\\
- effect of real trips subsidy on number of trips\\
- effect of real meals subsidy on self-worth and day-to-day skills\\

Methods:\\
- simple, metric\\
- standardized, metric\\
- cumulative logit\\
- with control variables\\
(- without outliers)\\
(- imputed data)\\

Diff in Diff\\

Outlook for CHILDREN\\
- partition analysis\\
(- correlation matrix)\\
(- factor analysis)\\
- general tips\\

%\printbibliography
\end{document}

### 2020-02-21 ANALYSIS/DATA/Merge.R
Änderung MakeGather

@@ -14,7 +14,7 @@ data201118 <- df_2018 %>% #data2019 %>%
   full_join(data2011)
 
 data201118 <- data201118 %>%
-  select(year, everything())
+  dplyr::select(year, everything())
   
 # Join the data with Bundesland
 

### 2020-02-21 paper.tex
removed standardized variables from double selection analysis
added examples in LaTeX file

@@
 % https://csgillespie.github.io/efficientR/efficient-inputoutput.html#efficient-data-export-.rdata-or-.rds
+
+% working with knitR and LaTeX
+% https://kbroman.org/knitr_knutshell/pages/latex.html
+% Command line
+% R -e 'library(knitr);knit("knitr_example.Rnw")'
 
@@
 - dynamics of real subsidy per individual\\
+(- which variables have largest variance; also relevant for variable selection)\\
 
@@
 
-Outlook for CHILDREN\\
+Outlook for CHILDREN/variable selection\\
+- double selection \\
 - partition analysis\\
@@
 
+Examples\\
+
+Equation\\
+
+\begin{equation}
+\label{ModelProdu}
+\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
+\end{equation}
+
+List\\
+
+\begin{itemize}
+  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
+  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
+  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
+\end{itemize}
+
+Figure
+
+\begin{figure}
+  \caption{Dispersion in productivity levels}
+  \label{LineDisp}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{ANALYSIS/GRAPHS/unnamed-chunk-2-1}
+
+}
+
+\end{knitrout}
+\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
+A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
+After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
+The shaded bars represent recessions as defined by the NBER.
+The year ticks refer to January 1.
+The dispersion measures take as their date the middle of the year, July 2.
+Compare Kehrig (2015), Figure 1.}
+\end{figure}
+
 %\printbibliography

### 2020-02-21 ANALYSIS/OLS Regressions.R

@@ -1,149 +1,0 @@
-# use package hdm to perform double selection: OLS regression after feature selection
-# https://insightr.wordpress.com/2017/08/04/the-package-hdm-for-double-selection-inference-with-a-simple-example/
-
-library(hdm)
-
-
-dataset <- mergedData %>% 
-  select_if(is.numeric)
-
-# drop_na drops rows containing missing values
-
-# select rows with year in which DGECriteriaNo was recorded
-
-dataset <- mergedDataImputeMode %>% 
-  filter(year %in% c(2018, 2017, 2016, 2014))
-  # dplyr::select(#participateMore, 
-  #               # tasksLunch,
-  #               # monthlyCooks,
-  #               # weeklyCooks,
-  #               # shoppers,
-  #               # ownIdeas,
-  #               # stayLonger,
-  #               # easyDishes,
-  #               # dietaryKnowledge,
-  #               #appreciateHealthy,
-  #               # foodCulture,
-  #               # influenceHome,
-  #               # cookAtHome,
-  #               # askRecipes,
-  #               # moreConcentrated,
-  #               # moreBalanced,
-  #               # lessIll,
-  #               dayToDaySkills,
-  #               moreIndependent,
-  #               betterTeamwork,
-  #               betterReading,
-  #               betterNumbers,
-  #               betterGrades,
-  #               moreRegularSchoolVisits,
-  #               selfworth,
-  #               moreOpen,
-  #               moreConfidence,
-  #               addressProblems,
-  #               proud,
-  #               DGECriteriaNo,
-  #               realSubsidy) %>% 
-  # drop_na()
-
-NAsPerVariableMergedData <- mergedData %>% 
-  summarise_all(list(~ sum(is.na(.)))) %>% 
-  arrange(.)
-
-datasetNewName <- dataset %>% 
-  rename(X3 = realSubsidy)
-
-fmNewName = paste("participateMore ~", paste(colnames(select(datasetNewName, -"participateMore")), collapse="+"))
-fmNewName = as.formula(fmNewName)
-
[…]

### 2020-02-21 ANALYSIS/double-selection.R

@@ -1,0 +1,158 @@
+# use package hdm to perform double selection: OLS regression after feature selection
+# https://insightr.wordpress.com/2017/08/04/the-package-hdm-for-double-selection-inference-with-a-simple-example/
+
+library(hdm)
+library(tidyselect)
+
+
+# dataset <- mergedData %>% 
+#   select_if(is.numeric)
+
+# drop_na drops rows containing missing values
+
+# select rows with year in which DGECriteriaNo was recorded
+
+dataset <- mergedDataImputeMode %>% 
+  filter(year %in% c(2018, 2017, 2016, 2014)) %>% 
+  dplyr::select(!tidyselect::contains('scaled'))
+  # dplyr::select(#participateMore, 
+  #               # tasksLunch,
+  #               # monthlyCooks,
+  #               # weeklyCooks,
+  #               # shoppers,
+  #               # ownIdeas,
+  #               # stayLonger,
+  #               # easyDishes,
+  #               # dietaryKnowledge,
+  #               #appreciateHealthy,
+  #               # foodCulture,
+  #               # influenceHome,
+  #               # cookAtHome,
+  #               # askRecipes,
+  #               # moreConcentrated,
+  #               # moreBalanced,
+  #               # lessIll,
+  #               dayToDaySkills,
+  #               moreIndependent,
+  #               betterTeamwork,
+  #               betterReading,
+  #               betterNumbers,
+  #               betterGrades,
+  #               moreRegularSchoolVisits,
+  #               selfworth,
+  #               moreOpen,
+  #               moreConfidence,
+  #               addressProblems,
+  #               proud,
+  #               DGECriteriaNo,
+  #               realSubsidy) %>% 
+  # drop_na()
+
+# NAsPerVariableMergedData <- mergedData %>% 
+#   summarise_all(list(~ sum(is.na(.)))) %>% 
+#   arrange(.)
+# 
+# datasetNewName <- dataset %>% 
+#   rename(X3 = realSubsidy)
+# 
[…]

### 2020-02-21 paper.Rnw
replaced tex file by Rnw file

--- 2020-02-21 paper.tex
@@
+% IMPORTANT
+% 
+% Install tex distribution
+% https://www.latex-project.org/get/
+% With Windows, install MikTeX
+% 
+% Go to Tools/Global Options/Sweave
+% Select Weave Rnw files using: knitr
+% Select Typeset LaTeX into PDF using: pdfLaTeX
+
 \documentclass[12pt, a4paper]{article}
@@
 \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage{floatrow}
-\usepackage[hidelinks]{hyperref}
+% \usepackage{floatrow}
+% \usepackage[hidelinks]{hyperref}
 % \usepackage[authoryear]{natbib}
 % \bibliographystyle{apalike}
-\usepackage{mathtools}
-\usepackage[onehalfspacing]{setspace}
-\usepackage[left = 72 pt, right = 72 pt]{geometry}
+% \usepackage{mathtools}
+% \usepackage[onehalfspacing]{setspace}
+% \usepackage[left = 72 pt, right = 72 pt]{geometry}
 
@@
 
-\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-\let\hlipl\hlkwb
+% \definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+% \newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+% \newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+% \newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+% \newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+% \newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+% \newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+% \newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+% \newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+% \newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+% \let\hlipl\hlkwb
 
-\usepackage{framed}
-\makeatletter
-\newenvironment{kframe}{%
- \def\at@end@of@kframe{}%
- \ifinner\ifhmode%
-  \def\at@end@of@kframe{\end{minipage}}%
-  \begin{minipage}{\columnwidth}%
- \fi\fi%
- \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
- \colorbox{shadecolor}{##1}\hskip-\fboxsep
-     % There is no \\@totalrightmargin, so:
-     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
- \MakeFramed {\advance\hsize-\width
-   \@totalleftmargin\z@ \linewidth\hsize
-   \@setminipage}}%
- {\par\unskip\endMakeFramed%
- \at@end@of@kframe}
-\makeatother
+% \usepackage{framed}
+% \makeatletter
+% \newenvironment{kframe}{%
+%  \def\at@end@of@kframe{}%
+%  \ifinner\ifhmode%
+%   \def\at@end@of@kframe{\end{minipage}}%
+%   \begin{minipage}{\columnwidth}%
+%  \fi\fi%
+%  \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+%  \colorbox{shadecolor}{##1}\hskip-\fboxsep
+%      % There is no \\@totalrightmargin, so:
+%      \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+%  \MakeFramed {\advance\hsize-\width
+%    \@totalleftmargin\z@ \linewidth\hsize
+%    \@setminipage}}%
+%  {\par\unskip\endMakeFramed%
+%  \at@end@of@kframe}
+% \makeatother
 
-\definecolor{shadecolor}{rgb}{.97, .97, .97}
-\definecolor{messagecolor}{rgb}{0, 0, 0}
-\definecolor{warningcolor}{rgb}{1, 0, 1}
-\definecolor{errorcolor}{rgb}{1, 0, 0}
-\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+% \definecolor{shadecolor}{rgb}{.97, .97, .97}
+% \definecolor{messagecolor}{rgb}{0, 0, 0}
+% \definecolor{warningcolor}{rgb}{1, 0, 1}
+% \definecolor{errorcolor}{rgb}{1, 0, 0}
+% \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
 
@@
 - dynamics of real total subsidy\\
-- dynamics of real subsidy per individual\\
+(- dynamics of real subsidy per individual)\\
 (- which variables have largest variance; also relevant for variable selection)\\

### 2020-02-21 ANALYSIS/double-selection.R

@@ -78,29 +78,31 @@ dataset <- mergedDataImputeMode %>%
 
 # loop for regressions with varying outcome and features
 
-flexibleRegression <- function(x, y) {
+flexibleRegression <- function(y) {
   #y <- x$y
   drops <- y
-  xOldName <- as.matrix(x[, !(names(x) %in% drops)] 
+  xOldName <- as.matrix(dataset[, !(names(dataset) %in% drops)] 
                         # %>% 
                         #   select(., - !!y)
                         )
-  yOldName <- as.matrix(x[, y] 
+  yOldName <- as.matrix(dataset[, y] 
                         # %>% 
                           # select(., !!y)
                           )
-  dOldName <- as.matrix(x$DGECriteriaNo)
+  dOldName <- as.matrix(dataset$DGECriteriaNo)
   #return(xOldName)
   rlassoEffect(xOldName, yOldName, dOldName)
   # return(yOldName)
   #rlassoEffect(xOldName, yOldName, dOldName)
 }
 
-DSflexibleTest <- flexibleRegression(dataset, "lessIll")
+DSflexibleTest <- flexibleRegression("lessIll")
 DSflexibleTest2 <- flexibleRegression(dataset, "moreBalanced")
 
-dataset %>% 
-  map(~ flexibleRegression(.x, .))
+testDS1 <- dataset %>% 
+  map(flexibleRegression(.x, .x))
+
+testDS2 <- map(names(dataset), flexibleRegression)
 
 # lasso.effect = rlassoEffects(as.matrix(dataset), lessIll, index=3)
 # 

### 2020-02-21 ANALYSIS/Real Subsidy Time Trend.R
äl

@@ -1,4 +1,4 @@
-#Real Subsidy Time Trend
+#Real Subsidy Time Trend Total & Median
 
 library(dplyr)
 library(estimatr)

### 2020-02-21 regression_table.R
regresiontable

@@ -1,0 +1,18 @@
+#Regressionstable erstellen
+
+library(stargazer)
+#Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.
+#R package version 5.2.2. https://CRAN.R-project.org/package=stargazer 
+
+lm1_selfworth <- lm(dfcEF$selfworth ~ dfcEF$treatEF)
+
+lm1_skills <- lm(dfcEF$dayToDaySkills ~ dfcEF$treatEF)
+
+
+
+
+stargazer(lm1_selfworth, lm1_skills,
+          title = "Results",
+          align = TRUE,
+          type = 'text')
+

### 2020-02-21 paper.Rnw
xx
Updated Rnw file

@@
 % Select Typeset LaTeX into PDF using: pdfLaTeX
-
-\documentclass[12pt, a4paper]{article}
-\usepackage[]{graphicx}
-\usepackage[utf8]{inputenc}
-\usepackage[]{color}
-\usepackage{alltt}
 
@@
 
+% Create list of packages used, Gandrud (2016), p 218/219
+
+\documentclass[12pt, a4paper]{article}
 \usepackage{lscape}
+\usepackage{graphicx}
+\usepackage[utf8]{inputenc}
 \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-% \usepackage{floatrow}
-% \usepackage[hidelinks]{hyperref}
+\usepackage{floatrow}
+\usepackage[hidelinks]{hyperref}
 % \usepackage[authoryear]{natbib}
 % \bibliographystyle{apalike}
-% \usepackage{mathtools}
-% \usepackage[onehalfspacing]{setspace}
-% \usepackage[left = 72 pt, right = 72 pt]{geometry}
+\usepackage{mathtools}
+\usepackage[onehalfspacing]{setspace}
+\usepackage[left = 72 pt, right = 72 pt]{geometry}
 
-%\addbibresource{Main.bib}
+% \addbibresource{Main.bib}
 
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
-\makeatletter
-\def\maxwidth{ %
-  \ifdim\Gin@nat@width>\linewidth
-    \linewidth
-  \else
-    \Gin@nat@width
-  \fi
-}
-\makeatother
+<<LoadingPackages, include=FALSE>>=
+library(knitr)
+library(xtable)
+library(dplyr)
+@
 
-% \definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
-% \newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
-% \newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
-% \newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
-% \newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
-% \newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
-% \newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
-% \newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
-% \newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
-% \newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
-% \let\hlipl\hlkwb
-
-% \usepackage{framed}
-% \makeatletter
-% \newenvironment{kframe}{%
-%  \def\at@end@of@kframe{}%
-%  \ifinner\ifhmode%
-%   \def\at@end@of@kframe{\end{minipage}}%
-%   \begin{minipage}{\columnwidth}%
-%  \fi\fi%
-%  \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
-%  \colorbox{shadecolor}{##1}\hskip-\fboxsep
-%      % There is no \\@totalrightmargin, so:
-%      \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
-%  \MakeFramed {\advance\hsize-\width
-%    \@totalleftmargin\z@ \linewidth\hsize
-%    \@setminipage}}%
-%  {\par\unskip\endMakeFramed%
-%  \at@end@of@kframe}
-% \makeatother
-
-% \definecolor{shadecolor}{rgb}{.97, .97, .97}
-% \definecolor{messagecolor}{rgb}{0, 0, 0}
-% \definecolor{warningcolor}{rgb}{1, 0, 1}
-% \definecolor{errorcolor}{rgb}{1, 0, 0}
-% \newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
-
-% Create list of packages used, Gandrud (2016), p 218/219
+<<CentAlignFig, include=FALSE>>=
+# Center align all knitr figures
+# Gandrud (2016), p. 53-55
+opts_chunk$set(fig.align = "center",
+                out.width = "0.8\\textwidth")
+@
 
@@
 \date{27th February 2020}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 
@@
   \label{LineDisp}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{ANALYSIS/GRAPHS/unnamed-chunk-2-1}
-
-}
-
-\end{knitrout}
+<<echo=FALSE>>=
+figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
+print(figureLineDisp)
+@
 \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.

### 2020-02-21 paper.tex
Updated Rnw file

@@
-\documentclass[12pt, a4paper]{article}
-\usepackage[]{graphicx}
-\usepackage[utf8]{inputenc}
-\usepackage[]{color}
-\usepackage{alltt}
+% IMPORTANT
+% 
+% Install tex distribution
+% https://www.latex-project.org/get/
+% With Windows, install MikTeX
+% 
+% Go to Tools/Global Options/Sweave
+% Select Weave Rnw files using: knitr
+% Select Typeset LaTeX into PDF using: pdfLaTeX
 
@@
 
-\usepackage{lscape}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage{floatrow}
-\usepackage[hidelinks]{hyperref}
-% \usepackage[authoryear]{natbib}
-% \bibliographystyle{apalike}
-\usepackage{mathtools}
-\usepackage[onehalfspacing]{setspace}
-\usepackage[left = 72 pt, right = 72 pt]{geometry}
+% Create list of packages used, Gandrud (2016), p 218/219
 
-%\addbibresource{Main.bib}
-
-%% maxwidth is the original width if it is less than linewidth
-%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\documentclass[12pt, a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
 \makeatletter
@@
 
-% Create list of packages used, Gandrud (2016), p 218/219
+\usepackage{alltt}
+\usepackage{lscape}
+\usepackage{graphicx}
+\usepackage[utf8]{inputenc}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage{floatrow}
+\usepackage[hidelinks]{hyperref}
+% \usepackage[authoryear]{natbib}
+% \bibliographystyle{apalike}
+\usepackage{mathtools}
+\usepackage[onehalfspacing]{setspace}
+\usepackage[left = 72 pt, right = 72 pt]{geometry}
+
+% \addbibresource{Main.bib}
 
@@
 \IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-
 \begin{document}
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{ANALYSIS/GRAPHS/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-1-1}
 

### 2020-02-21 ANALYSIS/Real Subsidy Time Trend.R
xx

@@ -1,41 +1,41 @@
-#Real Subsidy Time Trend
+#Real Subsidy Time Trend Total & Median
 
 library(dplyr)
+library(estimatr)
+library(tidyverse)
+library(ggplot2)
+library(stats)
 
-#totalvalues
-#lunch
+#yearlydatawithrealsub
 
 Values2011 <- dplyr::filter(mergedData, mergedData$year == 2011)
-realSub2011 <- sum(Values2011$realSubsidy, na.rm = TRUE)
-
 Values2012 <- dplyr::filter(mergedData, mergedData$year == 2012)
-realSub2012 <- sum(Values2012$realSubsidy, na.rm = TRUE)
-
 Values2013 <- dplyr::filter(mergedData, mergedData$year == 2013)
-realSub2013 <- sum(Values2011$realSubsidy, na.rm = TRUE)
-
 Values2014 <- dplyr::filter(mergedData, mergedData$year == 2014)
-realSub2014 <- sum(Values2014$realSubsidy, na.rm = TRUE)
-
 Values2015 <- dplyr::filter(mergedData, mergedData$year == 2015)
-realSub2015 <- sum(Values2015$realSubsidy, na.rm = TRUE)
-
 Values2016 <- dplyr::filter(mergedData, mergedData$year == 2016)
-realSub2016 <- sum(Values2016$realSubsidy, na.rm = TRUE)
-
 Values2017 <- dplyr::filter(mergedData, mergedData$year == 2017)
-realSub2017 <- sum(Values2017$realSubsidy, na.rm = TRUE)
-
 Values2018 <- dplyr::filter(mergedData, mergedData$year == 2018)
+
+#lunch
+
+#totalvalues
+
+realSub2011 <- sum(Values2011$realSubsidy, na.rm = TRUE)
+realSub2012 <- sum(Values2012$realSubsidy, na.rm = TRUE)
+realSub2013 <- sum(Values2011$realSubsidy, na.rm = TRUE)
+realSub2014 <- sum(Values2014$realSubsidy, na.rm = TRUE)
+realSub2015 <- sum(Values2015$realSubsidy, na.rm = TRUE)
+realSub2016 <- sum(Values2016$realSubsidy, na.rm = TRUE)
+realSub2017 <- sum(Values2017$realSubsidy, na.rm = TRUE)
 realSub2018 <- sum(Values2018$realSubsidy, na.rm = TRUE)
 
-##
-
-YearTotal <- c(2011,2012,2013,2014,2015,2016,2017,2018)
[…]

### 2020-02-21 ANALYSIS/DATA/variable-dynamics_plots.R
lp

@@ -231,12 +231,13 @@ View(ts_totalSubsidy_ma3)
 # the moving averages in the time series graphic
 
 # With trend lines:
-plot(ts_totalSubsidy, main = "Trend of total subsidy MT", xlab = "Time", 
+totalSubsidyTrend <- plot(ts_totalSubsidy, main = "Trend of total subsidy MT", xlab = "Time", 
      ylab = "Total subsidy MT", col = "blue", lwd = 2, ylim = c(550000,710000),cex.main = 1.25)
 lines(lt_totSub_fit, col = "red", lwd = 1.5)
 lines(ts_totalSubsidy_ma3, col = "green", lwd = 1.5)
 text(2016.25, 580000, "Total subsidy", adj = 0.3, cex = 0.9)
 box(which = "figure")
 
+#save for paper 
 
-
+saveRDS(totalSubsidyTrend, "./ANALYSIS/GRAPHS/PAPER GRAPHS/totalSubsidyTrend.Rds")

### 2020-02-21 ANALYSIS/DATA/control_regression.R
UPDATE

@@ -213,7 +213,11 @@ summary(lm4_skills)
 
 
 
-### 5. Regression: Zeit-varianter Treatment-Effekt ohne year FE und id FE
+### 5. Regression: Zeit-varianter Treatment-Effekt ohne id FE
+
+# Um den Treatment-Effekt für jedes einzelne Jahr zu schätzen, wird der Interaktionsterm
+# zwischen der Treatmentvariable "dfcEF$treatEF" und den Dummy-Variablen für die verschiedenen
+# Jahres in die Regressionsgleichung aufgenommen.
 
 lm5_skills <- lm(dfcEF$dayToDaySkills ~ (dfcEF$treatEF * dfcEF$dummy_2011)
                   (dfcEF$treatEF * dfcEF$dummy_2012) + (dfcEF$treatEF * dfcEF$dummy_2013)

### 2020-02-21 ANALYSIS/DATA/regression_tables.R
regression

@@ -1,0 +1,17 @@
+#Regressionstable erstellen
+
+library(stargazer)
+#Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.
+#R package version 5.2.2. https://CRAN.R-project.org/package=stargazer 
+
+lm1_selfworth <- lm(dfcEF$selfworth ~ dfcEF$treatEF)
+
+lm1_skills <- lm(dfcEF$dayToDaySkills ~ dfcEF$treatEF)
+
+#cc
+
+
+stargazer(lm1_selfworth, lm1_skills,
+          title = "Results",
+          align = TRUE,
+          type = 'text')

### 2020-02-21 paper.Rnw
updated paper

@@
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-
-\section{Introduction}
-
 \section{Outline}
@@
 
+\section{Introduction}
+
+CHILDREN's aims for data analysis\\ 
+CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
+We call them organizations in the following.
+They apply to CHILDREN for yearly grants.
+If approved, they are supposed to use them for specific purposes defined by CHILDREN.
+CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
+The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them.
+In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
+The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
+Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
+
+\section{Summary Statistics}
+
+% look up official names of price indices in English 
+At the beginning of the time series in 2011, they supported in x institutions.
+In 2018, this number had increased to y.
+In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
+We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
+We also look at selected outcomes, i.e.
+those related to health as well as self-worth and day-to-day skills.
+We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
+We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
+These are only available after logging in on DESTATIS.
+The organizations also gave information about their total yearly budget.
+We inflate this with the general price index.
+
+\begin{figure}
+  \caption{Yearly dynamics of total grants in Meals program}
+  \label{totalGrantsDyn}
+
+<<echo=FALSE>>=
+totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER GRAPHS/totalRealSubTrend.Rds")
+print(totalGrantsDyn)
+@
+
+\floatfoot{This graph shows the development of the sum of all grants in the Meals program.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
 Examples\\
@@
   \label{LineDisp}
+
 <<echo=FALSE>>=
@@
 @
+
 \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.

### 2020-02-21 ANALYSIS/double-selection.R

@@ -96,8 +96,8 @@ flexibleRegression <- function(y) {
   #rlassoEffect(xOldName, yOldName, dOldName)
 }
 
-DSflexibleTest <- flexibleRegression("lessIll")
-DSflexibleTest2 <- flexibleRegression(dataset, "moreBalanced")
+# DSflexibleTest <- flexibleRegression("selfworth")
+# DSflexibleTest2 <- flexibleRegression("dayToDaySkills")
 
 testDS1 <- dataset %>% 
   map(flexibleRegression(.x, .x))

### 2020-02-22 ANALYSIS/Summary Statistics with ggplot.R
new

@@ -1,0 +1,17 @@
+#Real Subsidy Time Trend Total & Median
+
+library(dplyr)
+library(estimatr)
+library(tidyverse)
+library(ggplot2)
+library(stats)
+library(cowplot)
+
+
+realTripsSubTotal <- mergedData %>% 
+  group_by(year)%>% summarize(totalTripsSubsidy=sum(realTripsSubsidy, na.rm = TRUE))%>%
+  filter(!(totalTripsSubsidy == 0.0))
+
+
+#plot the linear time trend with ggplot 
+ggplot(realTripsSubTotal, aes(year, totalTripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12)

### 2020-02-22 paper.tex
xx

@@
 
+\section{Introduction}
+
+CHILDREN's aims for data analysis\\ 
+CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
+We call them organizations in the following.
+They apply to CHILDREN for yearly grants.
+If approved, they are supposed to use them for specific purposes defined by CHILDREN.
+CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
+The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them.
+In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
+The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
+Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
+
+\section{Summary Statistics}
+
+% look up official names of price indices in English 
+At the beginning of the time series in 2011, they supported in x institutions.
+In 2018, this number had increased to y.
+In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
+We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
+We also look at selected outcomes, i.e.
+those related to health as well as self-worth and day-to-day skills.
+We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
+We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
+These are only available after logging in on DESTATIS.
+The organizations also gave information about their total yearly budget.
+We inflate this with the general price index.
+
+\begin{figure}
+  \caption{Yearly dynamics of total grants in Meals program}
+  \label{totalGrantsDyn}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{verbatim}
+## NULL
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\floatfoot{This graph shows the development of the sum of all grants in the Meals program.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
 Examples\\
@@
   \label{LineDisp}
+
 \begin{knitrout}
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-1-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
 
@@
 \end{knitrout}
+
 \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.

### 2020-02-22 paper.Rnw

@@
 Descriptive statistics\\
-- dynamics of selected outcomes\\
-- dynamics of real subsidy per institution\\
-- dynamics of real total subsidy\\
-(- dynamics of real subsidy per individual)\\
+dynamics of\\ 
+(- number of organizations)\\
+(- number of beneficiaries)\\
+- selected ordinal outcomes, stacked\\
+- real total subsidy\\
+- real median subsidy per institution\\
+- real median subsidy per individual\\
 (- which variables have largest variance; also relevant for variable selection)\\

### 2020-02-22 paper.Rnw
xx

@@
 
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
+Empirical Approach\\
+
+The baseline of the empirical approach is the determination of the treatment and control group.
+Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
+On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
+
 %\printbibliography

### 2020-02-22 paper.tex
xx

@@
 
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
+For our empirical analysis we define a treatment and a control group.
+Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
+On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
+Children that benefit from
+
+Empirical Approach\\
+
+The baseline of the empirical approach is the determination of the treatment and control group.
+
 %\printbibliography

### 2020-02-22 paper.Rnw
minor updates

--- 2020-02-21 paper.Rnw
@@
 Descriptive statistics\\
-- dynamics of selected outcomes\\
-- dynamics of real subsidy per institution\\
-- dynamics of real total subsidy\\
-(- dynamics of real subsidy per individual)\\
+dynamics of\\ 
+(- number of organizations)\\
+(- number of beneficiaries)\\
+- selected ordinal outcomes, stacked\\
+- real total subsidy\\
+- real median subsidy per institution\\
+- real median subsidy per beneficiary\\
 (- which variables have largest variance; also relevant for variable selection)\\
@@
 Questions:\\
-- effect of healthy meals (DGE criterion) on healthy characteristics\\
-- effect of real meals subsidy on number of meals\\
-- effect of real trips subsidy on number of trips\\
-- effect of real meals subsidy on self-worth and day-to-day skills\\
+effect of\\
+- healthy meals (DGE criterion) on healthy characteristics\\
+- real meals subsidy on number of meals\\
+- real trips subsidy on number of trips\\
+- real meals subsidy on self-worth and day-to-day skills\\
+- real trips subsidy on self-worth and day-to-day skills\\
 

### 2020-02-22 ANALYSIS/DATA/Impute.R

@@ -14,21 +14,29 @@ mergedDataImputeMode <- mergedData[, colSums(is.na(mergedData)) <= sum(is.na(mer
 
 ### order by year and id
 
-mergedDataImputeInterpolation <- mergedData[, colSums(is.na(mergedData)) <= sum(is.na(mergedData$DGECriteriaNo))] %>% 
+# [, colSums(is.na(mergedData)) <= sum(is.na(mergedData$DGECriteriaNo))]
+
+mergedDataImputeInterpolation <- mergedData %>% 
   select_if(is.numeric) %>%
   arrange(id, year) %>% 
   group_by(id) %>% 
-  mutate_all(na.approx, na.rm = FALSE)
+  mutate_all(na.approx, na.rm = FALSE) %>% 
+  ungroup()
+
+NAsPerVariableMergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
+  summarise_all(list(~ sum(is.na(.)))) %>%
+  arrange(.)
+
 # %>%
   # mutate(ppentInterp = na.approx(ppent, na.rm = FALSE))
 
-mergedDataImputeInterpolation <- ungroup(purrr::modify(mergedDataImputeInterpolation, na.approx, na.rm = FALSE))
+# mergedDataImputeInterpolation <- ungroup(purrr::modify(mergedDataImputeInterpolation, na.approx, na.rm = FALSE))
 
-mergedDataImputeTest <- mergedDataImputeInterpolation %>% 
-  purrr::modify_at("tasksLunch", na.approx, na.rm = FALSE)
+# mergedDataImputeTest <- mergedDataImputeInterpolation %>% 
+  # purrr::modify_at("tasksLunch", na.approx, na.rm = FALSE)
 
-mergedDataImputeTest <- mergedDataImputeInterpolation %>% 
-  mutate_all(na.approx, na.rm = FALSE)
+# mergedDataImputeTest <- mergedDataImputeInterpolation %>% 
+#   mutate_all(na.approx, na.rm = FALSE)
 # 
 # mergedDataImputeMode <- mergedData[, colSums(is.na(mergedData)) <= sum(is.na(mergedData$DGECriteriaNo))]  
 # 

### 2020-02-22 paper.Rnw

--- 2020-02-22 paper.Rnw
@@
 - real median subsidy per institution\\
-- real median subsidy per individual\\
+- real median subsidy per beneficiary\\
 (- which variables have largest variance; also relevant for variable selection)\\

### 2020-02-22 paper.Rnw
Started including first regression table from DiD in Rnw file

@@
 
+<<echo=FALSE, results='asis'>>=
+library(stargazer)
+lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
+lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
+lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
+lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
+# table1_selfworth <- 
+stargazer(lm1_selfworth,
+                    lm2_selfworth,
+                    lm3_selfworth,
+                    lm4_selfworth,
+          title = "Regression Results",
+          order = c('Constant', 'treatEF'),
+          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+                   'dummy_2018', 'id'
+                  ),
+          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+          align = TRUE)
+# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
+# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
+# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
+# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
+@
+
+% table1_selfworth <- stargazer(lm1_selfworth,
+%                     lm2_selfworth,
+%                     lm3_selfworth,
+%                     lm4_selfworth,
+%           title = "Regression Results",
+%           order = c('Constant', 'treatEF'),
+%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+%                    'dummy_2018', 'id'
+%                   ),
+%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+%           align = TRUE)
+
+% \begin{table}[!htbp] \centering 
+%   \caption{Regression Results} 
+%   \label{} 
+% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+% \\[-1.8ex]\hline 
+% \hline \\[-1.8ex] 
+%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+% \cline{2-5} 
+% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
+% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+% \hline \\[-1.8ex] 
+%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
+%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
+%   & & & & \\ 
+%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
+%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
+%   & & & & \\ 
+% \hline \\[-1.8ex] 
+% ID fixed effects & No & No & Yes & Yes \\ 
+% Time fixed effects & No & Yes & No & Yes \\ 
+% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
+% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
+% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
+% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
+% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
+% \hline 
+% \hline \\[-1.8ex] 
+% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+% \end{tabular} 
+% \end{table}
+
 %\printbibliography

### 2020-02-22 paper.tex
Started including first regression table from DiD in Rnw file

@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'cowplot' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(`\_inherit`, env, NULL): object 'GeomCustomAnn' not found}}\end{kframe}
 
@@
 
-For our empirical analysis we define a treatment and a control group.
-Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
-On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
-Children that benefit from
-
 Empirical Approach\\
@@
 The baseline of the empirical approach is the determination of the treatment and control group.
+Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
+On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
+
+\begin{kframe}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Please cite as:}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.}}
+
+{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ R package version 5.2.2. https://CRAN.R-project.org/package=stargazer}}\end{kframe}
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Sat, Feb 22, 2020 - 8:34:59 PM
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Regression Results} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+\hline \\[-1.8ex] 
+ Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
+  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
+  & & & & \\ 
+ treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
+  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+ID fixed effects & No & No & Yes & Yes \\ 
+Time fixed effects & No & Yes & No & Yes \\ 
+Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
+Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
+Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
+F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+% table1_selfworth <- stargazer(lm1_selfworth,
+%                     lm2_selfworth,
+%                     lm3_selfworth,
+%                     lm4_selfworth,
+%           title = "Regression Results",
+%           order = c('Constant', 'treatEF'),
+%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+%                    'dummy_2018', 'id'
+%                   ),
+%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+%           align = TRUE)
+
+% \begin{table}[!htbp] \centering 
+%   \caption{Regression Results} 
+%   \label{} 
+% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+% \\[-1.8ex]\hline 
+% \hline \\[-1.8ex] 
+%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+% \cline{2-5} 
+% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
+% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+% \hline \\[-1.8ex] 
+%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
+%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
+%   & & & & \\ 
+%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
+%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
+%   & & & & \\ 
+% \hline \\[-1.8ex] 
+% ID fixed effects & No & No & Yes & Yes \\ 
+% Time fixed effects & No & Yes & No & Yes \\ 
+% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
+% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
+% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
+% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
+% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
+% \hline 
+% \hline \\[-1.8ex] 
+% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+% \end{tabular} 
+% \end{table}
 

### 2020-02-22 ANALYSIS/DATA/regression_tables.R

@@ -152,130 +152,141 @@ lm4_skills_controls <- lm(dfcEF$dayToDaySkills ~ dfcEF$treatEF + dfcEF$id + dfcE
 
 ### 5. Alle LMs als RDS speichern ####
 
-saveRDS(lm1_selfworth, file = "./ANALYSIs/Tables/lm1_selfworth.rds")
-saveRDS(lm1_skills, file = "./ANALYSIs/Tables/lm1_skills.rds")
+saveRDS(lm1_selfworth, file = "./ANALYSIS/Tables/lm1_selfworth.Rds")
+saveRDS(lm1_selfworth_controls, file = "./ANALYSIS/Tables/lm1_selfworth_controls.Rds")
+saveRDS(lm1_selfworth_controls_nobad, file = "./ANALYSIS/Tables/lm1_selfworth_controls_nobad.Rds")
+saveRDS(lm1_skills, file = "./ANALYSIS/Tables/lm1_skills.Rds")
+saveRDS(lm1_skills_controls, file = "./ANALYSIS/Tables/lm1_skills_controls.Rds")
 
-saveRDS(lm2_selfworth, file = "./ANALYSIs/Tables/lm2_selfworth.rds")
-saveRDS(lm2_skills, file = "./ANALYSIs/Tables/lm2_skills.rds")
+saveRDS(lm2_selfworth, file = "./ANALYSIS/Tables/lm2_selfworth.Rds")
+saveRDS(lm2_selfworth_controls, file = "./ANALYSIS/Tables/lm2_selfworth_controls.Rds")
+saveRDS(lm2_selfworth_controls_nobad, file = "./ANALYSIS/Tables/lm2_selfworth_controls_nobad.Rds")
+saveRDS(lm2_skills, file = "./ANALYSIS/Tables/lm2_skills.Rds")
+saveRDS(lm2_skills_controls, file = "./ANALYSIS/Tables/lm2_skills_controls.Rds")
 
-saveRDS(lm3_selfworth, file = "./ANALYSIs/Tables/lm3_selfworth.rds")
-saveRDS(lm3_skills, file = "./ANALYSIs/Tables/lm3_skills.rds")
+saveRDS(lm3_selfworth, file = "./ANALYSIS/Tables/lm3_selfworth.Rds")
+saveRDS(lm3_selfworth_controls, file = "./ANALYSIS/Tables/lm3_selfworth_controls.Rds")
[…]

### 2020-02-22 paper.Rnw
completed first stargazer table

@@
 
+% rotate tables in knitr
+% https://stackoverflow.com/questions/21840878/rotate-a-table-from-r-markdown-in-pdf
+% in particular stargazer tables
+% https://stackoverflow.com/questions/31169845/rotate-stargazer-table-in-knitr/34292292#34292292
+
 % Create list of packages used, Gandrud (2016), p 218/219
@@
 \usepackage[hidelinks]{hyperref}
+\usepackage{rotating}
 % \usepackage[authoryear]{natbib}
@@
 library(dplyr)
+library(stargazer)
 @
@@
 
-<<echo=FALSE, results='asis'>>=
-library(stargazer)
+<<echo=FALSE, results='asis', message=FALSE>>=
 lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
@@
 lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
-# table1_selfworth <- 
-stargazer(lm1_selfworth,
+
+table1_selfworth <- stargazer(lm1_selfworth,
                     lm2_selfworth,
@@
                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-          align = TRUE)
+          align = TRUE,
+          float.env = "sidewaystable")
 # row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")

### 2020-02-22 paper.tex
completed first stargazer table

@@
 % R -e 'library(knitr);knit("knitr_example.Rnw")'
+
+% rotate tables in knitr
+% https://stackoverflow.com/questions/21840878/rotate-a-table-from-r-markdown-in-pdf
+% in particular stargazer tables
+% https://stackoverflow.com/questions/31169845/rotate-stargazer-table-in-knitr/34292292#34292292
 
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'cowplot' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(`\_inherit`, env, NULL): object 'GeomCustomAnn' not found}}\end{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\# \\\#\# Please cite as:}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ Hlavac, Marek (2018). stargazer: Well-Formatted Regression and Summary Statistics Tables.}}
-
-{\ttfamily\noindent\itshape\color{messagecolor}{\#\#\ \ R package version 5.2.2. https://CRAN.R-project.org/package=stargazer}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sat, Feb 22, 2020 - 8:34:59 PM
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
+% Date and time: Sa, Feb 22, 2020 - 21:10:01
+% Requires LaTeX packages: dcolumn rotating 
+\begin{sidewaystable}[!htbp] \centering 
   \caption{Regression Results} 
@@
 \end{tabular} 
-\end{table}
+\end{sidewaystable}
 

### 2020-02-23 paper.Rnw

@@
 <<echo=FALSE, results='asis', message=FALSE>>=
+
+# first, read in all Rds objects that you need
+
 lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
@@
           align = TRUE,
+
+          # this line of code rotates the table by 90 degrees counterclockwise
+
           float.env = "sidewaystable")

### 2020-02-23 paper.Rnw
told everyone to install knitR package
changes

--- 2020-02-22 paper.Rnw
@@
 - real median subsidy per institution\\
-- real median subsidy per beneficiary\\
+- real median subsidy per individual\\
 (- which variables have largest variance; also relevant for variable selection)\\
@@
 Questions:\\
-effect of\\
-- healthy meals (DGE criterion) on healthy characteristics\\
-- real meals subsidy on number of meals\\
-- real trips subsidy on number of trips\\
-- real meals subsidy on self-worth and day-to-day skills\\
-- real trips subsidy on self-worth and day-to-day skills\\
+- effect of healthy meals (DGE criterion) on healthy characteristics\\
+- effect of real meals subsidy on number of meals\\
+- effect of real trips subsidy on number of trips\\
+- effect of real meals subsidy on self-worth and day-to-day skills\\
 
@@
 
-<<echo=FALSE, results='asis'>>=
-library(stargazer)
-lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
-lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
-lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
-lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
-# table1_selfworth <- 
-stargazer(lm1_selfworth,
-                    lm2_selfworth,
-                    lm3_selfworth,
-                    lm4_selfworth,
-          title = "Regression Results",
-          order = c('Constant', 'treatEF'),
-          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-                   'dummy_2018', 'id'
-                  ),
-          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-          align = TRUE)
-# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
-# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
-# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
-# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
-@
+Determining the treatment and control group this way, however, was a problem.
 
-% table1_selfworth <- stargazer(lm1_selfworth,
-%                     lm2_selfworth,
-%                     lm3_selfworth,
-%                     lm4_selfworth,
-%           title = "Regression Results",
-%           order = c('Constant', 'treatEF'),
-%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-%                    'dummy_2018', 'id'
-%                   ),
-%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-%           align = TRUE)
+THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
+We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
+All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
+Our analysis is based on this very strong definition of the treatment and control group.
 
-% \begin{table}[!htbp] \centering 
-%   \caption{Regression Results} 
-%   \label{} 
-% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-% \\[-1.8ex]\hline 
-% \hline \\[-1.8ex] 
-%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-% \cline{2-5} 
-% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
-% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-% \hline \\[-1.8ex] 
-%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
-%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
-%   & & & & \\ 
-%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
-%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
-%   & & & & \\ 
-% \hline \\[-1.8ex] 
-% ID fixed effects & No & No & Yes & Yes \\ 
-% Time fixed effects & No & Yes & No & Yes \\ 
-% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
-% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
-% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
-% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
-% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
-% \hline 
-% \hline \\[-1.8ex] 
-% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-% \end{tabular} 
-% \end{table}
+Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
+THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
+
+As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
+Therefore we have to use the survey answers from the Mittagstisch survey.
+
+Generally our data set contains variables from the years 2011 until 2018.
+
+The constellation of the treatment and control group varies from year to year. 
+Assumption: erhalten der treatment gleichbedeutend wie ein verlust
+
+Possible variables as dependent variables
+how we determined that:
+The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
+possible variables selfworth, day to day skills
+used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
+
+looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
+
+linear regression just to look at whether there are effects
+
+add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
+how fixed effects are implemented
+
+which control variables we use
+how we determined which controls
+
+Ende??
+the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
 

### 2020-02-23 paper.tex
minor update in paper
changes

--- 2020-02-22 paper.tex
@@
 The baseline of the empirical approach is the determination of the treatment and control group.
+Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
+On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
+
+To construct the treatment and control variables we use the available dataset after the data preparation of the original Excel files provided by children.
+
+To construct the treatment and control group
+
+\begin{table}[!htbp] \centering 
+  \caption{Regression Results} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{dayToDaySkills} \\ 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+\hline \\[-1.8ex] 
+ Constant & -0.107 & -0.193 & -0.456 & -0.742 \\ 
+  & (0.362) & (0.376) & (0.763) & (0.793) \\ 
+  & & & & \\ 
+ treatEF & 0.253^{*} & 0.266^{*} & 0.608 & 0.640^{*} \\ 
+  & (0.139) & (0.140) & (0.382) & (0.382) \\ 
+  & & & & \\ 
+ selfworth & -0.049 & -0.048 & 0.038 & 0.050 \\ 
+  & (0.105) & (0.106) & (0.139) & (0.140) \\ 
+  & & & & \\ 
+ DGECriteriaNo & 0.013 & 0.014 & -0.019 & -0.024 \\ 
+  & (0.016) & (0.017) & (0.024) & (0.027) \\ 
+  & & & & \\ 
+ subsidy & 0.00001 & 0.00000 & 0.00002 & 0.00001 \\ 
+  & (0.00000) & (0.00000) & (0.00003) & (0.00003) \\ 
+  & & & & \\ 
+ tasksLunch & 0.032 & 0.040 & 0.053 & 0.068 \\ 
+  & (0.056) & (0.057) & (0.086) & (0.088) \\ 
+  & & & & \\ 
+ monthlyCooks & 0.045 & 0.047 & 0.106 & 0.113 \\ 
+  & (0.084) & (0.085) & (0.113) & (0.113) \\ 
+  & & & & \\ 
+ weeklyCooks & 0.014 & 0.006 & 0.049 & 0.035 \\ 
+  & (0.074) & (0.074) & (0.100) & (0.101) \\ 
+  & & & & \\ 
+ shoppers & 0.110^{*} & 0.111^{*} & -0.059 & -0.047 \\ 
+  & (0.056) & (0.057) & (0.089) & (0.090) \\ 
+  & & & & \\ 
+ easyDishes & 0.006 & 0.015 & 0.257^{**} & 0.285^{***} \\ 
+  & (0.072) & (0.074) & (0.102) & (0.105) \\ 
+  & & & & \\ 
+ dietaryKnowledge & 0.210^{***} & 0.210^{***} & 0.146 & 0.151 \\ 
+  & (0.072) & (0.072) & (0.092) & (0.092) \\ 
+  & & & & \\ 
+ appreciateHealthy & -0.066 & -0.070 & -0.056 & -0.073 \\ 
+  & (0.068) & (0.071) & (0.091) & (0.097) \\ 
+  & & & & \\ 
+ foodCulture & 0.088 & 0.091 & 0.075 & 0.075 \\ 
+  & (0.083) & (0.086) & (0.137) & (0.140) \\ 
+  & & & & \\ 
+ moreConcentrated & 0.063 & 0.070 & 0.035 & 0.054 \\ 
+  & (0.077) & (0.078) & (0.108) & (0.109) \\ 
+  & & & & \\ 
+ moreBalanced & -0.082 & -0.078 & 0.040 & 0.057 \\ 
+  & (0.087) & (0.089) & (0.120) & (0.121) \\ 
+  & & & & \\ 
+ moreIndependent & 0.489^{***} & 0.480^{***} & 0.322^{***} & 0.300^{**} \\ 
+  & (0.086) & (0.088) & (0.115) & (0.118) \\ 
+  & & & & \\ 
+ moreOpen & 0.187^{**} & 0.182^{**} & -0.002 & 0.013 \\ 
+  & (0.082) & (0.083) & (0.122) & (0.123) \\ 
+  & & & & \\ 
+ moreConfidence & -0.001 & -0.008 & 0.022 & 0.004 \\ 
+  & (0.089) & (0.090) & (0.122) & (0.123) \\ 
+  & & & & \\ 
+ addressProblems & 0.060 & 0.068 & 0.136 & 0.164 \\ 
+  & (0.075) & (0.076) & (0.106) & (0.108) \\ 
+  & & & & \\ 
+ proud & -0.118 & -0.112 & 0.011 & 0.020 \\ 
+  & (0.077) & (0.078) & (0.105) & (0.107) \\ 
+  & & & & \\ 
+ enoughFood & -0.064 & -0.063 & 0.043 & 0.045 \\ 
+  & (0.068) & (0.068) & (0.107) & (0.108) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+ID fixed effects & No & No & Yes & Yes \\ 
+Time fixed effects & No & Yes & No & Yes \\ 
+Observations & \multicolumn{1}{c}{176} & \multicolumn{1}{c}{176} & \multicolumn{1}{c}{176} & \multicolumn{1}{c}{176} \\ 
+R$^{2}$ & \multicolumn{1}{c}{0.568} & \multicolumn{1}{c}{0.572} & \multicolumn{1}{c}{0.734} & \multicolumn{1}{c}{0.742} \\ 
+Adjusted R$^{2}$ & \multicolumn{1}{c}{0.512} & \multicolumn{1}{c}{0.507} & \multicolumn{1}{c}{0.535} & \multicolumn{1}{c}{0.535} \\ 
+Residual Std. Error & \multicolumn{1}{c}{0.500 (df = 155)} & \multicolumn{1}{c}{0.503 (df = 152)} & \multicolumn{1}{c}{0.489 (df = 100)} & \multicolumn{1}{c}{0.488 (df = 97)} \\ 
+F Statistic & \multicolumn{1}{c}{10.181$^{***}$ (df = 20; 155)} & \multicolumn{1}{c}{8.828$^{***}$ (df = 23; 152)} & \multicolumn{1}{c}{3.682$^{***}$ (df = 75; 100)} & \multicolumn{1}{c}{3.582$^{***}$ (df = 78; 97)} \\
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 

### 2020-02-23 paper.Rnw
Removed merge conflict remains from paper.Rnw

@@
 % IMPORTANT
-% 
+
 % Install tex distribution
@@
 % With Windows, install MikTeX
-% 
+
+% in RStudio, install.packages("knitR")
+% also, install all packages that appear in first code chunk in this file, i.e. in the one that looks like this
+% <<LoadingPackages, include=FALSE>>=
+% library(knitr)
+% library(xtable)
+% library(dplyr)
+% library(stargazer)
+% @
+
 % Go to Tools/Global Options/Sweave
@@
 % Select Typeset LaTeX into PDF using: pdfLaTeX
+
+% Use button "Compile PDF" to knit the Rnw file to a tex file and compile the tex file to a pdf file.
+
+% Always install all packages that you're asked to after having pressed "Compile PDF".
+
+% If there is no error while knitting from Rnw to tex, but an error while compiling from tex to pdf, have a look at the pdf file. It might still have worked.
 
@@
 
-Figure
+Figure\\
 
@@
 
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
+lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
+lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
+lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
+
+table1_selfworth <- stargazer(lm1_selfworth,
+                    lm2_selfworth,
+                    lm3_selfworth,
+                    lm4_selfworth,
+          title = "Regression Results",
+          order = c('Constant', 'treatEF'),
+          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+                   'dummy_2018', 'id'
+                  ),
+          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+          align = TRUE,
+
+          # this line of code rotates the table by 90 degrees counterclockwise
+
+          float.env = "sidewaystable")
+# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
+# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
+# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
+# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
+@
+
 %\printbibliography

### 2020-02-23 paper.tex
restored file path without spaces

--- 2020-02-22 paper.tex
@@
 % With Windows, install MikTeX
-% 
+
+% in RStudio, install.packages("knitR")
+% also, install all packages that appear in first code chunk in this file, i.e. in the one that looks like this
+% <<LoadingPackages, include=FALSE>>=
+% library(knitr)
+% library(xtable)
+% library(dplyr)
+% library(stargazer)
+% library(cowplot)
+% @
+
 % Go to Tools/Global Options/Sweave
@@
 
+Determining the treatment and control group this way, however, was a problem.
+
+THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
+We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
+All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
+Our analysis is based on this very strong definition of the treatment and control group.
+
+Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
+THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
+
+As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
+Therefore we have to use the survey answers from the Mittagstisch survey.
+
+Generally our data set contains variables from the years 2011 until 2018.
+
+The constellation of the treatment and control group varies from year to year. 
+Assumption: erhalten der treatment gleichbedeutend wie ein verlust
+
+Possible variables as dependent variables
+how we determined that:
+The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
+possible variables selfworth, day to day skills
+used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
+
+looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
+
+linear regression just to look at whether there are effects
+
+add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
+how fixed effects are implemented
+
+which control variables we use
+how we determined which controls
+
+Ende??
+the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
+
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 22, 2020 - 21:10:01
+% Date and time: Sun, Feb 23, 2020 - 4:40:30 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-% table1_selfworth <- stargazer(lm1_selfworth,
-%                     lm2_selfworth,
-%                     lm3_selfworth,
-%                     lm4_selfworth,
-%           title = "Regression Results",
-%           order = c('Constant', 'treatEF'),
-%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-%                    'dummy_2018', 'id'
-%                   ),
-%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-%           align = TRUE)
-
-% \begin{table}[!htbp] \centering 
-%   \caption{Regression Results} 
-%   \label{} 
-% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-% \\[-1.8ex]\hline 
-% \hline \\[-1.8ex] 
-%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-% \cline{2-5} 
-% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
-% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-% \hline \\[-1.8ex] 
-%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
-%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
-%   & & & & \\ 
-%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
-%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
-%   & & & & \\ 
-% \hline \\[-1.8ex] 
-% ID fixed effects & No & No & Yes & Yes \\ 
-% Time fixed effects & No & Yes & No & Yes \\ 
-% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
-% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
-% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
-% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
-% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
-% \hline 
-% \hline \\[-1.8ex] 
-% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-% \end{tabular} 
-% \end{table}
-
 %\printbibliography

### 2020-02-23 paper.Rnw

@@
 % library(stargazer)
+% library(cowplot)
 % @
@@
 library(stargazer)
+library(cowplot)
 @
@@
 <<echo=FALSE>>=
-totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER GRAPHS/totalRealSubTrend.Rds")
+totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealSubTrend.Rds")
 print(totalGrantsDyn)

### 2020-02-23 ANALYSIS/DATA/Impute.R
wrote function to select variables which are recorded in all years in which variable of interest was recorded

@@ -2,7 +2,7 @@ library(tidyimpute)
 library(imputeMissings)
 library(zoo)
 
-# impute missing values in all variables where there are less missing values than in DGECriteriaNo
+# impute missing values in all variables where there are fewer missing values than in DGECriteriaNo
 
 ## impute mode
 
@@ -10,23 +10,33 @@ mergedDataImputeMode <- mergedData[, colSums(is.na(mergedData)) <= sum(is.na(mer
   select_if(is.numeric) %>%    
   impute_most_freq()
 
-## impute linear interpolation
+## impute linear interpolation by group
 
-### order by year and id
+## https://stackoverflow.com/questions/33696795/r-interpolation-of-nas-by-group
 
 # [, colSums(is.na(mergedData)) <= sum(is.na(mergedData$DGECriteriaNo))]
 
 mergedDataImputeInterpolation <- mergedData %>% 
   select_if(is.numeric) %>%
-  arrange(id, year) %>% 
   group_by(id) %>% 
   mutate_all(na.approx, na.rm = FALSE) %>% 
   ungroup()
 
+selectionInterpolation <- mergedDataImputeInterpolation[, c("id", "year", outcomesMeals)]
+
+#   NAsPerVariableMergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
+#   summarise_all(list(~ sum(is.na(.)))) %>%
+#   arrange(.)
+
 NAsPerVariableMergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
-  summarise_all(list(~ sum(is.na(.)))) %>%
+  purrr::map_dfc(~sum(is.na(.))) %>% 
   arrange(.)
 
+NAsPerVariableMergedDataImputeInterpolation
+
+NAsPerVariableMergedData <- mergedData %>% 
+  select_if(is.numeric) %>% 
+  map(~sum(is.na(.)))
 # %>%
   # mutate(ppentInterp = na.approx(ppent, na.rm = FALSE))
 

### 2020-02-23 ANALYSIS/double-selection.R

@@ -59,13 +59,78 @@ outcomesTrips <- c("tripsSuggestions",
                    "tripsKnowledgeOrdinal",
                    "tripsBehaviorOrdinal")
 
+# this function returns all years in which a variable was recorded
+
+availableYears <- function(dataSet, variableName) {
+  if(is_string(variableName)) {
+    variable <- dataSet[, variableName]
+  }
+  else {
+    variable <- variableName
+  }
+  availableObservations <- dataSet %>% 
+    filter(!is.na(variable))
+  availableYears <- unique(availableObservations$year)
+  return(availableYears)
+}
+
+# availableObservations1 <- mergedData %>% 
+#   filter(!is.na(mergedData[, "id"]))
+# 
+# availableObservations2 <- mergedData %>% 
+#   filter(!is.na(mergedData$id))
+# 
+# availableYears(mergedData, mergedData$kidsTotalNo)
+# compareAvailableYears("kidsTotalNo", "DGECriteriaNo", mergedData)
+
+# This function says whether "firstVariableName" was recorded in all years in which "secondVariableName" was recorded
+
+compareAvailableYears <- function(firstVariableName, secondVariableName, dataSet) {
+  if(availableYears(dataSet, secondVariableName) %in% availableYears(dataSet, firstVariableName)){
+    return(TRUE)
+  }
+  else {
+    return(FALSE)
+  }
+}
+
+# This function returns the names of all variables in "dataSet" that were recorded in all years in which "variableName" was recorded
+
+availableVariables <- function(dataSet, variableName) {
+  comparisonAvailableYears <- map_dfc(dataSet, compareAvailableYears, variableName, dataSet) %>% 
+    select_if(is_true)
+  return(names(comparisonAvailableYears))
+}
+
+# availableVariables(mergedData, "subsidy")
+# comparisonAvailableYears <- map_dfc(mergedData, compareAvailableYears, "subsidy", mergedData) 
+# 
+# comparisonAvailableYears %>% 
+#   select_if(is_true)
+# 
+# identical(mergedData$id), mergedData[,"id"])
+# this function selects all variables of a data set that were recorded in all year in which a given variable was recorded
+# availableVariables <- function(dataset, variableName) {
+#   variable <- dataset[, variableName]
[…]

### 2020-02-23 ANALYSIS/Partition.R
created references file

@@ -9,7 +9,7 @@ library(tidyselect)
 
 #excludeNAs
 
-PartitionedData <- mergedDataImputeMode[ ,colSums(is.na(mergedDataImputeMode)) == 0]
+PartitionedData <- mergedDataImputeAll[ ,colSums(is.na(mergedDataImputeAll)) == 0]
 PartitionedData <- PartitionedData %>% 
   dplyr::select(!contains('scaled'))
 

### 2020-02-24 ANALYSIS/Summary Statistics.R
ghjk

@@ -97,3 +97,8 @@ TripsOrganisationsNumber <- TripsOrgaData%>%
 #join 
 organisationsbeneficaries <- organisations_beneficiaries %>% 
   full_join(TripsOrganisationsNumber) 
+
+organisationsbeneficaries[1,3] <- NA
+
+fundamental_dynamics = saveRDS(organisationsbeneficaries,"./ANALYSIS/Tables/fundamental_dynamics.Rds")
+

### 2020-02-24 paper.Rnw
created references file
ghjk
example for xtable adapted DiD for weights

@@
 
-% \addbibresource{Main.bib}
+\addbibresource{references.bib}
 
@@
 
+% <<results='asis', echo=FALSE>>=
+% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
+% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
+% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
+% print(tableCyclicDisp, include.rownames = FALSE)
+% @
+
+<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
+
+colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+
+fundamental_dynamics <- xtable(fundamental_dynamics,
+                               digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Summary Statistics",
+          align = "lmmmmm"
+          )
+print(fundamental_dynamics, include.rownames = FALSE)
+@
 % look up official names of price indices in English 
@@
 
-%\printbibliography
+% table1_selfworth <- stargazer(lm1_selfworth,
+%                     lm2_selfworth,
+%                     lm3_selfworth,
+%                     lm4_selfworth,
+%           title = "Regression Results",
+%           order = c('Constant', 'treatEF'),
+%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+%                    'dummy_2018', 'id'
+%                   ),
+%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+%           align = TRUE)
+
+% \begin{table}[!htbp] \centering 
+%   \caption{Regression Results} 
+%   \label{} 
+% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+% \\[-1.8ex]\hline 
+% \hline \\[-1.8ex] 
+%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+% \cline{2-5} 
+% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
+% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+% \hline \\[-1.8ex] 
+%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
+%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
+%   & & & & \\ 
+%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
+%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
+%   & & & & \\ 
+% \hline \\[-1.8ex] 
+% ID fixed effects & No & No & Yes & Yes \\ 
+% Time fixed effects & No & Yes & No & Yes \\ 
+% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
+% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
+% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
+% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
+% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
+% \hline 
+% \hline \\[-1.8ex] 
+% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+% \end{tabular} 
+% \end{table}
+
+\printbibliography
 \end{document}

### 2020-02-24 paper.Rnw
ghj

@@
 @
+<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")
+
+colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
+colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
+
+xtable(partition_meals,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Meals"
+          #align = "lmmm"
+          )
+#print(partition_meals, include.rownames = FALSE)
+
+xtable(partition_trips,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Trips"
+          #align = "lmmm"
+          )
+print(partition_meals, partition_trips, include.rownames = FALSE)
+@
 

### 2020-02-24 ANALYSIS/DATA/Impute.R

@@ -33,9 +33,9 @@ outcomesMeals <- c("participateMore",
                    "proud")
 
 outcomesTrips <- c("tripsSuggestions",
-                   "tripsDecision",
+                   "tripsDecisions",
                    "tripsOrganization",
-                   "tripsCostCalculations",
+                   "tripsCostCalculation",
                    "tripsBudget",
                    "tripsMoney",
                    "tripsReview",
@@ -44,18 +44,14 @@ outcomesTrips <- c("tripsSuggestions",
                    "tripsNewPlaces",
                    "tripsNewCommunities",
                    "tripsNewIdeas",
-                   "tripsAdditionalAcivities",
+                   "tripsAdditionalActivities",
                    "tripsSpecificSkills",
                    "tripsDayToDaySkills",
                    "tripsSuccess",
                    "tripsSelfEfficacy",
                    "tripsSelfworth", 
                    "tripsSocialSkills",
-                   "tripsFrustrationTolerance",
-                   "tripsCHILDRENSuggestionsOrdinal",
-                   "tripsReachedOrdinal",
-                   "tripsKnowledgeOrdinal",
-                   "tripsBehaviorOrdinal")
+                   "tripsFrustrationTolerance")
 
 
 # impute missing values in all variables where there are fewer missing values than in DGECriteriaNo

### 2020-02-24 paper.Rnw
minor improvements variables over time

--- 2020-02-24 paper.Rnw
@@
 
-<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
-
 fundamental_dynamics <- xtable(fundamental_dynamics,
-                               digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Summary Statistics",
-          align = "lmmmmm"
+          title = "Summary Statistics"
+          #, align = TRUE
           )
-print(fundamental_dynamics, include.rownames = FALSE)
+print(fundamental_dynamics)
 @
 % look up official names of price indices in English
+
 At the beginning of the time series in 2011, they supported in x institutions.

### 2020-02-24 ANALYSIS/PlotVariablesOverTime.R

@@ -9,55 +9,65 @@ library(ggpubr)
 
 #setthevariables
 
-response= names(mergedData)[5:213]
-expl= names(mergedData)[4]
+response= names(mergedData)
+# [5:213]
+# expl= names(mergedData)[4]
 
-response = set_names(response)
-response
+response2 = set_names(response)
+# response
 
-expl = set_names(expl)
-expl
+# expl = set_names(expl)
+# expl
 
 #createfunctionHEREGGPLOT
 
 plotOutcomeOverTime = function(x, y){
   ggplot(mergedData, aes_string(fill = y, x = x, y = y) ) +
-    #geom_bar(position="stack", stat="identity") + 
+    # geom_bar(position="stack", stat="identity") + 
     geom_col(position = position_stack(reverse = TRUE)) +  
     theme_bw()
 }
 
+# plotOutcomeOverTimeTest = function(x, y){
+#   ggplot(mergedData, aes_string(fill = y, x = x, y = y) ) +
+#     geom_bar(position = position_stack(reverse = TRUE), stat="identity") + 
+#     # geom_col(position = position_stack(reverse = TRUE)) +  
+#     theme_bw()
+# }
+
 #checkifthefunctionworks
 
-plotOutcomeOverTime("year", "lessIllOrdinal")
+test <-  plotOutcomeOverTime("year", "lessIllOrdinal")
+
+# plotOutcomeOverTimeTest("year", "lessIllOrdinal")
 
 #mapthefunction
 
-YearlyOutcome <- map(mergedData, ~plotOutcomeOverTime("year", "lessIll"))
+# YearlyOutcome <- map(mergedData, ~plotOutcomeOverTime("year", "lessIll"))
 
 all_yearPlots = map(response,
-                ~map(expl, plotOutcomeOverTime, y = .x) )
+                ~map("year", plotOutcomeOverTime, y = .x) )
 
 #printtheplots #allvaribalescanbeplotted #examples
   
-all_yearPlots$age[1:2]
-all_yearPlots$eatersPerMealNo[1:2]
-all_yearPlots$newKidsNo[1:2]
-all_yearPlots$cateringNo[1:2]
-all_yearPlots$mealsInInstitutionNo[1:2]
-all_yearPlots$weeklyCooks
-all_yearPlots$monthlyCooks
-all_yearPlots$tasksLunch
-all_yearPlots$parentalDialog
-all_yearPlots$qualitySatisfies
-all_yearPlots$trainingCompletedNo
[…]

### 2020-02-24 paper.tex
created references file
ghjk

@@
 \section{Summary Statistics}
+
+% <<results='asis', echo=FALSE>>=
+% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
+% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
+% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
+% print(tableCyclicDisp, include.rownames = FALSE)
+% @
+
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Feb 24 13:15:38 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{mmmmm}
+  \hline
+Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
+  \hline
+2011 & 3748.0 &  & 52 &  \\ 
+  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
+  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
+  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
+  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
+  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
+  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
+  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
+\end{table}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sun, Feb 23, 2020 - 4:40:30 PM
+% Date and time: Mo, Feb 24, 2020 - 13:15:39
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-%\printbibliography
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Feb 24 13:15:39 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{rllr}
+  \hline
+ & Variable, Meals & Mapping, Meals & Information, Meals \\ 
+  \hline
+1 & participateMore & participateMore & 1.00 \\ 
+  2 & tasksLunch & tasksLunch & 1.00 \\ 
+  3 & ownIdeas & ownIdeas & 1.00 \\ 
+  4 & stayLonger & stayLonger & 1.00 \\ 
+  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
+  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
+  7 & foodCulture & foodCulture & 1.00 \\ 
+  8 & lessIll & lessIll & 1.00 \\ 
+  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
+  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
+  11 & addressProblems & addressProblems & 1.00 \\ 
+  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
+  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
+  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
+  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
+  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
+  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
+  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
+  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
+  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
+  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
+  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
+  23 & reduced\_var\_3 & proud & 0.43 \\ 
+  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
+  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
+  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
+  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
+  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
+  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Meals} 
+\end{table}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Feb 24 13:15:39 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{rllr}
+  \hline
+ & Variable, Trips & Mapping, Trips & Information, Trips \\ 
+  \hline
+1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
+  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
+  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
+  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
+  5 & tripsBudget & tripsBudget & 1.00 \\ 
+  6 & tripsMoney & tripsMoney & 1.00 \\ 
+  7 & tripsReview & tripsReview & 1.00 \\ 
+  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
+  9 & tripsMobility & tripsMobility & 1.00 \\ 
+  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
+  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
+  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
+  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
+  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
+  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
+  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
+  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
+  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
+  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
+  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Trips} 
+\end{table}
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+
+% table1_selfworth <- stargazer(lm1_selfworth,
+%                     lm2_selfworth,
+%                     lm3_selfworth,
+%                     lm4_selfworth,
+%           title = "Regression Results",
+%           order = c('Constant', 'treatEF'),
+%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
+%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
+%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
+%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
+%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
+%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
+%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
+%                    'dummy_2018', 'id'
+%                   ),
+%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
+%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
+%           align = TRUE)
+
+% \begin{table}[!htbp] \centering 
+%   \caption{Regression Results} 
+%   \label{} 
+% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+% \\[-1.8ex]\hline 
+% \hline \\[-1.8ex] 
+%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+% \cline{2-5} 
+% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
+% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+% \hline \\[-1.8ex] 
+%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
+%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
+%   & & & & \\ 
+%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
+%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
+%   & & & & \\ 
+% \hline \\[-1.8ex] 
+% ID fixed effects & No & No & Yes & Yes \\ 
+% Time fixed effects & No & Yes & No & Yes \\ 
+% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
+% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
+% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
+% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
+% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
+% \hline 
+% \hline \\[-1.8ex] 
+% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+% \end{tabular} 
+% \end{table}
+
+\printbibliography
 \end{document}

### 2020-02-24 ANALYSIS/DATA/did_estimation.R
regression

@@ -1,9 +1,108 @@
 ### DiD-Schätzungen
 
 # Erstellung von Interaktionstermen, in denen die Treatment-Variable mit den Jahres-Dummies interagiert werden
+### DID Term (Interaktionsterm erstellen) ####
 
-dfcEF$treat_2011 <- (dfcEF$treatEF*dfcEF$dummy_2011)
+library(dplyr)
+library(stargazer)
 
-dfcEF$treatEF <- as.numeric(dfcEF$treatEF)
+#dfcEF <- dfcEF %>% 
+#  mutate(
+#    treat_2011 = treatEF*dummy_2011,
+#    treat_2012 = treatEF*dummy_2012,
+#    treat_2013 = treatEF*dummy_2012,
+#    treat_2014 = treatEF*dummy_2012,
+#    treat_2015 = treatEF*dummy_2012,
+#    treat_2016 = treatEF*dummy_2012,
+#    treat_2017 = treatEF*dummy_2012,
+#    treat_2012 = treatEF*dummy_2012
+#  )
 
-dfcEF$treat_2012 <- (dfcEF$treatEF*dfcEF$dummy_2012)
+dfcEF <- dfcEF %>% 
+  mutate(
+    treat_2011 = ifelse(treatEF == 1 & dummy_2011 == 1, 1, 0),
+    treat_2012 = ifelse(treatEF == 1 & dummy_2012 == 1, 1, 0),
+    treat_2013 = ifelse(treatEF == 1 & dummy_2013 == 1, 1, 0),
+    treat_2014 = ifelse(treatEF == 1 & dummy_2014 == 1, 1, 0),
+    treat_2015 = ifelse(treatEF == 1 & dummy_2015 == 1, 1, 0),
+    treat_2016 = ifelse(treatEF == 1 & dummy_2015 == 1, 1, 0),
+    treat_2017 = ifelse(treatEF == 1 & dummy_2015 == 1, 1, 0),
+    treat_2018 = ifelse(treatEF == 1 & dummy_2015 == 1, 1, 0)
+  )
+
+#id als factor definieren
+dfcEF$id <- as.factor(dfcEF$id)
+dfcEF$year <- as.factor(dfcEF$year)
+dfcEF$treatEF <- as.factor(dfcEF$treatEF)
+
+### DID Regression ####
+
+#treatEF ist der treatment Effekt
+#year ist der Year fixed effect (Zeitfixedeffect)
[…]

### 2020-02-24 ANALYSIS/DATA/regression_example.R

@@ -14,7 +14,7 @@ rm(list = ls())
 
 # install necessary packages
 
-install.packages('devtools')
+#install.packages('devtools')
 library(devtools) # load devtools package
 
 devtools::install_github("leifeld/texreg") # get developer versions of packages directly from e.g. github, in this case: https://github.com/leifeld/texreg
@@ -212,16 +212,16 @@ rm(list = ls())
 
 # Install packages 
 # You only have to do this once; if you've already installed it, simply jump to the next step
-install.packages('tidyverse') 
-install.packages('rdrobust')
-install.packages('rdd')
-install.packages('haven') 
-install.packages('labelled')
-install.packages('ggplot2')
-install.packages('ggpubr')
-install.packages('stargazer')
-install.packages('devtools')
-install.packages('pander')
+#install.packages('tidyverse') 
+#install.packages('rdrobust')
+#install.packages('rdd')
+#install.packages('haven') 
+#install.packages('labelled')
+#install.packages('ggplot2')
+#install.packages('ggpubr')
+#install.packages('stargazer')
+#install.packages('devtools')
+#install.packages('pander')
 
 # NOTE: for the installation of 'texreg' see the Rscript 'texreg_rdrobust_extract_function_LV.R'
 

### 2020-02-24 paper.tex
hjk

@@
 % If there is no error while knitting from Rnw to tex, but an error while compiling from tex to pdf, have a look at the pdf file. It might still have worked.
+
+% Julian's suggestions from February 24
+
+% Freitag: 
+% - CD mit Daten, do-files
+% - Codebook in Anhang 
+% 
+% soll nicht nach Evaluation durch LMU klingen
+% 
+% Seitenbegrenzung egal
+% 
+% Cronbach's alpha
+% 
+% immer robuste Standardfehler
+% 
+% i.year i.id
+% 
+% leading trailing - abdiskontieren
+% 
+% thematisch gegliederter Appendix
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 13:15:38 2020
+% Mon Feb 24 22:10:57 2020
 \begin{table}[ht]
@@
 % look up official names of price indices in English
+
 At the beginning of the time series in 2011, they supported in x institutions.
@@
 \end{figure}
+
+\section{Regressions}
+
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
+
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
+
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
+% Error: Unrecognized object type.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Feb 24, 2020 - 13:15:39
+% Date and time: Mo, Feb 24, 2020 - 22:10:57
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\section{Factor Analysis}
+
+\section{Appendix}
+
+A1\\ 
+Cumulative Odds Regression 
+Outliers?
+
+A2\\
+Partition
+
+In addition to the factor analysis described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+
+QUOTES FROM PAPER, describe method
+
+In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
+It might be meaningful to decide to use only one of the variables a reduced variable consists of or a summarizing one for future surveys to avoid redundancy.
+Table x shows the obtained results of the dimensionality reduction and displays x variables which haven't been reduced, and x reduced ones.
+
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 13:15:39 2020
+% Mon Feb 24 22:10:58 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 13:15:39 2020
+% Mon Feb 24 22:10:58 2020
 \begin{table}[ht]

### 2020-02-24 ANALYSIS/factor_analysis.R
factor analysis with variables that were recorded in all years

@@ -11,54 +11,15 @@
 library(tidyverse)
 library(polycor)
 library(psych)
+library(lavaan)
 
 
-ordinalVariablesMeals <- mergedData %>% 
-  dplyr::select(participateMore, 
-         tasksLunch,
-         monthlyCooks,
-         weeklyCooks,
-         shoppers,
-         ownIdeas,
-         stayLonger,
-         easyDishes,
-         dietaryKnowledge,
-         appreciateHealthy,
-         foodCulture,
-         influenceHome,
-         cookAtHome,
-         askRecipes,
-         moreConcentrated,
-         moreBalanced,
-         lessIll,
-         dayToDaySkills,
-         moreIndependent,
-         betterTeamwork,
-         betterReading,
-         betterNumbers,
-         betterGrades,
-         moreRegularSchoolVisits,
-         selfworth,
-         moreOpen,
-         moreConfidence,
-         addressProblems,
-         proud)
-         # success, # collected only for 2018
-         # enoughFood,
-         # enoughStaffLunch,
-         # enoughStaffActivities,
-         # qualitySatisfies,
-         # regionalProducts,
-         # cultureReligion,
-         # unsweetenedDrinks,
-         # noSchoolLunch,
-         # expensiveSchoolLunch,
-         # organicFoodstuff,
-         # seasonalFoodstuff,
-         # parentalDialog,
-         # friendlyEnvironment,
-         # menu,
-         # menuCycle) 
+ordinalVariablesMeals <- mergedDataImputeInterpolation %>% 
+  dplyr::select(-generalOutcomes_scaled) %>% 
+  dplyr::select(one_of(alwaysRecordedVariables)) %>% 
+  dplyr::select(tidyselect::contains('scaled') & !tidyselect::contains('trips')) %>%
+  drop_na
+         
 
 # with ML=TRUE, hetcor() takes very long to compute
 # https://john-uebersax.com/stat/tetra.htm
@@ -84,11 +45,18 @@ highCorrelationsMeals <- correlationMatrixMealsLong %>%  arrange(desc(correlatio
 # use fa.parallel to estimate optimal number of factors
 # https://www.promptcloud.com/blog/exploratory-factor-analysis-in-r/
 
[…]

### 2020-02-24 paper.Rnw

--- 2020-02-24 paper.Rnw
@@
 \end{figure}
+
+\section{Regressions}
+
+<<Grants Regressions, echo=FALSE, results='asis', message=FALSE>>=
+
+lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+
+stargazer(lm_ms, lm_ts, title = "Regression outcome: Grants", align = TRUE)  
+@
+<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=
+
+#scaled regressions
+
+lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
+lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
+lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
+
+#expanded model less ill
+
+lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+
+stargazer(lm_lDGE, lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
+@
+<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=
+
+lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
+lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized
+
+stargazer(lm_s, lm_d, lm_ss, lm_ds, title = "Regression outcome: Chance Equality", align = TRUE)
+@
 
@@
 
+\section{Factor Analysis}
+
+\section{Appendix}
+
+A1\\ 
+Cumulative Odds Regression 
+Outliers?
+
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+#read in data from vglm models
+
+@
+
+A2\\
+Partition
+
+In addition to the factor analysis described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+
+QUOTES FROM PAPER, describe method
+
+In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
+It might be meaningful to decide to use only one of the variables a reduced variable consists of or a summarizing one for future surveys to avoid redundancy.
+Table x shows the obtained results of the dimensionality reduction and displays x variables which haven't been reduced, and x reduced ones.
+
+<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")
+
+colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
+colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
+
+xtable(partition_meals,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Meals"
+          #align = "lmmm"
+          )
+#print(partition_meals, include.rownames = FALSE)
+
+xtable(partition_trips,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Trips"
+          #align = "lmmm"
+          )
+print(partition_meals, partition_trips, include.rownames = FALSE)
+@
+
 % table1_selfworth <- stargazer(lm1_selfworth,

### 2020-02-24 paper.tex
compiled pdf

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 22:10:57 2020
+% Mon Feb 24 23:58:57 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Feb 24, 2020 - 22:10:57
+% Date and time: Mon, Feb 24, 2020 - 11:59:00 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 22:10:58 2020
+% Mon Feb 24 23:59:01 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
 

### 2020-02-25 ANALYSIS/DATA/MakeGather.R
correct standardization, weighting, and ordinalization for DGECriteriaN
first regressions with factors

@@ -39,6 +39,8 @@ source(encoding = "UTF8", "./ANALYSIS/DATA/additionalVariables.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Exclude Outliers Regression.R")
 
+
+
 # source(encoding = "UTF8", "./ANALYSIS/DATA/Standardized Coefficents.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Impute.R")

### 2020-02-25 ANALYSIS/Metric Regressions.R
ghjk

@@ -83,7 +83,7 @@ summary(lessIll_DGE.lm)
 
 saveRDS(lessIll_DGE.lm,"./ANALYSIS/Tables/lessIll_DGE.lm.Rds")
 
-lessIll_DGE_scaled.lm <- lm(lessIll_scaled ~ DGECriteriaNo_scaled, data = mergedData)
+lessIll_DGE_scaled.lm <- lm(lessIll_scaled ~ DGECriteriaNoScaled, data = mergedData)
 summary(lessIll_DGE_scaled.lm) #standardized
 
 lessIll_DGE_Scaled.lm <- coeftest(lessIll_DGE_scaled.lm, vcov. = vcovHC(lessIll_DGE_scaled.lm, type = 'HC1'))
@@ -100,7 +100,7 @@ summary(Expand_LessIll.lm)
 
 saveRDS(Expand_LessIll.lm,"./ANALYSIS/Tables/Expand_LessIll.lm.Rds")
 
-Expand_LessIll_scaled.lm = lm(lessIll_scaled ~ DGECriteriaNo_scaled + regionalProducts_scaled + yearsSupportSince + realSubsidy + state, data = mergedData)
+Expand_LessIll_scaled.lm = lm(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidy + state, data = mergedData)
 summary(Expand_LessIll_scaled.lm) #standardized
 
 Expand_LessIll_scaled.lm <- coeftest(Expand_LessIll_scaled.lm, vcov. = vcovHC(Expand_LessIll_scaled.lm, type = 'HC1'))
@@ -116,7 +116,7 @@ summary(dietaryKnowledge_DGE.lm)
 
 saveRDS(dietaryKnowledge_DGE.lm,"./ANALYSIS/Tables/dietaryKnowledge_DGE.lm.Rds")
 
-dietaryKnowledge_DGE_scaled.lm <- lm(dietaryKnowledge_scaled ~ DGECriteriaNo_scaled, data = mergedData)
+dietaryKnowledge_DGE_scaled.lm <- lm(dietaryKnowledge_scaled ~ DGECriteriaNoScaled, data = mergedData)
 summary(dietaryKnowledge_DGE_scaled.lm) #standardized
 
[…]

### 2020-02-25 ANALYSIS/Metric Regressions.R
hjk

@@ -163,7 +163,7 @@ saveRDS(lessIll_DGE_IM_scaled.lm,"./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds
 
 
 
-Expand_LessIll_IM.lm = lm(lessIll ~ DGECriteriaNo + regionalProducts + yearsSupportSince + realSubsidy + state, data = mergedDataImputeInterpolation)
+Expand_LessIll_IM.lm = lm(lessIll ~ DGECriteriaNo + regionalProducts + yearsSupportSince + realSubsidy, data = mergedDataImputeInterpolation)
 summary(Expand_LessIll_IM.lm)
 
 Expand_LessIll_IM.lm <- coeftest(Expand_LessIll_IM.lm, vcov. = vcovHC(Expand_LessIll_IM.lm, type = 'HC1'))
@@ -171,7 +171,7 @@ summary(Expand_LessIll_IM.lm)
 
 saveRDS(Expand_LessIll_IM.lm,"./ANALYSIS/Tables/Expand_LessIll_IM.lm.Rds")
 # 
-Expand_LessIll_IM_scaled.lm = lm(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidy + state, data = mergedDataImputeInterpolation)
+Expand_LessIll_IM_scaled.lm = lm(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidy, data = mergedDataImputeInterpolation)
 summary(Expand_LessIll_IM_scaled.lm) #standardized
 
 Expand_LessIll_IM_scaled.lm <- coeftest(Expand_LessIll_IM_scaled.lm, vcov. = vcovHC(Expand_LessIll_IM_scaled.lm, type = 'HC1'))

### 2020-02-25 paper.Rnw
correct standardization, weighting, and ordinalization for DGECriteriaN
first regressions with factors
ghjk
hjzuiu

@@
 library(cowplot)
+library(texreg)
 @
@@
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+#outlier meals
+#outlier trips 
+#impute meals
+#imputetrips
 
-stargazer(lm_ms, lm_ts, title = "Regression outcome: Grants", align = TRUE)  
+stargazer(list(lm_ms, lm_ts), title = "Regression outcome: Grants", align = TRUE)  
 @
+
+<<Health Regressions Scatterplots, echo=FALSE, results='asis', message=FALSE>>=
+Health_plots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_plots.Rds")
+print(Health_plots)
+@
+
+<<Health Regressions percentageplots, echo=FALSE, results='asis', message=FALSE>>=
+Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
+print(Health_percentageplots)
+@
+
 <<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-stargazer(lm_lDGE, lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
+stargazer(lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
 @
@@
 \label{ModelProdu}
-\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
+\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
 \end{equation}

### 2020-02-25 ANALYSIS/DATA/MakeGather.R

@@ -1,5 +1,6 @@
 # read packages
 
+library(texreg)
 library(readxl)
 library(tidyverse)
 library(Scale)
@@ -9,6 +10,7 @@ library(lattice)
 library(survival)
 library(Formula)
 library(tidyimpute)
+
 
 # Gather and cleanup raw data files
 

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
xxx

@@ -208,20 +208,3 @@ saveRDS(lmdid2_selfworth, file = "./ANALYSIS/Tables/lmdid2_selfworth.Rds")
 
 
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-

### 2020-02-25 paper.tex
jkl
xxx

--- 2020-02-24 paper.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 22:10:57 2020
+% Tue Feb 25 15:52:14 2020
 \begin{table}[ht]
@@
 
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
+\begin{kframe}
 
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: \$ operator not defined for this S4 class}}\end{kframe}
 
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
-% Error: Unrecognized object type.
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Health\_plots): Objekt 'Health\_plots' nicht gefunden}}\end{kframe}
+
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Health\_percentageplots): Objekt 'Health\_percentageplots' nicht gefunden}}\end{kframe}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Di, Feb 25, 2020 - 15:52:15
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Regression outcome: Health} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-3} 
+\\[-1.8ex] & \multicolumn{2}{c}{ } \\ 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
+\hline \\[-1.8ex] 
+ DGECriteriaNoScaled & 0.112^{*} & 0.266^{***} \\ 
+  & (0.063) & (0.065) \\ 
+  & & \\ 
+ Constant & 0.015 & -0.026 \\ 
+  & (0.067) & (0.070) \\ 
+  & & \\ 
+\hline \\[-1.8ex] 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Di, Feb 25, 2020 - 15:52:15
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Regression outcome: Chance Equality} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
+\cline{2-5} 
+\\[-1.8ex] & \multicolumn{4}{c}{ } \\ 
+\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
+\hline \\[-1.8ex] 
+ realSubsidy & 0.003^{***} & 0.003^{***} & 0.00000 & 0.00001^{***} \\ 
+  & (0.001) & (0.001) & (0.00000) & (0.00000) \\ 
+  & & & & \\ 
+ Constant & -13.419^{**} & -13.481^{**} & -0.056 & -0.158^{***} \\ 
+  & (5.715) & (5.727) & (0.063) & (0.060) \\ 
+  & & & & \\ 
+\hline \\[-1.8ex] 
+\hline 
+\hline \\[-1.8ex] 
+\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+\end{tabular} 
+\end{table}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Feb 24, 2020 - 22:10:57
+% Date and time: Di, Feb 25, 2020 - 15:52:16
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Feb 24 22:10:58 2020
+% Tue Feb 25 15:52:16 2020
 \begin{table}[ht]

### 2020-02-25 ANALYSIS/Metric Regressions.R

@@ -7,24 +7,30 @@ library(sandwich)
 library(lmtest)
 library(modelr)
 
+
+
 #NOCHKEINEMODELLEMITOUTLIERN ERSTELLEN
 
 ##subsidy 
 #dataset: mergedData
 
-mealsNo_sub.lm <- lm(mealsNo ~ realSubsidy, data = mergedData)
-summary(mealsNo_sub.lm)
+mealsNo_sub.lm <- lm_robust(mealsNo ~ realSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(mealsNo_sub.lm) 
 
-mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
-summary(mealsNo_sub.lm)
+texreg(mealsNo_sub.lm)
+
+# mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
+# summary(mealsNo_sub.lm)
 
 saveRDS(mealsNo_sub.lm,"./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
 
-tripsNo_sub.lm <- lm(tripsNo ~ realTripsSubsidy, data = mergedData)
+tripsNo_sub.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(tripsNo_sub.lm)
 
-tripsNo_sub.lm <- coeftest(tripsNo_sub.lm, vcov. = vcovHC(tripsNo_sub.lm, type = 'HC1'))
-summary(tripsNo_sub.lm)
+# tripsNo_sub.lm <- coeftest(tripsNo_sub.lm, vcov. = vcovHC(tripsNo_sub.lm, type = 'HC1'))
+# summary(tripsNo_sub.lm)
 
 saveRDS(tripsNo_sub.lm,"./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
 

### 2020-02-25 ANALYSIS/PlotVariablesOverTime.R

@@ -67,32 +67,42 @@ all_yearPlots = map(responset,
 # all_yearPlots$moreIndependent
 # all_yearPlots$dayToDaySkills
 # all_yearPlots$dayToDaySkillsOrdinal
-# all_yearPlots$lessIllOrdinal
+#all_yearPlots$lessIll_ordered
 
 
 #plotforpresentation..explainsubsidyvalue
 
 plotOutcomeOverTime("tripsSubsidy", "tripsNo")
-plotOutcomeOverTime("realTripsSubsidy", "tripsNo")
-
-#plots for paper 
+TripsSub_plot<- plotOutcomeOverTime("realTripsSubsidy", "tripsNo")
+MealsSub_plot<- plotOutcomeOverTime("realSubsidy", "mealsNo")
 
 
 ####plots we need for the paper 
 
-lessIll_Time<- all_yearPlots$lessIllOrdinal
-appreciateHealthy_Time<- all_yearPlots$appreciateHealthyOrdinal 
-dietaryKnowledge_Time<- all_yearPlots$dietaryKnowledgeOrdinal
+lessIll_Time<- plotOutcomeOverTime("year", "lessIll_ordered")
+appreciateHealthy_Time<- plotOutcomeOverTime("year", "appreciateHealthy_ordered")
+dietaryKnowledge_Time<- plotOutcomeOverTime("year", "dietaryKnowledge_ordered")
 
-saveRDS(lessIll_Time, "./ANALYSIS/GRAPHS/PAPER/lessIll_Time.Rds")
-saveRDS(AppreciateHealthy_Time, "./ANALYSIS/GRAPHS/PAPER/appreciateHealthy_time.Rds")
-saveRDS(DietaryKnowledge_Time, "./ANALYSIS/GRAPHS/PAPER/dietaryKnowledge_Time.Rds")
+Health_Year <- plot_grid(lessIll_Time, dietaryKnowledge_Time, appreciateHealthy_Time, 
+                          ncol = 2, nrow = 2, align = "hv",
+                          labels = "AUTO",
+                          label_x = 0, label_y = 0, hjust = -3, vjust = 
+                            -1.5, label_fontface = "plain", label_size = 11)
 
-selfworth_Time <- all_yearPlots$selfworthOrdinal
-dayToDaySkills_Time <- all_yearPlots$dayToDaySkillsOrdinal
 
[…]

### 2020-02-25 ANALYSIS/factor_analysis.R

@@ -23,7 +23,7 @@ ordinalVariablesMeals <- mergedDataImputeInterpolation %>%
 ordinalVariablesMealsFA <- ordinalVariablesMeals %>% 
   dplyr::select(-DGECriteriaNoScaled)
 
-lessIllDGECriteriaNo_scaled <- ordinalVariablesMeals %>% 
+lessIll_DGECriteriaNo <- ordinalVariablesMeals %>% 
   dplyr::select(DGECriteriaNoScaled, lessIll_scaled) %>% 
   data.frame()
 
@@ -55,16 +55,39 @@ numberFactorsMeals <- fa.parallel(correlationMatrixMeals$correlations, fm = 'ml'
 
 # fa.parallel(correlationMatrixMeals$correlations, fm = 'ml', fa = 'fa', n.obs = 300) suggests that the number of factors =  9
 
+# perform exploratory factor analysis on these variables 
+
+names(ordinalVariablesMealsFA)
+
+# this is the factor analysis
+
 factorAnalysisMeals <- fa(ordinalVariablesMealsFA, nfactors = numberFactorsMeals$nfact, scores = "regression", n.obs = nrow(ordinalVariablesMealsFA), rotate = "varimax", fm = "ml")
 
-# factorAnalysisMeals2 <- fa(ordinalVariablesMeals, nfactors = 2, scores="regression", n.obs = 48, rotate = "varimax", fm = "ml")
-
-scoresMeals <- data.frame(factorAnalysisMeals$scores)
-dfFATest <- cbind.data.frame(scoresMeals, lessIllDGECriteria_scaled)
-
-lmFAtest <- lm(lessIll_scaled ~ DGECriteriaNoScaled + ML1 + ML2 + ML3, dfFATest)
+# show factor loadings
 
 loadings(factorAnalysisMeals)
+
+# save factor scores
+
+scoresMeals <- data.frame(factorAnalysisMeals$scores)
+
+# append variables lessIll_scaled and DGECriteria_scaled to matrix with factor scores
+
+lessIll_DGECriteriaNo_scoresMeals <- cbind.data.frame(scoresMeals, lessIll_DGECriteriaNo)
+
+# show first couple of values of each variable
+
+str(lessIll_DGECriteriaNo_scoresMeals)
+
+# regress lessIll_scaled on DGECriteriaNoScaled, with factors as controls
+
[…]

### 2020-02-25 paper.Rnw
comments in factor analysis
fghj
moved examples in Rnw file upwards
deleted superfluous stuff

@@
 
+% models with robust standard errors texreg
+% https://github.com/DeclareDesign/estimatr/issues/316
+
 \documentclass[12pt, a4paper]{article}
@@
 \listoffigures
+
+Examples\\
+
+Equation with\\
+
+\begin{equation}
+\label{ModelProdu}
+\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
+\end{equation}
+
+List\\
+
+\begin{itemize}
+  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
+  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
+  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
+\end{itemize}
+
+Figure\\
+
+\begin{figure}
+  \caption{Dispersion in productivity levels}
+  \label{LineDisp}
+
+<<echo=FALSE>>=
+figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
+print(figureLineDisp)
+@
+
+\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
+A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
+After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
+The shaded bars represent recessions as defined by the NBER.
+The year ticks refer to January 1.
+The dispersion measures take as their date the middle of the year, July 2.
+Compare Kehrig (2015), Figure 1.}
+\end{figure}
+
+% <<results='asis', echo=FALSE>>=
+% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
+% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
+% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
+% print(tableCyclicDisp, include.rownames = FALSE)
+% @
+
+Regression fit ouput with texreg
+
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
 \section{Summary Statistics}
-
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
 
@@
 
+<<Health Regressions time plots, echo=FALSE, results='asis', message=FALSE>>=
+Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
+print(Health_timeplots)
+@
+
 <<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 @
-
-Examples\\
-
-Equation\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-Figure\\
-
-\begin{figure}
-  \caption{Dispersion in productivity levels}
-  \label{LineDisp}
-
-<<echo=FALSE>>=
-figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-print(figureLineDisp)
-@
-
-\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-\end{figure}
-
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
           float.env = "sidewaystable")
-# row.names(tableDispSumm) <- c("$Disp_t^n$", "$Disp_t^d$", "$Disp_t^a$", "$Y_t^n$", "$Y_t^d$", "$GDP_t$")
-# colnames(tableDispSumm) <- c("$Corr(X_t, X_{t-1})$", "$\\sigma(X)$", "$\\frac{\\sigma(X)}{\\sigma(Y)}$", "$\\frac{\\sigma(X)}{\\sigma(GDP)}$")
-# tableDispSumm <- xtable(tableDispSumm, caption = "Productivity dispersion: Summary statistics", digits = 3, align = "crccc")
-# print(tableDispSumm, sanitize.text.function = function(x) {x}, caption.placement = "top")
 @
@@
 
-% table1_selfworth <- stargazer(lm1_selfworth,
-%                     lm2_selfworth,
-%                     lm3_selfworth,
-%                     lm4_selfworth,
-%           title = "Regression Results",
-%           order = c('Constant', 'treatEF'),
-%           omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-%                    'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-%                    'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-%                    'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-%                    'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-%                    'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-%                    'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-%                    'dummy_2018', 'id'
-%                   ),
-%           add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-%                            c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-%           align = TRUE)
-
-% \begin{table}[!htbp] \centering 
-%   \caption{Regression Results} 
-%   \label{} 
-% \begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-% \\[-1.8ex]\hline 
-% \hline \\[-1.8ex] 
-%  & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-% \cline{2-5} 
-% \\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
-% \\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-% \hline \\[-1.8ex] 
-%  Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
-%   & (0.065) & (0.095) & (0.092) & (0.107) \\ 
-%   & & & & \\ 
-%  treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
-%   & (0.074) & (0.097) & (0.075) & (0.100) \\ 
-%   & & & & \\ 
-% \hline \\[-1.8ex] 
-% ID fixed effects & No & No & Yes & Yes \\ 
-% Time fixed effects & No & Yes & No & Yes \\ 
-% Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
-% R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
-% Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
-% Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
-% F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
-% \hline 
-% \hline \\[-1.8ex] 
-% \textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-% \end{tabular} 
-% \end{table}
-
 \printbibliography

### 2020-02-25 paper.Rnw
ghjk

--- 2020-02-25 paper.Rnw
@@
 % Create list of packages used, Gandrud (2016), p 218/219
+
+% models with robust standard errors texreg
+% https://github.com/DeclareDesign/estimatr/issues/316
 
@@
 
-<<Health Regressions Scatterplots, echo=FALSE, results='asis', message=FALSE>>=
-Health_plots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_plots.Rds")
-print(Health_plots)
-@
-
-<<Health Regressions percentageplots, echo=FALSE, results='asis', message=FALSE>>=
+\begin{figure}
+  \caption{Health Outcomes versus Healthy Meals}
+  \label{Health_Plots}
+<<Health Regressions percentageplots, echo=FALSE, message=FALSE>>=
 Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
 print(Health_percentageplots)
+@
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+According to information from CHILDREN, they ask the organizations to send them their menus.
+An ecotrophologist collaborating with CHILDREN assesed the menus.
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
+
+<<Health Regressions time plots, echo=FALSE, message=FALSE>>=
+Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
+print(Health_timeplots)
 @

### 2020-02-25 paper.tex
ghjk

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 15:52:14 2020
+% Tue Feb 25 17:16:40 2020
 \begin{table}[ht]
@@
 
-\begin{kframe}
+\begin{figure}
+  \caption{Health Outcomes versus Healthy Meals}
+  \label{Health_Plots}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_percentageplots-1}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Health\_plots): Objekt 'Health\_plots' nicht gefunden}}\end{kframe}
+}
 
-\begin{kframe}
+\end{knitrout}
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+According to information from CHILDREN, they ask the organizations to send them their menus.
+An ecotrophologist collaborating with CHILDREN assesed the menus.
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered.
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Health\_percentageplots): Objekt 'Health\_percentageplots' nicht gefunden}}\end{kframe}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_time_plots-1}
+
+}
+
+\end{knitrout}
 
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 15:52:15
+% Date and time: Di, Feb 25, 2020 - 17:16:42
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 15:52:15
+% Date and time: Di, Feb 25, 2020 - 17:16:42
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 15:52:16
+% Date and time: Di, Feb 25, 2020 - 17:16:43
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 15:52:16 2020
+% Tue Feb 25 17:16:43 2020
 \begin{table}[ht]

### 2020-02-25 ANALYSIS/PlotVariablesOverTime.R

@@ -84,7 +84,7 @@ appreciateHealthy_Time<- plotOutcomeOverTime("year", "appreciateHealthy_ordered"
 dietaryKnowledge_Time<- plotOutcomeOverTime("year", "dietaryKnowledge_ordered")
 
 Health_Year <- plot_grid(lessIll_Time, dietaryKnowledge_Time, appreciateHealthy_Time, 
-                          ncol = 2, nrow = 2, align = "hv",
+                          ncol = 1, nrow = 3, align = "v",
                           labels = "AUTO",
                           label_x = 0, label_y = 0, hjust = -3, vjust = 
                             -1.5, label_fontface = "plain", label_size = 11)
@@ -96,7 +96,7 @@ selfworth_Time <- plotOutcomeOverTime("year", "selfworth_ordered")
 dayToDaySkills_Time <- plotOutcomeOverTime("year", "dayToDaySkills_ordered")
 
 Equality_Year <- plot_grid(selfworth_Time, dayToDaySkills_Time, 
-                         ncol = 2, nrow = 1, align = "hv",
+                         ncol = 1, nrow = 2, align = "v",
                          labels = "AUTO",
                          label_x = 0, label_y = 0, hjust = -3, vjust = 
                            -1.5, label_fontface = "plain", label_size = 11)

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
DiD-Estimation

@@ -65,7 +65,7 @@ saveRDS(lmdid_dayToDaySkills, file = "./ANALYSIS/Tables/lmdid_dayToDaySkills.Rds
 
 ### b) Selfworth:
 
-lmdid_selfworth <- lm(dfcEF$selfworth_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year + dfcEF$newKidsNo)
+lmdid_selfworth <- lm(dfcEF$selfworth_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year)
 summary(lmdid_selfworth)
 
 # Berechnung von robusten Standardfehlern, indem eine Heteroskedastität-konsistente Varianz-Kovarianz-Matrix
@@ -91,10 +91,6 @@ table_did_selfworth <- stargazer(lmdid_selfworth,
 
 # Regressionstables als RDS speichern
 saveRDS(lmdid_selfworth, file = "./ANALYSIS/Tables/lmdid_selfworth.rds")
-
-
-
-
 
 
 
@@ -209,23 +205,109 @@ dfcEF2 <- dfcEF
 # Sobald eine Einrichtung i das Treatment erhält, ist der Treatment-Dummy für die folgenden Perioden 
 # immer gleich 1 (= Einmal Treatment, immer Treatment)
 
-# Identifizieren aller Einrichtungen, bei denen das Treatment-Status von Treat = 1 auf Treat = 0 wechselt
+# Identifizieren aller Einrichtungen, bei denen das Treatment-Status von TreatEF = 1 auf TreatEF = 0 wechselt
 
 dfcEF_check <- dfcEF2
 
 dfcEF_check <- dfcEF_check %>% 
   dplyr :: select(id, treatEF)
 
+# Identifizierte Einrichtungen mit folgenden ID's: 113, 141, 191, 221, 226 und 282
+
+# Sobald eine Einrichtung das Treatment erhält, gilt TreatEF = 1 für alle Folgejahre
+# Für die identifizierten Einrichtungen wird der Treatment-Status von TreatEF = 0 auf TreatEF = 1 für alle
+# Jahre ab dem ersten Treatment geändert.
+
+dfcEF2 [67, "treatEF"] <- 1
+dfcEF2 [168, "treatEF"] <- 1
[…]

### 2020-02-25 paper.Rnw

--- 2020-02-25 paper.Rnw
@@
 
-<<Health Regressions Scatterplots, echo=FALSE, results='asis', message=FALSE>>=
-Health_plots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_plots.Rds")
-print(Health_plots)
-@
-
-<<Health Regressions percentageplots, echo=FALSE, results='asis', message=FALSE>>=
+\begin{figure}
+  \caption{Health Outcomes versus Healthy Meals}
+  \label{Health_Plots}
+<<Health Regressions percentageplots, echo=FALSE, message=FALSE>>=
 Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
@@
 @
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+According to information from CHILDREN, they ask the organizations to send them their menus.
+An ecotrophologist collaborating with CHILDREN assesed the menus.
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
 
-<<Health Regressions time plots, echo=FALSE, results='asis', message=FALSE>>=
+<<Health Regressions time plots, echo=FALSE, message=FALSE>>=
 Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
DiD Estimation

@@ -309,4 +309,4 @@ table_did3_selfworth <- stargazer(lmdid3_selfworth,
 # Regressionstables als RDS speichern
 saveRDS(lmdid_selfworth, file = "./ANALYSIS/Tables/lmdid3_selfworth.rds")
 
-
+With controls

### 2020-02-25 paper.Rnw
additional examples

@@
 
-Regression fit ouput with texreg
+Regression fit output with texreg\\
+
+<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
+# , message=FALSE, warning=FALSE
+# first, read in all Rds objects that you need
+
+mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+
+texreg(list(mealsNo_sub.lm, tripsNo_sub.lm))
+@
 
@@
 
-<<Grants Regressions, echo=FALSE, results='asis', message=FALSE>>=
+<<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=
 
@@
   \label{Health_Plots}
-<<Health Regressions percentageplots, echo=FALSE, message=FALSE>>=
+<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
 Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
@@
 
-<<Health Regressions time plots, echo=FALSE, message=FALSE>>=
+<<HealthRegressionsTimePlots, echo=FALSE, message=FALSE>>=
 Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
@@
 
-<<Health Regressions, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 @
-<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=
+
+<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
 

### 2020-02-25 ANALYSIS/Metric Regressions.R

@@ -6,6 +6,7 @@ library(broom)
 library(sandwich)
 library(lmtest)
 library(modelr)
+library(texreg)
 
 
 
@@ -18,7 +19,7 @@ mealsNo_sub.lm <- lm_robust(mealsNo ~ realSubsidy, data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub.lm) 
 
-texreg(mealsNo_sub.lm)
+
 
 # mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
 # summary(mealsNo_sub.lm)

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
Update

@@ -309,4 +309,5 @@ table_did3_selfworth <- stargazer(lmdid3_selfworth,
 # Regressionstables als RDS speichern
 saveRDS(lmdid_selfworth, file = "./ANALYSIS/Tables/lmdid3_selfworth.rds")
 
-With controls
+
+# Kontrollvariablen: total cost, subsidy, eatersPerMealNo

### 2020-02-25 paper.tex

@@
 
+Examples\\
+
+Equation with\\
+
+\begin{equation}
+\label{ModelProdu}
+\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
+\end{equation}
+
+List\\
+
+\begin{itemize}
+  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
+  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
+  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
+\end{itemize}
+
+Figure\\
+
+\begin{figure}
+  \caption{Dispersion in productivity levels}
+  \label{LineDisp}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-1-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
+A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
+After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
+The shaded bars represent recessions as defined by the NBER.
+The year ticks refer to January 1.
+The dispersion measures take as their date the middle of the year, July 2.
+Compare Kehrig (2015), Figure 1.}
+\end{figure}
+
+% <<results='asis', echo=FALSE>>=
+% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
+% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
+% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
+% print(tableCyclicDisp, include.rownames = FALSE)
+% @
+
+Regression fit output with texreg\\
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c }
+\hline
+ & Model 1 & Model 2 \\
+\hline
+(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
+                 & $(5192.86)$     & $(0.33)$     \\
+realSubsidy      & $2.61^{***}$    &              \\
+                 & $(0.57)$        &              \\
+realTripsSubsidy &                 & $0.00^{*}$   \\
+                 &                 & $(0.00)$     \\
+\hline
+R$^2$            & 0.43            & 0.05         \\
+Adj. R$^2$       & 0.43            & 0.04         \\
+Num. obs.        & 329             & 322          \\
+RMSE             & 39992.79        & 2.96         \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\caption{Statistical models}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
@@
 
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
-
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 17:16:40 2020
+% Tue Feb 25 17:48:03 2020
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_percentageplots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsPercentageplots-1}
 
@@
 In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
 The x-axis plots the index for a healthy diet.
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_time_plots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsTimePlots-1}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:16:42
+% Date and time: Di, Feb 25, 2020 - 17:48:07
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:16:42
+% Date and time: Di, Feb 25, 2020 - 17:48:08
 % Requires LaTeX packages: dcolumn 
@@
 \end{table}
-
-Examples\\
-
-Equation\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-Figure\\
-
-\begin{figure}
-  \caption{Dispersion in productivity levels}
-  \label{LineDisp}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-\end{figure}
-
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:16:43
+% Date and time: Di, Feb 25, 2020 - 17:48:08
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 17:16:43 2020
+% Tue Feb 25 17:48:08 2020
 \begin{table}[ht]

### 2020-02-25 paper.Rnw
bk

--- 2020-02-25 paper.Rnw
@@
 \begin{figure}
-  \caption{Yearly dynamics of total grants in Meals program}
+  \caption{Yearly dynamics of total grants in Meals and Trips program}
   \label{totalGrantsDyn}
 
-<<echo=FALSE>>=
-totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealSubTrend.Rds")
+<<Grant Trend, echo=FALSE, message=FALSE>>=
+totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
 print(totalGrantsDyn)
@@
 
-\floatfoot{This graph shows the development of the sum of all grants in the Meals program.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+We distinguish between the sum of grants in one year, the median and the median grant per beneficiary.
+From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
+\begin{figure}
+  \caption{Health outcome over time}
+  \label{Health_timeplots}
+<<Health time plots, echo=FALSE, message=FALSE>>=
+Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
+print(Health_timeplots)
+@
+\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
+
+\begin{figure}
+  \caption{Equality of opportunities over time}
+  \label{Equality_timeplots}
+<<Equality time plots, echo=FALSE, message=FALSE>>=
+Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
+print(Equality_timeplots)
+@
+\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
 \end{figure}
@@
 
-stargazer(list(lm_ms, lm_ts), title = "Regression outcome: Grants", align = TRUE)  
+texreg(list(lm_ms, lm_ts), caption = "Grants Regressions", custom.model.names = c("Number of Meals", "Number of Trips"))
 @
@@
 \end{figure}
-
-<<Health Regressions time plots, echo=FALSE, message=FALSE>>=
-Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
-print(Health_timeplots)
-@
 

### 2020-02-25 paper.tex
bk

@@
 
-Regression fit output with texreg\\
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c }
-\hline
- & Model 1 & Model 2 \\
-\hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     \\
-realSubsidy      & $2.61^{***}$    &              \\
-                 & $(0.57)$        &              \\
-realTripsSubsidy &                 & $0.00^{*}$   \\
-                 &                 & $(0.00)$     \\
-\hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-\caption{Statistical models}
-\label{table:coefficients}
-\end{center}
-\end{table}
+Regression fit ouput with texreg
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 17:48:03 2020
+% Tue Feb 25 18:51:50 2020
 \begin{table}[ht]
@@
 \begin{figure}
-  \caption{Yearly dynamics of total grants in Meals program}
+  \caption{Yearly dynamics of total grants in Meals and Trips program}
   \label{totalGrantsDyn}
@@
 \begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{verbatim}
-## NULL
-\end{verbatim}
-\end{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Grant_Trend-1}
+
+}
+
 \end{knitrout}
 
-\floatfoot{This graph shows the development of the sum of all grants in the Meals program.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+We distinguish between the sum of grants in one year, the median and the median grant per beneficiary.
+From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
+\begin{figure}
+  \caption{Health outcome over time}
+  \label{Health_timeplots}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Health_time_plots-1}
+
+}
+
+\end{knitrout}
+\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
+
+\begin{figure}
+  \caption{Equality of opportunities over time}
+  \label{Equality_timeplots}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Equality_time_plots-1}
+
+}
+
+\end{knitrout}
+\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
 \end{figure}
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: \$ operator not defined for this S4 class}}\end{kframe}
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c }
+\hline
+ & Number of Meals & Number of Trips \\
+\hline
+(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
+                 & $(5192.86)$     & $(0.33)$     \\
+realSubsidy      & $2.61^{***}$    &              \\
+                 & $(0.57)$        &              \\
+realTripsSubsidy &                 & $0.00^{*}$   \\
+                 &                 & $(0.00)$     \\
+\hline
+R$^2$            & 0.43            & 0.05         \\
+Adj. R$^2$       & 0.43            & 0.04         \\
+Num. obs.        & 329             & 322          \\
+RMSE             & 39992.79        & 2.96         \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\caption{Grants Regressions}
+\label{table:coefficients}
+\end{center}
+\end{table}
 
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsPercentageplots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Health_Regressions_percentageplots-1}
 
@@
 
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsTimePlots-1}
-
-}
-
-\end{knitrout}
-
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:48:07
+% Date and time: Di, Feb 25, 2020 - 18:51:55
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:48:08
+% Date and time: Di, Feb 25, 2020 - 18:51:55
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 17:48:08
+% Date and time: Di, Feb 25, 2020 - 18:51:55
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 17:48:08 2020
+% Tue Feb 25 18:51:55 2020
 \begin{table}[ht]

### 2020-02-25 ANALYSIS/Coefficient Test Regression.R

@@ -1,0 +1,135 @@
+#coeftest regressions for robust standard errors
+
+##mealsno and tripsno
+
+#mergedData
+mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
+summary(mealsNo_sub.lm)
+
+tripsNo_sub.lm <- coeftest(tripsNo_sub.lm, vcov. = vcovHC(tripsNo_sub.lm, type = 'HC1'))
+summary(tripsNo_sub.lm)
+
+#excludedOutliers
+mealsNo_sub_ex.lm <- coeftest(mealsNo_sub_ex.lm, vcov. = vcovHC(mealsNo_sub_ex.lm, type = 'HC1'))
+summary(mealsNo_sub_ex.lm)
+
+tripsNo_sub_ex.lm <- coeftest(tripsNo_sub_ex.lm, vcov. = vcovHC(tripsNo_sub_ex.lm, type = 'HC1'))
+summary(tripsNo_sub_ex.lm)
+
+#impute
+
+mealsNo_sub_IM.lm <- coeftest(mealsNo_sub_IM.lm, vcov. = vcovHC(mealsNo_sub_IM.lm, type = 'HC1'))
+summary(mealsNo_sub_IM.lm)
+
+tripsNo_sub_IM.lm <- coeftest(tripsNo_sub_IM.lm, vcov. = vcovHC(tripsNo_sub_IM.lm, type = 'HC1'))
+summary(tripsNo_sub_IM.lm)
+
+#health influence
+
+#mergedData
+lessIll_DGE.lm <- coeftest(lessIll_DGE.lm, vcov. = vcovHC(lessIll_DGE.lm, type = 'HC1'))
+summary(lessIll_DGE.lm)
+
+lessIll_DGE_Scaled.lm <- coeftest(lessIll_DGE_scaled.lm, vcov. = vcovHC(lessIll_DGE_scaled.lm, type = 'HC1'))
+summary(lessIll_DGE_scaled.lm)
+
+Expand_LessIll.lm <- coeftest(Expand_LessIll.lm, vcov. = vcovHC(Expand_LessIll.lm, type = 'HC1'))
+summary(Expand_LessIll.lm)
+
+Expand_LessIll_scaled.lm <- coeftest(Expand_LessIll_scaled.lm, vcov. = vcovHC(Expand_LessIll_scaled.lm, type = 'HC1'))
+summary(Expand_LessIll_scaled.lm)
[…]

### 2020-02-25 ANALYSIS/Metric Regressions.R

@@ -8,9 +8,6 @@ library(lmtest)
 library(modelr)
 
 
-
-#NOCHKEINEMODELLEMITOUTLIERN ERSTELLEN
-
 ##subsidy 
 #dataset: mergedData
 
@@ -20,56 +17,45 @@ summary(mealsNo_sub.lm)
 
 texreg(mealsNo_sub.lm)
 
-# mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
-# summary(mealsNo_sub.lm)
-
 saveRDS(mealsNo_sub.lm,"./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+
 
 tripsNo_sub.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(tripsNo_sub.lm)
 
-# tripsNo_sub.lm <- coeftest(tripsNo_sub.lm, vcov. = vcovHC(tripsNo_sub.lm, type = 'HC1'))
-# summary(tripsNo_sub.lm)
+texreg(tripsNo_sub.lm)
 
 saveRDS(tripsNo_sub.lm,"./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
 
 
 #dataset with excluded outliers: mealsNo / tripsNo
 
-mealsNo_sub_ex.lm <- lm(mealsNo ~ realSubsidy, data = mealsNoEliminated)
+mealsNo_sub_ex.lm <- lm(mealsNo ~ realSubsidy, data = mealsNoOutliers)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub_ex.lm)
 
-mealsNo_sub_ex.lm <- coeftest(mealsNo_sub_ex.lm, vcov. = vcovHC(mealsNo_sub_ex.lm, type = 'HC1'))
-summary(mealsNo_sub_ex.lm)
+texreg(mealsNo_sub_ex.lm)
 
 saveRDS(mealsNo_sub_ex.lm,"./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")
 
-tripsNo_sub_ex.lm <- lm(tripsNo ~ realTripsSubsidy, data = tripsNoEliminated)
-summary(tripsNo_sub_ex.lm)
 
[…]

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
DiD Estimation

@@ -13,7 +13,7 @@ library(stargazer)
 
 
 
-### Zeit-variables Treatment ### ----------------------------------------
+### Zeit-variabler Treatment-Dummy ### ----------------------------------------
 
 ### Variante 1: Regression für DiD-Estimation ###
 
@@ -34,15 +34,38 @@ dfcEF$year <- as.factor(dfcEF$year)
 dfcEF$treatEF <- as.numeric(dfcEF$treatEF)
 
 # Für die oben beschriebene Regression wird der Befehl lm() verwendet, wobei lm() zunächst normale
-# Standardfehler berechnet. Die Regression wird unter "lmdid" gespeichert
+# Standardfehler berechnet. Für die erste Regression werden keine Kontrollvariablen verwendet.
+# Für die zweite Regression werden dann Einrichtungs-spezifische Kontrollvariablen implementiert:
+# Subsidy und Total Cost 
+
+# Ohne Kontrollvariablen
 lmdid_dayToDaySkills <- lm(dfcEF$dayToDaySkills_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year)
 summary(lmdid_dayToDaySkills)
 
+# Mit Kontrollvariablen
+# Problem: Die Kontrollvariablen "dfcEF$subsidy" und "dfcEF$totalCost" sind in Euro-Einheiten angegeben,
+# sodass der Regressionskoeffizient der beiden Variablen erst an der 5. - 7. Nachkommastelle eine Zahl
+# enthält und im Regressiontable somit ein Regressionskoeffizient von 0 ausgewiesen wird.
+# Lösung: Die Kontrollvariablen "dfcEF$subsidy" und "dfcEF$totalCost" werden durch 1000 geteilt. 
+
+# dfcEF$subsidy <- (dfcEF$subsidy/1000)
+# dfcEF$totalCost <- (dfcEF$totalCost/1000)
+
+lmdid_dayToDaySkills_controls <- lm(dfcEF$dayToDaySkills_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year
+                                    + dfcEF$subsidy + dfcEF$totalCost)
+summary(lmdid_dayToDaySkills_controls)
+
+
 # Berechnung von robusten Standardfehlern, indem eine Heteroskedastität-konsistente Varianz-Kovarianz-Matrix
[…]

### 2020-02-25 ANALYSIS/DATA/Standardize.R
ghj

@@ -60,9 +60,9 @@ tripsNoEliminated$dayToDaySkills_scaled<-scale(tripsNoEliminated$dayToDaySkills)
 # mergedDataImputeMode$realSubsidy_scaled<-scale(mergedDataImputeMode$realSubsidy)
 # mergedDataImputeMode$tripsNo_scaled<-scale(mergedDataImputeMode$tripsNo)
 # mergedDataImputeMode$realTripsSubsidy_scaled<-scale(mergedDataImputeMode$realTripsSubsidy)
-# mergedDataImputeMode$lessIll_scaled<-scale(mergedDataImputeMode$lessIll)
+mergedDataImputeInterpolation$lessIll_scaled<-scale(mergedDataImputeInterpolation$lessIll)
 # mergedDataImputeMode$DGECriteriaNo_scaled<-scale(mergedDataImputeMode$DGECriteriaNo)
-# mergedDataImputeMode$regionalProducts_scaled<-scale(mergedDataImputeMode$regionalProducts)
+mergedDataImputeInterpolation$regionalProducts_scaled<-scale(mergedDataImputeInterpolation$regionalProducts)
 # mergedDataImputeMode$dietaryKnowledge_scaled<-scale(mergedDataImputeMode$dietaryKnowledge)
 # mergedDataImputeMode$selfworth_scaled<-scale(mergedDataImputeMode$selfworth)
 # mergedDataImputeMode$dayToDaySkills_scaled<-scale(mergedDataImputeMode$dayToDaySkills)

### 2020-02-25 paper.Rnw
Imputed variables can take values in between integers between 0 and 4

--- 2020-02-25 paper.Rnw
@@
 \usepackage[onehalfspacing]{setspace}
-\usepackage[left = 72 pt, right = 72 pt]{geometry}
+\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
 
@@
 \title{Effects of CHILDREN's programs}
-\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
+\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz (11574909), Yannick Zurl}
 \date{27th February 2020}
@@
 \listoffigures
+
+\begin{abstract} 
+abstract on separate page
+100 - 150 words
+\end{abstract}
 
@@
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
@@
 
+the introduction should include: motivation, precise research questions, very short literature review, most important results, further proceedings
+
 CHILDREN's aims for data analysis\\ 
@@
 Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
+
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
 
+\section{Conclusion}
+
+\printbibliography
+
 \section{Appendix}
 
-A1\\ 
-Cumulative Odds Regression 
+\subsection{A1: Cumulative Odds Regression}
+
 Outliers?
@@
 
-A2\\
-Partition
+\subsection{A2: Partition}
 
@@
 
-\printbibliography
+\{Ehrenwörtliche Erklärung aller Teilnehmer}
+
 \end{document}

### 2020-02-25 ANALYSIS/DATA/categoricalData.R

@@ -10,7 +10,7 @@ library(purrr)
 library(tidyselect)
 library(stringr)
 
-categories <- c(NA, 0, 1, 2, 3, 4)
+categories <- c(NA, 0, 1, 2, 3, 4, 1/2, 3/2, 5/2, 7/2, 1/3, 2/3, 4/3, 5/3, 7/3, 8/3, 10/3, 11/3, 1/4, 3/4, 5/4, 7/4, 9/4, 11/4, 13/4, 15/4, 7/6, 8/6, 10/6, 11/6)
 
 pretendsToBeMetric <- function(x) {
   return(all(unique(x) %in% categories))
@@ -175,5 +175,19 @@ tripsNoOutliers <- tripsNoOutliers %>%
 # x 
 
 
-
+# names(dplyr::select(mergedData, tidyselect::contains('scaled'))) %in% names(dplyr::select(mergedDataImputeInterpolation, tidyselect::contains('scaled')))
+# 
+# c(unique(mergedDataImputeInterpolation$lessIll))[] %in% categories
+# class(c(unique(mergedDataImputeInterpolation$influenceHome))[10]) > class(1/3)
+# %in% categories
+# # numericData <- mergedData %>% 
+# #   select_if(!(is.numeric))
+# # 
+# # ncol(mergedData)
+# ncol(mergedDataImputeInterpolation)
+# ncol(mealsNoOutliers)
+# ncol(tripsNoOutliers)
+# ncol(numericData)
+# 
+# unique(mergedDataImputeInterpolation$lessIll) %in% categories
 

### 2020-02-25 ANALYSIS/Metric Regressions.R
from pull

@@ -9,9 +9,6 @@ library(modelr)
 library(texreg)
 
 
-
-#NOCHKEINEMODELLEMITOUTLIERN ERSTELLEN
-
 ##subsidy 
 #dataset: mergedData
 
@@ -19,58 +16,56 @@ mealsNo_sub.lm <- lm_robust(mealsNo ~ realSubsidy, data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub.lm) 
 
-
-
-# mealsNo_sub.lm <- coeftest(mealsNo_sub.lm, vcov. = vcovHC(mealsNo_sub.lm, type = 'HC1'))
-# summary(mealsNo_sub.lm)
+texreg(mealsNo_sub.lm)
 
 saveRDS(mealsNo_sub.lm,"./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+
 
 tripsNo_sub.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(tripsNo_sub.lm)
 
-# tripsNo_sub.lm <- coeftest(tripsNo_sub.lm, vcov. = vcovHC(tripsNo_sub.lm, type = 'HC1'))
-# summary(tripsNo_sub.lm)
+texreg(tripsNo_sub.lm)
 
 saveRDS(tripsNo_sub.lm,"./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
 
 
 #dataset with excluded outliers: mealsNo / tripsNo
 
-mealsNo_sub_ex.lm <- lm(mealsNo ~ realSubsidy, data = mealsNoEliminated)
+mealsNo_sub_ex.lm <- lm(mealsNo ~ realSubsidy, data = mealsNoOutliers)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub_ex.lm)
 
-mealsNo_sub_ex.lm <- coeftest(mealsNo_sub_ex.lm, vcov. = vcovHC(mealsNo_sub_ex.lm, type = 'HC1'))
-summary(mealsNo_sub_ex.lm)
+texreg(mealsNo_sub_ex.lm)
 
 saveRDS(mealsNo_sub_ex.lm,"./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")
 
-tripsNo_sub_ex.lm <- lm(tripsNo ~ realTripsSubsidy, data = tripsNoEliminated)
+
[…]

### 2020-02-25 ANALYSIS/Metric Regressions.R
hj

@@ -190,88 +190,136 @@ saveRDS(appreciateHealthy_DGE_IM_scaled.lm,"./ANALYSIS/Tables/appreciateHealthy_
 
 #lunch
 
-selfworth.lm <- lm(selfworth_weighted ~ realSubsidy, data = mergedData)
+selfworth.lm <- lm(selfworth_weighted ~ realSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(selfworth.lm)
+
+texreg(selfworth.lm)
 
 saveRDS(selfworth.lm,"./ANALYSIS/Tables/selfworth.lm.Rds")
 
-selfworth_scaled.lm <- lm(selfworth_scaled ~ realSubsidy, data = mergedData)
+selfworth_scaled.lm <- lm(selfworth_scaled ~ realSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(selfworth_scaled.lm) #standardized
+
+texreg(selfworth_scaled.lm)
 
 saveRDS(selfworth_scaled.lm,"./ANALYSIS/Tables/selfworth_scaled.Rds")
 
-dayToDaySkills.lm <- lm(dayToDaySkills_weighted ~ realSubsidy, data = mergedData)
+dayToDaySkills.lm <- lm(dayToDaySkills_weighted ~ realSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(dayToDaySkills.lm)
+
+texreg(dayToDaySkills.lm)
 
 saveRDS(dayToDaySkills.lm,"./ANALYSIS/Tables/dayToDaySkills.lm.Rds")
 
-dayToDaySkills_scaled.lm <- lm(dayToDaySkills_scaled ~ realSubsidy, data = mergedData)
+dayToDaySkills_scaled.lm <- lm(dayToDaySkills_scaled ~ realSubsidy, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
 summary(dayToDaySkills_scaled.lm) #standardized
+
+texreg(dayToDaySkills_scaled.lm)
 
 saveRDS(dayToDaySkills_scaled.lm,"./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds")
  
 #trips
[…]

### 2020-02-25 ANALYSIS/DATA/did_estimation.R
xxx

@@ -48,8 +48,8 @@ summary(lmdid_dayToDaySkills)
 # enthält und im Regressiontable somit ein Regressionskoeffizient von 0 ausgewiesen wird.
 # Lösung: Die Kontrollvariablen "dfcEF$subsidy" und "dfcEF$totalCost" werden durch 1000 geteilt. 
 
-# dfcEF$subsidy <- (dfcEF$subsidy/1000)
-# dfcEF$totalCost <- (dfcEF$totalCost/1000)
+#dfcEF$subsidy <- (dfcEF$subsidy/1000)
+#dfcEF$totalCost <- (dfcEF$totalCost/1000)
 
 lmdid_dayToDaySkills_controls <- lm(dfcEF$dayToDaySkills_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year
                                     + dfcEF$subsidy + dfcEF$totalCost)

### 2020-02-25 ANALYSIS/Metric Regressions.R
gh

@@ -32,7 +32,7 @@ saveRDS(tripsNo_sub.lm,"./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
 
 #dataset with excluded outliers: mealsNo / tripsNo
 
-mealsNo_sub_ex.lm <- lm(mealsNo ~ realSubsidy, data = mealsNoOutliers)%>%
+mealsNo_sub_ex.lm <- lm_robust(mealsNo ~ realSubsidy, data = mealsNoOutliers)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub_ex.lm)
 
@@ -41,7 +41,7 @@ texreg(mealsNo_sub_ex.lm)
 saveRDS(mealsNo_sub_ex.lm,"./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")
 
 
-tripsNo_sub_ex.lm <- lm(tripsNo ~ realTripsSubsidy, data = tripsNoOutliers)%>%
+tripsNo_sub_ex.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = tripsNoOutliers)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(tripsNo_sub_ex.lm)
 
@@ -53,7 +53,7 @@ saveRDS(tripsNo_sub_ex.lm,"./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds")
 
 #datset: mergedDataImputeInterpolation
 
-mealsNo_sub_IM.lm <- lm(mealsNo ~ realSubsidy, data = mergedDataImputeInterpolation)%>%
+mealsNo_sub_IM.lm <- lm_robust(mealsNo ~ realSubsidy, data = mergedDataImputeInterpolation)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(mealsNo_sub_IM.lm)
 
@@ -61,7 +61,7 @@ texreg(mealsNo_sub_IM.lm)
 
 saveRDS(mealsNo_sub_IM.lm,"./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")
 
-tripsNo_sub_IM.lm <- lm(tripsNo ~ realTripsSubsidy, data = mergedDataImputeInterpolation)%>%
+tripsNo_sub_IM.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = mergedDataImputeInterpolation)%>%
[…]

### 2020-02-25 paper.Rnw
complied with most formal requirements

--- 2020-02-25 paper.Rnw
@@
 
-\documentclass[12pt, a4paper]{article}
+\documentclass[12pt, a4paper, titlepage]{article}
 \usepackage{lscape}
@@
 \usepackage[onehalfspacing]{setspace}
-\usepackage[left = 72 pt, right = 72 pt]{geometry}
+\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+
+% 1.5 spacing in Word is about this in LaTeX
+% https://tex.stackexchange.com/questions/65849/confusion-onehalfspacing-vs-spacing-vs-word-vs-the-world
+
+\linespread{1.25}
 
@@
 
+% multiple authors
+% https://tex.stackexchange.com/questions/4805/whats-the-correct-use-of-author-when-multiple-authors
+
 \title{Effects of CHILDREN's programs}
-\author{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
+\author{
+Laura Huber\\
+\texttt{11111111}
+\and
+Laura Jepsen\\
+\texttt{11111111}
+\and
+Jonathan Kirschner\\
+\texttt{11724530}
+\and
+Rafael Schütz\\
+\texttt{11574909} 
+\and 
+Yannick Zurl\\
+\texttt{11111111}
+\and
+Studentisches Praxisprojekt zur Empirischen Wirtschaftsforschung PaRE3To\\
+\and
+Ludwig-Maximilians-Universität Munich
+}
+
+% Winter Term 2019/20\\
+
 \date{27th February 2020}
@@
 
-\begin{titlepage}
+% \begin{titlepage}
 \maketitle
-\end{titlepage}
+% \end{titlepage}
 
@@
 
-Examples\\
+\begin{abstract} 
+abstract on separate page
+100 - 150 words
+\end{abstract}
 
-Equation with\\
+\section{Formal requirements}
+all important information on title page, maybe use template\\
+always name sources of tables and graphs\\
+have to cite data sets\\
+
+\section{Examples}
+
+Equation with double index\\
 
@@
 
-Regression fit ouput with texreg
+Regression fit output with texreg\\
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
+# , message=FALSE, warning=FALSE
+# first, read in all Rds objects that you need
+# 
+mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+#  
+texreg(list(mealsNo_sub.lm, tripsNo_sub.lm))
+@
 
@@
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-#outlier meals
-#outlier trips 
-#impute meals
-#imputetrips
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
+lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds")#outlier trips 
+lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
+lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds")#imputetrips
 
-texreg(list(lm_ms, lm_ts), caption = "Grants Regressions", custom.model.names = c("Number of Meals", "Number of Trips"))
+texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
 @
+Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.
 
@@
 lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
+lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
+dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
+aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")
 
@@
 lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.Rds")
 
-stargazer(lm_dDGE, lm_aDGE, title = "Regression outcome: Health", align = TRUE)
+texreg(list(lm_lDGE, lm_dDGE, lm_aDGE, lDGE_i, dDGE_i, aDGE_i), caption = "Health Outcome Regressions", custom.model.names = c("LessIll", "DietaryKnowledge", "AppreciateHealthy","LessIll", "DietaryKnowledge", "AppreciateHealthy"))
 @
-<<Chance Equality Regressions, echo=FALSE, results='asis', message=FALSE>>=
+
+<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+ts =
+td =
 lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
 lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
+tss =
+tds =
 
-stargazer(lm_s, lm_d, lm_ss, lm_ds, title = "Regression outcome: Chance Equality", align = TRUE)
+texreg(list(), caption = "Equal Opportunities Regressions", custom.model.names = c())
 @

### 2020-02-25 paper.tex
complied with most formal requirements

@@
 
-\documentclass[12pt, a4paper]{article}\usepackage[]{graphicx}\usepackage[]{color}
+\documentclass[12pt, a4paper, titlepage]{article}\usepackage[]{graphicx}\usepackage[]{color}
 % maxwidth is the original width if it is less than linewidth
@@
 
-Regression fit ouput with texreg
+Regression fit output with texreg\\
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c }
+\hline
+ & Model 1 & Model 2 \\
+\hline
+(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
+                 & $(5192.86)$     & $(0.33)$     \\
+realSubsidy      & $2.61^{***}$    &              \\
+                 & $(0.57)$        &              \\
+realTripsSubsidy &                 & $0.00^{*}$   \\
+                 &                 & $(0.00)$     \\
+\hline
+R$^2$            & 0.43            & 0.05         \\
+Adj. R$^2$       & 0.43            & 0.04         \\
+Num. obs.        & 329             & 322          \\
+RMSE             & 39992.79        & 2.96         \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\caption{Statistical models}
+\label{table:coefficients}
+\end{center}
+\end{table}
 
@@
 
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
 \section{Summary Statistics}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 18:51:50 2020
+% Tue Feb 25 23:58:46 2020
 \begin{table}[ht]
@@
 \begin{center}
-\begin{tabular}{l c c }
+\begin{tabular}{l c c c c c c }
 \hline
- & Number of Meals & Number of Trips \\
+ & MealsNo & Trips No & Meals No & Trips No & Meals No & Trips No \\
 \hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     \\
-realSubsidy      & $2.61^{***}$    &              \\
-                 & $(0.57)$        &              \\
-realTripsSubsidy &                 & $0.00^{*}$   \\
-                 &                 & $(0.00)$     \\
+(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{***}$ & $3.70^{***}$ & $-12250.60^{***}$ & $3.62^{***}$ \\
+                 & $(5192.86)$     & $(0.33)$     & $(2919.15)$       & $(0.25)$     & $(2500.33)$       & $(0.25)$     \\
+realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$      &              & $2.72^{***}$      &              \\
+                 & $(0.57)$        &              & $(0.17)$          &              & $(0.14)$          &              \\
+realTripsSubsidy &                 & $0.00^{*}$   &                   & $0.00^{***}$ &                   & $0.00^{***}$ \\
+                 &                 & $(0.00)$     &                   & $(0.00)$     &                   & $(0.00)$     \\
 \hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
+R$^2$            & 0.43            & 0.05         & 0.43              & 0.05         & 0.45              & 0.05         \\
+Adj. R$^2$       & 0.43            & 0.04         & 0.43              & 0.04         & 0.45              & 0.05         \\
+Num. obs.        & 329             & 322          & 329               & 322          & 440               & 334          \\
+RMSE             & 39992.79        & 2.96         & 39992.79          & 2.96         & 39601.41          & 2.93         \\
 \hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \end{table}
+
+Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.
 
@@
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 18:51:55
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Regression outcome: Health} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-3} 
-\\[-1.8ex] & \multicolumn{2}{c}{ } \\ 
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)}\\ 
-\hline \\[-1.8ex] 
- DGECriteriaNoScaled & 0.112^{*} & 0.266^{***} \\ 
-  & (0.063) & (0.065) \\ 
-  & & \\ 
- Constant & 0.015 & -0.026 \\ 
-  & (0.067) & (0.070) \\ 
-  & & \\ 
-\hline \\[-1.8ex] 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): cannot open compressed file './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds', probable reason 'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): cannot open the connection}}\end{kframe}
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c c c }
 \hline
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
+ & LessIll & DietaryKnowledge & AppreciateHealthy & LessIll & DietaryKnowledge & AppreciateHealthy \\
+\hline
+(Intercept)         & $0.02$       & $0.02$   & $-0.03$      & $0.09$       & $0.02$     & $0.02$       \\
+                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
+                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
+Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
+Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
+RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
+\caption{Health Outcome Regressions}
+\label{table:coefficients}
+\end{center}
 \end{table}
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 18:51:55
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Regression outcome: Chance Equality} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
- & \multicolumn{4}{c}{\textit{Dependent variable:}} \\ 
-\cline{2-5} 
-\\[-1.8ex] & \multicolumn{4}{c}{ } \\ 
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-\hline \\[-1.8ex] 
- realSubsidy & 0.003^{***} & 0.003^{***} & 0.00000 & 0.00001^{***} \\ 
-  & (0.001) & (0.001) & (0.00000) & (0.00000) \\ 
-  & & & & \\ 
- Constant & -13.419^{**} & -13.481^{**} & -0.056 & -0.158^{***} \\ 
-  & (5.715) & (5.727) & (0.063) & (0.060) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{table}
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in l[[i]]: subscript out of bounds}}\end{kframe}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Di, Feb 25, 2020 - 18:51:55
+% Date and time: Tue, Feb 25, 2020 - 11:58:54 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\section{Conclusion}
+
+\printbibliography
+
 \section{Appendix}
 
-A1\\ 
-Cumulative Odds Regression 
+\subsection{A1: Cumulative Odds Regression}
+
 Outliers?
 
-A2\\
-Partition
+\subsection{A2: Partition}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 18:51:55 2020
+% Tue Feb 25 23:58:54 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
 
-\printbibliography
+\{Ehrenwörtliche Erklärung aller Teilnehmer}
+
 \end{document}

### 2020-02-25 ANALYSIS/Metric Regressions.R

@@ -82,7 +82,7 @@ summary(lessIll_DGE.lm)
 
 saveRDS(lessIll_DGE.lm,"./ANALYSIS/Tables/lessIll_DGE.lm.Rds")
 
-lessIll_DGE_scaled.lm <- lm(lessIll_scaled ~ DGECriteriaNoScaled, data = mergedData)%>%
+lessIll_DGE_scaled.lm <- lm(lessIll_scaled ~ DGECriteriaNoScaled, data = mergedData) %>%
   extract.lm_robust(include.ci = FALSE)
 summary(lessIll_DGE_scaled.lm) #standardized
 

### 2020-02-25 paper.Rnw

@@
 lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
-ts =
-td =
+ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
 lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
 lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
-tss =
-tds =
+tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.lm.Rds")
+tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
 
-texreg(list(), caption = "Equal Opportunities Regressions", custom.model.names = c())
+texreg(list(lm_s, lm_d, ts, td, lm_ss, lm_ds, tss, tds), caption = "Equal Opportunities Regressions", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
+@
+
+<<ChanceEqualityRegressionsImpute, echo=FALSE, results='asis', message=FALSE>>=
+
+sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.Rds") #standardized
+dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") #standardized 
+tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
+tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
+
+texreg(list(sI, dI, tsI, tdI, ssI, dsI, tssI, tdsI), caption = "Equal Opportunities Regressions, imputed data", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
 @

### 2020-02-25 paper.Rnw

@@
 
+\begin{equation}
+\label{Meals Grants Regression Model}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
 <<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
+Where: 
+y: Health outcomes: lessIll, dietaryKnowledge,  appreciateHealthy
+x: DGECriteria Number
+
 <<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
+Where: 
+y: Equal Opportunity proxies: selfworth, dayToDaySkills
+x: Real Lunch grant, real Trips grant
 <<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=

### 2020-02-25 paper.Rnw
dfghj

--- 2020-02-25 paper.Rnw
@@
 
+\begin{equation}
+\label{Equation 1}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+In this section we use a standard OLS equation, as described in equation 1.
+Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables.
+We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data.
+(DESCRIBE METHODS EXACT)
+
+\\Number of Meals and Number of Trips
+
+As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries.
+In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset.
+TableX shows the regression results.
+
 <<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 @
-Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.
+The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
+(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
+
+In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.
 
@@
 \end{figure}
+
+In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.
 

### 2020-02-25 paper.tex
dfghj

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 23:58:46 2020
+% Wed Feb 26 00:35:31 2020
 \begin{table}[ht]
@@
 
+\begin{equation}
+\label{Equation 1}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+In this section we use a standard OLS equation, as described in equation 1.
+Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables.
+We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data.
+(DESCRIBE METHODS EXACT)
+
+\\Number of Meals and Number of Trips
+
+As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries.
+In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset.
+TableX shows the regression results.
+
 \begin{table}
@@
 \hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{***}$ & $3.70^{***}$ & $-12250.60^{***}$ & $3.62^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     & $(2919.15)$       & $(0.25)$     & $(2500.33)$       & $(0.25)$     \\
+(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{*}$ & $3.70^{***}$ & $-12250.60^{**}$ & $3.62^{***}$ \\
+                 & $(5192.86)$     & $(0.33)$     & $(5192.86)$     & $(0.33)$     & $(4524.09)$      & $(0.33)$     \\
 realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$    &              & $2.72^{***}$     &              \\
-                 & $(0.57)$        &              & $(0.17)$          &              & $(0.14)$          &              \\
-realTripsSubsidy &                 & $0.00^{*}$   &                   & $0.00^{***}$ &                   & $0.00^{***}$ \\
+                 & $(0.57)$        &              & $(0.57)$        &              & $(0.51)$         &              \\
+realTripsSubsidy &                 & $0.00^{*}$   &                 & $0.00^{*}$   &                  & $0.00^{*}$   \\
                  &                 & $(0.00)$     &                 & $(0.00)$     &                  & $(0.00)$     \\
@@
 
-Table 3: The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed.
+The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
+(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
+
+In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.
 
@@
 
+In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.
+
 \begin{kframe}
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): cannot open compressed file './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds', probable reason 'No such file or directory'}}
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): cannot open the connection}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
 \begin{table}
@@
 DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
-                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
+                    & $(0.08)$     & $(0.06)$ & $(0.07)$     & $(0.07)$     & $(0.05)$   & $(0.06)$     \\
 \hline
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in l[[i]]: subscript out of bounds}}\end{kframe}
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworthTrips\_scaled.lm.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'tss' nicht gefunden}}\end{kframe}
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworth\_IM\_scaled.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'ssI' nicht gefunden}}\end{kframe}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Tue, Feb 25, 2020 - 11:58:54 PM
+% Date and time: Mi, Feb 26, 2020 - 00:35:36
 % Requires LaTeX packages: dcolumn rotating 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Tue Feb 25 23:58:54 2020
+% Wed Feb 26 00:35:36 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
 

### 2020-02-25 ANALYSIS/Propodds Regressions.R

@@ -58,17 +58,17 @@ saveRDS(DGE_lessIll_IM.cumulative.parallel,"./ANALYSIS/Tables/DGE_lessIll_IM.cum
 DGE_lessIll_IM.vglm.cumulative.notParallel = vglm(lessIll_ordered ~  DGECriteriaNo, data = mergedDataImputeInterpolation, family = cumulative(parallel = FALSE))
 summary(DGE_lessIll_IM.vglm.cumulative.notParallel)
 
-saveRDS(,"./ANALYSIS/Tables/.Rds")
+saveRDS(DGE_lessIll_IM.vglm.cumulative.notParallel,"./ANALYSIS/Tables/DGE_lessIll_IM.vglm.cumulative.notParallel.Rds")
 
 DGE_dietaryKnowledge_IM.cumulative.parallel = vglm(dietaryKnowledge_ordered ~ DGECriteriaNo, data = mergedDataImputeInterpolation, family = cumulative(parallel = TRUE))
 summary(DGE_dietaryKnowledge_IM.cumulative.parallel)
 
-saveRDS(,"./ANALYSIS/Tables/.Rds")
+saveRDS(DGE_dietaryKnowledge_IM.cumulative.parallel,"./ANALYSIS/Tables/DGE_dietaryKnowledge_IM.cumulative.parallel.Rds")
 
 DGE_appreciateHealthy_IM.cumulative.parallel = vglm(appreciateHealthy_ordered ~ DGECriteriaNo, data = mergedDataImputeInterpolation, family = cumulative(parallel = TRUE))
 summary(DGE_appreciateHealthy_IM.cumulative.parallel)
 
-saveRDS(,"./ANALYSIS/Tables/.Rds")
+saveRDS(DGE_appreciateHealthy_IM.cumulative.parallel,"./ANALYSIS/Tables/DGE_appreciateHealthy_IM.cumulative.parallel.Rds")
 
 
 
@@ -87,7 +87,7 @@ saveRDS(,"./ANALYSIS/Tables/.Rds")
 Expand_LessIll.cumulative.parallel = vglm(lessIll_ordered ~ DGECriteriaNo + regionalProducts_ordered + yearsSupportSince + realSubsidy + state, data = mergedData, family = cumulative(parallel = TRUE))
 summary(Expand_LessIll.cumulative.parallel)
 
-saveRDS(,"./ANALYSIS/Tables/.Rds")
[…]

### 2020-02-26 paper.Rnw
hh

@@
 Laura Jepsen\\
-\texttt{11111111}
+\texttt{11567799}
 \and
@@
 
+\section{Data}
+
 \section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
@@
 \section{Summary Statistics}
+\subsection{Fundamental Dynamics}
 
@@
 
+\subsection{Trend of grants}
+
 \begin{figure}
@@
 
+\subsection{Heatlh relevant variables over time}
+
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Equality of opportunities releveant variables over time}
 
@@
 
+\subsection{Empirical Approach}
+
 \begin{equation}
@@
 
-\\Number of Meals and Number of Trips
+\subsection{Variables of interest: Number of trips and number of meals}
 
@@
 (DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
+
+\subsection{Variables of interest: Health variables}
 
@@
 
+\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
+
 <<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
-tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.lm.Rds")
+tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")
 tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
@@
 tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
-ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.Rds") #standardized
+ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
 dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") #standardized 
@@
 
-#read in data from vglm models
+lessIllOdds <- readRDS("./ANALYSIS/Tables/lessIllProp.Rds")
 
+stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", align = TRUE)
+
+@
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+dietaryOdds <- readRDS("./ANALYSIS/Tables/DietaryProp.Rds")
+
+stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Dietary Knowledge", align = TRUE)
+@
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+appreciateOdds <- readRDS("./ANALYSIS/Tables/AppreciateProp.Rds")
+
+stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Appreciate Healthy", align = TRUE)
+@
+
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+selfworthOdds <- readRDS("./ANALYSIS/Tables/selfworthProp.Rds")
+
+stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Equality of opportunities, selfworth", align = TRUE)
+@
+
+<<echo=FALSE, results='asis', message=FALSE>>=
+
+dayToDayOdds <- readRDS("./ANALYSIS/Tables/dayToDayProb.Rds")
+
+stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Equality of opportunities, everyday expertise", align = TRUE)
 @

### 2020-02-26 paper.tex
hh

@@
 \section{Summary Statistics}
+\subsection{Fundamental Dynamics}
 
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 00:35:31 2020
+% Wed Feb 26 09:24:41 2020
 \begin{table}[ht]
@@
 
-\begin{kframe}
+\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworthTrips\_scaled.lm.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c c c c c }
+\hline
+ & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
+\hline
+(Intercept)      & $-13.42^{*}$ & $-13.48^{*}$ & $9.20^{***}$ & $8.25^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.10$   & $0.12$   \\
+                 & $(5.88)$     & $(5.89)$     & $(1.84)$     & $(1.78)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
+realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
+                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
+realTripsSubsidy &              &              & $0.00^{***}$ & $0.01^{***}$ &          &              & $-0.00$  & $-0.00$  \\
+                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
+\hline
+R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
+Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.00     & 0.01     \\
+Num. obs.        & 428          & 426          & 184          & 177          & 430      & 428          & 186      & 178      \\
+RMSE             & 41.50        & 41.59        & 21.93        & 21.36        & 1.00     & 0.98         & 1.00     & 0.98     \\
+\hline
+\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\caption{Equal Opportunities Regressions}
+\label{table:coefficients}
+\end{center}
+\end{table}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'tss' nicht gefunden}}\end{kframe}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworth\_IM\_scaled.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'ssI' nicht gefunden}}\end{kframe}
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c c c c c }
+\hline
+ & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
+\hline
+(Intercept)      & $-13.42^{*}$ & $-13.47^{*}$ & $9.25^{***}$ & $8.33^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.11$   & $0.13$   \\
+                 & $(5.88)$     & $(5.89)$     & $(1.82)$     & $(1.74)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
+realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
+                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
+realTripsSubsidy &              &              & $0.00^{***}$ & $0.00^{***}$ &          &              & $-0.00$  & $-0.00$  \\
+                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
+\hline
+R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.02     \\
+Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
+Num. obs.        & 428          & 427          & 186          & 180          & 430      & 429          & 189      & 182      \\
+RMSE             & 41.50        & 41.54        & 21.83        & 21.21        & 1.00     & 0.98         & 1.00     & 0.99     \\
+\hline
+\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+\caption{Equal Opportunities Regressions, imputed data}
+\label{table:coefficients}
+\end{center}
+\end{table}
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 00:35:36
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Less Ill} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
+\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
+\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
+\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Dietary Knowledge} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
+\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
+\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
+\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Appreciate Healthy} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
+\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
+\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
+\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
+\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
+\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
+\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Requires LaTeX packages: dcolumn 
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
+  \label{} 
+\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
+\hline \\[-1.8ex] 
+\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
+\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
+\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
+\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
 \subsection{A2: Partition}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 00:35:36 2020
+% Wed Feb 26 09:24:46 2020
 \begin{table}[ht]

### 2020-02-26 ANALYSIS/Propodds Regressions.R

@@ -18,9 +18,9 @@ library(texreg)
 #summary(DGE_lessIll.vglm.propOdds)
 
 DGE_lessIll.cumulative.parallel = vglm(lessIll_ordered ~  DGECriteriaNo, data = mergedData, family = cumulative(parallel = TRUE))
-summary(DGE_lessIll.cumulative.parallel)
+LessIllProp <- summaryvglm(DGE_lessIll.cumulative.parallel)
 
-saveRDS(DGE_lessIll.cumulative.parallel,"./ANALYSIS/Tables/DGE_lessIll.cumulative.parallel.Rds")
+saveRDS(LessIllProp,"./ANALYSIS/Tables/LessIllProp.Rds")
 # 
 
 #DGE_lessIll.vglm.cumulative.notParallel = vglm(lessIllOrdinal ~  DGECriteriaNo, data = mergedData, family = cumulative(parallel = FALSE))
@@ -30,9 +30,9 @@ saveRDS(DGE_lessIll.cumulative.parallel,"./ANALYSIS/Tables/DGE_lessIll.cumulativ
 #summary(DGE_dietaryKnowledge.vglm)
 
 DGE_dietaryKnowledge.cumulative.parallel = vglm(dietaryKnowledge_ordered ~ DGECriteriaNo, data = mergedData, family = cumulative(parallel = TRUE))
-summary(DGE_dietaryKnowledge.cumulative.parallel)
+DietaryProp <- summary(DGE_dietaryKnowledge.cumulative.parallel)
 
-saveRDS(DGE_dietaryKnowledge.cumulative.parallel,"./ANALYSIS/Tables/DGE_dietaryKnowledge.cumulative.parallel.Rds")
+saveRDS(DietaryProp,"./ANALYSIS/Tables/DietaryProp.Rds")
 
 #DGE_seasonalFoodstuff.vglm = vglm(seasonalFoodstuffOrdinal ~ DGECriteriaNo, data = mergedData, family = propodds)
 #summary(DGE_seasonalFoodstuff.vglm)
@@ -41,9 +41,9 @@ saveRDS(DGE_dietaryKnowledge.cumulative.parallel,"./ANALYSIS/Tables/DGE_dietaryK
 #summary(DGE_organicFoodstuff.vglm)
 
 DGE_appreciateHealthy.cumulative.parallel = vglm(appreciateHealthy_ordered ~ DGECriteriaNo, data = mergedData, family = cumulative(parallel = TRUE))
[…]

### 2020-02-26 paper.Rnw
clarification of which models we want

--- 2020-02-25 paper.Rnw
@@
 effect of\\
-- healthy meals (DGE criterion) on healthy characteristics\\
+- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
 - real meals subsidy on number of meals\\
 - real trips subsidy on number of trips\\
-- real meals subsidy on self-worth and day-to-day skills\\
-- real trips subsidy on self-worth and day-to-day skills\\
+- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
+- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
 
@@
 
-\begin{equation}
-\label{Meals Grants Regression Model}
-  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
-\end{equation}
-
 <<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-Where: 
-y: Health outcomes: lessIll, dietaryKnowledge,  appreciateHealthy
-x: DGECriteria Number
-
 <<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-Where: 
-y: Equal Opportunity proxies: selfworth, dayToDaySkills
-x: Real Lunch grant, real Trips grant
 <<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-\{Ehrenwörtliche Erklärung aller Teilnehmer}
+\section{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-02-26 paper.tex
xxx

@@
 \begin{center}
-\begin{tabular}{l c c }
+\begin{tabular}{l c c}
 \hline
@@
 \hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
+R$^2$            & $0.43$          & $0.05$       \\
+Adj. R$^2$       & $0.43$          & $0.04$       \\
+Num. obs.        & $329$           & $322$        \\
+RMSE             & $39992.79$      & $2.96$       \\
 \hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 09:24:41 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 12:46:00 2020
 \begin{table}[ht]
@@
 \begin{center}
-\begin{tabular}{l c c c c c c }
+\begin{tabular}{l c c c c c c}
 \hline
@@
 \hline
-R$^2$            & 0.43            & 0.05         & 0.43            & 0.05         & 0.45             & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         & 0.43            & 0.04         & 0.45             & 0.05         \\
-Num. obs.        & 329             & 322          & 329             & 322          & 440              & 334          \\
-RMSE             & 39992.79        & 2.96         & 39992.79        & 2.96         & 39601.41         & 2.93         \\
+R$^2$            & $0.43$          & $0.05$       & $0.43$          & $0.05$       & $0.45$           & $0.05$       \\
+Adj. R$^2$       & $0.43$          & $0.04$       & $0.43$          & $0.04$       & $0.45$           & $0.05$       \\
+Num. obs.        & $329$           & $322$        & $329$           & $322$        & $440$            & $334$        \\
+RMSE             & $39992.79$      & $2.96$       & $39992.79$      & $2.96$       & $39601.41$       & $2.93$       \\
 \hline
-\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
-Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
-Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
-RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
+R$^2$               & $0.12$       & $0.01$   & $0.06$       & $0.07$       & $0.02$     & $0.06$       \\
+Adj. R$^2$          & $0.11$       & $0.01$   & $0.06$       & $0.07$       & $0.01$     & $0.06$       \\
+Num. obs.           & $121$        & $214$    & $213$        & $177$        & $275$      & $274$        \\
+RMSE                & $0.91$       & $0.98$   & $1.02$       & $0.94$       & $0.96$     & $1.01$       \\
 \hline
-\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \begin{center}
-\begin{tabular}{l c c c c c c c c }
+\begin{tabular}{l c c c c c c c c}
 \hline
@@
 \hline
-R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
-Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.00     & 0.01     \\
-Num. obs.        & 428          & 426          & 184          & 177          & 430      & 428          & 186      & 178      \\
-RMSE             & 41.50        & 41.59        & 21.93        & 21.36        & 1.00     & 0.98         & 1.00     & 0.98     \\
+R$^2$            & $0.46$       & $0.46$       & $0.32$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.01$   \\
+Adj. R$^2$       & $0.45$       & $0.45$       & $0.31$       & $0.34$       & $0.00$   & $0.03$       & $0.00$   & $0.01$   \\
+Num. obs.        & $428$        & $426$        & $184$        & $177$        & $430$    & $428$        & $186$    & $178$    \\
+RMSE             & $41.50$      & $41.59$      & $21.93$      & $21.36$      & $1.00$   & $0.98$       & $1.00$   & $0.98$   \\
 \hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.02     \\
-Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
-Num. obs.        & 428          & 427          & 186          & 180          & 430      & 429          & 189      & 182      \\
-RMSE             & 41.50        & 41.54        & 21.83        & 21.21        & 1.00     & 0.98         & 1.00     & 0.99     \\
+R$^2$            & $0.46$       & $0.46$       & $0.32$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.02$   \\
+Adj. R$^2$       & $0.45$       & $0.45$       & $0.31$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.01$   \\
+Num. obs.        & $428$        & $427$        & $186$        & $180$        & $430$    & $429$        & $189$    & $182$    \\
+RMSE             & $41.50$      & $41.54$      & $21.83$      & $21.21$      & $1.00$   & $0.98$       & $1.00$   & $0.99$   \\
 \hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 
+\begin{table}
+\begin{center}
+\begin{tabular}{l c}
+\hline
+ & Selfworth \\
+\hline
+(Intercept)             & $-1.13^{***}$ \\
+                        & $(0.32)$      \\
+dfcEF2$treatEF          & $-0.47$       \\
+                        & $(0.31)$      \\
+\hline
+Num. obs.               & $430$         \\
+R$^2$ (full model)      & $0.47$        \\
+R$^2$ (proj model)      & $0.47$        \\
+Adj. R$^2$ (full model) & $0.36$        \\
+Adj. R$^2$ (proj model) & $0.36$        \\
+\hline
+\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+\end{tabular}
+\caption{linear regression}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
 Ende??
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Date and time: Mi., Feb 26, 2020 - 12:46:08
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Date and time: Mi., Feb 26, 2020 - 12:46:08
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 09:24:46 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 12:46:08 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 09:24:46 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 12:46:08 2020
 \begin{table}[ht]

### 2020-02-26 ANALYSIS/DATA/did_estimation.R

@@ -380,9 +380,9 @@ summary(lmdid3_selfworth)
 
 class(dfcEF2$year)
 
-install.packages("lfe")
-install.packages("Matrix")
-install.packages("texreg")
+#install.packages("lfe")
+#install.packages("Matrix")
+#install.packages("texreg")
 library(lfe)
 library(Matrix)
 library(texreg)
@@ -398,7 +398,7 @@ RpValue1 = coef(summary(lmdid3_test, robust = TRUE))[, "Pr(>|t|)"]
 x <- list('x' = 'treatEF')
 
 custom.name <- c('Intercept', 'Treat EF')
-screenreg(lmdid3_test, override.se = list(RSE1), override.pvalues = list(RpValue1),
+texreg(lmdid3_test, override.se = list(RSE1), override.pvalues = list(RpValue1),
           caption = "linear regression",
           custom.model.names = "Selfworth",
           omit.coef = 'id|year')

### 2020-02-26 paper.Rnw
xxx
ghj

@@
 have to cite data sets\\
+latin number pages\\
 
@@
 
-<<GrantsRegressions, echo=FALSE, results='asis', message=FALSE>>=
+<<GrantsRegressions Lunch, echo=FALSE, results='asis', message=FALSE>>=
 
 lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
+lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
+
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+@
+
+<<GrantsRegressions Trips, echo=FALSE, results='asis', message=FALSE>>=
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
-lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds")#outlier trips 
-lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
-lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds")#imputetrips
+lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
+lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips
 
-texreg(list(lm_ms, lm_ts, lm_ms_o, lm_ts_o, lm_ms_i, lm_ts_i), caption = "Grants Regressions", custom.model.names = c("MealsNo", "Trips No", "Meals No", "Trips No", "Meals No", "Trips No"))
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+
 @
-The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
-(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
-
 \subsection{Variables of interest: Health variables}
@@
 
-<<HealthRegressions, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions_LessIll, echo=FALSE, results='asis', message=FALSE>>=
 
-#scaled regressions
+lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
+#extraweighted
+lDGEw = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled_weighted.lm.Rds")
+#standardized
+lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
+#extraweighted
+lDGE_iw = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled_weighted.lm.Rds")
 
-lm_lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
-lm_dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
-lm_aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
-lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
+@
+
+<<HealthRegressions_DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
+dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
+dDGEw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled_weighted.Rds")
 dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
+dDGE_iw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled_weighted.lm.Rds")
+
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
+@
+
+<<HealthRegressions_AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
+aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
+aDGEw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled_weighted.Rds")
 aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")
+aDGE_iw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled_weighted.lm.Rds")
 
-#expanded model less ill
-
-lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
-elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.Rds")
-
-texreg(list(lm_lDGE, lm_dDGE, lm_aDGE, lDGE_i, dDGE_i, aDGE_i), caption = "Health Outcome Regressions", custom.model.names = c("LessIll", "DietaryKnowledge", "AppreciateHealthy","LessIll", "DietaryKnowledge", "AppreciateHealthy"))
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
 @
@@
 
-<<ChanceEqualityRegressions, echo=FALSE, results='asis', message=FALSE>>=
+<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=
 
-lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
-lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
-ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
-td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
-lm_ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardized
-lm_ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardized 
-tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")
-tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
+ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardizedweighted
+tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
+ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
+tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
 
-texreg(list(lm_s, lm_d, ts, td, lm_ss, lm_ds, tss, tds), caption = "Equal Opportunities Regressions", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
+texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
 @
 
-<<ChanceEqualityRegressionsImpute, echo=FALSE, results='asis', message=FALSE>>=
-
-sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
-dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
-tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
-tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
-ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
-dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") #standardized 
-tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
+<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
+ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
+tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
+dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
 tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
 
-texreg(list(sI, dI, tsI, tdI, ssI, dsI, tssI, tdsI), caption = "Equal Opportunities Regressions, imputed data", custom.model.names = c("selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills", "selfworth", "dayToDaySkills" ))
+texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
 @
@@
 @
+\subsection{A3: OLS Regressions}
+
+#normal weights selfworth& subsidiy
+<<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+@
+
+<<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+#expanded model less ill
+
+lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
+elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
+@
 

### 2020-02-26 paper.tex
ghj

--- 2020-02-26 paper.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 09:24:41 2020
+% Wed Feb 26 12:29:41 2020
 \begin{table}[ht]
@@
 \begin{center}
-\begin{tabular}{l c c c c c c }
+\scalebox{0.8}{
+\begin{tabular}{l c c c }
 \hline
- & MealsNo & Trips No & Meals No & Trips No & Meals No & Trips No \\
+ & OLS & OLS without Outliers & OLS Impute \\
 \hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ & $-12089.14^{*}$ & $3.70^{***}$ & $-12250.60^{**}$ & $3.62^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     & $(5192.86)$     & $(0.33)$     & $(4524.09)$      & $(0.33)$     \\
-realSubsidy      & $2.61^{***}$    &              & $2.61^{***}$    &              & $2.72^{***}$     &              \\
-                 & $(0.57)$        &              & $(0.57)$        &              & $(0.51)$         &              \\
-realTripsSubsidy &                 & $0.00^{*}$   &                 & $0.00^{*}$   &                  & $0.00^{*}$   \\
-                 &                 & $(0.00)$     &                 & $(0.00)$     &                  & $(0.00)$     \\
+(Intercept) & $-12089.14^{*}$ & $-12089.14^{*}$ & $-12250.60^{**}$ \\
+            & $(5192.86)$     & $(5192.86)$     & $(4524.09)$      \\
+realSubsidy & $2.61^{***}$    & $2.61^{***}$    & $2.72^{***}$     \\
+            & $(0.57)$        & $(0.57)$        & $(0.51)$         \\
 \hline
-R$^2$            & 0.43            & 0.05         & 0.43            & 0.05         & 0.45             & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         & 0.43            & 0.04         & 0.45             & 0.05         \\
-Num. obs.        & 329             & 322          & 329             & 322          & 440              & 334          \\
-RMSE             & 39992.79        & 2.96         & 39992.79        & 2.96         & 39601.41         & 2.93         \\
+R$^2$       & 0.43            & 0.43            & 0.45             \\
+Adj. R$^2$  & 0.43            & 0.43            & 0.45             \\
+Num. obs.   & 329             & 329             & 440              \\
+RMSE        & 39992.79        & 39992.79        & 39601.41         \\
 \hline
-\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
-\caption{Grants Regressions}
+}
+\caption{Regression Results: Number of meals}
 \label{table:coefficients}
@@
 
-The first two columns are simple OLS models, in column 3 and 4 outliers are excluded and in column 5 and 6 data is imputed. 
-(DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c }
+\hline
+ & OLS & OLS without Outliers & OLS Impute \\
+\hline
+(Intercept)      & $3.70^{***}$ & $3.70^{***}$ & $3.62^{***}$ \\
+                 & $(0.33)$     & $(0.33)$     & $(0.33)$     \\
+realTripsSubsidy & $0.00^{*}$   & $0.00^{*}$   & $0.00^{*}$   \\
+                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
+\hline
+R$^2$            & 0.05         & 0.05         & 0.05         \\
+Adj. R$^2$       & 0.04         & 0.04         & 0.05         \\
+Num. obs.        & 322          & 322          & 334          \\
+RMSE             & 2.96         & 2.96         & 2.93         \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Number of trips}
+\label{table:coefficients}
+\end{center}
+\end{table}
 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/Expand\_LessIll\_IM\_scaled.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
 \begin{table}
 \begin{center}
-\begin{tabular}{l c c c c c c }
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
 \hline
- & LessIll & DietaryKnowledge & AppreciateHealthy & LessIll & DietaryKnowledge & AppreciateHealthy \\
+ & OLS & WLS & OLS Impute & WLS Impute \\
 \hline
-(Intercept)         & $0.02$       & $0.02$   & $-0.03$      & $0.09$       & $0.02$     & $0.02$       \\
-                    & $(0.08)$     & $(0.07)$ & $(0.07)$     & $(0.07)$     & $(0.06)$   & $(0.06)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.11$   & $0.27^{***}$ & $0.25^{***}$ & $0.12^{*}$ & $0.25^{***}$ \\
-                    & $(0.08)$     & $(0.06)$ & $(0.07)$     & $(0.07)$     & $(0.05)$   & $(0.06)$     \\
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
 \hline
-R$^2$               & 0.12         & 0.01     & 0.06         & 0.07         & 0.02       & 0.06         \\
-Adj. R$^2$          & 0.11         & 0.01     & 0.06         & 0.07         & 0.01       & 0.06         \\
-Num. obs.           & 121          & 214      & 213          & 177          & 275        & 274          \\
-RMSE                & 0.91         & 0.98     & 1.02         & 0.94         & 0.96       & 1.01         \\
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
+Num. obs.           & 121          & 120         & 177          & 177          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
 \hline
-\multicolumn{7}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
-\caption{Health Outcome Regressions}
+}
+\caption{Regression Results: Less Ill}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
+Num. obs.           & 214      & 212      & 275        & 275      \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Dietary Knowledge}
+\label{table:coefficients}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
+Num. obs.           & 213          & 211      & 274          & 274        \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Appreciate Healthy}
 \label{table:coefficients}
@@
 \begin{center}
-\begin{tabular}{l c c c c c c c c }
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
 \hline
- & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
+ & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
 \hline
-(Intercept)      & $-13.42^{*}$ & $-13.48^{*}$ & $9.20^{***}$ & $8.25^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.10$   & $0.12$   \\
-                 & $(5.88)$     & $(5.89)$     & $(1.84)$     & $(1.78)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
-realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
-                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
-realTripsSubsidy &              &              & $0.00^{***}$ & $0.01^{***}$ &          &              & $-0.00$  & $-0.00$  \\
-                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
+                               & $(0.00)$ &          & $(0.00)$ &          \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
+                               &          & $(0.00)$ &          & $(0.00)$ \\
 \hline
-R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
-Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.00     & 0.01     \\
-Num. obs.        & 428          & 426          & 184          & 177          & 430      & 428          & 186      & 178      \\
-RMSE             & 41.50        & 41.59        & 21.93        & 21.36        & 1.00     & 0.98         & 1.00     & 0.98     \\
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
+Num. obs.                      & 428      & 184      & 430      & 187      \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
 \hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
-\caption{Equal Opportunities Regressions}
+}
+\caption{Regression Results: Selfworth}
 \label{table:coefficients}
@@
 \begin{center}
-\begin{tabular}{l c c c c c c c c }
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
 \hline
- & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
+ & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
 \hline
-(Intercept)      & $-13.42^{*}$ & $-13.47^{*}$ & $9.25^{***}$ & $8.33^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.11$   & $0.13$   \\
-                 & $(5.88)$     & $(5.89)$     & $(1.82)$     & $(1.74)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
-realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
-                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
-realTripsSubsidy &              &              & $0.00^{***}$ & $0.00^{***}$ &          &              & $-0.00$  & $-0.00$  \\
-                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
+                               & $(0.00)$ &          & $(0.00)$ &          \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
+                               &          & $(0.00)$ &          & $(0.00)$ \\
 \hline
-R$^2$            & 0.46         & 0.46         & 0.32         & 0.34         & 0.00     & 0.03         & 0.01     & 0.02     \\
-Adj. R$^2$       & 0.45         & 0.45         & 0.31         & 0.34         & 0.00     & 0.03         & 0.01     & 0.01     \\
-Num. obs.        & 428          & 427          & 186          & 180          & 430      & 429          & 189      & 182      \\
-RMSE             & 41.50        & 41.54        & 21.83        & 21.21        & 1.00     & 0.98         & 1.00     & 0.99     \\
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
+Num. obs.                      & 426      & 177      & 429      & 181      \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
 \hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
-\caption{Equal Opportunities Regressions, imputed data}
+}
+\caption{Regression Results: dayToDaySkills}
 \label{table:coefficients}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Date and time: Mi, Feb 26, 2020 - 12:29:46
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 09:24:46
+% Date and time: Mi, Feb 26, 2020 - 12:29:47
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 09:24:46 2020
+% Wed Feb 26 12:29:47 2020
 \begin{table}[ht]
@@
 {\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+\subsection{A3: OLS Regressions}
 
-\{Ehrenwörtliche Erklärung aller Teilnehmer}
+#normal weights selfworth& subsidiy
+
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
+
+\section{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-02-26 ANALYSIS/Health Regressions.R

@@ -1,0 +1,186 @@
+#health regressions
+library(estimatr)
+library(texreg)
+
+##healthinfluence 
+
+#dataset: mergedData
+
+# lessIll_DGE.lm <- lm(lessIll ~ DGECriteriaNo, data = mergedData)
+# summary(lessIll_DGE.lm)
+# 
+# saveRDS(lessIll_DGE.lm,"./ANALYSIS/Tables/lessIll_DGE.lm.Rds")
+
+lessIll_DGE_scaled.lm <- lm_robust(lessIll_scaled ~ DGECriteriaNoScaled, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(lessIll_DGE_scaled.lm) #standardized
+
+texreg(lessIll_DGE_scaled.lm)
+
+saveRDS(lessIll_DGE_scaled.lm,"./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
+#
+
+lessIll_DGE_scaled_weighted.lm <- lm_robust(lessIll_scaled ~ DGECriteriaNoScaled, weights = eatersPerMealNo, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(lessIll_DGE_scaled.lm) #standardized
+
+texreg(lessIll_DGE_scaled_weighted.lm)
+
+saveRDS(lessIll_DGE_scaled_weighted.lm,"./ANALYSIS/Tables/lessIll_DGE_scaled_weighted.lm.Rds")
+#
+
+# Expand_LessIll.lm = lm(lessIll_weighted ~ DGECriteriaNo + regionalProducts + yearsSupportSince + realSubsidy + state, data = mergedData)
+# summary(Expand_LessIll.lm)
+# 
+# saveRDS(Expand_LessIll.lm,"./ANALYSIS/Tables/Expand_LessIll.lm.Rds")
+
+Expand_LessIll_scaled.lm = lm_robust(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidyPerBeneficiary + state, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(Expand_LessIll_scaled.lm) #standardized
+
+texreg(Expand_LessIll_scaled.lm)
+
[…]

### 2020-02-26 paper.tex
hjkl

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 12:29:41 2020
+% Wed Feb 26 13:04:14 2020
 \begin{table}[ht]
@@
 \hline
-(Intercept) & $-12089.14^{*}$ & $-12089.14^{*}$ & $-12250.60^{**}$ \\
-            & $(5192.86)$     & $(5192.86)$     & $(4524.09)$      \\
-realSubsidy & $2.61^{***}$    & $2.61^{***}$    & $2.72^{***}$     \\
-            & $(0.57)$        & $(0.57)$        & $(0.51)$         \\
+(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
+            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
+realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
+            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
 \hline
-R$^2$       & 0.43            & 0.43            & 0.45             \\
-Adj. R$^2$  & 0.43            & 0.43            & 0.45             \\
-Num. obs.   & 329             & 329             & 440              \\
-RMSE        & 39992.79        & 39992.79        & 39601.41         \\
+R$^2$       & 0.43            & 0.13            & 0.45             \\
+Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
+Num. obs.   & 329             & 250             & 440              \\
+RMSE        & 39992.79        & 3629.72         & 39601.41         \\
 \hline
@@
 \hline
-(Intercept)      & $3.70^{***}$ & $3.70^{***}$ & $3.62^{***}$ \\
-                 & $(0.33)$     & $(0.33)$     & $(0.33)$     \\
-realTripsSubsidy & $0.00^{*}$   & $0.00^{*}$   & $0.00^{*}$   \\
+(Intercept)      & $3.70^{***}$ & $2.62^{***}$ & $3.62^{***}$ \\
+                 & $(0.33)$     & $(0.23)$     & $(0.33)$     \\
+realTripsSubsidy & $0.00^{*}$   & $0.00^{***}$ & $0.00^{*}$   \\
                  & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
 \hline
-R$^2$            & 0.05         & 0.05         & 0.05         \\
-Adj. R$^2$       & 0.04         & 0.04         & 0.05         \\
-Num. obs.        & 322          & 322          & 334          \\
-RMSE             & 2.96         & 2.96         & 2.93         \\
+R$^2$            & 0.05         & 0.09         & 0.05         \\
+Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
+Num. obs.        & 322          & 257          & 334          \\
+RMSE             & 2.96         & 1.70         & 2.93         \\
 \hline
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 12:29:46
+% Date and time: Mi, Feb 26, 2020 - 13:04:19
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 12:29:47
+% Date and time: Mi, Feb 26, 2020 - 13:04:19
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 12:29:47 2020
+% Wed Feb 26 13:04:19 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw
lg

--- 2020-02-26 paper.Rnw
@@
 effect of\\
-- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
+- healthy meals (DGE criterion) on healthy characteristics\\
 - real meals subsidy on number of meals\\
 - real trips subsidy on number of trips\\
-- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
+- real meals subsidy on self-worth and day-to-day skills\\
+- real trips subsidy on self-worth and day-to-day skills\\
 
@@
 Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
+
+\section{The Data}
+
+To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2012 to 2020.
+In each year they send a survey to the organizations with several questions about the previous year.
+The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
+In some organizations one employee fills in the survey and in others they do it as a team.
+Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
+The number of variables varies over time as well.
+Included are numbers like the average eaters per meal or the amount of money they provide to the organizations but also general questions.
+For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
+This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
+If an organization do not answer a question, this is documented as a “99”.
+We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
+The surveyed variables change over the years, but some of them are included every year.
+However, we did several steps to get a full dataset we could work with.
+The data was divided into one dataset for each survey from 2012 to 2020, but we only use the surveys till 2019 since in 2020 some organization-ID´s occurred several times and the data for 2020 were incomplete.
+Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
+Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
+This makes a quick work with R possible since we only use paths relative to the working directory.
+Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
+We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
+Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
+To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
+As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
+The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
+Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
+The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
+The questions are divided in two categories: the variables regarding to the Mittagstisch, answered by all organizations since they are all part of this program and the Entdeckerfonds variables, answered by the organizations that take part on the Entdeckerfonds program in the respective year.
+Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
 
@@
 
-\section{Ehrenwörtliche Erklärung aller Teilnehmer}
+\{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-02-26 paper.tex
lg

--- 2020-02-26 paper.tex
@@
 Laura Jepsen\\
-\texttt{11567799}
+\texttt{11111111}
 \and
@@
 
-\section{Data}
+\section{The Data}
+
+To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2012 to 2020.
+In each year they send a survey to the organizations with several questions about the previous year.
+The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
+In some organizations one employee fills in the survey and in others they do it as a team.
+Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
+The number of variables varies over time as well.
+Included are numbers like the average eaters per meal or the amount of money they provide to the organizations but also general questions.
+For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
+This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
+If an organization do not answer a question, this is documented as a “99”.
+We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
+The surveyed variables change over the years, but some of them are included every year.
+However, we did several steps to get a full dataset we could work with.
+The data was divided into one dataset for each survey from 2012 to 2020, but we only use the surveys till 2019 since in 2020 some organization-ID´s occurred several times and the data for 2020 were incomplete.
+Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
+Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
+This makes a quick work with R possible since we only use paths relative to the working directory.
+Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
+We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
+Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
+To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
+As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
+The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
+Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
+The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
+The questions are divided in two categories: the variables regarding to the Mittagstisch, answered by all organizations since they are all part of this program and the Entdeckerfonds variables, answered by the organizations that take part on the Entdeckerfonds program in the respective year.
+Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
 
@@
 \section{Summary Statistics}
-\subsection{Fundamental Dynamics}
 
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Wed Feb 26 12:46:00 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:07:44 2020
 \begin{table}[ht]
@@
 
-\subsection{Trend of grants}
-
 \begin{figure}
@@
 
-\subsection{Heatlh relevant variables over time}
-
 \begin{figure}
@@
 \end{figure}
-
-\subsection{Equality of opportunities releveant variables over time}
 
@@
 
-\subsection{Empirical Approach}
-
 \begin{equation}
@@
 
-\subsection{Variables of interest: Number of trips and number of meals}
+\\Number of Meals and Number of Trips
 
@@
 (DESCRIBE RESULTS) (COMPARE TO SUMMARY STATISTICS)
-
-\subsection{Variables of interest: Health variables}
 
@@
 
-\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
+\begin{kframe}
 
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c c c c c}
-\hline
- & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
-\hline
-(Intercept)      & $-13.42^{*}$ & $-13.48^{*}$ & $9.20^{***}$ & $8.25^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.10$   & $0.12$   \\
-                 & $(5.88)$     & $(5.89)$     & $(1.84)$     & $(1.78)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
-realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
-                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
-realTripsSubsidy &              &              & $0.00^{***}$ & $0.01^{***}$ &          &              & $-0.00$  & $-0.00$  \\
-                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
-\hline
-R$^2$            & $0.46$       & $0.46$       & $0.32$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.01$   \\
-Adj. R$^2$       & $0.45$       & $0.45$       & $0.31$       & $0.34$       & $0.00$   & $0.03$       & $0.00$   & $0.01$   \\
-Num. obs.        & $428$        & $426$        & $184$        & $177$        & $430$    & $428$        & $186$    & $178$    \\
-RMSE             & $41.50$      & $41.59$      & $21.93$      & $21.36$      & $1.00$   & $0.98$       & $1.00$   & $0.98$   \\
-\hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-\caption{Equal Opportunities Regressions}
-\label{table:coefficients}
-\end{center}
-\end{table}
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworthTrips\_scaled.lm.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
 
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c c c c c}
-\hline
- & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills & selfworth & dayToDaySkills \\
-\hline
-(Intercept)      & $-13.42^{*}$ & $-13.47^{*}$ & $9.25^{***}$ & $8.33^{***}$ & $-0.06$  & $-0.16^{**}$ & $0.11$   & $0.13$   \\
-                 & $(5.88)$     & $(5.89)$     & $(1.82)$     & $(1.74)$     & $(0.06)$ & $(0.06)$     & $(0.10)$ & $(0.11)$ \\
-realSubsidy      & $0.00^{***}$ & $0.00^{***}$ &              &              & $0.00$   & $0.00^{***}$ &          &          \\
-                 & $(0.00)$     & $(0.00)$     &              &              & $(0.00)$ & $(0.00)$     &          &          \\
-realTripsSubsidy &              &              & $0.00^{***}$ & $0.00^{***}$ &          &              & $-0.00$  & $-0.00$  \\
-                 &              &              & $(0.00)$     & $(0.00)$     &          &              & $(0.00)$ & $(0.00)$ \\
-\hline
-R$^2$            & $0.46$       & $0.46$       & $0.32$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.02$   \\
-Adj. R$^2$       & $0.45$       & $0.45$       & $0.31$       & $0.34$       & $0.00$   & $0.03$       & $0.01$   & $0.01$   \\
-Num. obs.        & $428$        & $427$        & $186$        & $180$        & $430$    & $429$        & $189$    & $182$    \\
-RMSE             & $41.50$      & $41.54$      & $21.83$      & $21.21$      & $1.00$   & $0.98$       & $1.00$   & $0.99$   \\
-\hline
-\multicolumn{9}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-\caption{Equal Opportunities Regressions, imputed data}
-\label{table:coefficients}
-\end{center}
-\end{table}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'tss' nicht gefunden}}\end{kframe}
+
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/Tables/selfworth\_IM\_scaled.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in "{}list"{} \%in\% class(l)[1]: Objekt 'ssI' nicht gefunden}}\end{kframe}
 
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{l c}
-\hline
- & Selfworth \\
-\hline
-(Intercept)             & $-1.13^{***}$ \\
-                        & $(0.32)$      \\
-dfcEF2$treatEF          & $-0.47$       \\
-                        & $(0.31)$      \\
-\hline
-Num. obs.               & $430$         \\
-R$^2$ (full model)      & $0.47$        \\
-R$^2$ (proj model)      & $0.47$        \\
-Adj. R$^2$ (full model) & $0.36$        \\
-Adj. R$^2$ (proj model) & $0.36$        \\
-\hline
-\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-\caption{linear regression}
-\label{table:coefficients}
-\end{center}
-\end{table}
-
 Ende??
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
+% Date and time: Mi, Feb 26, 2020 - 13:07:50
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Less Ill} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
-\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
-\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Dietary Knowledge} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -4.009 & 0.803 & -4.996 & 0.00000 \\ 
-\multicolumn{1}{c}{(Intercept):2} & -1.047 & 0.425 & -2.465 & 0.014 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 1.445 & 0.430 & 3.365 & 0.001 \\ 
-\multicolumn{1}{c}{DGECriteriaNo} & -0.089 & 0.052 & -1.712 & 0.087 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Appreciate Healthy} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -1.603 & 0.486 & -3.298 & 0.001 \\ 
-\multicolumn{1}{c}{(Intercept):2} & 0.586 & 0.413 & 1.419 & 0.156 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 3.052 & 0.471 & 6.483 & 0 \\ 
-\multicolumn{1}{c}{DGECriteriaNo} & -0.199 & 0.053 & -3.744 & 0.0002 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -4.855 & 0.584 & -8.315 & 0 \\ 
-\multicolumn{1}{c}{(Intercept):2} & -1.268 & 0.143 & -8.893 & 0 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 1.514 & 0.150 & 10.109 & 0 \\ 
-\multicolumn{1}{c}{realSubsidy} & -0.00001 & 0.00001 & -1.332 & 0.183 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi., Feb 26, 2020 - 12:46:08
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -3.543 & 0.343 & -10.330 & 0 \\ 
-\multicolumn{1}{c}{(Intercept):2} & -0.736 & 0.132 & -5.563 & 0.00000 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 1.764 & 0.157 & 11.249 & 0 \\ 
-\multicolumn{1}{c}{realSubsidy} & -0.00003 & 0.00001 & -4.070 & 0.00005 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
 \subsection{A2: Partition}
@@
 
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Wed Feb 26 12:46:08 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:07:50 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Wed Feb 26 12:46:08 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:07:50 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
 
-\section{Ehrenwörtliche Erklärung aller Teilnehmer}
+\{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-02-26 paper.tex
lg

--- 2020-02-26 paper.tex
@@
 \hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$            & $0.43$          & $0.05$       \\
+Adj. R$^2$       & $0.43$          & $0.04$       \\
+Num. obs.        & $329$           & $322$        \\
+RMSE             & $39992.79$      & $2.96$       \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 
+To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2012 to 2020.
+In each year they send a survey to the organizations with several questions about the previous year.
+The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
+In some organizations one employee fills in the survey and in others they do it as a team.
+Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
+The number of variables varies over time as well.
+Included are numbers like the average eaters per meal or the amount of money they provide to the organizations but also general questions.
+For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
+This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
+If an organization do not answer a question, this is documented as a “99”.
+We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
+The surveyed variables change over the years, but some of them are included every year.
+However, we did several steps to get a full dataset we could work with.
+The data was divided into one dataset for each survey from 2012 to 2020, but we only use the surveys till 2019 since in 2020 some organization-ID´s occurred several times and the data for 2020 were incomplete.
+Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
+Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
+This makes a quick work with R possible since we only use paths relative to the working directory.
+Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
+We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
+Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
+To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
+As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
+The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
+Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
+The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
+The questions are divided in two categories: the variables regarding to the Mittagstisch, answered by all organizations since they are all part of this program and the Entdeckerfonds variables, answered by the organizations that take part on the Entdeckerfonds program in the respective year.
+Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
+=======
+
 \section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 13:04:14 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:32:15 2020
 \begin{table}[ht]
@@
 
+\usepackage{graphicx}
+
 \begin{table}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c }
+\begin{tabular}{l c c c}
 \hline
@@
 \hline
-R$^2$       & 0.43            & 0.13            & 0.45             \\
-Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
-Num. obs.   & 329             & 250             & 440              \\
-RMSE        & 39992.79        & 3629.72         & 39601.41         \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$       & $0.43$          & $0.13$          & $0.45$           \\
+Adj. R$^2$  & $0.43$          & $0.12$          & $0.45$           \\
+Num. obs.   & $329$           & $250$           & $440$            \\
+RMSE        & $39992.79$      & $3629.72$       & $39601.41$       \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$            & 0.05         & 0.09         & 0.05         \\
-Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
-Num. obs.        & 322          & 257          & 334          \\
-RMSE             & 2.96         & 1.70         & 2.93         \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$            & $0.05$       & $0.09$       & $0.05$       \\
+Adj. R$^2$       & $0.04$       & $0.08$       & $0.05$       \\
+Num. obs.        & $322$        & $257$        & $334$        \\
+RMSE             & $2.96$       & $1.70$       & $2.93$       \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
+\begin{tabular}{l c c c c}
 \hline
@@
 \hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
-Num. obs.           & 121          & 120         & 177          & 177          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       \\
+Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       \\
+Num. obs.           & $121$        & $120$       & $177$        & $177$        \\
+RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
-Num. obs.           & 214      & 212      & 275        & 275      \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   \\
+Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   \\
+Num. obs.           & $214$    & $212$    & $275$      & $275$    \\
+RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
-Num. obs.           & 213          & 211      & 274          & 274        \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     \\
+Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    \\
+Num. obs.           & $213$        & $211$    & $274$        & $274$      \\
+RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
-Num. obs.                      & 428      & 184      & 430      & 187      \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
+Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
+Num. obs.                      & $428$    & $184$    & $430$    & $187$    \\
+RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 \hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
-Num. obs.                      & 426      & 177      & 429      & 181      \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
+Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
+Num. obs.                      & $426$    & $177$    & $429$    & $181$    \\
+RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:04:19
+% Date and time: Mi, Feb 26, 2020 - 13:32:20
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:04:19
+% Date and time: Mi, Feb 26, 2020 - 13:32:20
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:04:19
+% Date and time: Mi, Feb 26, 2020 - 13:32:21
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 13:04:19 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:32:21 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 13:04:19 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 13:32:21 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
 \subsection{A3: OLS Regressions}

### 2020-02-26 ANALYSIS/DATA/categoricalData.R
right order in makeGather

@@ -52,7 +52,9 @@ mergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
   mutate_if(pretendsToBeMetric, list(scaled = scale_this, ordered = as.ordered, weighted = weight))
 
 mergedDataImputeInterpolation <- mergedDataImputeInterpolation %>% 
-  mutate(DGECriteriaNoScaled = scale_this(DGECriteriaNo), DGECriteriaNoWeighted = weight(mergedData$DGECriteriaNo), DGECriteriaNoOrdered = as.ordered(DGECriteriaNo))
+  mutate(DGECriteriaNoScaled = scale_this(DGECriteriaNo), DGECriteriaNoWeighted = weight(mergedData$DGECriteriaNo), DGECriteriaNoOrdered = as.ordered(DGECriteriaNo),
+         lessIll_scaled = scale_this(lessIll), lessIll_weighted = weight(mergedData$lessIll), lessIll_ordered = as.ordered(lessIll),
+         influenceHome_scaled = scale_this(influenceHome), influenceHome_weighted = weight(mergedData$influenceHome), influenceHome_ordered = as.ordered(influenceHome))
 
 # do the same for mealsNoOutliers
 

### 2020-02-26 paper.Rnw
lg

@@
 The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
+Figure\\
+
+\begin{figure}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{LineDisp}
+
+<<echo=FALSE>>=
+figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
+print(figureDaytodayskillsSelfworth)
+@
+
+\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
 

### 2020-02-26 paper.tex
lg

@@
 
+Figure\\
+
+\begin{figure}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{LineDisp}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Summary Statistics}
@@
 % latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Wed Feb 26 13:32:15 2020
+% Wed Feb 26 15:07:47 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:20
+% Date and time: Mi, Feb 26, 2020 - 15:07:52
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:20
+% Date and time: Mi, Feb 26, 2020 - 15:07:52
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:21
+% Date and time: Mi, Feb 26, 2020 - 15:07:52
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Wed Feb 26 13:32:21 2020
+% Wed Feb 26 15:07:52 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw
references, labels, notes work in LaTeX

--- 2020-02-26 paper.Rnw
@@
 \usepackage{floatrow}
+\usepackage{booktabs}
 \usepackage[hidelinks]{hyperref}
@@
 \listoftables
+
+% note below table
+% https://stackoverflow.com/questions/44549464/table-spacing-issue-converting-to-pdf-via-latex-with-pandoc/44797387#44797387
 \listoffigures
@@
 
+Figure \ref{LineDisp}
+
 % <<results='asis', echo=FALSE>>=
@@
 
+Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
@@
 
-<<GrantsRegressions Lunch, echo=FALSE, results='asis', message=FALSE>>=
+<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ %stars.}", caption.above = TRUE, 
+    label = "GrantsRegressionsLunch", booktabs = TRUE)
 @
 
-<<GrantsRegressions Trips, echo=FALSE, results='asis', message=FALSE>>=
+Table \ref{GrantsRegressionsLunch}
+
+<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
@@
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips')
 
@@
 
-<<HealthRegressions_LessIll, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = "HealthRegressions-LessIll")
 @
 
-<<HealthRegressions_DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
 dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-DietaryKnowledge')
 @
 
-<<HealthRegressions_AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
 aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-AppreciateHealthy')
 @
@@
 
-texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
+texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
 @
@@
 
-texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
+texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
 @

### 2020-02-26 paper.tex
references, labels, notes work in LaTeX

--- 2020-02-26 paper.tex
@@
 \begin{center}
-\begin{tabular}{l c c}
+\begin{tabular}{l c c }
 \hline
@@
 \hline
-R$^2$            & $0.43$          & $0.05$       \\
-Adj. R$^2$       & $0.43$          & $0.04$       \\
-Num. obs.        & $329$           & $322$        \\
-RMSE             & $39992.79$      & $2.96$       \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$            & 0.43            & 0.05         \\
+Adj. R$^2$       & 0.43            & 0.04         \\
+Num. obs.        & 329             & 322          \\
+RMSE             & 39992.79        & 2.96         \\
+\hline
+\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Wed Feb 26 13:32:15 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Wed Feb 26 15:43:13 2020
 \begin{table}[ht]
@@
 
-\usepackage{graphicx}
+\usepackage{booktabs}
 
 \begin{table}
+\caption{Regression Results: Number of meals}
 \begin{center}
 \scalebox{0.8}{
-\begin{tabular}{l c c c}
-\hline
+\begin{tabular}{l c c c }
+\toprule
  & OLS & OLS without Outliers & OLS Impute \\
-\hline
+\midrule
 (Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
@@
             & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
-\hline
-R$^2$       & $0.43$          & $0.13$          & $0.45$           \\
-Adj. R$^2$  & $0.43$          & $0.12$          & $0.45$           \\
-Num. obs.   & $329$           & $250$           & $440$            \\
-RMSE        & $39992.79$      & $3629.72$       & $39601.41$       \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Number of meals}
-\label{table:coefficients}
+\midrule
+R$^2$       & 0.43            & 0.13            & 0.45             \\
+Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
+Num. obs.   & 329             & 250             & 440              \\
+RMSE        & 39992.79        & 3629.72         & 39601.41         \\
+\bottomrule
+\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
 \end{center}
@@
 
-\usepackage{graphicx}
+Table \ref{GrantsRegressionsLunch}
 
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c}
+\begin{tabular}{l c c c }
 \hline
@@
 \hline
-R$^2$            & $0.05$       & $0.09$       & $0.05$       \\
-Adj. R$^2$       & $0.04$       & $0.08$       & $0.05$       \\
-Num. obs.        & $322$        & $257$        & $334$        \\
-RMSE             & $2.96$       & $1.70$       & $2.93$       \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$            & 0.05         & 0.09         & 0.05         \\
+Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
+Num. obs.        & 322          & 257          & 334          \\
+RMSE             & 2.96         & 1.70         & 2.93         \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: Number of trips}
-\label{table:coefficients}
+\label{GrantsRegressionsTrips}
 \end{center}
@@
 
-\usepackage{graphicx}
-
 \begin{table}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c}
+\begin{tabular}{l c c c c }
 \hline
@@
 \hline
-R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       \\
-Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       \\
-Num. obs.           & $121$        & $120$       & $177$        & $177$        \\
-RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
+Num. obs.           & 121          & 120         & 177          & 177          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: Less Ill}
-\label{table:coefficients}
+\label{HealthRegressions-LessIll}
 \end{center}
 \end{table}
-
-\usepackage{graphicx}
 
@@
 \hline
-R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   \\
-Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   \\
-Num. obs.           & $214$    & $212$    & $275$      & $275$    \\
-RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
+Num. obs.           & 214      & 212      & 275        & 275      \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: Dietary Knowledge}
-\label{table:coefficients}
+\label{HealthRegressions-DietaryKnowledge}
 \end{center}
 \end{table}
-
-\usepackage{graphicx}
 
@@
 \hline
-R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     \\
-Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    \\
-Num. obs.           & $213$        & $211$    & $274$        & $274$      \\
-RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
+Num. obs.           & 213          & 211      & 274          & 274        \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: Appreciate Healthy}
-\label{table:coefficients}
+\label{HealthRegressions-AppreciateHealthy}
 \end{center}
@@
 \subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
-
-\usepackage{graphicx}
 
@@
 \hline
-R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
-Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
-Num. obs.                      & $428$    & $184$    & $430$    & $187$    \\
-RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
+Num. obs.                      & 428      & 184      & 430      & 187      \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: Selfworth}
-\label{table:coefficients}
+\label{SelfworthRegressions}
 \end{center}
 \end{table}
-
-\usepackage{graphicx}
 
@@
 \hline
-R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
-Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
-Num. obs.                      & $426$    & $177$    & $429$    & $181$    \\
-RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
+Num. obs.                      & 426      & 177      & 429      & 181      \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 \caption{Regression Results: dayToDaySkills}
-\label{table:coefficients}
+\label{DayToDaySkillsRegressions}
 \end{center}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:20
+% Date and time: Wed, Feb 26, 2020 - 3:43:31 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:20
+% Date and time: Wed, Feb 26, 2020 - 3:43:33 PM
 % Requires LaTeX packages: dcolumn 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:21
+% Date and time: Wed, Feb 26, 2020 - 3:43:33 PM
 % Requires LaTeX packages: dcolumn 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 13:32:21
+% Date and time: Wed, Feb 26, 2020 - 3:43:34 PM
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Wed Feb 26 13:32:21 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Wed Feb 26 15:43:34 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Wed Feb 26 13:32:21 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Wed Feb 26 15:43:34 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
 \subsection{A3: OLS Regressions}
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): cannot open the connection}}\end{kframe}
 

### 2020-02-26 paper.tex
update

@@
 \usepackage{floatrow}
-\usepackage{booktabs}
 \usepackage[hidelinks]{hyperref}
@@
 \listoftables
-
-% note below table
-% https://stackoverflow.com/questions/44549464/table-spacing-issue-converting-to-pdf-via-latex-with-pandoc/44797387#44797387
 \listoffigures
@@
 
-Figure \ref{LineDisp}
-
 % <<results='asis', echo=FALSE>>=
@@
 
-Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 15:43:13 2020
+% Wed Feb 26 14:21:55 2020
 \begin{table}[ht]
@@
 
-\usepackage{booktabs}
-
 \begin{table}
-\caption{Regression Results: Number of meals}
 \begin{center}
@@
 \begin{tabular}{l c c c }
-\toprule
+\hline
  & OLS & OLS without Outliers & OLS Impute \\
-\midrule
+\hline
 (Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
@@
             & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
-\midrule
+\hline
 R$^2$       & 0.43            & 0.13            & 0.45             \\
@@
 RMSE        & 39992.79        & 3629.72         & 39601.41         \\
-\bottomrule
-\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsLunch}
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Number of meals}
+\label{table:coefficients}
 \end{center}
 \end{table}
-
-Table \ref{GrantsRegressionsLunch}
 
@@
 \caption{Regression Results: Number of trips}
-\label{GrantsRegressionsTrips}
+\label{table:coefficients}
 \end{center}
@@
 \caption{Regression Results: Less Ill}
-\label{HealthRegressions-LessIll}
+\label{table:coefficients}
 \end{center}
@@
 \caption{Regression Results: Dietary Knowledge}
-\label{HealthRegressions-DietaryKnowledge}
+\label{table:coefficients}
 \end{center}
@@
 \caption{Regression Results: Appreciate Healthy}
-\label{HealthRegressions-AppreciateHealthy}
+\label{table:coefficients}
 \end{center}
@@
 \caption{Regression Results: Selfworth}
-\label{SelfworthRegressions}
+\label{table:coefficients}
 \end{center}
@@
 \caption{Regression Results: dayToDaySkills}
-\label{DayToDaySkillsRegressions}
+\label{table:coefficients}
 \end{center}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 3:43:31 PM
+% Date and time: Mi, Feb 26, 2020 - 14:22:05
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 3:43:33 PM
+% Date and time: Mi, Feb 26, 2020 - 14:22:06
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 3:43:34 PM
+% Date and time: Mi, Feb 26, 2020 - 14:22:06
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 15:43:34 2020
+% Wed Feb 26 14:22:06 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
 \subsection{A3: OLS Regressions}
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): cannot open the connection}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
 

### 2020-02-26 paper.Rnw
ghj

--- 2020-02-26 paper.Rnw
@@
 
-To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2012 to 2020.
+To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2011 to 2018.
 In each year they send a survey to the organizations with several questions about the previous year.
@@
 However, we did several steps to get a full dataset we could work with.
-The data was divided into one dataset for each survey from 2012 to 2020, but we only use the surveys till 2019 since in 2020 some organization-ID´s occurred several times and the data for 2020 were incomplete.
+The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete.
 Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
@@
 Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
-=======
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
-Figure\\
-
-\begin{figure}
-  \caption{Trend in everyday expertise and selfworth}
-  \label{LineDisp}
-
-<<echo=FALSE>>=
-figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
-print(figureDaytodayskillsSelfworth)
-@
-
-\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
-The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
+Many organizations do not answer all questions CHILDREN poses.
+We create a seperate data set, in which we impute missing values with an organization-specific linear trend.
+CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year.
+We fit our models with outliers excluded to see if they are driving results.
+We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile.
+Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.
 
@@
 \subsection{Fundamental Dynamics}
+
+In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
+We focus on the number of estimated ultimate beneficiaries in both programs, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
+We also look at selected outcomes, i.e.
+those related to health as well as self-worth and day-to-day skills.
+We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
+We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
+These are only available after logging in on DESTATIS.
+The organizations also gave information about their total yearly budget.
+We inflate this with the general price index.
 
@@
           caption = "Summary Statistics",
-          align = "lmmmmm"
+          align = "lmmmmm", 
+          label = "fundamentalDynamics"
           )
@@
 
-At the beginning of the time series in 2011, they supported in x institutions.
-In 2018, this number had increased to y.
-In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
-We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
-We also look at selected outcomes, i.e.
-those related to health as well as self-worth and day-to-day skills.
-We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
-We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
-These are only available after logging in on DESTATIS.
-The organizations also gave information about their total yearly budget.
-We inflate this with the general price index.
+Table \ref{fundamentalDynamics} shows that, at the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations.
+In 2018, this number has increased to 68.
+In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018.
+In the trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018.
+In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.
 
@@
 \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median and the median grant per beneficiary.
-From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
+From left to right: Meals, Trips.
+From top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
 \end{figure}
 
-\subsection{Heatlh relevant variables over time}
+For the dynamics of figure \ref{totalGrantsDyn} we visualze the dynamics of CHILDRENs' grants by distinguishing between the sum of grants in one year, the median and the median grant per beneficiary.
+We also compare the grants of the Lunch and the Trips Program.
+
+Figure \ref{totalGrantsDyn} shows no exact trend for the total real grant for the Lunch program.
+Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year.
+Since 2017 an increase is again visible.
+In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
+In accordance, the median Meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.
+
+In the total Trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince.
+The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
+
+These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
+
+\subsection{Health relevant variables over time}
+
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier, have a growing appreciation for a healthier diet, and have increased their knowledge about what constitutes a healthy diet.
+Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For this figure, we use the original ordinal varibles which result from the survey structure.
 
@@
 
+In Figure \ref{Health_timeplots}, for the variable 'lessIll', there is much non available data.
+In all years, most organizations say that most beneficiaries are more healthy (3).
+The least stated category is, that all beneficiaries are less ill(4).
+That few are less ill (1), appears sometimes and the leftover category,none (0), which is only coded for the variable 'lessIll', appears as good as never.
+
+In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge') mostorganizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
+The least stated category is that some beneficiaries increased their dietary knowledge (2).
+The leftover category, few (1), does not appear.
+
+The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy'.
+Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet (3).
+The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet (4).
+The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet (2).
+The leftover category, few, also does not appear.
+
 \subsection{Equality of opportunities releveant variables over time}
+
+In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
+Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.
 
@@
 
+Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth.
+Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3).
+The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2).
+The leftover category, few, does not appear.
+
+In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).
+
 \section{Regressions}
@@
 \begin{equation}
-\label{Equation 1}
+\label{SimpleLinearModel}
   y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
@@
 
-In this section we use a standard OLS equation, as described in equation 1.
-Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables.
-We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data.
-(DESCRIBE METHODS EXACT)
+In this section we use a simple linear model, as described in equation \ref{SimpleLinear Model}. We look at the association between:
 
-\subsection{Variables of interest: Number of trips and number of meals}
+\begin{itemize}
+  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
+  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
+   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
+\end{itemize}
+
+We discuss all these models in turn.
+
+\subsection{Direct effects of CHILDREN's grants}
+
+If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
+
+As table \ref{}
 
@@
 
-texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Effects of subsidy for Meals program on number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
 @
@@
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Effects of subsidy for Trips program on number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
 
@@
 @
+
+\section{Feature Selection}
+
+\subsection{Factor Analysis}
+
+\subsection{Double Selection}
+
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
 @
-
-\section{Factor Analysis}
 

### 2020-02-26 paper.tex
ghj

@@
 Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
-=======
-
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:21:55 2020
+% Wed Feb 26 14:56:01 2020
 \begin{table}[ht]
@@
 
-At the beginning of the time series in 2011, they supported in x institutions.
-In 2018, this number had increased to y.
+At the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations.
+In 2018, this number has increased to 68.
+In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018.
+In the trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018.
+In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.
 In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
@@
 
-\subsection{Heatlh relevant variables over time}
+For the dynamics of figure 2 we have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).
+We distinguish between the sum of grants in one year, the median and the median grant per beneficiary and between the Lunch and Trips Program.
+
+Figure 2 shows no exact trend for the total real grant for the Lunch program.
+Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year.
+Since 2017, an increase is again visible.
+In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
+In accordance, the median Meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.
+
+In the total Trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince.
+The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
+These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table 1, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
+
+\subsection{Health relevant variables over time}
 
@@
 
+\section{Feature Selection}
+
+\subsection{Factor Analysis}
+
+\subsection{Double Selection}
+
+\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
+
+How do children benefit from visiting social institutions that CHILDREN supports financially?
+So far this question could not be empirically validated.
+Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
+However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
+This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
+The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
+
 Empirical Approach\\
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:22:05
+% Date and time: Mi, Feb 26, 2020 - 14:56:06
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-\section{Factor Analysis}
-
 \section{Conclusion}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:22:06
+% Date and time: Mi, Feb 26, 2020 - 14:56:06
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:22:06 2020
+% Wed Feb 26 14:56:06 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw

@@
 Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.
+
+Figure\\
+
+\begin{figure}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{LineDisp}
+
+<<echo=FALSE>>=
+figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
+print(figureDaytodayskillsSelfworth)
+@
+>>>>>>> e374c897fa430f39f38663dd2617ee94ca47e4bb
+
+\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
 
@@
 
-texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Effects of subsidy for Meals program on number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ %stars.}", caption.above = TRUE, 
+    label = "GrantsRegressionsLunch", booktabs = TRUE)
+>>>>>>> e374c897fa430f39f38663dd2617ee94ca47e4bb
 @
 
-<<GrantsRegressions Trips, echo=FALSE, results='asis', message=FALSE>>=
+Table \ref{GrantsRegressionsLunch}
+
+<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
@@
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Effects of subsidy for Trips program on number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips')
 

### 2020-02-26 paper.Rnw
lg

--- 2020-02-26 paper.Rnw
@@
 
-\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
 The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
@@
 
-<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
+<<GrantsRegressions Lunch, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\\\ %stars.}", caption.above = TRUE, 
-    label = "GrantsRegressionsLunch", booktabs = TRUE)
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
 @
 
-Table \ref{GrantsRegressionsLunch}
-
-<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
+<<GrantsRegressions Trips, echo=FALSE, results='asis', message=FALSE>>=
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
@@
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips')
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8)
 
@@
 
-<<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions_LessIll, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = "HealthRegressions-LessIll")
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
 @
 
-<<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions_DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
 dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-DietaryKnowledge')
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
 @
 
-<<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
+<<HealthRegressions_AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
 aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-AppreciateHealthy')
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8)
 @
@@
 
-texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
+texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
 @
@@
 
-texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
+texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8)
 @

### 2020-02-26 paper.tex
lg

--- 2020-02-26 paper.tex
@@
 
+Figure\\
+
+\begin{figure}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{LineDisp}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Summary Statistics}
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:21:55 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 17:44:28 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:22:05
+% Date and time: Mi, Feb 26, 2020 - 17:44:35
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:22:06
+% Date and time: Mi, Feb 26, 2020 - 17:44:35
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:22:06 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 17:44:35 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:22:06 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Wed Feb 26 17:44:35 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw
ghjhj

--- 2020-02-26 paper.Rnw
@@
 @
->>>>>>> e374c897fa430f39f38663dd2617ee94ca47e4bb
 
@@
 
-In this section we use a simple linear model, as described in equation \ref{SimpleLinear Model}. We look at the association between:
+In this section we use a simple linear model with, as described in equation \ref{SimpleLinear Model}. We look at the association between:
 
@@
 
-As table \ref{}
-
-As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries.
-In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset.
-TableX shows the regression results.
+As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
+Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
+The estimated coefficents are very similar when we use the original dataset and the one with imputed values.
+In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
+This estimate is highly statistically significant.
+When we exclude outliers, i.e.
+those organizations that give out very many menus or very few menus,
+the estimated coefficent decreases by about one order of magnitude.
+Still, spending not much more than three EUR more goes hand in hand with one extra meal.
+The estimate is also highly statistically significant.
 
@@
     label = "GrantsRegressionsLunch", booktabs = TRUE)
->>>>>>> e374c897fa430f39f38663dd2617ee94ca47e4bb
 @
-
-Table \ref{GrantsRegressionsLunch}
+In the remit of the Trips program, the picture looks much different.
 
@@
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips')
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips', digits = 4)
 
@@
 
-Outliers?
+As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...
+
+Use from zwichenpräsentation
+
+\begin{equation}
+\label{ModelProdu}
+\ln y_{it} = \frac{}{}  \sum
+\end{equation}
 

### 2020-02-26 paper.tex
ghjhj

--- 2020-02-26 paper.tex
@@
 
+Many organizations do not answer all questions CHILDREN poses.
+We create a seperate data set, in which we impute missing values with an organization-specific linear trend.
+CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year.
+We fit our models with outliers excluded to see if they are driving results.
+We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile.
+Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.
+
+Figure\\
+
+\begin{figure}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{LineDisp}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Summary Statistics}
@@
 
+In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
+We focus on the number of estimated ultimate beneficiaries in both programs, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
+We also look at selected outcomes, i.e.
+those related to health as well as self-worth and day-to-day skills.
+We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
+We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
+These are only available after logging in on DESTATIS.
+The organizations also gave information about their total yearly budget.
+We inflate this with the general price index.
+
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:56:01 2020
+% Wed Feb 26 18:39:45 2020
 \begin{table}[ht]
@@
 \caption{Summary Statistics} 
+\label{fundamentalDynamics}
 \end{table}
@@
 
-At the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations.
+Table \ref{fundamentalDynamics} shows that, at the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations.
 In 2018, this number has increased to 68.
@@
 In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.
-In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
-We focus on the number of estimated ultimate beneficiaries, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
-We also look at selected outcomes, i.e.
-those related to health as well as self-worth and day-to-day skills.
-We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
-We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
-These are only available after logging in on DESTATIS.
-The organizations also gave information about their total yearly budget.
-We inflate this with the general price index.
 
@@
 \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median and the median grant per beneficiary.
-From left to right: Meals, Trips, from top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
+From left to right: Meals, Trips.
+From top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
 \end{figure}
 
-For the dynamics of figure 2 we have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals progam and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).
-We distinguish between the sum of grants in one year, the median and the median grant per beneficiary and between the Lunch and Trips Program.
-
-Figure 2 shows no exact trend for the total real grant for the Lunch program.
+For the dynamics of figure \ref{totalGrantsDyn} we visualze the dynamics of CHILDRENs' grants by distinguishing between the sum of grants in one year, the median and the median grant per beneficiary.
+We also compare the grants of the Lunch and the Trips Program.
+
+Figure \ref{totalGrantsDyn} shows no exact trend for the total real grant for the Lunch program.
 Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year.
-Since 2017, an increase is again visible.
+Since 2017 an increase is again visible.
 In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
@@
 The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
-These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table 1, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
+
+These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
 
 \subsection{Health relevant variables over time}
+
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the degree to which beneficiaries: are healthier, have a growing appreciation for a healthier diet, and have increased their knowledge about what constitutes a healthy diet.
+Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For this figure, we use the original ordinal varibles which result from the survey structure.
 
@@
 
-In this section we use a standard OLS equation, as described in equation 1.
-Where needed, we modified the given data, by using weights, excluding outliers and by scaling relevant variables.
-We also compared the results with the actual dataset to the results we gained by using a dataset in which we imputed necessary data.
-(DESCRIBE METHODS EXACT)
-
-\subsection{Variables of interest: Number of trips and number of meals}
-
-As the first variables of interest we consider the number of meals the organizations recorded and the number of trips the organizations made together with the beneficiaries.
-In this case, we use standard OLS in a first equation, exclude outliers from the variables 'mealsNo' and 'tripsNo' to obtain a believable value and compare to the imputed dataset.
-TableX shows the regression results.
+In this section we use a simple linear model with, as described in equation \ref{SimpleLinear Model}. We look at the association between:
+
+\begin{itemize}
+  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
+  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
+   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
+\end{itemize}
+
+We discuss all these models in turn.
+
+\subsection{Direct effects of CHILDREN's grants}
+
+If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
+
+As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
+Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
+The estimated coefficents are very similar when we use the original dataset and the one with imputed values.
+In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
+This estimate is highly statistically significant.
+When we exclude outliers, i.e.
+those organizations that give out very many menus or very few menus,
+the estimated coefficent decreases by about one order of magnitude.
+Still, spending not much more than three EUR more goes hand in hand with one extra meal.
+The estimate is also highly statistically significant.
+
+\usepackage{booktabs}
+
+\begin{table}
+\caption{Regression Results: Number of meals}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c }
+\toprule
+ & OLS & OLS without Outliers & OLS Impute \\
+\midrule
+(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
+            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
+realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
+            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
+\midrule
+R$^2$       & 0.43            & 0.13            & 0.45             \\
+Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
+Num. obs.   & 329             & 250             & 440              \\
+RMSE        & 39992.79        & 3629.72         & 39601.41         \\
+\bottomrule
+\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
+
+In the remit of the Trips program, the picture looks much different.
 
@@
 \hline
-(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
-            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
-realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
-            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
-\hline
-R$^2$       & 0.43            & 0.13            & 0.45             \\
-Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
-Num. obs.   & 329             & 250             & 440              \\
-RMSE        & 39992.79        & 3629.72         & 39601.41         \\
+(Intercept)      & $3.7049^{***}$ & $2.6236^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.2300)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+\hline
+R$^2$            & 0.0474         & 0.0880         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0844         & 0.0476         \\
+Num. obs.        & 322            & 257            & 334            \\
+RMSE             & 2.9565         & 1.6981         & 2.9310         \\
 \hline
@@
 }
-\caption{Regression Results: Number of meals}
-\label{table:coefficients}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c }
-\hline
- & OLS & OLS without Outliers & OLS Impute \\
-\hline
-(Intercept)      & $3.70^{***}$ & $2.62^{***}$ & $3.62^{***}$ \\
-                 & $(0.33)$     & $(0.23)$     & $(0.33)$     \\
-realTripsSubsidy & $0.00^{*}$   & $0.00^{***}$ & $0.00^{*}$   \\
-                 & $(0.00)$     & $(0.00)$     & $(0.00)$     \\
-\hline
-R$^2$            & 0.05         & 0.09         & 0.05         \\
-Adj. R$^2$       & 0.04         & 0.08         & 0.05         \\
-Num. obs.        & 322          & 257          & 334          \\
-RMSE             & 2.96         & 1.70         & 2.93         \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-}
 \caption{Regression Results: Number of trips}
-\label{table:coefficients}
+\label{GrantsRegressionsTrips}
 \end{center}
@@
 \caption{Regression Results: Less Ill}
-\label{table:coefficients}
+\label{HealthRegressions-LessIll}
 \end{center}
@@
 \caption{Regression Results: Dietary Knowledge}
-\label{table:coefficients}
+\label{HealthRegressions-DietaryKnowledge}
 \end{center}
@@
 \caption{Regression Results: Selfworth}
-\label{table:coefficients}
+\label{SelfworthRegressions}
 \end{center}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:56:06
+% Date and time: Mi, Feb 26, 2020 - 18:39:51
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-Outliers?
+As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...
+
+Use from zwichenpräsentation
+
+\begin{equation}
+\label{ModelProdu}
+\ln y_{it} = \frac{}{}  \sum
+\end{equation}
 
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:56:06
+% Date and time: Mi, Feb 26, 2020 - 18:39:52
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 14:56:06
+% Date and time: Mi, Feb 26, 2020 - 18:39:52
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 14:56:06 2020
+% Wed Feb 26 18:39:52 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw
commit  pull

@@
 
-In this section we use a simple linear model with, as described in equation \ref{SimpleLinear Model}. We look at the association between:
+In this section we use a simple linear model, as described in equation \ref{SimpleLinear Model}. We look at the association between:
 

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R
Update

@@ -1,0 +1,106 @@
+### DiD-Schätzung final ###
+
+# Laden der benötigten Packages
+
+library(estimatr)
+library(robustbase)
+library(tidyverse)
+library(sandwich)
+library(lmtest)
+library(broom)
+library(zoo)
+library(dplyr)
+library(stargazer)
+library(lfe)
+library(Matrix)
+library(texreg)
+
+
+#### Everyday expertise ####
+
+
+#### Erste Definition der Treatment Variable ####
+
+# Verwendeter Datensatz: dfcEF2
+
+# DiD-Estimation mit id fixed effects and year fixed effects
+
+lmdid_dayToDaySkills_1 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year)
+
+summary(lmdid_dayToDaySkills_1)
+summary(lmdid_dayToDaySkills_1, robust = TRUE)
+
+RSE_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Robust s.e"]
+RpValue_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Pr(>|t|)"]
+
+
+# Mit organization-specific Kontrollvariablen
+
+lmdid_dayToDaySkills_2 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year
+                                + dfcEF2$subsidy + dfcEF2$totalCost + dfcEF2$weeklyCooks_scaled)
+
+summary(lmdid_dayToDaySkills_2)
+summary(lmdid_dayToDaySkills_2, robust = TRUE)
+
+RSE_2 = coef(summary(lmdid_dayToDaySkills_2, robust = TRUE))[, "Robust s.e"]
+RpValue_2 = coef(summary(lmdid_dayToDaySkills_2, robust = TRUE))[, "Pr(>|t|)"]
+
+
+
+#### Zweite Definition der Treatment Variable ####
+
+# Verwendeter Datensatz: dfcEF
+
+# DiD-Estimation mit id fixed effects and year fixed effects
+
+lmdid_dayToDaySkills_3 <-  felm(dfcEF$dayToDaySkills_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year)
+
+summary(lmdid_dayToDaySkills_3)
[…]

### 2020-02-26 paper.Rnw
hjk

@@
 
-In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the degree to which beneficiaries: are healthier, have a growing appreciation for a healthier diet, and have increased their knowledge about what constitutes a healthy diet.
+In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet.
+These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
 Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
@@
 \floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
 The x-axis plots the year.
@@
 @
+
 In the remit of the Trips program, the picture looks much different.
+In the case of the original data set and the data set with imputed variables, an increase in the trips subsidy by 5000 EUR is needed for an extra trip.
+The coefficent of 0.0002 is statistically significant at the 5\% level.
+As soon as outliers are excluded, the coefficent changes to 0.0003, which is highly statistically significant.
+This means that, according to this model, at least 3000 EUR are needed for an additional trip.
+In sum, there seems to be no clear connection between how much money CHILDREN gives to an organization and the number of trips it organizes.
 
@@
 texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips', digits = 4)
+@
 
+\subsection{Variables of interest: selfworth and everyday expertise}
+
+In their surveys, CHILDREN asks about two variables in both programs.
+These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise.
+This feature could potentially allow us to compare the two programs regarding their realtive effectiveness.
+Like always, we standardize the two outcome variables.
+As before, we can only make associational claims.
+We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes.
+In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.
+
+Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.
+
+<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=
+
+ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") 
+tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
+ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
+tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
+
+texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
 @
+
+<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
+ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
+tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
+dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
+tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
+
+texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
+@
+
 \subsection{Variables of interest: Health variables}
 
-In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.
+Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could.
+In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus.
+An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were.
+This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+
+In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
+These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
+
+Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.
+
+We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
+If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.
 
@@
 \floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
-It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-According to information from CHILDREN, they ask the organizations to send them their menus.
-An ecotrophologist collaborating with CHILDREN assesed the menus.
+It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+According to information from CHILDREN, they ask the organizations to send them a sample of their menus.
+An ecotrophologist collaborating with CHILDREN assessed the menus.
 In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
 The x-axis plots the index for a healthy diet.
@@
 texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-AppreciateHealthy')
-@
-
-\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
-
-<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=
-
-ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") #standardizedweighted
-tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
-ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
-tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds")
-
-texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
-@
-
-<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
-ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
-tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
-dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
-tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
-
-texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
 @

### 2020-02-26 paper.Rnw
compiled pdf

--- 2020-02-26 paper.Rnw
@@
 
-<<Grant Trend, echo=FALSE, message=FALSE>>=
+<<GrantTrend, echo=FALSE, message=FALSE>>=
 totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
@@
   \label{Health_timeplots}
-<<Health time plots, echo=FALSE, message=FALSE>>=
+<<HealthTimePlots, echo=FALSE, message=FALSE>>=
 Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
@@
   \label{Equality_timeplots}
-<<Equality time plots, echo=FALSE, message=FALSE>>=
+<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
 Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
@@
 
-<<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-#expanded model less ill
-
-lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
-lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
-elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
-@
+% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% #expanded model less ill 
+% 
+% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
+% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
+% @
 

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R
texreg tables

@@ -103,8 +103,23 @@ print(readRDS('./ANALYSIS/Tables/lmdidtest.Rds'))
 
 ### erstellen der Regressions Tabellen ####
 
-lmdid_daytodayskills_test <- screenreg(
-  
+### DaytoDayskills ####
+
+screenreg(
+  list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2),
+  override.se = list(RSE_1, RSE_2),
+  override.pvalues = list(RpValue_1, RpValue_2),
+  #groups = list('first' = 3:67, 'second' = 68:75),
+  custom.model.names = c('Model 1', 'Model 2'),
+  #custom.coef.names = c('Intercept', 'treatEF', 'totalCost', 'weeklyCooks'),
+  stars = c(0.01, 0.05, 0.1),
+  omit.coef = 'id|year',
+  digits = 3,
+  #dann noch die Observations manuell hinzufügen, dann kann ich den Namen zu observations ändern
+  custom.gof.rows = list('ID FE' = c('yes', 'yes'), 'Year FE' = c('yes', 'yes')),
+  #reorder.gof = c(3, 1, 2, 4, 5, 6, 7),
+  include.adjrs = FALSE
 )
 
 
+### selfworth ####

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R
Update

@@ -16,43 +16,34 @@ library(Matrix)
 library(texreg)
 
 
+#### Vorarbeiten ####
+
+# Plausibilisierung für den Treatment-Dummy
+dfcEF_check <- dfcEF
+
+dfcEF_check <- dfcEF_check %>% 
+  dplyr :: select(id, treatEF)
+
+# Ändern des Variablen-Name von 'subsidy' zu 'funding', um den Regression-Table zu erstellen
+dfcEF <- dfcEF %>% 
+  dplyr::rename(funding = 'subsidy')
+
+# Teilen der in Euro angegebenen Kontroll-Variablen 'subsidy' und 'totalCost' durch 1000, damit die 
+# Regressionskoeffizienten leichter interpretiert werden können
+dfcEF$funding <- (dfcEF$funding/1000)
+dfcEF$totalCost <- (dfcEF$totalCost/1000)
+
+# Änderung des Datentyps
+dfcEF$id <- as.factor(dfcEF$id)
+dfcEF$year <- as.factor(dfcEF$year)
+dfcEF$treatEF <- as.numeric(dfcEF$treatEF)
+
+
+#### Treatment Variable: Variante 2 #### ____________________________________________________________
+
 #### Everyday expertise ####
 
-
-#### Erste Definition der Treatment Variable ####
-
-# Verwendeter Datensatz: dfcEF2
-
 # DiD-Estimation mit id fixed effects and year fixed effects
-
-lmdid_dayToDaySkills_1 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year)
-
-summary(lmdid_dayToDaySkills_1)
-summary(lmdid_dayToDaySkills_1, robust = TRUE)
-
-RSE_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Robust s.e"]
-RpValue_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Pr(>|t|)"]
-
-
-# Mit organization-specific Kontrollvariablen
-
-lmdid_dayToDaySkills_2 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year
-                                + dfcEF2$subsidy + dfcEF2$totalCost + dfcEF2$weeklyCooks_scaled)
[…]

### 2020-02-26 paper.tex

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 18:39:45 2020
+% Wed Feb 26 19:01:58 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 18:39:51
+% Date and time: Mi, Feb 26, 2020 - 19:02:05
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 18:39:52
+% Date and time: Mi, Feb 26, 2020 - 19:02:06
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 18:39:52 2020
+% Wed Feb 26 19:02:06 2020
 \begin{table}[ht]

### 2020-02-26 paper.tex
recoded factor scales from numbers to strings

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 19:01:58 2020
+% Wed Feb 26 22:15:10 2020
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/Grant_Trend-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/GrantTrend-1}
 
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/Health_time_plots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/HealthTimePlots-1}
 
@@
 
-In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
 These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/Equality_time_plots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/EqualityTimePlots-1}
 
@@
 Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
-The estimated coefficents are very similar when we use the original dataset and the one with imputed values.
+The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
 In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
@@
 those organizations that give out very many menus or very few menus,
-the estimated coefficent decreases by about one order of magnitude.
+the estimated coefficient decreases by about one order of magnitude.
 Still, spending not much more than three EUR more goes hand in hand with one extra meal.
@@
 In the remit of the Trips program, the picture looks much different.
+In the case of the original data set and the data set with imputed variables, an increase in the trips subsidy by 5000 EUR is needed for an extra trip.
+The coefficent of 0.0002 is statistically significant at the 5\% level.
+As soon as outliers are excluded, the coefficent changes to 0.0003, which is highly statistically significant.
+This means that, according to this model, at least 3000 EUR are needed for an additional trip.
+In sum, there seems to be no clear connection between how much money CHILDREN gives to an organization and the number of trips it organizes.
 
@@
 
-\subsection{Variables of interest: Health variables}
-
-In the next section, we want to explore the influence of the DGE Criterion on relevant health outcomes.
-
-\begin{figure}
-  \caption{Health Outcomes versus Healthy Meals}
-  \label{Health_Plots}
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsPercentageplots-1}
-
-}
-
-\end{knitrout}
-\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
-It is based on the criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-According to information from CHILDREN, they ask the organizations to send them their menus.
-An ecotrophologist collaborating with CHILDREN assesed the menus.
-In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the degree to which beneficiaries: are healthier (lessIll\_ordered), have a growing appreciation for a healthier diet (dietaryKnowledge\_ordered), and have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the index for a healthy diet.
-The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
-\end{figure}
-
-In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.
-
-\begin{table}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & OLS & WLS & OLS Impute & WLS Impute \\
-\hline
-(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
-\hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
-Num. obs.           & 121          & 120         & 177          & 177          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Less Ill}
-\label{HealthRegressions-LessIll}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & OLS & WLS & OLS Impute & WLS Impute \\
-\hline
-(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
-                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
-DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
-                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
-\hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
-Num. obs.           & 214      & 212      & 275        & 275      \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Dietary Knowledge}
-\label{HealthRegressions-DietaryKnowledge}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & OLS & WLS & OLS Impute & WLS Impute \\
-\hline
-(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
-                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
-DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
-                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
-\hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
-Num. obs.           & 213          & 211      & 274          & 274        \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Appreciate Healthy}
-\label{HealthRegressions-AppreciateHealthy}
-\end{center}
-\end{table}
-
-\subsection{Variables of interest: selfworth and everyday expertise as proxies for equality of opportunities}
+\subsection{Variables of interest: selfworth and everyday expertise}
+
+In their surveys, CHILDREN asks about two variables in both programs.
+These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise.
+This feature could potentially allow us to compare the two programs regarding their realtive effectiveness.
+Like always, we standardize the two outcome variables.
+As before, we can only make associational claims.
+We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes.
+In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.
+
+Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.
 
@@
 \label{DayToDaySkillsRegressions}
+\end{center}
+\end{table}
+
+\subsection{Variables of interest: Health variables}
+
+Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could.
+In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus.
+An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were.
+This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+
+In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
+These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
+
+Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.
+
+We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
+If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.
+
+\begin{figure}
+  \caption{Health Outcomes versus Healthy Meals}
+  \label{Health_Plots}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/HealthRegressionsPercentageplots-1}
+
+}
+
+\end{knitrout}
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+According to information from CHILDREN, they ask the organizations to send them a sample of their menus.
+An ecotrophologist collaborating with CHILDREN assessed the menus.
+In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+\end{figure}
+
+In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
+Num. obs.           & 121          & 120         & 177          & 177          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Less Ill}
+\label{HealthRegressions-LessIll}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
+Num. obs.           & 214      & 212      & 275        & 275      \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Dietary Knowledge}
+\label{HealthRegressions-DietaryKnowledge}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
+Num. obs.           & 213          & 211      & 274          & 274        \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Appreciate Healthy}
+\label{HealthRegressions-AppreciateHealthy}
 \end{center}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 19:02:05
+% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mi, Feb 26, 2020 - 19:02:06
+% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 19:02:06 2020
+% Wed Feb 26 22:15:20 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
 \subsection{A3: OLS Regressions}
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}\end{kframe}
+% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% #expanded model less ill 
+% 
+% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
+% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
+% @
 

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R
texreg tables

@@ -198,20 +198,36 @@ RpValue_selfworth_2 = coef(summary(lmdid_selfworth_2, robust = TRUE))[, "Pr(>|t|
 ### DaytoDayskills ####
 
 screenreg(
-  list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2),
-  override.se = list(RSE_1, RSE_2),
-  override.pvalues = list(RpValue_1, RpValue_2),
+  list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2, lmdid_dayToDaySkills_3, lmdid_dayToDaySkills_4),
+  override.se = list(RSE_1, RSE_2, RSE_3, RSE_4),
+  override.pvalues = list(RpValue_1, RpValue_2, RpValue_3, RpValue_4),
   #groups = list('first' = 3:67, 'second' = 68:75),
-  custom.model.names = c('Model 1', 'Model 2'),
+  custom.model.names = c('Model 1', 'Model 2', 'Model 3', 'Model 4'),
   #custom.coef.names = c('Intercept', 'treatEF', 'totalCost', 'weeklyCooks'),
   stars = c(0.01, 0.05, 0.1),
   omit.coef = 'id|year',
   digits = 3,
   #dann noch die Observations manuell hinzufügen, dann kann ich den Namen zu observations ändern
-  custom.gof.rows = list('ID FE' = c('yes', 'yes'), 'Year FE' = c('yes', 'yes')),
+  custom.gof.rows = list('ID FE' = c('yes', 'yes', 'yes', 'yes'), 'Year FE' = c('yes', 'yes', 'yes', 'yes')),
   #reorder.gof = c(3, 1, 2, 4, 5, 6, 7),
   include.adjrs = FALSE
 )
 
 
 ### selfworth ####
+
+screenreg(
+  list(lmdid_selfworth_1, lmdid_selfworth_2, lmdid_selfworth_3, lmdid_selfworth_4),
+  override.se = list(RSE_selfworth_1, RSE_selfworth_2, RSE_selfworth_3, RSE_selfworth_4),
+  override.pvalues = list(RpValue_selfworth_1, RpValue_selfworth_2, RpValue_selfworth_3, RpValue_selfworth_4),
+  #groups = list('first' = 3:67, 'second' = 68:75),
+  custom.model.names = c('Model 1', 'Model 2', 'Model 3', 'Model 4'),
[…]

### 2020-02-26 paper.Rnw

--- 2020-02-26 paper.Rnw
@@
 texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
+
 @

### 2020-02-26 paper.tex
xx

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:10 2020
+% Wed Feb 26 23:16:47 2020
 \begin{table}[ht]
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/GrantTrend-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Grant_Trend-1}
 
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/HealthTimePlots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Health_time_plots-1}
 
@@
 
-In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
 These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/EqualityTimePlots-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/Equality_time_plots-1}
 
@@
 Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
-The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
+The estimated coefficents are very similar when we use the original dataset and the one with imputed values.
 In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
@@
 those organizations that give out very many menus or very few menus,
-the estimated coefficient decreases by about one order of magnitude.
+the estimated coefficent decreases by about one order of magnitude.
 Still, spending not much more than three EUR more goes hand in hand with one extra meal.
@@
 
-\begin{table}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
-\hline
-(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
-                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
-                               & $(0.00)$ &          & $(0.00)$ &          \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
-                               &          & $(0.00)$ &          & $(0.00)$ \\
-\hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
-Num. obs.                      & 426      & 177      & 429      & 181      \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: dayToDaySkills}
-\label{DayToDaySkillsRegressions}
-\end{center}
-\end{table}
+\begin{kframe}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error: <text>:6:1: unerwartete Eingabe\\\#\# 5: \\\#\# 6: <<\\\#\#\ \ \ \ \textasciicircum{}}}\end{kframe}
 
@@
 We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.
+By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi, Feb 26, 2020 - 23:16:52
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-\subsection{A1: Cumulative Odds Regression}
-
-As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...
-
-Use from zwichenpräsentation
+\subsection{A1: Expanded Health Regression}
+
+In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
+
+% #normal weights selfworth& subsidiy
+% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% 
+% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% @
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)               & $-1.08^{***}$ & $-0.99^{**}$ & $0.02$      & $-0.08$    \\
+                          & $(0.24)$      & $(0.30)$     & $(0.15)$    & $(0.20)$   \\
+DGECriteriaNoScaled       & $0.34^{***}$  & $0.36^{***}$ & $0.19^{**}$ & $0.27$     \\
+                          & $(0.08)$      & $(0.06)$     & $(0.07)$    & $(0.14)$   \\
+regionalProducts\_scaled  & $0.02$        & $-0.03$      & $0.11$      & $0.02$     \\
+                          & $(0.08)$      & $(0.11)$     & $(0.07)$    & $(0.11)$   \\
+yearsSupportSince         & $0.02$        & $-0.03$      & $-0.01$     & $0.05^{*}$ \\
+                          & $(0.03)$      & $(0.04)$     & $(0.02)$    & $(0.02)$   \\
+realSubsidyPerBeneficiary & $-0.00$       & $0.00$       &             & $-0.00$    \\
+                          & $(0.00)$      & $(0.00)$     &             & $(0.00)$   \\
+stateBayern               & $0.96^{**}$   & $1.88^{***}$ &             &            \\
+                          & $(0.33)$      & $(0.49)$     &             &            \\
+stateBerlin               & $1.09^{**}$   & $1.34^{***}$ &             &            \\
+                          & $(0.37)$      & $(0.37)$     &             &            \\
+stateBrandenburg          & $2.21^{***}$  & $2.46^{***}$ &             &            \\
+                          & $(0.43)$      & $(0.40)$     &             &            \\
+stateBremen               & $1.00$        & $1.03$       &             &            \\
+                          & $(0.58)$      & $(0.59)$     &             &            \\
+stateHamburg              & $0.95$        & $1.96^{***}$ &             &            \\
+                          & $(0.67)$      & $(0.40)$     &             &            \\
+stateHessen               & $0.87^{***}$  & $1.16^{***}$ &             &            \\
+                          & $(0.23)$      & $(0.31)$     &             &            \\
+stateMV                   & $0.09$        & $0.14$       &             &            \\
+                          & $(0.21)$      & $(0.26)$     &             &            \\
+stateNiedersachsen        & $2.48^{***}$  & $2.30^{***}$ &             &            \\
+                          & $(0.40)$      & $(0.43)$     &             &            \\
+stateNRW                  & $0.68^{*}$    & $1.00^{**}$  &             &            \\
+                          & $(0.27)$      & $(0.33)$     &             &            \\
+stateSaarland             & $1.50^{***}$  & $1.75^{***}$ &             &            \\
+                          & $(0.32)$      & $(0.25)$     &             &            \\
+stateSachsen              & $1.34^{***}$  & $1.23^{***}$ &             &            \\
+                          & $(0.27)$      & $(0.27)$     &             &            \\
+stateSchleswig-Holstein   & $1.33^{***}$  & $1.63^{***}$ &             &            \\
+                          & $(0.37)$      & $(0.42)$     &             &            \\
+stateThüringen            & $0.99$        & $1.29^{*}$   &             &            \\
+                          & $(0.59)$      & $(0.55)$     &             &            \\
+realSubsidy               &               &              & $0.00^{**}$ &            \\
+                          &               &              & $(0.00)$    &            \\
+\hline
+R$^2$                     & 0.51          & 0.73         & 0.12        & 0.22       \\
+Adj. R$^2$                & 0.39          & 0.66         & 0.10        & 0.20       \\
+Num. obs.                 & 88            & 88           & 175         & 175        \\
+RMSE                      & 0.73          & 5.62         & 0.92        & 7.77       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Less ill expanded model}
+\label{expandLessIll}
+\end{center}
+\end{table}
+
+\subsection{A2: Cumulative Odds Regression}
+
+As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit from the VGAM package.
+Equation \ref{PropoddsModel} describes the model setup:
 
 \begin{equation}
-\label{ModelProdu}
-\ln y_{it} = \frac{}{}  \sum
+\label{PropoddsModel}
+  P(Y_i \leq \ r) = \frac{exp(y_0_r + x_i^Ty)}{1+exp(y_0_r + x_i^Ty)}    
 \end{equation}
 
+To demonstrate the results of this method, we show in the tables \ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds} the regressions of the health related variables on the healthy meals criterion and in \ref{selfworthOdds} and \ref{dayToDayOdds} the regressions of the real meals subsidy on selfworth and everyday expertise.
+
+As an example of interpreting such models, we consider the model of table \ref{lessIllOdds}: An increase of the healthy meals criterion by 1 is associated with an increase in chances, that a proportion of a maximum of r beneficiaries is healthier in relation to that a proportion of more than r beneficiaries are healthier, by the factor of exp(-0.29127) = 0.75.
+
+A summary of the remaining models:
+
+\begin{itemize}
+  \item{Dietary Knowledge: exp(-0.089) = 0.91}
+  \item{Appreciate Healthy: exp(-0199) = 0.82}
+  \item{Selfworth: exp(-0.00001) = 1}
+  \item{Everyday Expertise: (-0.00003) = 1} 
+\end{itemize}
+
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi, Feb 26, 2020 - 23:16:52
 % Requires LaTeX packages: dcolumn 
@@
   \caption{Propodss Regression Results: Less Ill} 
-  \label{} 
+  \label{lessIllOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi, Feb 26, 2020 - 23:16:53
 % Requires LaTeX packages: dcolumn 
@@
   \caption{Propodss Regression Results: Dietary Knowledge} 
-  \label{} 
+  \label{dietaryOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
   \caption{Propodss Regression Results: Appreciate Healthy} 
-  \label{} 
+  \label{appreciateOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi, Feb 26, 2020 - 23:16:53
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
-  \label{} 
+  \caption{Propodss Regression Results: Selfworth} 
+  \label{selfworthOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi, Feb 26, 2020 - 23:16:53
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
-  \label{} 
+  \caption{Propodss Regression Results: Everyday expertise} 
+  \label{dayToDayOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 
-\subsection{A2: Partition}
+\subsection{A3: Partition}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:20 2020
+% Wed Feb 26 23:16:53 2020
 \begin{table}[ht]
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
-\subsection{A3: OLS Regressions}
-
-#normal weights selfworth& subsidiy
-
-% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-% #expanded model less ill 
-% 
-% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
-% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
-% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
-% @
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
 

### 2020-02-26 paper.Rnw
xxx

@@
 
-To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2011 to 2018.
+To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018.
 In each year they send a survey to the organizations with several questions about the previous year.
@@
 The number of variables varies over time as well.
-Included are numbers like the average eaters per meal or the amount of money they provide to the organizations but also general questions.
+Included are numbers such as the average eaters per meal or the amount of money they provide to the organizations but also general questions.
 For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
 This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
-If an organization do not answer a question, this is documented as a “99”.
+If an organization does not answer a question, this is documented as a “99”.
 We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
 The surveyed variables change over the years, but some of them are included every year.
-However, we did several steps to get a full dataset we could work with.
+However, we did several steps to get a full dataset we could work with (we could use for our empirical analysis??).
 The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete.

### 2020-02-26 paper.tex
xxx

--- 2020-02-26 paper.tex
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:10 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 23:49:45 2020
 \begin{table}[ht]
@@
 
+\usepackage{graphicx}
 \usepackage{booktabs}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c }
+\begin{tabular}{l c c c}
 \toprule
@@
 \midrule
-R$^2$       & 0.43            & 0.13            & 0.45             \\
-Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
-Num. obs.   & 329             & 250             & 440              \\
-RMSE        & 39992.79        & 3629.72         & 39601.41         \\
+R$^2$       & $0.43$          & $0.13$          & $0.45$           \\
+Adj. R$^2$  & $0.43$          & $0.12$          & $0.45$           \\
+Num. obs.   & $329$           & $250$           & $440$            \\
+RMSE        & $39992.79$      & $3629.72$       & $39601.41$       \\
 \bottomrule
@@
 sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+aliquyam. \\ $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$            & 0.0474         & 0.0880         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0844         & 0.0476         \\
-Num. obs.        & 322            & 257            & 334            \\
-RMSE             & 2.9565         & 1.6981         & 2.9310         \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$            & $0.0474$       & $0.0880$       & $0.0504$       \\
+Adj. R$^2$       & $0.0444$       & $0.0844$       & $0.0476$       \\
+Num. obs.        & $322$          & $257$          & $334$          \\
+RMSE             & $2.9565$       & $1.6981$       & $2.9310$       \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi., Feb 26, 2020 - 23:49:53
 % Requires LaTeX packages: dcolumn rotating 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Mi., Feb 26, 2020 - 23:49:53
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:20 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 23:49:53 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:20 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Wed Feb 26 23:49:53 2020
 \begin{table}[ht]

### 2020-02-26 paper.Rnw
new function weightOuliers
moved all library calls from Gather and other data files to MakeGather

continued MakeAnalysis

finished first factor analysis

--- 2020-02-26 paper.Rnw
@@
 In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.
-
+The four variables are recorded for each year in which the program was operative.
 Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.
@@
 \subsection{Factor Analysis}
+
+We use imputed data set.
+
+we use the orthogonal rotation technique Varimax, which is recommended in Price (2017, p.
+307) when the goal of analysis is to "minimize complexity of factors by maximizing variance of loadings on each factor"
+We estimate factor scores with the Bartlett method, which is similar to a Maximum Likekelihood estimation, and presented as the most convential one in Eid and Schmidt (2010, p. 291)
+We use maximum likelihood as factoring method
 

### 2020-02-26 ANALYSIS/DATA/Data 2015.R

@@ -2,12 +2,6 @@
 
 # 1. Herunterladen der Daten ----------------------------------------------
 
-#rm(list = ls())
-
-library(readxl)
-library(dplyr)
-library(tidyverse)
-
 ### Daten 2016
 
 Wirkungsdaten_2015unbereinigt <- read_excel("./ANALYSIS/DATA/CHILDREN Wirkungsdaten_VERTRAULICH_final.xlsx",

### 2020-02-26 ANALYSIS/DATA/MakeReal.R

@@ -1,5 +1,3 @@
-library(dplyr)
-
 #calculating real values as well as differences in subsidy/request and the amount of years in programme
 
 mergedData <- mergedData %>% 

### 2020-02-26 ANALYSIS/DATA/specialVariables.R

@@ -66,4 +66,5 @@ availableVariables <- function(dataSet, variableName) {
   return(names(comparisonAvailableYears))
 }
 
-alwaysRecordedVariables <- availableVariables(mergedData, "subsidy")
+alwaysRecordedVariablesMeals <- availableVariables(mergedData, "subsidy")
+alwaysRecordedVariablesTrips <- availableVariables(mergedData, 'realSubsidy')

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R
commit pull

@@ -77,7 +77,7 @@ RpValue_selfworth_3 = coef(summary(lmdid_selfworth_3, robust = TRUE))[, "Pr(>|t|
 
 # Mit organization-specific Kontrollvariablen
 lmdid_selfworth_4 <-  felm(dfcEF$selfworth_scaled ~ dfcEF$treatEF + dfcEF$id + dfcEF$year
-                           + dfcEF$funding + dfcEF$totalCost + dfc$weeklyCooks_scaled)
+                           + dfcEF$funding + dfcEF$totalCost + dfcEF$weeklyCooks_scaled)
 
 summary(lmdid_selfworth_4)
 summary(lmdid_selfworth_4, robust = TRUE)
@@ -178,14 +178,6 @@ RpValue_selfworth_2 = coef(summary(lmdid_selfworth_2, robust = TRUE))[, "Pr(>|t|
 
 
 
-
-
-
-
-
-
-
-
 # screenreg(list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2),
 #                      override.se = list(RSE_1, RSE_2), override.pvalues = list(RpValue_1, RpValue_2),
 #      caption = "linear regression",
@@ -197,21 +189,92 @@ RpValue_selfworth_2 = coef(summary(lmdid_selfworth_2, robust = TRUE))[, "Pr(>|t|
 
 ### DaytoDayskills ####
 
-screenreg(
-  list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2),
-  override.se = list(RSE_1, RSE_2),
-  override.pvalues = list(RpValue_1, RpValue_2),
+test1 <- texreg(
+  list(lmdid_dayToDaySkills_1, lmdid_dayToDaySkills_2, lmdid_dayToDaySkills_3, lmdid_dayToDaySkills_4),
+  override.se = list(RSE_1, RSE_2, RSE_3, RSE_4),
+  override.pvalues = list(RpValue_1, RpValue_2, RpValue_3, RpValue_4),
   #groups = list('first' = 3:67, 'second' = 68:75),
-  custom.model.names = c('Model 1', 'Model 2'),
-  #custom.coef.names = c('Intercept', 'treatEF', 'totalCost', 'weeklyCooks'),
+  custom.model.names = c('(1)', '(2)', '(3)', '(4)'),
+  custom.coef.names = c('treatEF','subsidy', 'totalCost', 'weeklyCooks'),
[…]

### 2020-02-26 ANALYSIS/Health Regressions.R

@@ -34,7 +34,7 @@ saveRDS(lessIll_DGE_scaled_weighted.lm,"./ANALYSIS/Tables/lessIll_DGE_scaled_wei
 # 
 # saveRDS(Expand_LessIll.lm,"./ANALYSIS/Tables/Expand_LessIll.lm.Rds")
 
-Expand_LessIll_scaled.lm = lm_robust(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidyPerBeneficiary + state, data = mergedData)%>%
+Expand_LessIll_scaled.lm = lm_robust(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidyPerBeneficiary + state,  data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(Expand_LessIll_scaled.lm) #standardized
 
@@ -123,7 +123,7 @@ saveRDS(lessIll_DGE_IM_scaled_weighted.lm,"./ANALYSIS/Tables/lessIll_DGE_IM_scal
 # 
 # saveRDS(Expand_LessIll_IM.lm,"./ANALYSIS/Tables/Expand_LessIll_IM.lm.Rds")
 # 
-Expand_LessIll_IM_scaled.lm = lm_robust(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidy, data = mergedDataImputeInterpolation)%>%
+Expand_LessIll_IM_scaled.lm = lm_robust(lessIll_scaled ~ DGECriteriaNoScaled + regionalProducts_scaled + yearsSupportSince + realSubsidyPerBeneficiary, data = mergedDataImputeInterpolation)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(Expand_LessIll_IM_scaled.lm) #standardized
 

### 2020-02-26 ANALYSIS/DATA/MakeGather.R
commit pull

@@ -1,5 +1,6 @@
 # read packages
 
+
 library(texreg)
 library(readxl)
 library(tidyverse)
@@ -10,7 +11,10 @@ library(lattice)
 library(survival)
 library(Formula)
 library(tidyimpute)
-
+library(tidyselect)
+library(imputeMissings)
+library(zoo)
+library(rlang)
 
 # Gather and cleanup raw data files
 
@@ -32,7 +36,6 @@ source(encoding = "UTF8", "./ANALYSIS/DATA/DataPriceIndices.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Merge.R")
 
-
 source(encoding = "UTF8", "./ANALYSIS/DATA/MakeReal.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Impute.R")
@@ -43,9 +46,11 @@ source(encoding = "UTF8", "./ANALYSIS/DATA/Exclude Outliers Regression.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/categoricalData.R")
 
-# specialVariables has to be after cateogricalData
+# specialVariables has to be after categoricalData
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/specialVariables.R")
+
+
 
 # source(encoding = "UTF8", "./ANALYSIS/DATA/Standardized Coefficents.R")
 

### 2020-02-26 ANALYSIS/DATA/categoricalData.R

@@ -5,10 +5,7 @@
 # How does map from package purrr work: https://r4ds.had.co.nz/iteration.html
 # How to mutate columns selectively with automatic new names: https://dplyr.tidyverse.org/reference/mutate_all.html
 
-# load packages
-library(purrr)
-library(tidyselect)
-library(stringr)
+
 
 categories <- c(NA, 0, 1, 2, 3, 4, 1/2, 3/2, 5/2, 7/2, 1/3, 2/3, 4/3, 5/3, 7/3, 8/3, 10/3, 11/3, 1/4, 3/4, 5/4, 7/4, 9/4, 11/4, 13/4, 15/4, 7/6, 8/6, 10/6, 11/6)
 
@@ -23,6 +20,16 @@ weight <- function(expr) {
     }
   else {
     return(mergedData$eatersPerMealNo*0.25*expr)
+  }
+}
+
+weightOutliers <- function(expr) {
+  name <- quo_name(enquo(expr))
+  if(stringr::str_detect(name, "trips")) {
+    return(mealsNoOutliers$tripsKidsNo*0.25*expr)
+  }
+  else {
+    return(mealsNoOutliers$eatersPerMealNo*0.25*expr)
   }
 }
 
@@ -46,6 +53,10 @@ mergedData <- mergedData %>%
 mergedData <- mergedData %>% 
   mutate(DGECriteriaNoScaled = scale_this(DGECriteriaNo), DGECriteriaNoWeighted = weight(mergedData$DGECriteriaNo), DGECriteriaNoOrdered = as.ordered(DGECriteriaNo))
 
+mergedData <- mergedData %>% 
+  mutate_at(vars(contains('ordered')), funs(recode(., '0' = 'none', '1'= 'few', '2'= 'some', '3' = 'most', '4' = 'all')))
+
+
 # do the same for mergedDataImputeInterpolation
 
 mergedDataImputeInterpolation <- mergedDataImputeInterpolation %>% 
@@ -59,18 +70,18 @@ mergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
 # do the same for mealsNoOutliers
 
 mealsNoOutliers <- mealsNoOutliers %>% 
-  mutate_if(pretendsToBeMetric, list(scaled = scale_this, ordered = as.ordered, weighted = weight))
[…]

### 2020-02-26 ANALYSIS/DATA/did_estimation_final.R

@@ -16,43 +16,34 @@ library(Matrix)
 library(texreg)
 
 
+#### Vorarbeiten ####
+
+# Plausibilisierung für den Treatment-Dummy
+dfcEF_check <- dfcEF
+
+dfcEF_check <- dfcEF_check %>% 
+  dplyr :: select(id, treatEF)
+
+# Ändern des Variablen-Name von 'subsidy' zu 'funding', um den Regression-Table zu erstellen
+dfcEF <- dfcEF %>% 
+  dplyr::rename(funding = 'subsidy')
+
+# Teilen der in Euro angegebenen Kontroll-Variablen 'subsidy' und 'totalCost' durch 1000, damit die 
+# Regressionskoeffizienten leichter interpretiert werden können
+dfcEF$funding <- (dfcEF$funding/1000)
+dfcEF$totalCost <- (dfcEF$totalCost/1000)
+
+# Änderung des Datentyps
+dfcEF$id <- as.factor(dfcEF$id)
+dfcEF$year <- as.factor(dfcEF$year)
+dfcEF$treatEF <- as.numeric(dfcEF$treatEF)
+
+
+#### Treatment Variable: Variante 2 #### ____________________________________________________________
+
 #### Everyday expertise ####
 
-
-#### Erste Definition der Treatment Variable ####
-
-# Verwendeter Datensatz: dfcEF2
-
 # DiD-Estimation mit id fixed effects and year fixed effects
-
-lmdid_dayToDaySkills_1 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year)
-
-summary(lmdid_dayToDaySkills_1)
-summary(lmdid_dayToDaySkills_1, robust = TRUE)
-
-RSE_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Robust s.e"]
-RpValue_1 = coef(summary(lmdid_dayToDaySkills_1, robust = TRUE))[, "Pr(>|t|)"]
-
-
-# Mit organization-specific Kontrollvariablen
-
-lmdid_dayToDaySkills_2 <-  felm(dfcEF2$dayToDaySkills_scaled ~ dfcEF2$treatEF + dfcEF2$id + dfcEF2$year
-                                + dfcEF2$subsidy + dfcEF2$totalCost + dfcEF2$weeklyCooks_scaled)
-
-summary(lmdid_dayToDaySkills_2)
[…]

### 2020-02-27 paper.Rnw
xxx

--- 2020-02-26 paper.Rnw
@@
 % If there is no error while knitting from Rnw to tex, but an error while compiling from tex to pdf, have a look at the pdf file. It might still have worked.
+
+% instead of Compile PDF, go into Terminal and enter 
+% Rscript -e "library(knitr); knit('paper.Rnw')"
+% latexmk -pdf paper
 
@@
 % https://kbroman.org/knitr_knutshell/pages/latex.html
-% Command line
-% R -e 'library(knitr);knit("knitr_example.Rnw")'
 
@@
 \usepackage{booktabs}
-\usepackage[hidelinks]{hyperref}
+% \usepackage{bookmark}
 \usepackage{rotating}
@@
 \usepackage{mathtools}
-\usepackage[onehalfspacing]{setspace}
+% \usepackage[onehalfspacing]{setspace}
 \usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+\usepackage[hidelinks]{hyperref}
 
@@
 
+Citing\\
+
+If you want to cite \textcite{Millenstein.2020} inline, use this.
+If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
+If you want to cite \citeauthor{Millenstein.2020} only as authors, use this.
+
 Equation with double index\\
@@
 
-Figure\\
-
-\begin{figure}
-  \caption{Dispersion in productivity levels}
-  \label{LineDisp}
-
-<<echo=FALSE>>=
-figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-print(figureLineDisp)
-@
-
-\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
+% Figure\\
+% 
+% \begin{figure}
+%   \caption{Dispersion in productivity levels}
+%   \label{LineDisp}
+% 
+% <<echo=FALSE>>=
+% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
+% print(figureLineDisp)
+% @
+% 
+% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
 A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
@@
 Compare Kehrig (2015), Figure 1.}
-\end{figure}
+% \end{figure}
 
-Figure \ref{LineDisp}
+% Figure \ref{LineDisp}
 
@@
 #  
-texreg(list(mealsNo_sub.lm, tripsNo_sub.lm))
+texreg(list(mealsNo_sub.lm, tripsNo_sub.lm), label = "mealsTripsSubsidyRegressions")
 @
@@
 
+\subsection{Previous research}
+
+The previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
+Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance.
+Moreover, Deckers et.
+al.
+(2015) found by experiments in Germany, that children of higher educated parents are signficantly more patient.
+Children from parents with lower income and lower educational attainment typically have a lower weight at birth and are born in a later week of gestation, which are indicators for good initial conditions (Deckers et.
+al.
+2015, Case et.
+al.
+2002).
+Children that grow up in families with a low socio-economic status are often less mobile and more likely to keep to themselves.
+This could have a negative influence on their character development.
+For example, Chetty et.
+al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the result of Deckers et.
+al.
+(2020) provides causal evidence on the effect of social environment on prosocial attitudes.
+Being supported by a mentor could have a significant and persistant increase of elementary school children´s prosociality, in response to prosocial role models and intense social interactions.
+As investigated by Heckmann et.
+al.
+(2010) for a preschool education program in the US, investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+
 \section{Data}
@@
 
-<<echo=FALSE>>=
+<<DaytodayskillsSelfworth, echo=FALSE>>=
 figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
@@
 
+# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+# 
+# # first, read in all Rds objects that you need
+# 
+# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
+#  
+# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+# 
+# fundamental_dynamics <- xtable(fundamental_dynamics,
+#                                digits = c(0, 0, 1, 1, 0, 0),
+#           caption = "Summary Statistics",
+#           align = "lmmmmm", 
+#           label = "fundamentalDynamics"
+#           )
+# print(fundamental_dynamics, include.rownames = FALSE)
+# @
+
 <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
-fundamental_dynamics <- xtable(fundamental_dynamics,
-                               digits = c(0, 0, 1, 1, 0, 0),
+fundamental_dynamics <- stargazer(fundamental_dynamics,
+                                  summary = FALSE,
+                               # digits = c(0, 0, 1, 1, 0, 0),
           caption = "Summary Statistics",
-          align = "lmmmmm", 
+          # align = "lmmmmm", 
           label = "fundamentalDynamics"
@@
 Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
-The x-axis plots the index for a healthy diet.
+The x-axis displays the index for a healthy diet.
 The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.
+The possible values are: all, most, some, few and none.
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as most.
+The highest amount of healthy criteria to be fulfilled is x.
 
-We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.
+All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria.
+The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constituted a healthy diet.
+It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
+However, for the variable less ill, the least data is availabe.
+Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables.
+This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.
 
@@
 
-In the following equation we use standardized variables in a standard OLS approach. The results are as well compared to the output with the imputed dataset, where we also use scaled coefficents.
+We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
+By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
+
+In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
+An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations.
+Regressing with the imputed dataset, results decrease by about 0.1.
+Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
 
@@
 
-<<echo=FALSE, results='asis', message=FALSE>>=
+<<selfworth_tripsProgram, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-\subsection{A1: Cumulative Odds Regression}
+\subsection{A1: Expanded Health Regression}
 
-As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...
+In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
 
-Use from zwichenpräsentation
+% #normal weights selfworth& subsidiy
+% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% 
+% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% @
+
+<<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+#expanded model less ill
+
+lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
+elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.lm.Rds")
+elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.lm.Rds")
+
+texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'expandLessIll')
+@
+
+\subsection{A2: Cumulative Odds Regression}
+
+As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit from the VGAM package.
+Equation \ref{PropoddsModel} describes the model setup:
 
 \begin{equation}
-\label{ModelProdu}
-\ln y_{it} = \frac{}{}  \sum
+\label{PropoddsModel}
+  P(Y_i \leq \ r) = \frac{exp(y_0_r + x_i^Ty)}{1+exp(y_0_r + x_i^Ty)}    
 \end{equation}
 
-<<echo=FALSE, results='asis', message=FALSE>>=
+To demonstrate the results of this method, we show in the tables \ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds} the regressions of the health related variables on the healthy meals criterion and in the tables \ref{selfworthOdds} and \ref{dayToDayOdds} the regressions of the real meals subsidy on selfworth and everyday expertise.
+
+As an example of interpreting such models, we consider the model of table \ref{lessIllOdds}: An increase of the healthy meals criterion by 1 is associated with an increase in chances, that a proportion of a maximum of r beneficiaries is healthier in relation to that a proportion of more than r beneficiaries are healthier, by the factor of exp(-0.29127) = 0.75.
+
+A summary of the remaining models:
+
+\begin{itemize}
+  \item{Dietary Knowledge: exp(-0.089) = 0.91}
+  \item{Appreciate Healthy: exp(-0199) = 0.82}
+  \item{Selfworth: exp(-0.00001) = 1}
+  \item{Everyday Expertise: (-0.00003) = 1} 
+\end{itemize}
+
+<<lessIllOdds, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", align = TRUE)
+stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", align = TRUE, label = "lessIllOdds")
 
 @
-<<echo=FALSE, results='asis', message=FALSE>>=
+
+<<dietaryOdds, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Dietary Knowledge", align = TRUE)
+stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Dietary Knowledge", align = TRUE, label = "dietaryOdds")
 @
-<<echo=FALSE, results='asis', message=FALSE>>=
+
+<<appreciateOdds, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Appreciate Healthy", align = TRUE)
+stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Appreciate Healthy", align = TRUE, label = "appreciateOdds")
 @
 
-<<echo=FALSE, results='asis', message=FALSE>>=
+<<selfworthOdds, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Equality of opportunities, selfworth", align = TRUE)
+stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Selfworth", align = TRUE, label = "selfworthOdds")
 @
 
-<<echo=FALSE, results='asis', message=FALSE>>=
+<<dayToDayOdds, echo=FALSE, results='asis', message=FALSE>>=
 
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Equality of opportunities, everyday expertise", align = TRUE)
+stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Everyday expertise", align = TRUE, label = "dayToDayOdds")
 @
 
-\subsection{A2: Partition}
+\subsection{A3: Partition}
 
-In addition to the factor analysis described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+This method was developped by Millenstein et.
+al in the context of genome analysis.
 
-QUOTES FROM PAPER, describe method
+According to the researchers, potential benefits of reducing dimensionality are reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{} (p.677).
+
+The partition approach partitions data into subsets of related features.
+It then  summarizes each subset into one new feature.
+By that, it defines a surjective mapping \cite{} (p.676).
+A function g is implemented using the arithmetic mean.
+In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
+What is as well different is the information loss constraint.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced.\cite{}(p.677)
 
 In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
-It might be meaningful to decide to use only one of the variables a reduced variable consists of or a summarizing one for future surveys to avoid redundancy.
-Table x shows the obtained results of the dimensionality reduction and displays x variables which haven't been reduced, and x reduced ones.
+It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
+
+Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
+It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
+Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
 
@@
 
-xtable(partition_meals,
+stargazer(partition_meals,
                                #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of outcomes, Meals"
+          caption = "Partition of outcomes, Meals", 
+          label = 'partitionmeals'
           #align = "lmmm"
@@
 
-xtable(partition_trips,
+stargazer(partition_trips,
                                #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of outcomes, Trips"
+          caption = "Partition of outcomes, Trips",
+          label = 'partitiontrips'
           #align = "lmmm"
@@
 @
-\subsection{A3: OLS Regressions}
+
+\subsection{A4: OLS Regressions}
 
 #normal weights selfworth& subsidiy
-<<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+<<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 

### 2020-02-27 paper.tex
xxx

--- 2020-02-26 paper.tex
@@
 
-Figure\\
-
-\begin{figure}
-  \caption{Dispersion in productivity levels}
-  \label{LineDisp}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-1-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
+% Figure\\
+% 
+% \begin{figure}
+%   \caption{Dispersion in productivity levels}
+%   \label{LineDisp}
+% 
+% <<echo=FALSE>>=
+% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
+% print(figureLineDisp)
+% @
+% 
+% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
 A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
@@
 Compare Kehrig (2015), Figure 1.}
-\end{figure}
-
-Figure \ref{LineDisp}
+% \end{figure}
+
+% Figure \ref{LineDisp}
 
@@
 \caption{Statistical models}
-\label{table:coefficients}
+\label{mealsTripsSubsidyRegressions}
 \end{center}
@@
 
+\subsection{Previous research}
+
+The previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
+Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance.
+Moreover, Deckers et.
+al.
+(2015) found by experiments in Germany, that children of higher educated parents are signficantly more patient.
+Children from parents with lower income and lower educational attainment typically have a lower weight at birth and are born in a later week of gestation, which are indicators for good initial conditions (Deckers et.
+al.
+2015, Case et.
+al.
+2002).
+Children that grow up in families with a low socio-economic status are often less mobile and more likely to keep to themselves.
+This could have a negative influence on their character development.
+For example, Chetty et.
+al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the result of Deckers et.
+al.
+(2020) provides causal evidence on the effect of social environment on prosocial attitudes.
+Being supported by a mentor could have a significant and persistant increase of elementary school children´s prosociality, in response to prosocial role models and intense social interactions.
+As investigated by Heckmann et.
+al.
+(2010) for a preschool education program in the US, investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+
 \section{Data}
 
-To measure the effect of CHILDREN´s engagement on the organizations we use the data they collected from 2011 to 2018.
+To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018.
 In each year they send a survey to the organizations with several questions about the previous year.
@@
 
-{\centering \includegraphics[width=0.8\textwidth]{figure/unnamed-chunk-2-1}
+{\centering \includegraphics[width=0.8\textwidth]{figure/DaytodayskillsSelfworth-1}
 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:10 2020
-\begin{table}[ht]
-\centering
-\begin{tabular}{mmmmm}
-  \hline
-Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
-  \hline
-2011 & 3748.0 &  & 52 &  \\ 
-  2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
-  2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
-  2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
-  2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
-  2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
-  2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
-  2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
-   \hline
-\end{tabular}
-\caption{Summary Statistics} 
+# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+# 
+# # first, read in all Rds objects that you need
+# 
+# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
+#  
+# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+# 
+# fundamental_dynamics <- xtable(fundamental_dynamics,
+#                                digits = c(0, 0, 1, 1, 0, 0),
+#           caption = "Summary Statistics",
+#           align = "lmmmmm", 
+#           label = "fundamentalDynamics"
+#           )
+# print(fundamental_dynamics, include.rownames = FALSE)
+# @
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
   \label{fundamentalDynamics} 
-\end{table}
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
+$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
+$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
+$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
+$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
+$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
+$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
+$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{fundamentalDynamics} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Summary Statistics \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table} 
+ [1] ""                                                                                                           
+ [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
+ [3] "% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM"                                                            
+ [4] "\\begin{table}[!htbp] \\centering "                                                                         
+ [5] "  \\caption{} "                                                                                             
+ [6] "  \\label{fundamentalDynamics} "                                                                            
+ [7] "\\begin{tabular}{@{\\extracolsep{5pt}} ccccc} "                                                             
+ [8] "\\\\[-1.8ex]\\hline "                                                                                       
+ [9] "\\hline \\\\[-1.8ex] "                                                                                      
+[10] "$2,011$ & $3,748$ & $$ & $52$ & $$ \\\\ "                                                                   
+[11] "$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\\\ "                                                            
+[12] "$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\\\ "                                                            
+[13] "$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\\\ "                                                            
+[14] "$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\\\ "                                                            
+[15] "$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\\\ "                                                            
+[16] "$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\\\ "                                                            
+[17] "$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\\\ "                                                        
+[18] "\\hline \\\\[-1.8ex] "                                                                                      
+[19] "\\end{tabular} "                                                                                            
+[20] "\\end{table} "                                                                                              
+[21] ""                                                                                                           
+[22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
+[23] "% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM"                                                            
+[24] "\\begin{table}[!htbp] \\centering "                                                                         
+[25] "  \\caption{} "                                                                                             
+[26] "  \\label{fundamentalDynamics} "                                                                            
+[27] "\\begin{tabular}{@{\\extracolsep{5pt}} c} "                                                                 
+[28] "\\\\[-1.8ex]\\hline "                                                                                       
+[29] "\\hline \\\\[-1.8ex] "                                                                                      
+[30] "Summary Statistics \\\\ "                                                                                   
+[31] "\\hline \\\\[-1.8ex] "                                                                                      
+[32] "\\end{tabular} "                                                                                            
+[33] "\\end{table} "
 
@@
 Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
-The x-axis plots the index for a healthy diet.
+The x-axis displays the index for a healthy diet.
 The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.
-
-We use standardized versions of these variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-If we estimated these models with ordinary least squares, we would ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we fit the models with weighted least squares, using the number of beneficiaries as weights.
+The possible values are: all, most, some, few and none.
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as most.
+The highest amount of healthy criteria to be fulfilled is x.
+
+All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria.
+The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constituted a healthy diet.
+It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
+However, for the variable less ill, the least data is availabe.
+Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables.
+This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Thu, Feb 27, 2020 - 1:16:40 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 
-\subsection{A1: Cumulative Odds Regression}
-
-As an option to run an regression on the original ordinal variables, we use the vglm function from the VGAM package...
-
-Use from zwichenpräsentation
+\subsection{A1: Expanded Health Regression}
+
+In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
+
+% #normal weights selfworth& subsidiy
+% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% 
+% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% @
+
+\begin{table}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c }
+\hline
+ & OLS & WLS & OLS Impute & WLS Impute \\
+\hline
+(Intercept)               & $-1.08^{***}$ & $-0.99^{**}$ & $-0.04$      & $-0.08$    \\
+                          & $(0.24)$      & $(0.30)$     & $(0.18)$     & $(0.20)$   \\
+DGECriteriaNoScaled       & $0.34^{***}$  & $0.36^{***}$ & $0.23^{***}$ & $0.27$     \\
+                          & $(0.08)$      & $(0.06)$     & $(0.07)$     & $(0.14)$   \\
+regionalProducts\_scaled  & $0.02$        & $-0.03$      & $0.11$       & $0.02$     \\
+                          & $(0.08)$      & $(0.11)$     & $(0.07)$     & $(0.11)$   \\
+yearsSupportSince         & $0.02$        & $-0.03$      & $0.01$       & $0.05^{*}$ \\
+                          & $(0.03)$      & $(0.04)$     & $(0.02)$     & $(0.02)$   \\
+realSubsidyPerBeneficiary & $-0.00$       & $0.00$       & $0.00$       & $-0.00$    \\
+                          & $(0.00)$      & $(0.00)$     & $(0.00)$     & $(0.00)$   \\
+stateBayern               & $0.96^{**}$   & $1.88^{***}$ &              &            \\
+                          & $(0.33)$      & $(0.49)$     &              &            \\
+stateBerlin               & $1.09^{**}$   & $1.34^{***}$ &              &            \\
+                          & $(0.37)$      & $(0.37)$     &              &            \\
+stateBrandenburg          & $2.21^{***}$  & $2.46^{***}$ &              &            \\
+                          & $(0.43)$      & $(0.40)$     &              &            \\
+stateBremen               & $1.00$        & $1.03$       &              &            \\
+                          & $(0.58)$      & $(0.59)$     &              &            \\
+stateHamburg              & $0.95$        & $1.96^{***}$ &              &            \\
+                          & $(0.67)$      & $(0.40)$     &              &            \\
+stateHessen               & $0.87^{***}$  & $1.16^{***}$ &              &            \\
+                          & $(0.23)$      & $(0.31)$     &              &            \\
+stateMV                   & $0.09$        & $0.14$       &              &            \\
+                          & $(0.21)$      & $(0.26)$     &              &            \\
+stateNiedersachsen        & $2.48^{***}$  & $2.30^{***}$ &              &            \\
+                          & $(0.40)$      & $(0.43)$     &              &            \\
+stateNRW                  & $0.68^{*}$    & $1.00^{**}$  &              &            \\
+                          & $(0.27)$      & $(0.33)$     &              &            \\
+stateSaarland             & $1.50^{***}$  & $1.75^{***}$ &              &            \\
+                          & $(0.32)$      & $(0.25)$     &              &            \\
+stateSachsen              & $1.34^{***}$  & $1.23^{***}$ &              &            \\
+                          & $(0.27)$      & $(0.27)$     &              &            \\
+stateSchleswig-Holstein   & $1.33^{***}$  & $1.63^{***}$ &              &            \\
+                          & $(0.37)$      & $(0.42)$     &              &            \\
+stateThüringen            & $0.99$        & $1.29^{*}$   &              &            \\
+                          & $(0.59)$      & $(0.55)$     &              &            \\
+\hline
+R$^2$                     & 0.51          & 0.73         & 0.09         & 0.22       \\
+Adj. R$^2$                & 0.39          & 0.66         & 0.07         & 0.20       \\
+Num. obs.                 & 88            & 88           & 175          & 175        \\
+RMSE                      & 0.73          & 5.62         & 0.94         & 7.77       \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Less ill expanded model}
+\label{expandLessIll}
+\end{center}
+\end{table}
+
+\subsection{A2: Cumulative Odds Regression}
+
+As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit from the VGAM package.
+Equation \ref{PropoddsModel} describes the model setup:
 
 \begin{equation}
-\label{ModelProdu}
-\ln y_{it} = \frac{}{}  \sum
+\label{PropoddsModel}
+  P(Y_i \leq \ r) = \frac{exp(y_0_r + x_i^Ty)}{1+exp(y_0_r + x_i^Ty)}    
 \end{equation}
 
+To demonstrate the results of this method, we show in the tables \ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds} the regressions of the health related variables on the healthy meals criterion and in the tables \ref{selfworthOdds} and \ref{dayToDayOdds} the regressions of the real meals subsidy on selfworth and everyday expertise.
+
+As an example of interpreting such models, we consider the model of table \ref{lessIllOdds}: An increase of the healthy meals criterion by 1 is associated with an increase in chances, that a proportion of a maximum of r beneficiaries is healthier in relation to that a proportion of more than r beneficiaries are healthier, by the factor of exp(-0.29127) = 0.75.
+
+A summary of the remaining models:
+
+\begin{itemize}
+  \item{Dietary Knowledge: exp(-0.089) = 0.91}
+  \item{Appreciate Healthy: exp(-0199) = 0.82}
+  \item{Selfworth: exp(-0.00001) = 1}
+  \item{Everyday Expertise: (-0.00003) = 1} 
+\end{itemize}
+
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Thu, Feb 27, 2020 - 1:16:40 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Thu, Feb 27, 2020 - 1:16:40 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, selfworth} 
-  \label{} 
+  \caption{Propodss Regression Results: Selfworth} 
+  \label{selfworthOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Wed, Feb 26, 2020 - 10:15:19 PM
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Equality of opportunities, everyday expertise} 
-  \label{} 
+  \caption{Propodss Regression Results: Everyday expertise} 
+  \label{dayToDayOdds} 
 \begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
@@
 
-\subsection{A2: Partition}
-
-In addition to the factor analysis described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-
-QUOTES FROM PAPER, describe method
+\subsection{A3: Partition}
+
+In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+This method was developped by Millenstein et.
+al in the context of genome analysis.
+
+According to the researchers, potential benefits of reducing dimensionality are reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{} (p.677).
+
+The partition approach partitions data into subsets of related features.
+It then  summarizes each subset into one new feature.
+By that, it defines a surjective mapping \cite{} (p.676).
+A function g is implemented using the arithmetic mean.
+In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
+What is as well different is the information loss constraint.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced.\cite{}(p.677)
 
 In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
-It might be meaningful to decide to use only one of the variables a reduced variable consists of or a summarizing one for future surveys to avoid redundancy.
-Table x shows the obtained results of the dimensionality reduction and displays x variables which haven't been reduced, and x reduced ones.
-
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:20 2020
-\begin{table}[ht]
-\centering
-\begin{tabular}{rllr}
-  \hline
- & Variable, Meals & Mapping, Meals & Information, Meals \\ 
-  \hline
-1 & participateMore & participateMore & 1.00 \\ 
-  2 & tasksLunch & tasksLunch & 1.00 \\ 
-  3 & ownIdeas & ownIdeas & 1.00 \\ 
-  4 & stayLonger & stayLonger & 1.00 \\ 
-  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
-  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
-  7 & foodCulture & foodCulture & 1.00 \\ 
-  8 & lessIll & lessIll & 1.00 \\ 
-  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
-  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
-  11 & addressProblems & addressProblems & 1.00 \\ 
-  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
-  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
-  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
-  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
-  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
-  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
-  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
-  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
-  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
-  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
-  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
-  23 & reduced\_var\_3 & proud & 0.43 \\ 
-  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
-  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
-  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
-  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
-  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
-  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
-   \hline
-\end{tabular}
-\caption{Partition of outcomes, Meals} 
-\end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Wed Feb 26 22:15:20 2020
-\begin{table}[ht]
-\centering
-\begin{tabular}{rllr}
-  \hline
- & Variable, Trips & Mapping, Trips & Information, Trips \\ 
-  \hline
-1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
-  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
-  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
-  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
-  5 & tripsBudget & tripsBudget & 1.00 \\ 
-  6 & tripsMoney & tripsMoney & 1.00 \\ 
-  7 & tripsReview & tripsReview & 1.00 \\ 
-  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
-  9 & tripsMobility & tripsMobility & 1.00 \\ 
-  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
-  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
-  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
-  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
-  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
-  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
-  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
-  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
-  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
-  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
-  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
-   \hline
-\end{tabular}
-\caption{Partition of outcomes, Trips} 
+It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
+
+Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
+It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
+Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{partitionmeals} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+Information, Meals & 29 & 0.670 & 0.270 & 0 & 0.4 & 1 & 1 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{partitionmeals} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Partition of outcomes, Meals \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{partitiontrips} 
+\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
+Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
+\hline \\[-1.8ex] 
+Information, Trips & 20 & 0.834 & 0.215 & 0 & 0.6 & 1 & 1 \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+\begin{table}[!htbp] \centering 
+  \caption{} 
+  \label{partitiontrips} 
+\begin{tabular}{@{\extracolsep{5pt}} c} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+Partition of outcomes, Trips \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
 \end{table} 
@@
 {\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
-\subsection{A3: OLS Regressions}
+
+\subsection{A4: OLS Regressions}
 

### 2020-02-27 ANALYSIS/DATA/Data 2013&2014.R

@@ -1,7 +1,3 @@
-library(readxl)
-library(dplyr)
-library(tidyverse)
-
 data2013 <- read_excel("ANALYSIS/DATA/CHILDREN Wirkungsdaten_VERTRAULICH_final.xlsx", sheet = "2014")
 data2014 <- read_excel("ANALYSIS/DATA/CHILDREN Wirkungsdaten_VERTRAULICH_final.xlsx", sheet = "2015")
 

### 2020-02-27 ANALYSIS/DATA/Data 2016.R

@@ -1,12 +1,6 @@
 # PaRE3To-Projekt
 
-# 1. Herunterladen der Daten ----------------------------------------------
-
-#rm(list = ls())
-
-library(readxl)
-library(dplyr)
-library(tidyverse)
+# 1. Herunterladen der Daten -----------------------------------------------
 
 ### Daten 2017
 

### 2020-02-27 ANALYSIS/DATA/MakeGather.R

@@ -1,5 +1,6 @@
 # read packages
 
+
 library(texreg)
 library(readxl)
 library(tidyverse)
@@ -10,7 +11,18 @@ library(lattice)
 library(survival)
 library(Formula)
 library(tidyimpute)
-
+library(tidyselect)
+library(imputeMissings)
+library(zoo)
+library(rlang)
+library(stargazer)
+library(estimatr)
+library(ggplot2)
+library(stats)
+library(cowplot)
+library(ggpubr)
+library(polycor)
+library(lavaan)
 
 # Gather and cleanup raw data files
 
@@ -32,7 +44,6 @@ source(encoding = "UTF8", "./ANALYSIS/DATA/DataPriceIndices.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Merge.R")
 
-
 source(encoding = "UTF8", "./ANALYSIS/DATA/MakeReal.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/Impute.R")
@@ -43,9 +54,11 @@ source(encoding = "UTF8", "./ANALYSIS/DATA/Exclude Outliers Regression.R")
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/categoricalData.R")
 
-# specialVariables has to be after cateogricalData
+# specialVariables has to be after categoricalData
 
 source(encoding = "UTF8", "./ANALYSIS/DATA/specialVariables.R")
+
+
 
 # source(encoding = "UTF8", "./ANALYSIS/DATA/Standardized Coefficents.R")
 

### 2020-02-27 ANALYSIS/DATA/Merge.R

@@ -1,6 +1,3 @@
-# Load packages
-library(dplyr)
-
 # Join data from 2011 to 2018
 
 data201118 <- df_2018 %>% #data2019 %>%

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R

@@ -1,0 +1,92 @@
+#davor durchlaufen lassen: makegather, control_group, advanced_timeseries
+
+library(ggfortify)
+
+#use fortify to convert ts to ggplot
+
+df_dayToDaySkills_treat <- fortify(ts_dayToDaySkills_treat)
+
+# rename 
+
+df_dayToDaySkills_treat <- df_dayToDaySkills_treat %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+
+#look if it works
+
+plot_dayToDaySkills_treat <- ggplot(df_dayToDaySkills_treat, aes(Year, Data)) + geom_line()
+
+df_dayToDaySkills_control <- fortify(ts_dayToDaySkills_control) 
+df_dayToDaySkills_control <- df_dayToDaySkills_control %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+ggplot(df_dayToDaySkills_control, aes(Year, EverydayExpertise)) + geom_line()
+
+#selfworth
+
+df_selfworth_treat <- fortify(ts_selfworth_treat)
+df_selfworth_treat <- df_selfworth_treat %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + geom_line()
+
+df_selfworth_control <- fortify(ts_selfworth_control)
+df_selfworth_control <- df_selfworth_control %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+ggplot(df_selfworth_control, aes(Year, EverydayExpertise)) + geom_line()
+
+#weeklycooks
+
+df_weeklyCooks_treat <- fortify(ts_weeklyCooks_treat) 
+df_weeklyCooks_treat <- df_weeklyCooks_treat %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+ggplot(df_weeklyCooks_treat, aes(Year, EverydayExpertise)) + geom_line()
+
+df_weeklyCooks_control <- fortify(ts_weeklyCooks_control)
+df_weeklyCooks_control <- df_weeklyCooks_control %>% 
+  rename(Year = Index, EverydayExpertise = Data)
+ggplot(df_weeklyCooks_control, aes(Year, EverydayExpertise)) + geom_line()
+
+#monthlyCooks
+
+df_monthlyCooks_treat <- fortify(ts_monthlyCooks_treat) 
[…]

### 2020-02-27 ANALYSIS/DATA/categoricalData.R

@@ -5,10 +5,7 @@
 # How does map from package purrr work: https://r4ds.had.co.nz/iteration.html
 # How to mutate columns selectively with automatic new names: https://dplyr.tidyverse.org/reference/mutate_all.html
 
-# load packages
-library(purrr)
-library(tidyselect)
-library(stringr)
+
 
 categories <- c(NA, 0, 1, 2, 3, 4, 1/2, 3/2, 5/2, 7/2, 1/3, 2/3, 4/3, 5/3, 7/3, 8/3, 10/3, 11/3, 1/4, 3/4, 5/4, 7/4, 9/4, 11/4, 13/4, 15/4, 7/6, 8/6, 10/6, 11/6)
 
@@ -23,6 +20,16 @@ weight <- function(expr) {
     }
   else {
     return(mergedData$eatersPerMealNo*0.25*expr)
+  }
+}
+
+weightOutliers <- function(expr) {
+  name <- quo_name(enquo(expr))
+  if(stringr::str_detect(name, "trips")) {
+    return(mealsNoOutliers$tripsKidsNo*0.25*expr)
+  }
+  else {
+    return(mealsNoOutliers$eatersPerMealNo*0.25*expr)
   }
 }
 
@@ -60,21 +67,29 @@ mergedDataImputeInterpolation <- mergedDataImputeInterpolation %>%
          lessIll_scaled = scale_this(lessIll), lessIll_weighted = weight(mergedData$lessIll), lessIll_ordered = as.ordered(lessIll),
          influenceHome_scaled = scale_this(influenceHome), influenceHome_weighted = weight(mergedData$influenceHome), influenceHome_ordered = as.ordered(influenceHome))
 
+# append lost categorical variable state (number of rows hasn't changed)
+
+stateDF <- data.frame(mergedData$state)
+
+stateDF <- rename(stateDF, state = mergedData.state)
+
+mergedDataImputeInterpolation <- cbind.data.frame(stateDF, mergedDataImputeInterpolation)
+
 # do the same for mealsNoOutliers
 
 mealsNoOutliers <- mealsNoOutliers %>% 
-  mutate_if(pretendsToBeMetric, list(scaled = scale_this, ordered = as.ordered, weighted = weight))
+  mutate_if(pretendsToBeMetric, list(scaled = scale_this, ordered = as.ordered, weighted = weightOutliers))
 
[…]

### 2020-02-27 ANALYSIS/DATA/specialVariables.R

@@ -1,3 +1,17 @@
+# Names of variables used in models
+
+modelVariablesNames <- c('lessIll',
+                    'appreciateHealthy',
+                    'dietaryKnowledge',
+                    'DGECriteriaNo',
+                    'selfworth',
+                    'dayToDaySkills',
+                    'tripsSelfworth',
+                    'tripsDayToDaySkills',
+                    'realSubsidyPerBeneficiary',
+                    'realTripsSubsidyPerBeneficiary'
+                    )
+
 # outcomes not directly related to beneficiaries 
 
 generalOutcomes <- c(
@@ -66,4 +80,5 @@ availableVariables <- function(dataSet, variableName) {
   return(names(comparisonAvailableYears))
 }
 
-alwaysRecordedVariables <- availableVariables(mergedData, "subsidy")
+alwaysRecordedVariablesMeals <- availableVariables(mergedData, "subsidy")
+alwaysRecordedVariablesTrips <- availableVariables(mergedData, 'realSubsidy')

### 2020-02-27 ANALYSIS/MakeAnalysis.R

@@ -1,6 +1,14 @@
+source(encoding = "UTF8", "./ANALYSIS/SummaryStatistics.R")
+# source(encoding = "UTF8", "./ANALYSIS/SummaryStatistics_ggplot.R")
 source(encoding = "UTF8", "./ANALYSIS/PlotHealthVariables.R")
 source(encoding = "UTF8", "./ANALYSIS/PlotVariablesOverTime.R")
-source(encoding = "UTF8", "./ANALYSIS/Regressions.R")
-# source(encoding = "UTF8", "./ANALYSIS/CorrelationMatrixEntdecker.R")
-# source(encoding = "UTF8", "./ANALYSIS/CorrelationMatrixMittagstisch.R")
-# source(encoding = "UTF8", "./ANALYSIS/factor_analysis")
+source(encoding = "UTF8", "./ANALYSIS/factor_analysis.R")
+source(encoding = "UTF8", "./ANALYSIS/double-selection.R")
+source(encoding = "UTF8", "./ANALYSIS/Partition.R")
+source(encoding = "UTF8", "./ANALYSIS/MetricRegressions.R")
+source(encoding = "UTF8", "./ANALYSIS/HealthRegressions.R")
+source(encoding = "UTF8", "./ANALYSIS/PropoddsRegressions.R")
+source(encoding = "UTF8", "./ANALYSIS/Selfworth_dayToDaySkills.R")
+# source(encoding = "UTF8", "./ANALYSIS/DATA/regression_tables.R")
+
+

### 2020-02-27 ANALYSIS/PlotVariablesOverTime.R

@@ -1,12 +1,6 @@
 #inspectinfluenceofvariablesovertime
 #inpercentages
 
-library(ggplot2)
-library(cowplot)
-library(purrr)
-library(dplyr)
-library(ggpubr)
-
 #setthevariables
 
 responset= names(mergedData)

### 2020-02-27 ANALYSIS/SummaryStatistics.R

@@ -1,11 +1,15 @@
-#Real Subsidy Time Trend Total & Median
+#Real Subsidy Time Trend Total &Median
 
-library(dplyr)
-library(estimatr)
-library(tidyverse)
-library(ggplot2)
-library(stats)
-library(cowplot)
+
+# Inititial summary statistics about 
+
+modelVariables <- mergedData %>% 
+  dplyr::select(all_of(modelVariablesNames)) %>% 
+  data.frame()
+
+modelVariablesSummary <- stargazer(modelVariables)
+
+saveRDS(modelVariablesSummary, './ANALYSIS/Tables/modelVariablesSummary.Rds')
 
 ###total trips subsidy real 
 
@@ -78,7 +82,27 @@ summaryStatistics_Subsidy <- plot_grid(totalRealSub, totalRealTripSub, medianRea
                                        label_x = 0, label_y = 0, hjust = -3, vjust = 
                                          -1.5, label_fontface = "plain", label_size = 11)
 
-saveRDS(summaryStatistics_Subsidy, "./ANALYSIS/GRAPHS/PAPER GRAPHS/summaryStatistics_Subsidy.Rds")
+saveRDS(summaryStatistics_Subsidy, "./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
 
 
+#number of beneficiaries & organisations
+
+organisations_beneficiaries <- mergedData%>%
+  group_by(year)%>%
+  dplyr::summarize(Lunch_KidsNo=sum(eatersPerMealNo, na.rm = TRUE),trips_KidsNo=sum(tripsKidsNo, na.rm = TRUE), Lunch_OrganisationsNo = n_distinct(id))
+#trips no
+TripsOrgaData <- mergedData %>%
+  dplyr::filter(!(tripsKidsNo == 0 | is.na(tripsKidsNo)))
+
+TripsOrganisationsNumber <- TripsOrgaData%>%
+  group_by(year)%>%
+  dplyr::summarise(Trips_OrganisationNo = n_distinct(id))
+
+#join 
+organisationsbeneficaries <- organisations_beneficiaries %>% 
+  full_join(TripsOrganisationsNumber) 
+
+organisationsbeneficaries[1,3] <- NA
+
+fundamental_dynamics = saveRDS(organisationsbeneficaries,"./ANALYSIS/Tables/fundamental_dynamics.Rds")
 

### 2020-02-27 ANALYSIS/SummaryStatistics_ggplot.R

@@ -1,4 +1,4 @@
-#Real Subsidy Time Trend Total &Median
+#Real Subsidy Time Trend Total & Median
 
 library(dplyr)
 library(estimatr)
@@ -81,24 +81,4 @@ summaryStatistics_Subsidy <- plot_grid(totalRealSub, totalRealTripSub, medianRea
 saveRDS(summaryStatistics_Subsidy, "./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
 
 
-#number of beneficiaries & organisations
-
-organisations_beneficiaries <- mergedData%>%
-  group_by(year)%>%
-  dplyr::summarize(Lunch_KidsNo=sum(eatersPerMealNo, na.rm = TRUE),trips_KidsNo=sum(tripsKidsNo, na.rm = TRUE), Lunch_OrganisationsNo = n_distinct(id))
-#trips no
-TripsOrgaData <- mergedData %>%
-  dplyr::filter(!(tripsKidsNo == 0 | is.na(tripsKidsNo)))
-
-TripsOrganisationsNumber <- TripsOrgaData%>%
-  group_by(year)%>%
-  dplyr::summarise(Trips_OrganisationNo = n_distinct(id))
-
-#join 
-organisationsbeneficaries <- organisations_beneficiaries %>% 
-  full_join(TripsOrganisationsNumber) 
-
-organisationsbeneficaries[1,3] <- NA
-
-fundamental_dynamics = saveRDS(organisationsbeneficaries,"./ANALYSIS/Tables/fundamental_dynamics.Rds")
 

### 2020-02-27 ANALYSIS/double-selection.R

@@ -6,9 +6,9 @@ library(tidyselect)
 
 # select rows with year in which DGECriteriaNo was recorded
 
-datasetMode <- mergedDataImputeMode %>% 
-  filter(year %in% c(2018, 2017, 2016, 2014)) %>%
-  dplyr::select(!tidyselect::contains('scaled'))
+# datasetMode <- mergedDataImputeMode %>% 
+#   filter(year %in% c(2018, 2017, 2016, 2014)) %>%
+#   dplyr::select(!tidyselect::contains('scaled'))
 
 datasetInterpolation <- mergedDataImputeInterpolation %>% 
   filter(year %in% c(2018, 2017, 2016, 2014)) %>% 
@@ -21,13 +21,17 @@ datasetInterpolation <- mergedDataImputeInterpolation %>%
 # loop for regressions with varying outcome and features
 
 flexibleRegression <- function(response, predictor, dataset) {
+  dataset <- dataset %>% 
   x <- as.matrix(dataset[, !(names(dataset) %in% response)])
   y <- as.matrix(dataset[, response])
   d <- as.matrix(dataset[, predictor])
   rlassoEffect(x, y, d)
 }
 
-DSSelfworthRealSubsidy <- flexibleRegression("selfworth", "realSubsidy", mergedDataImputeAll)
+DF_DS <- mergedDataImputeInterpolation %>% 
+  drop_na()
+
+DSSelfworthRealSubsidy <- flexibleRegression("selfworth", "realSubsidy", datasetInterpolation)
 
 DSDayToDaySkillsRealSubsidy <- flexibleRegression("dayToDaySkills", "realSubsidy", mergedDataImputeAll)
 

### 2020-02-27 ANALYSIS/factor_analysis.R

@@ -7,25 +7,72 @@
 #z.B. kann ID der Einrichtung nicht verwendet werden 
 #deshalb muss ich nur die relevanten Variablen auswählen
 
-#relevante packages laden
-library(tidyverse)
-library(polycor)
-library(psych)
-library(lavaan)
+# --- create two data sets for factor analysis: one for Meals, one for Trips
 
-drop.cols <- c('DGECriteriaNoScaled', 'lessIll_scaled')
+additionalVariablesMeals <- c('DGECriteriaNoScaled', 'realSubsidyPerBeneficiary')
 
-ordinalVariablesMeals <- mergedDataImputeInterpolation %>% 
+dfFAMealsPlus <- mergedDataImputeInterpolation %>% 
   dplyr::select(-any_of(generalOutcomes_scaled)) %>% 
-  dplyr::select(c(any_of(alwaysRecordedVariables), drop.cols)) %>% 
-  dplyr::select(c(tidyselect::contains('_scaled') & !tidyselect::contains('trips'), drop.cols)) %>%
+  dplyr::select(c(any_of(alwaysRecordedVariablesMeals), additionalVariablesMeals)) %>% 
+  dplyr::select(c(tidyselect::contains('_scaled') & !tidyselect::contains('trips'), additionalVariablesMeals)) %>%
   drop_na
          
-ordinalVariablesMealsFA <- ordinalVariablesMeals %>% 
-  dplyr::select(-drop.cols)
+dfFAMeals <- dfFAMealsPlus %>% 
+  dplyr::select(-'realSubsidyPerBeneficiary')
 
-lessIll_DGECriteriaNo <- ordinalVariablesMeals %>% 
-  dplyr::select(drop.cols) %>% 
+nobsFA <- nrow(dfFAMeals)
+
+# General correlation matrix Meals
+
+# with ML=TRUE, hetcor() takes very long to compute
+# https://john-uebersax.com/stat/tetra.htm
+# latent correlations better name than polychoric correlations
+# pairwise.complete.obs. considered dangerous
+# https://www.r-bloggers.com/pairwise-complete-correlation-considered-dangerous/
+
+correlationMatrixMeals <- hetcor(dfFAMeals, ML=FALSE, use = "pairwise.complete.obs")
+
+# hetcor() creates many warnings, either "In log(P) : NaNs wurden erzeugt" or "In polychor(x, y, ML = ML, std.err = std.err) : 1 column with zero marginal removed"
+
+# select all correlations above a threshold
+## transform correlation matrix
[…]

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R
lg

@@ -69,10 +69,24 @@ ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) +
   grids(axis = c("x"), color = "grey92", size = NULL, linetype = NULL) +
   geom_smooth(method = "lm", se = FALSE, color = "grey0") +
   geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "grey") +
-  ggtitle("Trend of everyday expertise") + ylab("Everyday Expertise") 
+  ggtitle("Trend of everyday expertise") + ylab("Everyday Expertise")
+  
 
 
+#versuch, legende hinzuzufügen
 
+
+ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
+  geom_point() + 
+  geom_line(color = "grey0", aes(x=Year, y=EverydayExpertise, color="Treatment")) + 
+  geom_point(data = df_dayToDaySkills_control, color = "grey") + 
+  geom_line(data = df_dayToDaySkills_control, 
+            linetype = "dotted", color = "grey10", aes(x=Year, y=EverydayExpertise, color="Control")) +
+  grids(axis = c("x"), color = "grey92", size = NULL, linetype = NULL) +
+  geom_smooth(method = "lm", se = FALSE, color = "grey0") +
+  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "grey") +
+  ggtitle("Trend of everyday expertise") + ylab("Everyday Expertise") +
+  scale_color_discrete(name="legend")
 
 
 

### 2020-02-27 paper.Rnw
update rnw

@@
 
-# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+<<FundamentalDynamicsTest, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 # 
@@
 # print(fundamental_dynamics, include.rownames = FALSE)
-# @
+@
 
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{l c}
-\hline
- & Selfworth \\
-\hline
-(Intercept)             & $-1.13^{***}$ \\
-                        & $(0.32)$      \\
-dfcEF2$treatEF          & $-0.47$       \\
-                        & $(0.31)$      \\
-\hline
-Num. obs.               & $430$         \\
-R$^2$ (full model)      & $0.47$        \\
-R$^2$ (proj model)      & $0.47$        \\
-Adj. R$^2$ (full model) & $0.36$        \\
-Adj. R$^2$ (proj model) & $0.36$        \\
-\hline
-\multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-\caption{linear regression}
-\label{table:coefficients}
-\end{center}
-\end{table}
+% \begin{table}
+% \begin{center}
+% \begin{tabular}{l c}
+% \hline
+%  & Selfworth \\
+% \hline
+% (Intercept)             & $-1.13^{***}$ \\
+%                         & $(0.32)$      \\
+% dfcEF2$treatEF          & $-0.47$       \\
+%                         & $(0.31)$      \\
+% \hline
+% Num. obs.               & $430$         \\
+% R$^2$ (full model)      & $0.47$        \\
+% R$^2$ (proj model)      & $0.47$        \\
+% Adj. R$^2$ (full model) & $0.36$        \\
+% Adj. R$^2$ (proj model) & $0.36$        \\
+% \hline
+% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+% \end{tabular}
+% \caption{linear regression}
+% \label{table:coefficients}
+% \end{center}
+% \end{table}
 
@@
 
-% #normal weights selfworth& subsidiy
 % <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
-#normal weights selfworth& subsidiy
 <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=

### 2020-02-27 paper.tex
update rnw

@@
 
-# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-# 
-# # first, read in all Rds objects that you need
-# 
-# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
-#  
-# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
-# 
-# fundamental_dynamics <- xtable(fundamental_dynamics,
-#                                digits = c(0, 0, 1, 1, 0, 0),
-#           caption = "Summary Statistics",
-#           align = "lmmmmm", 
-#           label = "fundamentalDynamics"
-#           )
-# print(fundamental_dynamics, include.rownames = FALSE)
-# @
-
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM
+% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM
 \begin{table}[!htbp] \centering 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM
+% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM
 \begin{table}[!htbp] \centering 
@@
  [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM"                                                            
+ [3] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            
  [4] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 [22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Thu, Feb 27, 2020 - 1:16:32 PM"                                                            
+[23] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            
 [24] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:40 PM
+% Date and time: Thu, Feb 27, 2020 - 2:47:06 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:40 PM
+% Date and time: Thu, Feb 27, 2020 - 2:47:07 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+% Date and time: Thu, Feb 27, 2020 - 2:47:08 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 1:16:41 PM
+% Date and time: Thu, Feb 27, 2020 - 2:47:08 PM
 \begin{table}[!htbp] \centering 

### 2020-02-27 ANALYSIS/DATA/MakeGather.R
hjkiop

@@ -15,6 +15,7 @@ library(tidyselect)
 library(imputeMissings)
 library(zoo)
 library(rlang)
+library(estimatr)
 
 # Gather and cleanup raw data files
 

### 2020-02-27 ANALYSIS/Metric Regressions.R

@@ -22,7 +22,17 @@ texreg(mealsNo_sub.lm)
 
 saveRDS(mealsNo_sub.lm,"./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
 
+#mealsno with control 
 
+mealsNo_sub_control.lm <- lm_robust(mealsNo ~ realSubsidy + eatersPerMealNo, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(mealsNo_sub_control.lm) 
+
+texreg(mealsNo_sub_control.lm)
+
+saveRDS(mealsNo_sub_control.lm,"./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds")
+
+#trips without control
 tripsNo_sub.lm <- lm_robust(tripsNo ~ realTripsSubsidy, data = mergedData)%>%
   extract.lm_robust(include.ci = FALSE)
 summary(tripsNo_sub.lm)
@@ -30,6 +40,16 @@ summary(tripsNo_sub.lm)
 texreg(tripsNo_sub.lm)
 
 saveRDS(tripsNo_sub.lm,"./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+
+#trips with control 
+
+tripsNo_sub_control.lm <- lm_robust(tripsNo ~ realTripsSubsidy + tripsKidsNo, data = mergedData)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(tripsNo_sub_control.lm)
+
+texreg(tripsNo_sub_control.lm)
+
+saveRDS(tripsNo_sub_control.lm,"./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
 
 
 #dataset with excluded outliers: mealsNo / tripsNo
@@ -42,6 +62,17 @@ texreg(mealsNo_sub_ex.lm)
 
 saveRDS(mealsNo_sub_ex.lm,"./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")
 
+#outliers meals with control
+
+mealsNo_sub_ex_control.lm <- lm_robust(mealsNo ~ realSubsidy + eatersPerMeal, data = mealsNoOutliers)%>%
+  extract.lm_robust(include.ci = FALSE)
+summary(mealsNo_sub_ex_control.lm)
+
+texreg(mealsNo_sub_ex_control.lm)
+
[…]

### 2020-02-27 ANALYSIS/PlotVariablesOverTime.R

@@ -13,7 +13,7 @@ responset= names(mergedData)
 # [5:213]
 # expl= names(mergedData)[4]
 
-responset = purrr::set_names(response)
+responset = purrr::set_names(responset)
 responset
 
 explt = purrr::set_names("year")

### 2020-02-27 ANALYSIS/Summary Statistics with ggplot.R

@@ -1,84 +1,115 @@
-#Real Subsidy Time Trend Total & Median
+# #Real Subsidy Time Trend Total & Median
+# 
+# library(dplyr)
+# library(estimatr)
+# library(tidyverse)
+# library(ggplot2)
+# library(stats)
+# library(cowplot)
 
-library(dplyr)
-library(estimatr)
-library(tidyverse)
-library(ggplot2)
-library(stats)
-library(cowplot)
+share of beneficiaries with improved self-worth
 
-###total trips subsidy real 
+share of beneficiaries with broadened everyday expertise
 
-realTripsSubTotal <- mergedData %>% 
-  group_by(year)%>%
-  dplyr::summarize(total_TripsSubsidy=sum(realTripsSubsidy, na.rm = TRUE))%>%
-  dplyr::filter(!(total_TripsSubsidy == 0.0))
+share of beneficiaries who are less frequently ill 
 
+share of beneficiaries with expanded dietary knowledge 
 
-#plot the linear time trend of total real trips subsidy trend with ggplot 
-totalRealTripSub <- ggplot(realTripsSubTotal, aes(year, total_TripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x = "Year", y = "Trips, total")
+share of beneficiaries with increased appreciation for a healthy diet 
 
-###median trips subsidy real 
+realSubsidy: subsidy for Meals program in 2015 EUR 
 
-medianRealTripsSubTotal <- mergedData %>%
-  group_by(year)%>%
-  dplyr::summarize(Median_TripsSubsidy=median(realTripsSubsidy, na.rm = TRUE))%>%
-  dplyr::filter(!(Median_TripsSubsidy == 0.0))
+realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR
 
-#plot the linear time trend of median real trips subsidy trend with ggplot 
-medianRealTripSub <- ggplot(medianRealTripsSubTotal, aes(year, Median_TripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x= "Year", y = "Trips, median")
+realTripsSubsidy: subsidy for Trips program in 2015 EUR
 
-#total lunch subsidy 
-realSubTotal <- mergedData %>% 
-  group_by(year)%>%
[…]

### 2020-02-27 paper.Rnw

@@
 \begin{figure}
-  \caption{Trend in everyday expertise and selfworth}
+  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
   \label{LineDisp}
@@
 Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+The possible values are: all, most, some, few, and none.
 For this figure, we use the original ordinal varibles which result from the survey structure.
@@
 \floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the year.
-The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
 \end{figure}
 
-In Figure \ref{Health_timeplots}, for the variable 'lessIll', there is much non available data.
-In all years, most organizations say that most beneficiaries are more healthy (3).
-The least stated category is, that all beneficiaries are less ill(4).
-That few are less ill (1), appears sometimes and the leftover category,none (0), which is only coded for the variable 'lessIll', appears as good as never.
-
-In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge') mostorganizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
-The least stated category is that some beneficiaries increased their dietary knowledge (2).
-The leftover category, few (1), does not appear.
-
-The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy'.
-Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet (3).
-The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet (4).
-The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet (2).
+In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill).
+In all years, most organizations say that most beneficiaries are more healthy.
+The least stated category is, that all beneficiaries are less ill.
+That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.
+
+In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
+The least stated category is that some beneficiaries increased their dietary knowledge.
+The leftover category, few, does not appear.
+
+The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
+Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
+The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet.
+The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet.
 The leftover category, few, also does not appear.
 
-\subsection{Equality of opportunities releveant variables over time}
-
-In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
-These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
+\subsection{Selfworth and everyday expertise}
+
+In its yearly surveys, CHILDREN has always asked about the following two variables.
+These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise.
 Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+The possible values are: all, most, some, few, and none.
 As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.
@@
 \begin{figure}
-  \caption{Equality of opportunities over time}
+  \caption{Selfworth and everyday expertise over time}
   \label{Equality_timeplots}
@@
 @
-\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
-These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
-The x-axis plots the year.
-The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
+\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables.
+These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
 \end{figure}
 
-Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth.
-Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3).
-The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2).
+Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth).
+Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
+The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth.
 The leftover category, few, does not appear.
 
-In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).
+In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
 
@@
 
-In this section we use a simple linear model, as described in equation \ref{SimpleLinear Model}. We look at the association between:
+In this section we use a simple linear model, as described in equation \ref{SimpleLinearModel}. We look at the association between:
 
@@
   \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with improved self-worth}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with broadened everyday expertise}
    \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
@@
 lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
+lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
+lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
 lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
 
-texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\\\ %stars.}", caption.above = TRUE, 
-    label = "GrantsRegressionsLunch", booktabs = TRUE)
+texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
 @
@@
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+lm_ts_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
 lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
+lm_ts_o_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex_control.lm.Rds")
 lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips
 
-texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips', digits = 4)
+texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE)
 @
@@
 In their surveys, CHILDREN asks about two variables in both programs.
-These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise.
+These are the share of beneficiaries with improved self-worth and share of beneficiaries with broadened everyday expertise.
 This feature could potentially allow us to compare the two programs regarding their realtive effectiveness.
@@
 
-texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
+texreg(list(ss, tss, ssI, tssI ), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
 @
@@
 
-texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
+texreg(list(ds, tds, dsI, tdsI ), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
 
@@
 This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
+https://www.schuleplusessen.de/startseite/
 
 In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
-These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
-
-Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
+These are the shares of beneficiaries who are less frequently ill, with expanded dietary knowledge and with increased appreciation for a healthy diet.
+
+Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
+For these results, we use their ordinal values.
 The x-axis displays the index for a healthy diet.
@@
 For example, if an organization says that most beneficiaries are healthier, then this would be coded as most.
-The highest amount of healthy criteria to be fulfilled is x.
+In the last reporting period, there are 13 healthy diet criteria.
+In previous years there were up to 15.
+The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not.
+The healthy food incex is calculated as the number of fulfilled criteria.
+Examples for criteria are daily carbohydrates or daily vegetables.
 
 All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria.
-The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constituted a healthy diet.
+The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
 It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
@@
 @
-\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu.
 It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
@@
 In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the index for a healthy diet.
-The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
+These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
 \end{figure}
@@
 We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
+By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.
 
 In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
-An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations.
+An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations.
 Regressing with the imputed dataset, results decrease by about 0.1.
 Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
+
+An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.
+
+In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
+For the original data set, the coeffiecent is slightly negative.
+Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
+This coefficent is as well insignifacant.
+
+In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger.
+For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
+When using WLS, we find a slightly negative association.
+A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02.
+This coefficent is not significant.
+For the imputed dataset we find a similar picture.
+
+The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.
 
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = "HealthRegressions-LessIll")
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
 @
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-DietaryKnowledge')
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS  \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
 @
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-AppreciateHealthy')
-@
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
+@
+
+The previous simple linear models are regressed with metric versions of the survey varibales.
+Originally, variables which range from none to all are ordinal.
+To account for this, we present a method to regress those variables according to their original traits.
+Therefore, we use a cumulative logit model.
+Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
 
@@
 \subsection{Factor Analysis}
+
+Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millenstein.2020, p.677}.
 
@@
 
-texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'expandLessIll')
+texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable is less ill \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
 @
@@
 \label{PropoddsModel}
-  P(Y_i \leq \ r) = \frac{exp(y_0_r + x_i^Ty)}{1+exp(y_0_r + x_i^Ty)}    
+  P(Y_i \leq \ r) = \frac{exp(y_{0r} + x_i^Ty)}{1+exp(y_{0r} + x_i^Ty)}    
 \end{equation}
@@
 
-According to the researchers, potential benefits of reducing dimensionality are reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{} (p.677).
-
 The partition approach partitions data into subsets of related features.
 It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \cite{} (p.676).
+By that, it defines a surjective mapping \cite{Millenstein.2020, p.676}.
 A function g is implemented using the arithmetic mean.
@@
 What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced.\cite{}(p.677)
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \cite{Millenstein.2020, p.677}.
 

### 2020-02-27 paper.Rnw
lg

--- 2020-02-27 paper.Rnw
@@
 
-\subsection{Previous research}
+\subsection{Literature overview}
 
-The previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
@@
 al.
-(2015) found by experiments in Germany, that children of higher educated parents are signficantly more patient.
-Children from parents with lower income and lower educational attainment typically have a lower weight at birth and are born in a later week of gestation, which are indicators for good initial conditions (Deckers et.
+(2015) found by experiments in Germany, that children of higher educated parents are significantly more patient.
+Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et.
 al.
@@
 2002).
-Children that grow up in families with a low socio-economic status are often less mobile and more likely to keep to themselves.
+Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
 This could have a negative influence on their character development.
@@
 (2020) provides causal evidence on the effect of social environment on prosocial attitudes.
-Being supported by a mentor could have a significant and persistant increase of elementary school children´s prosociality, in response to prosocial role models and intense social interactions.
-As investigated by Heckmann et.
+Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
+Heckmann et.
 al.
-(2010) for a preschool education program in the US, investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+(2010) investigated a preschool education program in the US.
+He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
 

### 2020-02-27 paper.tex
lg

@@
 
-\subsection{Previous research}
-
-The previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+\subsection{Literature overview}
+
+Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM
+% Date and time: Do, Feb 27, 2020 - 17:09:29
 \begin{table}[!htbp] \centering 
@@
  [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            
+ [3] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
  [4] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 [22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Thu, Feb 27, 2020 - 2:46:58 PM"                                                            
+[23] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
 [24] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 2:47:06 PM
+% Date and time: Do, Feb 27, 2020 - 17:09:35
 % Requires LaTeX packages: dcolumn rotating 
@@
 \hline
-R$^2$                     & 0.51          & 0.73         & 0.09         & 0.22       \\
-Adj. R$^2$                & 0.39          & 0.66         & 0.07         & 0.20       \\
-Num. obs.                 & 88            & 88           & 175          & 175        \\
-RMSE                      & 0.73          & 5.62         & 0.94         & 7.77       \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+R$^2$                     & $0.51$        & $0.73$       & $0.09$       & $0.22$     \\
+Adj. R$^2$                & $0.39$        & $0.66$       & $0.07$       & $0.20$     \\
+Num. obs.                 & $88$          & $88$         & $175$        & $175$      \\
+RMSE                      & $0.73$        & $5.62$       & $0.94$       & $7.77$     \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
 \end{tabular}
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 2:47:07 PM
+% Date and time: Do, Feb 27, 2020 - 17:09:35
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 2:47:08 PM
+% Date and time: Do, Feb 27, 2020 - 17:09:35
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 2:47:08 PM
+% Date and time: Do, Feb 27, 2020 - 17:09:35
 \begin{table}[!htbp] \centering 
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): invalid 'digits' argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
 
 \subsection{A4: OLS Regressions}
-
-#normal weights selfworth& subsidiy
 

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R

@@ -60,47 +60,115 @@ ggplot(df_monthlyCooks_control, aes(Year, EverydayExpertise)) + geom_line()
 #erstellen der ggplots
 library(ggpubr)
 
-#dayToDaySkills
+###dayToDaySkills
 
 ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
-  geom_point() + geom_line(color = "grey0") + 
-  geom_point(data = df_dayToDaySkills_control, color = "grey") + 
-   geom_line(data = df_dayToDaySkills_control, linetype = "dotted", color = "grey10") +
+  geom_point(color="red") + geom_line(color = "red") + 
+  geom_point(data = df_dayToDaySkills_control, color = "blue") + 
+  geom_line(data = df_dayToDaySkills_control, linetype = "dotted", color = "blue") +
   grids(axis = c("x"), color = "grey92", size = NULL, linetype = NULL) +
-  geom_smooth(method = "lm", se = FALSE, color = "grey0") +
-  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "grey") +
-  ggtitle("Trend of everyday expertise") + ylab("Everyday Expertise")
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "blue") +
+  ggtitle("Trend Of Everyday Expertise") +
+  theme(plot.title = element_text(hjust = 0.5)) + ylab("Everyday Expertise")
   
+##speichern
 
-
-#versuch, legende hinzuzufügen
-
-
-ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
-  geom_point() + 
-  geom_line(color = "grey0", aes(x=Year, y=EverydayExpertise, color="Treatment")) + 
-  geom_point(data = df_dayToDaySkills_control, color = "grey") + 
-  geom_line(data = df_dayToDaySkills_control, 
-            linetype = "dotted", color = "grey10", aes(x=Year, y=EverydayExpertise, color="Control")) +
+plot_dtds <- ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
+  geom_point(color="red") + geom_line(color = "red") + 
+  geom_point(data = df_dayToDaySkills_control, color = "blue") + 
[…]

### 2020-02-27 paper.Rnw
xxx

--- 2020-02-27 paper.Rnw
@@
 Laura Huber\\
-\texttt{11111111}
+\texttt{11709507}
 \and
@@
 Yannick Zurl\\
-\texttt{11111111}
+\texttt{11701793}
 \and
@@
 
-\subsection{Literature overview}
-
-Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+\subsection{Previous research}
+
+The previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
@@
 al.
-(2015) found by experiments in Germany, that children of higher educated parents are significantly more patient.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et.
+(2015) found by experiments in Germany, that children of higher educated parents are signficantly more patient.
+Children from parents with lower income and lower educational attainment typically have a lower weight at birth and are born in a later week of gestation, which are indicators for good initial conditions (Deckers et.
 al.
@@
 2002).
-Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
+Children that grow up in families with a low socio-economic status are often less mobile and more likely to keep to themselves.
 This could have a negative influence on their character development.
@@
 (2020) provides causal evidence on the effect of social environment on prosocial attitudes.
-Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
-Heckmann et.
+Being supported by a mentor could have a significant and persistant increase of elementary school children´s prosociality, in response to prosocial role models and intense social interactions.
+As investigated by Heckmann et.
 al.
-(2010) investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+(2010) for a preschool education program in the US, investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
 
@@
 
-<<FundamentalDynamicsTest, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 # 
@@
 # print(fundamental_dynamics, include.rownames = FALSE)
-@
+# @
 
@@
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
+\section{The effects of the trips program on participating beneficiaries}
+
+How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially?
 So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
-Empirical Approach\\
-
-The baseline of the empirical approach is the determination of the treatment and control group.
-Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
-On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
-
-Determining the treatment and control group this way, however, was a problem.
-
-THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
-We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
-All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
-Our analysis is based on this very strong definition of the treatment and control group.
-
-Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
-THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
-
-As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
-Therefore we have to use the survey answers from the Mittagstisch survey.
-
-Generally our data set contains variables from the years 2011 until 2018.
-
-The constellation of the treatment and control group varies from year to year. 
-Assumption: erhalten der treatment gleichbedeutend wie ein verlust
-
-Possible variables as dependent variables
-how we determined that:
-The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
-possible variables selfworth, day to day skills
-used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
-
-looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
-
-linear regression just to look at whether there are effects
-
-add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
-how fixed effects are implemented
-
-which control variables we use
-how we determined which controls
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{l c}
-% \hline
-%  & Selfworth \\
-% \hline
-% (Intercept)             & $-1.13^{***}$ \\
-%                         & $(0.32)$      \\
-% dfcEF2$treatEF          & $-0.47$       \\
-%                         & $(0.31)$      \\
-% \hline
-% Num. obs.               & $430$         \\
-% R$^2$ (full model)      & $0.47$        \\
-% R$^2$ (proj model)      & $0.47$        \\
-% Adj. R$^2$ (full model) & $0.36$        \\
-% Adj. R$^2$ (proj model) & $0.36$        \\
-% \hline
-% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-% \end{tabular}
-% \caption{linear regression}
-% \label{table:coefficients}
-% \end{center}
-% \end{table}
-
-Ende??
-the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
-
-<<selfworth_tripsProgram, echo=FALSE, results='asis', message=FALSE>>=
-
-# first, read in all Rds objects that you need
-
-lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
-lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
-lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
-lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
-
-table1_selfworth <- stargazer(lm1_selfworth,
-                    lm2_selfworth,
-                    lm3_selfworth,
-                    lm4_selfworth,
-          title = "Regression Results",
-          order = c('Constant', 'treatEF'),
-          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-                   'dummy_2018', 'id'
-                  ),
-          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-          align = TRUE,
-
-          # this line of code rotates the table by 90 degrees counterclockwise
-
-          float.env = "sidewaystable")
-@
+Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program.
+However, not all organizations receive additional funding to provide the trips program.
+This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group.
+The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+
+\subsection{Empirical Approach}
+
+The basis of the empirical approach is the specification of the treatment and the control group.
+Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program.
+On the other hand, the control group represents all organizations that only receive funding for the meals program.
+Therefore, the social institutions in the control group do not participate in the trips program.
+
+\subsubsection{Specification of the Treatment Group}
+
+When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program.
+As previously mentioned, the CHILDREN survey consists of two parts.
+The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program.
+The dataset shows that there are several organizations that did not provide information regarding the trips program.
+In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
+Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group.
+When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey.
+There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year.
+Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
+Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.
+
+Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
+This implies that an organization remains in the control group as long as it does not receive funding for the trips program.
+Due to this definition, an organization cannot change from the treatment into the control group.
+
+In general, the constellation of the treatment and control group varies across years.
+As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
+At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods.
+In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
+However, the dataset also includes organizations that switch from the treatment to the control group.
+The first definition of the treatment variable does not take this case into account.
+Therefore, we additionally construct a second treatment indicator which is defined as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
+With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
+Consequently, the estimates cannot be very robust.
+Therefore, the results should not be overstated.
+
+\subsubsection{Dependent Variables}
+
+The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group.
+However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group.
+Therefore, we have to use variables of the meals program as outcome variables in our analysis.
+For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
+Firstly, both variables are applicable to the trips program as well as the meals program.
+In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
+
+\subsubsection{Graphical Evidence}
+
+To check for differences in treatment and control group, we created the following graphs using descriptive statistics.
+The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time while it decreased in the control group.
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group.
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+\subsubsection{Differences-in-Differences Estimation}
+
+For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children.
+The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group.
+The key identifying assumption for the DID strategy is the common trend assumption.
+The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
+In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
+As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend.
+Therefore, we cannot argue that the common trend assumption is fulfilled.
+
+Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
+\begin{equation}
+\label{didregression}
+  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
+\end{equation}
+
+where \begin{itshape}{i}\end{itshape} indexes the identification number of each organization supported by CHILDREN and \begin{itshape}{t}\end{itshape} indexes the year of observation.
+The outcome variable, denoted by \begin{itshape}Y_{it}\end{itshape}, is either selfworth or everyday expertise.
+As mentioned in the previous section, \begin{itshape}TreatEF_{it}\end{itshape} represents the treatment status of organization \begin{itshape}{i}\end{itshape} in year \begin{itshape}{t}\end{itshape}.
+The corresponding regression coefficient \begin{itshape}\beta\end{itshape} represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+
+The panel data set allows us to implement fixed effects.
+In our analysis we introduce individual fixed effects and time fixed effects.
+The ID fixed effects \begin{itshape}\gamma_{i}\end{itshape} control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
+For example, the state of an organization does not vary over time but might differ across supported social institutions.
+Additionally, the year fixed effects \begin{itshape}\delta_{t}\end{itshape} capture all variables that change across years but are the same for all organizations and within a specific year.
+For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
+
+One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics.
+Therefore, we include a set of control variables to deal with potential selection bias.
+For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
+Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
+
+\subsection{Results}
+
+\subsubsection{Everyday Expertise}
+
+The estimated coefficients of equation XX are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
+Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
+Columns (1) and (3) only include ID fixed effects and year fixed effects without any controls.
+Columns (2) and (4) expand the regression equation by adding the organization specific control variables: Subsidy, total costs and the number of days in a week on which children cook in a social institution.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.326)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.014)$    &           & $(0.014)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.000)$    &           & $(0.000)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Everyday Expertise}
+\label{table:coefficients1}
+\end{center}
+\end{table}
+
+Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
+Therefore, this finding should not be overstated.
+On the other hand, using the alternative specification of the treatment indicator in column (3), the average treatment effect is positive, but remains insignificant.
+Thus, the sign of the estimated treatment effect changes if we use the alternative definition of the treatment variable.
+With the second treatment variable, the number of organizations in the control group increases, as the treatment status depends on actually receiving funding in a given year.
+Nevertheless, the difference in size of the treatment and control group remains relatively large.
+However, the estimate in Column (3) could provide evidence that the treatment effect might be positive and potentially turn significant if the sample size increases.
+
+Adding the organization specific control variables in Column (2) and Column (4) does not influence the size of both effects and the significance substantially.
+
+\subsubsection{Selfworth}
+
+Using selfworth as the outcome variable, the estimates of regression equation \ref{didregression} are reported in Table \ref{table:coefficients2}, whose structure is equal to Table \ref{table:coefficients1}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.018)$ &           & $(0.017)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.001)$ &           & $(0.001)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.069)$ &           & $(0.069)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Selfworth}
+\label{table:coefficients2}
+\end{center}
+\end{table}
+
+Strinkinlgy, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
+In column (1)-(3), the average treatment effect is insignificant.
+However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
+This indicates that participating in the trips program would negatively influence the selfworth of the children and adolescents.
+This surprising result contradicts our hypothesis that the participation in the trips program positively influences the selfworth of the beneficiaries.
+As previously mentioned, the number of observation units in both treatment and control group is relatively small.
+Therefore, this unexpected negative effect of the trips program on selfworth should not be overstated.
+Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
+It might be difficult for the respondents of the survey to assess children specific characteristics, such as selfworth.
+During our visit in Augsburg, the employees confirmed that it is challenging to evaluate the variables asked in the survey for all participants in the entire social institution, especially with a lot of variation in attendance.
+One potential solution for this problem could be to directly ask the children and adolescents.
+Data on the individual level might be more precise because the children could assess themselves better.
+When using variables on the level of beneficiaries, we might observe a positive effect of the trips program on selfworth.
+As reported in the summary statistics, the outcome variable shows a low variation.
+This results from the fact that, most of the time, organizations give the answer “all children” and “most children” when asked about the improvement of children’s selfworth.
+In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
+In the survey of the year 2019, CHILDREN already implemented a wider scale by asking for the percentage of beneficiaries that increased their selfworth.
+As this alternative measuring method is more precise, it might result in a higher variation of answers.
+Therefore, finding significant effects of the trips program on selfworth might be more likely.
 
@@
 
+% #normal weights selfworth& subsidiy
 % <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
+#normal weights selfworth& subsidiy
 <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
+\subsection{A5: DID Regression Results}
+
+The estimated coefficients of equation \ref{didregression} are represented in Table \ref{table:coefficients3} with everyday expertise as the dependent variable and in Table \ref{table:coefficients4} with selfworth as the dependent variable.
+P-values are in parentheses.
+We observe decreasing p-values when using the second definition of the treatment variable.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.975)$ & $(0.681)$    & $(0.409)$ & $(0.410)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.181)$    &           & $(0.258)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.048)$    &           & $(0.060)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.022)$    &           & $(0.027)$    \\
+\hline
+ID fixed effects       & $YES$     & $YES$        & $YES$     & $YES$        \\
+Year fixed effects     & $YES$     & $YES$        & $YES$     & $YES$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation 1}
+\label{table:coefficients3}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.126)$ & $(0.125)$ & $(0.185)$ & $(0.085)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.540)$ &           & $(0.422)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.575)$ &           & $(0.446)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.609)$ &           & $(0.591)$    \\
+\hline
+ID fixed effects       & $YES$     & $YES$     & $YES$     & $YES$        \\
+Year fixed effects     & $YES$     & $YES$     & $YES$     & $YES$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation 2}
+\label{table:coefficients4}
+\end{center}
+\end{table}
+
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-27 paper.tex
xxx

@@
 
+# <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+# 
+# # first, read in all Rds objects that you need
+# 
+# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
+#  
+# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+# 
+# fundamental_dynamics <- xtable(fundamental_dynamics,
+#                                digits = c(0, 0, 1, 1, 0, 0),
+#           caption = "Summary Statistics",
+#           align = "lmmmmm", 
+#           label = "fundamentalDynamics"
+#           )
+# print(fundamental_dynamics, include.rownames = FALSE)
+# @
+
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:29
+% Date and time: Do., Feb 27, 2020 - 17:16:13
 \begin{table}[!htbp] \centering 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:29
+% Date and time: Do., Feb 27, 2020 - 17:16:13
 \begin{table}[!htbp] \centering 
@@
  [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
+ [3] "% Date and time: Do., Feb 27, 2020 - 17:16:13"                                                              
  [4] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 [22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
+[23] "% Date and time: Do., Feb 27, 2020 - 17:16:13"                                                              
 [24] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
+\section{The effects of the trips program on participating beneficiaries}
+
+How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially?
 So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
-Empirical Approach\\
-
-The baseline of the empirical approach is the determination of the treatment and control group.
-Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
-On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
-
-Determining the treatment and control group this way, however, was a problem.
-
-THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
-We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
-All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
-Our analysis is based on this very strong definition of the treatment and control group.
-
-Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
-THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
-
-As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
-Therefore we have to use the survey answers from the Mittagstisch survey.
-
-Generally our data set contains variables from the years 2011 until 2018.
-
-The constellation of the treatment and control group varies from year to year. 
-Assumption: erhalten der treatment gleichbedeutend wie ein verlust
-
-Possible variables as dependent variables
-how we determined that:
-The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
-possible variables selfworth, day to day skills
-used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
-
-looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
-
-linear regression just to look at whether there are effects
-
-add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
-how fixed effects are implemented
-
-which control variables we use
-how we determined which controls
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{l c}
-% \hline
-%  & Selfworth \\
-% \hline
-% (Intercept)             & $-1.13^{***}$ \\
-%                         & $(0.32)$      \\
-% dfcEF2$treatEF          & $-0.47$       \\
-%                         & $(0.31)$      \\
-% \hline
-% Num. obs.               & $430$         \\
-% R$^2$ (full model)      & $0.47$        \\
-% R$^2$ (proj model)      & $0.47$        \\
-% Adj. R$^2$ (full model) & $0.36$        \\
-% Adj. R$^2$ (proj model) & $0.36$        \\
-% \hline
-% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-% \end{tabular}
-% \caption{linear regression}
-% \label{table:coefficients}
-% \end{center}
-% \end{table}
-
-Ende??
-the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
-% Requires LaTeX packages: dcolumn rotating 
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Regression Results} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program.
+However, not all organizations receive additional funding to provide the trips program.
+This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group.
+The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+
+\subsection{Empirical Approach}
+
+The basis of the empirical approach is the specification of the treatment and the control group.
+Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program.
+On the other hand, the control group represents all organizations that only receive funding for the meals program.
+Therefore, the social institutions in the control group do not participate in the trips program.
+
+\subsubsection{Specification of the Treatment Group}
+
+When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program.
+As previously mentioned, the CHILDREN survey consists of two parts.
+The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program.
+The dataset shows that there are several organizations that did not provide information regarding the trips program.
+In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
+Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group.
+When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey.
+There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year.
+Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
+Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.
+
+Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
+This implies that an organization remains in the control group as long as it does not receive funding for the trips program.
+Due to this definition, an organization cannot change from the treatment into the control group.
+
+In general, the constellation of the treatment and control group varies across years.
+As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
+At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods.
+In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
+However, the dataset also includes organizations that switch from the treatment to the control group.
+The first definition of the treatment variable does not take this case into account.
+Therefore, we additionally construct a second treatment indicator which is defined as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
+With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
+Consequently, the estimates cannot be very robust.
+Therefore, the results should not be overstated.
+
+\subsubsection{Dependent Variables}
+
+The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group.
+However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group.
+Therefore, we have to use variables of the meals program as outcome variables in our analysis.
+For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
+Firstly, both variables are applicable to the trips program as well as the meals program.
+In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
+
+\subsubsection{Graphical Evidence}
+
+To check for differences in treatment and control group, we created the following graphs using descriptive statistics.
+The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time while it decreased in the control group.
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group.
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+\subsubsection{Differences-in-Differences Estimation}
+
+For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children.
+The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group.
+The key identifying assumption for the DID strategy is the common trend assumption.
+The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
+In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
+As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend.
+Therefore, we cannot argue that the common trend assumption is fulfilled.
+
+Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
+\begin{equation}
+\label{didregression}
+  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
+\end{equation}
+
+where \begin{itshape}{i}\end{itshape} indexes the identification number of each organization supported by CHILDREN and \begin{itshape}{t}\end{itshape} indexes the year of observation.
+The outcome variable, denoted by \begin{itshape}Y_{it}\end{itshape}, is either selfworth or everyday expertise.
+As mentioned in the previous section, \begin{itshape}TreatEF_{it}\end{itshape} represents the treatment status of organization \begin{itshape}{i}\end{itshape} in year \begin{itshape}{t}\end{itshape}.
+The corresponding regression coefficient \begin{itshape}\beta\end{itshape} represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+
+The panel data set allows us to implement fixed effects.
+In our analysis we introduce individual fixed effects and time fixed effects.
+The ID fixed effects \begin{itshape}\gamma_{i}\end{itshape} control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
+For example, the state of an organization does not vary over time but might differ across supported social institutions.
+Additionally, the year fixed effects \begin{itshape}\delta_{t}\end{itshape} capture all variables that change across years but are the same for all organizations and within a specific year.
+For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
+
+One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics.
+Therefore, we include a set of control variables to deal with potential selection bias.
+For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
+Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
+
+\subsection{Results}
+
+\subsubsection{Everyday Expertise}
+
+The estimated coefficients of equation XX are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
+Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
+Columns (1) and (3) only include ID fixed effects and year fixed effects without any controls.
+Columns (2) and (4) expand the regression equation by adding the organization specific control variables: Subsidy, total costs and the number of days in a week on which children cook in a social institution.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
 \\[-1.8ex]\hline
-\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\
 \cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-\hline \\[-1.8ex] 
- Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
-  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
-  & & & & \\ 
- treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
-  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-ID fixed effects & No & No & Yes & Yes \\ 
-Time fixed effects & No & Yes & No & Yes \\ 
-Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
-R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
-Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
-Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
-F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{sidewaystable}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.326)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.014)$    &           & $(0.014)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.000)$    &           & $(0.000)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Everyday Expertise}
+\label{table:coefficients1}
+\end{center}
+\end{table}
+
+Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
+Therefore, this finding should not be overstated.
+On the other hand, using the alternative specification of the treatment indicator in column (3), the average treatment effect is positive, but remains insignificant.
+Thus, the sign of the estimated treatment effect changes if we use the alternative definition of the treatment variable.
+With the second treatment variable, the number of organizations in the control group increases, as the treatment status depends on actually receiving funding in a given year.
+Nevertheless, the difference in size of the treatment and control group remains relatively large.
+However, the estimate in Column (3) could provide evidence that the treatment effect might be positive and potentially turn significant if the sample size increases.
+
+Adding the organization specific control variables in Column (2) and Column (4) does not influence the size of both effects and the significance substantially.
+
+\subsubsection{Selfworth}
+
+Using selfworth as the outcome variable, the estimates of regression equation \ref{didregression} are reported in Table \ref{table:coefficients2}, whose structure is equal to Table \ref{table:coefficients1}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.018)$ &           & $(0.017)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.001)$ &           & $(0.001)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.069)$ &           & $(0.069)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Selfworth}
+\label{table:coefficients2}
+\end{center}
+\end{table}
+
+Strinkinlgy, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
+In column (1)-(3), the average treatment effect is insignificant.
+However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
+This indicates that participating in the trips program would negatively influence the selfworth of the children and adolescents.
+This surprising result contradicts our hypothesis that the participation in the trips program positively influences the selfworth of the beneficiaries.
+As previously mentioned, the number of observation units in both treatment and control group is relatively small.
+Therefore, this unexpected negative effect of the trips program on selfworth should not be overstated.
+Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
+It might be difficult for the respondents of the survey to assess children specific characteristics, such as selfworth.
+During our visit in Augsburg, the employees confirmed that it is challenging to evaluate the variables asked in the survey for all participants in the entire social institution, especially with a lot of variation in attendance.
+One potential solution for this problem could be to directly ask the children and adolescents.
+Data on the individual level might be more precise because the children could assess themselves better.
+When using variables on the level of beneficiaries, we might observe a positive effect of the trips program on selfworth.
+As reported in the summary statistics, the outcome variable shows a low variation.
+This results from the fact that, most of the time, organizations give the answer “all children” and “most children” when asked about the improvement of children’s selfworth.
+In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
+In the survey of the year 2019, CHILDREN already implemented a wider scale by asking for the percentage of beneficiaries that increased their selfworth.
+As this alternative measuring method is more precise, it might result in a higher variation of answers.
+Therefore, finding significant effects of the trips program on selfworth might be more likely.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do., Feb 27, 2020 - 17:16:18
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do., Feb 27, 2020 - 17:16:19
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do., Feb 27, 2020 - 17:16:19
 \begin{table}[!htbp] \centering 
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
 
 \subsection{A4: OLS Regressions}
+
+#normal weights selfworth& subsidiy
 

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R
xxxx

@@ -60,33 +60,115 @@ ggplot(df_monthlyCooks_control, aes(Year, EverydayExpertise)) + geom_line()
 #erstellen der ggplots
 library(ggpubr)
 
-#dayToDaySkills
+###dayToDaySkills
 
 ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
-  geom_point() + geom_line(color = "grey0") + 
-  geom_point(data = df_dayToDaySkills_control, color = "grey") + 
-   geom_line(data = df_dayToDaySkills_control, linetype = "dotted", color = "grey10") +
+  geom_point(color="red") + geom_line(color = "red") + 
+  geom_point(data = df_dayToDaySkills_control, color = "blue") + 
+  geom_line(data = df_dayToDaySkills_control, linetype = "dotted", color = "blue") +
   grids(axis = c("x"), color = "grey92", size = NULL, linetype = NULL) +
-  geom_smooth(method = "lm", se = FALSE, color = "grey0") +
-  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "grey") +
-  ggtitle("Trend of everyday expertise") + ylab("Everyday Expertise") 
-
-
-
-
-
-
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "blue") +
+  ggtitle("Trend Of Everyday Expertise") +
+  theme(plot.title = element_text(hjust = 0.5)) + ylab("Everyday Expertise")
   
+##speichern
+
+plot_dtds <- ggplot(df_dayToDaySkills_treat, aes(Year, EverydayExpertise)) + 
+  geom_point(color="red") + geom_line(color = "red") + 
+  geom_point(data = df_dayToDaySkills_control, color = "blue") + 
+  geom_line(data = df_dayToDaySkills_control, linetype = "dotted", color = "blue") +
+  grids(axis = c("x"), color = "grey92", size = NULL, linetype = NULL) +
+  geom_smooth(method = "lm", se = FALSE, color = "red") +
+  geom_smooth(data =df_dayToDaySkills_control, method="lm", se = FALSE, color = "blue") +
+  ggtitle("Trend Of Everyday Expertise") +
[…]

### 2020-02-27 ANALYSIS/SummaryStatistics_ggplot.R

@@ -1,3 +1,120 @@
+<<<<<<< HEAD:ANALYSIS/Summary Statistics with ggplot.R
+# #Real Subsidy Time Trend Total & Median
+# 
+# library(dplyr)
+# library(estimatr)
+# library(tidyverse)
+# library(ggplot2)
+# library(stats)
+# library(cowplot)
+
+share of beneficiaries with improved self-worth
+
+share of beneficiaries with broadened everyday expertise
+
+share of beneficiaries who are less frequently ill 
+
+share of beneficiaries with expanded dietary knowledge 
+
+share of beneficiaries with increased appreciation for a healthy diet 
+
+realSubsidy: subsidy for Meals program in 2015 EUR 
+
+realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR
+
+realTripsSubsidy: subsidy for Trips program in 2015 EUR
+
+realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR
+
+DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu
+
+eatersPerMeal: number of beneficiaries of Lunch program 
+
+tripsKidsNo: number of beneficiaries of Trips program
+
+
+
+
+
+
+
+# 
+# ###total trips subsidy real 
+# 
+# realTripsSubTotal <- mergedData %>% 
+#   group_by(year)%>%
+#   dplyr::summarize(total_TripsSubsidy=sum(realTripsSubsidy, na.rm = TRUE))%>%
+#   dplyr::filter(!(total_TripsSubsidy == 0.0))
+# 
+# 
+# #plot the linear time trend of total real trips subsidy trend with ggplot 
+# totalRealTripSub <- ggplot(realTripsSubTotal, aes(year, total_TripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x = "Year", y = "Trips, total")
+# 
+# ###median trips subsidy real 
+# 
+# medianRealTripsSubTotal <- mergedData %>%
+#   group_by(year)%>%
+#   dplyr::summarize(Median_TripsSubsidy=median(realTripsSubsidy, na.rm = TRUE))%>%
+#   dplyr::filter(!(Median_TripsSubsidy == 0.0))
+# 
+# #plot the linear time trend of median real trips subsidy trend with ggplot 
[…]

### 2020-02-27 paper.Rnw
lg

--- 2020-02-27 paper.Rnw
@@
 The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
-The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid red line, the answers from the control group by the dotted blue line.
 Additionally, the linear trends of both groups are included as the straight lines.}

### 2020-02-27 paper.tex
lg

--- 2020-02-27 paper.tex
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:29
+% Date and time: Do, Feb 27, 2020 - 17:23:17
 \begin{table}[!htbp] \centering 
@@
  [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
+ [3] "% Date and time: Do, Feb 27, 2020 - 17:23:17"                                                               
  [4] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 [22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Do, Feb 27, 2020 - 17:09:29"                                                               
+[23] "% Date and time: Do, Feb 27, 2020 - 17:23:17"                                                               
 [24] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 \end{knitrout}
-\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
-These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
-The x-axis plots the year.
-The y-axis displays the share of organizarions in each category of the health outcome.
-The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
-For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
+\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables.
+These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
 \end{figure}
 
-Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth.
-Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3).
-The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2).
+Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth).
+Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
+The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth.
 The leftover category, few, does not appear.
 
-In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).
+In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
 
@@
 \begin{table}
-\caption{Regression Results: Number of meals}
+\caption{Association between number of meals and real subsidy}
 \begin{center}
 \scalebox{0.8}{
-\begin{tabular}{l c c c}
+\begin{tabular}{l c c c c c}
 \toprule
- & OLS & OLS without Outliers & OLS Impute \\
+ & (1) & (2) & (3) & (4) & (5) \\
 \midrule
-(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
-            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
-realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
-            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
+(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
+                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
+realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
+                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
+eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
+                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
 \midrule
-R$^2$       & $0.43$          & $0.13$          & $0.45$           \\
-Adj. R$^2$  & $0.43$          & $0.12$          & $0.45$           \\
-Num. obs.   & $329$           & $250$           & $440$            \\
-RMSE        & $39992.79$      & $3629.72$       & $39601.41$       \\
+R$^2$           & $0.43$          & $0.73$         & $0.13$          & $0.21$          & $0.45$           \\
+Adj. R$^2$      & $0.43$          & $0.73$         & $0.12$          & $0.20$          & $0.45$           \\
+Num. obs.       & $329$           & $329$          & $250$           & $250$           & $440$            \\
+RMSE            & $39992.79$      & $27390.90$     & $3629.72$       & $3463.66$       & $39601.41$       \\
 \bottomrule
-\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
-sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
-aliquyam. \\ $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \usepackage{graphicx}
+\usepackage{booktabs}
 
 \begin{table}
+\caption{Association between number of trips and real subsidy}
 \begin{center}
 \scalebox{0.8}{
-\begin{tabular}{l c c c}
-\hline
- & OLS & OLS without Outliers & OLS Impute \\
-\hline
-(Intercept)      & $3.7049^{***}$ & $2.6236^{***}$ & $3.6237^{***}$ \\
-                 & $(0.3313)$     & $(0.2300)$     & $(0.3253)$     \\
-realTripsSubsidy & $0.0002^{*}$   & $0.0003^{***}$ & $0.0002^{*}$   \\
-                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
-\hline
-R$^2$            & $0.0474$       & $0.0880$       & $0.0504$       \\
-Adj. R$^2$       & $0.0444$       & $0.0844$       & $0.0476$       \\
-Num. obs.        & $322$          & $257$          & $334$          \\
-RMSE             & $2.9565$       & $1.6981$       & $2.9310$       \\
-\hline
-\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Number of trips}
+\begin{tabular}{l c c c c c}
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
+                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
+\midrule
+R$^2$            & $0.0474$       & $0.0729$       & $0.0880$       & $0.1241$       & $0.0504$       \\
+Adj. R$^2$       & $0.0444$       & $0.0671$       & $0.0844$       & $0.1172$       & $0.0476$       \\
+Num. obs.        & $322$          & $319$          & $257$          & $256$          & $334$          \\
+RMSE             & $2.9565$       & $2.8967$       & $1.6981$       & $1.6579$       & $2.9310$       \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{GrantsRegressionsTrips}
@@
 \begin{table}
+\caption{Association between selfworth and subsidy per beneficiary}
 \begin{center}
@@
 \hline
- & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
+ & (1) & (2) & (3) & (4) \\
 \hline
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Selfworth}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{SelfworthRegressions}
@@
 \begin{table}
+\caption{Association between everyday expertise and subsidy per beneficiary}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: dayToDaySkills}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{DayToDaySkillsRegressions}
@@
 \end{knitrout}
-\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
+\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu.
 It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
@@
 We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
+By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.
 
 In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
-An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations.
+An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations.
 Regressing with the imputed dataset, results decrease by about 0.1.
@@
 
+An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.
+
+In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
+For the original data set, the coeffiecent is slightly negative.
+Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
+This coefficent is as well insignifacant.
+
+In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger.
+For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
+When using WLS, we find a slightly negative association.
+A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02.
+This coefficent is not significant.
+For the imputed dataset we find a similar picture.
+
+The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.
+
 \usepackage{graphicx}
@@
 \begin{table}
+\caption{Association between healthy meals criterion and beneficiaries being less ill}
 \begin{center}
@@
 \hline
- & OLS & WLS & OLS Impute & WLS Impute \\
+ & (1) & (2) & (3) & (4) \\
 \hline
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Less Ill}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{HealthRegressions-LessIll}
@@
 \begin{table}
+\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Dietary Knowledge}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{HealthRegressions-DietaryKnowledge}
@@
 \begin{table}
+\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-\end{tabular}
-}
-\caption{Regression Results: Appreciate Healthy}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+\end{tabular}
+}
 \label{HealthRegressions-AppreciateHealthy}
@@
 
+The previous simple linear models are regressed with metric versions of the survey varibales.
+Originally, variables which range from none to all are ordinal.
+To account for this, we present a method to regress those variables according to their original traits.
+Therefore, we use a cumulative logit model.
+Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
+
 \section{Feature Selection}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do, Feb 27, 2020 - 17:23:22
 % Requires LaTeX packages: dcolumn rotating 
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
+\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable is less ill \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do, Feb 27, 2020 - 17:23:22
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do, Feb 27, 2020 - 17:23:22
 \begin{table}[!htbp] \centering 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:09:35
+% Date and time: Do, Feb 27, 2020 - 17:23:23
 \begin{table}[!htbp] \centering 

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R

@@ -172,3 +172,17 @@ saveRDS(plot_dtds, "./ANALYSIS/GRAPHS/plot_dtds.Rds")
 saveRDS(plot_selfworth, "./ANALYSIS/GRAPHS/plot_selfworth.Rds")
 saveRDS(plot_weeklyCooks, "./ANALYSIS/GRAPHS/plot_weeklyCooks.Rds")
 saveRDS(plot_monthlyCooks, "./ANALYSIS/GRAPHS/plot_monthlyCooks.Rds")
+
+###plots zusammenfügen und speichern
+
+plot_dayToDaySkills_selfworth <- plot_grid(plot_dtds, plot_selfworth, 
+                          ncol = 2, nrow = 1, align = "h")
+
+plot_placebos <- plot_grid(plot_weeklyCooks, plot_monthlyCooks,
+                           ncol=2, nrow=1, align = "h")
+
+
+saveRDS(plot_dayToDaySkills_selfworth, "./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
+saveRDS(plot_placebos, "./ANALYSIS/GRAPHS/PAPER/plot_placebos.Rds")
+
+

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R
lg

@@ -175,7 +175,7 @@ saveRDS(plot_monthlyCooks, "./ANALYSIS/GRAPHS/plot_monthlyCooks.Rds")
 
 ###plots zusammenfügen und speichern
 
-plot_dayToDaySkills_selfworth <- plot_grid(plot_dtds, plot_selfworth, 
+plot_dayToDaySkills_selfworth <- plot_grid(plot_selfworth, plot_dtds, 
                           ncol = 2, nrow = 1, align = "h")
 
 plot_placebos <- plot_grid(plot_weeklyCooks, plot_monthlyCooks,
@@ -185,4 +185,5 @@ plot_placebos <- plot_grid(plot_weeklyCooks, plot_monthlyCooks,
 saveRDS(plot_dayToDaySkills_selfworth, "./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
 saveRDS(plot_placebos, "./ANALYSIS/GRAPHS/PAPER/plot_placebos.Rds")
 
-
+plot_dayToDaySkills_selfworth
+plot_placebos

### 2020-02-27 ANALYSIS/DATA/advanced_timeseries_ggplot.R
xx

@@ -172,3 +172,18 @@ saveRDS(plot_dtds, "./ANALYSIS/GRAPHS/plot_dtds.Rds")
 saveRDS(plot_selfworth, "./ANALYSIS/GRAPHS/plot_selfworth.Rds")
 saveRDS(plot_weeklyCooks, "./ANALYSIS/GRAPHS/plot_weeklyCooks.Rds")
 saveRDS(plot_monthlyCooks, "./ANALYSIS/GRAPHS/plot_monthlyCooks.Rds")
+
+###plots zusammenfügen und speichern
+
+plot_dayToDaySkills_selfworth <- plot_grid(plot_selfworth, plot_dtds, 
+                          ncol = 2, nrow = 1, align = "h")
+
+plot_placebos <- plot_grid(plot_weeklyCooks, plot_monthlyCooks,
+                           ncol=2, nrow=1, align = "h")
+
+
+saveRDS(plot_dayToDaySkills_selfworth, "./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
+saveRDS(plot_placebos, "./ANALYSIS/GRAPHS/PAPER/plot_placebos.Rds")
+
+plot_dayToDaySkills_selfworth
+plot_placebos

### 2020-02-27 paper.Rnw
xcxcx

--- 2020-02-27 paper.Rnw
@@
 
-If you want to cite \textcite{Millenstein.2020} inline, use this.
+If you want to cite \textcite{Millstein.2020} inline, use this.
 If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
-If you want to cite \citeauthor{Millenstein.2020} only as authors, use this.
+If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
 
@@
 texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable is less ill \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
+{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ regionalProducts: wether the organization offers meals with local ingredients or not \\\\ yearsSupportSince: the number of years an organization is already part of the Meals program \\\\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ state: german 'Bundeland' \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\\\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
 @
@@
 
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", align = TRUE, label = "lessIllOdds")
+stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Dietary Knowledge", align = TRUE, label = "dietaryOdds")
+stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge", align = TRUE, label = "dietaryOdds")
 @
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Appreciate Healthy", align = TRUE, label = "appreciateOdds")
+stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet", align = TRUE, label = "appreciateOdds")
 @
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Selfworth", align = TRUE, label = "selfworthOdds")
+stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth", align = TRUE, label = "selfworthOdds")
 @
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Everyday expertise", align = TRUE, label = "dayToDayOdds")
+stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise", align = TRUE, label = "dayToDayOdds")
 @
@@
 It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \cite{Millenstein.2020, p.676}.
+By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
 A function g is implemented using the arithmetic mean.
@@
 What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \cite{Millenstein.2020, p.677}.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
 

### 2020-02-27 paper.tex
xcxcx

@@
 The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
-The time trend of the average answers from the organizations in the treatment group is characterised by the solid red line, the answers from the control group by the dotted blue line.
+The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
 Additionally, the linear trends of both groups are included as the straight lines.}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:17
+% Date and time: Do, Feb 27, 2020 - 16:52:46
 \begin{table}[!htbp] \centering 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:17
+% Date and time: Do, Feb 27, 2020 - 16:52:47
 \begin{table}[!htbp] \centering 
@@
  [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Do, Feb 27, 2020 - 17:23:17"                                                               
+ [3] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
  [4] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 [22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Do, Feb 27, 2020 - 17:23:17"                                                               
+[23] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
 [24] "\\begin{table}[!htbp] \\centering "                                                                         
@@
 
-\usepackage{graphicx}
 \usepackage{booktabs}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c}
+\begin{tabular}{l c c c c c }
 \toprule
@@
 \midrule
-R$^2$           & $0.43$          & $0.73$         & $0.13$          & $0.21$          & $0.45$           \\
-Adj. R$^2$      & $0.43$          & $0.73$         & $0.12$          & $0.20$          & $0.45$           \\
-Num. obs.       & $329$           & $329$          & $250$           & $250$           & $440$            \\
-RMSE            & $39992.79$      & $27390.90$     & $3629.72$       & $3463.66$       & $39601.41$       \\
+R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
+Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
+Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
+RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \midrule
-R$^2$            & $0.0474$       & $0.0729$       & $0.0880$       & $0.1241$       & $0.0504$       \\
-Adj. R$^2$       & $0.0444$       & $0.0671$       & $0.0844$       & $0.1172$       & $0.0476$       \\
-Num. obs.        & $322$          & $319$          & $257$          & $256$          & $334$          \\
-RMSE             & $2.9565$       & $2.8967$       & $1.6981$       & $1.6579$       & $2.9310$       \\
+R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
+Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
+RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
-Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
-Num. obs.                      & $428$    & $184$    & $430$    & $187$    \\
-RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   \\
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
+Num. obs.                      & 428      & 184      & 430      & 187      \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \end{table}
-
-\usepackage{graphicx}
 
@@
 \hline
-R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
-Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
-Num. obs.                      & $426$    & $177$    & $429$    & $181$    \\
-RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   \\
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
+Num. obs.                      & 426      & 177      & 429      & 181      \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       \\
-Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       \\
-Num. obs.           & $121$        & $120$       & $177$        & $177$        \\
-RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       \\
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
+Num. obs.           & 121          & 120         & 177          & 177          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   \\
-Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   \\
-Num. obs.           & $214$    & $212$    & $275$      & $275$    \\
-RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   \\
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
+Num. obs.           & 214      & 212      & 275        & 275      \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     \\
-Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    \\
-Num. obs.           & $213$        & $211$    & $274$        & $274$      \\
-RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     \\
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
+Num. obs.           & 213          & 211      & 274          & 274        \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn rotating 
@@
 \hline
-R$^2$                     & $0.51$        & $0.73$       & $0.09$       & $0.22$     \\
-Adj. R$^2$                & $0.39$        & $0.66$       & $0.07$       & $0.20$     \\
-Num. obs.                 & $88$          & $88$         & $175$        & $175$      \\
-RMSE                      & $0.73$        & $5.62$       & $0.94$       & $7.77$     \\
+R$^2$                     & 0.51          & 0.73         & 0.09         & 0.22       \\
+Adj. R$^2$                & 0.39          & 0.66         & 0.07         & 0.20       \\
+Num. obs.                 & 88            & 88           & 175          & 175        \\
+RMSE                      & 0.73          & 5.62         & 0.94         & 7.77       \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable is less ill \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Less Ill} 
+  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
   \label{lessIllOdds} 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Dietary Knowledge} 
+  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
   \label{dietaryOdds} 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Appreciate Healthy} 
+  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
   \label{appreciateOdds} 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Selfworth} 
+  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
   \label{selfworthOdds} 
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Everyday expertise} 
+  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
   \label{dayToDayOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:22
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 \begin{table}[!htbp] \centering 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 17:23:23
+% Date and time: Do, Feb 27, 2020 - 16:52:52
 \begin{table}[!htbp] \centering 
@@
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right): ungültiges 'digits' Argument}}\end{kframe}
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
 

### 2020-02-27 paper.Rnw
pdf compiles without errors

@@
 \usepackage{rotating}
+\usepackage{dcolumn}
 % \usepackage[authoryear]{natbib}
@@
 If you want to cite \textcite{Millstein.2020} inline, use this.
-If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
+If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
 If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
 
-Equation with double index\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-% Figure\\
-% 
-% \begin{figure}
-%   \caption{Dispersion in productivity levels}
-%   \label{LineDisp}
-% 
-% <<echo=FALSE>>=
-% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-% print(figureLineDisp)
-% @
-% 
-% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-% \end{figure}
-
-% Figure \ref{LineDisp}
-
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
-
-Regression fit output with texreg\\
-
-<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
-# , message=FALSE, warning=FALSE
-# first, read in all Rds objects that you need
-# 
-mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-#  
-texreg(list(mealsNo_sub.lm, tripsNo_sub.lm), label = "mealsTripsSubsidyRegressions")
-@
-
-Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-\section{Outline}
-Descriptive statistics\\
-dynamics of\\ 
-(- number of organizations)\\
-(- number of beneficiaries)\\
-- selected ordinal outcomes, stacked\\
-- real total subsidy\\
-- real median subsidy per institution\\
-- real median subsidy per beneficiary\\
-(- which variables have largest variance; also relevant for variable selection)\\
-
-Regressions\\
-
-Questions:\\
-effect of\\
-- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
-- real meals subsidy on number of meals\\
-- real trips subsidy on number of trips\\
-- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-
-Methods:\\
-- simple, metric\\
-- standardized, metric\\
-- cumulative logit\\
-- with control variables\\
-(- without outliers)\\
-(- imputed data)\\
-
-Diff in Diff\\
-
-Outlook for CHILDREN/variable selection\\
-- double selection \\
-- partition analysis\\
-(- correlation matrix)\\
-(- factor analysis)\\
-- general tips\\
 
@@
 
-Figure\\
-
 \begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
-  \label{LineDisp}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{DaytodayskillsSelfworth}
 
 <<DaytodayskillsSelfworth, echo=FALSE>>=
-figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
+figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
 print(figureDaytodayskillsSelfworth)
@@
 
-<<FundamentalDynamicsTest, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-# 
-# # first, read in all Rds objects that you need
-# 
-# fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
-#  
-# colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
-# 
-# fundamental_dynamics <- xtable(fundamental_dynamics,
-#                                digits = c(0, 0, 1, 1, 0, 0),
-#           caption = "Summary Statistics",
-#           align = "lmmmmm", 
-#           label = "fundamentalDynamics"
-#           )
-# print(fundamental_dynamics, include.rownames = FALSE)
-@
-
 <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
-fundamental_dynamics <- stargazer(fundamental_dynamics,
-                                  summary = FALSE,
-                               # digits = c(0, 0, 1, 1, 0, 0),
+xtable(fundamental_dynamics,
+                                  # summary = FALSE,
+                                digits = c(0, 0, 1, 1, 0, 0),
            caption = "Summary Statistics",
-          # align = "lmmmmm", 
+           align = "lccccc", 
           label = "fundamentalDynamics"
           )
-print(fundamental_dynamics, include.rownames = FALSE)
+
 @
@@
 Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
-The possible values are: all, most, some, few, and none.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
 For this figure, we use the original ordinal varibles which result from the survey structure.
@@
 \floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
 \end{figure}
 
-In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill).
-In all years, most organizations say that most beneficiaries are more healthy.
-The least stated category is, that all beneficiaries are less ill.
-That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.
+In Figure \ref{Health_timeplots}, for the variable 'lessIll', there is much non available data.
+In all years, most organizations say that most beneficiaries are more healthy (3).
+The least stated category is, that all beneficiaries are less ill(4).
+That few are less ill (1), appears sometimes and the leftover category,none (0), which is only coded for the variable 'lessIll', appears as good as never.
 
-In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
-The least stated category is that some beneficiaries increased their dietary knowledge.
-The leftover category, few, does not appear.
+In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge') mostorganizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
+The least stated category is that some beneficiaries increased their dietary knowledge (2).
+The leftover category, few (1), does not appear.
 
-The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
-Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
-The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet.
-The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet.
+The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy'.
+Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet (3).
+The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet (4).
+The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet (2).
 The leftover category, few, also does not appear.
 
-\subsection{Selfworth and everyday expertise}
+\subsection{Equality of opportunities releveant variables over time}
 
-In its yearly surveys, CHILDREN has always asked about the following two variables.
-These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise.
+In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
 Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018.
-The possible values are: all, most, some, few, and none.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
 As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.
@@
 \begin{figure}
-  \caption{Selfworth and everyday expertise over time}
+  \caption{Equality of opportunities over time}
   \label{Equality_timeplots}
@@
 @
-\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables.
-These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
+\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
 \end{figure}
 
-Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth).
-Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
-The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth.
+Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth.
+Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3).
+The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2).
 The leftover category, few, does not appear.
 
-In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
+In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).
 
@@
   \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with improved self-worth}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with broadened everyday expertise}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' self-worth}
+  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized measure of beneficiaries' everyday expertise}
    \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
@@
 If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
+
+<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
+
+lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds") #outlier meals
+lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
+
+texreg(list(lm_ms, lm_ms_o,lm_ms_i), caption = "Regression Results: Number of meals", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\\\ %stars.}", caption.above = TRUE, 
+    label = "GrantsRegressionsLunch")
+@
 
@@
 
-<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
-
-lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
-lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
-lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
-lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
-
-texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
-@
-
 In the remit of the Trips program, the picture looks much different.
@@
 lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-lm_ts_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
 lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
-lm_ts_o_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex_control.lm.Rds")
 lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips
 
-texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE)
+texreg(list(lm_ts, lm_ts_o,lm_ts_i), caption = "Regression Results: Number of trips", custom.model.names = c("OLS", "OLS without Outliers", "OLS Impute"), scalebox = 0.8, label = 'GrantsRegressionsTrips', digits = 7)
 @
@@
 In their surveys, CHILDREN asks about two variables in both programs.
-These are the share of beneficiaries with improved self-worth and share of beneficiaries with broadened everyday expertise.
+These are the share of beneficiaries that are believed to have increased their self-worth and to have ehanced their everyday expertise.
 This feature could potentially allow us to compare the two programs regarding their realtive effectiveness.
@@
 
-texreg(list(ss, tss, ssI, tssI ), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
+texreg(list(ss, tss, ssI, tssI ), caption = "Regression Results: Selfworth", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'SelfworthRegressions')
 @
@@
 
-texreg(list(ds, tds, dsI, tdsI ), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+texreg(list(ds, tds, dsI, tdsI ), caption = "Regression Results: dayToDaySkills", custom.model.names = c("OLS Lunch", "OLS Trips", "OLS Lunch Impute", "OLS Trips Impute" ), scalebox = 0.8, label = 'DayToDaySkillsRegressions')
 
@@
 This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-https://www.schuleplusessen.de/startseite/
 
 In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill, with expanded dietary knowledge and with increased appreciation for a healthy diet.
+These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
 
-Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
-For these results, we use their ordinal values.
+Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
 The x-axis displays the index for a healthy diet.
@@
 For example, if an organization says that most beneficiaries are healthier, then this would be coded as most.
-In the last reporting period, there are 13 healthy diet criteria.
-In previous years there were up to 15.
-The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not.
-The healthy food incex is calculated as the number of fulfilled criteria.
-Examples for criteria are daily carbohydrates or daily vegetables.
+The highest amount of healthy criteria to be fulfilled is x.
 
 All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria.
-The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
+The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constituted a healthy diet.
 It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
@@
 @
-\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu.
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
 It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
@@
 In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the index for a healthy diet.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
 \end{figure}
@@
 We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.
+By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
 
 In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
-An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations.
+An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations.
 Regressing with the imputed dataset, results decrease by about 0.1.
 Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
-
-An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.
-
-In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
-For the original data set, the coeffiecent is slightly negative.
-Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
-This coefficent is as well insignifacant.
-
-In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger.
-For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
-When using WLS, we find a slightly negative association.
-A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02.
-This coefficent is not significant.
-For the imputed dataset we find a similar picture.
-
-The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.
 
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Regression Results: Less Ill", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = "HealthRegressions-LessIll")
 @
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS  \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Regression Results: Dietary Knowledge", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-DietaryKnowledge')
 @
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Regression Results: Appreciate Healthy", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'HealthRegressions-AppreciateHealthy')
 @
-
-The previous simple linear models are regressed with metric versions of the survey varibales.
-Originally, variables which range from none to all are ordinal.
-To account for this, we present a method to regress those variables according to their original traits.
-Therefore, we use a cumulative logit model.
-Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
 
@@
 \subsection{Factor Analysis}
-
-Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millenstein.2020, p.677}.
 
@@
 
-texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ regionalProducts: wether the organization offers meals with local ingredients or not \\\\ yearsSupportSince: the number of years an organization is already part of the Meals program \\\\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ state: german 'Bundeland' \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\\\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
+texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), scalebox = 0.8, label = 'expandLessIll')
 @
@@
 
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")
+stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Less Ill", label = "lessIllOdds")
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge", align = TRUE, label = "dietaryOdds")
+stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Dietary Knowledge", align = TRUE, label = "dietaryOdds")
 @
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet", align = TRUE, label = "appreciateOdds")
+stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Appreciate Healthy", align = TRUE, label = "appreciateOdds")
 @
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth", align = TRUE, label = "selfworthOdds")
+stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Selfworth", align = TRUE, label = "selfworthOdds")
 @
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise", align = TRUE, label = "dayToDayOdds")
+stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Everyday expertise", align = TRUE, label = "dayToDayOdds")
 @
@@
 In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-This method was developped by Millenstein et.
+This method was developped by Millstein et.
 al in the context of genome analysis.
+
+According to the researchers, potential benefits of reducing dimensionality are reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{} (p.677).
 
@@
 It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
+By that, it defines a surjective mapping \cite{} (p.676).
 A function g is implemented using the arithmetic mean.
@@
 What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced.\cite{}(p.677)
 
@@
 
-stargazer(partition_meals,
-                               #digits = c(0, 0, 1, 1, 0, 0),
+xtable(partition_meals,
+                               # digits = c(0, 0, 1, 1, 0, 0),
           caption = "Partition of outcomes, Meals", 
-          label = 'partitionmeals'
-          #align = "lmmm"
+          label = 'partitionmeals',
+          align = "lccc"
           )
@@
 
-stargazer(partition_trips,
+xtable(partition_trips,
                                #digits = c(0, 0, 1, 1, 0, 0),
           caption = "Partition of outcomes, Trips",
-          label = 'partitiontrips'
-          #align = "lmmm"
+          label = 'partitiontrips',
+          align = "lccc"
           )
-print(partition_meals, partition_trips, include.rownames = FALSE)
+# print(partition_meals, partition_trips, include.rownames = FALSE)
 @
@@
 
-<<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-
-lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
-lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
-ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
-td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
-sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
-dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
-tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
-tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
-@
+% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% # 
+% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% # @
 

### 2020-02-27 paper.tex
pdf compiles without errors

@@
 If you want to cite \textcite{Millstein.2020} inline, use this.
-If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
+If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
 If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
 
-Equation with double index\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-% Figure\\
-% 
-% \begin{figure}
-%   \caption{Dispersion in productivity levels}
-%   \label{LineDisp}
-% 
-% <<echo=FALSE>>=
-% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-% print(figureLineDisp)
-% @
-% 
-% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-% \end{figure}
-
-% Figure \ref{LineDisp}
-
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
-
-Regression fit output with texreg\\
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c }
-\hline
- & Model 1 & Model 2 \\
-\hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     \\
-realSubsidy      & $2.61^{***}$    &              \\
-                 & $(0.57)$        &              \\
-realTripsSubsidy &                 & $0.00^{*}$   \\
-                 &                 & $(0.00)$     \\
-\hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-\caption{Statistical models}
-\label{mealsTripsSubsidyRegressions}
-\end{center}
-\end{table}
-
-Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-\section{Outline}
-Descriptive statistics\\
-dynamics of\\ 
-(- number of organizations)\\
-(- number of beneficiaries)\\
-- selected ordinal outcomes, stacked\\
-- real total subsidy\\
-- real median subsidy per institution\\
-- real median subsidy per beneficiary\\
-(- which variables have largest variance; also relevant for variable selection)\\
-
-Regressions\\
-
-Questions:\\
-effect of\\
-- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
-- real meals subsidy on number of meals\\
-- real trips subsidy on number of trips\\
-- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-
-Methods:\\
-- simple, metric\\
-- standardized, metric\\
-- cumulative logit\\
-- with control variables\\
-(- without outliers)\\
-(- imputed data)\\
-
-Diff in Diff\\
-
-Outlook for CHILDREN/variable selection\\
-- double selection \\
-- partition analysis\\
-(- correlation matrix)\\
-(- factor analysis)\\
-- general tips\\
 
@@
 
-Figure\\
-
 \begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
-  \label{LineDisp}
+  \caption{Trend in everyday expertise and selfworth}
+  \label{DaytodayskillsSelfworth}
 
@@
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:46
-\begin{table}[!htbp] \centering 
-  \caption{} 
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 19:35:27 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
+  \hline
+1 & 2011 & 3748.0 &  & 52 &  \\ 
+  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
+  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
+  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
+  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
+  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
+  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
+  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
 \label{fundamentalDynamics}
-\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
-$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
-$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
-$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
-$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
-$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
-$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
-$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:47
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{fundamentalDynamics} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Summary Statistics \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table} 
- [1] ""                                                                                                           
- [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
- [4] "\\begin{table}[!htbp] \\centering "                                                                         
- [5] "  \\caption{} "                                                                                             
- [6] "  \\label{fundamentalDynamics} "                                                                            
- [7] "\\begin{tabular}{@{\\extracolsep{5pt}} ccccc} "                                                             
- [8] "\\\\[-1.8ex]\\hline "                                                                                       
- [9] "\\hline \\\\[-1.8ex] "                                                                                      
-[10] "$2,011$ & $3,748$ & $$ & $52$ & $$ \\\\ "                                                                   
-[11] "$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\\\ "                                                            
-[12] "$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\\\ "                                                            
-[13] "$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\\\ "                                                            
-[14] "$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\\\ "                                                            
-[15] "$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\\\ "                                                            
-[16] "$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\\\ "                                                            
-[17] "$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\\\ "                                                        
-[18] "\\hline \\\\[-1.8ex] "                                                                                      
-[19] "\\end{tabular} "                                                                                            
-[20] "\\end{table} "                                                                                              
-[21] ""                                                                                                           
-[22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
-[24] "\\begin{table}[!htbp] \\centering "                                                                         
-[25] "  \\caption{} "                                                                                             
-[26] "  \\label{fundamentalDynamics} "                                                                            
-[27] "\\begin{tabular}{@{\\extracolsep{5pt}} c} "                                                                 
-[28] "\\\\[-1.8ex]\\hline "                                                                                       
-[29] "\\hline \\\\[-1.8ex] "                                                                                      
-[30] "Summary Statistics \\\\ "                                                                                   
-[31] "\\hline \\\\[-1.8ex] "                                                                                      
-[32] "\\end{tabular} "                                                                                            
-[33] "\\end{table} "
+\end{table}
 
@@
 \floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
+These are the shares of beneficiaries who are healthier (lessIll\_ordered), have a growing appreciation for a healthy diet (dietaryKnowledge\_ordered), or have increased their knowledge about what constitutes a healthy diet (appreciateHealthy\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries are healthier, then this would be coded as 3.}
 \end{figure}
 
-In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill).
-In all years, most organizations say that most beneficiaries are more healthy.
-The least stated category is, that all beneficiaries are less ill.
-That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.
-
-In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
-The least stated category is that some beneficiaries increased their dietary knowledge.
-The leftover category, few, does not appear.
-
-The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
-Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
-The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet.
-The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet.
+In Figure \ref{Health_timeplots}, for the variable 'lessIll', there is much non available data.
+In all years, most organizations say that most beneficiaries are more healthy (3).
+The least stated category is, that all beneficiaries are less ill(4).
+That few are less ill (1), appears sometimes and the leftover category,none (0), which is only coded for the variable 'lessIll', appears as good as never.
+
+In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge') mostorganizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
+The least stated category is that some beneficiaries increased their dietary knowledge (2).
+The leftover category, few (1), does not appear.
+
+The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy'.
+Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet (3).
+The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet (4).
+The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet (2).
 The leftover category, few, also does not appear.
 
-\subsection{Selfworth and everyday expertise}
-
-In its yearly surveys, CHILDREN has always asked about the following two variables.
-These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise.
+\subsection{Equality of opportunities releveant variables over time}
+
+In its yearly surveys, CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth and have a growing understanding for everyday expertise.
 Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018.
-The possible values are: all, most, some, few, and none.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
 As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.
@@
 \end{knitrout}
-\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables.
-These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
+\floatfoot{In its yearly surveys CHILDREN has always asked about two variables closley related to increasing the beneficiaries' equality of opportunities.
+These are the degree to which beneficiaries: have more selfworth (selfworth\_ordered) and have a growing understanding for everyday expertise (dayToDaySkills\_ordered).
+The x-axis plots the year.
+The y-axis displays the share of organizarions in each category of the health outcome.
+The possible values are: all(coded as 4), most (3), some (2), few (1), and none (coded as 0).
+For example, if an organization says that most beneficiaries have more selfowrth, then this would be coded as 3.}
 \end{figure}
 
-Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth).
-Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
-The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth.
+Figure 4 shows in its upper plot the development of the answered categories for the variable selfworth.
+Mostly, the answer is that most beneficiaries in most organizations have more selfworth (3).
+The second most stated category is that all beneficiaries gained in selfworth (4) and the least stated is that some have more selfworth (2).
 The leftover category, few, does not appear.
 
-In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
+In the bottom plot of figure 4 the development of everyday expertise of the beneficiaries over time is visible.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise (3).
 
@@
 If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
+
+\begin{table}
+\caption{Regression Results: Number of meals}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c }
+\hline
+ & OLS & OLS without Outliers & OLS Impute \\
+\hline
+(Intercept) & $-12089.14^{*}$ & $3535.39^{***}$ & $-12250.60^{**}$ \\
+            & $(5192.86)$     & $(498.99)$      & $(4524.09)$      \\
+realSubsidy & $2.61^{***}$    & $0.29^{***}$    & $2.72^{***}$     \\
+            & $(0.57)$        & $(0.05)$        & $(0.51)$         \\
+\hline
+R$^2$       & 0.43            & 0.13            & 0.45             \\
+Adj. R$^2$  & 0.43            & 0.12            & 0.45             \\
+Num. obs.   & 329             & 250             & 440              \\
+RMSE        & 39992.79        & 3629.72         & 39601.41         \\
+\hline
+\multicolumn{4}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt}Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ Lorem ipsum dolor sit amet, consetetur sadipscing elitr, 
+sed diam nonumy eirmod tempor invidunt ut labore et dolore magna 
+aliquyam. \\ $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
 
@@
 
-\usepackage{booktabs}
-
-\begin{table}
-\caption{Association between number of meals and real subsidy}
-\begin{center}
-\scalebox{0.8}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
-                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
-realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
-                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
-eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
-                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
-\midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsLunch}
-\end{center}
-\end{table}
-
 In the remit of the Trips program, the picture looks much different.
@@
 
-\usepackage{booktabs}
-
 \begin{table}
-\caption{Association between number of trips and real subsidy}
 \begin{center}
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
-                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
-realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
-                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
-tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
-                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
-\midrule
-R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
-Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
-RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\begin{tabular}{l c c c }
+\hline
+ & OLS & OLS without Outliers & OLS Impute \\
+\hline
+(Intercept)      & $3.7049327^{***}$ & $2.6235738^{***}$ & $3.6236945^{***}$ \\
+                 & $(0.3313317)$     & $(0.2299664)$     & $(0.3253071)$     \\
+realTripsSubsidy & $0.0002270^{*}$   & $0.0002927^{***}$ & $0.0002350^{*}$   \\
+                 & $(0.0000948)$     & $(0.0000774)$     & $(0.0000946)$     \\
+\hline
+R$^2$            & 0.0473985         & 0.0880132         & 0.0504264         \\
+Adj. R$^2$       & 0.0444217         & 0.0844368         & 0.0475663         \\
+Num. obs.        & 322               & 257               & 334               \\
+RMSE             & 2.9564942         & 1.6980825         & 2.9310458         \\
+\hline
+\multicolumn{4}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Number of trips}
 \label{GrantsRegressionsTrips}
@@
 \begin{table}
-\caption{Association between selfworth and subsidy per beneficiary}
 \begin{center}
@@
 \hline
- & (1) & (2) & (3) & (4) \\
+ & OLS Lunch & OLS Trips & OLS Lunch Impute & OLS Trips Impute \\
 \hline
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Selfworth}
 \label{SelfworthRegressions}
@@
 \begin{table}
-\caption{Association between everyday expertise and subsidy per beneficiary}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: dayToDaySkills}
 \label{DayToDaySkillsRegressions}
@@
 This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-https://www.schuleplusessen.de/startseite/
 
 In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill, with expanded dietary knowledge and with increased appreciation for a healthy diet.
-
-Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
-For these results, we use their ordinal values.
+These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
+
+Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion and each of the three health-related variables.
 The x-axis displays the index for a healthy diet.
@@
 \end{knitrout}
-\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu.
+\floatfoot{DGECriteriaNo is an index that captures how healthy the meals in an organization are.
 It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
@@
 We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
-By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.
+By estimating these models with ordinary least squares, we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
+To control for this difference in size, we additionally fit the models with weighted least squares, using the number of beneficiaries as weights.
 
 In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
-An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations.
+An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being more healthy by 0.35 standard deviations.
 Regressing with the imputed dataset, results decrease by about 0.1.
@@
 
-An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.
-
-In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
-For the original data set, the coeffiecent is slightly negative.
-Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
-This coefficent is as well insignifacant.
-
-In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger.
-For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
-When using WLS, we find a slightly negative association.
-A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02.
-This coefficent is not significant.
-For the imputed dataset we find a similar picture.
-
-The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.
-
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries being less ill}
 \begin{center}
@@
 \hline
- & (1) & (2) & (3) & (4) \\
+ & OLS & WLS & OLS Impute & WLS Impute \\
 \hline
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Less Ill}
 \label{HealthRegressions-LessIll}
@@
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Dietary Knowledge}
 \label{HealthRegressions-DietaryKnowledge}
@@
 \begin{table}
-\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
 \begin{center}
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
+\end{tabular}
+}
+\caption{Regression Results: Appreciate Healthy}
 \label{HealthRegressions-AppreciateHealthy}
@@
 
-The previous simple linear models are regressed with metric versions of the survey varibales.
-Originally, variables which range from none to all are ordinal.
-To account for this, we present a method to regress those variables according to their original traits.
-Therefore, we use a cumulative logit model.
-Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
-
 \section{Feature Selection}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 7:35:48 PM
 % Requires LaTeX packages: dcolumn rotating 
@@
 \hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 7:35:50 PM
+\begin{table}[!htbp] \centering 
+  \caption{Propodss Regression Results: Less Ill} 
+  \label{lessIllOdds} 
+\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
+\\[-1.8ex]\hline 
+\hline \\[-1.8ex] 
+ & Estimate & Std. Error & z value & Pr(\textgreater \textbar z\textbar ) \\ 
+\hline \\[-1.8ex] 
+(Intercept):1 & $$-$2.799$ & $1.109$ & $$-$2.523$ & $0.012$ \\ 
+(Intercept):2 & $1.653$ & $0.582$ & $2.841$ & $0.004$ \\ 
+(Intercept):3 & $4.667$ & $0.738$ & $6.322$ & $0$ \\ 
+DGECriteriaNo & $$-$0.291$ & $0.075$ & $$-$3.883$ & $0.0001$ \\ 
+\hline \\[-1.8ex] 
+\end{tabular} 
+\end{table}
+
+% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
+% Date and time: Thu, Feb 27, 2020 - 7:35:51 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
-  \label{lessIllOdds} 
-\begin{tabular}{@{\extracolsep{5pt}} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{} & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{Std. Error} & \multicolumn{1}{c}{z value} & \multicolumn{1}{c}{Pr(\textgreater \textbar z\textbar )} \\ 
-\hline \\[-1.8ex] 
-\multicolumn{1}{c}{(Intercept):1} & -2.799 & 1.109 & -2.523 & 0.012 \\ 
-\multicolumn{1}{c}{(Intercept):2} & 1.653 & 0.582 & 2.841 & 0.004 \\ 
-\multicolumn{1}{c}{(Intercept):3} & 4.667 & 0.738 & 6.322 & 0 \\ 
-\multicolumn{1}{c}{DGECriteriaNo} & -0.291 & 0.075 & -3.883 & 0.0001 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-% Requires LaTeX packages: dcolumn 
-\begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
+  \caption{Propodss Regression Results: Dietary Knowledge} 
   \label{dietaryOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 7:35:51 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
+  \caption{Propodss Regression Results: Appreciate Healthy} 
   \label{appreciateOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 7:35:52 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
+  \caption{Propodss Regression Results: Selfworth} 
   \label{selfworthOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 7:35:52 PM
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
+  \caption{Propodss Regression Results: Everyday expertise} 
   \label{dayToDayOdds} 
@@
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 19:35:52 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Meals & Mapping, Meals & Information, Meals \\ 
+  \hline
+1 & participateMore & participateMore & 1.00 \\ 
+  2 & tasksLunch & tasksLunch & 1.00 \\ 
+  3 & ownIdeas & ownIdeas & 1.00 \\ 
+  4 & stayLonger & stayLonger & 1.00 \\ 
+  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
+  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
+  7 & foodCulture & foodCulture & 1.00 \\ 
+  8 & lessIll & lessIll & 1.00 \\ 
+  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
+  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
+  11 & addressProblems & addressProblems & 1.00 \\ 
+  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
+  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
+  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
+  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
+  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
+  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
+  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
+  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
+  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
+  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
+  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
+  23 & reduced\_var\_3 & proud & 0.43 \\ 
+  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
+  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
+  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
+  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
+  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
+  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Meals} 
 \label{partitionmeals}
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Information, Meals & 29 & 0.670 & 0.270 & 0 & 0.4 & 1 & 1 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{partitionmeals} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Partition of outcomes, Meals \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
+\end{table}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 19:35:52 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Trips & Mapping, Trips & Information, Trips \\ 
+  \hline
+1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
+  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
+  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
+  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
+  5 & tripsBudget & tripsBudget & 1.00 \\ 
+  6 & tripsMoney & tripsMoney & 1.00 \\ 
+  7 & tripsReview & tripsReview & 1.00 \\ 
+  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
+  9 & tripsMobility & tripsMobility & 1.00 \\ 
+  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
+  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
+  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
+  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
+  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
+  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
+  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
+  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
+  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
+  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
+  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Trips} 
 \label{partitiontrips}
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Information, Trips & 20 & 0.834 & 0.215 & 0 & 0.6 & 1 & 1 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{partitiontrips} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Partition of outcomes, Trips \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table} 
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+\end{table}
 
 \subsection{A4: OLS Regressions}
+
+% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% # 
+% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% # @
 

### 2020-02-27 ANALYSIS/PlotVariablesOverTime.R

@@ -3,7 +3,7 @@
 
 #setthevariables
 
-responset= names(mergedData)
+response= names(mergedData)
 # [5:213]
 # expl= names(mergedData)[4]
 

### 2020-02-27 paper.Rnw

--- 2020-02-27 paper.Rnw
@@
 If you want to cite \textcite{Millstein.2020} inline, use this.
-If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
+
+If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
+
 If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
 
-Equation with double index\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-% Figure\\
-% 
-% \begin{figure}
-%   \caption{Dispersion in productivity levels}
-%   \label{LineDisp}
-% 
-% <<echo=FALSE>>=
-% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-% print(figureLineDisp)
-% @
-% 
-% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-% \end{figure}
-
-% Figure \ref{LineDisp}
-
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
-
-Regression fit output with texreg\\
-
-<<mealsTripsSubsidyRegressions, echo=FALSE, results='asis'>>=
-# , message=FALSE, warning=FALSE
-# first, read in all Rds objects that you need
-# 
-mealsNo_sub.lm = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-tripsNo_sub.lm = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-#  
-texreg(list(mealsNo_sub.lm, tripsNo_sub.lm), label = "mealsTripsSubsidyRegressions")
-@
-
-Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-\section{Outline}
-Descriptive statistics\\
-dynamics of\\ 
-(- number of organizations)\\
-(- number of beneficiaries)\\
-- selected ordinal outcomes, stacked\\
-- real total subsidy\\
-- real median subsidy per institution\\
-- real median subsidy per beneficiary\\
-(- which variables have largest variance; also relevant for variable selection)\\
-
-Regressions\\
-
-Questions:\\
-effect of\\
-- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
-- real meals subsidy on number of meals\\
-- real trips subsidy on number of trips\\
-- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-
-Methods:\\
-- simple, metric\\
-- standardized, metric\\
-- cumulative logit\\
-- with control variables\\
-(- without outliers)\\
-(- imputed data)\\
-
-Diff in Diff\\
-
-Outlook for CHILDREN/variable selection\\
-- double selection \\
-- partition analysis\\
-(- correlation matrix)\\
-(- factor analysis)\\
-- general tips\\
 
@@
 
-Figure\\
-
-\begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
-  \label{LineDisp}
-
-<<DaytodayskillsSelfworth, echo=FALSE>>=
-figureDaytodayskillsSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dayToDaySkills_selfworth.Rds")
-print(figureDaytodayskillsSelfworth)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
-The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
 \section{Summary Statistics}
@@
 If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
+
+<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
+
+lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
+lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
+lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
+
+texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
+
+@
 
@@
 The estimate is also highly statistically significant.
-
-<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
-
-lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
-lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
-lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
-lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
-
-texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
-@
 
@@
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
+\section{The Effects of the Trips Program on Participating Beneficiaries}
+
+How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially?
 So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
-Empirical Approach\\
-
-The baseline of the empirical approach is the determination of the treatment and control group.
-Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
-On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
-
-Determining the treatment and control group this way, however, was a problem.
-
-THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
-We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
-All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
-Our analysis is based on this very strong definition of the treatment and control group.
-
-Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
-THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
-
-As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
-Therefore we have to use the survey answers from the Mittagstisch survey.
-
-Generally our data set contains variables from the years 2011 until 2018.
-
-The constellation of the treatment and control group varies from year to year. 
-Assumption: erhalten der treatment gleichbedeutend wie ein verlust
-
-Possible variables as dependent variables
-how we determined that:
-The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
-possible variables selfworth, day to day skills
-used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
-
-looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
-
-linear regression just to look at whether there are effects
-
-add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
-how fixed effects are implemented
-
-which control variables we use
-how we determined which controls
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{l c}
-% \hline
-%  & Selfworth \\
-% \hline
-% (Intercept)             & $-1.13^{***}$ \\
-%                         & $(0.32)$      \\
-% dfcEF2$treatEF          & $-0.47$       \\
-%                         & $(0.31)$      \\
-% \hline
-% Num. obs.               & $430$         \\
-% R$^2$ (full model)      & $0.47$        \\
-% R$^2$ (proj model)      & $0.47$        \\
-% Adj. R$^2$ (full model) & $0.36$        \\
-% Adj. R$^2$ (proj model) & $0.36$        \\
-% \hline
-% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-% \end{tabular}
-% \caption{linear regression}
-% \label{table:coefficients}
-% \end{center}
-% \end{table}
-
-Ende??
-the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
-
-<<selfworth_tripsProgram, echo=FALSE, results='asis', message=FALSE>>=
-
-# first, read in all Rds objects that you need
-
-lm1_selfworth = readRDS("./ANALYSIS/Tables/lm1_selfworth.Rds")
-lm2_selfworth = readRDS("./ANALYSIS/Tables/lm2_selfworth.Rds")
-lm3_selfworth = readRDS("./ANALYSIS/Tables/lm3_selfworth.Rds")
-lm4_selfworth = readRDS("./ANALYSIS/Tables/lm4_selfworth.Rds")
-
-table1_selfworth <- stargazer(lm1_selfworth,
-                    lm2_selfworth,
-                    lm3_selfworth,
-                    lm4_selfworth,
-          title = "Regression Results",
-          order = c('Constant', 'treatEF'),
-          omit = c('id104','id105','id106','id108','id109','id111','id112','id113','id114','id118','id122',
-                   'id123','id124','id125','id130','id131','id132','id133','id136','id137','id139','id141',
-                   'id142','id165','id186','id187','id188','id189','id190','id191','id192','id193','id194',
-                   'id209','id213','id214','id215','id216','id217','id218','id219','id220','id221','id226',
-                   'id233','id249','id255','id269','id270','id281','id282','id403','id404','id417','id418',
-                   'id437','id482','id483','id599','id600','id601','id602','id623','id684','id685','id686',
-                   'id687','dummy_2012','dummy_2013','dummy_2014','dummy_2015','dummy_2016','dummy_2017',
-                   'dummy_2018', 'id'
-                  ),
-          add.lines = list(c("ID fixed effects", 'No', 'No', 'Yes', 'Yes'),
-                           c('Time fixed effects', 'No', 'Yes', 'No', 'Yes')),
-          align = TRUE,
-
-          # this line of code rotates the table by 90 degrees counterclockwise
-
-          float.env = "sidewaystable")
-@
+Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program.
+However, not all organizations receive additional funding to provide the trips program.
+This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group.
+The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+
+\subsection{Empirical Approach}
+
+The basis of the empirical approach is the specification of the treatment and the control group.
+Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program.
+On the other hand, the control group represents all organizations that only receive funding for the meals program.
+Therefore, the social institutions in the control group do not participate in the trips program.
+
+\subsubsection{Specification of the Treatment Group}
+
+When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program.
+As previously mentioned, the CHILDREN survey consists of two parts.
+The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program.
+The dataset shows that there are several organizations that did not provide information regarding the trips program.
+In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
+Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group.
+When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey.
+There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year.
+Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
+Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.
+
+Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
+This implies that an organization remains in the control group as long as it does not receive funding for the trips program.
+Due to this definition, an organization cannot change from the treatment into the control group.
+
+In general, the constellation of the treatment and control group varies across years.
+As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
+At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods.
+In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
+However, the dataset also includes organizations that switch from the treatment to the control group.
+The first definition of the treatment variable does not take this case into account.
+Therefore, we additionally construct a second treatment indicator which is defined as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
+With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
+Consequently, the estimates cannot be very robust.
+Therefore, the results should not be overstated.
+
+\subsubsection{Dependent Variables}
+
+The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group.
+However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group.
+Therefore, we have to use variables of the meals program as outcome variables in our analysis.
+For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
+Firstly, both variables are applicable to the trips program as well as the meals program.
+In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
+
+\subsubsection{Graphical Evidence}
+
+\begin{figure}
+  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \label{selfworth_Trend}
+
+<<Selfworth, echo=FALSE>>=
+figureSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_selfworth.Rds")
+print(figureSelfworth)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \label{dayToDaySkills_Trend}
+
+<<Daytodayskills, echo=FALSE>>=
+figureDaytodayskills = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dtds.Rds")
+print(figureDaytodayskills)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to everyday expertise.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+To check for differences in treatment and control group, we created descriptive statistics regarding to the variables of interest.
+Figure 5 and Figure 6 represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time  while it decreased in the control group (Figure 5).
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6).
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+To check for differences in treatment and control group, we created the following graphs using descriptive statistics.
+
+The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time while it decreased in the control group.
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group.
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+\subsubsection{Differences-in-Differences Estimation}
+
+For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children.
+The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group.
+The key identifying assumption for the DID strategy is the common trend assumption.
+The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
+In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
+As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend.
+Therefore, we cannot argue that the common trend assumption is fulfilled.
+
+Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
+\begin{equation}
+\label{didregression}
+  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
+\end{equation}
+
+where \begin{itshape}{i}\end{itshape} indexes the identification number of each organization supported by CHILDREN and \begin{itshape}{t}\end{itshape} indexes the year of observation.
+The outcome variable, denoted by \begin{itshape}Y_{it}\end{itshape}, is either selfworth or everyday expertise.
+As mentioned in the previous section, \begin{itshape}TreatEF_{it}\end{itshape} represents the treatment status of organization \begin{itshape}{i}\end{itshape} in year \begin{itshape}{t}\end{itshape}.
+The corresponding regression coefficient \begin{itshape}\beta\end{itshape} represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+
+The panel data set allows us to implement fixed effects.
+In our analysis we introduce individual fixed effects and time fixed effects.
+The ID fixed effects \begin{itshape}\gamma_{i}\end{itshape} control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
+For example, the state of an organization does not vary over time but might differ across supported social institutions.
+Additionally, the year fixed effects \begin{itshape}\delta_{t}\end{itshape} capture all variables that change across years but are the same for all organizations and within a specific year.
+For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
+
+One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics.
+Therefore, we include a set of control variables to deal with potential selection bias.
+For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
+Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
+
+\subsection{Results}
+
+\subsubsection{Everyday Expertise}
+
+The estimated coefficients of equation XX are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
+Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
+Columns (1) and (3) only include ID fixed effects and year fixed effects without any controls.
+Columns (2) and (4) expand the regression equation by adding the organization specific control variables: Subsidy, total costs and the number of days in a week on which children cook in a social institution.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.326)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.014)$    &           & $(0.014)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.000)$    &           & $(0.000)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Everyday Expertise}
+\label{table:coefficients1}
+\end{center}
+\end{table}
+
+Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
+Therefore, this finding should not be overstated.
+On the other hand, using the alternative specification of the treatment indicator in column (3), the average treatment effect is positive, but remains insignificant.
+Thus, the sign of the estimated treatment effect changes if we use the alternative definition of the treatment variable.
+With the second treatment variable, the number of organizations in the control group increases, as the treatment status depends on actually receiving funding in a given year.
+Nevertheless, the difference in size of the treatment and control group remains relatively large.
+However, the estimate in Column (3) could provide evidence that the treatment effect might be positive and potentially turn significant if the sample size increases.
+
+Adding the organization specific control variables in Column (2) and Column (4) does not influence the size of both effects and the significance substantially.
+
+\subsubsection{Selfworth}
+
+Using selfworth as the outcome variable, the estimates of regression equation \ref{didregression} are reported in Table \ref{table:coefficients2}, whose structure is equal to Table \ref{table:coefficients1}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.018)$ &           & $(0.017)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.001)$ &           & $(0.001)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.069)$ &           & $(0.069)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Selfworth}
+\label{table:coefficients2}
+\end{center}
+\end{table}
+
+Strinkinlgy, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
+In column (1)-(3), the average treatment effect is insignificant.
+However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
+This indicates that participating in the trips program would negatively influence the selfworth of the children and adolescents.
+This surprising result contradicts our hypothesis that the participation in the trips program positively influences the selfworth of the beneficiaries.
+As previously mentioned, the number of observation units in both treatment and control group is relatively small.
+Therefore, this unexpected negative effect of the trips program on selfworth should not be overstated.
+Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
+It might be difficult for the respondents of the survey to assess children specific characteristics, such as selfworth.
+During our visit in Augsburg, the employees confirmed that it is challenging to evaluate the variables asked in the survey for all participants in the entire social institution, especially with a lot of variation in attendance.
+One potential solution for this problem could be to directly ask the children and adolescents.
+Data on the individual level might be more precise because the children could assess themselves better.
+When using variables on the level of beneficiaries, we might observe a positive effect of the trips program on selfworth.
+As reported in the summary statistics, the outcome variable shows a low variation.
+This results from the fact that, most of the time, organizations give the answer “all children” and “most children” when asked about the improvement of children’s selfworth.
+In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
+In the survey of the year 2019, CHILDREN already implemented a wider scale by asking for the percentage of beneficiaries that increased their selfworth.
+As this alternative measuring method is more precise, it might result in a higher variation of answers.
+Therefore, finding significant effects of the trips program on selfworth might be more likely.
 
@@
 In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-This method was developped by Millenstein et.
+This method was developped by Millstein et.
 al in the context of genome analysis.

### 2020-02-27 paper.tex
resolved conflicts in pdf

--- 2020-02-27 paper.tex
@@
 If you want to cite \textcite{Millstein.2020} inline, use this.
-If you want to cite \parencite[p.4]{Millenstein.2020} inline with a page number, use this.
+
+If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
+
 If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
 
-Equation with double index\\
-
-\begin{equation}
-\label{ModelProdu}
-\ln y_{it}^{n} = \beta_0 + \beta_k \ln k_{it-1}^{n} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
-\end{equation}
-
-List\\
-
-\begin{itemize}
-  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
-  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
-  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
-\end{itemize}
-
-% Figure\\
-% 
-% \begin{figure}
-%   \caption{Dispersion in productivity levels}
-%   \label{LineDisp}
-% 
-% <<echo=FALSE>>=
-% figureLineDisp = readRDS("./ANALYSIS/GRAPHS/LineDisp.Rds")
-% print(figureLineDisp)
-% @
-% 
-% \floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent.
-A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector.
-After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter.
-The shaded bars represent recessions as defined by the NBER.
-The year ticks refer to January 1.
-The dispersion measures take as their date the middle of the year, July 2.
-Compare Kehrig (2015), Figure 1.}
-% \end{figure}
-
-% Figure \ref{LineDisp}
-
-% <<results='asis', echo=FALSE>>=
-% tableCyclicDisp = readRDS("./Analysis/CyclicDisp.Rds")
-% colnames(tableCyclicDisp) <- c("Lead in years", "All", "p-value", "Non-Durables", "p-value", "Durables", "p-value")
-% tableCyclicDisp <- xtable(tableCyclicDisp, caption = "Cyclicality of productivity dispersion", digits = c(0, 0, 3, 2, 3, 2, 3, 2))
-% print(tableCyclicDisp, include.rownames = FALSE)
-% @
-
-Regression fit output with texreg\\
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c }
-\hline
- & Model 1 & Model 2 \\
-\hline
-(Intercept)      & $-12089.14^{*}$ & $3.70^{***}$ \\
-                 & $(5192.86)$     & $(0.33)$     \\
-realSubsidy      & $2.61^{***}$    &              \\
-                 & $(0.57)$        &              \\
-realTripsSubsidy &                 & $0.00^{*}$   \\
-                 &                 & $(0.00)$     \\
-\hline
-R$^2$            & 0.43            & 0.05         \\
-Adj. R$^2$       & 0.43            & 0.04         \\
-Num. obs.        & 329             & 322          \\
-RMSE             & 39992.79        & 2.96         \\
-\hline
-\multicolumn{3}{l}{\scriptsize{$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$}}
-\end{tabular}
-\caption{Statistical models}
-\label{mealsTripsSubsidyRegressions}
-\end{center}
-\end{table}
-
-Table \ref{mealsTripsSubsidyRegressions}
 % To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-\section{Outline}
-Descriptive statistics\\
-dynamics of\\ 
-(- number of organizations)\\
-(- number of beneficiaries)\\
-- selected ordinal outcomes, stacked\\
-- real total subsidy\\
-- real median subsidy per institution\\
-- real median subsidy per beneficiary\\
-(- which variables have largest variance; also relevant for variable selection)\\
-
-Regressions\\
-
-Questions:\\
-effect of\\
-- healthy meals (DGE criterion) standardized on healthy characteristics standardized, with eatersPerMeal as weights\\
-- real meals subsidy on number of meals\\
-- real trips subsidy on number of trips\\
-- real meals subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-- real trips subsidy per beneficiary on standardized self-worth and standardized day-to-day skills\\
-
-Methods:\\
-- simple, metric\\
-- standardized, metric\\
-- cumulative logit\\
-- with control variables\\
-(- without outliers)\\
-(- imputed data)\\
-
-Diff in Diff\\
-
-Outlook for CHILDREN/variable selection\\
-- double selection \\
-- partition analysis\\
-(- correlation matrix)\\
-(- factor analysis)\\
-- general tips\\
 
@@
 
-Figure\\
-
-\begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
-  \label{LineDisp}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/DaytodayskillsSelfworth-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to selfworth (graph x) and everyday expertise (graph y).
-The time trend of the average answers from the organizations in the treatment group is characterised by the solid line, the answers from the control group by the dotted line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
 \section{Summary Statistics}
@@
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:46
-\begin{table}[!htbp] \centering 
-  \caption{} 
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 20:41:58 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
+  \hline
+1 & 2011 & 3748.0 &  & 52 &  \\ 
+  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
+  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
+  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
+  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
+  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
+  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
+  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
 \label{fundamentalDynamics}
-\begin{tabular}{@{\extracolsep{5pt}} ccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-$2,011$ & $3,748$ & $$ & $52$ & $$ \\ 
-$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\ 
-$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\ 
-$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\ 
-$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\ 
-$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\ 
-$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\ 
-$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:47
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{fundamentalDynamics} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Summary Statistics \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table} 
- [1] ""                                                                                                           
- [2] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
- [3] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
- [4] "\\begin{table}[!htbp] \\centering "                                                                         
- [5] "  \\caption{} "                                                                                             
- [6] "  \\label{fundamentalDynamics} "                                                                            
- [7] "\\begin{tabular}{@{\\extracolsep{5pt}} ccccc} "                                                             
- [8] "\\\\[-1.8ex]\\hline "                                                                                       
- [9] "\\hline \\\\[-1.8ex] "                                                                                      
-[10] "$2,011$ & $3,748$ & $$ & $52$ & $$ \\\\ "                                                                   
-[11] "$2,012$ & $3,556$ & $2,803$ & $51$ & $44$ \\\\ "                                                            
-[12] "$2,013$ & $4,015$ & $2,823$ & $55$ & $42$ \\\\ "                                                            
-[13] "$2,014$ & $4,685$ & $2,752$ & $55$ & $43$ \\\\ "                                                            
-[14] "$2,015$ & $5,857$ & $3,823$ & $55$ & $49$ \\\\ "                                                            
-[15] "$2,016$ & $3,075$ & $3,819$ & $59$ & $48$ \\\\ "                                                            
-[16] "$2,017$ & $4,895$ & $4,150$ & $64$ & $48$ \\\\ "                                                            
-[17] "$2,018$ & $5,102.500$ & $6,911$ & $68$ & $49$ \\\\ "                                                        
-[18] "\\hline \\\\[-1.8ex] "                                                                                      
-[19] "\\end{tabular} "                                                                                            
-[20] "\\end{table} "                                                                                              
-[21] ""                                                                                                           
-[22] "% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu"
-[23] "% Date and time: Do, Feb 27, 2020 - 16:52:47"                                                               
-[24] "\\begin{table}[!htbp] \\centering "                                                                         
-[25] "  \\caption{} "                                                                                             
-[26] "  \\label{fundamentalDynamics} "                                                                            
-[27] "\\begin{tabular}{@{\\extracolsep{5pt}} c} "                                                                 
-[28] "\\\\[-1.8ex]\\hline "                                                                                       
-[29] "\\hline \\\\[-1.8ex] "                                                                                      
-[30] "Summary Statistics \\\\ "                                                                                   
-[31] "\\hline \\\\[-1.8ex] "                                                                                      
-[32] "\\end{tabular} "                                                                                            
-[33] "\\end{table} "
+\end{table}
 
@@
 These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
-Figure \ref{Health_timeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+Figure \ref{HealthTimeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
 The possible values are: all, most, some, few, and none.
@@
   \caption{Health outcome over time}
-  \label{Health_timeplots}
+  \label{HealthTimeplots}
 \begin{knitrout}
@@
 
-In Figure \ref{Health_timeplots}, for the variable 'lessIll_ordered', there is much non available data (lessIll_ordered refers to the share of beneficiaries who are less frequently ill).
+In Figure \ref{HealthTimeplots}, for the variable 'lessIll\_ordered', there is much non available data (lessIll\_ordered refers to the share of beneficiaries who are less frequently ill).
 In all years, most organizations say that most beneficiaries are more healthy.
 The least stated category is, that all beneficiaries are less ill.
-That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll_ordered', appears as good as never.
-
-In the second plot of figure \ref{Health_timeplots} (variable 'dietaryKnowledge_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
+That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll\_ordered', appears as good as never.
+
+In the second plot of figure \ref{HealthTimeplots} (variable 'dietaryKnowledge\_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
 The least stated category is that some beneficiaries increased their dietary knowledge.
@@
 
-The the bottom plot of figure \ref{Health_timeplots}, which visualizes the variable 'appreciateHealthy_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
+The the bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
 Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
@@
   \caption{Selfworth and everyday expertise over time}
-  \label{Equality_timeplots}
+  \label{EqualityTimeplots}
 \begin{knitrout}
@@
 
-Figure \ref{Equality_timeplots} shows in its upper plot the development of the answered categories for the variable selfworth_ordered (refers to the share of beneficiaries with improved self-worth).
+Figure \ref{EqualityTimeplots} shows in its upper plot the development of the answered categories for the variable selfworth\_ordered (refers to the share of beneficiaries with improved self-worth).
 Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
@@
 
-In the bottom plot of figure \ref{Equality_timeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
+In the bottom plot of figure \ref{EqualityTimeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
 The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
@@
 If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
-
-As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
-Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
-The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
-In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
-This estimate is highly statistically significant.
-When we exclude outliers, i.e.
-those organizations that give out very many menus or very few menus,
-the estimated coefficient decreases by about one order of magnitude.
-Still, spending not much more than three EUR more goes hand in hand with one extra meal.
-The estimate is also highly statistically significant.
-
-\usepackage{booktabs}
 
@@
 
+As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
+Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
+The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
+In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
+This estimate is highly statistically significant.
+When we exclude outliers, i.e.
+those organizations that give out very many menus or very few menus,
+the estimated coefficient decreases by about one order of magnitude.
+Still, spending not much more than three EUR more goes hand in hand with one extra meal.
+The estimate is also highly statistically significant.
+
 In the remit of the Trips program, the picture looks much different.
@@
 In sum, there seems to be no clear connection between how much money CHILDREN gives to an organization and the number of trips it organizes.
-
-\usepackage{booktabs}
 
@@
 
-Figure \ref{Health_Plots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
+Figure \ref{HealthPlots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
 For these results, we use their ordinal values.
@@
 
-All plots of Figure \ref{Health_Plots} show that most organizations suffice about 5 to 10 healthy food criteria.
+All plots of Figure \ref{HealthPlots} show that most organizations suffice about 5 to 10 healthy food criteria.
 The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
@@
   \caption{Health Outcomes versus Healthy Meals}
-  \label{Health_Plots}
+  \label{HealthPlots}
 \begin{knitrout}
@@
 
-Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millenstein.2020, p.677}.
+Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millstein.2020, p.677}.
 
@@
 
-\section{The effect of the "Entdeckerfonds" on the beneficiaries of the program}
-
-How do children benefit from visiting social institutions that CHILDREN supports financially?
+\section{The Effects of the Trips Program on Participating Beneficiaries}
+
+How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially?
 So far this question could not be empirically validated.
-Hence, one of the biggest challenges was determining a possible solution for measuring causal effects of the programs on the beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with the Mittagstisch program.
-However, not all organizations do receive addtitional funding to provide the Entdeckerfonds program.
-This fact could be used for applying an empirical approach which determines causal effects of the Entdeckerfonds program by comparing a treatment with a control group.
-The aim of this analysis is to show that the trips provided by Entdeckerfonds program funding have a positive effect on selfworth and everyday expertise of the participating children.
-
-Empirical Approach\\
-
-The baseline of the empirical approach is the determination of the treatment and control group.
-Using the data provided by children we specify the treatment group as all organizations that receive funding for both the Entdeckerfonds and the Mittagstisch program.
-On the other hand, the control group represents all organizations that do not receive funding from CHILDREN to provide the Entdeckerfonds.
-
-Determining the treatment and control group this way, however, was a problem.
-
-THerefore we used the cleaned data set and only determined the control group - all organizations that have no values/answers for the questions of the Entdeckerfonds.
-We assume that these organizations did not receive the funding for the Entdeckerfonds and therefore are the control group in our analysis.
-All organizations that gave answers to at least one question of the survey part regarding the entdeckerfonds are considered the treatment group.
-Our analysis is based on this very strong definition of the treatment and control group.
-
-Because we do not have data for the entdeckerfonds survey for the control group as this group is not observed we use the answers of the mittagstisch survey for our analysis.
-THerefore our possible dependent variables are limited as most of the questions are specific to the meals program.
-
-As the dataset does not include the variables for the Entdeckerfonds survey for the control group, the potential outcomes regarding the Entdeckerfonds are not observed.
-Therefore we have to use the survey answers from the Mittagstisch survey.
-
-Generally our data set contains variables from the years 2011 until 2018.
-
-The constellation of the treatment and control group varies from year to year. 
-Assumption: erhalten der treatment gleichbedeutend wie ein verlust
-
-Possible variables as dependent variables
-how we determined that:
-The used variables should not be specific to the mittagstisch but more general and should also apply to the context of the Entdeckerfonds
-possible variables selfworth, day to day skills
-used these variables because these variables could be influenced both by the mittagstisch and entdeckerfonds and are not specific to the entdeckerfonds
-
-looked at the general trends of these two variables with the difference of the treatment and control group to look at whether our idea makes sense
-
-linear regression just to look at whether there are effects
-
-add controls and fixed effects time and id fixedeffects --> explain why (id: specific effects of being in Bayern for example or the subsidy amount)
-how fixed effects are implemented
-
-which control variables we use
-how we determined which controls
-
-% \begin{table}
-% \begin{center}
-% \begin{tabular}{l c}
-% \hline
-%  & Selfworth \\
-% \hline
-% (Intercept)             & $-1.13^{***}$ \\
-%                         & $(0.32)$      \\
-% dfcEF2$treatEF          & $-0.47$       \\
-%                         & $(0.31)$      \\
-% \hline
-% Num. obs.               & $430$         \\
-% R$^2$ (full model)      & $0.47$        \\
-% R$^2$ (proj model)      & $0.47$        \\
-% Adj. R$^2$ (full model) & $0.36$        \\
-% Adj. R$^2$ (proj model) & $0.36$        \\
-% \hline
-% \multicolumn{2}{l}{\scriptsize{$^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$}}
-% \end{tabular}
-% \caption{linear regression}
-% \label{table:coefficients}
-% \end{center}
-% \end{table}
-
-Ende??
-the dataset does not allow a channel analysis but these could be possible channels that might explain the effects we find
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-% Requires LaTeX packages: dcolumn rotating 
-\begin{sidewaystable}[!htbp] \centering 
-  \caption{Regression Results} 
-  \label{} 
-\begin{tabular}{@{\extracolsep{5pt}}lD{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} D{.}{.}{-3} } 
+Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program.
+However, not all organizations receive additional funding to provide the trips program.
+This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group.
+The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+
+\subsection{Empirical Approach}
+
+The basis of the empirical approach is the specification of the treatment and the control group.
+Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program.
+On the other hand, the control group represents all organizations that only receive funding for the meals program.
+Therefore, the social institutions in the control group do not participate in the trips program.
+
+\subsubsection{Specification of the Treatment Group}
+
+When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program.
+As previously mentioned, the CHILDREN survey consists of two parts.
+The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program.
+The dataset shows that there are several organizations that did not provide information regarding the trips program.
+In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
+Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group.
+When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey.
+There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year.
+Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
+Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.
+
+Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
+This implies that an organization remains in the control group as long as it does not receive funding for the trips program.
+Due to this definition, an organization cannot change from the treatment into the control group.
+
+In general, the constellation of the treatment and control group varies across years.
+As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
+At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods.
+In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
+However, the dataset also includes organizations that switch from the treatment to the control group.
+The first definition of the treatment variable does not take this case into account.
+Therefore, we additionally construct a second treatment indicator which is defined as follows:
+\begin{equation}
+TreatEF_{it} =
+\begin{cases}
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
+0, & \text{otherwise}
+\end{cases}
+\end{equation}
+
+Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
+With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
+Consequently, the estimates cannot be very robust.
+Therefore, the results should not be overstated.
+
+\subsubsection{Dependent Variables}
+
+The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group.
+However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group.
+Therefore, we have to use variables of the meals program as outcome variables in our analysis.
+For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
+Firstly, both variables are applicable to the trips program as well as the meals program.
+In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
+
+\subsubsection{Graphical Evidence}
+
+\begin{figure}
+  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \label{selfworth_Trend}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Selfworth-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to selfworth.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \label{dayToDaySkills_Trend}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Daytodayskills-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to everyday expertise.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+To check for differences in treatment and control group, we created descriptive statistics regarding to the variables of interest.
+Figure 5 and Figure 6 represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time  while it decreased in the control group (Figure 5).
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6).
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+To check for differences in treatment and control group, we created the following graphs using descriptive statistics.
+
+The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
+The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
+In the treatment group the average selfworth increased over time while it decreased in the control group.
+Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group.
+The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
+
+\subsubsection{Differences-in-Differences Estimation}
+
+For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children.
+The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group.
+The key identifying assumption for the DID strategy is the common trend assumption.
+The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
+In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
+As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend.
+Therefore, we cannot argue that the common trend assumption is fulfilled.
+
+Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
+\begin{equation}
+\label{didregression}
+  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
+\end{equation}
+
+where $i$ indexes the identification number of each organization supported by CHILDREN and $t$ indexes the year of observation.
+The outcome variable, denoted by $Y_{it}$, is either selfworth or everyday expertise.
+As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$.
+The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+
+The panel data set allows us to implement fixed effects.
+In our analysis we introduce individual fixed effects and time fixed effects.
+The ID fixed effects $\gamma_{i}$ control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
+For example, the state of an organization does not vary over time but might differ across supported social institutions.
+Additionally, the year fixed effects $\delta_{t}$ capture all variables that change across years but are the same for all organizations and within a specific year.
+For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
+
+One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics.
+Therefore, we include a set of control variables to deal with potential selection bias.
+For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
+Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
+
+\subsection{Results}
+
+\subsubsection{Everyday Expertise}
+
+The estimated coefficients of equation XX are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
+Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
+Columns (1) and (3) only include ID fixed effects and year fixed effects without any controls.
+Columns (2) and (4) expand the regression equation by adding the organization specific control variables: Subsidy, total costs and the number of days in a week on which children cook in a social institution.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
 \\[-1.8ex]\hline
-\hline \\[-1.8ex] 
 & \multicolumn{4}{c}{\textit{Dependent variable:}} \\
 \cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{selfworth} \\ 
-\\[-1.8ex] & \multicolumn{1}{c}{(1)} & \multicolumn{1}{c}{(2)} & \multicolumn{1}{c}{(3)} & \multicolumn{1}{c}{(4)}\\ 
-\hline \\[-1.8ex] 
- Constant & 2.796^{***} & 2.870^{***} & 2.774^{***} & 2.847^{***} \\ 
-  & (0.065) & (0.095) & (0.092) & (0.107) \\ 
-  & & & & \\ 
- treatEF & 0.249^{***} & 0.320^{***} & 0.253^{***} & 0.333^{***} \\ 
-  & (0.074) & (0.097) & (0.075) & (0.100) \\ 
-  & & & & \\ 
-\hline \\[-1.8ex] 
-ID fixed effects & No & No & Yes & Yes \\ 
-Time fixed effects & No & Yes & No & Yes \\ 
-Observations & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} & \multicolumn{1}{c}{430} \\ 
-R$^{2}$ & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.026} & \multicolumn{1}{c}{0.036} \\ 
-Adjusted R$^{2}$ & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.017} & \multicolumn{1}{c}{0.022} & \multicolumn{1}{c}{0.015} \\ 
-Residual Std. Error & \multicolumn{1}{c}{0.642 (df = 428)} & \multicolumn{1}{c}{0.644 (df = 421)} & \multicolumn{1}{c}{0.642 (df = 427)} & \multicolumn{1}{c}{0.645 (df = 420)} \\ 
-F Statistic & \multicolumn{1}{c}{11.417$^{***}$ (df = 1; 428)} & \multicolumn{1}{c}{1.916$^{*}$ (df = 8; 421)} & \multicolumn{1}{c}{5.752$^{***}$ (df = 2; 427)} & \multicolumn{1}{c}{1.724$^{*}$ (df = 9; 420)} \\
-\hline 
-\hline \\[-1.8ex] 
-\textit{Note:}  & \multicolumn{4}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
-\end{tabular} 
-\end{sidewaystable}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.326)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.014)$    &           & $(0.014)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.000)$    &           & $(0.000)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Everyday Expertise}
+\label{table:coefficients1}
+\end{center}
+\end{table}
+
+Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
+Therefore, this finding should not be overstated.
+On the other hand, using the alternative specification of the treatment indicator in column (3), the average treatment effect is positive, but remains insignificant.
+Thus, the sign of the estimated treatment effect changes if we use the alternative definition of the treatment variable.
+With the second treatment variable, the number of organizations in the control group increases, as the treatment status depends on actually receiving funding in a given year.
+Nevertheless, the difference in size of the treatment and control group remains relatively large.
+However, the estimate in Column (3) could provide evidence that the treatment effect might be positive and potentially turn significant if the sample size increases.
+
+Adding the organization specific control variables in Column (2) and Column (4) does not influence the size of both effects and the significance substantially.
+
+\subsubsection{Selfworth}
+
+Using selfworth as the outcome variable, the estimates of regression equation \ref{didregression} are reported in Table \ref{table:coefficients2}, whose structure is equal to Table \ref{table:coefficients1}.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.018)$ &           & $(0.017)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.001)$ &           & $(0.001)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.069)$ &           & $(0.069)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation: Results for Selfworth}
+\label{table:coefficients2}
+\end{center}
+\end{table}
+
+Strinkinlgy, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
+In column (1)-(3), the average treatment effect is insignificant.
+However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
+This indicates that participating in the trips program would negatively influence the selfworth of the children and adolescents.
+This surprising result contradicts our hypothesis that the participation in the trips program positively influences the selfworth of the beneficiaries.
+As previously mentioned, the number of observation units in both treatment and control group is relatively small.
+Therefore, this unexpected negative effect of the trips program on selfworth should not be overstated.
+Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
+It might be difficult for the respondents of the survey to assess children specific characteristics, such as selfworth.
+During our visit in Augsburg, the employees confirmed that it is challenging to evaluate the variables asked in the survey for all participants in the entire social institution, especially with a lot of variation in attendance.
+One potential solution for this problem could be to directly ask the children and adolescents.
+Data on the individual level might be more precise because the children could assess themselves better.
+When using variables on the level of beneficiaries, we might observe a positive effect of the trips program on selfworth.
+As reported in the summary statistics, the outcome variable shows a low variation.
+This results from the fact that, most of the time, organizations give the answer “all children” and “most children” when asked about the improvement of children’s selfworth.
+In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
+In the survey of the year 2019, CHILDREN already implemented a wider scale by asking for the percentage of beneficiaries that increased their selfworth.
+As this alternative measuring method is more precise, it might result in a higher variation of answers.
+Therefore, finding significant effects of the trips program on selfworth might be more likely.
 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 8:42:23 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 8:42:24 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
+% Date and time: Thu, Feb 27, 2020 - 8:42:25 PM
 % Requires LaTeX packages: dcolumn 
@@
 
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 20:42:26 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Meals & Mapping, Meals & Information, Meals \\ 
+  \hline
+1 & participateMore & participateMore & 1.00 \\ 
+  2 & tasksLunch & tasksLunch & 1.00 \\ 
+  3 & ownIdeas & ownIdeas & 1.00 \\ 
+  4 & stayLonger & stayLonger & 1.00 \\ 
+  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
+  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
+  7 & foodCulture & foodCulture & 1.00 \\ 
+  8 & lessIll & lessIll & 1.00 \\ 
+  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
+  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
+  11 & addressProblems & addressProblems & 1.00 \\ 
+  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
+  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
+  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
+  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
+  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
+  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
+  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
+  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
+  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
+  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
+  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
+  23 & reduced\_var\_3 & proud & 0.43 \\ 
+  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
+  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
+  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
+  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
+  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
+  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Meals} 
 \label{partitionmeals}
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Information, Meals & 29 & 0.670 & 0.270 & 0 & 0.4 & 1 & 1 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{partitionmeals} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Partition of outcomes, Meals \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
+\end{table}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Thu Feb 27 20:42:26 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Trips & Mapping, Trips & Information, Trips \\ 
+  \hline
+1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
+  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
+  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
+  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
+  5 & tripsBudget & tripsBudget & 1.00 \\ 
+  6 & tripsMoney & tripsMoney & 1.00 \\ 
+  7 & tripsReview & tripsReview & 1.00 \\ 
+  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
+  9 & tripsMobility & tripsMobility & 1.00 \\ 
+  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
+  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
+  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
+  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
+  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
+  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
+  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
+  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
+  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
+  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
+  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Trips} 
 \label{partitiontrips}
-\begin{tabular}{@{\extracolsep{5pt}}lccccccc} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St.
-Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\
-\hline \\[-1.8ex] 
-Information, Trips & 20 & 0.834 & 0.215 & 0 & 0.6 & 1 & 1 \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table}
-
-% Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do, Feb 27, 2020 - 16:52:52
-\begin{table}[!htbp] \centering 
-  \caption{} 
-  \label{partitiontrips} 
-\begin{tabular}{@{\extracolsep{5pt}} c} 
-\\[-1.8ex]\hline 
-\hline \\[-1.8ex] 
-Partition of outcomes, Trips \\ 
-\hline \\[-1.8ex] 
-\end{tabular} 
-\end{table} 
-\begin{kframe}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print.default(m, ..., quote = quote, right = right, max = max): ungültiges 'digits' Argument}}\end{kframe}
+\end{table}
 
 \subsection{A4: OLS Regressions}
+
+% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% # 
+% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% # @
 

### 2020-02-27 paper.Rnw

@@
   \caption{Health outcome over time}
-  \label{Health_timeplots}
+  \label{HealthTimeplots}
 <<HealthTimePlots, echo=FALSE, message=FALSE>>=
@@
   \caption{Selfworth and everyday expertise over time}
-  \label{Equality_timeplots}
+  \label{EqualityTimeplots}
 <<EqualityTimePlots, echo=FALSE, message=FALSE>>=
@@
 texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE)
+{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
 
@@
 texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE)
+{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
 @
@@
   \caption{Health Outcomes versus Healthy Meals}
-  \label{Health_Plots}
+  \label{HealthPlots}
 <<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
@@
 
-where \begin{itshape}{i}\end{itshape} indexes the identification number of each organization supported by CHILDREN and \begin{itshape}{t}\end{itshape} indexes the year of observation.
-The outcome variable, denoted by \begin{itshape}Y_{it}\end{itshape}, is either selfworth or everyday expertise.
-As mentioned in the previous section, \begin{itshape}TreatEF_{it}\end{itshape} represents the treatment status of organization \begin{itshape}{i}\end{itshape} in year \begin{itshape}{t}\end{itshape}.
-The corresponding regression coefficient \begin{itshape}\beta\end{itshape} represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+where $i$ indexes the identification number of each organization supported by CHILDREN and $t$ indexes the year of observation.
+The outcome variable, denoted by $Y_{it}$, is either selfworth or everyday expertise.
+As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$.
+The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
 
@@
 In our analysis we introduce individual fixed effects and time fixed effects.
-The ID fixed effects \begin{itshape}\gamma_{i}\end{itshape} control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
+The ID fixed effects $\gamma_{i}$ control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
 For example, the state of an organization does not vary over time but might differ across supported social institutions.
-Additionally, the year fixed effects \begin{itshape}\delta_{t}\end{itshape} capture all variables that change across years but are the same for all organizations and within a specific year.
+Additionally, the year fixed effects $\delta_{t}$ capture all variables that change across years but are the same for all organizations and within a specific year.
 For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.

### 2020-02-27 paper.Rnw
lg

@@
 For example, Chetty et.
-al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+al (2014) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
 Furthermore, the result of Deckers et.
@@
 The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
-The questions are divided in two categories: the variables regarding to the Mittagstisch, answered by all organizations since they are all part of this program and the Entdeckerfonds variables, answered by the organizations that take part on the Entdeckerfonds program in the respective year.
+The questions are divided in two categories: the variables regarding to the meals program, answered by all organizations since they are all part of this program and the trips program variables, answered by the organizations that take part on the trips program in the respective year.
 Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
@@
 Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6).
-The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
-This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
-However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
-
-To check for differences in treatment and control group, we created the following graphs using descriptive statistics.
-
-The figures represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
-The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
-In the treatment group the average selfworth increased over time while it decreased in the control group.
-Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group.
 The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.

### 2020-02-27 paper.tex
lg

@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 20:41:58 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Thu Feb 27 21:02:17 2020
 \begin{table}[ht]
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c }
+\begin{tabular}{l c c c c c}
 \toprule
@@
 \midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+R$^2$           & $0.43$          & $0.73$         & $0.13$          & $0.21$          & $0.45$           \\
+Adj. R$^2$      & $0.43$          & $0.73$         & $0.12$          & $0.20$          & $0.45$           \\
+Num. obs.       & $329$           & $329$          & $250$           & $250$           & $440$            \\
+RMSE            & $39992.79$      & $27390.90$     & $3629.72$       & $3463.66$       & $39601.41$       \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \midrule
-R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
-Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
-RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
+R$^2$            & $0.0474$       & $0.0729$       & $0.0880$       & $0.1241$       & $0.0504$       \\
+Adj. R$^2$       & $0.0444$       & $0.0671$       & $0.0844$       & $0.1172$       & $0.0476$       \\
+Num. obs.        & $322$          & $319$          & $257$          & $256$          & $334$          \\
+RMSE             & $2.9565$       & $2.8967$       & $1.6981$       & $1.6579$       & $2.9310$       \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
-Num. obs.                      & 428      & 184      & 430      & 187      \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
+R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
+Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   \\
+Num. obs.                      & $428$    & $184$    & $430$    & $187$    \\
+RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \end{table}
+
+\usepackage{graphicx}
 
@@
 \hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
-Num. obs.                      & 426      & 177      & 429      & 181      \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
+R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
+Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   \\
+Num. obs.                      & $426$    & $177$    & $429$    & $181$    \\
+RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
-Num. obs.           & 121          & 120         & 177          & 177          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
+R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       \\
+Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       \\
+Num. obs.           & $121$        & $120$       & $177$        & $177$        \\
+RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
-Num. obs.           & 214      & 212      & 275        & 275      \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
+R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   \\
+Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   \\
+Num. obs.           & $214$    & $212$    & $275$      & $275$    \\
+RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
-Num. obs.           & 213          & 211      & 274          & 274        \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
+R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     \\
+Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    \\
+Num. obs.           & $213$        & $211$    & $274$        & $274$      \\
+RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$                     & 0.51          & 0.73         & 0.09         & 0.22       \\
-Adj. R$^2$                & 0.39          & 0.66         & 0.07         & 0.20       \\
-Num. obs.                 & 88            & 88           & 175          & 175        \\
-RMSE                      & 0.73          & 5.62         & 0.94         & 7.77       \\
+R$^2$                     & $0.51$        & $0.73$       & $0.09$       & $0.22$     \\
+Adj. R$^2$                & $0.39$        & $0.66$       & $0.07$       & $0.20$     \\
+Num. obs.                 & $88$          & $88$         & $175$        & $175$      \\
+RMSE                      & $0.73$        & $5.62$       & $0.94$       & $7.77$     \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:23 PM
+% Date and time: Do, Feb 27, 2020 - 21:02:23
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:24 PM
+% Date and time: Do, Feb 27, 2020 - 21:02:23
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:25 PM
+% Date and time: Do, Feb 27, 2020 - 21:02:23
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 20:42:26 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Thu Feb 27 21:02:23 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 20:42:26 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Thu Feb 27 21:02:23 2020
 \begin{table}[ht]

### 2020-02-27 paper.Rnw
adapted paper

@@
 % latexmk -pdf paper
-
-% Julian's suggestions from February 24
-
-% Freitag: 
-% - CD mit Daten, do-files
-% - Codebook in Anhang 
-% 
-% soll nicht nach Evaluation durch LMU klingen
-% 
-% Seitenbegrenzung egal
-% 
-% Cronbach's alpha
-% 
-% immer robuste Standardfehler
-% 
-% i.year i.id
-% 
-% leading trailing - abdiskontieren
-% 
-% thematisch gegliederter Appendix
-
-% Load graphicx package in your document's preamble
-% Gandrud (2016), p.192
 
@@
 \end{abstract}
-
-\section{Formal requirements}
-all important information on title page, maybe use template\\
-always name sources of tables and graphs\\
-have to cite data sets\\
-latin number pages\\
-
-\section{Examples}
-
-Citing\\
-
-If you want to cite \textcite{Millstein.2020} inline, use this.
-
-If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
-
-If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
-
-% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
 
@@
 
-\section{Regressions}
-
-\subsection{Empirical Approach}
+\section{Feature Selection}
+
+CHILDREN survey many variables, some of which seem closely related to each other.
+We use exploratory factor analysis for dimensionality reduction and employ extracted factors as controls in the models we estimate.
+In the appendix, we use the partition method suggested by \textcite{Millstein.2020} to establish a one-to-one correspondence between apparent and underlying variables.
+
+\subsection{Exploratory Factor Analysis}
+
+The fundamental theorem of factor analysis posits that each observable variable can be expressed as a linear combination of a smaller number of underlying factors as well as an error term.
+The coefficients of the factors are called loadings.
+\parencite[p.310]{Moosbrugger.2008}
+
+For factor analysis, we work with the imputed data set.
+We conduct a separate factor analysis for each model that we want to fit.
+Each time, we include all variables that were recorded in all years the Meals and the Trips program have been run respectively, but exclude those that we want to use as response and predictor in the corresponding model.
+
+First, we determine the optimum number of factors via the stochastic approach of parallel analysis, following the advice of \textcite[p.313]{Moosbrugger.2008}.
+We estimate factor scores and loadings with the Bartlett method, which is similar to a Maximum Likekelihood estimation, and presented as the most convential one in \textcite[p.291]{Eid.2014}.
+As the fundamental theorem of factor analysis has no unique solution, we have to decide on how to rotate the factors.
+As we want them to be orthogonal to each other, we use the rotation technique Varimax, which is recommended for this purpose in \textcite[p.317]{Price.2017}.
+
+% \subsection{Double Selection}
+
+\section{Associations between CHILDREN's grants and selected outcomes}
+
+\subsection{Empirical approach}
+
+In this section, we use a simple linear model, as described in equation \ref{SimpleLinearModel}.
+We estimate each model with the original data set, the one with imputed variables, and the one with excluded outliers.
+When appropriate, we include the relevant extracted factors as controls.
 
@@
 
-In this section we use a simple linear model, as described in equation \ref{SimpleLinearModel}. We look at the association between:
+ We look at the association between:
 
@@
 tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds") 
-
-texreg(list(ss, tss, ssI, tssI ), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
+sfactor = readRDS("./ANALYSIS/Tables/factorselfworthmeals.Rds")
+
+texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
 @
@@
 tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
-
-texreg(list(ds, tds, dsI, tdsI ), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+dfactorm = readRDS("./ANALYSIS/Tables/factordaytodayskillsmeals.Rds")
+dfactort = readRDS("./ANALYSIS/Tables/factordaytodayskillstrips.Rds")
+
+texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
 
@@
 lDGE_iw = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled_weighted.lm.Rds")
-
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
+illfactor = readRDS("./ANALYSIS/Tables/lessIllfactor.Rds")
+
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
 @
@@
 dDGE_iw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled_weighted.lm.Rds")
-
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS  \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
+dietaryf = readRDS("./ANALYSIS/Tables/dietaryknowledgefactor.Rds")
+
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
 @
@@
 aDGE_iw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled_weighted.lm.Rds")
-
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
+appreciatef = readRDS("./ANALYSIS/Tables/appreciatehealthyfactor.Rds")
+
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
 @
@@
 Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
-
-\section{Feature Selection}
-
-\subsection{Factor Analysis}
-
-Benefits of reducing dimensionality can be reduced computational demands, reduced multiple-testing burden, reduced noise, as well as better-behaved data \cite{Millstein.2020, p.677}.
-
-We use imputed data set.
-
-we use the orthogonal rotation technique Varimax, which is recommended in Price (2017, p.
-307) when the goal of analysis is to "minimize complexity of factors by maximizing variance of loadings on each factor"
-We estimate factor scores with the Bartlett method, which is similar to a Maximum Likekelihood estimation, and presented as the most convential one in Eid and Schmidt (2010, p. 291)
-We use maximum likelihood as factoring method
-
-\subsection{Double Selection}
 
@@
 \begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \caption{Trend in share of beneficiaries with improved selfworth}
   \label{selfworth_Trend}
@@
 \begin{figure}
-  \caption{Trend in share of beneficiaries with improved self-worth and with broadened everyday expertise}
+  \caption{Trend in share of beneficiaries with broadened everyday competence}
   \label{dayToDaySkills_Trend}
@@
 In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
-In the survey of the year 2019, CHILDREN already implemented a wider scale by asking for the percentage of beneficiaries that increased their selfworth.
-As this alternative measuring method is more precise, it might result in a higher variation of answers.
-Therefore, finding significant effects of the trips program on selfworth might be more likely.
+Therefore, one challenge for further analysis is to ask for variables that have a potentially higher variation.
 
@@
 
+Until now CHILDREN only influences whether organizations are supported and how much funding they receive to provide both the trips and the meals program.
+However, we find a strong positive correlation between the healthiness of the meals that organizations serve and health related outcomes of children and adolescents.
+During our visit of an organization in Augsburg, the employees told us that both the children and adolescents appreciate the healthy food and demand even more healthier meals.
+This might be one possible way for CHILDREN to improve the beneficiaries’ health without the necessity of spending particularly more money.
+In the yearly meetings, they could point out our results and mention their appreciation of the provision of healthy food.
+Moreover, CHILDREN could request that the organizations fulfill the DGE criteria for the provided meals.
+Due to the good relationship between CHILDREN and the supported social institutions, we think that the organizations are open to implementing this proposal.
+
+On the basis of the processed dataset, we cannot measure the causal effect of the trips program on everyday expertise and selfworth of beneficiaries.
+However, measuring significant effects of CHILDREN’s trips program might be possible if the data structure will be adjusted.
+At this point, we recommend to directly ask the beneficiaries to answer the children specific questions of the survey.
+During our first meeting with CHILDREN we were informed that they already have collected data from children and adolescents directly, that caused additional workload.
+For instance, the organizations need to obtain the permission of the parents.
+Nevertheless, the individual level data are perhaps more precise.
+
+The dataset contains several helpful features that made our analysis easier.
+For example, CHILDREN has asked for many survey questions from the supported organizations in every year across the whole observation period.
+Furthermore, the dataset includes variables regarding increased selfworth and broadened everyday expertise for both programs allowing a comparison of the meals and the trips program.
+Hence, we recommend to continue asking the same questions in every year and selected variables for both programs.
+
 \printbibliography
@@
 In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
+In comparison to the simple linear model, there are only small changes in coefficents.
 
@@
 
-As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit from the VGAM package.
-Equation \ref{PropoddsModel} describes the model setup:
+As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit. Equation \ref{PropoddsModel} describes the model setup:
 

### 2020-02-27 paper.tex
adapted paper

--- 2020-02-27 paper.tex
@@
 
-\section{Formal requirements}
-all important information on title page, maybe use template\\
-always name sources of tables and graphs\\
-have to cite data sets\\
-latin number pages\\
-
-\section{Examples}
-
-Citing\\
-
-If you want to cite \textcite{Millstein.2020} inline, use this.
-
-If you want to cite \parencite[p.4]{Millstein.2020} inline with a page number, use this.
-
-If you want to cite \citeauthor{Millstein.2020} only as authors, use this.
-
-% To have an unnumbered section, place an sterisk in it like this \*{Unnumbered Section}
-
 \section{Introduction}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 20:41:58 2020
+% Thu Feb 27 22:26:53 2020
 \begin{table}[ht]
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   \\
-                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
-                               & $(0.00)$ &          & $(0.00)$ &          \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
-                               &          & $(0.00)$ &          & $(0.00)$ \\
-\hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     \\
-Num. obs.                      & 428      & 184      & 430      & 187      \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              \\
+ML1                            &          &          &          &          & $0.24^{***}$ \\
+                               &          &          &          &          & $(0.06)$     \\
+ML2                            &          &          &          &          & $0.37^{***}$ \\
+                               &          &          &          &          & $(0.05)$     \\
+ML3                            &          &          &          &          & $0.15^{***}$ \\
+                               &          &          &          &          & $(0.04)$     \\
+\hline
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   \\
-                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          \\
-                               & $(0.00)$ &          & $(0.00)$ &          \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  \\
-                               &          & $(0.00)$ &          & $(0.00)$ \\
-\hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     \\
-Num. obs.                      & 426      & 177      & 429      & 181      \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\begin{tabular}{l c c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) & (6) \\
+\hline
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
+ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
+                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
+ML4                            &          &          &          &          &              & $0.49^{***}$ \\
+                               &          &          &          &          &              & $(0.06)$     \\
+\hline
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     \\
-\hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         \\
-Num. obs.           & 121          & 120         & 177          & 177          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         \\
-\hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
+ML1                 &              &             &              &              & $0.12^{*}$   \\
+                    &              &             &              &              & $(0.06)$     \\
+ML2                 &              &             &              &              & $0.27^{***}$ \\
+                    &              &             &              &              & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   \\
-                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ \\
-DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   \\
-                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ \\
-\hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     \\
-Num. obs.           & 214      & 212      & 275        & 275      \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     \\
-\hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS  \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
+ML1                 &          &          &            &          & $0.26^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML2                 &          &          &            &          & $0.24^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML3                 &          &          &            &          & $0.37^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c }
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ \\
-                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   \\
-DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     \\
-                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   \\
-\hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      \\
-Num. obs.           & 213          & 211      & 274          & 274        \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       \\
-\hline
-\multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
+ML1                 &              &          &              &            & $0.03$       \\
+                    &              &          &              &            & $(0.07)$     \\
+ML2                 &              &          &              &            & $0.47^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+ML3                 &              &          &              &            & $0.24^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:23 PM
+% Date and time: Thu, Feb 27, 2020 - 10:27:21 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:24 PM
+% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 8:42:25 PM
+% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 20:42:26 2020
+% Thu Feb 27 22:27:24 2020
 \begin{table}[ht]

### 2020-02-27 paper.Rnw

@@
 
+\begin{figure}
+  \caption{The trend of weekly cooks over time}
+  \label{weeklyCooks_Trend}
+
+<<WeeklyCooks, echo=FALSE>>=
+figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
+print(figureWeeklyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{The Trend of monthly cooks over time}
+  \label{monthlyCooks_Trend}
+
+<<MonthlyCooks, echo=FALSE>>=
+figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
+print(figureMonthlyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-27 paper.Rnw

@@
 \begin{abstract} 
-abstract on separate page
-100 - 150 words
+This study presents the results of the analysis of the data of effects of the non-profit organisation 'CHILDREN for a better world ev'.
+We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
+We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
 \end{abstract}
@@
 Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
+Regressing with the imputed data set with extracted factor scores as controls, we still obtain a slightly postive significant coefficent: An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.18 standard deviations.
+Overall, there is a positive association between the two variables.
 
@@
 This coefficent is as well insignifacant.
+Also, regressing with the imputed data set with extracted factor scores as controls, does not display a profound connection between beneficiaries dietary knowledge and the healthy meals index.
 
@@
 For the imputed dataset we find a similar picture.
+Similary to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.
 
@@
 By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
-A function g is implemented using the arithmetic mean.
-In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
+The function is implemented using the arithmetic mean.
+In contrast to methods like the factor analysis, if a feature is identified to be related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
 What is as well different is the information loss constraint.

### 2020-02-27 paper.Rnw
commit compile

--- 2020-02-27 paper.Rnw
@@
 
-In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
+In addition to table \ref{HealthRegressions-LessIll}, table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
 In comparison to the simple linear model, there are only small changes in coefficents.
@@
 
-In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-This method was developped by Millstein et.
-al in the context of genome analysis.
-
-The partition approach partitions data into subsets of related features.
-It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
-A function g is implemented using the arithmetic mean.
-In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
-What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
-
-In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
+In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
+This method is due to \textcite{Millstein.2020}.
+The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
+
+Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
+This means that the set of all variables is partitioned into subsets.
+A subset may contain only one variable.
+The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
+One can influence the number of subsets by manipulating a threshold limiting information loss.
+
+We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
 It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
 
-Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
-It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
-Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
+Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
+It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
+
+It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
 
@@
 
-\subsection{A4: OLS Regressions}
-
-% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-% # 
-% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
-% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
-% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
-% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
-% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
-% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
-% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
-% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
-% # @
-
-% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-% #expanded model less ill 
-% 
-% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
-% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
-% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
-% @
-
-\subsection{A5: DID Regression Results}
+\subsection{A4: DID Regression Results}
 

### 2020-02-27 paper.tex
commit compile

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:26:53 2020
+% Thu Feb 27 23:03:35 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:21 PM
+% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
+% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
+% Date and time: Thu, Feb 27, 2020 - 11:04:03 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
+% Date and time: Thu, Feb 27, 2020 - 11:04:04 PM
 % Requires LaTeX packages: dcolumn 
@@
 
-In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-This method was developped by Millstein et.
-al in the context of genome analysis.
-
-The partition approach partitions data into subsets of related features.
-It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
-A function g is implemented using the arithmetic mean.
-In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
-What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
-
-In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
+In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
+This method is due to \textcite{Millstein.2020}.
+The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
+
+Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
+This means that the set of all variables is partitioned into subsets.
+A subset may contain only one variable.
+The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
+One can influence the number of subsets by manipulating a threshold limiting information loss.
+
+We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
 It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
 
-Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
-It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
-Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
+Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
+It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
+
+It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
 
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:27:24 2020
+% Thu Feb 27 23:04:04 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:27:24 2020
+% Thu Feb 27 23:04:04 2020
 \begin{table}[ht]
@@
 
+\begin{figure}
+  \caption{The trend of weekly cooks over time}
+  \label{weeklyCooks_Trend}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/WeeklyCooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{The Trend of monthly cooks over time}
+  \label{monthlyCooks_Trend}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/MonthlyCooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-27 paper.tex

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:03:35 2020
+% Thu Feb 27 23:08:35 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
+% Date and time: Thu, Feb 27, 2020 - 11:09:02 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:04:02 PM
+% Date and time: Thu, Feb 27, 2020 - 11:09:03 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:04:03 PM
+% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:04:04 PM
+% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:04:04 PM
+% Date and time: Thu, Feb 27, 2020 - 11:09:05 PM
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:04:04 2020
+% Thu Feb 27 23:09:05 2020
 \begin{table}[ht]

### 2020-02-27 paper.Rnw

@@
 
-\begin{figure}
-  \caption{The trend of weekly cooks over time}
-  \label{weeklyCooks_Trend}
-
-<<WeeklyCooks, echo=FALSE>>=
-figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
-print(figureWeeklyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{The Trend of monthly cooks over time}
-  \label{monthlyCooks_Trend}
-
-<<MonthlyCooks, echo=FALSE>>=
-figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
-print(figureMonthlyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-27 paper.Rnw
xx

--- 2020-02-27 paper.Rnw
@@
 \begin{abstract} 
-This study presents the results of the analysis of the data of effects of the non-profit organisation 'CHILDREN for a better world ev'.
+This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'.
 We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
 We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
+Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
 \end{abstract}
@@
 
-In addition to table \ref{HealthRegressions-LessIll}, table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
+In addition to table \ref{HealthRegressions-LessIll} table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
 In comparison to the simple linear model, there are only small changes in coefficents.
@@
 
-In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
-This method is due to \textcite{Millstein.2020}.
-The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
-
-Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
-This means that the set of all variables is partitioned into subsets.
-A subset may contain only one variable.
-The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
-One can influence the number of subsets by manipulating a threshold limiting information loss.
-
-We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
+In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+This method was developped by Millstein et.
+al in the context of genome analysis.
+
+The partition approach partitions data into subsets of related features.
+It then  summarizes each subset into one new feature.
+By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
+The function is implemented using the arithmetic mean.
+In contrast to methods like the factor analysis, if a feature is identified to be related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
+What is as well different is the information loss constraint.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
+
+In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
 It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
 
-Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
-It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
-
-It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
+Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
+It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
+Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
 
@@
 
-\subsection{A4: DID Regression Results}
+\subsection{A4: OLS Regressions}
+
+% # <<equality_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% # 
+% # lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
+% # lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
+% # ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
+% # td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
+% # sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
+% # dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
+% # tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
+% # tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
+% # @
+
+% <<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+% #expanded model less ill 
+% 
+% lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
+% lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
+% elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.Rds")
+% @
+
+\subsection{A5: DID Regression Results}
 

### 2020-02-27 paper.Rnw
commimt

@@
 
-\title{Effects of CHILDREN's programs}
+\title{Analysis of survey data collected by CHILDREN for a better World e.V.}
 \author{
@@
 \begin{abstract} 
-This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'.
+This study presents the results of the analysis of the data of effects of the non-profit organisation 'CHILDREN for a better world ev'.
 We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
 We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
-Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
 \end{abstract}
@@
 
-the introduction should include: motivation, precise research questions, very short literature review, most important results, further proceedings
-
-CHILDREN's aims for data analysis\\ 
 CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
@@
 
-\subsection{Literature overview}
+\subsection{Literature Overview}
 
@@
 
-\subsection{Trend of grants}
+\subsection{Trends of grants}
 
@@
 
-\subsection{Health relevant variables over time}
+\subsection{Dynamics of Health-Related Variables}
 
@@
 
-\section{Associations between CHILDREN's grants and selected outcomes}
-
-\subsection{Empirical approach}
+\section{Associations Between CHILDREN's Grants and Selected Outcomes}
+
+\subsection{Empirical Approach}
 
@@
 
-\subsection{Direct effects of CHILDREN's grants}
+\subsection{Direct Effects of CHILDREN's Grants}
 

### 2020-02-27 paper.Rnw
xxx

--- 2020-02-27 paper.Rnw
@@
 \begin{abstract} 
-This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'.
-We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
-We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
-Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
+abstract on separate page
+100 - 150 words
 \end{abstract}
@@
 
-the introduction should include: motivation, precise research questions, very short literature review, most important results, further proceedings
-
-CHILDREN's aims for data analysis\\ 
-CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
-We call them organizations in the following.
-They apply to CHILDREN for yearly grants.
-If approved, they are supposed to use them for specific purposes defined by CHILDREN.
+CHILDREN for a better World e.V.
+is a non-profit organization supporting social institutions for children and adolescents across Germany, such as youth centers.
+Their goal is to foster equality of opportunities for the youth in Germany.
+CHILDREN supports poor and disadvantaged families and young people in socially problematic areas.
+Furthermore, they fight child poverty and encourage the youth to engage in society.
+We call the institutions funded by CHILDREN organizations in the following.
+Organizations have to apply for funding from CHILDREN each year again.
+In the application process, CHILDREN requires the applicants to answer a survey which contains questions about outcomes related to CHILDREN’s programs as well as general information about the organization such as the yearly budget.
 CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
-The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them.
+The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and adolescents that visit them.
 In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
 The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
-Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
-
-\subsection{Literature overview}
-
-Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+
+Previous research shows that childhood and youth are central in the development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance.
+Heckmann and Carneiro (2003) show that especially early family factors determine most of the gaps in high school attendance.
 Moreover, Deckers et.
 al.
-(2015) found by experiments in Germany, that children of higher educated parents are significantly more patient.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et.
+(2015) found, by experiments conducted in Germany, that children of higher educated parents are significantly more patient.
+Children from parents with lower income and a lower educational level typically have a lower weight at birth and are born in a later week of gestation, which are all indicators for bad initial conditions (Deckers et.
 al.
@@
 2002).
-Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
+Children that grow up in families with a low socio-economic status are often believed to be less mobile.
 This could have a negative influence on their character development.
 For example, Chetty et.
-al (2014) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
-Furthermore, the result of Deckers et.
+al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the results of Deckers et.
 al.
-(2020) provides causal evidence on the effect of social environment on prosocial attitudes.
-Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
+(2020) provide evidence for the effect of the social environment on prosocial attitudes.
+Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children.
 Heckmann et.
@@
 (2010) investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+The authors show that an investment in the improvement of the childhood conditions could have a high rate of return, even after controlling for possible distortions.
+
+The aim of our project paper is to test whether CHILDREN’s programs positively influence the beneficiaries.
+We look at the associations between the subsidy CHILDREN provides and the share of beneficiaries with broadened everyday expertise and improved selfworth.
+Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries.
+The aim of our applied differences-in-differences estimation is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth.
+On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill.
+By using the differences-in-differences (DID) strategy, the estimates show that the participation in the trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
+Strikingly, we observe a negative association between participating in the trips program and selfworth.
+However, the results of the DID estimation should not be overstated because of the small sample size.
+The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis.
+The summary statistics are presented in section XX.
+We explain the dimensionality reducing method factor analysis in section XX.
+The proceeding section XX reports different regression results.
+In section XX, we implement the differences-in-differences strategy to test for the effects of the trips program.
+Finally, section XX concludes and provides suggestions for CHILDREN.
 
 \section{Data}
-
-To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018.
-In each year they send a survey to the organizations with several questions about the previous year.
-The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
-In some organizations one employee fills in the survey and in others they do it as a team.
-Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
-The number of variables varies over time as well.
-Included are numbers such as the average eaters per meal or the amount of money they provide to the organizations but also general questions.
-For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
-This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
-If an organization does not answer a question, this is documented as a “99”.
-We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
-The surveyed variables change over the years, but some of them are included every year.
-However, we did several steps to get a full dataset we could work with (we could use for our empirical analysis??).
-The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete.
-Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
-Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
-This makes a quick work with R possible since we only use paths relative to the working directory.
-Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
-We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
-Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
-To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
-As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+\label{data}
+
+To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018.
+In each year CHILDREN sends a survey to the organizations with several questions about the previous year.
+The number of organizations varies across years and increases over time: From 52 organizations in 2011 to 68 organizations in 2018.
+In some organizations one specific employee answers the survey questions, while in other institutions the questionnaire is answered in a team.
+As the children and adolescents are not questioned directly, all responses are documented as perceptions of the employees.
+The constellation of the variables in the data set also varies across years.
+For instance, CHILDREN asks for the average amount of kids that increased their confidence or improved their dietary knowledge.
+These questions of the survey are based on a scale of five levels from no to all kids.
+We perform several steps to receive a full dataset, which we use in our empirical analysis.
+Originally, the data was divided into seperate data sets for the respective years.
+We only use the surveys until 2018, because in 2019 some organization-ID´s occurred multiple times and the dataset for 2019 was incomplete.
+To ensure comparability across years, we named all variables the same.
+We merged the different datasets to a common dataset, including all years and variables CHILDREN collected.
 For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
-The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
-Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
-The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
-The questions are divided in two categories: the variables regarding to the meals program, answered by all organizations since they are all part of this program and the trips program variables, answered by the organizations that take part on the trips program in the respective year.
-Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
-
+The three variants are ordinal, standardized and weighted.
+Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
+The final dataset for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
+The questions are divided in two categories.
+The first part of the data set includes variables regarding the meals program.
+The second part contains variables affecting the trips program.
+The final data set comprises the years 2011 to 2018.
 Many organizations do not answer all questions CHILDREN poses.
@@
 Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
-Regressing with the imputed data set with extracted factor scores as controls, we still obtain a slightly postive significant coefficent: An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.18 standard deviations.
-Overall, there is a positive association between the two variables.
 
@@
 This coefficent is as well insignifacant.
-Also, regressing with the imputed data set with extracted factor scores as controls, does not display a profound connection between beneficiaries dietary knowledge and the healthy meals index.
 
@@
 For the imputed dataset we find a similar picture.
-Similary to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.
 
@@
 
-In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
-This method is due to \textcite{Millstein.2020}.
-The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
-
-Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
-This means that the set of all variables is partitioned into subsets.
-A subset may contain only one variable.
-The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
-One can influence the number of subsets by manipulating a threshold limiting information loss.
-
-We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
+In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
+This method was developped by Millstein et.
+al in the context of genome analysis.
+
+The partition approach partitions data into subsets of related features.
+It then  summarizes each subset into one new feature.
+By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
+A function g is implemented using the arithmetic mean.
+In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
+What is as well different is the information loss constraint.
+It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
+
+In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
 It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
 
-Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
-It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
-
-It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
+Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
+It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
+Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
 

### 2020-02-27 paper.tex
xxx

--- 2020-02-27 paper.tex
@@
 (2010) investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+The authors show that an investment in the improvement of the childhood conditions could have a high rate of return, even after controlling for possible distortions.
+
+The aim of our project paper is to test whether CHILDREN’s programs positively influence the beneficiaries.
+We look at the associations between the subsidy CHILDREN provides and the share of beneficiaries with broadened everyday expertise and improved selfworth.
+Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries.
+The aim of our applied differences-in-differences estimation is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth.
+On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill.
+By using the differences-in-differences (DID) strategy, the estimates show that the participation in the trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
+Strikingly, we observe a negative association between participating in the trips program and selfworth.
+However, the results of the DID estimation should not be overstated because of the small sample size.
+The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis.
+The summary statistics are presented in section XX.
+We explain the dimensionality reducing method factor analysis in section XX.
+The proceeding section XX reports different regression results.
+In section XX, we implement the differences-in-differences strategy to test for the effects of the trips program.
+Finally, section XX concludes and provides suggestions for CHILDREN.
 
 \section{Data}
+\label{data}
 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:26:53 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Thu Feb 27 22:37:37 2020
 \begin{table}[ht]
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c }
+\begin{tabular}{l c c c c c}
 \hline
@@
 \hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
-Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   & $0.30$       \\
+Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   & $0.28$       \\
+Num. obs.                      & $428$    & $184$    & $430$    & $187$    & $161$        \\
+RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   & $0.79$       \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c c }
+\begin{tabular}{l c c c c c c}
 \hline
@@
 \hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
-Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   & $0.37$       & $0.37$       \\
+Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   & $0.36$       & $0.35$       \\
+Num. obs.                      & $426$    & $177$    & $429$    & $181$    & $161$        & $169$        \\
+RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   & $0.78$       & $0.80$       \\
 \hline
 \multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
-Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       & $0.19$       \\
+Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       & $0.17$       \\
+Num. obs.           & $121$        & $120$       & $177$        & $177$        & $161$        \\
+RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       & $0.87$       \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
-Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   & $0.31$       \\
+Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   & $0.29$       \\
+Num. obs.           & $214$    & $212$    & $275$      & $275$    & $161$        \\
+RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   & $0.83$       \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
-Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     & $0.37$       \\
+Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    & $0.35$       \\
+Num. obs.           & $213$        & $211$    & $274$        & $274$      & $161$        \\
+RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     & $0.82$       \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:21 PM
+% Date and time: Do., Feb 27, 2020 - 22:37:45
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:22 PM
+% Date and time: Do., Feb 27, 2020 - 22:37:45
 % Requires LaTeX packages: dcolumn 
@@
 
+\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 10:27:23 PM
+% Date and time: Do., Feb 27, 2020 - 22:37:45
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:27:24 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Thu Feb 27 22:37:45 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 22:27:24 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Thu Feb 27 22:37:45 2020
 \begin{table}[ht]

### 2020-02-27 paper.Rnw

@@
 \begin{abstract} 
-abstract on separate page
-100 - 150 words
+This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'.
+We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
+We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
+Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
 \end{abstract}

### 2020-02-28 paper.Rnw

@@
 \section{Introduction}
+
+CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
+We call them organizations in the following.
+They apply to CHILDREN for yearly grants.
+If approved, they are supposed to use them for specific purposes defined by CHILDREN.
+CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
+The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them.
+In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
+The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
+Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
+
+Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
+Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
+Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
+This could have a negative influence on their character development.
+For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes.
+Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
+\textcite{Heckman.2010} investigated a preschool education program in the US.
+He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
 
@@
 The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis.
-The summary statistics are presented in section XX.
-We explain the dimensionality reducing method factor analysis in section XX.
-The proceeding section XX reports different regression results.
-In section XX, we implement the differences-in-differences strategy to test for the effects of the trips program.
-Finally, section XX concludes and provides suggestions for CHILDREN.
+Then we present summary statistics.
+We explain the dimensionality reducing method factor analysis.
+The proceeding section reports different regression results.
+After that, we implement the differences-in-differences strategy to test for the effects of the trips program.
+Finally, we conclude and provide suggestions for CHILDREN.
 
@@
 This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-https://www.schuleplusessen.de/startseite/
 
@@
 
-The estimated coefficients of equation XX are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
+The estimated coefficients of equation 4 are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
 Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
@@
 
+\section{Division of tasks}
+
+Data preparation, fundamental dynamics: everybody\\
+Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-28 paper.tex

--- 2020-02-27 paper.tex
@@
 
-\subsection{Literature overview}
-
 Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Heckmann and Carneiro (2003) show that especially early family factors determine the most of gaps in highschool attendance.
+Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
+Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
+This could have a negative influence on their character development.
+For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes.
+Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
+\textcite{Heckman.2010} investigated a preschool education program in the US.
+He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+
+CHILDREN for a better World e.V.
+is a non-profit organization supporting social institutions for children and adolescents across Germany, such as youth centers.
+Their goal is to foster equality of opportunities for the youth in Germany.
+CHILDREN supports poor and disadvantaged families and young people in socially problematic areas.
+Furthermore, they fight child poverty and encourage the youth to engage in society.
+We call the institutions funded by CHILDREN organizations in the following.
+Organizations have to apply for funding from CHILDREN each year again.
+In the application process, CHILDREN requires the applicants to answer a survey which contains questions about outcomes related to CHILDREN’s programs as well as general information about the organization such as the yearly budget.
+CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
+The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and adolescents that visit them.
+In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
+The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
+
+Previous research shows that childhood and youth are central in the development of character traits and future opportunities.
+Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
+Heckmann and Carneiro (2003) show that especially early family factors determine most of the gaps in high school attendance.
 Moreover, Deckers et.
 al.
-(2015) found by experiments in Germany, that children of higher educated parents are significantly more patient.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions (Deckers et.
+(2015) found, by experiments conducted in Germany, that children of higher educated parents are significantly more patient.
+Children from parents with lower income and a lower educational level typically have a lower weight at birth and are born in a later week of gestation, which are all indicators for bad initial conditions (Deckers et.
 al.
@@
 (2010) investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
+The authors show that an investment in the improvement of the childhood conditions could have a high rate of return, even after controlling for possible distortions.
+
+The aim of our project paper is to test whether CHILDREN’s programs positively influence the beneficiaries.
+We look at the associations between the subsidy CHILDREN provides and the share of beneficiaries with broadened everyday expertise and improved selfworth.
+Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries.
+The aim of our applied differences-in-differences estimation is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth.
+On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill.
+By using the differences-in-differences (DID) strategy, the estimates show that the participation in the trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
+Strikingly, we observe a negative association between participating in the trips program and selfworth.
+However, the results of the DID estimation should not be overstated because of the small sample size.
+The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis.
+Then we present summary statistics.
+We explain the dimensionality reducing method factor analysis.
+The proceeding section reports different regression results.
+After that, we implement the differences-in-differences strategy to test for the effects of the trips program.
+Finally, we conclude and provide suggestions for CHILDREN.
 
 \section{Data}
-
-To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018.
-In each year they send a survey to the organizations with several questions about the previous year.
-The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
-In some organizations one employee fills in the survey and in others they do it as a team.
-Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
-The number of variables varies over time as well.
-Included are numbers such as the average eaters per meal or the amount of money they provide to the organizations but also general questions.
-For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
-This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
-If an organization does not answer a question, this is documented as a “99”.
-We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
-The surveyed variables change over the years, but some of them are included every year.
-However, we did several steps to get a full dataset we could work with (we could use for our empirical analysis??).
-The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete.
-Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
-Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
-This makes a quick work with R possible since we only use paths relative to the working directory.
-Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
-We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
-Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
-To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
-As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+\label{data}
+
+To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018.
+In each year CHILDREN sends a survey to the organizations with several questions about the previous year.
+The number of organizations varies across years and increases over time: From 52 organizations in 2011 to 68 organizations in 2018.
+In some organizations one specific employee answers the survey questions, while in other institutions the questionnaire is answered in a team.
+As the children and adolescents are not questioned directly, all responses are documented as perceptions of the employees.
+The constellation of the variables in the data set also varies across years.
+For instance, CHILDREN asks for the average amount of kids that increased their confidence or improved their dietary knowledge.
+These questions of the survey are based on a scale of five levels from no to all kids.
+We perform several steps to receive a full dataset, which we use in our empirical analysis.
+Originally, the data was divided into seperate data sets for the respective years.
+We only use the surveys until 2018, because in 2019 some organization-ID´s occurred multiple times and the dataset for 2019 was incomplete.
+To ensure comparability across years, we named all variables the same.
+We merged the different datasets to a common dataset, including all years and variables CHILDREN collected.
 For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
-The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
-Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
-The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
-The questions are divided in two categories: the variables regarding to the meals program, answered by all organizations since they are all part of this program and the trips program variables, answered by the organizations that take part on the trips program in the respective year.
-Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
-
+The three variants are ordinal, standardized and weighted.
+Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
+The final dataset for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
+The questions are divided in two categories.
+The first part of the data set includes variables regarding the meals program.
+The second part contains variables affecting the trips program.
+The final data set comprises the years 2011 to 2018.
 Many organizations do not answer all questions CHILDREN poses.
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:08:35 2020
+% Thu Feb 27 23:48:26 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:09:02 PM
+% Date and time: Thu, Feb 27, 2020 - 11:48:53 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:09:03 PM
+% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
+% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:09:04 PM
+% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
 % Requires LaTeX packages: dcolumn 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:09:05 PM
+% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:09:05 2020
+% Thu Feb 27 23:48:56 2020
 \begin{table}[ht]

### 2020-02-28 ANALYSIS/DATA/Impute.R
compile pdf

@@ -1,63 +1,11 @@
-# outcomesMeals <- c("participateMore",
-#                    "tasksLunch",
-#                    "monthlyCooks",
-#                    "weeklyCooks",
-#                    "shoppers",
-#                    "ownIdeas",
-#                    "stayLonger",
-#                    "easyDishes",
-#                    "dietaryKnowledge",
-#                    "appreciateHealthy",
-#                    "foodCulture",
-#                    "influenceHome",
-#                    "cookAtHome",
-#                    "askRecipes",
-#                    "moreConcentrated",
-#                    "moreBalanced",
-#                    "lessIll",
-#                    "dayToDaySkills",
-#                    "moreIndependent",
-#                    "betterTeamwork",
-#                    "betterReading",
-#                    "betterNumbers",
-#                    "betterGrades",
-#                    "moreRegularSchoolVisits",
-#                    "selfworth",
-#                    "moreOpen",
-#                    "moreConfidence",
-#                    "addressProblems",
-#                    "proud")
-# 
-# outcomesTrips <- c("tripsSuggestions",
-#                    "tripsDecisions",
-#                    "tripsOrganization",
-#                    "tripsCostCalculation",
-#                    "tripsBudget",
-#                    "tripsMoney",
-#                    "tripsReview",
-#                    "tripsPublicTransport",
-#                    "tripsMobility",
-#                    "tripsNewPlaces",
-#                    "tripsNewCommunities",
-#                    "tripsNewIdeas",
-#                    "tripsAdditionalActivities",
-#                    "tripsSpecificSkills",
-#                    "tripsDayToDaySkills",
-#                    "tripsSuccess",
-#                    "tripsSelfEfficacy",
-#                    "tripsSelfworth", 
-#                    "tripsSocialSkills",
-#                    "tripsFrustrationTolerance")
-
-
 # impute missing values in all variables where there are fewer missing values than in DGECriteriaNo
 
 ## impute mode
 
-# mergedDataImputeAll <- mergedData[, colSums(is.na(mergedData)) < nrow(mergedData)] %>% 
-#   select_if(is.numeric) %>%    
-#   impute_most_freq() %>% 
-#   dplyr::select(!tidyselect::contains('scaled'))
+mergedDataImputeAll <- mergedData[, colSums(is.na(mergedData)) < nrow(mergedData)] %>% 
[…]

### 2020-02-28 ANALYSIS/MakeAnalysis.R

@@ -1,14 +1,43 @@
+# Summary statistics
+
 source(encoding = "UTF8", "./ANALYSIS/SummaryStatistics.R")
-# source(encoding = "UTF8", "./ANALYSIS/SummaryStatistics_ggplot.R")
+
+# Plots of health-related variables
+
 source(encoding = "UTF8", "./ANALYSIS/PlotHealthVariables.R")
+
+# Plots of dynamics of selected outcomes
+
 source(encoding = "UTF8", "./ANALYSIS/PlotVariablesOverTime.R")
+
+# Factor analysis Meals program
+
 source(encoding = "UTF8", "./ANALYSIS/factor_analysis.R")
-source(encoding = "UTF8", "./ANALYSIS/double-selection.R")
-source(encoding = "UTF8", "./ANALYSIS/Partition.R")
+
+# Factor analysis Trips program
+
+source(encoding = "UTF8", "./ANALYSIS/factoranalysis_trips.R")
+
+# Associations between CHILDREN's grants and organization's direct outputs
+
 source(encoding = "UTF8", "./ANALYSIS/MetricRegressions.R")
+
+# Associations between healthiness of meals and health-related outcomes
+
 source(encoding = "UTF8", "./ANALYSIS/HealthRegressions.R")
+
+# Regressions with extracted factors as controls
+
+source(encoding = "UTF8", "./ANALYSIS/FactorRegressions.R")
+
+# Cumulative logit regressions
+
 source(encoding = "UTF8", "./ANALYSIS/PropoddsRegressions.R")
+
+# Association between CHILDREN's grants and selected outcomes
+
 source(encoding = "UTF8", "./ANALYSIS/Selfworth_dayToDaySkills.R")
-# source(encoding = "UTF8", "./ANALYSIS/DATA/regression_tables.R")
 
+# Partition analysis
 
+source(encoding = "UTF8", "./ANALYSIS/Partition.R")

### 2020-02-28 ANALYSIS/PlotVariablesOverTime.R

@@ -3,7 +3,7 @@
 
 #setthevariables
 
-response= names(mergedData)
+responset = names(mergedData)
 # [5:213]
 # expl= names(mergedData)[4]
 

### 2020-02-28 ANALYSIS/DATA/MakeDID.R
compile pdf

@@ -1,36 +1,0 @@
-#### Make file for the DiD estimations ####
-
-### Joining the required R scripts
-
-# Create the data set used in the empirical 
-source(encoding = "UTF8", "./ANALYSIS/DATA/MakeGather.R")
-
-# Preparation of defining the treatment and control group
-source(encoding = "UTF8", "./ANALYSIS/DATA/control_gruppe.R")
-
-# Definition of the second treatment variable
-source(encoding = "UTF8", "./ANALYSIS/DATA/treat_dummy.R")
-
-# Generate dummy variables for every organization ID
-source(encoding = "UTF8", "./ANALYSIS/DATA/control_IDFixedEffects.R")
-
-# DiD-estimation and regression tables
-source(encoding = "UTF8", "./ANALYSIS/DATA/did_estimation_final.R")
-
-
-
-#### Make file for figure 5 and 6 (Section 6.1.3) and figure 7 and 8 (Appendix A4)
-
-# Create the data set used in the empirical 
-source(encoding = "UTF8", "./ANALYSIS/DATA/MakeGather.R")
-
-# Preparation of defining the treatment and control group
-source(encoding = "UTF8", "./ANALYSIS/DATA/control_gruppe.R")
-
-# Time series of different variables
-source(encoding = "UTF8", "./ANALYSIS/DATA/advanced_timeseries.R")
-
-# Creating plots
-source(encoding = "UTF8", "./ANALYSIS/DATA/advanced_timeseries_ggplot.R")
-
-

### 2020-02-28 ANALYSIS/MakeDID.R

@@ -2,35 +2,29 @@
 
 ### Joining the required R scripts
 
-# Create the data set used in the empirical 
-source(encoding = "UTF8", ".//DATA/MakeGather.R")
-
 # Preparation of defining the treatment and control group
-source(encoding = "UTF8", ".//DATA/control_gruppe.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/control_gruppe.R")
 
 # Definition of the second treatment variable
-source(encoding = "UTF8", "./DATA/treat_dummy.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/treat_dummy.R")
 
 # Generate dummy variables for every organization ID
-source(encoding = "UTF8", "./DATA/control_IDFixedEffects.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/control_IDFixedEffects.R")
 
 # DiD-estimation and regression tables
-source(encoding = "UTF8", "./DATA/did_estimation_final.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/did_estimation_final.R")
 
 
 
 #### Make file for figure 5 and 6 (Section 6.1.3) and figure 7 and 8 (Appendix A4)
 
-# Create the data set used in the empirical 
-source(encoding = "UTF8", "./DATA/MakeGather.R")
-
 # Preparation of defining the treatment and control group
-source(encoding = "UTF8", "./DATA/control_gruppe.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/control_gruppe.R")
 
 # Time series of different variables
-source(encoding = "UTF8", "./DATA/advanced_timeseries.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/advanced_timeseries.R")
 
 # Creating plots
-source(encoding = "UTF8", "./DATA/advanced_timeseries_ggplot.R")
+source(encoding = "UTF8", "./ANALYSIS/DATA/advanced_timeseries_ggplot.R")
 
 

### 2020-02-29 presentation.Rnw
Created presentation

\documentclass{beamer}

\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{eurosym}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{floatrow}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{subfigure}
\usepackage[flushleft]{threeparttable}
\usepackage{booktabs}
\usepackage{adjustbox}
\usepackage{sidecap}
\usepackage{ifthen}
\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
\usepackage[hidelinks]{hyperref}
% \graphicspath{{./Visuals/}}
\usetheme{CambridgeUS}
\usecolortheme{dolphin}
\addbibresource{references.bib}

% Fancy fit image command with optional caption copied from https://www.patrickbaylis.com/posts/2018-10-11-beamer-resizing/
\makeatletter
\newcommand{\fitimage}[2][\@nil]{
	\begin{figure}
		\begin{adjustbox}{width=0.9\textwidth, totalheight=\textheight-2\baselineskip-2\baselineskip,keepaspectratio}
			\includegraphics{#2}
		\end{adjustbox}
		\def\tmp{#1}%
		\ifx\tmp\@nnil
		\else
		\caption{#1}
		\fi
	\end{figure}
}
\makeatother

\rmfamily
\title[Cleansing/Sullying Effects of Recessions]{Analyse der Survey-Daten von CHILDREN for a better World e.V. \\
	\small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}}
\author[Laura, Laura, Jonathan, Rafael und Yannick]{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
\date{March 3, 2020}

\begin{document}
	\begin{frame}
	\maketitle
\end{frame}

\frame{\frametitle{Table of Contents}
	\tableofcontents
}

\section{Introduction}
\subsection*{Terminology}

\frame{\frametitle{Terminology}
	\begin{itemize}
		\item{Properties of recessions:}
		\begin{itemize}
			\item{Cleansing effects: relatively unproductive firms exit in and around recessions}
			\item{Sullying effects: more firms become relatively unproductive/ unproductive firms become 
				even more unproductive in and around recessions}
		\end{itemize}
		\item{Effects on productivity dispersion:}
		\begin{itemize}
			\item{Productivity dispersion is \textit{procyclical}, when cleansing effects are at work}
			\item{Productivity dispersion is \textit{countercyclical}, when sullying effects are dominant}
		\end{itemize}
	\end{itemize}
}

\frame{\frametitle{Illustration of concepts}
	\begin{figure}[h]
		\includegraphics[width = 5.5cm]{gdp_growth.pdf}
		\includegraphics[width = 5.5cm]{norm_distribution.pdf}
		\caption{Business Cycles and Probability Densitiy Function (\footnotesize{\textit{Source: Own Illustration}})}
	\end{figure}
}

\subsection*{Relevance}
\frame{\frametitle{Why Should We Care?}
	\begin{enumerate}
		\item[1]{Relevance for the economy \& society:}
		\begin{itemize}
			\item{Various important connections between the nature of recessions and economic welfare:
				\begin{itemize}
					\item{Short-run: Besides undesirable effects of recessions (e.g. unemployment, higher government deficits, lower 
						profiability), do recessions have a \textit{creative destruction}-quality as proposed 
						by Pre-Keynesian liquidationists?}
					\item{Long-run: Are recessions crucial for promoting long-run technological progress, i.e. productivity 
						growth?}
				\end{itemize}
			}
		\end{itemize}
		\item[2]{Economic policy implications:
			\begin{itemize}
				\item{Should fiscal and monetary policy even focus on preventing or mitigating economic recessions?}
				\item{If recessions have (undesirable) sullying properties, which policy instruments 
					could be helpful for eliminating respective causes (e.g. market imperfections, liquiditiy frictions)}
		\end{itemize}}
	\end{enumerate}
}

\frame{\frametitle{Why Should We Care?}
	\begin{enumerate}    
		\item[3]{Academia:}
		\begin{itemize}
			\item{Assessing the behavior of micro-level variables over the business cycle is essential 
				for comprehending and predicting aggregate macroeconomic outcomes}
			\item{Which theoretical models in terms of recession properties are backed by empirical evidence?}
		\end{itemize}
	\end{enumerate}
}

\subsection*{Literature}
\frame{\frametitle{Related Literature}
	\begin{itemize}
		\item{Extensive (recent) literature on how firm-level-variables and their cross-sectional dispersion behave over the business cycle 
			(see \cite{10.1257/aer.104.4.1392}, \cite{doi:10.1111/j.0013-0427.2004.00371.x}, \cite{NBERw18245})}
		\item{Identification of recession properties via resource (i.e. production input) reallocation 
			in and around times of economic downturn (e.g. \cite{10.1111/j.1467-937X.2005.00334.x}, \cite{Mustre})}
		\item{Behavior of productivity dispersion over the business cycle \cite{kehrig}:}
		\begin{itemize}
			\item{Productivity dispersion is \textit{countercyclical} and particularly peaks during 
				or following recessions}
			\item{Results are driven by unproductive firms, becoming even more unproductive during recessions}
			\item{Evidence supports sullying properties}
		\end{itemize}
	\end{itemize}
}

\section{Data}

\frame{\frametitle{Data Sources}
	\begin{itemize}
		\item{Primary source: COMPUSTAT Capital IQ - Fundamentals Annual in North America}
		\begin{itemize}
			\item{Provider: Standard \& Poor's (S\&P), data is primarly drawn from SEC filings}
			\item{Contains annual financial information on publicly traded, active and inactive firms}
			\item{Sample selection issues \cite{Davis}}
			\item{Initial sample: 1950-2018 and firms from all divisions ($n = 450.000$)}
		\end{itemize}
		\item{Additional sources:}
		\begin{itemize}
			\item{Bureau of Economic Analysis: price deflators, GDP-growth and real GDP-values, gross 
				output by industry-data}
			\item{Bureau of Labor Statistics: entry and exit rates within divisions}
		\end{itemize}
	\end{itemize}
}

\frame{\frametitle{Variable selection and grouping levels}
	\begin{itemize}
		\item{Variables of interest:}
		\begin{enumerate}
			\item{Identification variables: GVKEY, fyear}
			\item{Variables for selection purposes: FIC, SIC, AQC, AT}
			\item{Firm-level variables for analysis: PPEGT, PPENT, SALE, EMP, COGS}
		\end{enumerate}
		\item{Data grouping into divisions and industries via SIC codes}
		\item{Within manufacturing: distinction between durable-goods- and non-durable-goods-producing firms}
	\end{itemize}
}

\frame{\frametitle{Data grouping}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 5.5cm]{Divisions.JPG}
		\includegraphics[width = 5.5cm]{Manufacturing.JPG}
		\caption{Data grouping levels according to SIC-codes \newline \footnotesize{\textit{Source: https://www.naics.com/sic-codes-industry-drilldown/}}}
	\end{figure}
}

\frame{\frametitle{Sample Selection and Variable ``Treatments''}
	\begin{enumerate}
		\item{Restrict analysis to US-firms}
		\item{Main focus: manufacturing firms, supplemented by other division(s) for comparative 
			reasons (e.g. services)}
		\item{Exclude:}
		\begin{itemize}
			\item{Utility firms and financial firms}
			\item{Observations in which $AQC > 5\%~ of ~AT$}
			\item{Observations with no entries on firm-level variables}
			\item{Observations with $SALE > 0$ \& $EMP = 0$}
			\item{Observations with $PPEGT = 0$ or $PPENT = 0$}
			\item{Years with too little observations (per industry) to allow for statistically 
				reliable results}
		\end{itemize}
		\item{Denominate nominal value variables in real values by deflating}
	\end{enumerate}
}

\frame{\frametitle{Sample Size}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 5cm]{Observations1.JPG}
		\includegraphics[width = 5cm]{Observations2.JPG}
		\caption{Annual number of observations, (\textit{Source: Own calculations})}
	\end{figure}
}

\frame{\frametitle{Summary Statistics}
	\begin{table}[h]
		\footnotesize
		\centering
		\caption{Descriptive statistics of production inputs and outputs}
		\begin{tabular}{p{2.0cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}}
			\hline\hline \\
			\textbf{Sample} &\hfill Capital &\hfill Labor &\hfill Interm. &\hfill Sale &\hfill \textbf{n} \\
			\hline
			\textbf{Manufacturing} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{107783}\\ 
			mean &\hfill 691.18 &\hfill 4.84 &\hfill 985.16 &\hfill 1400.99 \\
			$\sigma$ &\hfill 5188.13 &\hfill 20.53 &\hfill 6812.45 &\hfill 8815.76  \\
			\hline
			\textbf{Services} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{38218}\\
			mean &\hfill 297.95 &\hfill 5.29 &\hfill 340.46  &\hfill 580.84  \\
			$\sigma$ &\hfill 2162.94 &\hfill 28.37 &\hfill 1823.36 &\hfill 3563.94 \\
			\hline 
			\textbf{Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{67020} \\
			mean &\hfill 464.25 &\hfill 4.62 &\hfill 780.05 &\hfill 1078.07 \\
			\hline
			\textbf{Non-Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{40763} \\
			mean &\hfill 1068.12 &\hfill 5.21 &\hfill 1322.36 &\hfill 1931.90 \\
			\hline %need to find a double-hline!
			\textbf{Overall} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{146001} \\
			\hline\hline
			% Sigma-values need to denominated in smaller letters, or alternatively brackets. 
		\end{tabular} \\
		\vspace{2mm}
		{\tiny \textit{Note: Capital, intermediaries and sales are denominated in mio. USD, labor 
				is denominated in thousands of employees. All figures are rounded to two decimal digits.}}
		\label{tab: 1}
	\end{table}  
}

\section{Dispersion Measurement}
\frame{\frametitle{Estimating Productivity}
	\begin{equation}
	ln~y_{it} = \beta_0 + \beta_k~ln~k_{it-1} + \beta_n ~ ln~n_{it} + \beta_m ~ ln~m_{it} 
	+ \beta_i D_i + \beta_t D_t + \epsilon_{it}
	\end{equation}
	\begin{itemize}
		\small
		\item{$y_{it}$: Real Sales}
		\item{$k_{it-1}$: Constructed Capital via PIM:}
		\item{$n_{it}$: Number of Employees}
		\item{$m_{it}$: Real Cost of Sold Goods}
		\item{$D_i$: Firm Dummy}
		\item{$D_t$: Year Dummy}
		\item{$\epsilon_{it}$: Firm-level productivity}
	\end{itemize}

}

\frame{\frametitle{Compute Productivity Dispersion}
	\begin{block}{\textbf{\color{red}Goal:}}
		\color{black} $\Rightarrow$ Compute an aggregated productivity 
		dispersion measure for every industry
	\end{block}
	\begin{enumerate}
		\item[1.]{Adjustment: control for industry specific productivity growth trend \newline
			$\epsilon_{ijt} = g_{j}t + z_{ijt}$}
		\begin{itemize}
			\item{$\epsilon_{ijt}$: Productivity}
			\item{$g_j$: Industry-specific growth trend}
			\item{$z_{ijt}$: Productivity dispersion}
		\end{itemize}
		\item[2.]{Adjustment: decenter and scale to construct cross-sectional dispersion}
		\item[3.]{Adjustment: control for a long-term trend}
	\end{enumerate}
}

\frame{\frametitle{Dispersion Measure}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 12cm]{Dispersion.JPG}
		\caption{Illustration of adjustment steps (\footnotesize{\textit{Source: Kehrig (2015)}})}
	\end{figure}
}

\frame{\frametitle{The Distribution of Normalized Productivity Dispersion}
	\begin{figure}[h]
		\centering
		\includegraphics[height = 4.5cm, width = 5.5cm]{28_1998.pdf}
		\includegraphics[height = 4.5cm, width = 5.5cm]{34_2003.pdf}
		\caption{Exemplary normalized productivity dispersion for two industries, (\textit{Source: Own illustration})}
	\end{figure}
}

\frame{\frametitle{The Normalized Productivity Dispersion}
	\begin{minipage}[c]{0.6\textwidth}
		\begin{figure}[h]
			\centering
			\includegraphics[width = 7cm]{normalized_productvitiy.pdf}
			\caption{Normalized productivity over years}
		\end{figure}
	\end{minipage}
	\begin{minipage}[b]{0.2\textwidth}
		\begin{flalign*}
		Dispersion_t &= \\
		Median_t[Std_{jt}&(\frac{z_{ijt} - \bar{z_j}}{\sigma_j})]
		\end{flalign*}
	\end{minipage}
}
\frame{\frametitle{Growth-Trends in Productivity-Dispersion}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 8.5cm]{long_final.pdf}
		\caption{Actual dispersion behavior and trends over time, (\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{First Estimations}
	\begin{table}[htb]
		\centering
		\caption{Results of OLS Regression}\vspace{1ex}
		\begin{tabular}{@{}lcccc@{}}
			\toprule[2pt]
			{\bf ln\_sale} & Coefficient & Robust St. Err. & t-Statistics & p-value \\
			\hline
			\bf ln\_capital & 0.4300*** & 0.0097 & 44.12 & 0.000\\
			\bf ln\_emp &0.4801*** & 0.0099 & 48.20 & 0.000\\
			\bf ln\_cog &0.1035*** & 0.0064 & 16.13 & 0.000\\
			\hline 
			\midrule
			\multicolumn{5}{c}{R-squared=0.9681 Adj.R-squared=0.969 RMSE=0.4686}\\
			\bottomrule[2pt]
		\end{tabular}
	\end{table}
}

\frame{\frametitle{First Estimations}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 9cm]{fixed_final.pdf}
		\caption{Annual time-FE-coefficients and GDP-growth (\textit{Source: Own Illustration})}
	\end{figure}
}

\section{Empirical Analysis}
\frame{\frametitle{Duables and Non-Durables Within Manufacturing}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 8cm]{durable_final.pdf}
		\caption{Dispersion of productivity levels within durables and non-durables, (\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{AutoscaledLineDispTot}
	\fitimage{LineDispTot.pdf}
}

\frame{\frametitle{}
	\begin{figure}[h]
		\centering
		\includegraphics[]{LineDispTot.pdf}
		\caption{(\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 9cm]{ScatDispTot.pdf}
		\caption{(\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{}
	\begin{table}[ht]
		\centering
		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
			\begin{tabular}{ccccccc}
				\hline
				Lead in years & All & p-value & Non-Durables & p-value & Durables & p-value \\ 
				\hline
				-2 & 0.195 & 0.12 & -0.144 & 0.30 & 0.030 & 0.83 \\ 
				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
				0 & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
				2 & -0.160 & 0.20 & 0.056 & 0.69 & 0.297 & 0.03 \\ 
				\hline
			\end{tabular}
		\end{adjustbox}
	\end{table}
}

\frame{\frametitle{}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 9cm]{PlotQuantilesLow.pdf}
		\caption{(\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{}
	\begin{figure}[h]
		\centering
		\includegraphics[width = 9cm]{PlotQuantilesHigh.pdf}
		\caption{(\textit{Source: Own Illustration})}
	\end{figure}
}

\frame{\frametitle{Dynamics in the Manufacturing Division}
	\begin{figure}[h]
		\centering
		\includegraphics[width=8cm]{quantile_m_final.pdf}
		\caption{Productivity changes in different manufacturing quantiles, (\textit{Source: Own illustration})}
	\end{figure}
}

\section{Discussion}
\frame{\frametitle{}
	\begin{table}[ht]
		\centering
		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
			\begin{tabular}{lcccccc}
				\hline
				& All & p-value & Non-durables & p-value & Durables & p-value \\ 
				\hline
				Standard Deviation & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
				Variance & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
				Inter-quartile range & 0.005 & 0.97 & 0.114 & 0.41 & -0.140 & 0.31 \\ 
				Median absolute deviation & -0.023 & 0.86 & 0.135 & 0.33 & -0.091 & 0.51 \\ 
				\hline
			\end{tabular}
		\end{adjustbox}
	\end{table}
}

\frame{\frametitle{}
	\begin{table}[ht]
		\centering
		\begin{adjustbox}{{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
				\begin{tabular}{lcccccc}
					\hline
					& All & p-value & Non-durables & p-value & Durables & p-value \\ 
					\hline
					Production - HP filtered ($\lambda = 100$) &  &  & 0.132 & 0.34 & -0.184 & 0.18 \\ 
					Production - HP filtered ($\lambda = 6.25$) &  &  & 0.150 & 0.28 & -0.322 & 0.02 \\ 
					Production growth rate &  &  & 0.032 & 0.82 & -0.343 & 0.01 \\ 
					GDP - HP filtered ($\lambda = 100$) & -0.045 & 0.71 & 0.058 & 0.64 & -0.100 & 0.42 \\ 
					GDP - HP filtered ($\lambda = 6.25$) & -0.121 & 0.33 & 0.109 & 0.38 & -0.129 & 0.29 \\ 
					GDP growth rate & -0.043 & 0.73 & -0.041 & 0.74 & 0.018 & 0.89 \\ 
					\hline
				\end{tabular}
			\end{adjustbox}
		\end{table}
	}

	\section{Conclusion}
	\frame{\frametitle{Conclusion}
		\begin{itemize}
			\item{\textbf{Main result:}}
			\begin{itemize}
				\item{No clear general cyclical or countercyclical pattern}
				\item{But: Productivitiy dispersion is countercyclical for durables}
				\item{Recessions do have (small) sullying effects, in particular in the manufacturing division}
			\end{itemize}
			\item{\textbf{Where to go from here?}}
			\begin{itemize}
				\item{Replicate findings with quarterly data}
				\item{Did policy interventions in the analyzed NBER-recessions already have an impact (potential OVB)?}
				\item{Identify causal link for sullying effecs: Why do unproductive firms remain in business (potential frictions)?}
			\end{itemize}
		\end{itemize}
	}
	\frame[allowframebreaks]{\frametitle{References}
		\tiny\bibliography{Cleansing}
	}

\end{document}

### 2020-02-29 paper.Rnw
compile pdf

@@
 
-partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
-partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
 
@@
 
-\begin{figure}
-  \caption{The trend of weekly cooks over time}
-  \label{weeklyCooks_Trend}
-
-<<WeeklyCooks, echo=FALSE>>=
-figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
-print(figureWeeklyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{The Trend of monthly cooks over time}
-  \label{monthlyCooks_Trend}
-
-<<MonthlyCooks, echo=FALSE>>=
-figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
-print(figureMonthlyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
 \section{Division of tasks}

### 2020-02-29 presentation.Rnw
example slide in presentation

@@
+% Rscript -e "library(knitr); knit('paper.Rnw')"
+% pdflatex paper
+% biber paper
+% pdflatex paper
+% pdflatex paper
+
 \documentclass{beamer}
@@
 \rmfamily
-\title[Cleansing/Sullying Effects of Recessions]{Analyse der Survey-Daten von CHILDREN for a better World e.V. \\
-	\small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}}
+\title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V. \\
+	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}}
 \author[Laura, Laura, Jonathan, Rafael und Yannick]{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
@@
 
-\frame{\frametitle{Illustration of concepts}
-	\begin{figure}[h]
-		\includegraphics[width = 5.5cm]{gdp_growth.pdf}
-		\includegraphics[width = 5.5cm]{norm_distribution.pdf}
-		\caption{Business Cycles and Probability Densitiy Function (\footnotesize{\textit{Source: Own Illustration}})}
-	\end{figure}
-}
-
-\subsection*{Relevance}
-\frame{\frametitle{Why Should We Care?}
-	\begin{enumerate}
-		\item[1]{Relevance for the economy \& society:}
-		\begin{itemize}
-			\item{Various important connections between the nature of recessions and economic welfare:
-				\begin{itemize}
-					\item{Short-run: Besides undesirable effects of recessions (e.g. unemployment, higher government deficits, lower 
-						profiability), do recessions have a \textit{creative destruction}-quality as proposed 
-						by Pre-Keynesian liquidationists?}
-					\item{Long-run: Are recessions crucial for promoting long-run technological progress, i.e. productivity 
-						growth?}
-				\end{itemize}
-			}
-		\end{itemize}
-		\item[2]{Economic policy implications:
-			\begin{itemize}
-				\item{Should fiscal and monetary policy even focus on preventing or mitigating economic recessions?}
-				\item{If recessions have (undesirable) sullying properties, which policy instruments 
-					could be helpful for eliminating respective causes (e.g. market imperfections, liquiditiy frictions)}
-		\end{itemize}}
-	\end{enumerate}
-}
-
-\frame{\frametitle{Why Should We Care?}
-	\begin{enumerate}    
-		\item[3]{Academia:}
-		\begin{itemize}
-			\item{Assessing the behavior of micro-level variables over the business cycle is essential 
-				for comprehending and predicting aggregate macroeconomic outcomes}
-			\item{Which theoretical models in terms of recession properties are backed by empirical evidence?}
-		\end{itemize}
-	\end{enumerate}
-}
-
-\subsection*{Literature}
-\frame{\frametitle{Related Literature}
-	\begin{itemize}
-		\item{Extensive (recent) literature on how firm-level-variables and their cross-sectional dispersion behave over the business cycle 
-			(see \cite{10.1257/aer.104.4.1392}, \cite{doi:10.1111/j.0013-0427.2004.00371.x}, \cite{NBERw18245})}
-		\item{Identification of recession properties via resource (i.e. production input) reallocation 
-			in and around times of economic downturn (e.g. \cite{10.1111/j.1467-937X.2005.00334.x}, \cite{Mustre})}
-		\item{Behavior of productivity dispersion over the business cycle \cite{kehrig}:}
-		\begin{itemize}
-			\item{Productivity dispersion is \textit{countercyclical} and particularly peaks during 
-				or following recessions}
-			\item{Results are driven by unproductive firms, becoming even more unproductive during recessions}
-			\item{Evidence supports sullying properties}
-		\end{itemize}
-	\end{itemize}
-}
-
-\section{Data}
-
-\frame{\frametitle{Data Sources}
-	\begin{itemize}
-		\item{Primary source: COMPUSTAT Capital IQ - Fundamentals Annual in North America}
-		\begin{itemize}
-			\item{Provider: Standard \& Poor's (S\&P), data is primarly drawn from SEC filings}
-			\item{Contains annual financial information on publicly traded, active and inactive firms}
-			\item{Sample selection issues \cite{Davis}}
-			\item{Initial sample: 1950-2018 and firms from all divisions ($n = 450.000$)}
-		\end{itemize}
-		\item{Additional sources:}
-		\begin{itemize}
-			\item{Bureau of Economic Analysis: price deflators, GDP-growth and real GDP-values, gross 
-				output by industry-data}
-			\item{Bureau of Labor Statistics: entry and exit rates within divisions}
-		\end{itemize}
-	\end{itemize}
-}
-
-\frame{\frametitle{Variable selection and grouping levels}
-	\begin{itemize}
-		\item{Variables of interest:}
-		\begin{enumerate}
-			\item{Identification variables: GVKEY, fyear}
-			\item{Variables for selection purposes: FIC, SIC, AQC, AT}
-			\item{Firm-level variables for analysis: PPEGT, PPENT, SALE, EMP, COGS}
-		\end{enumerate}
-		\item{Data grouping into divisions and industries via SIC codes}
-		\item{Within manufacturing: distinction between durable-goods- and non-durable-goods-producing firms}
-	\end{itemize}
-}
-
-\frame{\frametitle{Data grouping}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 5.5cm]{Divisions.JPG}
-		\includegraphics[width = 5.5cm]{Manufacturing.JPG}
-		\caption{Data grouping levels according to SIC-codes \newline \footnotesize{\textit{Source: https://www.naics.com/sic-codes-industry-drilldown/}}}
-	\end{figure}
-}
-
-\frame{\frametitle{Sample Selection and Variable ``Treatments''}
-	\begin{enumerate}
-		\item{Restrict analysis to US-firms}
-		\item{Main focus: manufacturing firms, supplemented by other division(s) for comparative 
-			reasons (e.g. services)}
-		\item{Exclude:}
-		\begin{itemize}
-			\item{Utility firms and financial firms}
-			\item{Observations in which $AQC > 5\%~ of ~AT$}
-			\item{Observations with no entries on firm-level variables}
-			\item{Observations with $SALE > 0$ \& $EMP = 0$}
-			\item{Observations with $PPEGT = 0$ or $PPENT = 0$}
-			\item{Years with too little observations (per industry) to allow for statistically 
-				reliable results}
-		\end{itemize}
-		\item{Denominate nominal value variables in real values by deflating}
-	\end{enumerate}
-}
-
-\frame{\frametitle{Sample Size}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 5cm]{Observations1.JPG}
-		\includegraphics[width = 5cm]{Observations2.JPG}
-		\caption{Annual number of observations, (\textit{Source: Own calculations})}
-	\end{figure}
-}
-
-\frame{\frametitle{Summary Statistics}
-	\begin{table}[h]
-		\footnotesize
-		\centering
-		\caption{Descriptive statistics of production inputs and outputs}
-		\begin{tabular}{p{2.0cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}}
-			\hline\hline \\
-			\textbf{Sample} &\hfill Capital &\hfill Labor &\hfill Interm. &\hfill Sale &\hfill \textbf{n} \\
-			\hline
-			\textbf{Manufacturing} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{107783}\\ 
-			mean &\hfill 691.18 &\hfill 4.84 &\hfill 985.16 &\hfill 1400.99 \\
-			$\sigma$ &\hfill 5188.13 &\hfill 20.53 &\hfill 6812.45 &\hfill 8815.76  \\
-			\hline
-			\textbf{Services} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{38218}\\
-			mean &\hfill 297.95 &\hfill 5.29 &\hfill 340.46  &\hfill 580.84  \\
-			$\sigma$ &\hfill 2162.94 &\hfill 28.37 &\hfill 1823.36 &\hfill 3563.94 \\
-			\hline 
-			\textbf{Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{67020} \\
-			mean &\hfill 464.25 &\hfill 4.62 &\hfill 780.05 &\hfill 1078.07 \\
-			\hline
-			\textbf{Non-Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{40763} \\
-			mean &\hfill 1068.12 &\hfill 5.21 &\hfill 1322.36 &\hfill 1931.90 \\
-			\hline %need to find a double-hline!
-			\textbf{Overall} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{146001} \\
-			\hline\hline
-			% Sigma-values need to denominated in smaller letters, or alternatively brackets. 
-		\end{tabular} \\
-		\vspace{2mm}
-		{\tiny \textit{Note: Capital, intermediaries and sales are denominated in mio. USD, labor 
-				is denominated in thousands of employees. All figures are rounded to two decimal digits.}}
-		\label{tab: 1}
-	\end{table}  
-}
-
-\section{Dispersion Measurement}
-\frame{\frametitle{Estimating Productivity}
-	\begin{equation}
-	ln~y_{it} = \beta_0 + \beta_k~ln~k_{it-1} + \beta_n ~ ln~n_{it} + \beta_m ~ ln~m_{it} 
-	+ \beta_i D_i + \beta_t D_t + \epsilon_{it}
-	\end{equation}
-	\begin{itemize}
-		\small
-		\item{$y_{it}$: Real Sales}
-		\item{$k_{it-1}$: Constructed Capital via PIM:}
-		\item{$n_{it}$: Number of Employees}
-		\item{$m_{it}$: Real Cost of Sold Goods}
-		\item{$D_i$: Firm Dummy}
-		\item{$D_t$: Year Dummy}
-		\item{$\epsilon_{it}$: Firm-level productivity}
-	\end{itemize}
-
-}
-
-\frame{\frametitle{Compute Productivity Dispersion}
-	\begin{block}{\textbf{\color{red}Goal:}}
-		\color{black} $\Rightarrow$ Compute an aggregated productivity 
-		dispersion measure for every industry
-	\end{block}
-	\begin{enumerate}
-		\item[1.]{Adjustment: control for industry specific productivity growth trend \newline
-			$\epsilon_{ijt} = g_{j}t + z_{ijt}$}
-		\begin{itemize}
-			\item{$\epsilon_{ijt}$: Productivity}
-			\item{$g_j$: Industry-specific growth trend}
-			\item{$z_{ijt}$: Productivity dispersion}
-		\end{itemize}
-		\item[2.]{Adjustment: decenter and scale to construct cross-sectional dispersion}
-		\item[3.]{Adjustment: control for a long-term trend}
-	\end{enumerate}
-}
-
-\frame{\frametitle{Dispersion Measure}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 12cm]{Dispersion.JPG}
-		\caption{Illustration of adjustment steps (\footnotesize{\textit{Source: Kehrig (2015)}})}
-	\end{figure}
-}
-
-\frame{\frametitle{The Distribution of Normalized Productivity Dispersion}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[height = 4.5cm, width = 5.5cm]{28_1998.pdf}
-		\includegraphics[height = 4.5cm, width = 5.5cm]{34_2003.pdf}
-		\caption{Exemplary normalized productivity dispersion for two industries, (\textit{Source: Own illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{The Normalized Productivity Dispersion}
-	\begin{minipage}[c]{0.6\textwidth}
-		\begin{figure}[h]
-			\centering
-			\includegraphics[width = 7cm]{normalized_productvitiy.pdf}
-			\caption{Normalized productivity over years}
-		\end{figure}
-	\end{minipage}
-	\begin{minipage}[b]{0.2\textwidth}
-		\begin{flalign*}
-		Dispersion_t &= \\
-		Median_t[Std_{jt}&(\frac{z_{ijt} - \bar{z_j}}{\sigma_j})]
-		\end{flalign*}
-	\end{minipage}
-}
-\frame{\frametitle{Growth-Trends in Productivity-Dispersion}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 8.5cm]{long_final.pdf}
-		\caption{Actual dispersion behavior and trends over time, (\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{First Estimations}
-	\begin{table}[htb]
-		\centering
-		\caption{Results of OLS Regression}\vspace{1ex}
-		\begin{tabular}{@{}lcccc@{}}
-			\toprule[2pt]
-			{\bf ln\_sale} & Coefficient & Robust St. Err. & t-Statistics & p-value \\
-			\hline
-			\bf ln\_capital & 0.4300*** & 0.0097 & 44.12 & 0.000\\
-			\bf ln\_emp &0.4801*** & 0.0099 & 48.20 & 0.000\\
-			\bf ln\_cog &0.1035*** & 0.0064 & 16.13 & 0.000\\
-			\hline 
-			\midrule
-			\multicolumn{5}{c}{R-squared=0.9681 Adj.R-squared=0.969 RMSE=0.4686}\\
-			\bottomrule[2pt]
-		\end{tabular}
-	\end{table}
-}
-
-\frame{\frametitle{First Estimations}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 9cm]{fixed_final.pdf}
-		\caption{Annual time-FE-coefficients and GDP-growth (\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\section{Empirical Analysis}
-\frame{\frametitle{Duables and Non-Durables Within Manufacturing}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 8cm]{durable_final.pdf}
-		\caption{Dispersion of productivity levels within durables and non-durables, (\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{AutoscaledLineDispTot}
-	\fitimage{LineDispTot.pdf}
-}
-
-\frame{\frametitle{}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[]{LineDispTot.pdf}
-		\caption{(\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 9cm]{ScatDispTot.pdf}
-		\caption{(\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{}
-	\begin{table}[ht]
-		\centering
-		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-			\begin{tabular}{ccccccc}
-				\hline
-				Lead in years & All & p-value & Non-Durables & p-value & Durables & p-value \\ 
-				\hline
-				-2 & 0.195 & 0.12 & -0.144 & 0.30 & 0.030 & 0.83 \\ 
-				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-				0 & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-				2 & -0.160 & 0.20 & 0.056 & 0.69 & 0.297 & 0.03 \\ 
-				\hline
-			\end{tabular}
-		\end{adjustbox}
-	\end{table}
-}
-
-\frame{\frametitle{}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 9cm]{PlotQuantilesLow.pdf}
-		\caption{(\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width = 9cm]{PlotQuantilesHigh.pdf}
-		\caption{(\textit{Source: Own Illustration})}
-	\end{figure}
-}
-
-\frame{\frametitle{Dynamics in the Manufacturing Division}
-	\begin{figure}[h]
-		\centering
-		\includegraphics[width=8cm]{quantile_m_final.pdf}
-		\caption{Productivity changes in different manufacturing quantiles, (\textit{Source: Own illustration})}
-	\end{figure}
-}
-
-\section{Discussion}
-\frame{\frametitle{}
-	\begin{table}[ht]
-		\centering
-		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-			\begin{tabular}{lcccccc}
-				\hline
-				& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-				\hline
-				Standard Deviation & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-				Variance & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-				Inter-quartile range & 0.005 & 0.97 & 0.114 & 0.41 & -0.140 & 0.31 \\ 
-				Median absolute deviation & -0.023 & 0.86 & 0.135 & 0.33 & -0.091 & 0.51 \\ 
-				\hline
-			\end{tabular}
-		\end{adjustbox}
-	\end{table}
-}
-
-\frame{\frametitle{}
-	\begin{table}[ht]
-		\centering
-		\begin{adjustbox}{{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-				\begin{tabular}{lcccccc}
-					\hline
-					& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-					\hline
-					Production - HP filtered ($\lambda = 100$) &  &  & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-					Production - HP filtered ($\lambda = 6.25$) &  &  & 0.150 & 0.28 & -0.322 & 0.02 \\ 
-					Production growth rate &  &  & 0.032 & 0.82 & -0.343 & 0.01 \\ 
-					GDP - HP filtered ($\lambda = 100$) & -0.045 & 0.71 & 0.058 & 0.64 & -0.100 & 0.42 \\ 
-					GDP - HP filtered ($\lambda = 6.25$) & -0.121 & 0.33 & 0.109 & 0.38 & -0.129 & 0.29 \\ 
-					GDP growth rate & -0.043 & 0.73 & -0.041 & 0.74 & 0.018 & 0.89 \\ 
-					\hline
-				\end{tabular}
-			\end{adjustbox}
-		\end{table}
-	}
-
-	\section{Conclusion}
-	\frame{\frametitle{Conclusion}
-		\begin{itemize}
-			\item{\textbf{Main result:}}
-			\begin{itemize}
-				\item{No clear general cyclical or countercyclical pattern}
-				\item{But: Productivitiy dispersion is countercyclical for durables}
-				\item{Recessions do have (small) sullying effects, in particular in the manufacturing division}
-			\end{itemize}
-			\item{\textbf{Where to go from here?}}
-			\begin{itemize}
-				\item{Replicate findings with quarterly data}
-				\item{Did policy interventions in the analyzed NBER-recessions already have an impact (potential OVB)?}
-				\item{Identify causal link for sullying effecs: Why do unproductive firms remain in business (potential frictions)?}
-			\end{itemize}
-		\end{itemize}
-	}
+% \frame{\frametitle{Illustration of concepts}
+% 	\begin{figure}[h]
+% 		\includegraphics[width = 5.5cm]{gdp_growth.pdf}
+% 		\includegraphics[width = 5.5cm]{norm_distribution.pdf}
+% 		\caption{Business Cycles and Probability Densitiy Function (\footnotesize{\textit{Source: Own Illustration}})}
+% 	\end{figure}
+% }
+% 
+% \subsection*{Relevance}
+% \frame{\frametitle{Why Should We Care?}
+% 	\begin{enumerate}
+% 		\item[1]{Relevance for the economy \& society:}
+% 		\begin{itemize}
+% 			\item{Various important connections between the nature of recessions and economic welfare:
+% 				\begin{itemize}
+% 					\item{Short-run: Besides undesirable effects of recessions (e.g. unemployment, higher government deficits, lower 
+% 						profiability), do recessions have a \textit{creative destruction}-quality as proposed 
+% 						by Pre-Keynesian liquidationists?}
+% 					\item{Long-run: Are recessions crucial for promoting long-run technological progress, i.e. productivity 
+% 						growth?}
+% 				\end{itemize}
+% 			}
+% 		\end{itemize}
+% 		\item[2]{Economic policy implications:
+% 			\begin{itemize}
+% 				\item{Should fiscal and monetary policy even focus on preventing or mitigating economic recessions?}
+% 				\item{If recessions have (undesirable) sullying properties, which policy instruments 
+% 					could be helpful for eliminating respective causes (e.g. market imperfections, liquiditiy frictions)}
+% 		\end{itemize}}
+% 	\end{enumerate}
+% }
+% 
+% \frame{\frametitle{Why Should We Care?}
+% 	\begin{enumerate}    
+% 		\item[3]{Academia:}
+% 		\begin{itemize}
+% 			\item{Assessing the behavior of micro-level variables over the business cycle is essential 
+% 				for comprehending and predicting aggregate macroeconomic outcomes}
+% 			\item{Which theoretical models in terms of recession properties are backed by empirical evidence?}
+% 		\end{itemize}
+% 	\end{enumerate}
+% }
+% 
+% \subsection*{Literature}
+% \frame{\frametitle{Related Literature}
+% 	\begin{itemize}
+% 		\item{Extensive (recent) literature on how firm-level-variables and their cross-sectional dispersion behave over the business cycle 
+% 			(see \cite{10.1257/aer.104.4.1392}, \cite{doi:10.1111/j.0013-0427.2004.00371.x}, \cite{NBERw18245})}
+% 		\item{Identification of recession properties via resource (i.e. production input) reallocation 
+% 			in and around times of economic downturn (e.g. \cite{10.1111/j.1467-937X.2005.00334.x}, \cite{Mustre})}
+% 		\item{Behavior of productivity dispersion over the business cycle \cite{kehrig}:}
+% 		\begin{itemize}
+% 			\item{Productivity dispersion is \textit{countercyclical} and particularly peaks during 
+% 				or following recessions}
+% 			\item{Results are driven by unproductive firms, becoming even more unproductive during recessions}
+% 			\item{Evidence supports sullying properties}
+% 		\end{itemize}
+% 	\end{itemize}
+% }
+% 
+% \section{Data}
+% 
+% \frame{\frametitle{Data Sources}
+% 	\begin{itemize}
+% 		\item{Primary source: COMPUSTAT Capital IQ - Fundamentals Annual in North America}
+% 		\begin{itemize}
+% 			\item{Provider: Standard \& Poor's (S\&P), data is primarly drawn from SEC filings}
+% 			\item{Contains annual financial information on publicly traded, active and inactive firms}
+% 			\item{Sample selection issues \cite{Davis}}
+% 			\item{Initial sample: 1950-2018 and firms from all divisions ($n = 450.000$)}
+% 		\end{itemize}
+% 		\item{Additional sources:}
+% 		\begin{itemize}
+% 			\item{Bureau of Economic Analysis: price deflators, GDP-growth and real GDP-values, gross 
+% 				output by industry-data}
+% 			\item{Bureau of Labor Statistics: entry and exit rates within divisions}
+% 		\end{itemize}
+% 	\end{itemize}
+% }
+% 
+% \frame{\frametitle{Variable selection and grouping levels}
+% 	\begin{itemize}
+% 		\item{Variables of interest:}
+% 		\begin{enumerate}
+% 			\item{Identification variables: GVKEY, fyear}
+% 			\item{Variables for selection purposes: FIC, SIC, AQC, AT}
+% 			\item{Firm-level variables for analysis: PPEGT, PPENT, SALE, EMP, COGS}
+% 		\end{enumerate}
+% 		\item{Data grouping into divisions and industries via SIC codes}
+% 		\item{Within manufacturing: distinction between durable-goods- and non-durable-goods-producing firms}
+% 	\end{itemize}
+% }
+% 
+% \frame{\frametitle{Data grouping}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 5.5cm]{Divisions.JPG}
+% 		\includegraphics[width = 5.5cm]{Manufacturing.JPG}
+% 		\caption{Data grouping levels according to SIC-codes \newline \footnotesize{\textit{Source: https://www.naics.com/sic-codes-industry-drilldown/}}}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{Sample Selection and Variable ``Treatments''}
+% 	\begin{enumerate}
+% 		\item{Restrict analysis to US-firms}
+% 		\item{Main focus: manufacturing firms, supplemented by other division(s) for comparative 
+% 			reasons (e.g. services)}
+% 		\item{Exclude:}
+% 		\begin{itemize}
+% 			\item{Utility firms and financial firms}
+% 			\item{Observations in which $AQC > 5\%~ of ~AT$}
+% 			\item{Observations with no entries on firm-level variables}
+% 			\item{Observations with $SALE > 0$ \& $EMP = 0$}
+% 			\item{Observations with $PPEGT = 0$ or $PPENT = 0$}
+% 			\item{Years with too little observations (per industry) to allow for statistically 
+% 				reliable results}
+% 		\end{itemize}
+% 		\item{Denominate nominal value variables in real values by deflating}
+% 	\end{enumerate}
+% }
+% 
+% \frame{\frametitle{Sample Size}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 5cm]{Observations1.JPG}
+% 		\includegraphics[width = 5cm]{Observations2.JPG}
+% 		\caption{Annual number of observations, (\textit{Source: Own calculations})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{Summary Statistics}
+% 	\begin{table}[h]
+% 		\footnotesize
+% 		\centering
+% 		\caption{Descriptive statistics of production inputs and outputs}
+% 		\begin{tabular}{p{2.0cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}}
+% 			\hline\hline \\
+% 			\textbf{Sample} &\hfill Capital &\hfill Labor &\hfill Interm. &\hfill Sale &\hfill \textbf{n} \\
+% 			\hline
+% 			\textbf{Manufacturing} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{107783}\\ 
+% 			mean &\hfill 691.18 &\hfill 4.84 &\hfill 985.16 &\hfill 1400.99 \\
+% 			$\sigma$ &\hfill 5188.13 &\hfill 20.53 &\hfill 6812.45 &\hfill 8815.76  \\
+% 			\hline
+% 			\textbf{Services} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{38218}\\
+% 			mean &\hfill 297.95 &\hfill 5.29 &\hfill 340.46  &\hfill 580.84  \\
+% 			$\sigma$ &\hfill 2162.94 &\hfill 28.37 &\hfill 1823.36 &\hfill 3563.94 \\
+% 			\hline 
+% 			\textbf{Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{67020} \\
+% 			mean &\hfill 464.25 &\hfill 4.62 &\hfill 780.05 &\hfill 1078.07 \\
+% 			\hline
+% 			\textbf{Non-Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{40763} \\
+% 			mean &\hfill 1068.12 &\hfill 5.21 &\hfill 1322.36 &\hfill 1931.90 \\
+% 			\hline %need to find a double-hline!
+% 			\textbf{Overall} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{146001} \\
+% 			\hline\hline
+% 			% Sigma-values need to denominated in smaller letters, or alternatively brackets. 
+% 		\end{tabular} \\
+% 		\vspace{2mm}
+% 		{\tiny \textit{Note: Capital, intermediaries and sales are denominated in mio. USD, labor 
+% 				is denominated in thousands of employees. All figures are rounded to two decimal digits.}}
+% 		\label{tab: 1}
+% 	\end{table}  
+% }
+% 
+% \section{Dispersion Measurement}
+% \frame{\frametitle{Estimating Productivity}
+% 	\begin{equation}
+% 	ln~y_{it} = \beta_0 + \beta_k~ln~k_{it-1} + \beta_n ~ ln~n_{it} + \beta_m ~ ln~m_{it} 
+% 	+ \beta_i D_i + \beta_t D_t + \epsilon_{it}
+% 	\end{equation}
+% 	\begin{itemize}
+% 		\small
+% 		\item{$y_{it}$: Real Sales}
+% 		\item{$k_{it-1}$: Constructed Capital via PIM:}
+% 		\item{$n_{it}$: Number of Employees}
+% 		\item{$m_{it}$: Real Cost of Sold Goods}
+% 		\item{$D_i$: Firm Dummy}
+% 		\item{$D_t$: Year Dummy}
+% 		\item{$\epsilon_{it}$: Firm-level productivity}
+% 	\end{itemize}
+% 	
+% }
+% 
+% \frame{\frametitle{Compute Productivity Dispersion}
+% 	\begin{block}{\textbf{\color{red}Goal:}}
+% 		\color{black} $\Rightarrow$ Compute an aggregated productivity 
+% 		dispersion measure for every industry
+% 	\end{block}
+% 	\begin{enumerate}
+% 		\item[1.]{Adjustment: control for industry specific productivity growth trend \newline
+% 			$\epsilon_{ijt} = g_{j}t + z_{ijt}$}
+% 		\begin{itemize}
+% 			\item{$\epsilon_{ijt}$: Productivity}
+% 			\item{$g_j$: Industry-specific growth trend}
+% 			\item{$z_{ijt}$: Productivity dispersion}
+% 		\end{itemize}
+% 		\item[2.]{Adjustment: decenter and scale to construct cross-sectional dispersion}
+% 		\item[3.]{Adjustment: control for a long-term trend}
+% 	\end{enumerate}
+% }
+% 
+% \frame{\frametitle{Dispersion Measure}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 12cm]{Dispersion.JPG}
+% 		\caption{Illustration of adjustment steps (\footnotesize{\textit{Source: Kehrig (2015)}})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{The Distribution of Normalized Productivity Dispersion}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[height = 4.5cm, width = 5.5cm]{28_1998.pdf}
+% 		\includegraphics[height = 4.5cm, width = 5.5cm]{34_2003.pdf}
+% 		\caption{Exemplary normalized productivity dispersion for two industries, (\textit{Source: Own illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{The Normalized Productivity Dispersion}
+% 	\begin{minipage}[c]{0.6\textwidth}
+% 		\begin{figure}[h]
+% 			\centering
+% 			\includegraphics[width = 7cm]{normalized_productvitiy.pdf}
+% 			\caption{Normalized productivity over years}
+% 		\end{figure}
+% 	\end{minipage}
+% 	\begin{minipage}[b]{0.2\textwidth}
+% 		\begin{flalign*}
+% 		Dispersion_t &= \\
+% 		Median_t[Std_{jt}&(\frac{z_{ijt} - \bar{z_j}}{\sigma_j})]
+% 		\end{flalign*}
+% 	\end{minipage}
+% }
+% \frame{\frametitle{Growth-Trends in Productivity-Dispersion}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 8.5cm]{long_final.pdf}
+% 		\caption{Actual dispersion behavior and trends over time, (\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{First Estimations}
+% 	\begin{table}[htb]
+% 		\centering
+% 		\caption{Results of OLS Regression}\vspace{1ex}
+% 		\begin{tabular}{@{}lcccc@{}}
+% 			\toprule[2pt]
+% 			{\bf ln\_sale} & Coefficient & Robust St. Err. & t-Statistics & p-value \\
+% 			\hline
+% 			\bf ln\_capital & 0.4300*** & 0.0097 & 44.12 & 0.000\\
+% 			\bf ln\_emp &0.4801*** & 0.0099 & 48.20 & 0.000\\
+% 			\bf ln\_cog &0.1035*** & 0.0064 & 16.13 & 0.000\\
+% 			\hline 
+% 			\midrule
+% 			\multicolumn{5}{c}{R-squared=0.9681 Adj.R-squared=0.969 RMSE=0.4686}\\
+% 			\bottomrule[2pt]
+% 		\end{tabular}
+% 	\end{table}
+% }
+% 
+% \frame{\frametitle{First Estimations}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 9cm]{fixed_final.pdf}
+% 		\caption{Annual time-FE-coefficients and GDP-growth (\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \section{Empirical Analysis}
+% \frame{\frametitle{Duables and Non-Durables Within Manufacturing}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 8cm]{durable_final.pdf}
+% 		\caption{Dispersion of productivity levels within durables and non-durables, (\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{AutoscaledLineDispTot}
+% 	\fitimage{LineDispTot.pdf}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[]{LineDispTot.pdf}
+% 		\caption{(\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 9cm]{ScatDispTot.pdf}
+% 		\caption{(\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{table}[ht]
+% 		\centering
+% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
+% 			\begin{tabular}{ccccccc}
+% 				\hline
+% 				Lead in years & All & p-value & Non-Durables & p-value & Durables & p-value \\ 
+% 				\hline
+% 				-2 & 0.195 & 0.12 & -0.144 & 0.30 & 0.030 & 0.83 \\ 
+% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
+% 				0 & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
+% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
+% 				2 & -0.160 & 0.20 & 0.056 & 0.69 & 0.297 & 0.03 \\ 
+% 				\hline
+% 			\end{tabular}
+% 		\end{adjustbox}
+% 	\end{table}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 9cm]{PlotQuantilesLow.pdf}
+% 		\caption{(\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width = 9cm]{PlotQuantilesHigh.pdf}
+% 		\caption{(\textit{Source: Own Illustration})}
+% 	\end{figure}
+% }
+% 
+% \frame{\frametitle{Dynamics in the Manufacturing Division}
+% 	\begin{figure}[h]
+% 		\centering
+% 		\includegraphics[width=8cm]{quantile_m_final.pdf}
+% 		\caption{Productivity changes in different manufacturing quantiles, (\textit{Source: Own illustration})}
+% 	\end{figure}
+% }
+% 
+% \section{Discussion}
+% \frame{\frametitle{}
+% 	\begin{table}[ht]
+% 		\centering
+% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
+% 			\begin{tabular}{lcccccc}
+% 				\hline
+% 				& All & p-value & Non-durables & p-value & Durables & p-value \\ 
+% 				\hline
+% 				Standard Deviation & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
+% 				Variance & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
+% 				Inter-quartile range & 0.005 & 0.97 & 0.114 & 0.41 & -0.140 & 0.31 \\ 
+% 				Median absolute deviation & -0.023 & 0.86 & 0.135 & 0.33 & -0.091 & 0.51 \\ 
+% 				\hline
+% 			\end{tabular}
+% 		\end{adjustbox}
+% 	\end{table}
+% }
+% 
+% \frame{\frametitle{}
+% 	\begin{table}[ht]
+% 		\centering
+% 		\begin{adjustbox}{{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
+% 				\begin{tabular}{lcccccc}
+% 					\hline
+% 					& All & p-value & Non-durables & p-value & Durables & p-value \\ 
+% 					\hline
+% 					Production - HP filtered ($\lambda = 100$) &  &  & 0.132 & 0.34 & -0.184 & 0.18 \\ 
+% 					Production - HP filtered ($\lambda = 6.25$) &  &  & 0.150 & 0.28 & -0.322 & 0.02 \\ 
+% 					Production growth rate &  &  & 0.032 & 0.82 & -0.343 & 0.01 \\ 
+% 					GDP - HP filtered ($\lambda = 100$) & -0.045 & 0.71 & 0.058 & 0.64 & -0.100 & 0.42 \\ 
+% 					GDP - HP filtered ($\lambda = 6.25$) & -0.121 & 0.33 & 0.109 & 0.38 & -0.129 & 0.29 \\ 
+% 					GDP growth rate & -0.043 & 0.73 & -0.041 & 0.74 & 0.018 & 0.89 \\ 
+% 					\hline
+% 				\end{tabular}
+% 			\end{adjustbox}
+% 		\end{table}
+% 	}
+% 	
+% 	\section{Conclusion}
+% 	\frame{\frametitle{Conclusion}
+% 		\begin{itemize}
+% 			\item{\textbf{Main result:}}
+% 			\begin{itemize}
+% 				\item{No clear general cyclical or countercyclical pattern}
+% 				\item{But: Productivitiy dispersion is countercyclical for durables}
+% 				\item{Recessions do have (small) sullying effects, in particular in the manufacturing division}
+% 			\end{itemize}
+% 			\item{\textbf{Where to go from here?}}
+% 			\begin{itemize}
+% 				\item{Replicate findings with quarterly data}
+% 				\item{Did policy interventions in the analyzed NBER-recessions already have an impact (potential OVB)?}
+% 				\item{Identify causal link for sullying effecs: Why do unproductive firms remain in business (potential frictions)?}
+% 			\end{itemize}
+% 		\end{itemize}
+% 	}
 	\frame[allowframebreaks]{\frametitle{References}
-		\tiny\bibliography{Cleansing}
+		\tiny\printbibliography
 	}

### 2020-02-29 paper.Rnw
removed wrong apostrophe from word

--- 2020-02-28 paper.Rnw
@@
 Originally, the data was divided into seperate data sets for the respective years.
-We only use the surveys until 2018, because in 2019 some organization-ID´s occurred multiple times and the dataset for 2019 was incomplete.
+We only use the surveys until 2018, because in 2019 some organization-ID's occurred multiple times and the dataset for 2019 was incomplete.
 To ensure comparability across years, we named all variables the same.

### 2020-02-29 presentation.tex
removed wrong apostrophe from word

--- 2020-02-29 presentation.Rnw
@@
-% Rscript -e "library(knitr); knit('paper.Rnw')"
-% pdflatex paper
-% biber paper
-% pdflatex paper
-% pdflatex paper
+% Rscript -e "library(knitr); knit('presentation.Rnw')"
+% pdflatex presentation
+% biber presentation
+% pdflatex presentation
+% pdflatex presentation
 
-\documentclass{beamer}
+\documentclass[hyperref={pdfpagelabels=false}\usepackage[]{graphicx}\usepackage[]{color}
+% maxwidth is the original width if it is less than linewidth
+% otherwise use linewidth (to make sure the graphics do not exceed the margin)
+\makeatletter
+\def\maxwidth{ %
+  \ifdim\Gin@nat@width>\linewidth
+    \linewidth
+  \else
+    \Gin@nat@width
+  \fi
+}
+\makeatother
 
+\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
+\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
+\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
+\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
+\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
+\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
+\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
+\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
+\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
+\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
+\let\hlipl\hlkwb
+
+\usepackage{framed}
+\makeatletter
+\newenvironment{kframe}{%
+ \def\at@end@of@kframe{}%
+ \ifinner\ifhmode%
+  \def\at@end@of@kframe{\end{minipage}}%
+  \begin{minipage}{\columnwidth}%
+ \fi\fi%
+ \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
+ \colorbox{shadecolor}{##1}\hskip-\fboxsep
+     % There is no \\@totalrightmargin, so:
+     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
+ \MakeFramed {\advance\hsize-\width
+   \@totalleftmargin\z@ \linewidth\hsize
+   \@setminipage}}%
+ {\par\unskip\endMakeFramed%
+ \at@end@of@kframe}
+\makeatother
+
+\definecolor{shadecolor}{rgb}{.97, .97, .97}
+\definecolor{messagecolor}{rgb}{0, 0, 0}
+\definecolor{warningcolor}{rgb}{1, 0, 1}
+\definecolor{errorcolor}{rgb}{1, 0, 0}
+\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX
+
+\usepackage{alltt}]{beamer}
+\usepackage{lmodern}
+\usepackage{lscape}
+\usepackage{graphicx}
+\usepackage[utf8]{inputenc}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage{floatrow}
+\usepackage{booktabs}
+% \usepackage{bookmark}
+\usepackage{rotating}
+\usepackage{dcolumn}
 \usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{latexsym}
-\usepackage{eurosym}
-\usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage{dcolumn}
-\usepackage{floatrow}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage{subfigure}
-\usepackage[flushleft]{threeparttable}
-\usepackage{booktabs}
-\usepackage{adjustbox}
-\usepackage{sidecap}
-\usepackage{ifthen}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage[hidelinks]{hyperref}
+\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+% \usepackage[hidelinks]{hyperref}
+% \usepackage{mathtools}
+% \usepackage{amssymb}
+% \usepackage{latexsym}
+% \usepackage{eurosym}
+% \usepackage{xcolor}
+% \usepackage{graphicx}
+% \usepackage{dcolumn}
+% \usepackage{floatrow}
+% \usepackage[english]{babel}
+% \usepackage[utf8]{inputenc}
+% \usepackage{subfigure}
+% \usepackage[flushleft]{threeparttable}
+% \usepackage{booktabs}
+% \usepackage{adjustbox}
+% \usepackage{sidecap}
+% \usepackage{ifthen}
+% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% \usepackage[hidelinks]{hyperref}
 % \graphicspath{{./Visuals/}}
@@
 \rmfamily
-\title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V. \\
-	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}}
-\author[Laura, Laura, Jonathan, Rafael und Yannick]{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
+\title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V. 
+	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}
+	}
+\author[Laura, Laura, Jonathan, Rafael und Yannick]{
+Laura Huber\\
+\and
+Laura Jepsen\\
+\and
+Jonathan Kirschner\\
+\and
+Rafael Schütz\\
+\and 
+Yannick Zurl\\
+\and
+Studentisches Praxisprojekt zur Empirischen Wirtschaftsforschung PaRE3To\\
+\and
+Ludwig-Maximilians-Universität München}
 \date{March 3, 2020}
-
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
 \begin{document}
@@
 	\tableofcontents
+}
+
+\frame{\frametitle{List of Tables}
+	\listoftables
+}
+
+\frame{\frametitle{List of Figures}
+	\listoffigures
 }
@@
 }
+
+\section{Summary Statistics}
+
+\frame{\frametitle{Fundamental Dynamic}}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Sat Feb 29 17:39:39 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
+  \hline
+1 & 2011 & 3748.0 &  & 52 &  \\ 
+  2 & 2012 & 3556.0 & 2803.0 & 51 & 44 \\ 
+  3 & 2013 & 4015.0 & 2823.0 & 55 & 42 \\ 
+  4 & 2014 & 4685.0 & 2752.0 & 55 & 43 \\ 
+  5 & 2015 & 5857.0 & 3823.0 & 55 & 49 \\ 
+  6 & 2016 & 3075.0 & 3819.0 & 59 & 48 \\ 
+  7 & 2017 & 4895.0 & 4150.0 & 64 & 48 \\ 
+  8 & 2018 & 5102.5 & 6911.0 & 68 & 49 \\ 
+   \hline
+\end{tabular}
+\caption{Summary Statistics} 
+\label{fundamentalDynamics}
+\end{table}
 

### 2020-02-29 presentation.Rnw

@@
-% Rscript -e "library(knitr); knit('paper.Rnw')"
-% pdflatex paper
-% biber paper
-% pdflatex paper
-% pdflatex paper
+% Rscript -e "library(knitr); knit('presentation.Rnw')"
+% pdflatex presentation
+% biber presentation
+% pdflatex presentation
+% pdflatex presentation
 
-\documentclass{beamer}
-
+\documentclass[hyperref={pdfpagelabels=false}]{beamer}
+\usepackage{lmodern}
+\usepackage{lscape}
+\usepackage{graphicx}
+\usepackage[utf8]{inputenc}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage{floatrow}
+\usepackage{booktabs}
+% \usepackage{bookmark}
+\usepackage{rotating}
+\usepackage{dcolumn}
 \usepackage{mathtools}
-\usepackage{amssymb}
-\usepackage{latexsym}
-\usepackage{eurosym}
-\usepackage{xcolor}
-\usepackage{graphicx}
-\usepackage{dcolumn}
-\usepackage{floatrow}
-\usepackage[english]{babel}
-\usepackage[utf8]{inputenc}
-\usepackage{subfigure}
-\usepackage[flushleft]{threeparttable}
-\usepackage{booktabs}
-\usepackage{adjustbox}
-\usepackage{sidecap}
-\usepackage{ifthen}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage[hidelinks]{hyperref}
+\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+% \usepackage[hidelinks]{hyperref}
+% \usepackage{mathtools}
+% \usepackage{amssymb}
+% \usepackage{latexsym}
+% \usepackage{eurosym}
+% \usepackage{xcolor}
+% \usepackage{graphicx}
+% \usepackage{dcolumn}
+% \usepackage{floatrow}
+% \usepackage[english]{babel}
+% \usepackage[utf8]{inputenc}
+% \usepackage{subfigure}
+% \usepackage[flushleft]{threeparttable}
+% \usepackage{booktabs}
+% \usepackage{adjustbox}
+% \usepackage{sidecap}
+% \usepackage{ifthen}
+% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% \usepackage[hidelinks]{hyperref}
 % \graphicspath{{./Visuals/}}
@@
 \addbibresource{references.bib}
+
+<<LoadingPackages, include=FALSE>>=
+library(knitr)
+library(xtable)
+library(dplyr)
+library(stargazer)
+library(cowplot)
+library(texreg)
+@
 
@@
 \rmfamily
-\title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V. \\
-	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}}
-\author[Laura, Laura, Jonathan, Rafael und Yannick]{Laura Huber, Laura Jepsen, Jonathan Kirschner, Rafael Schütz, Yannick Zurl}
+\title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V. 
+	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}
+	}
+\author[Laura, Laura, Jonathan, Rafael und Yannick]{
+Laura Huber\\
+\and
+Laura Jepsen\\
+\and
+Jonathan Kirschner\\
+\and
+Rafael Schütz\\
+\and 
+Yannick Zurl\\
+\and
+Studentisches Praxisprojekt zur Empirischen Wirtschaftsforschung PaRE3To\\
+\and
+Ludwig-Maximilians-Universität München}
 \date{March 3, 2020}
@@
 }
+
+\section{Summary Statistics}
+
+\frame{\frametitle{Fundamental Dynamic}}
+<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
+
+colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+
+xtable(fundamental_dynamics,
+                                  # summary = FALSE,
+                                digits = c(0, 0, 1, 1, 0, 0),
+           caption = "Summary Statistics",
+           align = "lccccc", 
+          label = "fundamentalDynamics"
+          )
+
+@
 

### 2020-02-29 paper.tex
compile pdf
ghjklöä
removed wrong apostrophe from word
Update
lg

--- 2020-02-27 paper.tex
@@
 
-To measure the effect of CHILDREN´s engagement on the funded organizations, we use the data CHILDREN collected from 2011 to 2018.
-In each year they send a survey to the organizations with several questions about the previous year.
-The number of organizations varies among the years and increases over time, from 52 in the 2012 survey to 73 in the survey from 2020.
-In some organizations one employee fills in the survey and in others they do it as a team.
-Since the children and adolescents are not questioned directly, all responses are documented through the perception of the employees.
-The number of variables varies over time as well.
-Included are numbers such as the average eaters per meal or the amount of money they provide to the organizations but also general questions.
-For instance, CHILDREN asks the average amount of kids with a better confidence or an improved dietary knowledge in the specific organization.
-This part of the survey must be answered on a scale from zero (no kids) to four (all kids).
-If an organization does not answer a question, this is documented as a “99”.
-We worked with the statistical program “R” and therefore changed the format from 99s to NA´s (not available) to avoid distortions.
-The surveyed variables change over the years, but some of them are included every year.
-However, we did several steps to get a full dataset we could work with (we could use for our empirical analysis??).
-The data was divided into one dataset for each survey from 2011 to 2019, but we only use the surveys till 2018 since in 2019 some organization-ID´s occurred several times and the data for 2019 were incomplete.
-Since each survey includes data about the year before, we changed the names of the dataset to the corresponding year and finally used the years from 2011 to 2018.
-Moreover, we outlined a hierarchical file structure, enabling us to use relative file paths throughout.
-This makes a quick work with R possible since we only use paths relative to the working directory.
-Afterwards we made sure that variables with names containing non-standard characters like German “Umlaute” are correctly read in and established naming conventions.
-We created a file reading the excel sheets and we reviewed and aligned new English-language variable names across the years.
-Moreover, we systematically compared variable names between years by creating a correspondence table, ordered first by variables of 2019, then of 2018 and so on.
-To ensure the comparability between the years, we gave all variables from the different years that equal each other the same name.
-As a next step, we merged the different datasets to one dataset, including all years and variables CHILDREN collected.
+To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018.
+In each year CHILDREN sends a survey to the organizations with several questions about the previous year.
+The number of organizations varies across years and increases over time: From 52 organizations in 2011 to 68 organizations in 2018.
+In some organizations one specific employee answers the survey questions, while in other institutions the questionnaire is answered in a team.
+As the children and adolescents are not questioned directly, all responses are documented as perceptions of the employees.
+The constellation of the variables in the data set also varies across years.
+For instance, CHILDREN asks for the average amount of kids that increased their confidence or improved their dietary knowledge.
+These questions of the survey are based on a scale of five levels from no to all kids.
+We perform several steps to receive a full dataset, which we use in our empirical analysis.
+Originally, the data was divided into seperate data sets for the respective years.
+We only use the surveys until 2018, because in 2019 some organization-ID's occurred multiple times and the dataset for 2019 was incomplete.
+To ensure comparability across years, we named all variables the same.
+We merged the different datasets to a common dataset, including all years and variables CHILDREN collected.
 For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
-The three variants are ordinal, standardized and weighted (FUßNOTE: The variables regarding the Mittagstisch are weighted as variable*0.25*eaterspermeal, the variables that are assigned to the Entdeckerfonds as variable*0.25*tripskidsno).
-Furthermore, we created more new variables: We used the information CHILDREN gave us in another excel-sheet to assign the German states to the corresponding organization-ID and created dummy-variables for each ID, every year and a treatment dummy that will be explained in a later section.
-The final dataset we worked with is structured as follows: Each row represents one organization-ID with the answers the organization gave in the specific year.
-The questions are divided in two categories: the variables regarding to the meals program, answered by all organizations since they are all part of this program and the trips program variables, answered by the organizations that take part on the trips program in the respective year.
-Including the years from 2011 to 2018 and all variables we created, the final dataset has X observations of Y variables.
-
+The three variants are ordinal, standardized and weighted.
+Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
+The final dataset for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
+The questions are divided in two categories.
+The first part of the data set includes variables regarding the meals program.
+The second part contains variables affecting the trips program.
+The final data set comprises the years 2011 to 2018.
 Many organizations do not answer all questions CHILDREN poses.
@@
 
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Thu Feb 27 22:37:37 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Sat Feb 29 17:58:47 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Do., Feb 27, 2020 - 22:37:45
+% Date and time: Sa, Feb 29, 2020 - 17:58:55
 % Requires LaTeX packages: dcolumn 
@@
 
-In addition to the factor analysis which is described in section 6, we would like to introduce to a another dimensionality reduction method called partition.
-This method was developped by Millstein et.
-al in the context of genome analysis.
-
-The partition approach partitions data into subsets of related features.
-It then  summarizes each subset into one new feature.
-By that, it defines a surjective mapping \parencite[p.676]{Millstein.2020}.
-A function g is implemented using the arithmetic mean.
-In contrast to methods like the factor analysis, if a feature is identified as related to a response of interest, the exact subset of features that are implicated to the surjective mapping is known without ambiguity.
-What is as well different is the information loss constraint.
-It lets the extent of dependences among features on a local level guide the extent to which the number of features is reduced \parencite[p.677]{Millstein.2020}.
-
-In the following a threshold of 0.4 is used, meaning that the reduced variable consists of variables which explain each other to at least 40 percent.
+In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
+This method is due to \textcite{Millstein.2020}.
+The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
+
+Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
+This means that the set of all variables is partitioned into subsets.
+A subset may contain only one variable.
+The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
+One can influence the number of subsets by manipulating a threshold limiting information loss.
+
+We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
 It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
 
-Table \ref{partitionmeals} shows the obtained results of the dimensionality reduction for the variables of the Lunch program.
-It displays 10 variables which haven't been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} shows the partitioned results for the variables of the Trips program.
-Here, 12 variables haven't been reduced, and a number of featured variables are summarized to 3 reduced variables.
-
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Thu Feb 27 22:37:45 2020
+Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
+It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
+
+Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
+
+It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
+
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Sat Feb 29 17:58:55 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Thu Feb 27 22:37:45 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Sat Feb 29 17:58:55 2020
 \begin{table}[ht]
@@
 
-\begin{figure}
-  \caption{The trend of weekly cooks over time}
-  \label{weeklyCooks_Trend}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/WeeklyCooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{The Trend of monthly cooks over time}
-  \label{monthlyCooks_Trend}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/MonthlyCooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
+\section{Division of tasks}
+
+Data preparation, fundamental dynamics: everybody\\
+Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
 \section{Ehrenwörtliche Erklärung aller Teilnehmer}

### 2020-02-29 ANALYSIS/SummaryStatistics.R
ijocjjvldkldklllll

@@ -22,6 +22,8 @@ realTripsSubTotal <- mergedData %>%
 #plot the linear time trend of total real trips subsidy trend with ggplot 
 totalRealTripSub <- ggplot(realTripsSubTotal, aes(year, total_TripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x = "Year", y = "Trips, total")
 
+saveRDS(totalRealTripSub, './ANALYSIS/Tables/totalRealTripSub.Rds')
+
 ###median trips subsidy real 
 
 medianRealTripsSubTotal <- mergedData %>%
@@ -32,6 +34,8 @@ medianRealTripsSubTotal <- mergedData %>%
 #plot the linear time trend of median real trips subsidy trend with ggplot 
 medianRealTripSub <- ggplot(medianRealTripsSubTotal, aes(year, Median_TripsSubsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x= "Year", y = "Trips, median")
 
+saveRDS(medianRealTripSub, './ANALYSIS/Tables/medianRealTripSub.Rds')
+
 #total lunch subsidy 
 realSubTotal <- mergedData %>% 
   group_by(year)%>%
@@ -40,6 +44,7 @@ realSubTotal <- mergedData %>%
 #plot the linear time trend of total real subsidy trend with ggplot 
 totalRealSub <- ggplot(realSubTotal, aes(year, total_Subsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x= "Year", y= "Meals, total")
 
+saveRDS(totalRealSub, './ANALYSIS/Tables/totalRealSub.Rds')
 
 #median lunch subsidy 
 
@@ -49,6 +54,8 @@ medianRealSub <- mergedData %>%
   
 #plot the linear time trend of median real trips subsidy trend with ggplot 
 medianRealSub <- ggplot(medianRealSub, aes(year, median_Subsidy)) + geom_line() + geom_smooth(method = "lm") + theme_cowplot(12) + labs(x= "Year", y= "Meals, median")
+
+saveRDS(medianRealSub, './ANALYSIS/Tables/medianRealSub.Rds')
 
 ###per individual 
 
@@ -62,6 +69,7 @@ medianRealSubInd <- mergedData %>%
 #plot the linear time trend of median real trips subsidy per ind trend with ggplot 
[…]

### 2020-02-29 presentation.Rnw
lg
compiling presentation possible

@@
+% in Terminal enter
 % Rscript -e "library(knitr); knit('presentation.Rnw')"
@@
 
-\documentclass[hyperref={pdfpagelabels=false}]{beamer}
-\usepackage{lmodern}
-\usepackage{lscape}
-\usepackage{graphicx}
-\usepackage[utf8]{inputenc}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage{floatrow}
-\usepackage{booktabs}
-% \usepackage{bookmark}
-\usepackage{rotating}
-\usepackage{dcolumn}
-\usepackage{mathtools}
-\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+% when you begin a slide with a table or figure on it, always write
+% \begin{frame}[fragile]
+% the fragile option is important
+
+% to make tables and figures fit, use
+% scalebox = '0.75'
+% or another number
+
+% https://github.com/yihui/knitr/blob/master/inst/examples/knitr-beamer.Rnw
+
+\documentclass{beamer}
+% \usepackage{lmodern}
+% \usepackage{lscape}
+% \usepackage{graphicx}
+% \usepackage[utf8]{inputenc}
+% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% \usepackage{floatrow}
+% \usepackage{booktabs}
+% \usepackage{rotating}
+% \usepackage{dcolumn}
+% \usepackage{mathtools}
+% \usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
 % \usepackage[hidelinks]{hyperref}
@@
 % \graphicspath{{./Visuals/}}
+% \setcounter{secnumdepth}{3}
+% \setcounter{tocdepth}{3}
+% \usepackage{url}
+% \ifx\hypersetup\undefined
+%   \AtBeginDocument{%
+%     \hypersetup{unicode=true,pdfusetitle,
+%  bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+%  breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false}
+%   }
+% \else
+%   \hypersetup{unicode=true,pdfusetitle,
+%  bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+%  breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false}
+% \fi
+% \usepackage{breakurl}
+% 
+% \makeatletter
+%
+% Fancy fit image command with optional caption copied from https://www.patrickbaylis.com/posts/2018-10-11-beamer-resizing/
+% \makeatletter
+% \newcommand{\fitimage}[2][\@nil]{
+% 	\begin{figure}
+% 		\begin{adjustbox}{width=0.9\textwidth, totalheight=\textheight-2\baselineskip-2\baselineskip,keepaspectratio}
+% 			\includegraphics{#2}
+% 		\end{adjustbox}
+% 		\def\tmp{#1}%
+% 		\ifx\tmp\@nnil
+% 		\else
+% 		\caption{#1}
+% 		\fi
+% 	\end{figure}
+% }
+% \makeatother
+% 
+% \rmfamily
+
 \usetheme{CambridgeUS}
-\usecolortheme{dolphin}
-\addbibresource{references.bib}
+% \usecolortheme{dolphin}
+% \addbibresource{references.bib}
+%
+
+\begin{document}
 
@@
 library(texreg)
+opts_chunk$set(fig.path='figure/beamer-',fig.align='center',fig.show='hold',size='footnotesize')
 @
 
-% Fancy fit image command with optional caption copied from https://www.patrickbaylis.com/posts/2018-10-11-beamer-resizing/
-\makeatletter
-\newcommand{\fitimage}[2][\@nil]{
-	\begin{figure}
-		\begin{adjustbox}{width=0.9\textwidth, totalheight=\textheight-2\baselineskip-2\baselineskip,keepaspectratio}
-			\includegraphics{#2}
-		\end{adjustbox}
-		\def\tmp{#1}%
-		\ifx\tmp\@nnil
-		\else
-		\caption{#1}
-		\fi
-	\end{figure}
-}
-\makeatother
-
-\rmfamily
 \title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V.
-	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}
 	}
@@
 
-\begin{document}
 \begin{frame}
@@
 
-\section{Introduction}
-\subsection*{Terminology}
-
-\frame{\frametitle{Terminology}
-	\begin{itemize}
-		\item{Properties of recessions:}
-		\begin{itemize}
-			\item{Cleansing effects: relatively unproductive firms exit in and around recessions}
-			\item{Sullying effects: more firms become relatively unproductive/ unproductive firms become 
-				even more unproductive in and around recessions}
-		\end{itemize}
-		\item{Effects on productivity dispersion:}
-		\begin{itemize}
-			\item{Productivity dispersion is \textit{procyclical}, when cleansing effects are at work}
-			\item{Productivity dispersion is \textit{countercyclical}, when sullying effects are dominant}
-		\end{itemize}
-	\end{itemize}
-}
-
 \section{Summary Statistics}
 
-\frame{\frametitle{Fundamental Dynamic}}
+\begin{frame}[fragile]
 <<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
-xtable(fundamental_dynamics,
+print(xtable(fundamental_dynamics,
                                   # summary = FALSE,
@@
           label = "fundamentalDynamics"
-          )
+          ), scalebox = '0.75')
 
 @
+\end{frame}
 
-% \frame{\frametitle{Illustration of concepts}
-% 	\begin{figure}[h]
-% 		\includegraphics[width = 5.5cm]{gdp_growth.pdf}
-% 		\includegraphics[width = 5.5cm]{norm_distribution.pdf}
-% 		\caption{Business Cycles and Probability Densitiy Function (\footnotesize{\textit{Source: Own Illustration}})}
-% 	\end{figure}
+% \begin
+% \frame[allowframebreaks]{\frametitle{References}
+% 		\tiny
+% 		\printbibliography
 % }
-% 
-% \subsection*{Relevance}
-% \frame{\frametitle{Why Should We Care?}
-% 	\begin{enumerate}
-% 		\item[1]{Relevance for the economy \& society:}
-% 		\begin{itemize}
-% 			\item{Various important connections between the nature of recessions and economic welfare:
-% 				\begin{itemize}
-% 					\item{Short-run: Besides undesirable effects of recessions (e.g. unemployment, higher government deficits, lower 
-% 						profiability), do recessions have a \textit{creative destruction}-quality as proposed 
-% 						by Pre-Keynesian liquidationists?}
-% 					\item{Long-run: Are recessions crucial for promoting long-run technological progress, i.e. productivity 
-% 						growth?}
-% 				\end{itemize}
-% 			}
-% 		\end{itemize}
-% 		\item[2]{Economic policy implications:
-% 			\begin{itemize}
-% 				\item{Should fiscal and monetary policy even focus on preventing or mitigating economic recessions?}
-% 				\item{If recessions have (undesirable) sullying properties, which policy instruments 
-% 					could be helpful for eliminating respective causes (e.g. market imperfections, liquiditiy frictions)}
-% 		\end{itemize}}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Why Should We Care?}
-% 	\begin{enumerate}    
-% 		\item[3]{Academia:}
-% 		\begin{itemize}
-% 			\item{Assessing the behavior of micro-level variables over the business cycle is essential 
-% 				for comprehending and predicting aggregate macroeconomic outcomes}
-% 			\item{Which theoretical models in terms of recession properties are backed by empirical evidence?}
-% 		\end{itemize}
-% 	\end{enumerate}
-% }
-% 
-% \subsection*{Literature}
-% \frame{\frametitle{Related Literature}
-% 	\begin{itemize}
-% 		\item{Extensive (recent) literature on how firm-level-variables and their cross-sectional dispersion behave over the business cycle 
-% 			(see \cite{10.1257/aer.104.4.1392}, \cite{doi:10.1111/j.0013-0427.2004.00371.x}, \cite{NBERw18245})}
-% 		\item{Identification of recession properties via resource (i.e. production input) reallocation 
-% 			in and around times of economic downturn (e.g. \cite{10.1111/j.1467-937X.2005.00334.x}, \cite{Mustre})}
-% 		\item{Behavior of productivity dispersion over the business cycle \cite{kehrig}:}
-% 		\begin{itemize}
-% 			\item{Productivity dispersion is \textit{countercyclical} and particularly peaks during 
-% 				or following recessions}
-% 			\item{Results are driven by unproductive firms, becoming even more unproductive during recessions}
-% 			\item{Evidence supports sullying properties}
-% 		\end{itemize}
-% 	\end{itemize}
-% }
-% 
-% \section{Data}
-% 
-% \frame{\frametitle{Data Sources}
-% 	\begin{itemize}
-% 		\item{Primary source: COMPUSTAT Capital IQ - Fundamentals Annual in North America}
-% 		\begin{itemize}
-% 			\item{Provider: Standard \& Poor's (S\&P), data is primarly drawn from SEC filings}
-% 			\item{Contains annual financial information on publicly traded, active and inactive firms}
-% 			\item{Sample selection issues \cite{Davis}}
-% 			\item{Initial sample: 1950-2018 and firms from all divisions ($n = 450.000$)}
-% 		\end{itemize}
-% 		\item{Additional sources:}
-% 		\begin{itemize}
-% 			\item{Bureau of Economic Analysis: price deflators, GDP-growth and real GDP-values, gross 
-% 				output by industry-data}
-% 			\item{Bureau of Labor Statistics: entry and exit rates within divisions}
-% 		\end{itemize}
-% 	\end{itemize}
-% }
-% 
-% \frame{\frametitle{Variable selection and grouping levels}
-% 	\begin{itemize}
-% 		\item{Variables of interest:}
-% 		\begin{enumerate}
-% 			\item{Identification variables: GVKEY, fyear}
-% 			\item{Variables for selection purposes: FIC, SIC, AQC, AT}
-% 			\item{Firm-level variables for analysis: PPEGT, PPENT, SALE, EMP, COGS}
-% 		\end{enumerate}
-% 		\item{Data grouping into divisions and industries via SIC codes}
-% 		\item{Within manufacturing: distinction between durable-goods- and non-durable-goods-producing firms}
-% 	\end{itemize}
-% }
-% 
-% \frame{\frametitle{Data grouping}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 5.5cm]{Divisions.JPG}
-% 		\includegraphics[width = 5.5cm]{Manufacturing.JPG}
-% 		\caption{Data grouping levels according to SIC-codes \newline \footnotesize{\textit{Source: https://www.naics.com/sic-codes-industry-drilldown/}}}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Sample Selection and Variable ``Treatments''}
-% 	\begin{enumerate}
-% 		\item{Restrict analysis to US-firms}
-% 		\item{Main focus: manufacturing firms, supplemented by other division(s) for comparative 
-% 			reasons (e.g. services)}
-% 		\item{Exclude:}
-% 		\begin{itemize}
-% 			\item{Utility firms and financial firms}
-% 			\item{Observations in which $AQC > 5\%~ of ~AT$}
-% 			\item{Observations with no entries on firm-level variables}
-% 			\item{Observations with $SALE > 0$ \& $EMP = 0$}
-% 			\item{Observations with $PPEGT = 0$ or $PPENT = 0$}
-% 			\item{Years with too little observations (per industry) to allow for statistically 
-% 				reliable results}
-% 		\end{itemize}
-% 		\item{Denominate nominal value variables in real values by deflating}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Sample Size}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 5cm]{Observations1.JPG}
-% 		\includegraphics[width = 5cm]{Observations2.JPG}
-% 		\caption{Annual number of observations, (\textit{Source: Own calculations})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Summary Statistics}
-% 	\begin{table}[h]
-% 		\footnotesize
-% 		\centering
-% 		\caption{Descriptive statistics of production inputs and outputs}
-% 		\begin{tabular}{p{2.0cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}}
-% 			\hline\hline \\
-% 			\textbf{Sample} &\hfill Capital &\hfill Labor &\hfill Interm. &\hfill Sale &\hfill \textbf{n} \\
-% 			\hline
-% 			\textbf{Manufacturing} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{107783}\\ 
-% 			mean &\hfill 691.18 &\hfill 4.84 &\hfill 985.16 &\hfill 1400.99 \\
-% 			$\sigma$ &\hfill 5188.13 &\hfill 20.53 &\hfill 6812.45 &\hfill 8815.76  \\
-% 			\hline
-% 			\textbf{Services} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{38218}\\
-% 			mean &\hfill 297.95 &\hfill 5.29 &\hfill 340.46  &\hfill 580.84  \\
-% 			$\sigma$ &\hfill 2162.94 &\hfill 28.37 &\hfill 1823.36 &\hfill 3563.94 \\
-% 			\hline 
-% 			\textbf{Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{67020} \\
-% 			mean &\hfill 464.25 &\hfill 4.62 &\hfill 780.05 &\hfill 1078.07 \\
-% 			\hline
-% 			\textbf{Non-Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{40763} \\
-% 			mean &\hfill 1068.12 &\hfill 5.21 &\hfill 1322.36 &\hfill 1931.90 \\
-% 			\hline %need to find a double-hline!
-% 			\textbf{Overall} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{146001} \\
-% 			\hline\hline
-% 			% Sigma-values need to denominated in smaller letters, or alternatively brackets. 
-% 		\end{tabular} \\
-% 		\vspace{2mm}
-% 		{\tiny \textit{Note: Capital, intermediaries and sales are denominated in mio. USD, labor 
-% 				is denominated in thousands of employees. All figures are rounded to two decimal digits.}}
-% 		\label{tab: 1}
-% 	\end{table}  
-% }
-% 
-% \section{Dispersion Measurement}
-% \frame{\frametitle{Estimating Productivity}
-% 	\begin{equation}
-% 	ln~y_{it} = \beta_0 + \beta_k~ln~k_{it-1} + \beta_n ~ ln~n_{it} + \beta_m ~ ln~m_{it} 
-% 	+ \beta_i D_i + \beta_t D_t + \epsilon_{it}
-% 	\end{equation}
-% 	\begin{itemize}
-% 		\small
-% 		\item{$y_{it}$: Real Sales}
-% 		\item{$k_{it-1}$: Constructed Capital via PIM:}
-% 		\item{$n_{it}$: Number of Employees}
-% 		\item{$m_{it}$: Real Cost of Sold Goods}
-% 		\item{$D_i$: Firm Dummy}
-% 		\item{$D_t$: Year Dummy}
-% 		\item{$\epsilon_{it}$: Firm-level productivity}
-% 	\end{itemize}
-% 	
-% }
-% 
-% \frame{\frametitle{Compute Productivity Dispersion}
-% 	\begin{block}{\textbf{\color{red}Goal:}}
-% 		\color{black} $\Rightarrow$ Compute an aggregated productivity 
-% 		dispersion measure for every industry
-% 	\end{block}
-% 	\begin{enumerate}
-% 		\item[1.]{Adjustment: control for industry specific productivity growth trend \newline
-% 			$\epsilon_{ijt} = g_{j}t + z_{ijt}$}
-% 		\begin{itemize}
-% 			\item{$\epsilon_{ijt}$: Productivity}
-% 			\item{$g_j$: Industry-specific growth trend}
-% 			\item{$z_{ijt}$: Productivity dispersion}
-% 		\end{itemize}
-% 		\item[2.]{Adjustment: decenter and scale to construct cross-sectional dispersion}
-% 		\item[3.]{Adjustment: control for a long-term trend}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Dispersion Measure}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 12cm]{Dispersion.JPG}
-% 		\caption{Illustration of adjustment steps (\footnotesize{\textit{Source: Kehrig (2015)}})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{The Distribution of Normalized Productivity Dispersion}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[height = 4.5cm, width = 5.5cm]{28_1998.pdf}
-% 		\includegraphics[height = 4.5cm, width = 5.5cm]{34_2003.pdf}
-% 		\caption{Exemplary normalized productivity dispersion for two industries, (\textit{Source: Own illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{The Normalized Productivity Dispersion}
-% 	\begin{minipage}[c]{0.6\textwidth}
-% 		\begin{figure}[h]
-% 			\centering
-% 			\includegraphics[width = 7cm]{normalized_productvitiy.pdf}
-% 			\caption{Normalized productivity over years}
-% 		\end{figure}
-% 	\end{minipage}
-% 	\begin{minipage}[b]{0.2\textwidth}
-% 		\begin{flalign*}
-% 		Dispersion_t &= \\
-% 		Median_t[Std_{jt}&(\frac{z_{ijt} - \bar{z_j}}{\sigma_j})]
-% 		\end{flalign*}
-% 	\end{minipage}
-% }
-% \frame{\frametitle{Growth-Trends in Productivity-Dispersion}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 8.5cm]{long_final.pdf}
-% 		\caption{Actual dispersion behavior and trends over time, (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{First Estimations}
-% 	\begin{table}[htb]
-% 		\centering
-% 		\caption{Results of OLS Regression}\vspace{1ex}
-% 		\begin{tabular}{@{}lcccc@{}}
-% 			\toprule[2pt]
-% 			{\bf ln\_sale} & Coefficient & Robust St. Err. & t-Statistics & p-value \\
-% 			\hline
-% 			\bf ln\_capital & 0.4300*** & 0.0097 & 44.12 & 0.000\\
-% 			\bf ln\_emp &0.4801*** & 0.0099 & 48.20 & 0.000\\
-% 			\bf ln\_cog &0.1035*** & 0.0064 & 16.13 & 0.000\\
-% 			\hline 
-% 			\midrule
-% 			\multicolumn{5}{c}{R-squared=0.9681 Adj.R-squared=0.969 RMSE=0.4686}\\
-% 			\bottomrule[2pt]
-% 		\end{tabular}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{First Estimations}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{fixed_final.pdf}
-% 		\caption{Annual time-FE-coefficients and GDP-growth (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \section{Empirical Analysis}
-% \frame{\frametitle{Duables and Non-Durables Within Manufacturing}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 8cm]{durable_final.pdf}
-% 		\caption{Dispersion of productivity levels within durables and non-durables, (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{AutoscaledLineDispTot}
-% 	\fitimage{LineDispTot.pdf}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[]{LineDispTot.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{ScatDispTot.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 			\begin{tabular}{ccccccc}
-% 				\hline
-% 				Lead in years & All & p-value & Non-Durables & p-value & Durables & p-value \\ 
-% 				\hline
-% 				-2 & 0.195 & 0.12 & -0.144 & 0.30 & 0.030 & 0.83 \\ 
-% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-% 				0 & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-% 				2 & -0.160 & 0.20 & 0.056 & 0.69 & 0.297 & 0.03 \\ 
-% 				\hline
-% 			\end{tabular}
-% 		\end{adjustbox}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{PlotQuantilesLow.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{PlotQuantilesHigh.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Dynamics in the Manufacturing Division}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width=8cm]{quantile_m_final.pdf}
-% 		\caption{Productivity changes in different manufacturing quantiles, (\textit{Source: Own illustration})}
-% 	\end{figure}
-% }
-% 
-% \section{Discussion}
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 			\begin{tabular}{lcccccc}
-% 				\hline
-% 				& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-% 				\hline
-% 				Standard Deviation & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				Variance & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				Inter-quartile range & 0.005 & 0.97 & 0.114 & 0.41 & -0.140 & 0.31 \\ 
-% 				Median absolute deviation & -0.023 & 0.86 & 0.135 & 0.33 & -0.091 & 0.51 \\ 
-% 				\hline
-% 			\end{tabular}
-% 		\end{adjustbox}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 				\begin{tabular}{lcccccc}
-% 					\hline
-% 					& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-% 					\hline
-% 					Production - HP filtered ($\lambda = 100$) &  &  & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 					Production - HP filtered ($\lambda = 6.25$) &  &  & 0.150 & 0.28 & -0.322 & 0.02 \\ 
-% 					Production growth rate &  &  & 0.032 & 0.82 & -0.343 & 0.01 \\ 
-% 					GDP - HP filtered ($\lambda = 100$) & -0.045 & 0.71 & 0.058 & 0.64 & -0.100 & 0.42 \\ 
-% 					GDP - HP filtered ($\lambda = 6.25$) & -0.121 & 0.33 & 0.109 & 0.38 & -0.129 & 0.29 \\ 
-% 					GDP growth rate & -0.043 & 0.73 & -0.041 & 0.74 & 0.018 & 0.89 \\ 
-% 					\hline
-% 				\end{tabular}
-% 			\end{adjustbox}
-% 		\end{table}
-% 	}
-% 	
-% 	\section{Conclusion}
-% 	\frame{\frametitle{Conclusion}
-% 		\begin{itemize}
-% 			\item{\textbf{Main result:}}
-% 			\begin{itemize}
-% 				\item{No clear general cyclical or countercyclical pattern}
-% 				\item{But: Productivitiy dispersion is countercyclical for durables}
-% 				\item{Recessions do have (small) sullying effects, in particular in the manufacturing division}
-% 			\end{itemize}
-% 			\item{\textbf{Where to go from here?}}
-% 			\begin{itemize}
-% 				\item{Replicate findings with quarterly data}
-% 				\item{Did policy interventions in the analyzed NBER-recessions already have an impact (potential OVB)?}
-% 				\item{Identify causal link for sullying effecs: Why do unproductive firms remain in business (potential frictions)?}
-% 			\end{itemize}
-% 		\end{itemize}
-% 	}
-	\frame[allowframebreaks]{\frametitle{References}
-		\tiny\printbibliography
-	}
 

### 2020-02-29 presentation.tex
lg
ijocjjvldkldklllll
compiling presentation possible

@@
 
-\documentclass[hyperref={pdfpagelabels=false}\usepackage[]{graphicx}\usepackage[]{color}
+% https://github.com/yihui/knitr/blob/master/inst/examples/knitr-beamer.Rnw
+
+\documentclass{beamer}\usepackage[]{graphicx}\usepackage[]{color}
 % maxwidth is the original width if it is less than linewidth
@@
 
-\usepackage{alltt}]{beamer}
-\usepackage{lmodern}
-\usepackage{lscape}
-\usepackage{graphicx}
-\usepackage[utf8]{inputenc}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
-\usepackage{floatrow}
-\usepackage{booktabs}
-% \usepackage{bookmark}
-\usepackage{rotating}
-\usepackage{dcolumn}
-\usepackage{mathtools}
-\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
+\usepackage{alltt}
+% \usepackage{lmodern}
+% \usepackage{lscape}
+% \usepackage{graphicx}
+% \usepackage[utf8]{inputenc}
+% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% \usepackage{floatrow}
+% \usepackage{booktabs}
+% \usepackage{rotating}
+% \usepackage{dcolumn}
+% \usepackage{mathtools}
+% \usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
 % \usepackage[hidelinks]{hyperref}
@@
 % \graphicspath{{./Visuals/}}
+% \setcounter{secnumdepth}{3}
+% \setcounter{tocdepth}{3}
+% \usepackage{url}
+% \ifx\hypersetup\undefined
+%   \AtBeginDocument{%
+%     \hypersetup{unicode=true,pdfusetitle,
+%  bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+%  breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false}
+%   }
+% \else
+%   \hypersetup{unicode=true,pdfusetitle,
+%  bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
+%  breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false}
+% \fi
+% \usepackage{breakurl}
+% 
+% \makeatletter
+%
+% Fancy fit image command with optional caption copied from https://www.patrickbaylis.com/posts/2018-10-11-beamer-resizing/
+% \makeatletter
+% \newcommand{\fitimage}[2][\@nil]{
+% 	\begin{figure}
+% 		\begin{adjustbox}{width=0.9\textwidth, totalheight=\textheight-2\baselineskip-2\baselineskip,keepaspectratio}
+% 			\includegraphics{#2}
+% 		\end{adjustbox}
+% 		\def\tmp{#1}%
+% 		\ifx\tmp\@nnil
+% 		\else
+% 		\caption{#1}
+% 		\fi
+% 	\end{figure}
+% }
+% \makeatother
+% 
+% \rmfamily
+
 \usetheme{CambridgeUS}
-\usecolortheme{dolphin}
-\addbibresource{references.bib}
+% \usecolortheme{dolphin}
+% \addbibresource{references.bib}
+%
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\begin{document}
 
-% Fancy fit image command with optional caption copied from https://www.patrickbaylis.com/posts/2018-10-11-beamer-resizing/
-\makeatletter
-\newcommand{\fitimage}[2][\@nil]{
-	\begin{figure}
-		\begin{adjustbox}{width=0.9\textwidth, totalheight=\textheight-2\baselineskip-2\baselineskip,keepaspectratio}
-			\includegraphics{#2}
-		\end{adjustbox}
-		\def\tmp{#1}%
-		\ifx\tmp\@nnil
-		\else
-		\caption{#1}
-		\fi
-	\end{figure}
-}
-\makeatother
-
-\rmfamily
 \title[Analyse der Survey-Daten von CHILDREN]{Analyse der Survey-Daten von CHILDREN for a better World e.V.
-	% \small{\textit{following Kehrig: The Cyclical Nature of the Productivity Distribution}}
 	}
@@
 \date{March 3, 2020}
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\begin{document}
+
 \begin{frame}
@@
 
-\section{Introduction}
-\subsection*{Terminology}
-
-\frame{\frametitle{Terminology}
-	\begin{itemize}
-		\item{Properties of recessions:}
-		\begin{itemize}
-			\item{Cleansing effects: relatively unproductive firms exit in and around recessions}
-			\item{Sullying effects: more firms become relatively unproductive/ unproductive firms become 
-				even more unproductive in and around recessions}
-		\end{itemize}
-		\item{Effects on productivity dispersion:}
-		\begin{itemize}
-			\item{Productivity dispersion is \textit{procyclical}, when cleansing effects are at work}
-			\item{Productivity dispersion is \textit{countercyclical}, when sullying effects are dominant}
-		\end{itemize}
-	\end{itemize}
-}
-
 \section{Summary Statistics}
 
-\frame{\frametitle{Fundamental Dynamic}}
+\begin{frame}[fragile]
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sat Feb 29 17:39:39 2020
+% Sat Feb 29 22:45:36 2020
 \begin{table}[ht]
 \centering
+\scalebox{0.75}{
 \begin{tabular}{lccccc}
@@
 \end{tabular}
+}
 \caption{Summary Statistics} 
@@
 
-% \frame{\frametitle{Illustration of concepts}
-% 	\begin{figure}[h]
-% 		\includegraphics[width = 5.5cm]{gdp_growth.pdf}
-% 		\includegraphics[width = 5.5cm]{norm_distribution.pdf}
-% 		\caption{Business Cycles and Probability Densitiy Function (\footnotesize{\textit{Source: Own Illustration}})}
-% 	\end{figure}
+\end{frame}
+
+% \begin
+% \frame[allowframebreaks]{\frametitle{References}
+% 		\tiny
+% 		\printbibliography
 % }
-% 
-% \subsection*{Relevance}
-% \frame{\frametitle{Why Should We Care?}
-% 	\begin{enumerate}
-% 		\item[1]{Relevance for the economy \& society:}
-% 		\begin{itemize}
-% 			\item{Various important connections between the nature of recessions and economic welfare:
-% 				\begin{itemize}
-% 					\item{Short-run: Besides undesirable effects of recessions (e.g. unemployment, higher government deficits, lower 
-% 						profiability), do recessions have a \textit{creative destruction}-quality as proposed 
-% 						by Pre-Keynesian liquidationists?}
-% 					\item{Long-run: Are recessions crucial for promoting long-run technological progress, i.e. productivity 
-% 						growth?}
-% 				\end{itemize}
-% 			}
-% 		\end{itemize}
-% 		\item[2]{Economic policy implications:
-% 			\begin{itemize}
-% 				\item{Should fiscal and monetary policy even focus on preventing or mitigating economic recessions?}
-% 				\item{If recessions have (undesirable) sullying properties, which policy instruments 
-% 					could be helpful for eliminating respective causes (e.g. market imperfections, liquiditiy frictions)}
-% 		\end{itemize}}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Why Should We Care?}
-% 	\begin{enumerate}    
-% 		\item[3]{Academia:}
-% 		\begin{itemize}
-% 			\item{Assessing the behavior of micro-level variables over the business cycle is essential 
-% 				for comprehending and predicting aggregate macroeconomic outcomes}
-% 			\item{Which theoretical models in terms of recession properties are backed by empirical evidence?}
-% 		\end{itemize}
-% 	\end{enumerate}
-% }
-% 
-% \subsection*{Literature}
-% \frame{\frametitle{Related Literature}
-% 	\begin{itemize}
-% 		\item{Extensive (recent) literature on how firm-level-variables and their cross-sectional dispersion behave over the business cycle 
-% 			(see \cite{10.1257/aer.104.4.1392}, \cite{doi:10.1111/j.0013-0427.2004.00371.x}, \cite{NBERw18245})}
-% 		\item{Identification of recession properties via resource (i.e. production input) reallocation 
-% 			in and around times of economic downturn (e.g. \cite{10.1111/j.1467-937X.2005.00334.x}, \cite{Mustre})}
-% 		\item{Behavior of productivity dispersion over the business cycle \cite{kehrig}:}
-% 		\begin{itemize}
-% 			\item{Productivity dispersion is \textit{countercyclical} and particularly peaks during 
-% 				or following recessions}
-% 			\item{Results are driven by unproductive firms, becoming even more unproductive during recessions}
-% 			\item{Evidence supports sullying properties}
-% 		\end{itemize}
-% 	\end{itemize}
-% }
-% 
-% \section{Data}
-% 
-% \frame{\frametitle{Data Sources}
-% 	\begin{itemize}
-% 		\item{Primary source: COMPUSTAT Capital IQ - Fundamentals Annual in North America}
-% 		\begin{itemize}
-% 			\item{Provider: Standard \& Poor's (S\&P), data is primarly drawn from SEC filings}
-% 			\item{Contains annual financial information on publicly traded, active and inactive firms}
-% 			\item{Sample selection issues \cite{Davis}}
-% 			\item{Initial sample: 1950-2018 and firms from all divisions ($n = 450.000$)}
-% 		\end{itemize}
-% 		\item{Additional sources:}
-% 		\begin{itemize}
-% 			\item{Bureau of Economic Analysis: price deflators, GDP-growth and real GDP-values, gross 
-% 				output by industry-data}
-% 			\item{Bureau of Labor Statistics: entry and exit rates within divisions}
-% 		\end{itemize}
-% 	\end{itemize}
-% }
-% 
-% \frame{\frametitle{Variable selection and grouping levels}
-% 	\begin{itemize}
-% 		\item{Variables of interest:}
-% 		\begin{enumerate}
-% 			\item{Identification variables: GVKEY, fyear}
-% 			\item{Variables for selection purposes: FIC, SIC, AQC, AT}
-% 			\item{Firm-level variables for analysis: PPEGT, PPENT, SALE, EMP, COGS}
-% 		\end{enumerate}
-% 		\item{Data grouping into divisions and industries via SIC codes}
-% 		\item{Within manufacturing: distinction between durable-goods- and non-durable-goods-producing firms}
-% 	\end{itemize}
-% }
-% 
-% \frame{\frametitle{Data grouping}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 5.5cm]{Divisions.JPG}
-% 		\includegraphics[width = 5.5cm]{Manufacturing.JPG}
-% 		\caption{Data grouping levels according to SIC-codes \newline \footnotesize{\textit{Source: https://www.naics.com/sic-codes-industry-drilldown/}}}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Sample Selection and Variable ``Treatments''}
-% 	\begin{enumerate}
-% 		\item{Restrict analysis to US-firms}
-% 		\item{Main focus: manufacturing firms, supplemented by other division(s) for comparative 
-% 			reasons (e.g. services)}
-% 		\item{Exclude:}
-% 		\begin{itemize}
-% 			\item{Utility firms and financial firms}
-% 			\item{Observations in which $AQC > 5\%~ of ~AT$}
-% 			\item{Observations with no entries on firm-level variables}
-% 			\item{Observations with $SALE > 0$ \& $EMP = 0$}
-% 			\item{Observations with $PPEGT = 0$ or $PPENT = 0$}
-% 			\item{Years with too little observations (per industry) to allow for statistically 
-% 				reliable results}
-% 		\end{itemize}
-% 		\item{Denominate nominal value variables in real values by deflating}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Sample Size}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 5cm]{Observations1.JPG}
-% 		\includegraphics[width = 5cm]{Observations2.JPG}
-% 		\caption{Annual number of observations, (\textit{Source: Own calculations})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Summary Statistics}
-% 	\begin{table}[h]
-% 		\footnotesize
-% 		\centering
-% 		\caption{Descriptive statistics of production inputs and outputs}
-% 		\begin{tabular}{p{2.0cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}p{1.3cm}}
-% 			\hline\hline \\
-% 			\textbf{Sample} &\hfill Capital &\hfill Labor &\hfill Interm. &\hfill Sale &\hfill \textbf{n} \\
-% 			\hline
-% 			\textbf{Manufacturing} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{107783}\\ 
-% 			mean &\hfill 691.18 &\hfill 4.84 &\hfill 985.16 &\hfill 1400.99 \\
-% 			$\sigma$ &\hfill 5188.13 &\hfill 20.53 &\hfill 6812.45 &\hfill 8815.76  \\
-% 			\hline
-% 			\textbf{Services} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{38218}\\
-% 			mean &\hfill 297.95 &\hfill 5.29 &\hfill 340.46  &\hfill 580.84  \\
-% 			$\sigma$ &\hfill 2162.94 &\hfill 28.37 &\hfill 1823.36 &\hfill 3563.94 \\
-% 			\hline 
-% 			\textbf{Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{67020} \\
-% 			mean &\hfill 464.25 &\hfill 4.62 &\hfill 780.05 &\hfill 1078.07 \\
-% 			\hline
-% 			\textbf{Non-Durables} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{40763} \\
-% 			mean &\hfill 1068.12 &\hfill 5.21 &\hfill 1322.36 &\hfill 1931.90 \\
-% 			\hline %need to find a double-hline!
-% 			\textbf{Overall} &\hfill &\hfill &\hfill &\hfill &\hfill \textbf{146001} \\
-% 			\hline\hline
-% 			% Sigma-values need to denominated in smaller letters, or alternatively brackets. 
-% 		\end{tabular} \\
-% 		\vspace{2mm}
-% 		{\tiny \textit{Note: Capital, intermediaries and sales are denominated in mio. USD, labor 
-% 				is denominated in thousands of employees. All figures are rounded to two decimal digits.}}
-% 		\label{tab: 1}
-% 	\end{table}  
-% }
-% 
-% \section{Dispersion Measurement}
-% \frame{\frametitle{Estimating Productivity}
-% 	\begin{equation}
-% 	ln~y_{it} = \beta_0 + \beta_k~ln~k_{it-1} + \beta_n ~ ln~n_{it} + \beta_m ~ ln~m_{it} 
-% 	+ \beta_i D_i + \beta_t D_t + \epsilon_{it}
-% 	\end{equation}
-% 	\begin{itemize}
-% 		\small
-% 		\item{$y_{it}$: Real Sales}
-% 		\item{$k_{it-1}$: Constructed Capital via PIM:}
-% 		\item{$n_{it}$: Number of Employees}
-% 		\item{$m_{it}$: Real Cost of Sold Goods}
-% 		\item{$D_i$: Firm Dummy}
-% 		\item{$D_t$: Year Dummy}
-% 		\item{$\epsilon_{it}$: Firm-level productivity}
-% 	\end{itemize}
-% 	
-% }
-% 
-% \frame{\frametitle{Compute Productivity Dispersion}
-% 	\begin{block}{\textbf{\color{red}Goal:}}
-% 		\color{black} $\Rightarrow$ Compute an aggregated productivity 
-% 		dispersion measure for every industry
-% 	\end{block}
-% 	\begin{enumerate}
-% 		\item[1.]{Adjustment: control for industry specific productivity growth trend \newline
-% 			$\epsilon_{ijt} = g_{j}t + z_{ijt}$}
-% 		\begin{itemize}
-% 			\item{$\epsilon_{ijt}$: Productivity}
-% 			\item{$g_j$: Industry-specific growth trend}
-% 			\item{$z_{ijt}$: Productivity dispersion}
-% 		\end{itemize}
-% 		\item[2.]{Adjustment: decenter and scale to construct cross-sectional dispersion}
-% 		\item[3.]{Adjustment: control for a long-term trend}
-% 	\end{enumerate}
-% }
-% 
-% \frame{\frametitle{Dispersion Measure}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 12cm]{Dispersion.JPG}
-% 		\caption{Illustration of adjustment steps (\footnotesize{\textit{Source: Kehrig (2015)}})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{The Distribution of Normalized Productivity Dispersion}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[height = 4.5cm, width = 5.5cm]{28_1998.pdf}
-% 		\includegraphics[height = 4.5cm, width = 5.5cm]{34_2003.pdf}
-% 		\caption{Exemplary normalized productivity dispersion for two industries, (\textit{Source: Own illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{The Normalized Productivity Dispersion}
-% 	\begin{minipage}[c]{0.6\textwidth}
-% 		\begin{figure}[h]
-% 			\centering
-% 			\includegraphics[width = 7cm]{normalized_productvitiy.pdf}
-% 			\caption{Normalized productivity over years}
-% 		\end{figure}
-% 	\end{minipage}
-% 	\begin{minipage}[b]{0.2\textwidth}
-% 		\begin{flalign*}
-% 		Dispersion_t &= \\
-% 		Median_t[Std_{jt}&(\frac{z_{ijt} - \bar{z_j}}{\sigma_j})]
-% 		\end{flalign*}
-% 	\end{minipage}
-% }
-% \frame{\frametitle{Growth-Trends in Productivity-Dispersion}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 8.5cm]{long_final.pdf}
-% 		\caption{Actual dispersion behavior and trends over time, (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{First Estimations}
-% 	\begin{table}[htb]
-% 		\centering
-% 		\caption{Results of OLS Regression}\vspace{1ex}
-% 		\begin{tabular}{@{}lcccc@{}}
-% 			\toprule[2pt]
-% 			{\bf ln\_sale} & Coefficient & Robust St. Err. & t-Statistics & p-value \\
-% 			\hline
-% 			\bf ln\_capital & 0.4300*** & 0.0097 & 44.12 & 0.000\\
-% 			\bf ln\_emp &0.4801*** & 0.0099 & 48.20 & 0.000\\
-% 			\bf ln\_cog &0.1035*** & 0.0064 & 16.13 & 0.000\\
-% 			\hline 
-% 			\midrule
-% 			\multicolumn{5}{c}{R-squared=0.9681 Adj.R-squared=0.969 RMSE=0.4686}\\
-% 			\bottomrule[2pt]
-% 		\end{tabular}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{First Estimations}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{fixed_final.pdf}
-% 		\caption{Annual time-FE-coefficients and GDP-growth (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \section{Empirical Analysis}
-% \frame{\frametitle{Duables and Non-Durables Within Manufacturing}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 8cm]{durable_final.pdf}
-% 		\caption{Dispersion of productivity levels within durables and non-durables, (\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{AutoscaledLineDispTot}
-% 	\fitimage{LineDispTot.pdf}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[]{LineDispTot.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{ScatDispTot.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 			\begin{tabular}{ccccccc}
-% 				\hline
-% 				Lead in years & All & p-value & Non-Durables & p-value & Durables & p-value \\ 
-% 				\hline
-% 				-2 & 0.195 & 0.12 & -0.144 & 0.30 & 0.030 & 0.83 \\ 
-% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-% 				0 & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				1 & 0.038 & 0.76 & 0.101 & 0.47 & 0.186 & 0.18 \\ 
-% 				2 & -0.160 & 0.20 & 0.056 & 0.69 & 0.297 & 0.03 \\ 
-% 				\hline
-% 			\end{tabular}
-% 		\end{adjustbox}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{PlotQuantilesLow.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width = 9cm]{PlotQuantilesHigh.pdf}
-% 		\caption{(\textit{Source: Own Illustration})}
-% 	\end{figure}
-% }
-% 
-% \frame{\frametitle{Dynamics in the Manufacturing Division}
-% 	\begin{figure}[h]
-% 		\centering
-% 		\includegraphics[width=8cm]{quantile_m_final.pdf}
-% 		\caption{Productivity changes in different manufacturing quantiles, (\textit{Source: Own illustration})}
-% 	\end{figure}
-% }
-% 
-% \section{Discussion}
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 			\begin{tabular}{lcccccc}
-% 				\hline
-% 				& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-% 				\hline
-% 				Standard Deviation & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				Variance & -0.045 & 0.71 & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 				Inter-quartile range & 0.005 & 0.97 & 0.114 & 0.41 & -0.140 & 0.31 \\ 
-% 				Median absolute deviation & -0.023 & 0.86 & 0.135 & 0.33 & -0.091 & 0.51 \\ 
-% 				\hline
-% 			\end{tabular}
-% 		\end{adjustbox}
-% 	\end{table}
-% }
-% 
-% \frame{\frametitle{}
-% 	\begin{table}[ht]
-% 		\centering
-% 		\begin{adjustbox}{{width=\textwidth, totalheight=\textheight-2\baselineskip, keepaspectratio}
-% 				\begin{tabular}{lcccccc}
-% 					\hline
-% 					& All & p-value & Non-durables & p-value & Durables & p-value \\ 
-% 					\hline
-% 					Production - HP filtered ($\lambda = 100$) &  &  & 0.132 & 0.34 & -0.184 & 0.18 \\ 
-% 					Production - HP filtered ($\lambda = 6.25$) &  &  & 0.150 & 0.28 & -0.322 & 0.02 \\ 
-% 					Production growth rate &  &  & 0.032 & 0.82 & -0.343 & 0.01 \\ 
-% 					GDP - HP filtered ($\lambda = 100$) & -0.045 & 0.71 & 0.058 & 0.64 & -0.100 & 0.42 \\ 
-% 					GDP - HP filtered ($\lambda = 6.25$) & -0.121 & 0.33 & 0.109 & 0.38 & -0.129 & 0.29 \\ 
-% 					GDP growth rate & -0.043 & 0.73 & -0.041 & 0.74 & 0.018 & 0.89 \\ 
-% 					\hline
-% 				\end{tabular}
-% 			\end{adjustbox}
-% 		\end{table}
-% 	}
-% 	
-% 	\section{Conclusion}
-% 	\frame{\frametitle{Conclusion}
-% 		\begin{itemize}
-% 			\item{\textbf{Main result:}}
-% 			\begin{itemize}
-% 				\item{No clear general cyclical or countercyclical pattern}
-% 				\item{But: Productivitiy dispersion is countercyclical for durables}
-% 				\item{Recessions do have (small) sullying effects, in particular in the manufacturing division}
-% 			\end{itemize}
-% 			\item{\textbf{Where to go from here?}}
-% 			\begin{itemize}
-% 				\item{Replicate findings with quarterly data}
-% 				\item{Did policy interventions in the analyzed NBER-recessions already have an impact (potential OVB)?}
-% 				\item{Identify causal link for sullying effecs: Why do unproductive firms remain in business (potential frictions)?}
-% 			\end{itemize}
-% 		\end{itemize}
-% 	}
-	\frame[allowframebreaks]{\frametitle{References}
-		\tiny\printbibliography
-	}
 

### 2020-03-01 presentation.Rnw
khjgh
changed colortheme
szdjugioul
zui

@@
 % pdflatex presentation
+% 
+% Einleitung
+% 
+% Überblick children kurz
+% Wie fördern sie
+% Über d verteilt
+% Beide programme erklären
+% Daten sammlung prozess
+% Datenstruktur
+% Datenaufbereitung
+% 
+% Summary Statistics
+% 
+% Mittagstisch
+% Entdeckerfonds
+% Subsidy
+% Selfworth
+% Daytodayskills
+% Health variables
+% 
+% Regressionen
+% 
+% DiD-Ansatz
+% 
+% Grundlegende Idee – was wollen wir testen?
+% Zielvariablen und warum
+% Grafische evidenz 
+% Resultate - Regressionstabellen
+% 
+% Fazit und Verbesserungsvorschläge
+% 
+% Gründe für fehlende effekte 
+% Tipps zur datenerhebung und struktur
+% partition
 
@@
 % \usepackage[utf8]{inputenc}
-% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
 % \usepackage{floatrow}
@@
 \usetheme{CambridgeUS}
-% \usecolortheme{dolphin}
-% \addbibresource{references.bib}
+
+\usecolortheme{crane}
+
+\addbibresource{references.bib}
+
 %
@@
 \begin{frame}[fragile]
-<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+\frametitle{Summary Statistics}
+<<SummaryStatistics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 
@@
 @
+
 \end{frame}
 
-% \begin
-% \frame[allowframebreaks]{\frametitle{References}
-% 		\tiny
-% 		\printbibliography
-% }
+\begin{frame}[fragile]
+\frametitle{Dynamics}
+
+\begin{figure}
+  \caption{Yearly dynamics of total grants in Meals and Trips program}
+  \label{totalGrantsDyn}
+
+<<GrantTrend, echo=FALSE, message=FALSE>>=
+totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+print(totalGrantsDyn, scalebox = '0.25')
+@
+
+% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
+From left to right: Meals, Trips.
+From top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
+\end{frame}
+
+\frame[allowframebreaks]{\frametitle{References}
+		\tiny
+		\printbibliography
+}
 

### 2020-03-01 presentation.Rnw
Update
lh
inserted all regression results tables from first part

@@
 % \usepackage{floatrow}
-% \usepackage{booktabs}
+\usepackage{booktabs}
 % \usepackage{rotating}
@@
 
+\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+
+\begin{frame}
+\frametitle{Empirische Ansatz}
+\begin{equation}
+\label{SimpleLinearModel}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+\end{frame}
+
+\subsection{Direkte Effekte von CHILDRENs Zuschüssen}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Mahlzeiten und Zuschüsse}
+
+<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
+
+lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
+lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
+lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
+lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
+lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
+
+texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.5, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
+
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Ausflüge und Zuschüsse}
+<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
+lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
+lm_ts_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
+lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
+lm_ts_o_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex_control.lm.Rds")
+lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips
+
+texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
+@
+\end{frame}
+
+\subsection{Selbstwertgefühl, Alltagskompetenzen und Zuschüsse}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
+
+<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=
+
+ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") 
+tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
+ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
+tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds") 
+sfactor = readRDS("./ANALYSIS/Tables/factorselfworthmeals.Rds")
+
+texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
+@
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+
+<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
+ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
+tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
+dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
+tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
+dfactorm = readRDS("./ANALYSIS/Tables/factordaytodayskillsmeals.Rds")
+dfactort = readRDS("./ANALYSIS/Tables/factordaytodayskillstrips.Rds")
+
+texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+@
+
+\end{frame}
+
+\subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Seltener krank}
+<<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
+
+lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
+#extraweighted
+lDGEw = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled_weighted.lm.Rds")
+#standardized
+lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
+#extraweighted
+lDGE_iw = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled_weighted.lm.Rds")
+illfactor = readRDS("./ANALYSIS/Tables/lessIllfactor.Rds")
+
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
+@
+\end{frame}
+
+\begin{frame}
+\frametitle{Ernährungswissen}
+<<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
+dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
+dDGEw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled_weighted.Rds")
+dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
+dDGE_iw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled_weighted.lm.Rds")
+dietaryf = readRDS("./ANALYSIS/Tables/dietaryknowledgefactor.Rds")
+
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Wertschätzung für gesundes Essen}
+<<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
+aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
+aDGEw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled_weighted.Rds")
+aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")
+aDGE_iw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled_weighted.lm.Rds")
+appreciatef = readRDS("./ANALYSIS/Tables/appreciatehealthyfactor.Rds")
+
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
+@
+\end{frame}
+
 \frame[allowframebreaks]{\frametitle{References}

### 2020-03-01 presentation.tex
khjgh
yxjklö
vbnmk,l.ö
szdjugioul
lh
Presentation
new compile
lg
first figure in presentation
Update
inserted all regression results tables from first part

@@
 % pdflatex presentation
+% 
+% Einleitung
+% 
+% Überblick children kurz
+% Wie fördern sie
+% Über d verteilt
+% Beide programme erklären
+% Daten sammlung prozess
+% Datenstruktur
+% Datenaufbereitung
+% 
+% Summary Statistics
+% 
+% Mittagstisch
+% Entdeckerfonds
+% Subsidy
+% Selfworth
+% Daytodayskills
+% Health variables
+% 
+% Regressionen
+% 
+% DiD-Ansatz
+% 
+% Grundlegende Idee – was wollen wir testen?
+% Zielvariablen und warum
+% Grafische evidenz 
+% Resultate - Regressionstabellen
+% 
+% Fazit und Verbesserungsvorschläge
+% 
+% Gründe für fehlende effekte 
+% Tipps zur datenerhebung und struktur
+% partition
+
+% when you begin a slide with a table or figure on it, always write
+% \begin{frame}[fragile]
+% the fragile option is important
+
+% to make tables and figures fit, use
+% scalebox = '0.75'
+% or another number
 
@@
 % \usepackage[utf8]{inputenc}
-% \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
 % \usepackage{floatrow}
-% \usepackage{booktabs}
+\usepackage{booktabs}
 % \usepackage{rotating}
@@
 \begin{frame}[fragile]
+\frametitle{Summary Statistics}
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sat Feb 29 22:45:36 2020
+% Sun Mar 01 16:40:03 2020
 \begin{table}[ht]
@@
 
-% \begin
-% \frame[allowframebreaks]{\frametitle{References}
-% 		\tiny
-% 		\printbibliography
-% }
+\begin{frame}[fragile]
+\frametitle{Dynamics}
+
+\begin{figure}
+  \caption{Yearly dynamics of total grants in Meals and Trips program}
+  \label{totalGrantsDyn}
+
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-GrantTrend-1}
+
+}
+
+\end{knitrout}
+
+% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
+From left to right: Meals, Trips.
+From top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+\end{figure}
+
+\end{frame}
+
+\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+
+\begin{frame}
+\frametitle{Empirische Ansatz}
+\begin{equation}
+\label{SimpleLinearModel}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+\end{frame}
+
+\subsection{Direkte Effekte von CHILDRENs Zuschüssen}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Mahlzeiten und Zuschüsse}
+
+\begin{table}
+\caption{Association between number of meals and real subsidy}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
+                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
+realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
+                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
+eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
+                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
+\midrule
+R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
+Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
+Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
+RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Ausflüge und Zuschüsse}
+
+\begin{table}
+\caption{Association between number of trips and real subsidy}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
+                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
+\midrule
+R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
+Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
+RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsTrips}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\subsection{Selbstwertgefühl, Alltagskompetenzen und Zuschüsse}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
+
+\begin{table}
+\caption{Association between selfworth and subsidy per beneficiary}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              \\
+ML1                            &          &          &          &          & $0.24^{***}$ \\
+                               &          &          &          &          & $(0.06)$     \\
+ML2                            &          &          &          &          & $0.37^{***}$ \\
+                               &          &          &          &          & $(0.05)$     \\
+ML3                            &          &          &          &          & $0.15^{***}$ \\
+                               &          &          &          &          & $(0.04)$     \\
+\hline
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{SelfworthRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+
+\begin{table}
+\caption{Association between everyday expertise and subsidy per beneficiary}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) & (6) \\
+\hline
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
+ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
+                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
+ML4                            &          &          &          &          &              & $0.49^{***}$ \\
+                               &          &          &          &          &              & $(0.06)$     \\
+\hline
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{DayToDaySkillsRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Seltener krank}
+
+\begin{table}
+\caption{Association between healthy meals criterion and beneficiaries being less ill}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
+ML1                 &              &             &              &              & $0.12^{*}$   \\
+                    &              &             &              &              & $(0.06)$     \\
+ML2                 &              &             &              &              & $0.27^{***}$ \\
+                    &              &             &              &              & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-LessIll}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Ernährungswissen}
+
+\begin{table}
+\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
+ML1                 &          &          &            &          & $0.26^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML2                 &          &          &            &          & $0.24^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML3                 &          &          &            &          & $0.37^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-DietaryKnowledge}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Wertschätzung für gesundes Essen}
+
+\begin{table}
+\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
+ML1                 &              &          &              &            & $0.03$       \\
+                    &              &          &              &            & $(0.07)$     \\
+ML2                 &              &          &              &            & $0.47^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+ML3                 &              &          &              &            & $0.24^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-AppreciateHealthy}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\frame[allowframebreaks]{\frametitle{References}
+		\tiny
+		\printbibliography
+}
 

### 2020-03-01 presentation.Rnw
added partitions

@@
 Ludwig-Maximilians-Universität München}
-\date{March 3, 2020}
+\date{3. März 2020}
 
@@
 }
+\section{Einleitung}
+
+\begin{frame}[fragile]
+\frametitle{Einleitung}
+
+\begin{itemize}
+ \item<1-> Text visible on slide 1
+ \item<2-> Text visible on slide 2
+ \item<3> Text visible on slide 3
+ \item<4-> Text visible on slide 4
+\end{itemize}
+
+\end{frame}
+
+\section{Datenaufbereitung}
+
+\begin{frame}[fragile]
+\frametitle{Datenaufbereitung}
+
+\begin{itemize}
+ \item<1-> Text visible on slide 1
+ \item<2-> Text visible on slide 2
+ \item<3> Text visible on slide 3
+ \item<4-> Text visible on slide 4
+\end{itemize}
+
+\end{frame}
 
@@
 
+\section{DID - Estimation}
+
+\begin{frame}[fragile]
+\frametitle{Graphical evidence}
+\end{frame}
+
+\section{Partition}
+
+\begin{frame}[fragile]
+\frametitle{Partition Mittagstisch}
+<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
+
+colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
+colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
+
+xtable(partition_meals,
+                               # digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Meals", 
+          label = 'partitionmeals',
+          align = "lccc",
+          scalebox = "0.5"
+          )
+#print(partition_meals, include.rownames = FALSE)
+@
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Partition Entdeckerfonds}
+
+<<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+xtable(partition_trips,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition of outcomes, Trips",
+          label = 'partitiontrips',
+          align = "lccc",
+          scalebox = "0.5"
+          )
+# print(partition_meals, partition_trips, include.rownames = FALSE)
+@
+
+\end{frame}
+
 \frame[allowframebreaks]{\frametitle{References}

### 2020-03-01 presentation.tex
added partitions

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 16:40:03 2020
+% Sun Mar 01 17:15:18 2020
 \begin{table}[ht]
@@
 
+\section{DID - Estimation}
+
+\begin{frame}[fragile]
+\frametitle{Graphical evidence}
+\end{frame}
+
+\section{Partition}
+
+\begin{frame}[fragile]
+\frametitle{Partition Mittagstisch}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Sun Mar 01 17:15:22 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Meals & Mapping, Meals & Information, Meals \\ 
+  \hline
+1 & participateMore & participateMore & 1.00 \\ 
+  2 & tasksLunch & tasksLunch & 1.00 \\ 
+  3 & ownIdeas & ownIdeas & 1.00 \\ 
+  4 & stayLonger & stayLonger & 1.00 \\ 
+  5 & dietaryKnowledge & dietaryKnowledge & 1.00 \\ 
+  6 & appreciateHealthy & appreciateHealthy & 1.00 \\ 
+  7 & foodCulture & foodCulture & 1.00 \\ 
+  8 & lessIll & lessIll & 1.00 \\ 
+  9 & betterTeamwork & betterTeamwork & 1.00 \\ 
+  10 & moreRegularSchoolVisits & moreRegularSchoolVisits & 1.00 \\ 
+  11 & addressProblems & addressProblems & 1.00 \\ 
+  12 & reduced\_var\_1 & moreConcentrated & 0.66 \\ 
+  13 & reduced\_var\_1 & moreBalanced & 0.66 \\ 
+  14 & reduced\_var\_2 & monthlyCooks & 0.42 \\ 
+  15 & reduced\_var\_2 & weeklyCooks & 0.42 \\ 
+  16 & reduced\_var\_2 & shoppers & 0.42 \\ 
+  17 & reduced\_var\_2 & easyDishes & 0.42 \\ 
+  18 & reduced\_var\_3 & dayToDaySkills & 0.43 \\ 
+  19 & reduced\_var\_3 & moreIndependent & 0.43 \\ 
+  20 & reduced\_var\_3 & selfworth & 0.43 \\ 
+  21 & reduced\_var\_3 & moreOpen & 0.43 \\ 
+  22 & reduced\_var\_3 & moreConfidence & 0.43 \\ 
+  23 & reduced\_var\_3 & proud & 0.43 \\ 
+  24 & reduced\_var\_4 & betterReading & 0.53 \\ 
+  25 & reduced\_var\_4 & betterNumbers & 0.53 \\ 
+  26 & reduced\_var\_4 & betterGrades & 0.53 \\ 
+  27 & reduced\_var\_5 & influenceHome & 0.41 \\ 
+  28 & reduced\_var\_5 & cookAtHome & 0.41 \\ 
+  29 & reduced\_var\_5 & askRecipes & 0.41 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Meals} 
+\label{partitionmeals}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Partition Entdeckerfonds}
+
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Sun Mar 01 17:15:22 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccc}
+  \hline
+ & Variable, Trips & Mapping, Trips & Information, Trips \\ 
+  \hline
+1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
+  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
+  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
+  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
+  5 & tripsBudget & tripsBudget & 1.00 \\ 
+  6 & tripsMoney & tripsMoney & 1.00 \\ 
+  7 & tripsReview & tripsReview & 1.00 \\ 
+  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
+  9 & tripsMobility & tripsMobility & 1.00 \\ 
+  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
+  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
+  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
+  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
+  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
+  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
+  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
+  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
+  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
+  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
+  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
+   \hline
+\end{tabular}
+\caption{Partition of outcomes, Trips} 
+\label{partitiontrips}
+\end{table}
+
+\end{frame}
+
 \frame[allowframebreaks]{\frametitle{References}

### 2020-03-01 presentation.Rnw
Update
ojhno

--- 2020-03-01 presentation.Rnw
@@
 library(texreg)
-opts_chunk$set(fig.path='figure/beamer-',fig.align='center',fig.show='hold',size='footnotesize')
+opts_chunk$set(fig.path='figure/beamer-',fig.align='center',fig.show='hold',size='footnotesize', fig.height=2.8, fig.width=4.2)
 @
@@
 
-\section{Summary Statistics}
+\section{Summary Statistics and Fundamental Dynamics}
+\subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
 
@@
 @
+\end{frame}
 
+\subsection{Entwicklung der Fördersummen über die Zeit}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Summe}
+
+<<FundamentalDynamicsMealsTotal, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+totalMealsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealSub.Rds")
+print(totalMealsGrantsDyn, caption = "Fundamentale Dynamik Mittagstisch: Summe", label = "fundamentalMittagstischSumme")
+@
 \end{frame}
@@
 \begin{frame}[fragile]
-\frametitle{Dynamics}
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median}
 
-\begin{figure}
-  \caption{Yearly dynamics of total grants in Meals and Trips program}
-  \label{totalGrantsDyn}
+<<FundamentalDynamicsMealsMedian, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 
-<<GrantTrend, echo=FALSE, message=FALSE>>=
-totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-print(totalGrantsDyn, scalebox = '0.25')
+medianMealsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/medianRealSub.Rds")
+print(medianMealsGrantsDyn, caption = "Fundamentale Dynamik Mittagstisch: Median", label = "fundamentalMittagstischMedian")
 @
+\end{frame}
 
-% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
-From left to right: Meals, Trips.
-From top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-\end{figure}
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median pro Begünstigter}
+<<FundamentalDynamicsMealsMedianPerBene, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
 
+medianMealsGrantsDynBene = readRDS("./ANALYSIS/GRAPHS/PAPER/medianSubInd.Rds")
+print(medianMealsGrantsDynBene, caption = "Fundamentale Dynamik Mittagstisch: Median pro Begünstigter", label = "fundamentalMittagstischMedianBeneficiary")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Summe}
+
+<<FundamentalDynamicsTripsTotal, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+totalTripsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealTripSub.Rds")
+print(totalTripsGrantsDyn, caption = "Fundamentale Dynamik Entdeckerfonds: Summe", label = "fundamentalEntdeckerfondsSumme")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median}
+
+<<FundamentalDynamicsTripsMedian, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianTripsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/medianRealTripSub.Rds")
+print(medianTripsGrantsDyn, caption = "Fundamentale Dynamik Entdeckerfonds: Median", label = "fundamentalEntdeckerfondsMedian")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median pro Begünstigter}
+<<FundamentalDynamicsTripsMedianPerBene, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianTripsGrantsDynBene = readRDS("./ANALYSIS/GRAPHS/PAPER/medianTripsSubInd.Rds")
+print(medianTripsGrantsDynBene, caption = "Fundamentale Dynamik Entdeckerfonds: Median pro Begünstigter", label = "fundamentalEntdeckerfondsMedianBeneficiary")
+@
+\end{frame}
+
+\subsection{Dynamiken des Selbstwertgefühls und der Alltagskompetenzen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Selbstwertgefühl": Dynamik}
+<<SelfworthTime, echo=FALSE, message=FALSE>>=
+selfworthtimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/selfworth_Time.Rds")
+print(selfworthtimeplot, label = "selfworthtimeplot")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Alltagskompetenzen": Dynamik}
+<<SelfworthTime, echo=FALSE, message=FALSE>>=
+daytodaytimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/dayToDay_Time.Rds")
+print(daytodaytimeplot, label = "daytodaytimeplot")
+@
+\end{frame}
+
+\subsection{Dynamiken der gesundheitsrelevanten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Dynamik}
+<<lessIllTime, echo=FALSE, message=FALSE>>=
+lessilltimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/lessIll_Time.Rds")
+print(lessilltimeplot, label = "lessilltimeplot")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
+
+<<appreciateTime, echo=FALSE, message=FALSE>>=
+appreciatetimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate_Time.Rds.Rds")
+print(appreciatetimeplot, label = "lessilltimeplot")
+@
 \end{frame}

### 2020-03-01 presentation.tex
Update
ojhno

--- 2020-02-29 presentation.tex
@@
 
-\section{Summary Statistics}
+\section{Summary Statistics and Fundamental Dynamics}
+\subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
 
 \begin{frame}[fragile]
+\frametitle{Summary Statistics}
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sat Feb 29 22:45:36 2020
+% Sun Mar 01 17:09:51 2020
 \begin{table}[ht]
@@
 
-% \begin
-% \frame[allowframebreaks]{\frametitle{References}
-% 		\tiny
-% 		\printbibliography
-% }
+\subsection{Entwicklung der Fördersummen über die Zeit}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Mittagstisch: Summe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsTotal-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Mittagstisch: Median}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsMedian-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Mittagstisch: Median pro Begünstigter}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsMedianPerBene-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Entdeckerfonds: Summe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsTotal-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Entdeckerfonds: Median}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsMedian-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Fundamentale Dynamiken der Fördersumme, Entdeckerfonds: Median pro Begünstigter}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsMedianPerBene-1}
+
+}
+
+\end{frame}
+
+\frame[allowframebreaks]{\frametitle{References}
+		\tiny
+		\printbibliography
+}
 

### 2020-03-01 presentation.Rnw
Update

--- 2020-03-01 presentation.Rnw
@@
 % \usepackage{graphicx}
-% \usepackage[utf8]{inputenc}
+\usepackage[utf8]{inputenc}
 \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
@@
 
-\end{frame}
-
 \section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
@@
 \begin{frame}
-\frametitle{Empirische Ansatz}
+\frametitle{Empirischer Ansatz}
 \begin{equation}
@@
 
-\section{DID - Estimation}
-
-\begin{frame}[fragile]
-\frametitle{Graphical evidence}
-\end{frame}
-
 \section{Partition}
@@
 \frametitle{Partition Entdeckerfonds}
-
 <<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 @
+\end{frame}
 
+\section{Effekte des Entdeckerfonds}
+
+\subsection{Idee}
+
+\begin{frame}[fragile]
+\frametitle{Idee}
+\end{frame}
+
+\subsection{Empirische Methode}
+
+\begin{frame}[fragile]
+\frametitle{Definition der Treatmentgruppe}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zielvariable}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Graphische Darstellung: Alltagskompetenzen}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Graphische Darstellung: Selbstwertgefühl}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{DID - Schätzung}
+\end{frame}
+
+\subsection{Ergebnisse}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
 \end{frame}

### 2020-03-01 paper.Rnw
hjklooi

--- 2020-02-29 paper.Rnw
@@
 texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
 
@@
 
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")
+stargazer(lessIllOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge", align = TRUE, label = "dietaryOdds")
+stargazer(dietaryOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge", align = TRUE, label = "dietaryOdds")
 @
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet", align = TRUE, label = "appreciateOdds")
+stargazer(appreciateOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet", align = TRUE, label = "appreciateOdds")
 @
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth", align = TRUE, label = "selfworthOdds")
+stargazer(selfworthOdds@coef3, title= "Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth", align = TRUE, label = "selfworthOdds")
 @
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise", align = TRUE, label = "dayToDayOdds")
+stargazer(dayToDayOdds@coef3, title= "Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise", align = TRUE, label = "dayToDayOdds")
 @
@@
 Data preparation, fundamental dynamics: everybody\\
-Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+Factor analysis, general regressions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
 DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl

### 2020-03-01 presentation.Rnw
vbnm

@@
 \begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median}
+
+<<FundamentalDynamicsMealsMedian, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianMealsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/medianRealSub.Rds")
+print(medianMealsGrantsDyn, caption = "Fundamentale Dynamik Mittagstisch: Median", label = "fundamentalMittagstischMedian")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median pro Begünstigter}
+<<FundamentalDynamicsMealsMedianPerBene, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianMealsGrantsDynBene = readRDS("./ANALYSIS/GRAPHS/PAPER/medianSubInd.Rds")
+print(medianMealsGrantsDynBene, caption = "Fundamentale Dynamik Mittagstisch: Median pro Begünstigter", label = "fundamentalMittagstischMedianBeneficiary")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Summe}
+
+<<FundamentalDynamicsTripsTotal, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+totalTripsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/totalRealTripSub.Rds")
+print(totalTripsGrantsDyn, caption = "Fundamentale Dynamik Entdeckerfonds: Summe", label = "fundamentalEntdeckerfondsSumme")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median}
+
+<<FundamentalDynamicsTripsMedian, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianTripsGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/medianRealTripSub.Rds")
+print(medianTripsGrantsDyn, caption = "Fundamentale Dynamik Entdeckerfonds: Median", label = "fundamentalEntdeckerfondsMedian")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median pro Begünstigter}
+<<FundamentalDynamicsTripsMedianPerBene, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+medianTripsGrantsDynBene = readRDS("./ANALYSIS/GRAPHS/PAPER/medianTripsSubInd.Rds")
+print(medianTripsGrantsDynBene, caption = "Fundamentale Dynamik Entdeckerfonds: Median pro Begünstigter", label = "fundamentalEntdeckerfondsMedianBeneficiary")
+@
+\end{frame}
+
+\subsection{Dynamiken des Selbstwertgefühls und der Alltagskompetenzen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Selbstwertgefühl": Dynamik}
+<<SelfworthTime, echo=FALSE, message=FALSE>>=
+selfworthtimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/selfworth_Time.Rds")
+print(selfworthtimeplot, label = "selfworthtimeplot")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Alltagskompetenzen": Dynamik}
+<<DayToDayTime, echo=FALSE, message=FALSE>>=
+daytodaytimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/dayToDay_Time.Rds")
+print(daytodaytimeplot, label = "daytodaytimeplot")
+@
+\end{frame}
+
+\subsection{Dynamiken der gesundheitsrelevanten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Dynamik}
+<<lessIllTime, echo=FALSE, message=FALSE>>=
+lessilltimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/lessIll_Time.Rds")
+print(lessilltimeplot, label = "lessilltimeplot")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
+
+<<appreciateTime, echo=FALSE, message=FALSE>>=
+appreciatetimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate_Time.Rds.Rds")
+print(appreciatetimeplot, label = "lessilltimeplot")
+@
+\end{frame}
 \frametitle{Dynamics}

### 2020-03-01 presentation.Rnw
first translations to German

--- 2020-03-01 presentation.Rnw
@@
 % \usepackage{graphicx}
-\usepackage[utf8]{inputenc}
+% \usepackage[utf8]{inputenc}
 \usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
@@
 
-\section{Summary Statistics}
+\section{Zusammenfassende Statistiken}
 
 \begin{frame}[fragile]
-\frametitle{Summary Statistics}
+\frametitle{Zusammenfassende Statistiken}
 <<SummaryStatistics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 
-colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
+colnames(fundamental_dynamics) <- c("Jahr", "Begünstigte, Mittagstisch", "Begünstigte, Entdeckerfonds", "Einrichtungen, Mittagstisch", "Einrichtungen, Entdeckerfonds")
 
@@
           label = "fundamentalDynamics"
-          ), scalebox = '0.75')
+          ), scalebox = '0.7')
 
@@
 
-\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\end{frame}
+
+\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
 \begin{frame}
-\frametitle{Empirischer Ansatz}
+\frametitle{Empirische Ansatz}
 \begin{equation}
@@
 
-texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.5, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
+texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.5, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\\\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
 
@@
 
+\section{DID - Estimation}
+
+\begin{frame}[fragile]
+\frametitle{Graphical evidence}
+\end{frame}
+
 \section{Partition}
@@
 \frametitle{Partition Entdeckerfonds}
+
 <<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 @
-\end{frame}
 
-\section{Effekte des Entdeckerfonds}
-
-\subsection{Idee}
-
-\begin{frame}[fragile]
-\frametitle{Idee}
-\end{frame}
-
-\subsection{Empirische Methode}
-
-\begin{frame}[fragile]
-\frametitle{Definition der Treatmentgruppe}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Zielvariable}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Graphische Darstellung: Alltagskompetenzen}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Graphische Darstellung: Selbstwertgefühl}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{DID - Schätzung}
-\end{frame}
-
-\subsection{Ergebnisse}
-
-\begin{frame}[fragile]
-\frametitle{Alltagskompetenzen}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Selbstwertgefühl}
 \end{frame}

### 2020-03-01 presentation.tex
Update
first translations to German

--- 2020-03-01 presentation.tex
@@
 
-\section{Summary Statistics}
+\section{Zusammenfassende Statistiken}
 
 \begin{frame}[fragile]
-\frametitle{Summary Statistics}
+\frametitle{Zusammenfassende Statistiken}
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 17:15:18 2020
+% Sun Mar 01 20:25:18 2020
 \begin{table}[ht]
 \centering
-\scalebox{0.75}{
+\scalebox{0.7}{
 \begin{tabular}{lccccc}
   \hline
- & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
+ & Jahr & Begünstigte, Mittagstisch & Begünstigte, Entdeckerfonds & Einrichtungen, Mittagstisch & Einrichtungen, Entdeckerfonds \\ 
   \hline
@@
 
-\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
@@
 \begin{table}
-\caption{Association between number of meals and real subsidy}
+\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
 \begin{center}
@@
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 17:15:22 2020
+% Sun Mar 01 20:25:23 2020
 \begin{table}[ht]

### 2020-03-01 paper.tex
ijocjjvldkldklllll
Update
commit pull

--- 2020-02-28 paper.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:48:26 2020
+% Sun Mar 01 18:56:51 2020
 \begin{table}[ht]
@@
 \multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:48:53 PM
+% Date and time: So, Mrz 01, 2020 - 18:56:58
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
+  \caption{Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
   \label{lessIllOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
+% Date and time: So, Mrz 01, 2020 - 18:56:58
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
+  \caption{Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
   \label{dietaryOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:48:54 PM
+% Date and time: So, Mrz 01, 2020 - 18:56:58
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
+  \caption{Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
   \label{appreciateOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
+% Date and time: So, Mrz 01, 2020 - 18:56:58
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
+  \caption{Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
   \label{selfworthOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Thu, Feb 27, 2020 - 11:48:55 PM
+% Date and time: So, Mrz 01, 2020 - 18:56:58
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
+  \caption{Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
   \label{dayToDayOdds} 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Thu Feb 27 23:48:56 2020
+% Sun Mar 01 18:56:58 2020
 \begin{table}[ht]
@@
 
-\begin{figure}
-  \caption{The trend of weekly cooks over time}
-  \label{weeklyCooks_Trend}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/WeeklyCooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the weekly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{The Trend of monthly cooks over time}
-  \label{monthlyCooks_Trend}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/MonthlyCooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to the monthly cooks they made.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
 \section{Division of tasks}

### 2020-03-01 presentation.Rnw

--- 2020-03-01 presentation.Rnw
@@
 
-\section{Summary Statistics and Fundamental Dynamics}
+\section{Zusammenfassende Statistiken}
 \subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
@@
 \begin{frame}[fragile]
-\frametitle{Summary Statistics}
+\frametitle{Zusammenfassende Statistiken}
 <<SummaryStatistics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
@@
 \end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Dynamics}
@@
 
-\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\end{frame}
+
+\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
@@
 \end{equation}
-
 \end{frame}

### 2020-03-01 presentation.tex

@@
 \section{Zusammenfassende Statistiken}
+\subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:25:18 2020
+% Sun Mar 01 20:36:52 2020
 \begin{table}[ht]
@@
 
+\end{frame}
+
+\subsection{Entwicklung der Fördersummen über die Zeit}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Summe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsTotal-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsMedian-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Mittagstisch: Median pro Begünstigter}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsMealsMedianPerBene-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Summe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsTotal-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsMedian-1}
+
+}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Dynamik der Fördersumme, Entdeckerfonds: Median pro Begünstigter}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-FundamentalDynamicsTripsMedianPerBene-1}
+
+}
+
+\end{frame}
+
+\subsection{Dynamiken des Selbstwertgefühls und der Alltagskompetenzen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Selbstwertgefühl": Dynamik}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-SelfworthTime-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Alltagskompetenzen": Dynamik}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-DayToDayTime-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\subsection{Dynamiken der gesundheitsrelevanten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Dynamik}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllTime-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
+
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/appreciate\_Time.Rds.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(appreciatetimeplot, label = "{}lessilltimeplot"{}): Objekt 'appreciatetimeplot' nicht gefunden}}\end{kframe}
+\end{knitrout}
 \end{frame}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:25:23 2020
+% Sun Mar 01 20:37:09 2020
 \begin{table}[ht]
@@
 \frametitle{Partition Entdeckerfonds}
-
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:25:23 2020
+% Sun Mar 01 20:37:09 2020
 \begin{table}[ht]
@@
 
+\section{Effekte des Entdeckerfonds}
+
+\subsection{Idee}
+
+\begin{frame}[fragile]
+\frametitle{Idee}
+\end{frame}
+
+\subsection{Empirische Methode}
+
+\begin{frame}[fragile]
+\frametitle{Definition der Treatmentgruppe}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zielvariable}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Graphische Darstellung: Alltagskompetenzen}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Graphische Darstellung: Selbstwertgefühl}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{DID - Schätzung}
+\end{frame}
+
+\subsection{Ergebnisse}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
+\end{frame}
+
 \frame[allowframebreaks]{\frametitle{References}

### 2020-03-01 presentation.Rnw
xkxk

--- 2020-03-01 presentation.Rnw
@@
 
-\section{Summary Statistics and Fundamental Dynamics}
+\section{Summary Statistics und Fundamentale Dynamiken}
 \subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
@@
 \subsection{Entwicklung der Fördersummen über die Zeit}
+
+\begin{frame}[fragile]
+\frametitle{Umrechnung der Fördersummen: reale Werte}
+\begin{itemize}
+  \item{Darstellung der Entwicklung der Fördersummen über die Zeit: Zur besseren Vergleichbarkeit Berechung der realen Werte}
+  \item{Verwendung der Preisindizes des statistischen Bundesamtes}
+  \item{Mittagstisch Fördersumme: Preisindex für Nahrungsmittel und alkoholfreie Getränke}
+  \item{Entdeckerfonds: Preisindex für Freizeit, Unterhaltung und Kultur}
+  \item{Unterscheidung zwischen den Gesamtsummen, dem Median und dem Median pro Begünstigtem}
+\end{itemize}
+\end{frame}
 
@@
 
-\subsection{Dynamiken der gesundheitsrelevanten Variablen}
+\subsection{Dynamiken gesundheitsrelevanter Variablen}
 
@@
 \begin{frame}[fragile]
+\frametitle{Variable "erweitertes Ernährungswissen": Dynamik}
+<<dietaryTime, echo=FALSE, message=FALSE>>=
+dietarytimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/dietary_Time.Rds")
+print(dietarytimeplot, label = "dietarytimeplot")
+@
+\end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
-
 <<appreciateTime, echo=FALSE, message=FALSE>>=
@@
 
-\begin{figure}
-  \caption{Yearly dynamics of total grants in Meals and Trips program}
-  \label{totalGrantsDyn}
-
-<<GrantTrend, echo=FALSE, message=FALSE>>=
-totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-print(totalGrantsDyn, scalebox = '0.25')
-@
-
-% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+% \begin{figure}
+%   \caption{Yearly dynamics of total grants in Meals and Trips program}
+%   \label{totalGrantsDyn}
+%   
+% <<GrantTrend, echo=FALSE, message=FALSE>>=
+% totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+% print(totalGrantsDyn, scalebox = '0.25')
+% @
+% 
+% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-\end{figure}
+% \end{figure}
+%
 
 \section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\subsection{Empirischer Ansatz}
 
@@
 \end{equation}
+\begin{itemize}
+\item Schätzung der Modelle mit OLS (Ordinary least squares)
+\item An geeigneter Stelle: Vergleich der Ergebnisse mit WLS (Weighted least squares)
+\end{frame}
 
+\begin{frame}[fragile]
+\frametitle{Empirischer Ansatz: Imputieren fehlender Werte}
+\begin{itemize}
+\item Viele Organisationen beantworten nicht alle Fragen aus CHILDREN's Fragebogen 
+\begin{itemize}
+\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
+\item Imputierung der Daten mit einem organisations-spezifischem linearen Trend
+\end{itemize}
+\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empirischer Ansatz: Ausschließen von Außreißern}
+\begin{itemize}
+\item CHILDREN fördert einige Organisationen, die überproportional viele Essen ausgeben und Ausflüge unternehmen 
+\begin{itemize}
+\item Lösung: Wir erstellen Datensätze, in welchen solche Ausreißer ausgeschlossen werden
+\item Für die Variablen: Anzahl von Essen und Anzahl von Ausflügen
+\end{itemize}
+\item Definition eines Ausreißers: 
+\begin{itemize}
+\item Werte, die 1.5 Interquantilsäbstände unter des 25\%-Perzentils liegen
+\item Werte, die 1.5 Interqauntilsabstände über des 25\%-Perzentils liegen
+\end{itemize}
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empirische Fragestellungen (1), Assoziationen zwischen:}
+\begin{itemize}
+\item Der realen Fördersumme die eine Organisation für den Mittagstisch erhält und der Anzahl der Essen die sie ausgibt
+\item Der realen Fördersumme die eine Organisation für den Entdeckerfonds erhält und der Anzahl der Ausflüge die sie unternimmt
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, deren Selbstwertgefühl gestiegen ist
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, die ihre Alltagskompetenzen erweitert haben
+\end{itemize} 
 \end{frame}
@@
 \subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Empirische Fragestellungen (2), Assoziationen zwischen:}
+\begin{itemize}
+\item Dem standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählten standardisierten gesundheitsrelevanten Variablen 
+\begin{itemize}
+\item Anteil an Begünstigten, die seltener krank sind 
+\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben 
+\item Anteil an Begünstigten, die gesund Ernährung stärker wertschätzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
+<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+lessillDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/lessill.Rds")
+print(lessillDGE, label = "lessillDGE")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
+<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+dietaryDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/dietary.Rds")
+print(dietaryDGE, label = "dietaryDGE")
+@
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
+<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+appreciateDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate.Rds")
+print(appreciateDGE, label = "appreciateDGE")
+@
+\end{frame}
 

### 2020-03-01 presentation.tex
xkxk

@@
 
-\section{Zusammenfassende Statistiken}
+\section{Summary Statistics and Fundamental Dynamics}
 \subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
@@
 \begin{frame}[fragile]
-\frametitle{Zusammenfassende Statistiken}
+\frametitle{Summary Statistics}
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:36:52 2020
+% Sun Mar 01 19:09:39 2020
 \begin{table}[ht]
 \centering
-\scalebox{0.7}{
+\scalebox{0.75}{
 \begin{tabular}{lccccc}
   \hline
- & Jahr & Begünstigte, Mittagstisch & Begünstigte, Entdeckerfonds & Einrichtungen, Mittagstisch & Einrichtungen, Entdeckerfonds \\ 
+ & Year & Beneficiaries, Meals & Beneficiaries, Trips & Organizations, Meals & Organizations, Trips \\ 
   \hline
@@
 \end{frame}
-
-\begin{frame}[fragile]
 \frametitle{Dynamics}
@@
 
-\end{frame}
-
-\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
@@
 \end{equation}
+
 \end{frame}
@@
 \begin{table}
-\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
+\caption{Association between number of meals and real subsidy}
 \begin{center}
@@
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Dependent variable: number of meals \\ realSubsidy: subsidy for Meals program in 2015 EUR \\ eatersPerMeal: number of beneficiaries of Lunch program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:37:09 2020
+% Sun Mar 01 19:09:47 2020
 \begin{table}[ht]

### 2020-03-01 presentation.Rnw
fghj

@@
 \section{Summary Statistics und Fundamentale Dynamiken}
+
+\section{Zusammenfassende Statistiken}
+
 \subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
@@
 \subsection{Empirischer Ansatz}
+\end{frame}
+
+\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
@@
 \frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
-<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+<<dietaryDGEplot, echo=FALSE, message=FALSE>>=
 dietaryDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/dietary.Rds")
@@
 \frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
-<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+<<appreciateDGEplot, echo=FALSE, message=FALSE>>=
 appreciateDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate.Rds")

### 2020-03-01 presentation.tex
fghj

--- 2020-03-01 presentation.tex
@@
 
+\section{Summary Statistics und Fundamentale Dynamiken}
+
 \section{Zusammenfassende Statistiken}
+
 \subsection{Überblick: Entwickung der Anzahl der geförderten Einrichtungen}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:36:52 2020
+% Sun Mar 01 20:46:57 2020
 \begin{table}[ht]
@@
 \begin{frame}[fragile]
+\frametitle{Variable "erweitertes Ernährungswissen": Dynamik}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryTime-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
-
 \begin{knitrout}\footnotesize
@@
 
-\begin{figure}
-  \caption{Yearly dynamics of total grants in Meals and Trips program}
-  \label{totalGrantsDyn}
-
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-GrantTrend-1}
-
-}
-
-\end{knitrout}
-
-% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+% \begin{figure}
+%   \caption{Yearly dynamics of total grants in Meals and Trips program}
+%   \label{totalGrantsDyn}
+%   
+% <<GrantTrend, echo=FALSE, message=FALSE>>=
+% totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+% print(totalGrantsDyn, scalebox = '0.25')
+% @
+% 
+% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-\end{figure}
+% \end{figure}
+%
 
+\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\subsection{Empirischer Ansatz}
 \end{frame}
@@
 \end{equation}
+\begin{itemize}
+\item Schätzung der Modelle mit OLS (Ordinary least squares)
+\item An geeigneter Stelle: Vergleich der Ergebnisse mit WLS (Weighted least squares)
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empirischer Ansatz: Imputieren fehlender Werte}
+\begin{itemize}
+\item Viele Organisationen beantworten nicht alle Fragen aus CHILDREN's Fragebogen 
+\begin{itemize}
+\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
+\item Imputierung der Daten mit einem organisations-spezifischem linearen Trend
+\end{itemize}
+\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empirischer Ansatz: Ausschließen von Außreißern}
+\begin{itemize}
+\item CHILDREN fördert einige Organisationen, die überproportional viele Essen ausgeben und Ausflüge unternehmen 
+\begin{itemize}
+\item Lösung: Wir erstellen Datensätze, in welchen solche Ausreißer ausgeschlossen werden
+\item Für die Variablen: Anzahl von Essen und Anzahl von Ausflügen
+\end{itemize}
+\item Definition eines Ausreißers: 
+\begin{itemize}
+\item Werte, die 1.5 Interquantilsäbstände unter des 25\%-Perzentils liegen
+\item Werte, die 1.5 Interqauntilsabstände über des 25\%-Perzentils liegen
+\end{itemize}
+\end{itemize} 
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empirische Fragestellungen (1), Assoziationen zwischen:}
+\begin{itemize}
+\item Der realen Fördersumme die eine Organisation für den Mittagstisch erhält und der Anzahl der Essen die sie ausgibt
+\item Der realen Fördersumme die eine Organisation für den Entdeckerfonds erhält und der Anzahl der Ausflüge die sie unternimmt
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, deren Selbstwertgefühl gestiegen ist
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, die ihre Alltagskompetenzen erweitert haben
+\end{itemize} 
 \end{frame}
@@
 \begin{frame}[fragile]
+\frametitle{Empirische Fragestellungen (2), Assoziationen zwischen:}
+\begin{itemize}
+\item Dem standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählten standardisierten gesundheitsrelevanten Variablen 
+\begin{itemize}
+\item Anteil an Begünstigten, die seltener krank sind 
+\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben 
+\item Anteil an Begünstigten, die gesund Ernährung stärker wertschätzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 244 rows containing missing values (position\_stack).}}\end{kframe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 244 rows containing missing values (position\_stack).}}\end{kframe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 244 rows containing missing values (position\_stack).}}\end{kframe}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Seltener krank}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:37:09 2020
+% Sun Mar 01 20:47:04 2020
 \begin{table}[ht]

### 2020-03-01 presentation.Rnw
ghjkl
resolved error from missing end
asdfghjklö

@@
 <<appreciateTime, echo=FALSE, message=FALSE>>=
-appreciatetimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate_Time.Rds.Rds")
+appreciatetimeplot <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate_Time.Rds")
 print(appreciatetimeplot, label = "lessilltimeplot")
@@
 
-\begin{frame}[fragile]
-\frametitle{Dynamics}
+% \begin{frame}[fragile]
+% \frametitle{Dynamics}
 
@@
 % \end{figure}
+
 %
 
-\section{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+% \end{frame}
+% 
+% 
+\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+
+% 
 \subsection{Empirischer Ansatz}
-\end{frame}
-
-\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
@@
 \frametitle{Empirischer Ansatz}
+
 \begin{equation}
@@
 \end{equation}
+
 \begin{itemize}
@@
 \item An geeigneter Stelle: Vergleich der Ergebnisse mit WLS (Weighted least squares)
+\end{itemize}
+
 \end{frame}
@@
 \begin{frame}[fragile]
-\frametitle{Empirischer Ansatz: Ausschließen von Außreißern}
+\frametitle{Empirischer Ansatz: Ausschließen von Ausreißern}
 \begin{itemize}

### 2020-03-01 ANALYSIS/DATA/control_variables.R
Update

@@ -87,3 +87,4 @@ view(Rnew)
 # dietaryKnowledge, appreciateHealthy, foodCulture, moreConcentrated, moreBalanced,
 # moreIndependent, moreOpen, moreConfidence, adressProblems, proud, enoughFood
 
+# Test

### 2020-03-01 ANALYSIS/DATA/control_variables.R
Update

@@ -86,5 +86,3 @@ view(Rnew)
 # selfworth, DGECriterialNo, subsidy, tasksLunch, monthlyCooks, weeklyCooks, shoppers, easyDishes,
 # dietaryKnowledge, appreciateHealthy, foodCulture, moreConcentrated, moreBalanced,
 # moreIndependent, moreOpen, moreConfidence, adressProblems, proud, enoughFood
-
-# Test

### 2020-03-01 presentation.tex
ghjkl
resolved error from missing end
bö
asdfghjklö
Update

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:46:57 2020
+% Sun Mar  1 23:08:51 2020
 \begin{table}[ht]
@@
 \begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/appreciate\_Time.Rds.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateTime-1}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+}
 
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(appreciatetimeplot, label = "{}lessilltimeplot"{}): Objekt 'appreciatetimeplot' nicht gefunden}}\end{kframe}
 \end{knitrout}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 20:47:04 2020
+% Sun Mar  1 23:08:56 2020
 \begin{table}[ht]
@@
 \section{Effekte des Entdeckerfonds}
+
+\begin{frame}[fragile]
+\frametitle{Fragestellung}
+\begin{itemize}
+\item Welchen Effekt besitzt die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds auf die teilnehmenden Kinder und Jugendlichen?
+\item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmmen 
+\item Hypothese: Die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds besitzt einen positiven Effekt auf die Alltagskompetenzen und das Selbstwertgefühl der Kinder und Jugendlichen
+\end{itemize}
+\end{frame}
 

### 2020-03-02 paper.Rnw
Update

@@
 \hline
-ID fixed effects       & $YES$     & $YES$        & $YES$     & $YES$        \\
-Year fixed effects     & $YES$     & $YES$        & $YES$     & $YES$        \\
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
 Number of observations & $428$     & $410$        & $428$     & $410$        \\
@@
 \hline
-ID fixed effects       & $YES$     & $YES$     & $YES$     & $YES$        \\
-Year fixed effects     & $YES$     & $YES$     & $YES$     & $YES$        \\
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
 Number of observations & $428$     & $410$     & $428$     & $410$        \\
@@
 
+\subsection{A5: Placebo test}
+
+\begin{figure}
+  \caption{Trend of weekly cooks}
+  \label{figureWeeklyCooks}
+
+<<Weekly cooks, echo=FALSE>>=
+figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
+print(figureWeeklyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend of monthly cooks}
+  \label{figureMonthlyCooks}
+
+<<Monthly cooks, echo=FALSE>>=
+figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
+print(figureMonthlyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \section{Division of tasks}

### 2020-03-02 paper.tex
Update

@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 18:56:51 2020
+% Mon Mar  2 10:26:01 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: So, Mrz 01, 2020 - 18:56:58
+% Date and time: Mo, Mär 02, 2020 - 10:26:06
 % Requires LaTeX packages: dcolumn 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar 01 18:56:58 2020
+% Mon Mar  2 10:26:06 2020
 \begin{table}[ht]
@@
 \end{table}
+
+\subsection{A5: Placebo test}
+
+\begin{figure}
+  \caption{Trend of weekly cooks}
+  \label{figureWeeklyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Weekly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend of monthly cooks}
+  \label{figureMonthlyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Monthly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
 

### 2020-03-02 paper.Rnw
xxx

--- 2020-03-01 paper.Rnw
@@
 
-\title{Analysis of survey data collected by CHILDREN for a better World e.V.}
+\title{Analysis of Survey Data Collected by CHILDREN for a better World e.V.}
 \author{
 Laura Huber\\
-\texttt{11709507}
+%\texttt{11709507}
 \and
 Laura Jepsen\\
-\texttt{11567799}
+%\texttt{11567799}
 \and
 Jonathan Kirschner\\
-\texttt{11724530}
+%\texttt{11724530}
 \and
 Rafael Schütz\\
-\texttt{11574909} 
+%\texttt{11574909} 
 \and 
 Yannick Zurl\\
-\texttt{11701793}
+%\texttt{11701793}
 \and
@@
 We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
-Using a differences-in-differences strategy, we cannot show a significant effect of participating in the trips program on the everyday expertise and selfworth of the beneficiaries.
+Using a differences-in-differences strategy, we cannot show a significant effect of participating in the Trips program on the everyday expertise and selfworth of the beneficiaries.
 \end{abstract}
@@
 \section{Introduction}
-
-CHILDREN supports organizations working with children and youth across Germany (in German: Einrichtungen der offenen Kinder- und Jugendarbeit) across Germany.
-We call them organizations in the following.
-They apply to CHILDREN for yearly grants.
-If approved, they are supposed to use them for specific purposes defined by CHILDREN.
-CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
-The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and youth that visit them.
-In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
-The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
-Unless otherwise specified, we consider all variables to be metric, even if they are ordinal.
-
-Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
-Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
-Children which grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
-This could have a negative influence on their character development.
-For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
-Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes.
-Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
-\textcite{Heckman.2010} investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
-
 CHILDREN for a better World e.V.
@@
 
-Previous research shows that childhood and youth are central in the development of character traits and future opportunities.
+Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Heckmann and Carneiro (2003) show that especially early family factors determine most of the gaps in high school attendance.
-Moreover, Deckers et.
-al.
-(2015) found, by experiments conducted in Germany, that children of higher educated parents are significantly more patient.
-Children from parents with lower income and a lower educational level typically have a lower weight at birth and are born in a later week of gestation, which are all indicators for bad initial conditions (Deckers et.
-al.
-2015, Case et.
-al.
-2002).
-Children that grow up in families with a low socio-economic status are often believed to be less mobile.
+Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
+Children that grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
 This could have a negative influence on their character development.
-For example, Chetty et.
-al (2012) investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
-Furthermore, the results of Deckers et.
-al.
-(2020) provide evidence for the effect of the social environment on prosocial attitudes.
-Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children.
-Heckmann et.
-al.
-(2010) investigated a preschool education program in the US.
-The authors show that an investment in the improvement of the childhood conditions could have a high rate of return, even after controlling for possible distortions.
+For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
+Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes.
+Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
+\textcite{Heckman.2010} investigated a preschool education program in the US.
+He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
 
@@
 Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries.
-The aim of our applied differences-in-differences estimation is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+The aim of our applied differences-in-differences estimation is to test whether the activities offered by the Trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
 We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth.
 On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill.
-By using the differences-in-differences (DID) strategy, the estimates show that the participation in the trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
-Strikingly, we observe a negative association between participating in the trips program and selfworth.
+By using the differences-in-differences (DID) strategy, the estimates show that the participation in the Trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
+Strikingly, we observe a negative association between participating in the Trips program and selfworth.
 However, the results of the DID estimation should not be overstated because of the small sample size.
@@
 The proceeding section reports different regression results.
-After that, we implement the differences-in-differences strategy to test for the effects of the trips program.
+After that, we implement the differences-in-differences strategy to test for the effects of the Trips program.
 Finally, we conclude and provide suggestions for CHILDREN.
@@
 \label{data}
-
 To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018.
@@
 Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
-The final dataset for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
+The final dataset that we used for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
 The questions are divided in two categories.
-The first part of the data set includes variables regarding the meals program.
-The second part contains variables affecting the trips program.
+The first part of the data set includes variables regarding the Meals program.
+The second part contains variables affecting the Trips program.
 The final data set comprises the years 2011 to 2018.
@@
 \subsection{Fundamental Dynamics} 
-
 In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
@@
 In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018.
-In the trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018.
+In the Trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018.
 In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.
 
-\subsection{Trends of grants}
+\subsection{Trends of Grants}
 
 \begin{figure}
-  \caption{Yearly dynamics of total grants in Meals and Trips program}
+  \caption{Yearly Dynamics of Total Grants in Meals and Trips Program}
   \label{totalGrantsDyn}
@@
 For the dynamics of figure \ref{totalGrantsDyn} we visualze the dynamics of CHILDRENs' grants by distinguishing between the sum of grants in one year, the median and the median grant per beneficiary.
-We also compare the grants of the Lunch and the Trips Program.
+We also compare the grants of the Lunch and the Trips program.
 
@@
 Since 2017 an increase is again visible.
-In comparison to this, there is a clearer negative trend in median Meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
-In accordance, the median Meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.
-
-In the total Trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince.
-The Trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
-
-These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that children was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
+In comparison to this, there is a clearer negative trend in median meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
+In accordance, the median meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.
+
+In the total trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince.
+The trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
+
+These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that CHILDREN was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
 
@@
 These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
-Figure \ref{HealthTimeplots} displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+Figure \ref{HealthTimeplots} displays the share of organizations in each category of the health outcome from 2011 to 2018.
 The possible values are: all, most, some, few, and none.
@@
 \begin{figure}
-  \caption{Health outcome over time}
+  \caption{Health Outcome Over Time}
   \label{HealthTimeplots}
@@
 These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few and none.}
+The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few and none.}
 \end{figure}
@@
 
-The the bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
+The bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
 Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
@@
 
-\subsection{Selfworth and everyday expertise}
+\subsection{Selfworth and Everyday Expertise}
 
@@
 These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise.
-Figure 4 displays the share of organizarions in each category of the health outcome from 2011 to 2018.
+Figure 4 displays the share of organizations in each category of the health outcome from 2011 to 2018.
 The possible values are: all, most, some, few, and none.
@@
 \begin{figure}
-  \caption{Selfworth and everyday expertise over time}
+  \caption{Selfworth and Everyday Expertise Over Time}
   \label{EqualityTimeplots}
@@
 In the bottom plot of figure \ref{EqualityTimeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organisations have a growing understanding for everyday expertise.
+The results are about similar to the previous results of selfworth: Most beneficiaries in most organizations have a growing understanding of everyday expertise.
 
@@
 
-texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association between number of meals and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association Between Number of Meals and Real Subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
@@
 As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
-Whether we look at the original data set, the one without outliers and the one with imputed values, a strong association becomes evident.
+Whether we look at the original data set, the one without outliers or the one with imputed values, a strong association becomes evident.
 The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
-In the case of the original data set, increasing the subsidy to an organization by one EUR is associated with 2.6 additional meals dispensed.
+In the case of the original data set, increasing the subsidy of an organization by one EUR is associated with 2.6 additional meals dispensed.
 This estimate is highly statistically significant.
@@
 
-texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association Between Number of Trips and Real Subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
@@
 
-\subsection{Variables of interest: selfworth and everyday expertise}
+\subsection{Variables of Interest: Selfworth and Everyday Expertise}
 
@@
 We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes.
-In fact, no coefficent is statistically significantly differnent from zero at any of the usual levels.
+In fact, no coefficent is statistically significantly different from zero at any of the usual levels.
 The four variables are recorded for each year in which the program was operative.
@@
 
-texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association Between Selfworth and Subsidy per Beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
@@
 
-texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
-
-@
-
-\subsection{Variables of interest: Health variables}
+texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association Between Everyday Expertise and Subsidy per Beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+
+@
+
+\subsection{Variables of Interest: Health Variables}
 
@@
 The x-axis displays the index for a healthy diet.
-The y-axis displays the share of organizarions in each category of the health outcome.
+The y-axis displays the share of organizations in each category of the health outcome.
 The possible values are: all, most, some, few and none.
@@
 The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not.
-The healthy food incex is calculated as the number of fulfilled criteria.
+The healthy food index is calculated as the number of fulfilled criteria.
 Examples for criteria are daily carbohydrates or daily vegetables.
@@
 All plots of Figure \ref{HealthPlots} show that most organizations suffice about 5 to 10 healthy food criteria.
-The largest part of criterion values are associated with most beneficiaries being less Ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
+The largest part of criterion values are associated with most beneficiaries being less ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
 It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
@@
 Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables.
-This connection is empiricaly examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.
+This connection is empirically examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.
 
@@
 These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the index for a healthy diet. The y-axis displays the share of organizarions in each category of the health outcome. The possible values are: all, most, some, few, and none}
+The x-axis plots the index for a healthy diet. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none}
 \end{figure}
 
-We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as predictor in each.
+We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as a predictor in each.
 By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
@@
 In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
-For the original data set, the coeffiecent is slightly negative.
+For the original data set, the coefficient is slightly negative.
 Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
@@
 
-In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weíghted least squares are much stronger.
+In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weighted least squares are much stronger.
 For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
@@
 For the imputed dataset we find a similar picture.
-Similary to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.
+Similar to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.
 
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association Between Healthy Meals Criterion and Beneficiaries Being Less Ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association Between Healthy Meals Criterion and Beneficiaries Dietary Knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association Between Healthy Meals Criterion and  Beneficiaries Appreciation of a Healthy Diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
@@
 Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their meals program.
-However, not all organizations receive additional funding to provide the trips program.
-This fact could be used for applying an empirical approach which determines the effects of the trips program by comparing a treatment with a control group.
-The aim of this analysis is to test whether the activities offered by the trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
+During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their Meals program.
+However, not all organizations receive additional funding to provide the Trips program.
+This fact could be used for applying an empirical approach which determines the effects of the Trips program by comparing a treatment with a control group.
+The aim of this analysis is to test whether the activities offered by the Trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
 
@@
 The basis of the empirical approach is the specification of the treatment and the control group.
-Using the data provided by children we determine the treatment group as all organizations that receive funding for both the trips and the meals program.
-On the other hand, the control group represents all organizations that only receive funding for the meals program.
-Therefore, the social institutions in the control group do not participate in the trips program.
+Using the data provided by children we determine the treatment group as all organizations that receive funding for both the Trips and the Meals program.
+On the other hand, the control group represents all organizations that only receive funding for the Meals program.
+Therefore, the social institutions in the control group do not participate in the Trips program.
 
@@
 
-When analyzing the available dataset, it was not certain which organizations actually received funding for the trips program.
+When analyzing the available dataset, it was not certain which organizations actually received funding for the Trips program.
 As previously mentioned, the CHILDREN survey consists of two parts.
-The first part contains questions that are specific to the meals program and the second part includes all questions which are relevant for organizations that receive funding for the trips program.
-The dataset shows that there are several organizations that did not provide information regarding the trips program.
+The first part contains questions that are specific to the Meals program and the second part includes all questions which are relevant for organizations that receive funding for the Trips program.
+The dataset shows that there are several organizations that did not provide information regarding the Trips program.
 In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
-Hence, we assumed that all organizations that did not provide information regarding the trips program in a given year, did not receive funding for the program and would be part of the control group.
-When analyzing the possible treatment group, we realized that some organizations did not completely answer the trips program survey.
-There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Entdeckerfonds survey questions such as the number of trips in a given year.
+Hence, we assumed that all organizations that did not provide information regarding the Trips program in a given year, did not receive funding for the program and would be part of the control group.
+When analyzing the possible treatment group, we realized that some organizations did not completely answer the Trips program survey.
+There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Trips program survey questions such as the number of trips in a given year.
 Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
-Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the trips program with the remaining funding of the year before.
+Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the Trips program with the remaining funding of the year before.
 
@@
 \begin{cases}
-1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the Trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
 0, & \text{otherwise}
@@
 
-In this setting, once an organization receives funding for the trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
-This implies that an organization remains in the control group as long as it does not receive funding for the trips program.
+In this setting, once an organization receives funding for the Trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
+This implies that an organization remains in the control group as long as it does not receive funding for the Trips program.
 Due to this definition, an organization cannot change from the treatment into the control group.
@@
 As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
-At first, new organizations are generally funded to provide the meals program and might receive funding for the trips program during later funding periods.
+At first, new organizations are generally funded to provide the Meals program and might receive funding for the Trips program during later funding periods.
 In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
@@
 \begin{cases}
-1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the trips program in year \begin{itshape}{t}\end{itshape}}\\
+1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the Trips program in year \begin{itshape}{t}\end{itshape}}\\
 0, & \text{otherwise}
@@
 
-Using this alternative treatment variable, the actual funding for the trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
+Using this alternative treatment variable, the actual funding for the Trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
 With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
@@
 
-The fact that all organizations within the control group did not answer the trips program survey questions was helpful to categorize the control and the treatment group.
-However, the impact of the trips program cannot be measured with variables that are specific to the trips program as these were only observed for the treatment group.
-Therefore, we have to use variables of the meals program as outcome variables in our analysis.
+The fact that all organizations within the control group did not answer the Trips program survey questions was helpful to categorize the control and the treatment group.
+However, the impact of the Trips program cannot be measured with variables that are specific to the Trips program as these were only observed for the treatment group.
+Therefore, we have to use variables of the Meals program as outcome variables in our analysis.
 For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
-Firstly, both variables are applicable to the trips program as well as the meals program.
+Firstly, both variables are applicable to the Trips program as well as the Meals program.
 In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
@@
 \begin{figure}
-  \caption{Trend in share of beneficiaries with improved selfworth}
+  \caption{Trend in Share of Beneficiaries With Improved Selfworth}
   \label{selfworth_Trend}
@@
 
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the Trips program starts in 2012.
 The y-axis represents the average answers from the organizations regarding to selfworth.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+The time trend of the average answers of the organizations in the treatment group is characterized by the solid red line, the answers of the control group by the dotted blue line.
 Additionally, the linear trends of both groups are included as the straight lines.}
@@
 \begin{figure}
-  \caption{Trend in share of beneficiaries with broadened everyday competence}
+  \caption{Trend in Share of Beneficiaries With Broadened Everyday Competence}
   \label{dayToDaySkills_Trend}
@@
 
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the Trips program starts in 2012.
 The y-axis represents the average answers from the organizations regarding to everyday expertise.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+The time trend of the average answers of the organizations in the treatment group is characterized by the solid red line, the answers of the control group by the dotted blue line.
 Additionally, the linear trends of both groups are included as the straight lines.}
@@
 
-To check for differences in treatment and control group, we created descriptive statistics regarding to the variables of interest.
+To check for differences in treatment and control group, we created descriptive statistics regarding the variables of interest.
 Figure 5 and Figure 6 represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
@@
 Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6).
-The divergence shown in both graphs suggests that funding for the trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
-This evidence could support the hypothesis that the trips program positively influences the beneficiaries.
+The divergence shown in both graphs suggests that funding for the Trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
+This evidence could support the hypothesis that the Trips program positively influences the beneficiaries.
 However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
@@
 
-For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the trips program has a positive influence on the selfworth and everyday expertise of the supported children.
-The DID estimator measures the effect of participating in the trips program by comparing the changes in dependent variables over time between the treatment and control group.
+For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the Trips program has a positive influence on the selfworth and everyday expertise of the supported children.
+The DID estimator measures the effect of participating in the Trips program by comparing the changes in dependent variables over time between the treatment and control group.
 The key identifying assumption for the DID strategy is the common trend assumption.
-The assumption states that, in the absence of the trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
+The assumption states that, in the absence of the Trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
 In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
@@
 As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$.
-The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the trips program.
+The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the Trips program.
 
@@
 For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
-Furthermore, we control for organization specific characteristics which include the subsidy received for the meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
+Furthermore, we control for organization specific characteristics which include the subsidy received for the Meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
 
@@
 \end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in the text.
+The outcome variable is standardized.
+Below each coefficient the robust standard errors are reported in parentheses.}
 \end{table}
 
-Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
-Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
-However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+Using the first definition of the treatment variable, the average treatment effect of participating in the Trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the Trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the Trips program in a given year.
 As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
@@
 \end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in the text.
+The outcome variable is standardized.
+Below each coefficient the robust standard errors are reported in parentheses.}
 \end{table}
@@
 However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
-This indicates that participating in the trips program would negatively influence the selfworth of the children and adolescents.
-This surprising result contradicts our hypothesis that the participation in the trips program positively influences the selfworth of the beneficiaries.
+This indicates that participating in the Trips program would negatively influence the selfworth of the children and adolescents.
+This surprising result contradicts our hypothesis that the participation in the Trips program positively influences the selfworth of the beneficiaries.
 As previously mentioned, the number of observation units in both treatment and control group is relatively small.
-Therefore, this unexpected negative effect of the trips program on selfworth should not be overstated.
+Therefore, this unexpected negative effect of the Trips program on selfworth should not be overstated.
 Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
@@
 Data on the individual level might be more precise because the children could assess themselves better.
-When using variables on the level of beneficiaries, we might observe a positive effect of the trips program on selfworth.
+When using variables on the level of beneficiaries, we might observe a positive effect of the Trips program on selfworth.
 As reported in the summary statistics, the outcome variable shows a low variation.
@@
 
-Until now CHILDREN only influences whether organizations are supported and how much funding they receive to provide both the trips and the meals program.
+Until now CHILDREN only influences whether organizations are supported and how much funding they receive to provide both the Trips and the Meals program.
 However, we find a strong positive correlation between the healthiness of the meals that organizations serve and health related outcomes of children and adolescents.
@@
 
-On the basis of the processed dataset, we cannot measure the causal effect of the trips program on everyday expertise and selfworth of beneficiaries.
-However, measuring significant effects of CHILDREN’s trips program might be possible if the data structure will be adjusted.
+On the basis of the processed dataset, we cannot measure the causal effect of the Trips program on everyday expertise and selfworth of beneficiaries.
+However, measuring significant effects of CHILDREN’s Trips program might be possible if the data structure will be adjusted.
 At this point, we recommend to directly ask the beneficiaries to answer the children specific questions of the survey.
@@
 For example, CHILDREN has asked for many survey questions from the supported organizations in every year across the whole observation period.
-Furthermore, the dataset includes variables regarding increased selfworth and broadened everyday expertise for both programs allowing a comparison of the meals and the trips program.
+Furthermore, the dataset includes variables regarding increased selfworth and broadened everyday expertise for both programs allowing a comparison of the meals and the Trips program.
 Hence, we recommend to continue asking the same questions in every year and selected variables for both programs.
@@
 
-texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less ill expanded model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
+texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less Ill Expanded Model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ regionalProducts: wether the organization offers meals with local ingredients or not \\\\ yearsSupportSince: the number of years an organization is already part of the Meals program \\\\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ state: german 'Bundeland' \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\\\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
@@
 
-stargazer(lessIllOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill", align = TRUE, label = "lessIllOdds")
+stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill", align = TRUE, label = "lessIllOdds")
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge", align = TRUE, label = "dietaryOdds")
+stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge", align = TRUE, label = "dietaryOdds")
 @
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodds Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet", align = TRUE, label = "appreciateOdds")
+stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet", align = TRUE, label = "appreciateOdds")
 @
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth", align = TRUE, label = "selfworthOdds")
+stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth", align = TRUE, label = "selfworthOdds")
 @
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodds Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise", align = TRUE, label = "dayToDayOdds")
+stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise", align = TRUE, label = "dayToDayOdds")
 @
@@
                                # digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of outcomes, Meals", 
+          caption = "Partition of Outcomes, Meals", 
           label = 'partitionmeals',
@@
                                #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of outcomes, Trips",
+          caption = "Partition of Outcomes, Trips",
           label = 'partitiontrips',
@@
 \end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in section 6.1.4.
+The outcome variable is standardized.
+Below each coefficient the p-values are reported in parentheses.}
 \end{table}
@@
 \end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in section 6.1.4.
+The outcome variable is standardized.
+Below each coefficient the p-values are reported in parentheses.}
 \end{table}
 
-\section{Division of tasks}
-
-Data preparation, fundamental dynamics: everybody\\
-Factor analysis, general regressions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
-DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
-\section{Ehrenwörtliche Erklärung aller Teilnehmer}
+% %\section{Division of tasks}
+% 
+% Data preparation, fundamental dynamics: everybody\\
+% Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+% DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
+% 
+% 
+% \section{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-03-02 paper.tex
xxx

--- 2020-02-29 paper.tex
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Sat Feb 29 17:58:47 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Mon Mar 02 10:59:09 2020
 \begin{table}[ht]
@@
 \begin{table}
-\caption{Association between number of meals and real subsidy}
+\caption{Association Between Number of Meals and Real Subsidy}
 \begin{center}
@@
 \begin{table}
-\caption{Association between number of trips and real subsidy}
+\caption{Association Between Number of Trips and Real Subsidy}
 \begin{center}
@@
 \begin{table}
-\caption{Association between selfworth and subsidy per beneficiary}
+\caption{Association Between Selfworth and Subsidy per Beneficiary}
 \begin{center}
@@
 \begin{table}
-\caption{Association between everyday expertise and subsidy per beneficiary}
+\caption{Association Between Everyday Expertise and Subsidy per Beneficiary}
 \begin{center}
@@
 
-\subsection{Variables of interest: Health variables}
+\subsection{Variables of Interest: Health Variables}
 
@@
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries being less ill}
+\caption{Association Between Healthy Meals Criterion and Beneficiaries Being Less Ill}
 \begin{center}
@@
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
+\caption{Association Between Healthy Meals Criterion and Beneficiaries Dietary Knowledge}
 \begin{center}
@@
 \begin{table}
-\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
+\caption{Association Between Healthy Meals Criterion and  Beneficiaries Appreciation of a Healthy Diet}
 \begin{center}
@@
 \end{center}
-\end{table}
-
-Using the first definition of the treatment variable, the average treatment effect of participating in the trips program on everyday expertise is negative, but not statistically significant.
-Therefore, the estimated coefficient in column (1) implies that the trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
-However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the trips program in a given year.
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in the text.
+The outcome variable is standardized.
+Below each coefficient the robust standard errors are reported in parentheses.}
+\end{table}
+
+Using the first definition of the treatment variable, the average treatment effect of participating in the Trips program on everyday expertise is negative, but not statistically significant.
+Therefore, the estimated coefficient in column (1) implies that the Trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
+However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the Trips program in a given year.
 As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
@@
 }
-\caption{Regression Results: Less ill expanded model}
+\caption{Regression Results: Less Ill Expanded Model}
 \label{expandLessIll}
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 29, 2020 - 17:58:55
+% Date and time: Mo., Mär 02, 2020 - 10:59:18
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries who are less frequently ill} 
+  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill} 
   \label{lessIllOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 29, 2020 - 17:58:55
+% Date and time: Mo., Mär 02, 2020 - 10:59:18
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and share of beneficiaries with expanded dietary knowledge} 
+  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge} 
   \label{dietaryOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 29, 2020 - 17:58:55
+% Date and time: Mo., Mär 02, 2020 - 10:59:18
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of index of healthy diet criteria fulfilled in organization's menu and the share of beneficiaries with increased appreciation for a healthy diet} 
+  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet} 
   \label{appreciateOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 29, 2020 - 17:58:55
+% Date and time: Mo., Mär 02, 2020 - 10:59:18
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with improved self-worth} 
+  \caption{Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth} 
   \label{selfworthOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Sa, Feb 29, 2020 - 17:58:55
+% Date and time: Mo., Mär 02, 2020 - 10:59:18
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of subsidy for Meals program in 2015 EUR and the share of beneficiaries with broadened everyday expertise} 
+  \caption{Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise} 
   \label{dayToDayOdds} 
@@
 
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Sat Feb 29 17:58:55 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Mon Mar 02 10:59:18 2020
 \begin{table}[ht]
@@
 \end{tabular}
-\caption{Partition of outcomes, Meals} 
+\caption{Partition of Outcomes, Meals} 
 \label{partitionmeals}
 \end{table}
-% latex table generated in R 3.5.1 by xtable 1.8-4 package
-% Sat Feb 29 17:58:55 2020
+% latex table generated in R 3.6.1 by xtable 1.8-4 package
+% Mon Mar 02 10:59:18 2020
 \begin{table}[ht]
@@
 \end{tabular}
-\caption{Partition of outcomes, Trips} 
+\caption{Partition of Outcomes, Trips} 
 \label{partitiontrips}
@@
 \end{center}
-\end{table}
-
-\section{Division of tasks}
-
-Data preparation, fundamental dynamics: everybody\\
-Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
-DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
-\section{Ehrenwörtliche Erklärung aller Teilnehmer}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in section 6.1.4.
+The outcome variable is standardized.
+Below each coefficient the p-values are reported in parentheses.}
+\end{table}
+
+% %\section{Division of tasks}
+% 
+% Data preparation, fundamental dynamics: everybody\\
+% Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+% DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
+% 
+% 
+% \section{Ehrenwörtliche Erklärung aller Teilnehmer}
 

### 2020-03-02 presentation.Rnw

@@
 
+\begin{frame}[fragile]
+\frametitle{Fragestellung}
+\begin{itemize}
+\item Welchen Effekt besitzt die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds auf die teilnehmenden Kinder und Jugendlichen?
+\item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmmen 
+\item Hypothese: Die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds besitzt einen positiven Effekt auf die Alltagskompetenzen und das Selbstwertgefühl der Kinder und Jugendlichen
+\end{itemize}
+\end{frame}
+
 \subsection{Idee}

### 2020-03-02 presentation.tex
lg

@@
 \frametitle{Zusammenfassende Statistiken}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar  1 23:08:51 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 10:21:37 2020
 \begin{table}[ht]
@@
 \scalebox{0.5}{
-\begin{tabular}{l c c c c c }
+\begin{tabular}{l c c c c c}
 \toprule
@@
 \midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+R$^2$           & $0.43$          & $0.73$         & $0.13$          & $0.21$          & $0.45$           \\
+Adj. R$^2$      & $0.43$          & $0.73$         & $0.12$          & $0.20$          & $0.45$           \\
+Num. obs.       & $329$           & $329$          & $250$           & $250$           & $440$            \\
+RMSE            & $39992.79$      & $27390.90$     & $3629.72$       & $3463.66$       & $39601.41$       \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \frametitle{Partition Mittagstisch}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar  1 23:08:56 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 10:21:45 2020
 \begin{table}[ht]
@@
 \frametitle{Partition Entdeckerfonds}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar  1 23:08:56 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 10:21:45 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw

@@
 \begin{frame}[fragile]
-\frametitle{Einleitung}
+\frametitle{CHILDREN for a better World e.V.}
 
 \begin{itemize}
- \item<1-> Text visible on slide 1
- \item<2-> Text visible on slide 2
- \item<3> Text visible on slide 3
- \item<4-> Text visible on slide 4
+ \item<1-> Spendenfinanzierte Kinderhilfsorganisation
+ \item<2-> Finanziert Einrichtungen deutschlandweit
+ \linebreak
+ \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
 \end{itemize}
@@
 \begin{frame}[fragile]
+\frametitle{Datenerhebung von CHILDREN}
+
+\begin{itemize}
+ \item<1-> Jährliche Umfragebögen an die Einrichtungen
+ \item<2-> Beantwortung durch Mitarbeiter
+ \item<3-> Verschiedene Fragen zu Mittagstisch und Entdeckerfonds
+ \item<4-> Generelle Variablen (z.B. Fördersumme, Anzahl angebotener Mahlzeiten, Anzahl Aktivitäten)
+ \item<5-> Abhängige Variablen (z.B. Selbstwertgefühl, seltener krank)
+
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Datenaufbereitung}
@@
 \begin{itemize}
- \item<1-> Text visible on slide 1
- \item<2-> Text visible on slide 2
- \item<3> Text visible on slide 3
- \item<4-> Text visible on slide 4
+ \item<1-> Arbeit mit dem Statistik-Programm “R”
+ \item<2-> Zusammenfügen der verschiedenen Datensätze
+ \item<3-> Anpassung und Vergleich der Variablennamen
+ \item<4-> Abstimmung des Teams über “Git”
+
 \end{itemize}

### 2020-03-02 presentation.Rnw
Update

--- 2020-03-02 presentation.Rnw
@@
 \item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmmen
+\linebreak
 \item Hypothese: Die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds besitzt einen positiven Effekt auf die Alltagskompetenzen und das Selbstwertgefühl der Kinder und Jugendlichen
@@
 \begin{frame}[fragile]
-\frametitle{Idee}
+\frametitle{Hintergrund}
+\begin{itemize}
+\item Alle geförderten Einrichtungen erhalten finanzielle Mittel für die Bereitstellung des CHILDREN Mittagstischs
+\item Aber: Nicht jede soziale Einrichtung nimmt am CHILDREN Entdeckerfonds teil, um den Kindern und Jugendlichen Ausflüge und Aktivitäten anzubieten
+\linebreak
+\item [$\Rightarrow$] Der Unterschied zwischen den Einrichtungen hinsichtlich der Teilnahme am CHILDREN Entdeckerfonds wird dazu verwendet, um die Wirkung des Programms zu messen
+\end{itemize}
 \end{frame}
@@
 \begin{frame}[fragile]
-\frametitle{Definition der Treatmentgruppe}
+\frametitle{Einteilung in Treatment- und Kontrollgruppe}
+\begin{itemize}
+\item Treatmentgruppe: Alle Einrichtungen, die sowohl am CHILDREN Mittagstisch als auch am CHILDREN Entdeckerfonds teilnehmen
+\item Kontrollgruppe: Alle Einrichtungen, die nicht am CHILDREN Entdeckerfonds teilnehmen, sondern nur durch den CHILDREN Mittagtisch gefördert werden
+\item Um die Einrichtungen in Treatment- und Kontrollgruppe einzuteilen, wurde analysiert, ob bei den Survey-Fragen zum Entdeckerfonds in einem bestimmten Jahr Angaben gemacht wurden
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Treatment-Variable}
+\begin{itemize}
+\item Um die Einrichtungen in Treatment- und Kontrollgruppe einzuteilen, wird eine Dummy-Variable konstruiert
+\item $TreatEF_{it}$ = 1, wenn Einrichtung $i$ im Jahr $t$ am Entdeckerfonds teilgenommen hat und sich somit in der Treatmentgruppe befindet
+\item $TreatEF_{it}$ = 0, wenn Einrichtung $i$ im Jahr $t$ nicht am Entdeckerfonds teilgenommen hat und sich somit in der Kontrollgruppe befindet
+\item Die Kontrollgruppe ist wesentlich kleiner als die Treatmentgruppe
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante 1}
+\begin{itemize}
+\item "Einmal Treatment, immer Treatment"
+\item Sobald eine Einrichtung am Entdeckerfonds teilgenommen hat, gilt $TreatEF_{it}$ = 1 für das Jahr der ersten Förderung durch den Entdeckerfonds und alle darauffolgenden Jahre
+\item [$\Rightarrow$] Kein Wechsel von der Treatmentgruppe in die Kontrollgruppe möglich
+\item Solange eine Einrichtung keine Förderung vom CHILDREN Entdeckerfonds erhält, befindet sich diese in der Kontrollgruppe
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante 2}
+\begin{itemize}
+\item Zeit-flexibler Treatment-Dummy
+\item Eine Einrichtung befindet sich im Jahr $t$ nur dann in der Treatmentgruppe, wenn diese tatsächlich Fördergelder vom CHILDREN Entdeckerfonds erhalten hat
+\item [$\Rightarrow$] Wechsel von der Treatmentgruppe in die Kontrollgruppe möglich
+\end{itemize}
 \end{frame}
@@
 \frametitle{Zielvariable}
+\begin{itemize}
+\item Problem: Keine Variablen zum Entdeckerfonds für Einrichtungen, die nicht am Entdeckerfonds teilgenommen haben (= Kontrollgruppe) 
+\item Verwendete Zielvariablen vom Mittagtisch: Alltagskompetenzen und Selbstwertgefühl
+\item [$\Rightarrow$] Anwendbar auf den CHILDREN Mittagstisch und den CHILDREN Entdeckerfonds 
+\item [$\Rightarrow$] Über den gesamten Beobachtungszeitraum verfügbar
+\item [$\Rightarrow$] Die Alltagskompetenzen und das Selbstwertgefühl der Kinder und Jugendlichen könnten dadurch beeinflusst werden, dass eine Einrichtung am Entdeckerfonds teilnimmt
+\end{itemize}
 \end{frame}
@@
 \frametitle{DID - Schätzung}
+\begin{itemize}
+\item Empirische Methode: Differences-in-Differences (DID)
+\item Der DID-Schätzer misst den Effekt des Entdeckerfonds, indem die Veränderung der abhängigen Variable über die Zeit in der Treatmentgruppe mit der Veränderung in der Kontrollgruppe verglichen wird
+\linebreak
+\item Regressionsgleichung:
+\end{itemize}
+
+\begin{equation}
+\label{DID equation}
+  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
+\end{equation}
+
+\begin{itemize}
+\item $\gamma_{i}$ = Einrichtung Fixed Effects, $\delta_{t}$ = Year Fixed Effects
+\item Der Regressionskoeffizient $\beta$ entspricht dem DID-Schätzer
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Annahmen und Probleme}
+\begin{itemize}
+\item Zentrale Annahme des DID-Ansatzes:
+\item Commond Trend Assumption: Ohne den Entdeckerfonds würden sich die Zielvariablen in der Treatment- und Kontrollgruppe mit dem gleichen Trend entwickeln
+\linebreak
+\item Potentielle Probleme:
+\item Verletzung der Common Trend Assumption
+\item Selection bias / Endogenität: Nicht zufällig, welche Einrichtungen am Entdeckerfonds teilnehmen
+\item [$\Rightarrow$] Implementierung von Kontrollvariablen, die sich auf die Eigenschaften der geförderten Einrichtungen beziehen
+\end{itemize}
 \end{frame}
@@
 \begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+\begin{itemize}
+\item Das Vorzeichen des Effekts hängt von der Definition der Treatment-Variable ab
+\item Hauptresultat: Die Teilnahme einer Einrichtung am Entdeckerfonds besitzt keinen statistisch signifikanten Effekt auf die Alltagskompetenzen der Kinder und Jugendlichen
+\item Aber: Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist sehr gering
+\item Wenn der Stichprobenumfang steigt, dann könnte der Effekt des Entdeckerfonds gegebenenfalls positiv und statistisch signifikant werden
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
 \frametitle{Selbstwertgefühl}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
+\begin{itemize}
+\item Hauptresultat: Der Effekt des Entdeckerfonds auf das Selbstwertgefühl der Kinder und Jugendlichen ist negativ und teilweise statistisch signifikant
+\linebreak
+\item Mögliche Gründe:
+\item Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist gering
+\item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
+\item Die Skalierung der Zielvariable führt zu geringerer Variation
+\item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
+\end{itemize}
 \end{frame}

### 2020-03-02 presentation.tex
Update

--- 2020-03-01 presentation.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar  1 23:08:51 2020
+% Mon Mar  2 13:12:28 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Sun Mar  1 23:08:56 2020
+% Mon Mar  2 13:12:33 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
some translations from English to German

@@
 
+\section{Explorative Faktoranalyse}
+
+\begin{frame}[fragile]
+\frametitle{Situation}
+
+\begin{itemize}
+ \item<1-> Viele Zielvariablen 
+ \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
+ \linebreak
+ \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
+\end{itemize}
+
+\end{frame}
+
 % \begin{frame}[fragile]
@@
 texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.5, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\\\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\\\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
+{\\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\\\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\\\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\\\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\\\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\\\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\\\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\\\ Alle Standardfehler sind robust.
+%stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
 

### 2020-03-02 presentation.tex
some translations from English to German

@@
 \begin{frame}[fragile]
-\frametitle{Einleitung}
-
-\begin{itemize}
- \item<1-> Text visible on slide 1
- \item<2-> Text visible on slide 2
- \item<3> Text visible on slide 3
- \item<4-> Text visible on slide 4
+\frametitle{CHILDREN for a better World e.V.}
+
+\begin{itemize}
+ \item<1-> Spendenfinanzierte Kinderhilfsorganisation
+ \item<2-> Finanziert Einrichtungen deutschlandweit
+ \linebreak
+ \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
 \end{itemize}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 13:12:28 2020
+% Mon Mar 02 15:10:15 2020
 \begin{table}[ht]
@@
 \end{knitrout}
+\end{frame}
+
+\section{Explorative Faktoranalyse}
+
+\begin{frame}[fragile]
+\frametitle{Situation}
+
+\begin{itemize}
+ \item<1-> Viele Zielvariablen 
+ \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
+ \linebreak
+ \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
+\end{itemize}
+
 \end{frame}
@@
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
+$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 13:12:33 2020
+% Mon Mar 02 15:10:26 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
Update

--- 2020-03-02 presentation.Rnw
@@
 \frametitle{Graphische Darstellung: Alltagskompetenzen}
+<<DIDDtdsplot, echo=FALSE, message=FALSE>>=
+DIDDtdsplot <- readRDS("./ANALYSIS/GRAPHS/plot_dtds.Rds")
+print(DIDDtdsplot, label = "DIDDtdslot")
+@
 \end{frame}
@@
 \frametitle{Graphische Darstellung: Selbstwertgefühl}
+<<DIDSelfworthplot, echo=FALSE, message=FALSE>>=
+DIDSelfworthplot <- readRDS("./ANALYSIS/GRAPHS/plot_selfworth.Rds")
+print(DIDSelfworthplot, label = "DIDSelfworthplot")
+@
 \end{frame}
@@
 \frametitle{Alltagskompetenzen}
+\begin{table}
+\begin{center}
+\scalebox{0.9}{
+\begin{tabular}{l c c c c }
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Abhängige Variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Alltagskompetenzen} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF     & $-0.143$  & $-0.166$     & $0.247$   & $0.255$      \\
+            & $(0.402)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
+subsidy     &           & $0.019$      &           & $0.016$      \\
+            &           & $(0.014)$    &           & $(0.014)$    \\
+totalCost   &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+            &           & $(0.000)$    &           & $(0.000)$    \\
+weeklyCooks &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+            &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
+\end{tabular}
+}
+\end{center}
+\caption{DID-Schätzung: Ergebnisse für Alltagskompetenzen}
+\end{table}
 \end{frame}
@@
 \frametitle{Selbstwertgefühl}
+\begin{table}
+\begin{center}
+\scalebox{0.9}{
+\begin{tabular}{l c c c c }
+\\[-1.8ex]\hline
+& \multicolumn{4}{c}{\textit{Abhängige Variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selbstwertgefühl} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF     & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+            & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
+subsidy     &           & $0.011$   &           & $0.014$      \\
+            &           & $(0.018)$ &           & $(0.017)$    \\
+totalCost   &           & $0.000$   &           & $0.000$      \\
+            &           & $(0.001)$ &           & $(0.001)$    \\
+weeklyCooks &           & $0.036$   &           & $0.037$      \\
+            &           & $(0.069)$ &           & $(0.069)$    \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
+\end{tabular}
+}
+\caption{DID-Schätzung: Ergebnisse für Selbstwertgefühl}
+\end{center}
+\end{table}
 \end{frame}

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 13:12:28 2020
+% Mon Mar  2 15:29:54 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 13:12:33 2020
+% Mon Mar  2 15:29:58 2020
 \begin{table}[ht]
@@
 \frametitle{Graphische Darstellung: Alltagskompetenzen}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-DIDDtdsplot-1}
+
+}
+
+\end{knitrout}
 \end{frame}
@@
 \frametitle{Graphische Darstellung: Selbstwertgefühl}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-DIDSelfworthplot-1}
+
+}
+
+\end{knitrout}
 \end{frame}

### 2020-03-02 presentation.Rnw
lg

--- 2020-03-02 presentation.Rnw
@@
 
-% \begin{figure}
-%   \caption{Yearly dynamics of total grants in Meals and Trips program}
-%   \label{totalGrantsDyn}
-%
-% <<GrantTrend, echo=FALSE, message=FALSE>>=
-% totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-% print(totalGrantsDyn, scalebox = '0.25')
-% @
-%
-% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+ \begin{figure}
+   \caption{Yearly dynamics of total grants in Meals and Trips program}
+   \label{totalGrantsDyn}
+
+ <<GrantTrend, echo=FALSE, message=FALSE>>=
+ totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+ print(totalGrantsDyn, scalebox = '0.25')
+ @
+
+ \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-% \end{figure}
+ \end{figure}
 
-%
-
-% \end{frame}
+\end{frame}
 % 
@@
 texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE, use.packages=FALSE)
 @
@@
 texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE, use.packages=FALSE)
 @
@@
 texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
+{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE, use.packages=FALSE)
 @
@@
 texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
+{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE, use.packages=FALSE)
 @
@@
 \frametitle{Graphische Darstellung: Alltagskompetenzen}
-<<DIDDtdsplot, echo=FALSE, message=FALSE>>=
-DIDDtdsplot <- readRDS("./ANALYSIS/GRAPHS/plot_dtds.Rds")
-print(DIDDtdsplot, label = "DIDDtdslot")
-@
 \end{frame}
@@
 \frametitle{Graphische Darstellung: Selbstwertgefühl}
-<<DIDSelfworthplot, echo=FALSE, message=FALSE>>=
-DIDSelfworthplot <- readRDS("./ANALYSIS/GRAPHS/plot_selfworth.Rds")
-print(DIDSelfworthplot, label = "DIDSelfworthplot")
-@
 \end{frame}
@@
 \frametitle{Alltagskompetenzen}
-\begin{table}
-\begin{center}
-\scalebox{0.9}{
-\begin{tabular}{l c c c c }
-\\[-1.8ex]\hline
-& \multicolumn{4}{c}{\textit{Abhängige Variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Alltagskompetenzen} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF     & $-0.143$  & $-0.166$     & $0.247$   & $0.255$      \\
-            & $(0.402)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
-subsidy     &           & $0.019$      &           & $0.016$      \\
-            &           & $(0.014)$    &           & $(0.014)$    \\
-totalCost   &           & $0.001^{**}$ &           & $0.001^{*}$  \\
-            &           & $(0.000)$    &           & $(0.000)$    \\
-weeklyCooks &           & $0.166^{**}$ &           & $0.162^{**}$ \\
-            &           & $(0.072)$    &           & $(0.073)$    \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
-\end{tabular}
-}
-\end{center}
-\caption{DID-Schätzung: Ergebnisse für Alltagskompetenzen}
-\end{table}
 \end{frame}
@@
 \frametitle{Selbstwertgefühl}
-\begin{table}
-\begin{center}
-\scalebox{0.9}{
-\begin{tabular}{l c c c c }
-\\[-1.8ex]\hline
-& \multicolumn{4}{c}{\textit{Abhängige Variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Selbstwertgefühl} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF     & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
-            & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
-subsidy     &           & $0.011$   &           & $0.014$      \\
-            &           & $(0.018)$ &           & $(0.017)$    \\
-totalCost   &           & $0.000$   &           & $0.000$      \\
-            &           & $(0.001)$ &           & $(0.001)$    \\
-weeklyCooks &           & $0.036$   &           & $0.037$      \\
-            &           & $(0.069)$ &           & $(0.069)$    \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
-\end{tabular}
-}
-\caption{DID-Schätzung: Ergebnisse für Selbstwertgefühl}
-\end{center}
-\end{table}
 \end{frame}

### 2020-03-02 presentation.tex
lg

--- 2020-03-02 presentation.tex
@@
 \frametitle{Zusammenfassende Statistiken}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 15:10:15 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 15:39:22 2020
 \begin{table}[ht]
@@
 
-\section{Explorative Faktoranalyse}
-
-\begin{frame}[fragile]
-\frametitle{Situation}
-
-\begin{itemize}
- \item<1-> Viele Zielvariablen 
- \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
- \linebreak
- \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
- \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
-\end{itemize}
-
-\end{frame}
-
 % \begin{frame}[fragile]
@@
 
-% \begin{figure}
-%   \caption{Yearly dynamics of total grants in Meals and Trips program}
-%   \label{totalGrantsDyn}
-%
-% <<GrantTrend, echo=FALSE, message=FALSE>>=
-% totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-% print(totalGrantsDyn, scalebox = '0.25')
-% @
-%
-% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+ \begin{figure}
+   \caption{Yearly dynamics of total grants in Meals and Trips program}
+   \label{totalGrantsDyn}
+
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-GrantTrend-1}
+
+}
+
+\end{knitrout}
+
+ \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-% \end{figure}
-
-%
-
-% \end{frame}
+ \end{figure}
+
+\end{frame}
 % 
@@
 \midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+R$^2$           & $0.43$          & $0.73$         & $0.13$          & $0.21$          & $0.45$           \\
+Adj. R$^2$      & $0.43$          & $0.73$         & $0.12$          & $0.20$          & $0.45$           \\
+Num. obs.       & $329$           & $329$          & $250$           & $250$           & $440$            \\
+RMSE            & $39992.79$      & $27390.90$     & $3629.72$       & $3463.66$       & $39601.41$       \\
 \bottomrule
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
-$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Ansatz der kleinsten Quadrate \\ Modell (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
 \end{tabular}
@@
 \frametitle{Wertschätzung für gesundes Essen}
+
+\usepackage{graphicx}
 
@@
  \frametitle{Partition Mittagstisch}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 15:10:26 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 15:39:32 2020
 \begin{table}[ht]
@@
 \frametitle{Partition Entdeckerfonds}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 15:10:26 2020
+% latex table generated in R 3.5.1 by xtable 1.8-4 package
+% Mon Mar 02 15:39:32 2020
 \begin{table}[ht]

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
 \end{itemize}
-
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Beispiel: Datensatz}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+
+{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/dataExample.Rds' nicht öffnen.
+Grund evtl.
+'No such file or directory'}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
+
+{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Datensatz, label = "{}Datensatz"{}): Objekt 'Datensatz' nicht gefunden}}\end{kframe}
+\end{knitrout}
 \end{frame}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 15:10:15 2020
+% Mon Mar  2 15:48:14 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 15:10:26 2020
+% Mon Mar  2 15:48:19 2020
 \begin{table}[ht]

### 2020-03-02 paper.tex
added reference

@@
+% in Terminal enter
+% Rscript -e "library(knitr); knit('paper.Rnw')"
+% pdflatex paper
+% biber paper
+% pdflatex paper
+% pdflatex paper
+
 % IMPORTANT
@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% bibstyle=apa, citestyle=authoryear
+\usepackage[backend=biber, style=apa]{biblatex}
 \usepackage{floatrow}
 \usepackage{booktabs}
+\usepackage[ngerman, english]{babel}
 % \usepackage{bookmark}
@@
 % \begin{titlepage}
-\maketitle
+% \maketitle
 % \end{titlepage}
@@
 
-Previous research shows, that the childhood and youth is central in development of character traits and future opportunities.
+Previous research shows that childhood and youth are central in development of character traits and future opportunities.
 Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
+Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation \parencite{Deckers.27.04.2015}, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
 Children that grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
@@
 
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Mon Mar 02 10:59:09 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Mar 02 16:10:45 2020
 \begin{table}[ht]
@@
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c}
+\begin{tabular}{l c c c c c }
 \hline
@@
 \hline
-R$^2$                          & $0.00$   & $0.01$   & $0.00$   & $0.01$   & $0.30$       \\
-Adj. R$^2$                     & $0.00$   & $0.01$   & $0.00$   & $0.01$   & $0.28$       \\
-Num. obs.                      & $428$    & $184$    & $430$    & $187$    & $161$        \\
-RMSE                           & $1.00$   & $1.00$   & $1.00$   & $1.00$   & $0.79$       \\
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 
-\usepackage{graphicx}
-
 \begin{table}
-\caption{Association Between Everyday Expertise and Subsidy per Beneficiary}
+\caption{Association between everyday expertise and subsidy per beneficiary}
 \begin{center}
 \scalebox{0.8}{
-\begin{tabular}{l c c c c c c}
+\begin{tabular}{l c c c c c c }
 \hline
@@
 \hline
-R$^2$                          & $0.01$   & $0.01$   & $0.01$   & $0.01$   & $0.37$       & $0.37$       \\
-Adj. R$^2$                     & $0.01$   & $0.01$   & $0.01$   & $0.01$   & $0.36$       & $0.35$       \\
-Num. obs.                      & $426$    & $177$    & $429$    & $181$    & $161$        & $169$        \\
-RMSE                           & $1.00$   & $0.98$   & $1.00$   & $0.99$   & $0.78$       & $0.80$       \\
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
 \hline
 \multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.12$       & $0.29$      & $0.07$       & $0.16$       & $0.19$       \\
-Adj. R$^2$          & $0.11$       & $0.29$      & $0.07$       & $0.16$       & $0.17$       \\
-Num. obs.           & $121$        & $120$       & $177$        & $177$        & $161$        \\
-RMSE                & $0.91$       & $7.83$      & $0.94$       & $7.95$       & $0.87$       \\
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.01$   & $0.00$   & $0.02$     & $0.01$   & $0.31$       \\
-Adj. R$^2$          & $0.01$   & $-0.00$  & $0.01$     & $0.01$   & $0.29$       \\
-Num. obs.           & $214$    & $212$    & $275$      & $275$    & $161$        \\
-RMSE                & $0.98$   & $8.49$   & $0.96$     & $9.45$   & $0.83$       \\
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 \hline
-R$^2$               & $0.06$       & $0.00$   & $0.06$       & $0.00$     & $0.37$       \\
-Adj. R$^2$          & $0.06$       & $-0.00$  & $0.06$       & $-0.00$    & $0.35$       \\
-Num. obs.           & $213$        & $211$    & $274$        & $274$      & $161$        \\
-RMSE                & $1.02$       & $8.61$   & $1.01$       & $9.00$     & $0.82$       \\
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
 \hline
 \multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 
-Strinkinlgy, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
+Strikingly, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
 In column (1)-(3), the average treatment effect is insignificant.
@@
 \hline
-R$^2$                     & $0.51$        & $0.73$       & $0.09$       & $0.22$     \\
-Adj. R$^2$                & $0.39$        & $0.66$       & $0.07$       & $0.20$     \\
-Num. obs.                 & $88$          & $88$         & $175$        & $175$      \\
-RMSE                      & $0.73$        & $5.62$       & $0.94$       & $7.77$     \\
+R$^2$                     & 0.51          & 0.73         & 0.09         & 0.22       \\
+Adj. R$^2$                & 0.39          & 0.66         & 0.07         & 0.20       \\
+Num. obs.                 & 88            & 88           & 175          & 175        \\
+RMSE                      & 0.73          & 5.62         & 0.94         & 7.77       \\
 \hline
 \multicolumn{5}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$; $^{**}p<0.01$; $^{*}p<0.05$.}}}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ regionalProducts: wether the organization offers meals with local ingredients or not \\ yearsSupportSince: the number of years an organization is already part of the Meals program \\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ state: german 'Bundeland' \\ Model (1): original data set, simple linear model with controls, estimated with OLS \\ Model (2): original data set, simple linear model with controls, estimated with WLS \\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
 \end{tabular}
@@
 
-\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: namespace 'VGAM' is not available and has been replaced\\\#\# by .GlobalEnv when processing object ''}}\end{kframe}
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo., Mär 02, 2020 - 10:59:18
+% Date and time: Mo, Mrz 02, 2020 - 16:10:54
 % Requires LaTeX packages: dcolumn 
@@
 
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Mon Mar 02 10:59:18 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Mar 02 16:10:55 2020
 \begin{table}[ht]
@@
 \end{table}
-% latex table generated in R 3.6.1 by xtable 1.8-4 package
-% Mon Mar 02 10:59:18 2020
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Mar 02 16:10:55 2020
 \begin{table}[ht]
@@
 
+\subsection{A5: Placebo Tests}
+
+\begin{figure}
+  \caption{Trend of weekly cooks}
+  \label{figureWeeklyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Weekly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend of monthly cooks}
+  \label{figureMonthlyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Monthly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \end{document}

### 2020-03-02 presentation.tex
added reference

@@
 \end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Beispiel: Datensatz}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/dataExample.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Datensatz, label = "{}Datensatz"{}): Objekt 'Datensatz' nicht gefunden}}\end{kframe}
-\end{knitrout}
+
 \end{frame}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:14 2020
+% Mon Mar 02 15:12:42 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:19 2020
+% Mon Mar 02 15:12:52 2020
 \begin{table}[ht]
@@
 \frametitle{Graphische Darstellung: Alltagskompetenzen}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-DIDDtdsplot-1}
-
-}
-
-\end{knitrout}
 \end{frame}
@@
 \frametitle{Graphische Darstellung: Selbstwertgefühl}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-DIDSelfworthplot-1}
-
-}
-
-\end{knitrout}
 \end{frame}

### 2020-03-02 presentation.Rnw
Update

@@
 \frametitle{CHILDREN for a better World e.V.}
-
 \begin{itemize}
@@
 \end{itemize}
-
 \end{frame}
@@
 \frametitle{Datenerhebung von CHILDREN}
-
 \begin{itemize}
@@
  \item<5-> Abhängige Variablen (z.B. Selbstwertgefühl, seltener krank)
-
 \end{itemize}
@@
 \frametitle{Datenaufbereitung}
-
 \begin{itemize}
@@
  \item<4-> Abstimmung des Teams über “Git”
+\end{itemize}
+\end{frame}
 
-\end{itemize}
+\begin{frame}[fragile]
+\frametitle{Beispiel: Datensatz}
+<<Datensatz, echo=FALSE, message=FALSE>>=
 
+Datensatz = readRDS("./ANALYSIS/GRAPHS/PAPER/dataExample.Rds")
+
+colnames(Datensatz) <- c("ID", "Jahr", "Anzahl der Kinder MT", "Selbstwertgefühl", "Ausflüge")
+
+print(xtable(Datensatz, include.rownames = FALSE,
+           caption = "Beispielhafter Datensatz",
+           align = "lccccc",
+          label = "Datensatz"
+          ), scalebox = '0.7')
+@
 \end{frame}
@@
 
-% \begin{frame}[fragile]
-% \frametitle{Dynamics}
-
+\begin{frame}[fragile]
+\frametitle{Dynamics}
  \begin{figure}
@@
    \label{totalGrantsDyn}
-
  <<GrantTrend, echo=FALSE, message=FALSE>>=
@@
  @
-
- \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 \end{figure}
+\end{frame}
 
-\end{frame}
-% 
-% 
 \section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
-% 
 \subsection{Empirischer Ansatz}
@@
 
+\subsection{Idee}
+
 \begin{frame}[fragile]
@@
 \begin{itemize}
-\item Welchen Effekt besitzt die Teilnahme einer sozialen Einrichtung am CHILDREN Entdeckerfonds auf die teilnehmenden Kinder und Jugendlichen?
+\item Welchen Effekt besitzt die Förderung einer sozialen Einrichtung durch den CHILDREN Entdeckerfonds auf die teilnehmenden Kinder und Jugendlichen?
 \item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmmen
@@
 \end{frame}
-
-\subsection{Idee}
 

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
  \item<4-> Abstimmung des Teams über “Git”
-
 \end{itemize}
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/dataExample.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Datensatz, label = "{}Datensatz"{}): Objekt 'Datensatz' nicht gefunden}}\end{kframe}
+\begin{verbatim}
+## % latex table generated in R 3.6.2 by xtable 1.8-4 package
+## % Mon Mar  2 16:43:52 2020
+## \begin{table}[ht]
+## \centering
+## \scalebox{0.7}{
+## \begin{tabular}{lccccc}
+##   \hline
+##  & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+##   \hline
+## 1 & 103.00 & 2014.00 & 30.00 & 3.00 & 4.00 \\ 
+##   2 & 103.00 & 2015.00 & 50.00 & 3.00 & 6.00 \\ 
+##   3 & 103.00 & 2016.00 &  & 2.00 & 3.00 \\ 
+##   4 & 112.00 & 2014.00 & 27.00 & 3.00 &  \\ 
+##   5 & 112.00 & 2015.00 & 55.00 & 3.00 &  \\ 
+##   6 & 112.00 & 2016.00 & 35.00 & 3.00 &  \\ 
+##   7 & 112.00 & 2018.00 & 36.00 & 2.00 &  \\ 
+##    \hline
+## \end{tabular}
+## }
+## \caption{Beispielhafter Datensatz} 
+## \label{Datensatz}
+## \end{table}
+\end{verbatim}
+\end{kframe}
 \end{knitrout}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:14 2020
+% Mon Mar  2 16:43:52 2020
 \begin{table}[ht]
@@
 
-% \begin{frame}[fragile]
-% \frametitle{Dynamics}
-
-% \begin{figure}
-%   \caption{Yearly dynamics of total grants in Meals and Trips program}
-%   \label{totalGrantsDyn}
-%
-% <<GrantTrend, echo=FALSE, message=FALSE>>=
-% totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-% print(totalGrantsDyn, scalebox = '0.25')
-% @
-%
-% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+\begin{frame}[fragile]
+\frametitle{Dynamics}
+ \begin{figure}
+   \caption{Yearly dynamics of total grants in Meals and Trips program}
+   \label{totalGrantsDyn}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-GrantTrend-1}
+
+}
+
+\end{knitrout}
+% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-% \end{figure}
-
-%
-
-% \end{frame}
-% 
-% 
+\end{figure}
+\end{frame}
+
 \section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
-% 
 \subsection{Empirischer Ansatz}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:19 2020
+% Mon Mar  2 16:43:58 2020
 \begin{table}[ht]

### 2020-03-02 paper.Rnw

@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+% bibstyle=apa, citestyle=authoryear
+\usepackage[backend=biber, style=apa]{biblatex}
 \usepackage{floatrow}
 \usepackage{booktabs}
+\usepackage[ngerman, english]{babel}
+\usepackage{csquotes}
 % \usepackage{bookmark}
@@
 
-texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association Between Everyday Expertise and Subsidy per Beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
+texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
 
@@
 stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet", align = TRUE, label = "appreciateOdds")
+
 @
@@
 stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth", align = TRUE, label = "selfworthOdds")
+
 @
@@
 stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise", align = TRUE, label = "dayToDayOdds")
+
 @
@@
 
+\subsection{A5: Placebo Tests}
+
+\begin{figure}
+  \caption{Trend of weekly cooks}
+  \label{figureWeeklyCooks}
+
+<<Weekly cooks, echo=FALSE>>=
+figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
+print(figureWeeklyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend of monthly cooks}
+  \label{figureMonthlyCooks}
+
+<<Monthly cooks, echo=FALSE>>=
+figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
+print(figureMonthlyCooks)
+@
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 \end{document}

### 2020-03-02 paper.Rnw
fghjk

@@
 
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill", align = TRUE, label = "lessIllOdds")
+stargazer(lessIllOdds@coef3, title= "Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill", align = TRUE, label = "lessIllOdds")
 
@@
 
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge", align = TRUE, label = "dietaryOdds")
+stargazer(dietaryOdds@coef3, title= "Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge", align = TRUE, label = "dietaryOdds")
 @
@@
 
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet", align = TRUE, label = "appreciateOdds")
+stargazer(appreciateOdds@coef3, title= "Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet", align = TRUE, label = "appreciateOdds")
 
@@
 
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth", align = TRUE, label = "selfworthOdds")
+stargazer(selfworthOdds@coef3, title= "Propodds Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth", align = TRUE, label = "selfworthOdds")
 
@@
 
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise", align = TRUE, label = "dayToDayOdds")
+stargazer(dayToDayOdds@coef3, title= "Propodds Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise", align = TRUE, label = "dayToDayOdds")
 

### 2020-03-02 paper.tex
fghjk

@@
 \usepackage[ngerman, english]{babel}
+\usepackage{csquotes}
 % \usepackage{bookmark}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 16:10:45 2020
+% Mon Mar 02 17:51:55 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 17:52:02
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill} 
+  \caption{Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill} 
   \label{lessIllOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 17:52:02
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge} 
+  \caption{Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge} 
   \label{dietaryOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 17:52:02
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet} 
+  \caption{Propodds Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet} 
   \label{appreciateOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 17:52:02
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth} 
+  \caption{Propodds Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth} 
   \label{selfworthOdds} 
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 17:52:02
 % Requires LaTeX packages: dcolumn 
 \begin{table}[!htbp] \centering 
-  \caption{Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise} 
+  \caption{Propodds Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise} 
   \label{dayToDayOdds} 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 16:10:55 2020
+% Mon Mar 02 17:52:02 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
fghjk

@@
 
-\begin{frame}[fragile]
-\frametitle{Dynamics}
- \begin{figure}
-   \caption{Yearly dynamics of total grants in Meals and Trips program}
-   \label{totalGrantsDyn}
- <<GrantTrend, echo=FALSE, message=FALSE>>=
- totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
- print(totalGrantsDyn, scalebox = '0.25')
- @
-% \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+% \begin{frame}[fragile]
+% \frametitle{Dynamics}
+%  \begin{figure}
+%    \caption{Yearly dynamics of total grants in Meals and Trips program}
+%    \label{totalGrantsDyn}
+%  <<GrantTrend, echo=FALSE, message=FALSE>>=
+%  totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+%  print(totalGrantsDyn, scalebox = '0.25')
+%  @
+% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
 We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
@@
 We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-\end{figure}
-\end{frame}
+% \end{figure}
+% \end{frame}
 
@@
 \item Schätzung der Modelle mit OLS (Ordinary least squares)
-\item An geeigneter Stelle: Vergleich der Ergebnisse mit WLS (Weighted least squares)
+\item An geeigneter Stelle Vergleich der Ergebnisse mit WLS (Weighted least squares) \item[$\Rightarrow$]Gewichtung der Regressionen mit Variablen die sich stark in ihrer Größe zwischen den verschiednen Organisationen unterscheiden (e.g.
+Anzahl an Essen die ausgegeben werden, Ausflüge die unternommen werden)
 \end{itemize}
@@
 
+\begin{frame}
+\frametitle{Empirische Fragestellungen (1): Ergebnisse der Fördersumme}
+
+\begin{itemize}
+\item Effekt auf Anzahl an Essen & Ausflüge
+\begin{itemize}
+\item Mittagstisch: Circa 3 Euro mehr resultieren in einer Mahlzeit mehr
+\item Entdeckerfonds: kein klarer Zusammenhang 
+\end{itemze}
+\item Effekt auf das Selbstwertgefühl & die Alltagskompetenzen 
+\begin{itemize}
+\item Nulleffekte bei beiden Variablen 
+\end{itemize}
+\end{itemize}
+
+\end{frame}
+
 \subsection{Gesundheit}
@@
 \frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
-<<lessIllDGEplot, echo=FALSE, message=FALSE>>=
+<<lessIllDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
 lessillDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/lessill.Rds")
@@
 \frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
-<<dietaryDGEplot, echo=FALSE, message=FALSE>>=
+<<dietaryDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
 dietaryDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/dietary.Rds")
@@
 \frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
-<<appreciateDGEplot, echo=FALSE, message=FALSE>>=
+<<appreciateDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
 appreciateDGE <- readRDS("./ANALYSIS/GRAPHS/PAPER/appreciate.Rds")
@@
 \end{frame}
+
+\begin{frame}
+\frametitle{Empirische Fragestellungen (2): Ergebnisse des DGE-Kriteriums}
+
+\begin{itemize}
+\item
 

### 2020-03-02 presentation.tex

--- 2020-03-02 presentation.tex
@@
 \definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning in gzfile(file, "{}rb"{}): kann komprimierte Datei './ANALYSIS/GRAPHS/PAPER/dataExample.Rds' nicht öffnen.
-Grund evtl.
-'No such file or directory'}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in gzfile(file, "{}rb"{}): kann Verbindung nicht öffnen}}
-
-{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in print(Datensatz, label = "{}Datensatz"{}): Objekt 'Datensatz' nicht gefunden}}\end{kframe}
+\begin{verbatim}
+## % latex table generated in R 3.6.2 by xtable 1.8-4 package
+## % Mon Mar 02 17:19:43 2020
+## \begin{table}[ht]
+## \centering
+## \scalebox{0.7}{
+## \begin{tabular}{lccccc}
+##   \hline
+##  & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+##   \hline
+## 1 & 103.00 & 2014.00 & 30.00 & 3.00 & 4.00 \\ 
+##   2 & 103.00 & 2015.00 & 50.00 & 3.00 & 6.00 \\ 
+##   3 & 103.00 & 2016.00 &  & 2.00 & 3.00 \\ 
+##   4 & 112.00 & 2014.00 & 27.00 & 3.00 &  \\ 
+##   5 & 112.00 & 2015.00 & 55.00 & 3.00 &  \\ 
+##   6 & 112.00 & 2016.00 & 35.00 & 3.00 &  \\ 
+##   7 & 112.00 & 2018.00 & 36.00 & 2.00 &  \\ 
+##    \hline
+## \end{tabular}
+## }
+## \caption{Beispielhafter Datensatz} 
+## \label{Datensatz}
+## \end{table}
+\end{verbatim}
+\end{kframe}
 \end{knitrout}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:14 2020
+% Mon Mar 02 17:19:43 2020
 \begin{table}[ht]
@@
 % \frametitle{Dynamics}
-
 %  \begin{figure}
@@
 %    \label{totalGrantsDyn}
-%
 %  <<GrantTrend, echo=FALSE, message=FALSE>>=
@@
 %  @
-%
 % % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
@@
 % \end{figure}
-
-%
-
 % \end{frame}
-% 
-% 
+
 \section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
 
-% 
 \subsection{Empirischer Ansatz}
@@
 \begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-
-{\ttfamily\noindent\color{warningcolor}{\#\# Warning: Removed 244 rows containing missing values (position\_stack).}}\end{kframe}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 15:48:19 2020
+% Mon Mar 02 17:19:51 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
Update

@@
 \hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
 \multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
@@
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable führt zu geringerer Variation
+\item Die Skalierung der Zielvariable "Selbstwertgefühl" führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden

### 2020-03-02 presentation.tex
Update

@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 17:19:43 2020
+## % Mon Mar  2 19:45:07 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 17:19:43 2020
+% Mon Mar  2 19:45:07 2020
 \begin{table}[ht]
@@
 
+\begin{frame}
+\frametitle{Empirische Fragestellungen (2): Ergebnisse des DGE-Kriteriums}
+
+\begin{itemize}
+\item
+
 \section{Partition}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 17:19:51 2020
+% Mon Mar  2 19:45:12 2020
 \begin{table}[ht]

### 2020-03-02 paper.Rnw
paper without partition

--- 2020-03-02 paper.Rnw
@@
 \usepackage[backend=biber, style=apa]{biblatex}
+\DeclareLanguageMapping{english}{english-apa}
 \usepackage{floatrow}
@@
 
-<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-
-# first, read in all Rds objects that you need
-
-partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
-partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
-
-colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
-colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
-
-xtable(partition_meals,
-                               # digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of Outcomes, Meals", 
-          label = 'partitionmeals',
-          align = "lccc"
-          )
-#print(partition_meals, include.rownames = FALSE)
-
-xtable(partition_trips,
-                               #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of Outcomes, Trips",
-          label = 'partitiontrips',
-          align = "lccc"
-          )
-# print(partition_meals, partition_trips, include.rownames = FALSE)
-@
-
 \subsection{A4: DID Regression Results}
@@
 
+<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+# first, read in all Rds objects that you need
+
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
+
+ # colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
+ # colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
+
+xtable(partition_meals,
+                                # digits = c(0, 0, 1, 1, 0, 0),
+           caption = "Partition of Outcomes, Meals", 
+           label = 'partitionmeals',
+           align = "lccc"
+           )
+ #print(partition_meals, include.rownames = FALSE)
+
+ # xtable(partition_trips,
+ #                                #digits = c(0, 0, 1, 1, 0, 0),
+ #           caption = "Partition of Outcomes, Trips",
+ #           label = 'partitiontrips',
+ #           align = "lccc"
+ #           )
+ # print(partition_meals, partition_trips, include.rownames = FALSE)
+ @
+
 \end{document}

### 2020-03-02 paper.tex
paper without partition

--- 2020-03-02 paper.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 16:10:45 2020
+% Mon Mar 02 18:00:31 2020
 \begin{table}[ht]
@@
 % Table created by stargazer v.5.2.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
-% Date and time: Mo, Mrz 02, 2020 - 16:10:54
+% Date and time: Mo, Mrz 02, 2020 - 18:00:42
 % Requires LaTeX packages: dcolumn 
@@
 
+\subsection{A4: DID Regression Results}
+
+The estimated coefficients of equation \ref{didregression} are represented in Table \ref{table:coefficients3} with everyday expertise as the dependent variable and in Table \ref{table:coefficients4} with selfworth as the dependent variable.
+P-values are in parentheses.
+We observe decreasing p-values when using the second definition of the treatment variable.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
+                       & $(0.975)$ & $(0.681)$    & $(0.409)$ & $(0.410)$    \\
+subsidy                &           & $0.019$      &           & $0.016$      \\
+                       &           & $(0.181)$    &           & $(0.258)$    \\
+totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
+                       &           & $(0.048)$    &           & $(0.060)$    \\
+weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
+                       &           & $(0.022)$    &           & $(0.027)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation 1}
+\label{table:coefficients3}
+\end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in section 6.1.4.
+The outcome variable is standardized.
+Below each coefficient the p-values are reported in parentheses.}
+\end{table}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{l c c c c}
+& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
+\cline{2-5}
+\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
+\hline
+ & (1) & (2) & (3) & (4) \\
+\hline
+treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
+                       & $(0.126)$ & $(0.125)$ & $(0.185)$ & $(0.085)$    \\
+subsidy                &           & $0.011$   &           & $0.014$      \\
+                       &           & $(0.540)$ &           & $(0.422)$    \\
+totalCost              &           & $0.000$   &           & $0.000$      \\
+                       &           & $(0.575)$ &           & $(0.446)$    \\
+weeklyCooks            &           & $0.036$   &           & $0.037$      \\
+                       &           & $(0.609)$ &           & $(0.591)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
+\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
+\end{tabular}
+\caption{DID Estimation 2}
+\label{table:coefficients4}
+\end{center}
+\floatfoot{Notes: The Table reports OLS results.
+Observations are at the organization level.
+Full details of each control variable are provided in section 6.1.4.
+The outcome variable is standardized.
+Below each coefficient the p-values are reported in parentheses.}
+\end{table}
+
+% %\section{Division of tasks}
+% 
+% Data preparation, fundamental dynamics: everybody\\
+% Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
+% DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
+% 
+% 
+% \section{Ehrenwörtliche Erklärung aller Teilnehmer}
+
+\subsection{A5: Placebo Tests}
+
+\begin{figure}
+  \caption{Trend of weekly cooks}
+  \label{figureWeeklyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Weekly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
+\begin{figure}
+  \caption{Trend of monthly cooks}
+  \label{figureMonthlyCooks}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=0.8\textwidth]{figure/Monthly_cooks-1}
+
+}
+
+\end{knitrout}
+
+\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
+The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
+The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
+Additionally, the linear trends of both groups are included as the straight lines.}
+\end{figure}
+
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 16:10:55 2020
+% Mon Mar 02 18:00:44 2020
 \begin{table}[ht]
@@
   \hline
- & Variable, Meals & Mapping, Meals & Information, Meals \\ 
+ & Meals\_variable & Meals\_mappings & Meals\_information \\ 
   \hline
@@
 \end{table}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 16:10:55 2020
-\begin{table}[ht]
-\centering
-\begin{tabular}{lccc}
-  \hline
- & Variable, Trips & Mapping, Trips & Information, Trips \\ 
-  \hline
-1 & tripsSuggestions & tripsSuggestions & 1.00 \\ 
-  2 & tripsDecisions & tripsDecisions & 1.00 \\ 
-  3 & tripsOrganization & tripsOrganization & 1.00 \\ 
-  4 & tripsCostCalculation & tripsCostCalculation & 1.00 \\ 
-  5 & tripsBudget & tripsBudget & 1.00 \\ 
-  6 & tripsMoney & tripsMoney & 1.00 \\ 
-  7 & tripsReview & tripsReview & 1.00 \\ 
-  8 & tripsPublicTransport & tripsPublicTransport & 1.00 \\ 
-  9 & tripsMobility & tripsMobility & 1.00 \\ 
-  10 & tripsAdditionalActivities & tripsAdditionalActivities & 1.00 \\ 
-  11 & tripsSelfworth & tripsSelfworth & 1.00 \\ 
-  12 & tripsFrustrationTolerance & tripsFrustrationTolerance & 1.00 \\ 
-  13 & reduced\_var\_1 & tripsSuccess & 0.68 \\ 
-  14 & reduced\_var\_1 & tripsSelfEfficacy & 0.68 \\ 
-  15 & reduced\_var\_2 & tripsNewPlaces & 0.60 \\ 
-  16 & reduced\_var\_2 & tripsNewCommunities & 0.60 \\ 
-  17 & reduced\_var\_2 & tripsNewIdeas & 0.60 \\ 
-  18 & reduced\_var\_2 & tripsSocialSkills & 0.60 \\ 
-  19 & reduced\_var\_3 & tripsSpecificSkills & 0.46 \\ 
-  20 & reduced\_var\_3 & tripsDayToDaySkills & 0.46 \\ 
-   \hline
-\end{tabular}
-\caption{Partition of Outcomes, Trips} 
-\label{partitiontrips}
-\end{table}
-
-\subsection{A4: DID Regression Results}
-
-The estimated coefficients of equation \ref{didregression} are represented in Table \ref{table:coefficients3} with everyday expertise as the dependent variable and in Table \ref{table:coefficients4} with selfworth as the dependent variable.
-P-values are in parentheses.
-We observe decreasing p-values when using the second definition of the treatment variable.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
-                       & $(0.975)$ & $(0.681)$    & $(0.409)$ & $(0.410)$    \\
-subsidy                &           & $0.019$      &           & $0.016$      \\
-                       &           & $(0.181)$    &           & $(0.258)$    \\
-totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
-                       &           & $(0.048)$    &           & $(0.060)$    \\
-weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
-                       &           & $(0.022)$    &           & $(0.027)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$        & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation 1}
-\label{table:coefficients3}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in section 6.1.4.
-The outcome variable is standardized.
-Below each coefficient the p-values are reported in parentheses.}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
-                       & $(0.126)$ & $(0.125)$ & $(0.185)$ & $(0.085)$    \\
-subsidy                &           & $0.011$   &           & $0.014$      \\
-                       &           & $(0.540)$ &           & $(0.422)$    \\
-totalCost              &           & $0.000$   &           & $0.000$      \\
-                       &           & $(0.575)$ &           & $(0.446)$    \\
-weeklyCooks            &           & $0.036$   &           & $0.037$      \\
-                       &           & $(0.609)$ &           & $(0.591)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$     & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation 2}
-\label{table:coefficients4}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in section 6.1.4.
-The outcome variable is standardized.
-Below each coefficient the p-values are reported in parentheses.}
-\end{table}
-
-% %\section{Division of tasks}
-% 
-% Data preparation, fundamental dynamics: everybody\\
-% Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
-% DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
-% 
-% 
-% \section{Ehrenwörtliche Erklärung aller Teilnehmer}
-
-\subsection{A5: Placebo Tests}
-
-\begin{figure}
-  \caption{Trend of weekly cooks}
-  \label{figureWeeklyCooks}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/Weekly_cooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{Trend of monthly cooks}
-  \label{figureMonthlyCooks}
-
-\begin{knitrout}
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=0.8\textwidth]{figure/Monthly_cooks-1}
-
-}
-
-\end{knitrout}
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
 

### 2020-03-02 presentation.Rnw
gdfhfjfkj

--- 2020-03-02 presentation.Rnw
@@
 
-\section[Zusammenhang Zuschüsse \& ausgewählte Variablen]{Zusammenhang zwischen CHILDRENs Zuschüssen und ausgewählten Variablen}
+\section{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
 
@@
 \begin{itemize}
-\item Schätzung der Modelle mit OLS (Ordinary least squares)
-\item An geeigneter Stelle Vergleich der Ergebnisse mit WLS (Weighted least squares) \item[$\Rightarrow$]Gewichtung der Regressionen mit Variablen die sich stark in ihrer Größe zwischen den verschiednen Organisationen unterscheiden (e.g.
-Anzahl an Essen die ausgegeben werden, Ausflüge die unternommen werden)
+\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
+\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
+\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
+\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Empirischer Ansatz: Imputieren fehlender Werte}
+\frametitle{Variante: Imputieren fehlender Werte}
 \begin{itemize}
-\item Viele Organisationen beantworten nicht alle Fragen aus CHILDREN's Fragebogen
+\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
 \begin{itemize}
 \item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
-\item Imputierung der Daten mit einem organisations-spezifischem linearen Trend
+\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Empirischer Ansatz: Ausschließen von Ausreißern}
+\frametitle{Variante: Ausschließen von Ausreißern}
 \begin{itemize}
-\item CHILDREN fördert einige Organisationen, die überproportional viele Essen ausgeben und Ausflüge unternehmen
-\begin{itemize}
-\item Lösung: Wir erstellen Datensätze, in welchen solche Ausreißer ausgeschlossen werden
-\item Für die Variablen: Anzahl von Essen und Anzahl von Ausflügen
-\end{itemize}
+\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
+\item Lösung: Datensätze ohne Ausreißer
+\item Mittagstisch: Ausreißer bei Anzahl von Essen
+\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
 \item Definition eines Ausreißers:
 \begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter des 25\%-Perzentils liegen
-\item Werte, die 1.5 Interqauntilsabstände über des 25\%-Perzentils liegen
+\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
 \end{itemize}
@@
 
+\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
+
 \begin{frame}[fragile]
-\frametitle{Empirische Fragestellungen (1), Assoziationen zwischen:}
+\frametitle{Assoziationen zwischen:}
 \begin{itemize}
@@
 
-\begin{frame}
-\frametitle{Empirische Fragestellungen (1): Ergebnisse der Fördersumme}
+\begin{frame}[fragile]
+\frametitle{Ergebnisse der Fördersumme}
 
 \begin{itemize}
-\item Effekt auf Anzahl an Essen & Ausflüge
+\item Effekt auf Anzahl an Essen \& Ausflüge
 \begin{itemize}
@@
 \item Entdeckerfonds: kein klarer Zusammenhang 
-\end{itemze}
-\item Effekt auf das Selbstwertgefühl & die Alltagskompetenzen 
+\end{itemize}
+\item Effekt auf das Selbstwertgefühl \& die Alltagskompetenzen 
 \begin{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Empirische Fragestellungen (2), Assoziationen zwischen:}
+\frametitle{Fragestellungen, Assoziationen zwischen:}
 \begin{itemize}
@@
 
+\subsection{Empirische Fragestellungen (2): Ergebnisse}
+
 \begin{frame}
-\frametitle{Empirische Fragestellungen (2): Ergebnisse des DGE-Kriteriums}
+\frametitle{Empirische Fragestellungen (2): }
 
 \begin{itemize}
-\item
+\item Signifikante Effekte in Bezug auf den Zusammenhang des Kriteriums für gesundes Essen und gesundheitsrelevanten Variablen 
+\item Hinzunahme von extrahierten Faktoren als Kontrollen:
+\begin{itemize}
+\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
+\end{itemize}
+\end{itemize}
+\end{frame}
 

### 2020-03-02 presentation.tex
gdfhfjfkj

--- 2020-03-02 presentation.tex
@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 17:19:43 2020
+## % Mon Mar 02 20:08:58 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 17:19:43 2020
+% Mon Mar 02 20:08:58 2020
 \begin{table}[ht]
@@
 \begin{itemize}
-\item Schätzung der Modelle mit OLS (Ordinary least squares)
-\item An geeigneter Stelle: Vergleich der Ergebnisse mit WLS (Weighted least squares)
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Empirischer Ansatz: Imputieren fehlender Werte}
-\begin{itemize}
-\item Viele Organisationen beantworten nicht alle Fragen aus CHILDREN's Fragebogen
+\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
+\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
+\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
+\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Imputieren fehlender Werte}
+\begin{itemize}
+\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
 \begin{itemize}
 \item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
-\item Imputierung der Daten mit einem organisations-spezifischem linearen Trend
+\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Empirischer Ansatz: Ausschließen von Ausreißern}
-\begin{itemize}
-\item CHILDREN fördert einige Organisationen, die überproportional viele Essen ausgeben und Ausflüge unternehmen
-\begin{itemize}
-\item Lösung: Wir erstellen Datensätze, in welchen solche Ausreißer ausgeschlossen werden
-\item Für die Variablen: Anzahl von Essen und Anzahl von Ausflügen
-\end{itemize}
+\frametitle{Variante: Ausschließen von Ausreißern}
+\begin{itemize}
+\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
+\item Lösung: Datensätze ohne Ausreißer
+\item Mittagstisch: Ausreißer bei Anzahl von Essen
+\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
 \item Definition eines Ausreißers:
 \begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter des 25\%-Perzentils liegen
-\item Werte, die 1.5 Interqauntilsabstände über des 25\%-Perzentils liegen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Empirische Fragestellungen (1), Assoziationen zwischen:}
+\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Assoziationen zwischen:}
 \begin{itemize}
@@
 
+\begin{frame}[fragile]
+\frametitle{Ergebnisse der Fördersumme}
+
+\begin{itemize}
+\item Effekt auf Anzahl an Essen \& Ausflüge
+\begin{itemize}
+\item Mittagstisch: Circa 3 Euro mehr resultieren in einer Mahlzeit mehr
+\item Entdeckerfonds: kein klarer Zusammenhang 
+\end{itemize}
+\item Effekt auf das Selbstwertgefühl \& die Alltagskompetenzen 
+\begin{itemize}
+\item Nulleffekte bei beiden Variablen 
+\end{itemize}
+\end{itemize}
+
+\end{frame}
+
 \subsection{Gesundheit}
@@
 
+\subsection{Empirische Fragestellungen (2): Ergebnisse}
+
+\begin{frame}
+\frametitle{Empirische Fragestellungen (2): }
+
+\begin{itemize}
+\item Signifikante Effekte in Bezug auf den Zusammenhang des Kriteriums für gesundes Essen und gesundheitsrelevanten Variablen 
+\item Hinzunahme von extrahierten Faktoren als Kontrollen:
+\begin{itemize}
+\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
+\end{itemize}
+\end{itemize}
+\end{frame}
+
 \section{Partition}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 17:19:51 2020
+% Mon Mar 02 20:09:05 2020
 \begin{table}[ht]

### 2020-03-02 test.Rnw

--- 2020-03-02 paper.Rnw
@@
-% in Terminal enter
-% Rscript -e "library(knitr); knit('paper.Rnw')"
-% pdflatex paper
-% biber paper
-% pdflatex paper
-% pdflatex paper
-
-% IMPORTANT
-
-% Install tex distribution
-% https://www.latex-project.org/get/
-% With Windows, install MikTeX
-
-% in RStudio, install.packages("knitR")
-% also, install all packages that appear in first code chunk in this file, i.e. in the one that looks like this
-% <<LoadingPackages, include=FALSE>>=
-% library(knitr)
-% library(xtable)
-% library(dplyr)
-% library(stargazer)
-% library(cowplot)
-% @
-
-% Go to Tools/Global Options/Sweave
-% Select Weave Rnw files using: knitr
-% Select Typeset LaTeX into PDF using: pdfLaTeX
-
-% Use button "Compile PDF" to knit the Rnw file to a tex file and compile the tex file to a pdf file.
-
-% Always install all packages that you're asked to after having pressed "Compile PDF".
-
-% If there is no error while knitting from Rnw to tex, but an error while compiling from tex to pdf, have a look at the pdf file. It might still have worked.
-
-% instead of Compile PDF, go into Terminal and enter 
-% Rscript -e "library(knitr); knit('paper.Rnw')"
-% latexmk -pdf paper
-
-% turn page 90 degrees with lscape Gandrud (2016), p.185
-
-% Create clickable hyperlinks with hyperref package, Gandrud (2016), p. 218
-
-% Use natbib package for bibliography formatting, authoryear for Harvard style , Gandrud (2016), p. 227
-% commands to change what information is included in the parentheses, Gandrud (2016), p. 228, table 11.2
-
-% Using saveRDS and readRDS, following 
-% https://csgillespie.github.io/efficientR/efficient-inputoutput.html#efficient-data-export-.rdata-or-.rds
-
-% working with knitR and LaTeX
-% https://kbroman.org/knitr_knutshell/pages/latex.html
-
-% rotate tables in knitr
-% https://stackoverflow.com/questions/21840878/rotate-a-table-from-r-markdown-in-pdf
-% in particular stargazer tables
-% https://stackoverflow.com/questions/31169845/rotate-stargazer-table-in-knitr/34292292#34292292
-
-% Create list of packages used, Gandrud (2016), p 218/219
-
-% models with robust standard errors texreg
-% https://github.com/DeclareDesign/estimatr/issues/316
+% Rscript -e "library(knitr); knit('test.Rnw')"
+% pdflatex test
+% biber test
+% pdflatex test
+% pdflatex test
 
 \documentclass[12pt, a4paper, titlepage]{article}
-\usepackage{lscape}
-\usepackage{graphicx}
-\usepackage[utf8]{inputenc}
-% bibstyle=apa, citestyle=authoryear
-\usepackage[backend=biber, style=apa]{biblatex}
-\DeclareLanguageMapping{english}{english-apa}
-\usepackage{floatrow}
-\usepackage{booktabs}
-\usepackage[ngerman, english]{babel}
-\usepackage{csquotes}
-% \usepackage{bookmark}
-\usepackage{rotating}
-\usepackage{dcolumn}
-% \usepackage[authoryear]{natbib}
-% \bibliographystyle{apalike}
-\usepackage{mathtools}
-% \usepackage[onehalfspacing]{setspace}
-\usepackage[left = 2.5cm, top = 2.5cm, right = 2.5cm, bottom = 2.0cm]{geometry}
-\usepackage[hidelinks]{hyperref}
-
-% 1.5 spacing in Word is about this in LaTeX
-% https://tex.stackexchange.com/questions/65849/confusion-onehalfspacing-vs-spacing-vs-word-vs-the-world
-
-\linespread{1.25}
-
-\addbibresource{references.bib}
 
@@
 
-<<CentAlignFig, include=FALSE>>=
-# Center align all knitr figures
-# Gandrud (2016), p. 53-55
-opts_chunk$set(fig.align = "center",
-                out.width = "0.8\\textwidth")
-@
-
-% multiple authors
-% https://tex.stackexchange.com/questions/4805/whats-the-correct-use-of-author-when-multiple-authors
-
-\title{Analysis of Survey Data Collected by CHILDREN for a better World e.V.}
-\author{
-Laura Huber\\
-%\texttt{11709507}
-\and
-Laura Jepsen\\
-%\texttt{11567799}
-\and
-Jonathan Kirschner\\
-%\texttt{11724530}
-\and
-Rafael Schütz\\
-%\texttt{11574909} 
-\and 
-Yannick Zurl\\
-%\texttt{11701793}
-\and
-Studentisches Praxisprojekt zur Empirischen Wirtschaftsforschung PaRE3To\\
-\and
-Ludwig-Maximilians-Universität Munich
-}
-
-% Winter Term 2019/20\\
-
-\date{27th February 2020}
-
 \begin{document}
 
-% \begin{titlepage}
-% \maketitle
-% \end{titlepage}
-
-\tableofcontents
-\listoftables
-
-% note below table
-% https://stackoverflow.com/questions/44549464/table-spacing-issue-converting-to-pdf-via-latex-with-pandoc/44797387#44797387
-\listoffigures
-
-\begin{abstract} 
-This study describes the analysis of the data from the non-profit organisation 'CHILDREN for a better world e.V.'.
-We obtain null-results associated to the subsidy CHILDREN provides for its two flagship programs, Meals and Trips, and selected outcome variables.
-We find a strong but only partially robust connection between health relevant outcomes and the index of healthy diet criteria fulfilled in organization's menus.
-Using a differences-in-differences strategy, we cannot show a significant effect of participating in the Trips program on the everyday expertise and selfworth of the beneficiaries.
-\end{abstract}
-
-\section{Introduction}
-CHILDREN for a better World e.V.
-is a non-profit organization supporting social institutions for children and adolescents across Germany, such as youth centers.
-Their goal is to foster equality of opportunities for the youth in Germany.
-CHILDREN supports poor and disadvantaged families and young people in socially problematic areas.
-Furthermore, they fight child poverty and encourage the youth to engage in society.
-We call the institutions funded by CHILDREN organizations in the following.
-Organizations have to apply for funding from CHILDREN each year again.
-In the application process, CHILDREN requires the applicants to answer a survey which contains questions about outcomes related to CHILDREN’s programs as well as general information about the organization such as the yearly budget.
-CHILDREN provided us with data from two of its flagship programs: Mittagstisch (we refer to this as Meals program) and Entdeckerfonds (Trips program).
-The organizations use money from the Meals program to finance meals, from breakfast to dinner, that they sell at concessionary prices to the children and adolescents that visit them.
-In the following, we call these children and youth who ultimately profit from CHILDREN's grants beneficiaries.
-The organizations also use money from the Trips program to make trips to nearby places usually unknown to the beneficiaries.
-
-Previous research shows that childhood and youth are central in development of character traits and future opportunities.
-Factors like education, stable family conditions, social contacts and mobility shape children and adolescents for their further life.
-Children from parents with lower income and lower educational attainment have typically a lower weight at birth and are born in a later week of gestation \parencite{Deckers.27.04.2015}, which are indicators for bad initial conditions, as shown by \textcite{Case.2002}.
-Children that grow up in families with a low socio-economic status are often less mobile and more likely to stay amongst themselves.
-This could have a negative influence on their character development.
-For example, \textcite{Chetty.2014} investigate for the US, that areas with more mobility are highly correlated with better primary schools, greater social capital and more stable family conditions.
-Furthermore, the result of \textcite{Kosse.2020} provides causal evidence on the effect of social environment on prosocial attitudes.
-Being supported by a mentor could result in a significant and persistent increase in the prosociality of elementary school children, with regard to prosocial role models and intense social interactions.
-\textcite{Heckman.2010} investigated a preschool education program in the US.
-He shows that an investment in the improvement of the childhood conditions could have a high rate of return, even by controlling for possible distortions.
-
-The aim of our project paper is to test whether CHILDREN’s programs positively influence the beneficiaries.
-We look at the associations between the subsidy CHILDREN provides and the share of beneficiaries with broadened everyday expertise and improved selfworth.
-Furthermore, we analyze the association between the measure of the healthiness of the meals the organizations offer and health-relevant outcomes of beneficiaries.
-The aim of our applied differences-in-differences estimation is to test whether the activities offered by the Trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
-We find no profound connection between the subsidy CHILDREN provides and the effectiveness of the organizations regarding the share of beneficiaries with broadened everyday expertise and improved selfworth.
-On the other hand, focusing on health relevant variables, we obtain a positive association between the index of healthy diet criteria fulfilled by organizations and the share of beneficiaries who are less frequently ill.
-By using the differences-in-differences (DID) strategy, the estimates show that the participation in the Trips program has a positive, but insignificant effect on the everyday expertise of beneficiaries.
-Strikingly, we observe a negative association between participating in the Trips program and selfworth.
-However, the results of the DID estimation should not be overstated because of the small sample size.
-The remainder of this project paper is structured as follows: Section \ref{data} describes the variable used for the empirical analysis.
-Then we present summary statistics.
-We explain the dimensionality reducing method factor analysis.
-The proceeding section reports different regression results.
-After that, we implement the differences-in-differences strategy to test for the effects of the Trips program.
-Finally, we conclude and provide suggestions for CHILDREN.
-
-\section{Data}
-\label{data}
-To measure the effect of CHILDREN's programs on the supported organizations, we use data from 2011 to 2018.
-In each year CHILDREN sends a survey to the organizations with several questions about the previous year.
-The number of organizations varies across years and increases over time: From 52 organizations in 2011 to 68 organizations in 2018.
-In some organizations one specific employee answers the survey questions, while in other institutions the questionnaire is answered in a team.
-As the children and adolescents are not questioned directly, all responses are documented as perceptions of the employees.
-The constellation of the variables in the data set also varies across years.
-For instance, CHILDREN asks for the average amount of kids that increased their confidence or improved their dietary knowledge.
-These questions of the survey are based on a scale of five levels from no to all kids.
-We perform several steps to receive a full dataset, which we use in our empirical analysis.
-Originally, the data was divided into seperate data sets for the respective years.
-We only use the surveys until 2018, because in 2019 some organization-ID's occurred multiple times and the dataset for 2019 was incomplete.
-To ensure comparability across years, we named all variables the same.
-We merged the different datasets to a common dataset, including all years and variables CHILDREN collected.
-For an efficient and clear data structure, we created a function that automatically changed the data type of all variables from "character" to "ordinal" and added several versions for each initially metric encoded variable afterwards.
-The three variants are ordinal, standardized and weighted.
-Furthermore, we created a set of new variables. For instance, we used the information CHILDREN gave us to assign the German states to the corresponding organization-ID. 
-The final dataset that we used for the empirical analysis is structured as follows: Each row represents a specific organization observed in a specific year.
-The questions are divided in two categories.
-The first part of the data set includes variables regarding the Meals program.
-The second part contains variables affecting the Trips program.
-The final data set comprises the years 2011 to 2018.
-Many organizations do not answer all questions CHILDREN poses.
-We create a seperate data set, in which we impute missing values with an organization-specific linear trend.
-CHILDREN supports some very large organizations that give out hundreds of meals a day or conduct dozens of trips per year.
-We fit our models with outliers excluded to see if they are driving results.
-We define an outlier as a value that is at least 1.5 interquartile ranges below the 25th percentile or equally far above the 75th percentile.
-Once we exclude outliers in terms of numbers of meals and once in terms of number of trips.
-
-\section{Summary Statistics}
-\subsection{Fundamental Dynamics} 
-In this section, we give an overview of the dynamics of CHILDREN's two flagship programs.
-We focus on the number of estimated ultimate beneficiaries in both programs, median total subsidy, median subsidy per institution, and median subsidy per beneficiary.
-We also look at selected outcomes, i.e.
-those related to health as well as self-worth and day-to-day skills.
-We have converted all nominal monetary variables into 2015 euros, using price indices from the Federal Statistical Office of Germany (Statistisches Bundesamt).
-We deflate (requested) grants as well as organizations' total expenses for the Meals program  with the price index related to food and non-alcoholic beverages (in German: Nahrungsmittel und alkoholfreie Getränke) and (requested) grants towards the Trips program with the price index for leisure, entertainment, and culture (in German: Freizeit, Unterhaltung und Kultur).
-These are only available after logging in on DESTATIS.
-The organizations also gave information about their total yearly budget.
-We inflate this with the general price index.
-
-<<FundamentalDynamics, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+<<Partition, echo=FALSE, results='asis', message=TRUE, warning=TRUE>>=
 
@@
 
-fundamental_dynamics = readRDS("./ANALYSIS/Tables/fundamental_dynamics.Rds")
-
-colnames(fundamental_dynamics) <- c("Year", "Beneficiaries, Meals", "Beneficiaries, Trips", "Organizations, Meals", "Organizations, Trips")
-
-xtable(fundamental_dynamics,
-                                  # summary = FALSE,
-                                digits = c(0, 0, 1, 1, 0, 0),
-           caption = "Summary Statistics",
-           align = "lccccc", 
-          label = "fundamentalDynamics"
-          )
-
-@
-% look up official names of price indices in English
-
-Table \ref{fundamentalDynamics} shows that, at the beginning of the time series in 2011, in the Lunch program they supported in 52 organizations.
-In 2018, this number has increased to 68.
-In 2011, CHILDREN financed meals for 3748 beneficiaries, and for 5103 in 2018.
-In the Trips program, which launched in 2012, the number of supported organizations amounted to 44 in 2012 and grew to 49 until 2018.
-In 2012, their grant allowed 2803 beneficiaries to go on trips, and 6911 in 2018.
-
-\subsection{Trends of Grants}
-
-\begin{figure}
-  \caption{Yearly Dynamics of Total Grants in Meals and Trips Program}
-  \label{totalGrantsDyn}
-
-<<GrantTrend, echo=FALSE, message=FALSE>>=
-totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-print(totalGrantsDyn)
-@
-
-\floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
-From left to right: Meals, Trips.
-From top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-\end{figure}
-
-For the dynamics of figure \ref{totalGrantsDyn} we visualze the dynamics of CHILDRENs' grants by distinguishing between the sum of grants in one year, the median and the median grant per beneficiary.
-We also compare the grants of the Lunch and the Trips program.
-
-Figure \ref{totalGrantsDyn} shows no exact trend for the total real grant for the Lunch program.
-Between 2013 and 2015 the grant increased from about 600000 EUR to 680000 EUR, but falls behind in the following year.
-Since 2017 an increase is again visible.
-In comparison to this, there is a clearer negative trend in median meals subsidy, falling from about 8000 EUR in 2012 to about 6500 EUR in 2018.
-In accordance, the median meals grant per beneficiary shrinks from about 250 EUR to about 200 EUR.
-
-In the total trips grant, a slightly negative trend is visible, after the subsidy increased to approximately 200000 EUR in 2014, but decreased to about 130000 EUR in 2016, and is connstand eversince.
-The trips median grant therefore also decreased from 3000 EUR to 2000 EUR over the time period, as well as the median grant per beneficiary decreased from about 60 EUR to about 30 EUR.
-
-These results visualize, for the Lunch as well as for the Trips program, together with the fundamental dynamics of table \ref{fundamentalDynamics}, that CHILDREN was able to increase the number of organizations they support, but had to distribute the available subsidy among them.
-
-\subsection{Dynamics of Health-Related Variables}
-
-In its yearly surveys, CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are healthier, have a growing appreciation for a healthy diet, or have increased their knowledge about what constitutes a healthy diet.
-Figure \ref{HealthTimeplots} displays the share of organizations in each category of the health outcome from 2011 to 2018.
-The possible values are: all, most, some, few, and none.
-For this figure, we use the original ordinal varibles which result from the survey structure.
-
-\begin{figure}
-  \caption{Health Outcome Over Time}
-  \label{HealthTimeplots}
-<<HealthTimePlots, echo=FALSE, message=FALSE>>=
-Health_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_Year.Rds")
-print(Health_timeplots)
-@
-\floatfoot{In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few and none.}
-\end{figure}
-
-In Figure \ref{HealthTimeplots}, for the variable 'lessIll\_ordered', there is much non available data (lessIll\_ordered refers to the share of beneficiaries who are less frequently ill).
-In all years, most organizations say that most beneficiaries are more healthy.
-The least stated category is, that all beneficiaries are less ill.
-That few are less ill, appears sometimes and the leftover category, none, which is only coded for the variable 'lessIll\_ordered', appears as good as never.
-
-In the second plot of figure \ref{HealthTimeplots} (variable 'dietaryKnowledge\_ordered', refers to the share of beneficiaries with expanded dietary knowledge) most organizations state, that predominantely most or all beneficiaries increased their knowledge about what constitutes a healthy diet.
-The least stated category is that some beneficiaries increased their dietary knowledge.
-The leftover category, few, does not appear.
-
-The bottom plot of figure \ref{HealthTimeplots}, which visualizes the variable 'appreciateHealthy\_ordered' (refers to the share of beneficiaries with increased appreciation for a healthy diet).
-Again most organizations state, that most beneficiaries have a growing appreciation for a healthier diet.
-The second most stated answer is that all beneficiaries have a growing appreciation for a healthier diet.
-The least stated category by the organizations is, as well as in the second plot, that some have a growing appreciation for a healthier diet.
-The leftover category, few, also does not appear.
-
-\subsection{Selfworth and Everyday Expertise}
-
-In its yearly surveys, CHILDREN has always asked about the following two variables.
-These are the shares of beneficiaries with improved self-worth and with broadened everyday expertise.
-Figure 4 displays the share of organizations in each category of the health outcome from 2011 to 2018.
-The possible values are: all, most, some, few, and none.
-As well as in the last figure (figure 3), we use the original ordinal varibles which result from the survey structure.
-
-\begin{figure}
-  \caption{Selfworth and Everyday Expertise Over Time}
-  \label{EqualityTimeplots}
-<<EqualityTimePlots, echo=FALSE, message=FALSE>>=
-Equality_timeplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Equality_Year.Rds")
-print(Equality_timeplots)
-@
-\floatfoot{In its yearly surveys CHILDREN has always asked about following two variables.
-These are the shares of beneficiaries with improved self-worth (selfworth\_ordered) and with a broadened understanding for everyday expertise (dayToDaySkills\_ordered).
-The x-axis plots the year. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none.}
-\end{figure}
-
-Figure \ref{EqualityTimeplots} shows in its upper plot the development of the answered categories for the variable selfworth\_ordered (refers to the share of beneficiaries with improved self-worth).
-Mostly, the answer is that most beneficiaries in most organizations have more selfworth.
-The second most stated category is that all beneficiaries gained in selfworth and the least stated is that some have more selfworth.
-The leftover category, few, does not appear.
-
-In the bottom plot of figure \ref{EqualityTimeplots} the development of the share of beneficiaries with a broadened understanding for everyday expertise over time is visible.
-The results are about similar to the previous results of selfworth: Most beneficiaries in most organizations have a growing understanding of everyday expertise.
-
-\section{Feature Selection}
-
-CHILDREN survey many variables, some of which seem closely related to each other.
-We use exploratory factor analysis for dimensionality reduction and employ extracted factors as controls in the models we estimate.
-In the appendix, we use the partition method suggested by \textcite{Millstein.2020} to establish a one-to-one correspondence between apparent and underlying variables.
-
-\subsection{Exploratory Factor Analysis}
-
-The fundamental theorem of factor analysis posits that each observable variable can be expressed as a linear combination of a smaller number of underlying factors as well as an error term.
-The coefficients of the factors are called loadings.
-\parencite[p.310]{Moosbrugger.2008}
-
-For factor analysis, we work with the imputed data set.
-We conduct a separate factor analysis for each model that we want to fit.
-Each time, we include all variables that were recorded in all years the Meals and the Trips program have been run respectively, but exclude those that we want to use as response and predictor in the corresponding model.
-
-First, we determine the optimum number of factors via the stochastic approach of parallel analysis, following the advice of \textcite[p.313]{Moosbrugger.2008}.
-We estimate factor scores and loadings with the Bartlett method, which is similar to a Maximum Likekelihood estimation, and presented as the most convential one in \textcite[p.291]{Eid.2014}.
-As the fundamental theorem of factor analysis has no unique solution, we have to decide on how to rotate the factors.
-As we want them to be orthogonal to each other, we use the rotation technique Varimax, which is recommended for this purpose in \textcite[p.317]{Price.2017}.
-
-% \subsection{Double Selection}
-
-\section{Associations Between CHILDREN's Grants and Selected Outcomes}
-
-\subsection{Empirical Approach}
-
-In this section, we use a simple linear model, as described in equation \ref{SimpleLinearModel}.
-We estimate each model with the original data set, the one with imputed variables, and the one with excluded outliers.
-When appropriate, we include the relevant extracted factors as controls.
-
-\begin{equation}
-\label{SimpleLinearModel}
-  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
-\end{equation}
-
- We look at the association between:
-
-\begin{itemize}
-  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Meals program and the number of meals it dispenses}
-  \item{the subsidy (in 2015 EUR) an organization receives through CHILDREN's Trips program and the number of trips it conducts}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with improved self-worth}
-  \item{the subsidy per beneficiary (in 2015 EUR) an organization receives through CHILDREN's Meals program and the standardized share of beneficiaries with broadened everyday expertise}
-   \item{a standardized measure of the healthiness of the meals an organization dispenses and various standardized health-related outcomes of beneficiaries} 
-\end{itemize}
-
-We discuss all these models in turn.
-
-\subsection{Direct Effects of CHILDREN's Grants}
-
-If CHILDREN's grants are to have an effect on beneficiaries, they should first influence the output of organizations in terms of meals dispensed and trips conducted.
-
-<<GrantsRegressionsLunch, echo=FALSE, results='asis', message=FALSE>>=
-
-lm_ms = readRDS("./ANALYSIS/Tables/mealsNo_sub.lm.Rds")
-lm_ms_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_control.lm.Rds") #control
-lm_ms_o = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex.lm.Rds")#outlier meals
-lm_ms_o_c = readRDS("./ANALYSIS/Tables/mealsNo_sub_ex_control.lm.Rds")#outliercontr
-lm_ms_i = readRDS("./ANALYSIS/Tables/mealsNo_sub_IM.lm.Rds")#impute meals
-
-texreg(list(lm_ms, lm_ms_c, lm_ms_o, lm_ms_o_c, lm_ms_i), caption = "Association Between Number of Meals and Real Subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of meals \\\\ realSubsidy: subsidy for Meals program in 2015 EUR \\\\ eatersPerMeal: number of beneficiaries of Lunch program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "GrantsRegressionsLunch", booktabs = TRUE, use.packages=FALSE)
-
-@
-
-As table \ref{GrantsRegressionsLunch} shows, this is emphatically true.
-Whether we look at the original data set, the one without outliers or the one with imputed values, a strong association becomes evident.
-The estimated coefficients are very similar when we use the original dataset and the one with imputed values.
-In the case of the original data set, increasing the subsidy of an organization by one EUR is associated with 2.6 additional meals dispensed.
-This estimate is highly statistically significant.
-When we exclude outliers, i.e.
-those organizations that give out very many menus or very few menus,
-the estimated coefficient decreases by about one order of magnitude.
-Still, spending not much more than three EUR more goes hand in hand with one extra meal.
-The estimate is also highly statistically significant.
-
-In the remit of the Trips program, the picture looks much different.
-In the case of the original data set and the data set with imputed variables, an increase in the trips subsidy by 5000 EUR is needed for an extra trip.
-The coefficent of 0.0002 is statistically significant at the 5\% level.
-As soon as outliers are excluded, the coefficent changes to 0.0003, which is highly statistically significant.
-This means that, according to this model, at least 3000 EUR are needed for an additional trip.
-In sum, there seems to be no clear connection between how much money CHILDREN gives to an organization and the number of trips it organizes.
-
-<<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
-lm_ts = readRDS("./ANALYSIS/Tables/tripsNo_sub.lm.Rds")
-lm_ts_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_control.lm.Rds")
-lm_ts_o = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex.lm.Rds") #outlier trips
-lm_ts_o_c = readRDS("./ANALYSIS/Tables/tripsNo_sub_ex_control.lm.Rds")
-lm_ts_i = readRDS("./ANALYSIS/Tables/tripsNo_sub_IM.lm.Rds") #imputetrips
-
-texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association Between Number of Trips and Real Subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
-@
-
-\subsection{Variables of Interest: Selfworth and Everyday Expertise}
-
-In their surveys, CHILDREN asks about two variables in both programs.
-These are the share of beneficiaries with improved self-worth and share of beneficiaries with broadened everyday expertise.
-This feature could potentially allow us to compare the two programs regarding their realtive effectiveness.
-Like always, we standardize the two outcome variables.
-As before, we can only make associational claims.
-We invariably find no clear-cut relationship between the subsidy per beneficiary and the two outcomes.
-In fact, no coefficent is statistically significantly different from zero at any of the usual levels.
-The four variables are recorded for each year in which the program was operative.
-Tables \ref{SelfworthRegressions} and \ref{DayToDaySkillsRegressions} present the null results.
-
-<<SelfworthRegressions, echo=FALSE, results='asis', message=FALSE>>=
-
-ss = readRDS("./ANALYSIS/Tables/selfworth_scaled.Rds") 
-tss = readRDS("./ANALYSIS/Tables/selfworthTrips_scaled.Rds")#sw
-ssI = readRDS("./ANALYSIS/Tables/selfworth_IM_scaled.lm.Rds") #standardized
-tssI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM_scaled.lm.Rds") 
-sfactor = readRDS("./ANALYSIS/Tables/factorselfworthmeals.Rds")
-
-texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association Between Selfworth and Subsidy per Beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE)
-@
-
-<<DayToDaySkillsRegressions, echo=FALSE, results='asis', message=FALSE>>=
-ds = readRDS("./ANALYSIS/Tables/dayToDaySkills_scaled.lm.Rds") #standardizedweigh
-tds = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_scaled.lm.Rds")
-dsI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM_scaled.lm.Rds") 
-tdsI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM_scaled.lm.Rds")
-dfactorm = readRDS("./ANALYSIS/Tables/factordaytodayskillsmeals.Rds")
-dfactort = readRDS("./ANALYSIS/Tables/factordaytodayskillstrips.Rds")
-
-texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE)
-
-@
-
-\subsection{Variables of Interest: Health Variables}
-
-Now, we turn to a predictor that CHILDREN does not directly influence until now, but that it easily could.
-In 2014, 2016, 2017 and 2018 the organizations had to send CHILDREN a sample of their menus.
-An ecotrophologist collaborating with CHILDREN assessed those menus with regards to how healthy they were.
-This assessment was based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-
-In its yearly surveys, CHILDREN asks about three variables closely related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill, with expanded dietary knowledge and with increased appreciation for a healthy diet.
-
-Figure \ref{HealthPlots} gives an overview of the relationship between the healthy food criterion (DGECriteriaNo, index of healthy diet criteria fulfilled in organization's menu) and each of the three health-related variables.
-For these results, we use their ordinal values.
-The x-axis displays the index for a healthy diet.
-The y-axis displays the share of organizations in each category of the health outcome.
-The possible values are: all, most, some, few and none.
-For example, if an organization says that most beneficiaries are healthier, then this would be coded as most.
-In the last reporting period, there are 13 healthy diet criteria.
-In previous years there were up to 15.
-The ecotrophologist assessed each criterion individually and decided wether it was fulfilled or not.
-The healthy food index is calculated as the number of fulfilled criteria.
-Examples for criteria are daily carbohydrates or daily vegetables.
-
-All plots of Figure \ref{HealthPlots} show that most organizations suffice about 5 to 10 healthy food criteria.
-The largest part of criterion values are associated with most beneficiaries being less ill, having a growing appreciation for a healthy diet or having increased their knowledge about what constitutes a healthy diet.
-It secondly becomes visible that the healthy criterion only exchanges with a growing appreciation for a healthy diet or an increasing dietary knowlege for all beneficiaries (which is the second most stated criterion in the two bottom plots), but not with all beneficaries being more healthy.
-However, for the variable less ill, the least data is availabe.
-Overall, the criteria, even a few, seem to have a positive relationship with beneficiaries health relevant variables.
-This connection is empirically examined in regressions \ref{HealthRegressions-LessIll}, \ref{HealthRegressions-DietaryKnowledge} and \ref{HealthRegressions-AppreciateHealthy}.
-
-\begin{figure}
-  \caption{Health Outcomes versus Healthy Meals}
-  \label{HealthPlots}
-<<HealthRegressionsPercentageplots, echo=FALSE, message=FALSE>>=
-Health_percentageplots <- readRDS("./ANALYSIS/GRAPHS/PAPER/Health_percentageplots.Rds")
-print(Health_percentageplots)
-@
-\floatfoot{DGECriteriaNo is an index of healthy diet criteria fulfilled in organization's menu.
-It is based on criteria of the German Nutrition Society (Deutsche Gesellschaft für Ernährung).
-According to information from CHILDREN, they ask the organizations to send them a sample of their menus.
-An ecotrophologist collaborating with CHILDREN assessed the menus.
-In its yearly surveys CHILDREN asks about three variables closley related to a healthy diet.
-These are the shares of beneficiaries who are less frequently ill (lessIll\_ordered), with expanded dietary knowledge (dietaryKnowledge\_ordered), or with increased appreciation for a healthy diet (appreciateHealthy\_ordered).
-The x-axis plots the index for a healthy diet. The y-axis displays the share of organizations in each category of the health outcome. The possible values are: all, most, some, few, and none}
-\end{figure}
-
-We use standardized versions of the health related variables as outcomes in simple linear models with a standardized version of the healthy food criterion as a predictor in each.
-By estimating these models with ordinary least squares (OLS), we ascribe the same weight to an organization where a thousand beneficiaries regularly eat as to one where only ten people do so.
-To control for this difference in size, we additionally fit the models with weighted least squares (WLS), using the number of beneficiaries as weights.
-
-In Table \ref{HealthRegressions-LessIll}, after weighting the regression for the original data set, the coefficent rises slightly but is becoming less statistically significant.
-An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.35 standard deviations.
-Regressing with the imputed dataset, results decrease by about 0.1.
-Using weighted least squares additionaly results in a slighty decreased coefficent, which is not significant anymore.
-Regressing with the imputed data set with extracted factor scores as controls, we still obtain a slightly postive significant coefficent: An increase of the healthy food criterion by one standard deviation is associated with an increase in beneficiaris being less frequently ill by 0.18 standard deviations.
-Overall, there is a positive association between the two variables.
-
-An expanded model with the dependent variable less Ill is presented in Appendix 1 in table \ref{expandLessIll}.
-
-In Table \ref{HealthRegressions-DietaryKnowledge} weighted least squares constanly leads to smaller coefficents which are not statistically significant.
-For the original data set, the coefficient is slightly negative.
-Using the imputed data set, an increase in the healthy meals criterion by one standard deviation is associated with an increase in beneficiaries dietary knowledge by 0.l standard deviations.
-This coefficent is as well insignifacant.
-Also, regressing with the imputed data set with extracted factor scores as controls, does not display a profound connection between beneficiaries dietary knowledge and the healthy meals index.
-
-In the regressions presented in table \ref{HealthRegressions-AppreciateHealthy}, the changes between ordinary and weighted least squares are much stronger.
-For the original data set, the OLS coefficent amounts to 0.27, which is highly significant.
-When using WLS, we find a slightly negative association.
-A one standard deviation increase in the healthy meals criterion is associated with a decrease in the appreciation of a healthy diet by 0.02.
-This coefficent is not significant.
-For the imputed dataset we find a similar picture.
-Similar to the previous regression, the imputed data set with extracted factor scores as controls, does not show any association between the appreciation of a healthy diet and the healthy meals index.
-
-The regressions with WLS suggest that the results obtained using OLS, are driven by large oraganizations.
-
-<<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
-
-lDGE = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled.lm.Rds")
-#extraweighted
-lDGEw = readRDS("./ANALYSIS/Tables/lessIll_DGE_scaled_weighted.lm.Rds")
-#standardized
-lDGE_i = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled.lm.Rds")
-#extraweighted
-lDGE_iw = readRDS("./ANALYSIS/Tables/lessIll_DGE_IM_scaled_weighted.lm.Rds")
-illfactor = readRDS("./ANALYSIS/Tables/lessIllfactor.Rds")
-
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association Between Healthy Meals Criterion and Beneficiaries Being Less Ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE)
-@
-
-<<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
-dDGE = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled.Rds")
-dDGEw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_scaled_weighted.Rds")
-dDGE_i = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled.lm.Rds")
-dDGE_iw = readRDS("./ANALYSIS/Tables/dietaryKnowledge_DGE_IM_scaled_weighted.lm.Rds")
-dietaryf = readRDS("./ANALYSIS/Tables/dietaryknowledgefactor.Rds")
-
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association Between Healthy Meals Criterion and Beneficiaries Dietary Knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE)
-@
-
-<<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
-aDGE = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled.Rds")
-aDGEw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_scaled_weighted.Rds")
-aDGE_i = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled.lm.Rds")
-aDGE_iw = readRDS("./ANALYSIS/Tables/appreciateHealthy_DGE_IM_scaled_weighted.lm.Rds")
-appreciatef = readRDS("./ANALYSIS/Tables/appreciatehealthyfactor.Rds")
-
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association Between Healthy Meals Criterion and  Beneficiaries Appreciation of a Healthy Diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
-@
-
-The previous simple linear models are regressed with metric versions of the survey varibales.
-Originally, variables which range from none to all are ordinal.
-To account for this, we present a method to regress those variables according to their original traits.
-Therefore, we use a cumulative logit model.
-Selected results for the Meals program are presented in appendix 2 in the tables\ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds}, \ref{selfworthOdds} and \ref{dayToDayOdds}.
-
-\section{The Effects of the Trips Program on Participating Beneficiaries}
-
-How do children and adolescents benefit from visiting social institutions that CHILDREN supports financially?
-So far this question could not be empirically validated.
-Hence, one of our biggest challenges was determining a possible solution for measuring potential causal effects of the supported programs on the participating beneficiaries.
-During the first meeting with CHILDREN, Wiltrud de Haan presented relevant information that CHILDREN supports all organizations with their Meals program.
-However, not all organizations receive additional funding to provide the Trips program.
-This fact could be used for applying an empirical approach which determines the effects of the Trips program by comparing a treatment with a control group.
-The aim of this analysis is to test whether the activities offered by the Trips program have a positive effect on the participating children, measured through a change in selfworth and everyday expertise.
-
-\subsection{Empirical Approach}
-
-The basis of the empirical approach is the specification of the treatment and the control group.
-Using the data provided by children we determine the treatment group as all organizations that receive funding for both the Trips and the Meals program.
-On the other hand, the control group represents all organizations that only receive funding for the Meals program.
-Therefore, the social institutions in the control group do not participate in the Trips program.
-
-\subsubsection{Specification of the Treatment Group}
-
-When analyzing the available dataset, it was not certain which organizations actually received funding for the Trips program.
-As previously mentioned, the CHILDREN survey consists of two parts.
-The first part contains questions that are specific to the Meals program and the second part includes all questions which are relevant for organizations that receive funding for the Trips program.
-The dataset shows that there are several organizations that did not provide information regarding the Trips program.
-In consultation with Wiltrud de Haan, she informed us that these specific organizations did not receive funding to offer trips and activities.
-Hence, we assumed that all organizations that did not provide information regarding the Trips program in a given year, did not receive funding for the program and would be part of the control group.
-When analyzing the possible treatment group, we realized that some organizations did not completely answer the Trips program survey.
-There are organizations, for example organization 103 in 2015, that did not provide information about the funding amount but answered the Trips program survey questions such as the number of trips in a given year.
-Wiltrud de Haan informed us, that one possible explanation for this occurrence is that these organizations did not completely use the funding in the previous year.
-Therefore, they did not receive additional funding in the following year but were able to organize trips for the children as part of the Trips program with the remaining funding of the year before.
-
-Due to these uncertainties we determine the treatment group in two different ways. Firstly, the treatment variable is specified as follows:
-\begin{equation}
-TreatEF_{it} =
-\begin{cases}
-1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the Trips program in year \begin{itshape}{t}\end{itshape} or any year before}\\
-0, & \text{otherwise}
-\end{cases}
-\end{equation}
-
-In this setting, once an organization receives funding for the Trips program, we consider this organization as treated in the year of the first funding and all proceeding years.
-This implies that an organization remains in the control group as long as it does not receive funding for the Trips program.
-Due to this definition, an organization cannot change from the treatment into the control group.
-
-In general, the constellation of the treatment and control group varies across years.
-As the number of organizations supported by CHILDREN increased over time, both the treatment and control group increased as well.
-At first, new organizations are generally funded to provide the Meals program and might receive funding for the Trips program during later funding periods.
-In this case, organizations change from the control group into the treatment group resulting in an overall adjustment of the constellation of both groups.
-However, the dataset also includes organizations that switch from the treatment to the control group.
-The first definition of the treatment variable does not take this case into account.
-Therefore, we additionally construct a second treatment indicator which is defined as follows:
-\begin{equation}
-TreatEF_{it} =
-\begin{cases}
-1, & \text{if organization \begin{itshape}{i}\end{itshape} participates in the Trips program in year \begin{itshape}{t}\end{itshape}}\\
-0, & \text{otherwise}
-\end{cases}
-\end{equation}
-
-Using this alternative treatment variable, the actual funding for the Trips program in a given year determines the treatment. Therefore, the treatment status could change every year.
-With both definitions of the treatment variable, the number of observations units in the control group is substantially lower than in the treatment group.
-Consequently, the estimates cannot be very robust.
-Therefore, the results should not be overstated.
-
-\subsubsection{Dependent Variables}
-
-The fact that all organizations within the control group did not answer the Trips program survey questions was helpful to categorize the control and the treatment group.
-However, the impact of the Trips program cannot be measured with variables that are specific to the Trips program as these were only observed for the treatment group.
-Therefore, we have to use variables of the Meals program as outcome variables in our analysis.
-For this purpose, we identified selfworth and everyday expertise as appropriate dependent variables.
-Firstly, both variables are applicable to the Trips program as well as the Meals program.
-In addition, the chosen variables are observed in every year throughout the whole observation period and seem to be influenced by the fact that an organization receives funding to provide trips and other activities.
-
-\subsubsection{Graphical Evidence}
-
-\begin{figure}
-  \caption{Trend in Share of Beneficiaries With Improved Selfworth}
-  \label{selfworth_Trend}
-
-<<Selfworth, echo=FALSE>>=
-figureSelfworth = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_selfworth.Rds")
-print(figureSelfworth)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the Trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to selfworth.
-The time trend of the average answers of the organizations in the treatment group is characterized by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{Trend in Share of Beneficiaries With Broadened Everyday Competence}
-  \label{dayToDaySkills_Trend}
-
-<<Daytodayskills, echo=FALSE>>=
-figureDaytodayskills = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_dtds.Rds")
-print(figureDaytodayskills)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the Trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to everyday expertise.
-The time trend of the average answers of the organizations in the treatment group is characterized by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-To check for differences in treatment and control group, we created descriptive statistics regarding the variables of interest.
-Figure 5 and Figure 6 represent the development of average selfworth and average everyday expertise over time for both the treatment and control group.
-The two graphs illustrate a difference in levels as well as in trends between the treatment and control group in either average selfworth or average everyday expertise.
-In the treatment group the average selfworth increased over time  while it decreased in the control group (Figure 5).
-Moreover, average everyday expertise declines in the control group over time while it remains constant in the treatment group (Figure 6).
-The divergence shown in both graphs suggests that funding for the Trips program might positively influence the selfworth and everyday expertise of participating children and adolescents.
-This evidence could support the hypothesis that the Trips program positively influences the beneficiaries.
-However, this graphical analysis is only descriptive and therefore cannot be interpreted as a causal relationship.
-
-\subsubsection{Differences-in-Differences Estimation}
-
-For the empirical analysis, we implement a differences-in-differences (DID) strategy to test whether the Trips program has a positive influence on the selfworth and everyday expertise of the supported children.
-The DID estimator measures the effect of participating in the Trips program by comparing the changes in dependent variables over time between the treatment and control group.
-The key identifying assumption for the DID strategy is the common trend assumption.
-The assumption states that, in the absence of the Trips program, both the treatment and control group would have evolved with the same trend meaning that the difference between the groups would have stayed the same.
-In case of a violation of the parallel trend assumption, the estimated treatment effect would be biased.
-As the dataset contains 2011 as the only year in the pre-period, we are not able to observe a pre-trend.
-Therefore, we cannot argue that the common trend assumption is fulfilled.
-
-Using the panel structure of the dataset we implement the DID estimation with the following regression equation:
-\begin{equation}
-\label{didregression}
-  Y_{it} = \alpha + \beta \cdot TreatEF_{it} + \gamma_{i} + \delta_{t} + \epsilon_{it}
-\end{equation}
-
-where $i$ indexes the identification number of each organization supported by CHILDREN and $t$ indexes the year of observation.
-The outcome variable, denoted by $Y_{it}$, is either selfworth or everyday expertise.
-As mentioned in the previous section, $TreatEF_{it}$ represents the treatment status of organization $i$ in year $t$.
-The corresponding regression coefficient $\beta$ represents the DiD estimator, which measures the average treatment effect of participating in the Trips program.
-
-The panel data set allows us to implement fixed effects.
-In our analysis we introduce individual fixed effects and time fixed effects.
-The ID fixed effects $\gamma_{i}$ control for organization specific observable and unobservable characteristics that are constant over time but differ across social institutions.
-For example, the state of an organization does not vary over time but might differ across supported social institutions.
-Additionally, the year fixed effects $\delta_{t}$ capture all variables that change across years but are the same for all organizations and within a specific year.
-For all following regression estimations, we use robust standard errors to take potential heteroscedasticity into account.
-
-One concern with our empirical approach is that the allocation to treatment and control group might not be perfectly randomized because the selection into the treatment could be driven by time-variant characteristics.
-Therefore, we include a set of control variables to deal with potential selection bias.
-For this, we select variables of the available dataset that might influence both the treatment status and either of the outcome variables.
-Furthermore, we control for organization specific characteristics which include the subsidy received for the Meals program, the corresponding total costs of providing meals and the number of days in a week on which children cook in a specific social institution.
-
-\subsection{Results}
-
-\subsubsection{Everyday Expertise}
-
-The estimated coefficients of equation 4 are represented in Table \ref{table:coefficients1} with everyday expertise as the dependent variable.
-Columns (1)-(2) report estimates using the first definition of the treatment variable, while columns (3)-(4) apply the second treatment specification.
-Columns (1) and (3) only include ID fixed effects and year fixed effects without any controls.
-Columns (2) and (4) expand the regression equation by adding the organization specific control variables: Subsidy, total costs and the number of days in a week on which children cook in a social institution.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-\\[-1.8ex]\hline
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
-                       & $(0.326)$ & $(0.405)$    & $(0.299)$ & $(0.310)$    \\
-subsidy                &           & $0.019$      &           & $0.016$      \\
-                       &           & $(0.014)$    &           & $(0.014)$    \\
-totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
-                       &           & $(0.000)$    &           & $(0.000)$    \\
-weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
-                       &           & $(0.072)$    &           & $(0.073)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$        & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation: Results for Everyday Expertise}
-\label{table:coefficients1}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in the text.
-The outcome variable is standardized.
-Below each coefficient the robust standard errors are reported in parentheses.}
-\end{table}
-
-Using the first definition of the treatment variable, the average treatment effect of participating in the Trips program on everyday expertise is negative, but not statistically significant.
-Therefore, the estimated coefficient in column (1) implies that the Trips program would not have a significant effect on everyday expertise of the supported children and adolescents.
-However, this negative estimate could result from the fact that we consider several organizations as treated even though they did not receive funding for the Trips program in a given year.
-As a result, the number of observation units in the control group is reduced so that the difference in size between the treatment and control group is considerably high.
-Therefore, this finding should not be overstated.
-On the other hand, using the alternative specification of the treatment indicator in column (3), the average treatment effect is positive, but remains insignificant.
-Thus, the sign of the estimated treatment effect changes if we use the alternative definition of the treatment variable.
-With the second treatment variable, the number of organizations in the control group increases, as the treatment status depends on actually receiving funding in a given year.
-Nevertheless, the difference in size of the treatment and control group remains relatively large.
-However, the estimate in Column (3) could provide evidence that the treatment effect might be positive and potentially turn significant if the sample size increases.
-
-Adding the organization specific control variables in Column (2) and Column (4) does not influence the size of both effects and the significance substantially.
-
-\subsubsection{Selfworth}
-
-Using selfworth as the outcome variable, the estimates of regression equation \ref{didregression} are reported in Table \ref{table:coefficients2}, whose structure is equal to Table \ref{table:coefficients1}.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-\\[-1.8ex]\hline
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
-                       & $(0.309)$ & $(0.312)$ & $(0.247)$ & $(0.256)$    \\
-subsidy                &           & $0.011$   &           & $0.014$      \\
-                       &           & $(0.018)$ &           & $(0.017)$    \\
-totalCost              &           & $0.000$   &           & $0.000$      \\
-                       &           & $(0.001)$ &           & $(0.001)$    \\
-weeklyCooks            &           & $0.036$   &           & $0.037$      \\
-                       &           & $(0.069)$ &           & $(0.069)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$     & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation: Results for Selfworth}
-\label{table:coefficients2}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in the text.
-The outcome variable is standardized.
-Below each coefficient the robust standard errors are reported in parentheses.}
-\end{table}
-
-Strikingly, all columns of Table \ref{table:coefficients2} report a negative treatment effect, regardless of the definition of the treatment variable or the inclusion of organization specific controls.
-In column (1)-(3), the average treatment effect is insignificant.
-However, the estimated effect is significant if we use the second specification of the treatment status and include controls in column (4).
-This indicates that participating in the Trips program would negatively influence the selfworth of the children and adolescents.
-This surprising result contradicts our hypothesis that the participation in the Trips program positively influences the selfworth of the beneficiaries.
-As previously mentioned, the number of observation units in both treatment and control group is relatively small.
-Therefore, this unexpected negative effect of the Trips program on selfworth should not be overstated.
-Moreover, another possible explanation for the observed results could be that the survey questions are answered by employees of an organization and not by the children and adolescents themselves.
-It might be difficult for the respondents of the survey to assess children specific characteristics, such as selfworth.
-During our visit in Augsburg, the employees confirmed that it is challenging to evaluate the variables asked in the survey for all participants in the entire social institution, especially with a lot of variation in attendance.
-One potential solution for this problem could be to directly ask the children and adolescents.
-Data on the individual level might be more precise because the children could assess themselves better.
-When using variables on the level of beneficiaries, we might observe a positive effect of the Trips program on selfworth.
-As reported in the summary statistics, the outcome variable shows a low variation.
-This results from the fact that, most of the time, organizations give the answer “all children” and “most children” when asked about the improvement of children’s selfworth.
-In general, it is more unlikely to find significant effects if the variation of the dependent variable is low.
-Therefore, one challenge for further analysis is to ask for variables that have a potentially higher variation.
-
-\section{Conclusion}
-
-Until now CHILDREN only influences whether organizations are supported and how much funding they receive to provide both the Trips and the Meals program.
-However, we find a strong positive correlation between the healthiness of the meals that organizations serve and health related outcomes of children and adolescents.
-During our visit of an organization in Augsburg, the employees told us that both the children and adolescents appreciate the healthy food and demand even more healthier meals.
-This might be one possible way for CHILDREN to improve the beneficiaries’ health without the necessity of spending particularly more money.
-In the yearly meetings, they could point out our results and mention their appreciation of the provision of healthy food.
-Moreover, CHILDREN could request that the organizations fulfill the DGE criteria for the provided meals.
-Due to the good relationship between CHILDREN and the supported social institutions, we think that the organizations are open to implementing this proposal.
-
-On the basis of the processed dataset, we cannot measure the causal effect of the Trips program on everyday expertise and selfworth of beneficiaries.
-However, measuring significant effects of CHILDREN’s Trips program might be possible if the data structure will be adjusted.
-At this point, we recommend to directly ask the beneficiaries to answer the children specific questions of the survey.
-During our first meeting with CHILDREN we were informed that they already have collected data from children and adolescents directly, that caused additional workload.
-For instance, the organizations need to obtain the permission of the parents.
-Nevertheless, the individual level data are perhaps more precise.
-
-The dataset contains several helpful features that made our analysis easier.
-For example, CHILDREN has asked for many survey questions from the supported organizations in every year across the whole observation period.
-Furthermore, the dataset includes variables regarding increased selfworth and broadened everyday expertise for both programs allowing a comparison of the meals and the Trips program.
-Hence, we recommend to continue asking the same questions in every year and selected variables for both programs.
-
-\printbibliography
-
-\section{Appendix}
-
-\subsection{A1: Expanded Health Regression}
-
-In addition to table \ref{HealthRegressions-LessIll}, table \ref{expandLessIll} presents the results of an OLS approach with scaled outcomes as well as a WLS approach with scaled outcomes with following control variables: to which extent an organization uses regional products, since when an organization is part of the Lunch program, the real subsidy per beneficiary and the state an organization is located.
-In comparison to the simple linear model, there are only small changes in coefficents.
-
-% <<eqaulity_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-% 
-% lm_s = readRDS("./ANALYSIS/Tables/selfworth.lm.Rds") #weighted
-% lm_d = readRDS("./ANALYSIS/Tables/dayToDaySkills.lm.Rds") #weighted
-% ts = readRDS("./ANALYSIS/Tables/selfworthTrips.lm.Rds")
-% td = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips.lm.Rds")
-% sI = readRDS("./ANALYSIS/Tables/selfworth_IM.lm.Rds") #weighted
-% dI = readRDS("./ANALYSIS/Tables/dayToDaySkills_IM.lm.Rds") #weighted
-% tsI = readRDS("./ANALYSIS/Tables/selfworthTrips_IM.lm.Rds")
-% tdI = readRDS("./ANALYSIS/Tables/dayToDaySkillsTrips_IM.lm.Rds")
-% @
-
-<<lessIll_extra_reg, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-#expanded model less ill
-
-lm_elDGE = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled.Rds")
-lm_elDGEw = readRDS("./ANALYSIS/Tables/Expand_LessIll_scaled_weighted.Rds")
-elDGE_i = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled.lm.Rds")
-elDGE_iw = readRDS("./ANALYSIS/Tables/Expand_LessIll_IM_scaled_weighted.lm.Rds")
-
-texreg(list(lm_elDGE, lm_elDGEw, elDGE_i, elDGE_iw), caption = "Regression Results: Less Ill Expanded Model", custom.model.names = c("OLS", "WLS", "OLS Impute","WLS Impute"), custom.note = "\\parbox{\\linewidth}
-{\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ regionalProducts: wether the organization offers meals with local ingredients or not \\\\ yearsSupportSince: the number of years an organization is already part of the Meals program \\\\ realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ state: german 'Bundeland' \\\\ Model (1): original data set, simple linear model with controls, estimated with OLS \\\\ Model (2): original data set, simple linear model with controls, estimated with WLS \\\\ Model (3): imputed data set, simple linear model with controls, estimated with OLS \\\\ Model (4): imputed data set, simple linear model with controls, estimated with WLS \\\\ All regressions are estimated with robust standard errors %stars.}", scalebox = 0.8, label = 'expandLessIll')
-@
-
-\subsection{A2: Cumulative Odds Regression}
-
-As an option to run a regression on the original ordinal variables, we use the proportional odds version of the cumulative logit. Equation \ref{PropoddsModel} describes the model setup:
-
-\begin{equation}
-\label{PropoddsModel}
-  P(Y_i \leq \ r) = \frac{exp(y_{0r} + x_i^Ty)}{1+exp(y_{0r} + x_i^Ty)}    
-\end{equation}
-
-To demonstrate the results of this method, we show in the tables \ref{lessIllOdds}, \ref{dietaryOdds}, \ref{appreciateOdds} the regressions of the health related variables on the healthy meals criterion and in the tables \ref{selfworthOdds} and \ref{dayToDayOdds} the regressions of the real meals subsidy on selfworth and everyday expertise.
-
-As an example of interpreting such models, we consider the model of table \ref{lessIllOdds}: An increase of the healthy meals criterion by 1 is associated with an increase in chances, that a proportion of a maximum of r beneficiaries is healthier in relation to that a proportion of more than r beneficiaries are healthier, by the factor of exp(-0.29127) = 0.75.
-
-A summary of the remaining models:
-
-\begin{itemize}
-  \item{Dietary Knowledge: exp(-0.089) = 0.91}
-  \item{Appreciate Healthy: exp(-0199) = 0.82}
-  \item{Selfworth: exp(-0.00001) = 1}
-  \item{Everyday Expertise: (-0.00003) = 1} 
-\end{itemize}
-
-<<lessIllOdds, echo=FALSE, results='asis', message=FALSE>>=
-
-lessIllOdds <- readRDS("./ANALYSIS/Tables/lessIllProp.Rds")
-
-stargazer(lessIllOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries Who Are Less Frequently Ill", align = TRUE, label = "lessIllOdds")
-
-@
-
-<<dietaryOdds, echo=FALSE, results='asis', message=FALSE>>=
-
-dietaryOdds <- readRDS("./ANALYSIS/Tables/DietaryProp.Rds")
-
-stargazer(dietaryOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and Share of Beneficiaries with Expanded Dietary Knowledge", align = TRUE, label = "dietaryOdds")
-@
-
-<<appreciateOdds, echo=FALSE, results='asis', message=FALSE>>=
-
-appreciateOdds <- readRDS("./ANALYSIS/Tables/AppreciateProp.Rds")
-
-stargazer(appreciateOdds@coef3, title= "Propodss Regression Results: Association of Index of Healthy Diet Criteria Fulfilled in Organization's Menu and the Share of Beneficiaries with Increased Appreciation for a Healthy Diet", align = TRUE, label = "appreciateOdds")
-
-@
-
-<<selfworthOdds, echo=FALSE, results='asis', message=FALSE>>=
-
-selfworthOdds <- readRDS("./ANALYSIS/Tables/selfworthProp.Rds")
-
-stargazer(selfworthOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals Program in 2015 EUR and the Share of Beneficiaries with Improved Self-worth", align = TRUE, label = "selfworthOdds")
-
-@
-
-<<dayToDayOdds, echo=FALSE, results='asis', message=FALSE>>=
-
-dayToDayOdds <- readRDS("./ANALYSIS/Tables/dayToDayProb.Rds")
-
-stargazer(dayToDayOdds@coef3, title= "Propodss Regression Results: Association of Subsidy for Meals program in 2015 EUR and the Share of Beneficiaries with Broadened Everyday Expertise", align = TRUE, label = "dayToDayOdds")
-
-@
-
-\subsection{A3: Partition}
-
-In addition to factor analysis, we have conducted another dimensionality reduction exercise called partition.
-This method is due to \textcite{Millstein.2020}.
-The authors propose it in the context of genome analysis, where high dimensionality is a perennnial statistical problem.
-
-Unlike exploratory factor analysis, the partition approach is deliberately designed to establish a one-to-one correspondence between the measured variables and presumed underlying variables.
-This means that the set of all variables is partitioned into subsets.
-A subset may contain only one variable.
-The deterministic partition algorithm is constructed in such a way as to ensure that there is a high correlation within subsets and a small correlation between.
-One can influence the number of subsets by manipulating a threshold limiting information loss.
-
-We use a threshold of 0.4, which means that the variables in each subset explain each other to at least 40 percent.
-It might be meaningful to decide to use only one of the featured variables in a reduced variable (or a summarizing one) for future surveys to avoid redundancy.
-
-Table \ref{partitionmeals} shows the obtained results of the partition method for the variables of the Lunch program.
-It displays 10 variables which have not been reduced, and 5 reduced variables with a number of featured variables.
-
-Table \ref{partitiontrips} does the same for the variables of the Trips program. Here, 12 variables have not been reduced, and a number of featured variables are summarized to 3 reduced variables.
-
-It is our impression that the partition technique results in a highly intuitive dimensionality reduction.
-
-\subsection{A4: DID Regression Results}
-
-The estimated coefficients of equation \ref{didregression} are represented in Table \ref{table:coefficients3} with everyday expertise as the dependent variable and in Table \ref{table:coefficients4} with selfworth as the dependent variable.
-P-values are in parentheses.
-We observe decreasing p-values when using the second definition of the treatment variable.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Everyday Expertise} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.010$  & $-0.166$     & $0.247$   & $0.255$      \\
-                       & $(0.975)$ & $(0.681)$    & $(0.409)$ & $(0.410)$    \\
-subsidy                &           & $0.019$      &           & $0.016$      \\
-                       &           & $(0.181)$    &           & $(0.258)$    \\
-totalCost              &           & $0.001^{**}$ &           & $0.001^{*}$  \\
-                       &           & $(0.048)$    &           & $(0.060)$    \\
-weeklyCooks            &           & $0.166^{**}$ &           & $0.162^{**}$ \\
-                       &           & $(0.022)$    &           & $(0.027)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$        & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation 1}
-\label{table:coefficients3}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in section 6.1.4.
-The outcome variable is standardized.
-Below each coefficient the p-values are reported in parentheses.}
-\end{table}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{l c c c c}
-& \multicolumn{4}{c}{\textit{Dependent variable:}} \\
-\cline{2-5}
-\\[-1.8ex] & \multicolumn{4}{c}{Selfworth} \\
-\hline
- & (1) & (2) & (3) & (4) \\
-\hline
-treatEF                & $-0.474$  & $-0.481$  & $-0.328$  & $-0.442^{*}$ \\
-                       & $(0.126)$ & $(0.125)$ & $(0.185)$ & $(0.085)$    \\
-subsidy                &           & $0.011$   &           & $0.014$      \\
-                       &           & $(0.540)$ &           & $(0.422)$    \\
-totalCost              &           & $0.000$   &           & $0.000$      \\
-                       &           & $(0.575)$ &           & $(0.446)$    \\
-weeklyCooks            &           & $0.036$   &           & $0.037$      \\
-                       &           & $(0.609)$ &           & $(0.591)$    \\
-\hline
-ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$     & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
-\hline
-\multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$; $^{**}p<0.05$; $^{*}p<0.1$}}
-\end{tabular}
-\caption{DID Estimation 2}
-\label{table:coefficients4}
-\end{center}
-\floatfoot{Notes: The Table reports OLS results.
-Observations are at the organization level.
-Full details of each control variable are provided in section 6.1.4.
-The outcome variable is standardized.
-Below each coefficient the p-values are reported in parentheses.}
-\end{table}
-
-% %\section{Division of tasks}
-% 
-% Data preparation, fundamental dynamics: everybody\\
-% Factor analysis, general regresions, partition, cumulative odds model: Laura Jepsen and Rafael Schütz\\
-% DiD estimations and time series: Laura Huber, Jonathan Kirschner, and Yannick Zurl
-% 
-% 
-% \section{Ehrenwörtliche Erklärung aller Teilnehmer}
-
-\subsection{A5: Placebo Tests}
-
-\begin{figure}
-  \caption{Trend of weekly cooks}
-  \label{figureWeeklyCooks}
-
-<<Weekly cooks, echo=FALSE>>=
-figureWeeklyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_weeklyCooks.Rds")
-print(figureWeeklyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to weekly cooks they offered.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-\begin{figure}
-  \caption{Trend of monthly cooks}
-  \label{figureMonthlyCooks}
-
-<<Monthly cooks, echo=FALSE>>=
-figureMonthlyCooks = readRDS("./ANALYSIS/GRAPHS/PAPER/plot_monthlyCooks.Rds")
-print(figureMonthlyCooks)
-@
-
-\floatfoot{Note: The x-axis represents the years from 2012 to 2018, the year 2011 is left out because the trips program starts in 2012.
-The y-axis represents the average answers from the organizations regarding to monthly cooks they offered.
-The time trend of the average answers of the organizations in the treatment group is characterised by the solid red line, the answers of the control group by the dotted blue line.
-Additionally, the linear trends of both groups are included as the straight lines.}
-\end{figure}
-
-<<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-
-# first, read in all Rds objects that you need
-
-partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
-partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
+partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.4.Rds")
+partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.4.Rds")
 

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar  2 19:45:07 2020
+## % Mon Mar  2 19:54:53 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 19:45:07 2020
+% Mon Mar  2 19:54:53 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 19:45:12 2020
+% Mon Mar  2 19:54:58 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
Update
resized all table and graphs translated all headlines

@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
+\usepackage[backend=biber, style=apa]{biblatex}
 % \usepackage{floatrow}
 \usepackage{booktabs}
+\usepackage[ngerman]{babel}
 % \usepackage{rotating}
@@
 
+\setbeamerfont{subsection in toc}{size=\tiny}
+
 \usecolortheme{crane}
@@
 
-\frame{\frametitle{Table of Contents}
+\frame[allowframebreaks]{\frametitle{Table of Contents}
 	\tableofcontents
@@
 
-\frame{\frametitle{List of Tables}
+\frame[allowframebreaks]{\frametitle{List of Tables}
 	\listoftables
@@
 
-\frame{\frametitle{List of Figures}
+\frame[allowframebreaks]{\frametitle{List of Figures}
 	\listoffigures
@@
 
-\section{Summary Statistics und Fundamentale Dynamiken}
-
 \section{Zusammenfassende Statistiken}
@@
                                 digits = c(0, 0, 1, 1, 0, 0),
-           caption = "Summary Statistics",
+           caption = "Zusammenfassende Statistiken",
            align = "lccccc",
           label = "fundamentalDynamics"
-          ), scalebox = '0.7')
+          ), scalebox = '0.5')
 
@@
 \begin{itemize}
-  \item{Darstellung der Entwicklung der Fördersummen über die Zeit: Zur besseren Vergleichbarkeit Berechung der realen Werte}
+  \item{Zur besseren Vergleichbarkeit der Fördersummen über die Zeit: Umrechnung in 2015 EUR}
   \item{Verwendung der Preisindizes des statistischen Bundesamtes}
   \item{Mittagstisch Fördersumme: Preisindex für Nahrungsmittel und alkoholfreie Getränke}
-  \item{Entdeckerfonds: Preisindex für Freizeit, Unterhaltung und Kultur}
-  \item{Unterscheidung zwischen den Gesamtsummen, dem Median und dem Median pro Begünstigtem}
+  \item{Entdeckerfonds Fördersumme: Preisindex für Freizeit, Unterhaltung und Kultur}
 \end{itemize}
@@
  \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
- \linebreak
- \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
- \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
+ \item<3-> Welche Variablen liegen zugrunde?
+ \item<4-> Variablenreduktion zur Bestimmung möglicher Kontrollen
 \end{itemize}
@@
 
-% \begin{frame}[fragile]
-% \frametitle{Dynamics}
-%  \begin{figure}
-%    \caption{Yearly dynamics of total grants in Meals and Trips program}
-%    \label{totalGrantsDyn}
-%  <<GrantTrend, echo=FALSE, message=FALSE>>=
-%  totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-%  print(totalGrantsDyn, scalebox = '0.25')
-%  @
-% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
-From left to right: Meals, Trips.
-From top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-% \end{figure}
-% \end{frame}
+\begin{frame}[fragile]
+\frametitle{Technisches Vorgehen}
+
+\begin{itemize}
+ \item<1-> Imputierter Datensatz 
+ \item<2-> Separate Faktoranalyse für jedes später zu schätzende Modell: Abhhängige Variable und Prädiktor ausgeschlossen
+ \item<3-> Jede Variable als Linearkombination von wenigen Faktoren
+ \item<4-> Schätzung an sich uneindeutig $\Rightarrow$ rotiere Faktoren so, dass orthogonal zueinander
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Beispiel Faktoranalyse Mittagstisch}
+<<Faktoranalyse-Beispiel, results='asis', echo=FALSE, message=FALSE>>=
+
+loadings_FA_lessIll_DGECriteriaNo = readRDS("./ANALYSIS/Tables/loadings_FA_lessIll_DGECriteriaNo.Rds")
+
+xtable(loadings_FA_lessIll_DGECriteriaNo,
+           caption = "Faktoranalyse Mittagstisch ohne 'seltener krank'",
+           align = "lcc",
+          label = "factor-analysis-example"
+          )
+# , scalebox = '0.7')
+@
+
+\end{frame}
 
@@
 \begin{itemize}
-\item Der realen Fördersumme die eine Organisation für den Mittagstisch erhält und der Anzahl der Essen die sie ausgibt
-\item Der realen Fördersumme die eine Organisation für den Entdeckerfonds erhält und der Anzahl der Ausflüge die sie unternimmt
-\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, deren Selbstwertgefühl gestiegen ist
-\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, die ihre Alltagskompetenzen erweitert haben
+\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
+\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
+\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
+\begin{itemize}
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
+\end{itemize}
 \end{itemize}
@@
 
-\subsection{Direkte Effekte von CHILDRENs Zuschüssen}
-
 \begin{frame}[fragile]
-\frametitle{Zusammenhang Mahlzeiten und Zuschüsse}
+\frametitle{Anzahl Mahlzeiten und Fördersumme}
 
@@
 \begin{frame}[fragile]
-\frametitle{Zusammenhang Ausflüge und Zuschüsse}
+\frametitle{Anzahl Ausflüge und Fördersumme}
 <<GrantsRegressionsTrips, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Association between number of trips and real subsidy", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(lm_ts, lm_ts_c, lm_ts_o, lm_ts_o_c, lm_ts_i), caption = "Zusammenhang zwischen Anzahl Ausflüge und Fördersumme", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)"), scalebox = 0.7, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: number of trips \\\\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\\\ tripsKidsNo: number of beneficiaries of Trips program \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, linear model with controls, estimated with OLS \\\\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\\\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\\\ Model (5): imputed data set, simple linear model, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'GrantsRegressionsTrips', digits = 4, booktabs = TRUE, use.packages=FALSE)
@@
 
-\subsection{Selbstwertgefühl, Alltagskompetenzen und Zuschüsse}
-
 \begin{frame}[fragile]
-\frametitle{Selbstwertgefühl}
+\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
 
@@
 
-texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Association between selfworth and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(ss, tss, ssI, tssI, sfactor), caption = "Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)" ), scalebox = 0.4, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\\\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'SelfworthRegressions', bookmarks = TRUE, use.packages=FALSE)
@@
 \begin{frame}[fragile]
-\frametitle{Alltagskompetenzen}
+\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
 
@@
 
-texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Association between everyday expertise and subsidy per beneficiary", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(ds, tds, dsI, tdsI, dfactorm, dfactort), caption = "Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem", custom.model.names = c("(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), scalebox = 0.4, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\\\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\\\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\\\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\\\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\\\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'DayToDaySkillsRegressions', bookmarks = TRUE, use.packages=FALSE)
@@
 \begin{frame}[fragile]
-\frametitle{Ergebnisse der Fördersumme}
+\frametitle{Zusammenfassung der Ergebnisse}
 
 \begin{itemize}
-\item Effekt auf Anzahl an Essen \& Ausflüge
-\begin{itemize}
-\item Mittagstisch: Circa 3 Euro mehr resultieren in einer Mahlzeit mehr
-\item Entdeckerfonds: kein klarer Zusammenhang 
-\end{itemize}
-\item Effekt auf das Selbstwertgefühl \& die Alltagskompetenzen 
-\begin{itemize}
-\item Nulleffekte bei beiden Variablen 
-\end{itemize}
+\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
+\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
+\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
 \end{itemize}
@@
 \begin{itemize}
-\item Dem standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählten standardisierten gesundheitsrelevanten Variablen
+\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
 \begin{itemize}
@@
 \item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
-\item Anteil an Begünstigten, die gesund Ernährung stärker wertschätzen
+\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
 \end{itemize}
+\item Schätzung mit WLS
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
+\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
 <<lessIllDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
+\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
 <<dietaryDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit DGE-Kriterium}
 <<appreciateDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Seltener krank}
+\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Association between healthy meals criterion and beneficiaries being less ill", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(lDGE, lDGEw, lDGE_i, lDGE_iw, illfactor), caption = "Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.65, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = "HealthRegressions-LessIll", bookmarks = TRUE, use.packages=FALSE)
@@
 \begin{frame}
-\frametitle{Ernährungswissen}
+\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Association between healthy meals criterion and beneficiaries dietary knowledge", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(dDGE, dDGEw, dDGE_i, dDGE_iw, dietaryf), caption = "Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.55, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-DietaryKnowledge', bookmarks = TRUE, use.packages=FALSE)
@@
 \begin{frame}[fragile]
-\frametitle{Wertschätzung für gesundes Essen}
+\frametitle{Variable 'Wertschätzung gesunder Ernährung': Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
@@
 
-texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.8, custom.note = "\\parbox{\\linewidth}
+texreg(list(aDGE, aDGEw, aDGE_i, aDGE_iw, appreciatef), caption = "Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'", custom.model.names = c("(1)", "(2)", "(3)","(4)", "(5)"), scalebox = 0.5, custom.note = "\\parbox{\\linewidth}
 {\\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\\\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\\\ Model (1): original data set, simple linear model, estimated with OLS \\\\ Model (2): original data set, simple linear model, estimated with WLS \\\\ Model (3): imputed data set, simple linear model, estimated with OLS \\\\ Model (4): imputed data set, simple linear model, estimated with WLS \\\\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\\\ All regressions are estimated with robust standard errors %stars.}", caption.above = TRUE, label = 'HealthRegressions-AppreciateHealthy')
@@
 
-\subsection{Empirische Fragestellungen (2): Ergebnisse}
-
 \begin{frame}
-\frametitle{Empirische Fragestellungen (2): }
+\frametitle{Zusammenfassung der Ergebnisse}
 
 \begin{itemize}
-\item Signifikante Effekte in Bezug auf den Zusammenhang des Kriteriums für gesundes Essen und gesundheitsrelevanten Variablen 
+\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
 \item Hinzunahme von extrahierten Faktoren als Kontrollen:
@@
 \item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
+\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": kein Zusammenhang mehr erkennbar
 \end{itemize}
@@
 
- xtable(partition_meals,
+ print(xtable(partition_meals,
                                 # digits = c(0, 0, 1, 1, 0, 0),
-           caption = "Partition of outcomes, Meals",
+           caption = "Partition der Zielvariablen, Mittagstisch",
            label = 'partitionmeals',
-           align = "lccc",
-           scalebox = "0.5"
-           )
+           align = "lccc"
+           ), scalebox = "0.4")
  #print(partition_meals, include.rownames = FALSE)
@@
 <<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-xtable(partition_trips,
+print(xtable(partition_trips,
                                #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition of outcomes, Trips",
+          caption = "Partition der Zielvariablen, Entdeckerfonds",
           label = 'partitiontrips',
-          align = "lccc",
-          scalebox = "0.5"
-          )
+          align = "lccc"
+          ),
+          scalebox = "0.5")
 # print(partition_meals, partition_trips, include.rownames = FALSE)

### 2020-03-02 presentation.tex
resized all table and graphs translated all headlines

--- 2020-03-02 presentation.tex
@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 20:08:58 2020
+## % Mon Mar 02 22:19:03 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 20:08:58 2020
+% Mon Mar 02 22:19:03 2020
 \begin{table}[ht]
 \centering
-\scalebox{0.7}{
+\scalebox{0.5}{
 \begin{tabular}{lccccc}
@@
 }
-\caption{Summary Statistics} 
+\caption{Zusammenfassende Statistiken} 
 \label{fundamentalDynamics}
@@
  \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
- \linebreak
- \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
- \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
-\end{itemize}
-
-\end{frame}
-
-% \begin{frame}[fragile]
-% \frametitle{Dynamics}
-%  \begin{figure}
-%    \caption{Yearly dynamics of total grants in Meals and Trips program}
-%    \label{totalGrantsDyn}
-%  <<GrantTrend, echo=FALSE, message=FALSE>>=
-%  totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
-%  print(totalGrantsDyn, scalebox = '0.25')
-%  @
-% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
-We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
-From left to right: Meals, Trips.
-From top to bottom: sum, median, median per beneficiary.
-We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
-% \end{figure}
-% \end{frame}
+ \item<3-> Welche Variablen liegen zugrunde?
+ \item<4-> Variablenreduktion zur Bestimmung möglicher Kontrollen
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Technisches Vorgehen}
+
+\begin{itemize}
+ \item<1-> Imputierter Datensatz 
+ \item<2-> Separate Faktoranalyse für jedes später zu schätzende Modell: Abhhängige Variable und Prädiktor ausgeschlossen
+ \item<3-> Jede Variable als Linearkombination von wenigen Faktoren
+ \item<4-> Schätzung an sich uneindeutig $\Rightarrow$ rotiere Faktoren so, dass orthogonal zueinander
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Beispiel Faktoranalyse Mittagstisch}
+% latex table generated in R 3.6.2 by xtable 1.8-4 package
+% Mon Mar 02 22:19:08 2020
+\begin{table}[ht]
+\centering
+\begin{tabular}{lcc}
+  \hline
+ & ML2 & ML1 \\ 
+  \hline
+participateMore\_scaled & 0.14 & 0.07 \\ 
+  monthlyCooks\_scaled & 0.22 & 0.79 \\ 
+  weeklyCooks\_scaled & 0.17 & 0.85 \\ 
+  shoppers\_scaled & 0.16 & 0.55 \\ 
+  easyDishes\_scaled & 0.47 & 0.44 \\ 
+  dietaryKnowledge\_scaled & 0.64 & 0.20 \\ 
+  appreciateHealthy\_scaled & 0.74 & 0.00 \\ 
+  foodCulture\_scaled & 0.56 & 0.14 \\ 
+  dayToDaySkills\_scaled & 0.57 & 0.34 \\ 
+  selfworth\_scaled & 0.54 & 0.26 \\ 
+  influenceHome\_scaled & 0.46 & 0.17 \\ 
+   \hline
+\end{tabular}
+\caption{Faktoranalyse Mittagstisch ohne 'seltener krank'} 
+\label{factor-analysis-example}
+\end{table}
+
+\end{frame}
 
@@
 \begin{itemize}
-\item Der realen Fördersumme die eine Organisation für den Mittagstisch erhält und der Anzahl der Essen die sie ausgibt
-\item Der realen Fördersumme die eine Organisation für den Entdeckerfonds erhält und der Anzahl der Ausflüge die sie unternimmt
-\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, deren Selbstwertgefühl gestiegen ist
-\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, die ihre Alltagskompetenzen erweitert haben
-\end{itemize}
-\end{frame}
-
-\subsection{Direkte Effekte von CHILDRENs Zuschüssen}
-
-\begin{frame}[fragile]
-\frametitle{Zusammenhang Mahlzeiten und Zuschüsse}
+\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
+\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
+\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
+\begin{itemize}
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Anzahl Mahlzeiten und Fördersumme}
 
@@
 \begin{frame}[fragile]
-\frametitle{Zusammenhang Ausflüge und Zuschüsse}
+\frametitle{Anzahl Ausflüge und Fördersumme}
 
 \begin{table}
-\caption{Association between number of trips and real subsidy}
+\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.7}{
 \begin{tabular}{l c c c c c }
@@
 
-\subsection{Selbstwertgefühl, Alltagskompetenzen und Zuschüsse}
-
-\begin{frame}[fragile]
-\frametitle{Selbstwertgefühl}
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
 
 \begin{table}
-\caption{Association between selfworth and subsidy per beneficiary}
+\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.4}{
 \begin{tabular}{l c c c c c }
@@
 \begin{frame}[fragile]
-\frametitle{Alltagskompetenzen}
+\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
 
 \begin{table}
-\caption{Association between everyday expertise and subsidy per beneficiary}
+\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.4}{
 \begin{tabular}{l c c c c c c }
@@
 \begin{frame}[fragile]
-\frametitle{Ergebnisse der Fördersumme}
-
-\begin{itemize}
-\item Effekt auf Anzahl an Essen \& Ausflüge
-\begin{itemize}
-\item Mittagstisch: Circa 3 Euro mehr resultieren in einer Mahlzeit mehr
-\item Entdeckerfonds: kein klarer Zusammenhang 
-\end{itemize}
-\item Effekt auf das Selbstwertgefühl \& die Alltagskompetenzen 
-\begin{itemize}
-\item Nulleffekte bei beiden Variablen 
-\end{itemize}
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
+\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
+\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
 \end{itemize}
@@
 \item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
-\item Anteil an Begünstigten, die gesund Ernährung stärker wertschätzen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
+\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
+\end{itemize}
+\item Schätzung mit WLS
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
+\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit DGE-Kriterium}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Seltener krank}
+\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
 
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries being less ill}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.65}{
 \begin{tabular}{l c c c c c }
@@
 \begin{frame}
-\frametitle{Ernährungswissen}
+\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
 
 \begin{table}
-\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.55}{
 \begin{tabular}{l c c c c c }
@@
 \begin{frame}[fragile]
-\frametitle{Wertschätzung für gesundes Essen}
+\frametitle{Variable 'Wertschätzung gesunder Ernährung': Zusammenhang mit DGE-Kriterium}
 
 \begin{table}
-\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
 \begin{center}
-\scalebox{0.8}{
+\scalebox{0.5}{
 \begin{tabular}{l c c c c c }
@@
 
-\subsection{Empirische Fragestellungen (2): Ergebnisse}
-
 \begin{frame}
-\frametitle{Empirische Fragestellungen (2): }
-
-\begin{itemize}
-\item Signifikante Effekte in Bezug auf den Zusammenhang des Kriteriums für gesundes Essen und gesundheitsrelevanten Variablen 
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
 \item Hinzunahme von extrahierten Faktoren als Kontrollen:
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 20:09:05 2020
+% Mon Mar 02 22:19:11 2020
 \begin{table}[ht]
 \centering
+\scalebox{0.4}{
 \begin{tabular}{lccc}
@@
 \end{tabular}
-\caption{Partition of outcomes, Meals} 
+}
+\caption{Partition der Zielvariablen, Mittagstisch} 
 \label{partitionmeals}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 20:09:05 2020
+% Mon Mar 02 22:19:11 2020
 \begin{table}[ht]
 \centering
+\scalebox{0.5}{
 \begin{tabular}{lccc}
@@
 \end{tabular}
-\caption{Partition of outcomes, Trips} 
+}
+\caption{Partition der Zielvariablen, Entdeckerfonds} 
 \label{partitiontrips}

### 2020-03-02 ANALYSIS/factor_analysis.R

@@ -101,6 +101,10 @@ scores_lessIll_DGECriteriaNo <- data.frame(FA_lessIll_DGECriteriaNo$scores)
 
 lessIll_DGECriteriaNo_Factors <- cbind.data.frame(scores_lessIll_DGECriteriaNo, lessIll_DGECriteriaNo)
 
+loadings_FA_lessIll_DGECriteriaNo <- data.frame((FA_lessIll_DGECriteriaNo$loadings)[1:11, 1:2])
+
+saveRDS(loadings_FA_lessIll_DGECriteriaNo, "./ANALYSIS/Tables/loadings_FA_lessIll_DGECriteriaNo.Rds")
+
 #factor analysis dietary knowledge_scaled vs DGECriteriaNoScaled
 
 dfFA_dietaryKnowledge_DGECriteriaNo <- dfFAMeals %>% 

### 2020-03-02 presentation.Rnw
Update

--- 2020-03-02 presentation.Rnw
@@
 	}
-\author[Laura, Laura, Jonathan, Rafael und Yannick]{
+\author[PaRE3To]{
 Laura Huber\\
@@
 	\tableofcontents
+
 }
 
-\frame{\frametitle{List of Tables}
-	\listoftables
-}
-
-\frame{\frametitle{List of Figures}
-	\listoffigures
-}
 \section{Einleitung}
@@
 \begin{itemize}
- \item<1-> Spendenfinanzierte Kinderhilfsorganisation
- \item<2-> Finanziert Einrichtungen deutschlandweit
+ \item Spendenfinanzierte Kinderhilfsorganisation
+ \item Finanziert Einrichtungen in ganz Deutschland
  \linebreak
- \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
- \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
+ \item CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
 \end{itemize}
@@
 \begin{itemize}
- \item<1-> Jährliche Umfragebögen an die Einrichtungen
- \item<2-> Beantwortung durch Mitarbeiter
- \item<3-> Verschiedene Fragen zu Mittagstisch und Entdeckerfonds
- \item<4-> Generelle Variablen (z.B. Fördersumme, Anzahl angebotener Mahlzeiten, Anzahl Aktivitäten)
- \item<5-> Abhängige Variablen (z.B. Selbstwertgefühl, seltener krank)
+ \item Jährliche Umfragebögen an die Einrichtungen
+ \item Beantwortung durch Mitarbeiter
+ \item Verschiedene Fragen zu Mittagstisch und Entdeckerfonds
+ \item Allgemeine Variablen zu den Einrichtungen (z.B. Fördersumme, Anzahl angebotener Mahlzeiten, Anzahl Aktivitäten)
+ \item Abhängige Variablen zu den Kindern (z.B. Selbstwertgefühl, seltener krank)
 \end{itemize}
@@
 \begin{itemize}
- \item<1-> Arbeit mit dem Statistik-Programm “R”
- \item<2-> Zusammenfügen der verschiedenen Datensätze
- \item<3-> Anpassung und Vergleich der Variablennamen
- \item<4-> Abstimmung des Teams über “Git”
+ \item Zusammenfügen der Datensätze aus den verschiedenen Jahren
+ \item Anpassung der Variablennamen und Hinzufügen von neuen Variablen
+ \item Änderung der Datentypen von Variablen
+ \item [$\Rightarrow$] Erstellung eines finalen Datensatzes
+ \linebreak
+ \item Datenauswertung mit dem Statistik-Programm “R”
+ \item Versionskontrolle über "Git"
 \end{itemize}
@@
 \frametitle{Beispiel: Datensatz}
-<<Datensatz, echo=FALSE, message=FALSE>>=
-
-Datensatz = readRDS("./ANALYSIS/GRAPHS/PAPER/dataExample.Rds")
-
-colnames(Datensatz) <- c("ID", "Jahr", "Anzahl der Kinder MT", "Selbstwertgefühl", "Ausflüge")
-
-print(xtable(Datensatz, include.rownames = FALSE,
-           caption = "Beispielhafter Datensatz",
-           align = "lccccc",
-          label = "Datensatz"
-          ), scalebox = '0.7')
-@
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+  \hline
+1 & 103 & 2014 & 30 & 3 & 4 \\ 
+  2 & 103 & 2015 & 50 & 3 & 6 \\ 
+  3 & 103 & 2016 & NA & 2 & 3 \\ 
+  4 & 112 & 2014 & 27 & 3 & NA \\ 
+  5 & 112 & 2015 & 55 & 3 & NA \\ 
+  6 & 112 & 2016 & 35 & 3 & NA \\ 
+   \hline
+\end{tabular}
+\caption{Beispielhafter Datensatz} 
+\end{table}
 \end{frame}
@@
 \item Welchen Effekt besitzt die Förderung einer sozialen Einrichtung durch den CHILDREN Entdeckerfonds auf die teilnehmenden Kinder und Jugendlichen?
-\item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmmen
+\item Herausforderung: Identifizieren einer geeigneten empirischen Methode, um die Wirkungseffekte des CHILDREN Entdeckerfonds zu bestimmen
 \linebreak
@@
 \item Treatmentgruppe: Alle Einrichtungen, die sowohl am CHILDREN Mittagstisch als auch am CHILDREN Entdeckerfonds teilnehmen
-\item Kontrollgruppe: Alle Einrichtungen, die nicht am CHILDREN Entdeckerfonds teilnehmen, sondern nur durch den CHILDREN Mittagtisch gefördert werden
+\item Kontrollgruppe: Alle Einrichtungen, die nicht am CHILDREN Entdeckerfonds teilnehmen, sondern nur durch den CHILDREN Mittagstisch gefördert werden
 \item Um die Einrichtungen in Treatment- und Kontrollgruppe einzuteilen, wurde analysiert, ob bei den Survey-Fragen zum Entdeckerfonds in einem bestimmten Jahr Angaben gemacht wurden
@@
 \item Problem: Keine Variablen zum Entdeckerfonds für Einrichtungen, die nicht am Entdeckerfonds teilgenommen haben (= Kontrollgruppe) 
-\item Verwendete Zielvariablen vom Mittagtisch: Alltagskompetenzen und Selbstwertgefühl
+\item Verwendete Zielvariablen vom Mittagstisch: Alltagskompetenzen und Selbstwertgefühl
 \item [$\Rightarrow$] Anwendbar auf den CHILDREN Mittagstisch und den CHILDREN Entdeckerfonds 
@@
 \begin{itemize}
-\item Zentrale Annahme des DID-Ansatzes:
+\item[ ] Zentrale Annahme des DID-Ansatzes:
 \item Commond Trend Assumption: Ohne den Entdeckerfonds würden sich die Zielvariablen in der Treatment- und Kontrollgruppe mit dem gleichen Trend entwickeln
 \linebreak
-\item Potentielle Probleme:
+\item[ ] Potentielle Probleme:
 \item Verletzung der Common Trend Assumption
@@
 \begin{center}
-\scalebox{0.9}{
+\scalebox{0.8}{
 \begin{tabular}{l c c c c }
@@
 \hline
+ID fixed effects       & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$     & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$     & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.484$   & $0.474$   & $0.485$      \\
+\hline
 \multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
@@
 \linebreak
-\item Mögliche Gründe:
+\item [ ] Mögliche Gründe:
 \item Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist gering
@@
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empfehlungen für CHILDREN}
+\begin{itemize}
+\item[a)] Datenstruktur und -erhebung:
+\item Kinder und Jugendliche direkt befragen
+\item Einheitliche Variablen, die jedes Jahr erfragt werden
+\item Elektronische Fragebögen und Datenerhebung
+\item[b)] Auswahl der Variablen:
 \end{itemize}

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
 	\tableofcontents
-}
-
-\frame{\frametitle{List of Tables}
-	\listoftables
-}
-
-\frame{\frametitle{List of Figures}
-	\listoffigures
-}
+
+}
+
 \section{Einleitung}
@@
 \frametitle{Beispiel: Datensatz}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{verbatim}
-## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 20:08:58 2020
-## \begin{table}[ht]
-## \centering
-## \scalebox{0.7}{
-## \begin{tabular}{lccccc}
-##   \hline
-##  & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
-##   \hline
-## 1 & 103.00 & 2014.00 & 30.00 & 3.00 & 4.00 \\ 
-##   2 & 103.00 & 2015.00 & 50.00 & 3.00 & 6.00 \\ 
-##   3 & 103.00 & 2016.00 &  & 2.00 & 3.00 \\ 
-##   4 & 112.00 & 2014.00 & 27.00 & 3.00 &  \\ 
-##   5 & 112.00 & 2015.00 & 55.00 & 3.00 &  \\ 
-##   6 & 112.00 & 2016.00 & 35.00 & 3.00 &  \\ 
-##   7 & 112.00 & 2018.00 & 36.00 & 2.00 &  \\ 
-##    \hline
-## \end{tabular}
-## }
-## \caption{Beispielhafter Datensatz} 
-## \label{Datensatz}
-## \end{table}
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+  \hline
+1 & 103 & 2014 & 30 & 3 & 4 \\ 
+  2 & 103 & 2015 & 50 & 3 & 6 \\ 
+  3 & 103 & 2016 & NA & 2 & 3 \\ 
+  4 & 112 & 2014 & 27 & 3 & NA \\ 
+  5 & 112 & 2015 & 55 & 3 & NA \\ 
+  6 & 112 & 2016 & 35 & 3 & NA \\ 
+   \hline
+\end{tabular}
+\caption{Beispielhafter Datensatz} 
+\end{table}
 \end{frame}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 20:08:58 2020
+% Mon Mar  2 22:27:47 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 20:09:05 2020
+% Mon Mar  2 22:27:52 2020
 \begin{table}[ht]
@@
 \linebreak
-\item Mögliche Gründe:
+\item [ ] Mögliche Gründe:
 \item Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist gering
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable führt zu geringerer Variation
+\item Die Skalierung der Zielvariable "Selbstwertgefühl" führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empfehlungen für CHILDREN}
+\begin{itemize}
+\item[a)] Datenstruktur und -erhebung:
+\item Kinder und Jugendliche direkt befragen
+\item Einheitliche Variablen, die jedes Jahr erfragt werden
+\item Elektronische Fragebögen und Datenerhebung
+\item[b)] Auswahl der Variablen:
 \end{itemize}

### 2020-03-02 presentation.Rnw
Update

--- 2020-03-02 presentation.Rnw
@@
 	\tableofcontents
+
 }
 
-\frame[allowframebreaks]{\frametitle{List of Tables}
-	\listoftables
-}
-
-\frame[allowframebreaks]{\frametitle{List of Figures}
-	\listoffigures
-}
 \section{Einleitung}
@@
 \begin{itemize}
- \item<1-> Arbeit mit dem Statistik-Programm “R”
- \item<2-> Zusammenfügen der verschiedenen Datensätze
- \item<3-> Anpassung und Vergleich der Variablennamen
- \item<4-> Abstimmung des Teams über “Git”
+ \item Zusammenfügen der Datensätze aus den verschiedenen Jahren
+ \item Anpassung der Variablennamen und Hinzufügen von neuen Variablen
+ \item Änderung der Datentypen von Variablen
+ \item [$\Rightarrow$] Erstellung eines finalen Datensatzes
+ \linebreak
+ \item Datenauswertung mit dem Statistik-Programm \glqq R\grqq
+ \item Versionskontrolle über \glqq Git\grqq
 \end{itemize}
@@
 \frametitle{Beispiel: Datensatz}
-<<Datensatz, echo=FALSE, message=FALSE>>=
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+  \hline
+1 & 103 & 2014 & 30 & 3 & 4 \\ 
+  2 & 103 & 2015 & 50 & 3 & 6 \\ 
+  3 & 103 & 2016 & NA & 2 & 3 \\ 
+  4 & 112 & 2014 & 27 & 3 & NA \\ 
+  5 & 112 & 2015 & 55 & 3 & NA \\ 
+  6 & 112 & 2016 & 35 & 3 & NA \\ 
+   \hline
+\end{tabular}
+\caption{Beispielhafter Datensatz} 
+\end{table}
+\end{frame}
 
-Datensatz = readRDS("./ANALYSIS/GRAPHS/PAPER/dataExample.Rds")
-
-colnames(Datensatz) <- c("ID", "Jahr", "Anzahl der Kinder MT", "Selbstwertgefühl", "Ausflüge")
-
-print(xtable(Datensatz, include.rownames = FALSE,
-           caption = "Beispielhafter Datensatz",
-           align = "lccccc",
-          label = "Datensatz"
-          ), scalebox = '0.7')
-@
-\end{frame}
+\section{Summary Statistics und Fundamentale Dynamiken}
 
@@
 \begin{frame}[fragile]
-\frametitle{Umrechnung der Fördersummen: reale Werte}
+\frametitle{Umrechnung der Fördersummen: Reale Werte}
 \begin{itemize}
@@
 \begin{itemize}
-\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
-\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": kein Zusammenhang mehr erkennbar
+\item Variable "seltener krank": Nach wie vor großer, statistisch signifikanter Koeffizient
+\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": Kein Zusammenhang mehr erkennbar
 \end{itemize}
@@
 \begin{itemize}
-\item "Einmal Treatment, immer Treatment"
+\item \glqq Einmal Treatment, immer Treatment\grqq
 \item Sobald eine Einrichtung am Entdeckerfonds teilgenommen hat, gilt $TreatEF_{it}$ = 1 für das Jahr der ersten Förderung durch den Entdeckerfonds und alle darauffolgenden Jahre
@@
 \linebreak
-\item Mögliche Gründe:
+\item [ ] Mögliche Gründe:
 \item Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist gering
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable "Selbstwertgefühl" führt zu geringer Variation
+\item Die Skalierung der Zielvariable \glqq Selbstwertgefühl\grqq{} führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empfehlungen für CHILDREN}
+\begin{itemize}
+\item[a)] Datenstruktur und -erhebung:
+\item Kinder und Jugendliche direkt befragen
+\item Einheitliche Variablen, die jedes Jahr erfragt werden
+\item Elektronische Fragebögen und Datenerhebung
+\item[b)] Auswahl der Variablen:
 \end{itemize}

### 2020-03-02 presentation.tex
Update

--- 2020-03-02 presentation.tex
@@
 	\tableofcontents
-}
-
-\frame[allowframebreaks]{\frametitle{List of Tables}
-	\listoftables
-}
-
-\frame[allowframebreaks]{\frametitle{List of Figures}
-	\listoffigures
-}
+
+}
+
 \section{Einleitung}
@@
 \frametitle{Beispiel: Datensatz}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
-\begin{verbatim}
-## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 22:19:03 2020
-## \begin{table}[ht]
-## \centering
-## \scalebox{0.7}{
-## \begin{tabular}{lccccc}
-##   \hline
-##  & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
-##   \hline
-## 1 & 103.00 & 2014.00 & 30.00 & 3.00 & 4.00 \\ 
-##   2 & 103.00 & 2015.00 & 50.00 & 3.00 & 6.00 \\ 
-##   3 & 103.00 & 2016.00 &  & 2.00 & 3.00 \\ 
-##   4 & 112.00 & 2014.00 & 27.00 & 3.00 &  \\ 
-##   5 & 112.00 & 2015.00 & 55.00 & 3.00 &  \\ 
-##   6 & 112.00 & 2016.00 & 35.00 & 3.00 &  \\ 
-##   7 & 112.00 & 2018.00 & 36.00 & 2.00 &  \\ 
-##    \hline
-## \end{tabular}
-## }
-## \caption{Beispielhafter Datensatz} 
-## \label{Datensatz}
-## \end{table}
-\end{verbatim}
-\end{kframe}
-\end{knitrout}
-\end{frame}
+\begin{table}[ht]
+\centering
+\begin{tabular}{lccccc}
+  \hline
+ & ID & Jahr & Anzahl der Kinder MT & Selbstwertgefühl & Ausflüge \\ 
+  \hline
+1 & 103 & 2014 & 30 & 3 & 4 \\ 
+  2 & 103 & 2015 & 50 & 3 & 6 \\ 
+  3 & 103 & 2016 & NA & 2 & 3 \\ 
+  4 & 112 & 2014 & 27 & 3 & NA \\ 
+  5 & 112 & 2015 & 55 & 3 & NA \\ 
+  6 & 112 & 2016 & 35 & 3 & NA \\ 
+   \hline
+\end{tabular}
+\caption{Beispielhafter Datensatz} 
+\end{table}
+\end{frame}
+
+\section{Summary Statistics und Fundamentale Dynamiken}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:03 2020
+% Mon Mar  2 23:16:47 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:08 2020
+% Mon Mar  2 23:16:50 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:11 2020
+% Mon Mar  2 23:16:51 2020
 \begin{table}[ht]

### 2020-03-02 presentation.Rnw
wdfv

--- 2020-03-02 presentation.Rnw
@@
 \usepackage[ngerman]{babel}
+\usepackage{csquotes}
 % \usepackage{rotating}
@@
 \usecolortheme{crane}
+
+\setbeamercolor{titlelike}{parent=structure, fg = black}
 
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Selbstwertgefühl": Dynamik}
+\frametitle{Variable \glqq Selbstwertgefühl\grqq: Dynamik}
 <<SelfworthTime, echo=FALSE, message=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Alltagskompetenzen": Dynamik}
+\frametitle{Variable \glqq Alltagskompetenzen\grqq: Dynamik}
 <<DayToDayTime, echo=FALSE, message=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "seltener krank": Dynamik}
+\frametitle{Variable \glqq seltener krank\grqq: Dynamik}
 <<lessIllTime, echo=FALSE, message=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "erweitertes Ernährungswissen": Dynamik}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Dynamik}
 <<dietaryTime, echo=FALSE, message=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Dynamik}
 <<appreciateTime, echo=FALSE, message=FALSE>>=
@@
  \item<1-> Viele Zielvariablen 
- \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
+ \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B.
+Begünstigte \glqq kochen mindestensts einmal im Monat in der Einrichtung\grqq und \glqq kochen mindestens einmal in der Woche in der Einrichtung\grqq
  \item<3-> Welche Variablen liegen zugrunde?
@@
 
-\section{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
+\section{Partition}
+\begin{frame}[fragile]
+\frametitle{Alternative zu Faktoranalyse?}
+\begin{itemize}
+\item<1-> Neue Methode aus Biostatistik zur Dimensionalitätsreduktion: Partition \parencite{Millstein.2020}
+\item<2-> Aufteilung der Menge aller Variablen in Gruppen
+\item<3-> Jeder Variable wird genau eine zugrundeliegende Variable zugewiesen
+\item<3-> In jeder Gruppe muss Intraklassen-Korrelationskoeffizient mindestens bestimmten, willkürlich festgelegten Wert annehmen
+\item<4-> Bestimmung der Gruppen durch deterministischen Nächste-Nachbarn-Algorithmus
+
+\end{itemize}
+\end{frame}
+
+ \begin{frame}[fragile]
+ \frametitle{Partition Mittagstisch}
+ <<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+
+ # first, read in all Rds objects that you need
+
+ partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
+ partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
+
+ colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
+ colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
+
+ print(xtable(partition_meals,
+                                # digits = c(0, 0, 1, 1, 0, 0),
+           caption = "Partition der Zielvariablen, Mittagstisch",
+           label = 'partitionmeals',
+           align = "lccc"
+           ), scalebox = "0.4")
+ #print(partition_meals, include.rownames = FALSE)
+ @
+
+ \end{frame}
+
+\begin{frame}
+\frametitle{Partition Entdeckerfonds}
+<<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
+print(xtable(partition_trips,
+                               #digits = c(0, 0, 1, 1, 0, 0),
+          caption = "Partition der Zielvariablen, Entdeckerfonds",
+          label = 'partitiontrips',
+          align = "lccc"
+          ),
+          scalebox = "0.5")
+# print(partition_meals, partition_trips, include.rownames = FALSE)
+@
+\end{frame}
+
+\section{Effekte des Entdeckerfonds}
+
+\section[Zusammenhänge]{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
 
@@
 \begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
-\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
+\item Werte, die 1,5 Interquantilsabstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1,5 Interqauntilsabstände über dem 75\%-Perzentil liegen
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
 <<lessIllDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
 <<dietaryDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
 <<appreciateDGEplot, echo=FALSE, message=FALSE, warning=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-LessIll, echo=FALSE, results='asis', message=FALSE>>=
@@
 \begin{frame}
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-DietaryKnowledge, echo=FALSE, results='asis', message=FALSE>>=
@@
 \begin{frame}[fragile]
-\frametitle{Variable 'Wertschätzung gesunder Ernährung': Zusammenhang mit DGE-Kriterium}
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
 <<HealthRegressions-AppreciateHealthy, echo=FALSE, results='asis', message=FALSE>>=
@@
 \begin{itemize}
-\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
-\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": kein Zusammenhang mehr erkennbar
+\item Variable \glqq seltener krank\grqq: nach wie vor großer, statistisch signifikanter Koeffizient
+\item Variablen \glqq erweitertes Ernährungswissen\grqq und \glqq Wertschätzung gesunder Ernährung\grqq: kein Zusammenhang mehr erkennbar
 \end{itemize}
@@
 \end{frame}
-
-\section{Partition}
-
- \begin{frame}[fragile]
- \frametitle{Partition Mittagstisch}
- <<Partition, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-
- # first, read in all Rds objects that you need
-
- partition_meals = readRDS("./ANALYSIS/Tables/PartitionMeals.Rds")
- partition_trips = readRDS("./ANALYSIS/Tables/PartitionTrips.Rds")
-
- colnames(partition_meals) <- c("Variable, Meals", "Mapping, Meals", "Information, Meals")
- colnames(partition_trips) <- c("Variable, Trips", "Mapping, Trips", "Information, Trips")
-
- print(xtable(partition_meals,
-                                # digits = c(0, 0, 1, 1, 0, 0),
-           caption = "Partition der Zielvariablen, Mittagstisch",
-           label = 'partitionmeals',
-           align = "lccc"
-           ), scalebox = "0.4")
- #print(partition_meals, include.rownames = FALSE)
- @
-
- \end{frame}
-
-\begin{frame}
-\frametitle{Partition Entdeckerfonds}
-<<PartitionTrips, echo=FALSE, results='asis', message=FALSE, warning=FALSE>>=
-print(xtable(partition_trips,
-                               #digits = c(0, 0, 1, 1, 0, 0),
-          caption = "Partition der Zielvariablen, Entdeckerfonds",
-          label = 'partitiontrips',
-          align = "lccc"
-          ),
-          scalebox = "0.5")
-# print(partition_meals, partition_trips, include.rownames = FALSE)
-@
-\end{frame}
-
-\section{Effekte des Entdeckerfonds}
 
@@
 \hline
-ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
-Number of observations & $428$     & $410$        & $428$     & $410$        \\
-R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
-\hline
 \multicolumn{5}{l}{\scriptsize{$^{***}p<0.01$, $^{**}p<0.05$, $^*p<0.1$}}
@@
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable "Selbstwertgefühl" führt zu geringer Variation
+\item Die Skalierung der Zielvariable \glqq Selbstwertgefühl\grqq führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Statistisches Lob für CHILDREN}
+\begin{itemize}
+\item<1-> Erfassung vieler Variablen über die ganze Zeit
+\item<2-> Unveränderte Datenskala (alle bis keine)
+\item<3-> Erfassung von zwei Variablen sowohl bei Mittagstisch als auch bei Entdeckerfonds
+\item<4-> Fragebogen wird automatisch ausgefüllt $\Rightarrow$ wenige fehlende Werte
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Empfehlungen für CHILDREN}
+\begin{itemize}
+\item[a)] Datenstruktur:
+\item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 
+\item[c)] Datenerhebung: Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
+\item[d)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
 \end{itemize}

### 2020-03-02 presentation.tex
wdfv

--- 2020-03-02 presentation.tex
@@
 
+\setbeamercolor{titlelike}{parent=structure, fg = black}
+
 \addbibresource{references.bib}
@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 22:19:03 2020
+## % Mon Mar 02 23:17:27 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:03 2020
+% Mon Mar 02 23:17:27 2020
 \begin{table}[ht]
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Selbstwertgefühl": Dynamik}
+\frametitle{Variable \glqq Selbstwertgefühl\grqq: Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Alltagskompetenzen": Dynamik}
+\frametitle{Variable \glqq Alltagskompetenzen\grqq: Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "seltener krank": Dynamik}
+\frametitle{Variable \glqq seltener krank\grqq: Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "erweitertes Ernährungswissen": Dynamik}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Dynamik}
 \begin{knitrout}\footnotesize
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:08 2020
+% Mon Mar 02 23:17:32 2020
 \begin{table}[ht]
@@
 
-\section{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
-
-\subsection{Empirischer Ansatz}
-
-\begin{frame}
-\frametitle{Empirischer Ansatz}
-
-\begin{equation}
-\label{SimpleLinearModel}
-  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
-\end{equation}
-
-\begin{itemize}
-\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
-\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
-\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
-\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Imputieren fehlender Werte}
-\begin{itemize}
-\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
-\begin{itemize}
-\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
-\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
-\end{itemize}
-\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Ausschließen von Ausreißern}
-\begin{itemize}
-\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
-\item Lösung: Datensätze ohne Ausreißer
-\item Mittagstisch: Ausreißer bei Anzahl von Essen
-\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
-\item Definition eines Ausreißers:
-\begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
-\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
-
-\begin{frame}[fragile]
-\frametitle{Assoziationen zwischen:}
-\begin{itemize}
-\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
-\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
-\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
-\begin{itemize}
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Mahlzeiten und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
-                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
-realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
-                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
-eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
-                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
-\midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
-$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsLunch}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Ausflüge und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
-\begin{center}
-\scalebox{0.7}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
-                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
-realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
-                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
-tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
-                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
-\midrule
-R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
-Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
-RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsTrips}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
-                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              \\
-ML1                            &          &          &          &          & $0.24^{***}$ \\
-                               &          &          &          &          & $(0.06)$     \\
-ML2                            &          &          &          &          & $0.37^{***}$ \\
-                               &          &          &          &          & $(0.05)$     \\
-ML3                            &          &          &          &          & $0.15^{***}$ \\
-                               &          &          &          &          & $(0.04)$     \\
-\hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
-Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{SelfworthRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) & (6) \\
-\hline
-(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
-                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
-ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
-                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
-ML4                            &          &          &          &          &              & $0.49^{***}$ \\
-                               &          &          &          &          &              & $(0.06)$     \\
-\hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
-Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
-\hline
-\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{DayToDaySkillsRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
-\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
-\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
-\end{itemize}
-
-\end{frame}
-
-\subsection{Gesundheit}
-
-\begin{frame}[fragile]
-\frametitle{Fragestellungen, Assoziationen zwischen:}
-\begin{itemize}
-\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
-\begin{itemize}
-\item Anteil an Begünstigten, die seltener krank sind
-\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
-\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
-\end{itemize}
-\item Schätzung mit WLS
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
-\begin{center}
-\scalebox{0.65}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
-ML1                 &              &             &              &              & $0.12^{*}$   \\
-                    &              &             &              &              & $(0.06)$     \\
-ML2                 &              &             &              &              & $0.27^{***}$ \\
-                    &              &             &              &              & $(0.06)$     \\
-\hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
-Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-LessIll}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
-\begin{center}
-\scalebox{0.55}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
-                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
-DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
-                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
-ML1                 &          &          &            &          & $0.26^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML2                 &          &          &            &          & $0.24^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML3                 &          &          &            &          & $0.37^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-\hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
-Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-DietaryKnowledge}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'Wertschätzung gesunder Ernährung': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
-                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
-DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
-                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
-ML1                 &              &          &              &            & $0.03$       \\
-                    &              &          &              &            & $(0.07)$     \\
-ML2                 &              &          &              &            & $0.47^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-ML3                 &              &          &              &            & $0.24^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-\hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
-Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-AppreciateHealthy}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
-\item Hinzunahme von extrahierten Faktoren als Kontrollen:
-\begin{itemize}
-\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
-\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": kein Zusammenhang mehr erkennbar
-\end{itemize}
-\end{itemize}
-\end{frame}
-
 \section{Partition}
+\begin{frame}[fragile]
+\frametitle{Alternative zu Faktoranalyse?}
+\begin{itemize}
+\item<1-> Neue Methode aus Biostatistik zur Dimensionalitätsreduktion: Partition \parencite{Millstein.2020}
+\item<2-> Aufteilung der Menge aller Variablen in Gruppen
+\item<3-> Jeder Variable wird genau eine zugrundeliegende Variable zugewiesen
+\item<3-> In jeder Gruppe muss Intraklassen-Korrelationskoeffizient mindestens bestimmten, willkürlich festgelegten Wert annehmen
+\item<4-> Bestimmung der Gruppen durch deterministischen Nächste-Nachbarn-Algorithmus
+
+\end{itemize}
+\end{frame}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 22:19:11 2020
+% Mon Mar 02 23:17:32 2020
 \begin{table}[ht]
@@
 
+\section[Zusammenhänge]{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
+
+\subsection{Empirischer Ansatz}
+
+\begin{frame}
+\frametitle{Empirischer Ansatz}
+
+\begin{equation}
+\label{SimpleLinearModel}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+\begin{itemize}
+\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
+\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
+\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
+\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Imputieren fehlender Werte}
+\begin{itemize}
+\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
+\begin{itemize}
+\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
+\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
+\end{itemize}
+\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Ausschließen von Ausreißern}
+\begin{itemize}
+\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
+\item Lösung: Datensätze ohne Ausreißer
+\item Mittagstisch: Ausreißer bei Anzahl von Essen
+\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
+\item Definition eines Ausreißers:
+\begin{itemize}
+\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Assoziationen zwischen:}
+\begin{itemize}
+\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
+\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
+\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
+\begin{itemize}
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Anzahl Mahlzeiten und Fördersumme}
+
+\begin{table}
+\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
+                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
+realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
+                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
+eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
+                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
+\midrule
+R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
+Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
+Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
+RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
+$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Anzahl Ausflüge und Fördersumme}
+
+\begin{table}
+\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
+\begin{center}
+\scalebox{0.7}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
+                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
+\midrule
+R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
+Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
+RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsTrips}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
+
+\begin{table}
+\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
+\begin{center}
+\scalebox{0.4}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              \\
+ML1                            &          &          &          &          & $0.24^{***}$ \\
+                               &          &          &          &          & $(0.06)$     \\
+ML2                            &          &          &          &          & $0.37^{***}$ \\
+                               &          &          &          &          & $(0.05)$     \\
+ML3                            &          &          &          &          & $0.15^{***}$ \\
+                               &          &          &          &          & $(0.04)$     \\
+\hline
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{SelfworthRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
+
+\begin{table}
+\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
+\begin{center}
+\scalebox{0.4}{
+\begin{tabular}{l c c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) & (6) \\
+\hline
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
+ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
+                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
+ML4                            &          &          &          &          &              & $0.49^{***}$ \\
+                               &          &          &          &          &              & $(0.06)$     \\
+\hline
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{DayToDaySkillsRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
+\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
+\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
+\end{itemize}
+
+\end{frame}
+
+\subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Fragestellungen, Assoziationen zwischen:}
+\begin{itemize}
+\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
+\begin{itemize}
+\item Anteil an Begünstigten, die seltener krank sind
+\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
+\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
+\end{itemize}
+\item Schätzung mit WLS
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
+\begin{center}
+\scalebox{0.65}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
+ML1                 &              &             &              &              & $0.12^{*}$   \\
+                    &              &             &              &              & $(0.06)$     \\
+ML2                 &              &             &              &              & $0.27^{***}$ \\
+                    &              &             &              &              & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-LessIll}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
+\begin{center}
+\scalebox{0.55}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
+ML1                 &          &          &            &          & $0.26^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML2                 &          &          &            &          & $0.24^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML3                 &          &          &            &          & $0.37^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-DietaryKnowledge}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
+ML1                 &              &          &              &            & $0.03$       \\
+                    &              &          &              &            & $(0.07)$     \\
+ML2                 &              &          &              &            & $0.47^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+ML3                 &              &          &              &            & $0.24^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-AppreciateHealthy}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
+\item Hinzunahme von extrahierten Faktoren als Kontrollen:
+\begin{itemize}
+\item Variable \glqq seltener krank\grqq: nach wie vor großer, statistisch signifikanter Koeffizient
+\item Variablen \glqq erweitertes Ernährungswissen\grqq und \grqq Wertschätzung gesunder Ernährung\glqq: kein Zusammenhang mehr erkennbar
+\end{itemize}
+\end{itemize}
+\end{frame}
+
 \subsection{Idee}

### 2020-03-02 presentation.Rnw

@@
 \begin{itemize}
+
 \item Variable \glqq seltener krank\grqq: nach wie vor großer, statistisch signifikanter Koeffizient
@@
             &           & $(0.072)$    &           & $(0.073)$    \\
+\hline
+ID fixed effects       & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Year fixed effects     & $Yes$     & $Yes$        & $Yes$     & $Yes$        \\
+Number of observations & $428$     & $410$        & $428$     & $410$        \\
+R$^2$                  & $0.475$   & $0.490$      & $0.476$   & $0.491$      \\
 \hline
@@
 \linebreak
-\item Mögliche Gründe:
+\item [ ] Mögliche Gründe:
 \item Die Anzahl der Beobachtungseinheiten in der Kontrollgruppe ist gering
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable \glqq Selbstwertgefühl\grqq führt zu geringer Variation
+\item Die Skalierung der Zielvariable \glqq Selbstwertgefühl\grqq{} führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
@@
 \begin{itemize}
-\item[a)] Datenstruktur:
+\item[a)] Datenstruktur und -erhebung:
+\item Kinder und Jugendliche direkt befragen
+\item Einheitliche Variablen, die jedes Jahr erfragt werden
+\item Elektronische Fragebögen und Datenerhebung
 \item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 

### 2020-03-02 presentation.tex
ghjklö

--- 2020-03-02 presentation.tex
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 23:16:47 2020
+% Mon Mar 02 23:53:11 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 23:16:50 2020
+% Mon Mar 02 23:53:16 2020
 \begin{table}[ht]
@@
 
-\section{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
-
-\subsection{Empirischer Ansatz}
-
-\begin{frame}
-\frametitle{Empirischer Ansatz}
-
-\begin{equation}
-\label{SimpleLinearModel}
-  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
-\end{equation}
-
-\begin{itemize}
-\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
-\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
-\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
-\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Imputieren fehlender Werte}
-\begin{itemize}
-\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
-\begin{itemize}
-\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
-\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
-\end{itemize}
-\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Ausschließen von Ausreißern}
-\begin{itemize}
-\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
-\item Lösung: Datensätze ohne Ausreißer
-\item Mittagstisch: Ausreißer bei Anzahl von Essen
-\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
-\item Definition eines Ausreißers:
-\begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
-\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
-
-\begin{frame}[fragile]
-\frametitle{Assoziationen zwischen:}
-\begin{itemize}
-\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
-\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
-\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
-\begin{itemize}
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Mahlzeiten und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
-                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
-realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
-                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
-eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
-                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
-\midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
-$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsLunch}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Ausflüge und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
-\begin{center}
-\scalebox{0.7}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
-                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
-realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
-                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
-tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
-                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
-\midrule
-R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
-Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
-RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsTrips}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
-                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              \\
-ML1                            &          &          &          &          & $0.24^{***}$ \\
-                               &          &          &          &          & $(0.06)$     \\
-ML2                            &          &          &          &          & $0.37^{***}$ \\
-                               &          &          &          &          & $(0.05)$     \\
-ML3                            &          &          &          &          & $0.15^{***}$ \\
-                               &          &          &          &          & $(0.04)$     \\
-\hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
-Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{SelfworthRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) & (6) \\
-\hline
-(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
-                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
-ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
-                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
-ML4                            &          &          &          &          &              & $0.49^{***}$ \\
-                               &          &          &          &          &              & $(0.06)$     \\
-\hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
-Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
-\hline
-\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{DayToDaySkillsRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
-\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
-\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
-\end{itemize}
-
-\end{frame}
-
-\subsection{Gesundheit}
-
-\begin{frame}[fragile]
-\frametitle{Fragestellungen, Assoziationen zwischen:}
-\begin{itemize}
-\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
-\begin{itemize}
-\item Anteil an Begünstigten, die seltener krank sind
-\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
-\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
-\end{itemize}
-\item Schätzung mit WLS
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'seltener krank': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
-\begin{center}
-\scalebox{0.65}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
-ML1                 &              &             &              &              & $0.12^{*}$   \\
-                    &              &             &              &              & $(0.06)$     \\
-ML2                 &              &             &              &              & $0.27^{***}$ \\
-                    &              &             &              &              & $(0.06)$     \\
-\hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
-Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-LessIll}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Variable 'erweitertes Ernährungswissen': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
-\begin{center}
-\scalebox{0.55}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
-                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
-DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
-                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
-ML1                 &          &          &            &          & $0.26^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML2                 &          &          &            &          & $0.24^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML3                 &          &          &            &          & $0.37^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-\hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
-Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-DietaryKnowledge}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable 'Wertschätzung gesunder Ernährung': Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
-                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
-DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
-                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
-ML1                 &              &          &              &            & $0.03$       \\
-                    &              &          &              &            & $(0.07)$     \\
-ML2                 &              &          &              &            & $0.47^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-ML3                 &              &          &              &            & $0.24^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-\hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
-Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-AppreciateHealthy}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
-\item Hinzunahme von extrahierten Faktoren als Kontrollen:
-\begin{itemize}
-\item Variable "seltener krank": Nach wie vor großer, statistisch signifikanter Koeffizient
-\item Variablen "erweitertes Ernährungswissen" und "Wertschätzung gesunder Ernährung": Kein Zusammenhang mehr erkennbar
-\end{itemize}
-\end{itemize}
-\end{frame}
-
 \section{Partition}
+
+\begin{frame}[fragile]
+\frametitle{Alternative zu Faktoranalyse?}
+\begin{itemize}
+\item<1-> Neue Methode aus Biostatistik zur Dimensionalitätsreduktion: Partition \parencite{Millstein.2020}
+\item<2-> Aufteilung der Menge aller Variablen in Gruppen
+\item<3-> Jeder Variable wird genau eine zugrundeliegende Variable zugewiesen
+\item<3-> In jeder Gruppe muss Intraklassen-Korrelationskoeffizient mindestens bestimmten, willkürlich festgelegten Wert annehmen
+\item<4-> Bestimmung der Gruppen durch deterministischen Nächste-Nachbarn-Algorithmus
+
+\end{itemize}
+\end{frame}
 
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar  2 23:16:51 2020
+% Mon Mar 02 23:53:16 2020
 \begin{table}[ht]
@@
 
+\section[Zusammenhänge]{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
+
+\subsection{Empirischer Ansatz}
+
+\begin{frame}
+\frametitle{Empirischer Ansatz}
+
+\begin{equation}
+\label{SimpleLinearModel}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+\begin{itemize}
+\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
+\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
+\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
+\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Imputieren fehlender Werte}
+\begin{itemize}
+\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
+\begin{itemize}
+\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
+\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
+\end{itemize}
+\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Ausschließen von Ausreißern}
+\begin{itemize}
+\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
+\item Lösung: Datensätze ohne Ausreißer
+\item Mittagstisch: Ausreißer bei Anzahl von Essen
+\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
+\item Definition eines Ausreißers:
+\begin{itemize}
+\item Werte, die 1,5 Interquantilsabstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1,5 Interqauntilsabstände über dem 75\%-Perzentil liegen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Assoziationen zwischen:}
+\begin{itemize}
+\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
+\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
+\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
+\begin{itemize}
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
+\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Anzahl Mahlzeiten und Fördersumme}
+
+\begin{table}
+\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
+                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
+realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
+                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
+eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
+                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
+\midrule
+R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
+Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
+Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
+RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
+$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Anzahl Ausflüge und Fördersumme}
+
+\begin{table}
+\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
+\begin{center}
+\scalebox{0.7}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
+                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
+\midrule
+R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
+Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
+RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsTrips}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
+
+\begin{table}
+\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
+\begin{center}
+\scalebox{0.4}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              \\
+ML1                            &          &          &          &          & $0.24^{***}$ \\
+                               &          &          &          &          & $(0.06)$     \\
+ML2                            &          &          &          &          & $0.37^{***}$ \\
+                               &          &          &          &          & $(0.05)$     \\
+ML3                            &          &          &          &          & $0.15^{***}$ \\
+                               &          &          &          &          & $(0.04)$     \\
+\hline
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{SelfworthRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
+
+\begin{table}
+\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
+\begin{center}
+\scalebox{0.4}{
+\begin{tabular}{l c c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) & (6) \\
+\hline
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
+ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
+                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
+ML4                            &          &          &          &          &              & $0.49^{***}$ \\
+                               &          &          &          &          &              & $(0.06)$     \\
+\hline
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{DayToDaySkillsRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
+\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
+\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
+\end{itemize}
+
+\end{frame}
+
+\subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Fragestellungen, Assoziationen zwischen:}
+\begin{itemize}
+\item Standardisiertes Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
+\begin{itemize}
+\item Anteil an Begünstigten, die seltener krank sind
+\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
+\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
+\end{itemize}
+\item Schätzung mit WLS
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
+\begin{center}
+\scalebox{0.65}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
+ML1                 &              &             &              &              & $0.12^{*}$   \\
+                    &              &             &              &              & $(0.06)$     \\
+ML2                 &              &             &              &              & $0.27^{***}$ \\
+                    &              &             &              &              & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-LessIll}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
+\begin{center}
+\scalebox{0.55}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
+ML1                 &          &          &            &          & $0.26^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML2                 &          &          &            &          & $0.24^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML3                 &          &          &            &          & $0.37^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-DietaryKnowledge}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
+
+\begin{table}
+\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
+ML1                 &              &          &              &            & $0.03$       \\
+                    &              &          &              &            & $(0.07)$     \\
+ML2                 &              &          &              &            & $0.47^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+ML3                 &              &          &              &            & $0.24^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-AppreciateHealthy}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Zusammenfassung der Ergebnisse}
+
+\begin{itemize}
+\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
+\item Hinzunahme von extrahierten Faktoren als Kontrollen:
+\begin{itemize}
+
+\item Variable \glqq seltener krank\grqq: nach wie vor großer, statistisch signifikanter Koeffizient
+\item Variablen \glqq erweitertes Ernährungswissen\grqq und \glqq Wertschätzung gesunder Ernährung\grqq: kein Zusammenhang mehr erkennbar
+\end{itemize}
+\end{itemize}
+\end{frame}
+
 \section{Effekte des Entdeckerfonds}
@@
 \begin{itemize}
-\item $\gamma_{i}$ = Einrichtung Fixed Effects, $\delta_{t}$ = Year Fixed Effects
+\item $\gamma_{i}$ = Einrichtungs-Fixed Effects, $\delta_{t}$ = Jahr-Fixed Effects
 \item Der Regressionskoeffizient $\beta$ entspricht dem DID-Schätzer
@@
 
+\begin{frame}
+\frametitle{Statistisches Lob für CHILDREN}
+\begin{itemize}
+\item<1-> Erfassung vieler Variablen über die ganze Zeit
+\item<2-> Unveränderte Datenskala (alle bis keine)
+\item<3-> Erfassung von zwei Variablen sowohl bei Mittagstisch als auch bei Entdeckerfonds
+\item<4-> Fragebogen wird automatisch ausgefüllt $\Rightarrow$ wenige fehlende Werte
+\end{itemize}
+\end{frame}
+
 \begin{frame}[fragile]
@@
 \item Elektronische Fragebögen und Datenerhebung
-\item[b)] Auswahl der Variablen:
+\item Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
+\item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 
+\item[c)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
 \end{itemize}
@@
 
+\begin{frame}
+
+Danke für die Zusammenarbeit!
+
+\end{frame}
+
 \end{document}

### 2020-03-03 presentation.tex
Update

@@
 
+\section{Summary Statistics und Fundamentale Dynamiken}
+
 \section{Zusammenfassende Statistiken}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:53:11 2020
+% Mon Mar  2 23:28:59 2020
 \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:53:16 2020
+% Mon Mar  2 23:29:02 2020
 \begin{table}[ht]
@@
 \section{Partition}
-
 \begin{frame}[fragile]
@@
 \end{frame}
+
+\section{Effekte des Entdeckerfonds}
 
@@
 \begin{itemize}
-\item Standardisiertes Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
+\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
 \begin{itemize}
@@
 
-\section{Effekte des Entdeckerfonds}
-
 \subsection{Idee}
@@
 \begin{itemize}
-\item $\gamma_{i}$ = Einrichtungs-Fixed Effects, $\delta_{t}$ = Jahr-Fixed Effects
+\item $\gamma_{i}$ = Einrichtung Fixed Effects, $\delta_{t}$ = Year Fixed Effects
 \item Der Regressionskoeffizient $\beta$ entspricht dem DID-Schätzer
@@
 \item Elektronische Fragebögen und Datenerhebung
-\item Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
 \item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 
-\item[c)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
+\item[c)] Datenerhebung: Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
+\item[d)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
 \end{itemize}
@@
 
-\begin{frame}
-
-Danke für die Zusammenarbeit!
-
-\end{frame}
-
 \end{document}

### 2020-03-03 presentation.tex
notes presentation

--- 2020-03-02 presentation.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage[backend=biber, style=apa]{biblatex}
+\usepackage[backend=biber, bibstyle=apa, citestyle=authoryear]{biblatex}
 % \usepackage{floatrow}
 \usepackage{booktabs}
-\usepackage[ngerman]{babel}
-\usepackage{csquotes}
 % \usepackage{rotating}
@@
 
-\setbeamerfont{subsection in toc}{size=\tiny}
-
 \usecolortheme{crane}
-
-\setbeamercolor{titlelike}{parent=structure, fg = black}
 
@@
 
-\frame[allowframebreaks]{\frametitle{Table of Contents}
+\frame{\frametitle{Table of Contents}
 	\tableofcontents
@@
 
-\frame[allowframebreaks]{\frametitle{List of Tables}
+\frame{\frametitle{List of Tables}
 	\listoftables
@@
 
-\frame[allowframebreaks]{\frametitle{List of Figures}
+\frame{\frametitle{List of Figures}
 	\listoffigures
@@
 ## % latex table generated in R 3.6.2 by xtable 1.8-4 package
-## % Mon Mar 02 23:17:27 2020
+## % Mon Mar 02 20:11:52 2020
 ## \begin{table}[ht]
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:17:27 2020
+% Mon Mar 02 20:11:53 2020
 \begin{table}[ht]
 \centering
-\scalebox{0.5}{
+\scalebox{0.7}{
 \begin{tabular}{lccccc}
@@
 }
-\caption{Zusammenfassende Statistiken} 
+\caption{Summary Statistics} 
 \label{fundamentalDynamics}
@@
 \begin{itemize}
-  \item{Zur besseren Vergleichbarkeit der Fördersummen über die Zeit: Umrechnung in 2015 EUR}
+  \item{Darstellung der Entwicklung der Fördersummen über die Zeit: Zur besseren Vergleichbarkeit Berechung der realen Werte}
   \item{Verwendung der Preisindizes des statistischen Bundesamtes}
   \item{Mittagstisch Fördersumme: Preisindex für Nahrungsmittel und alkoholfreie Getränke}
-  \item{Entdeckerfonds Fördersumme: Preisindex für Freizeit, Unterhaltung und Kultur}
+  \item{Entdeckerfonds: Preisindex für Freizeit, Unterhaltung und Kultur}
+  \item{Unterscheidung zwischen den Gesamtsummen, dem Median und dem Median pro Begünstigtem}
 \end{itemize}
@@
 \begin{frame}[fragile]
-\frametitle{Variable \glqq Selbstwertgefühl\grqq: Dynamik}
+\frametitle{Variable "Selbstwertgefühl": Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable \glqq Alltagskompetenzen\grqq: Dynamik}
+\frametitle{Variable "Alltagskompetenzen": Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable \glqq seltener krank\grqq: Dynamik}
+\frametitle{Variable "seltener krank": Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Dynamik}
+\frametitle{Variable "erweitertes Ernährungswissen": Dynamik}
 \begin{knitrout}\footnotesize
@@
 \begin{frame}[fragile]
-\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Dynamik}
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Dynamik}
 \begin{knitrout}\footnotesize
@@
  \item<1-> Viele Zielvariablen 
- \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B.
-Begünstigte \glqq kochen mindestensts einmal im Monat in der Einrichtung\grqq und \glqq kochen mindestens einmal in der Woche in der Einrichtung\grqq
- \item<3-> Welche Variablen liegen zugrunde?
- \item<4-> Variablenreduktion zur Bestimmung möglicher Kontrollen
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Technisches Vorgehen}
-
-\begin{itemize}
- \item<1-> Imputierter Datensatz 
- \item<2-> Separate Faktoranalyse für jedes später zu schätzende Modell: Abhhängige Variable und Prädiktor ausgeschlossen
- \item<3-> Jede Variable als Linearkombination von wenigen Faktoren
- \item<4-> Schätzung an sich uneindeutig $\Rightarrow$ rotiere Faktoren so, dass orthogonal zueinander
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Beispiel Faktoranalyse Mittagstisch}
+ \item<2-> Teilweise sehr ähnliche Zielvariablen, z.B. Begünstigte "kochen mindestensts einmal im Monat in der Einrichtung" und "kochen mindestens einmal in der Woche in der Einrichtung"
+ \linebreak
+ \item<3-> CHILDREN Mittagstisch: Bereitstellung von Mahlzeiten, um eine ausgewogene und gesunde Ernährung der Kinder und Jugendlichen zu fördern
+ \item<4-> CHILDREN Entdeckerfonds: Durch Ausflüge und Aktivitäten wird es Kindern und Jugendlichen ermöglicht, neue Erfahrungen zu sammeln
+\end{itemize}
+
+\end{frame}
+
+% \begin{frame}[fragile]
+% \frametitle{Dynamics}
+%  \begin{figure}
+%    \caption{Yearly dynamics of total grants in Meals and Trips program}
+%    \label{totalGrantsDyn}
+%  <<GrantTrend, echo=FALSE, message=FALSE>>=
+%  totalGrantsDyn = readRDS("./ANALYSIS/GRAPHS/PAPER/summaryStatistics_Subsidy.Rds")
+%  print(totalGrantsDyn, scalebox = '0.25')
+%  @
+% % \floatfoot{This graph shows the development of grants in the Meals compared to the Trips program.
+We distinguish between the sum of grants in one year, the median grant and the median grant per beneficiary.
+From left to right: Meals, Trips.
+From top to bottom: sum, median, median per beneficiary.
+We have deflated the values to 2015 euros using the price index related to food and non-alcoholic beverages(in German: Nahrungsmittel und alkoholfreie Getränke) for the Meals program and the price index related to Leisure, Entertainment and Culture (in German: Freizeit, Unterhaltung, Kultur) provided by the Federal Statistical Office of Germany (Statistisches Bundesamt).}
+% \end{figure}
+% \end{frame}
+
+\section{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
+
+\subsection{Empirischer Ansatz}
+
+\begin{frame}
+\frametitle{Empirischer Ansatz}
+
+\begin{equation}
+\label{SimpleLinearModel}
+  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
+\end{equation}
+
+\begin{itemize}
+\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
+\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
+\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
+\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
+\end{itemize}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Imputieren fehlender Werte}
+\begin{itemize}
+\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
+\begin{itemize}
+\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
+\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
+\end{itemize}
+\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variante: Ausschließen von Ausreißern}
+\begin{itemize}
+\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
+\item Lösung: Datensätze ohne Ausreißer
+\item Mittagstisch: Ausreißer bei Anzahl von Essen
+\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
+\item Definition eines Ausreißers:
+\begin{itemize}
+\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
+\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
+
+\begin{frame}[fragile]
+\frametitle{Assoziationen zwischen:}
+\begin{itemize}
+\item Der realen Fördersumme die eine Organisation für den Mittagstisch erhält und der Anzahl der Essen die sie ausgibt
+\item Der realen Fördersumme die eine Organisation für den Entdeckerfonds erhält und der Anzahl der Ausflüge die sie unternimmt
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, deren Selbstwertgefühl gestiegen ist
+\item Der realen Fördersumme pro Begünstigtem und dem standardisierten Anteil der Begünstigten, die ihre Alltagskompetenzen erweitert haben
+\end{itemize}
+\end{frame}
+
+\subsection{Direkte Effekte von CHILDRENs Zuschüssen}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Mahlzeiten und Zuschüsse}
+
+\begin{table}
+\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
+\begin{center}
+\scalebox{0.5}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
+                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
+realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
+                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
+eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
+                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
+\midrule
+R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
+Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
+Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
+RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
+$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsLunch}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Zusammenhang Ausflüge und Zuschüsse}
+
+\begin{table}
+\caption{Association between number of trips and real subsidy}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\toprule
+ & (1) & (2) & (3) & (4) & (5) \\
+\midrule
+(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
+                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
+realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
+                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
+tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
+                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
+\midrule
+R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
+Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
+Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
+RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
+\bottomrule
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{GrantsRegressionsTrips}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\subsection{Selbstwertgefühl, Alltagskompetenzen und Zuschüsse}
+
+\begin{frame}[fragile]
+\frametitle{Selbstwertgefühl}
+
+\begin{table}
+\caption{Association between selfworth and subsidy per beneficiary}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
+                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              \\
+ML1                            &          &          &          &          & $0.24^{***}$ \\
+                               &          &          &          &          & $(0.06)$     \\
+ML2                            &          &          &          &          & $0.37^{***}$ \\
+                               &          &          &          &          & $(0.05)$     \\
+ML3                            &          &          &          &          & $0.15^{***}$ \\
+                               &          &          &          &          & $(0.04)$     \\
+\hline
+R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
+Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
+Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
+RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{SelfworthRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Alltagskompetenzen}
+
+\begin{table}
+\caption{Association between everyday expertise and subsidy per beneficiary}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) & (6) \\
+\hline
+(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
+                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
+realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
+                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
+realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
+                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
+ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
+                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
+ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
+                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
+ML4                            &          &          &          &          &              & $0.49^{***}$ \\
+                               &          &          &          &          &              & $(0.06)$     \\
+\hline
+R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
+Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
+Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
+RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
+\hline
+\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{DayToDaySkillsRegressions}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Ergebnisse der Fördersumme}
+
+\begin{itemize}
+\item Effekt auf Anzahl an Essen \& Ausflüge
+\begin{itemize}
+\item Mittagstisch: Circa 3 Euro mehr resultieren in einer Mahlzeit mehr
+\item Entdeckerfonds: kein klarer Zusammenhang 
+\end{itemize}
+\item Effekt auf das Selbstwertgefühl \& die Alltagskompetenzen 
+\begin{itemize}
+\item Nulleffekte bei beiden Variablen 
+\end{itemize}
+\end{itemize}
+
+\end{frame}
+
+\subsection{Gesundheit}
+
+\begin{frame}[fragile]
+\frametitle{Fragestellungen, Assoziationen zwischen:}
+\begin{itemize}
+\item Dem standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählten standardisierten gesundheitsrelevanten Variablen
+\begin{itemize}
+\item Anteil an Begünstigten, die seltener krank sind
+\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
+\item Anteil an Begünstigten, die gesund Ernährung stärker wertschätzen
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "seltener krank": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "erweitertes Ernährungswissen": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Variable "Wertschätzung gesunder Ernährung": Zusammenhang mit dem DGE-Kriterium}
+\begin{knitrout}\footnotesize
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
+
+{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
+
+}
+
+\end{knitrout}
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Seltener krank}
+
+\begin{table}
+\caption{Association between healthy meals criterion and beneficiaries being less ill}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
+DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
+                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
+ML1                 &              &             &              &              & $0.12^{*}$   \\
+                    &              &             &              &              & $(0.06)$     \\
+ML2                 &              &             &              &              & $0.27^{***}$ \\
+                    &              &             &              &              & $(0.06)$     \\
+\hline
+R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
+Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
+Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
+RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-LessIll}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Ernährungswissen}
+
+\begin{table}
+\caption{Association between healthy meals criterion and beneficiaries dietary knowledge}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
+                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
+DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
+                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
+ML1                 &          &          &            &          & $0.26^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML2                 &          &          &            &          & $0.24^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+ML3                 &          &          &            &          & $0.37^{***}$ \\
+                    &          &          &            &          & $(0.06)$     \\
+\hline
+R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
+Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
+Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
+RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-DietaryKnowledge}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}[fragile]
+\frametitle{Wertschätzung für gesundes Essen}
+
+\begin{table}
+\caption{Association between healthy meals criterion and  beneficiaries appreciation of a healthy diet}
+\begin{center}
+\scalebox{0.8}{
+\begin{tabular}{l c c c c c }
+\hline
+ & (1) & (2) & (3) & (4) & (5) \\
+\hline
+(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
+                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
+DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
+                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
+ML1                 &              &          &              &            & $0.03$       \\
+                    &              &          &              &            & $(0.07)$     \\
+ML2                 &              &          &              &            & $0.47^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+ML3                 &              &          &              &            & $0.24^{***}$ \\
+                    &              &          &              &            & $(0.05)$     \\
+\hline
+R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
+Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
+Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
+RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
+\hline
+\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
+{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
+\end{tabular}
+}
+\label{HealthRegressions-AppreciateHealthy}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\subsection{Empirische Fragestellungen (2): Ergebnisse}
+
+\begin{frame}
+\frametitle{Empirische Fragestellungen (2): }
+
+\begin{itemize}
+\item Signifikante Effekte in Bezug auf den Zusammenhang des Kriteriums für gesundes Essen und gesundheitsrelevanten Variablen 
+\item Hinzunahme von extrahierten Faktoren als Kontrollen:
+\begin{itemize}
+\item Variable "seltener krank": nach wie vor großer, statistisch signifikanter Koeffizient
+\end{itemize}
+\end{itemize}
+\end{frame}
+
+\section{Partition}
+
+ \begin{frame}[fragile]
+ \frametitle{Partition Mittagstisch}
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:17:32 2020
+% Mon Mar 02 20:12:04 2020
 \begin{table}[ht]
 \centering
-\begin{tabular}{lcc}
-  \hline
- & ML2 & ML1 \\ 
-  \hline
-participateMore\_scaled & 0.14 & 0.07 \\ 
-  monthlyCooks\_scaled & 0.22 & 0.79 \\ 
-  weeklyCooks\_scaled & 0.17 & 0.85 \\ 
-  shoppers\_scaled & 0.16 & 0.55 \\ 
-  easyDishes\_scaled & 0.47 & 0.44 \\ 
-  dietaryKnowledge\_scaled & 0.64 & 0.20 \\ 
-  appreciateHealthy\_scaled & 0.74 & 0.00 \\ 
-  foodCulture\_scaled & 0.56 & 0.14 \\ 
-  dayToDaySkills\_scaled & 0.57 & 0.34 \\ 
-  selfworth\_scaled & 0.54 & 0.26 \\ 
-  influenceHome\_scaled & 0.46 & 0.17 \\ 
-   \hline
-\end{tabular}
-\caption{Faktoranalyse Mittagstisch ohne 'seltener krank'} 
-\label{factor-analysis-example}
-\end{table}
-
-\end{frame}
-
-\section{Partition}
-\begin{frame}[fragile]
-\frametitle{Alternative zu Faktoranalyse?}
-\begin{itemize}
-\item<1-> Neue Methode aus Biostatistik zur Dimensionalitätsreduktion: Partition \parencite{Millstein.2020}
-\item<2-> Aufteilung der Menge aller Variablen in Gruppen
-\item<3-> Jeder Variable wird genau eine zugrundeliegende Variable zugewiesen
-\item<3-> In jeder Gruppe muss Intraklassen-Korrelationskoeffizient mindestens bestimmten, willkürlich festgelegten Wert annehmen
-\item<4-> Bestimmung der Gruppen durch deterministischen Nächste-Nachbarn-Algorithmus
-
-\end{itemize}
-\end{frame}
-
- \begin{frame}[fragile]
- \frametitle{Partition Mittagstisch}
-% latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:17:32 2020
-\begin{table}[ht]
-\centering
-\scalebox{0.4}{
 \begin{tabular}{lccc}
@@
 \end{tabular}
-}
-\caption{Partition der Zielvariablen, Mittagstisch} 
+\caption{Partition of outcomes, Meals} 
 \label{partitionmeals}
@@
 % latex table generated in R 3.6.2 by xtable 1.8-4 package
-% Mon Mar 02 23:17:32 2020
+% Mon Mar 02 20:12:04 2020
 \begin{table}[ht]
 \centering
-\scalebox{0.5}{
 \begin{tabular}{lccc}
@@
 \end{tabular}
-}
-\caption{Partition der Zielvariablen, Entdeckerfonds} 
+\caption{Partition of outcomes, Trips} 
 \label{partitiontrips}
@@
 \section{Effekte des Entdeckerfonds}
-
-\section[Zusammenhänge]{Zusammenhänge zwischen CHILDRENs Zuschüssen, dem DGE-Kriterium und ausgewählten Variablen}
-
-\subsection{Empirischer Ansatz}
-
-\begin{frame}
-\frametitle{Empirischer Ansatz}
-
-\begin{equation}
-\label{SimpleLinearModel}
-  y_{it} = \beta_0 + \beta_1 x_{it} + \epsilon_{it}
-\end{equation}
-
-\begin{itemize}
-\item Schätzung der Modelle mit OLS (Methode der kleinsten Quadrate)
-\item Problem: Einrichtungen werden gleich gewichtet, unabhängig von Größe
-\item Lösung: Modellschätzung mit WLS (Gewichtete kleinste Quadrate)
-\item [$\Rightarrow$] Gewichte: Anzahl der regelmäßigen Teilnehmer am Mittagstisch und im Entdeckerfonds
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Imputieren fehlender Werte}
-\begin{itemize}
-\item Problem: Viele Einrichtungen beantworten nicht alle Fragen
-\begin{itemize}
-\item Lösung: Erstellung eines seperaten Datensatzes in welchem fehlende Werte imputiert werden
-\item [$\Rightarrow$] Imputieren der Daten mit einrichtungs-spezifischem linearen Trend
-\end{itemize}
-\item Vergleich von Regressionen mit den Daten des originalen Datenatzes mit den imputierten Daten
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variante: Ausschließen von Ausreißern}
-\begin{itemize}
-\item Problem: CHILDREN fördert Einrichtungen mit sehr vielen und sehr wenigen ausgegebenen Essen und unternommenen Ausflügen
-\item Lösung: Datensätze ohne Ausreißer
-\item Mittagstisch: Ausreißer bei Anzahl von Essen
-\item Entdeckerfonds: Ausreißer bei Anzahl von Ausflügen
-\item Definition eines Ausreißers:
-\begin{itemize}
-\item Werte, die 1.5 Interquantilsäbstände unter dem 25\%-Perzentil liegen
-\item Werte, die 1.5 Interqauntilsabstände über dem 75\%-Perzentil liegen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\subsection{Assoziationen zwischen Fördersumme und ausgewählten Variablen}
-
-\begin{frame}[fragile]
-\frametitle{Assoziationen zwischen:}
-\begin{itemize}
-\item Fördersumme für Mittagstisch (in 2015 EUR) und Anzahl ausgegebener Essen
-\item Fördersumme für Entdeckerfonds (in 2015 EUR) und Anzahl unternommener Ausflüge
-\item Sowohl für Mittagstisch als auch für Entdeckerfonds:
-\begin{itemize}
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit gestiegenen Selbstwertgefühl
-\item Fördersumme pro Begünstigter (in 2015 EUR) und standardisierter Anteil der Begünstigten mit erweiterten Alltagskompetenzen
-\end{itemize}
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Mahlzeiten und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl der Mahlzeiten und realer Fördersumme}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)     & $-12089.14^{*}$ & $-1814.16$     & $3535.39^{***}$ & $3107.70^{***}$ & $-12250.60^{**}$ \\
-                & $(5192.86)$     & $(1765.93)$    & $(498.99)$      & $(508.94)$      & $(4524.09)$      \\
-realSubsidy     & $2.61^{***}$    & $0.50^{**}$    & $0.29^{***}$    & $0.25^{***}$    & $2.72^{***}$     \\
-                & $(0.57)$        & $(0.18)$       & $(0.05)$        & $(0.05)$        & $(0.51)$         \\
-eatersPerMealNo &                 & $172.83^{***}$ &                 & $19.00^{*}$     &                  \\
-                &                 & $(14.92)$      &                 & $(8.45)$        &                  \\
-\midrule
-R$^2$           & 0.43            & 0.73           & 0.13            & 0.21            & 0.45             \\
-Adj. R$^2$      & 0.43            & 0.73           & 0.12            & 0.20            & 0.45             \\
-Num. obs.       & 329             & 329            & 250             & 250             & 440              \\
-RMSE            & 39992.79        & 27390.90       & 3629.72         & 3463.66         & 39601.41         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Abhängige Variable: Anzahl der Mahlzeiten \\ realSubsidy: Fördersumme für Mittagstisch (EUR von 2015)\\ eatersPerMeal: Anzahl der durch Mittagtisch Begünstigten \\ Modell (1): einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (2): ursprünglicher Datensatz, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinsten Quadrate \\ Modell (3): Datensatz ohne Ausreißer, einfaches lineares Modell, geschätzt mit Methode der kleinsten Quadrate \\ Modell (4): Datensatz ohne Ausreißer, lineares Modell mit Kontrollen, geschätzt mit Methode der kleinesten Quadrate \\ Modell (5): Datensatz mit durch lineare Interpolation pro Einrichtung imputierten Daten, einfaches lineare Modell, geschätzt mit Methode der kleinsten Quadrate  \\ Alle Standardfehler sind robust.
-$^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsLunch}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Anzahl Ausflüge und Fördersumme}
-
-\begin{table}
-\caption{Zusammenhang zwischen Anzahl Ausflüge und Fördersumme}
-\begin{center}
-\scalebox{0.7}{
-\begin{tabular}{l c c c c c }
-\toprule
- & (1) & (2) & (3) & (4) & (5) \\
-\midrule
-(Intercept)      & $3.7049^{***}$ & $3.4394^{***}$ & $2.6236^{***}$ & $2.3660^{***}$ & $3.6237^{***}$ \\
-                 & $(0.3313)$     & $(0.3359)$     & $(0.2300)$     & $(0.2609)$     & $(0.3253)$     \\
-realTripsSubsidy & $0.0002^{*}$   & $0.0001$       & $0.0003^{***}$ & $0.0003^{***}$ & $0.0002^{*}$   \\
-                 & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     & $(0.0001)$     \\
-tripsKidsNo      &                & $0.0059$       &                & $0.0043$       &                \\
-                 &                & $(0.0032)$     &                & $(0.0027)$     &                \\
-\midrule
-R$^2$            & 0.0474         & 0.0729         & 0.0880         & 0.1241         & 0.0504         \\
-Adj. R$^2$       & 0.0444         & 0.0671         & 0.0844         & 0.1172         & 0.0476         \\
-Num. obs.        & 322            & 319            & 257            & 256            & 334            \\
-RMSE             & 2.9565         & 2.8967         & 1.6981         & 1.6579         & 2.9310         \\
-\bottomrule
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: number of trips \\ realTripsSubsidy: subsidy for Trips program in 2015 EUR \\ tripsKidsNo: number of beneficiaries of Trips program \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, linear model with controls, estimated with OLS \\ Model (3): data set without outliers, simple linear model, esmitaed with OLS \\ Model (4): data set without outliers, linear model with controls, estimated with OLS \\ Model (5): imputed data set, simple linear model, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{GrantsRegressionsTrips}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Selbstwertgefühl und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Selbstwertgefühl und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)                    & $0.08$   & $0.12$   & $0.09$   & $0.12$   & $0.23^{*}$   \\
-                               & $(0.09)$ & $(0.12)$ & $(0.09)$ & $(0.11)$ & $(0.11)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              \\
-ML1                            &          &          &          &          & $0.24^{***}$ \\
-                               &          &          &          &          & $(0.06)$     \\
-ML2                            &          &          &          &          & $0.37^{***}$ \\
-                               &          &          &          &          & $(0.05)$     \\
-ML3                            &          &          &          &          & $0.15^{***}$ \\
-                               &          &          &          &          & $(0.04)$     \\
-\hline
-R$^2$                          & 0.00     & 0.01     & 0.00     & 0.01     & 0.30         \\
-Adj. R$^2$                     & 0.00     & 0.01     & 0.00     & 0.01     & 0.28         \\
-Num. obs.                      & 428      & 184      & 430      & 187      & 161          \\
-RMSE                           & 1.00     & 1.00     & 1.00     & 1.00     & 0.79         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\Model (1): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with improved self-worth in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with improved self-worth in the Trips program, imputed data set, simple linear model, estimated with OLS \\ Model (5): dependent variable: share of beneficiaries with improved self-worth in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{SelfworthRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Alltagskompetenzen und Fördersumme pro Begünstigter}
-
-\begin{table}
-\caption{Zusammenhang zwischen Alltagskompetenzen und Fördersumme pro Begünstigtem}
-\begin{center}
-\scalebox{0.4}{
-\begin{tabular}{l c c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) & (6) \\
-\hline
-(Intercept)                    & $0.15$   & $0.13$   & $0.14$   & $0.11$   & $0.28^{*}$   & $0.08$       \\
-                               & $(0.09)$ & $(0.10)$ & $(0.09)$ & $(0.10)$ & $(0.11)$     & $(0.09)$     \\
-realSubsidyPerBeneficiary      & $-0.00$  &          & $-0.00$  &          & $-0.00$      &              \\
-                               & $(0.00)$ &          & $(0.00)$ &          & $(0.00)$     &              \\
-realTripsSubsidyPerBeneficiary &          & $-0.00$  &          & $-0.00$  &              & $-0.00$      \\
-                               &          & $(0.00)$ &          & $(0.00)$ &              & $(0.00)$     \\
-ML1                            &          &          &          &          & $0.31^{***}$ & $0.03$       \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML2                            &          &          &          &          & $0.40^{***}$ & $0.16^{*}$   \\
-                               &          &          &          &          & $(0.06)$     & $(0.07)$     \\
-ML3                            &          &          &          &          & $0.16^{**}$  & $0.19^{**}$  \\
-                               &          &          &          &          & $(0.05)$     & $(0.06)$     \\
-ML4                            &          &          &          &          &              & $0.49^{***}$ \\
-                               &          &          &          &          &              & $(0.06)$     \\
-\hline
-R$^2$                          & 0.01     & 0.01     & 0.01     & 0.01     & 0.37         & 0.37         \\
-Adj. R$^2$                     & 0.01     & 0.01     & 0.01     & 0.01     & 0.36         & 0.35         \\
-Num. obs.                      & 426      & 177      & 429      & 181      & 161          & 169          \\
-RMSE                           & 1.00     & 0.98     & 1.00     & 0.99     & 0.78         & 0.80         \\
-\hline
-\multicolumn{7}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} realSubsidyPerBeneficiary: subsidy per beneficiary of Meals program in 2015 EUR \\ realTripsSubsidyPerBeneficiary: subsidy per beneficiary of Trips program in 2015 EUR \\ Model (1): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, original data set, simple linear model, estimated with OLS \\ Model (2): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, original data set, simple linear model, estimated with OLS \\ Model (3): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, simple linear model, estimated with OLS \\ Model (4): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, simple linear model, estimated with OLS\\ Model (5): dependent variable: share of beneficiaries with with broadened everyday expertise in the Lunch program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ Model (6): dependent variable: share of beneficiaries with with broadened everyday expertise in the Trips program, imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{DayToDaySkillsRegressions}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Mittagstisch ohne Ausreißer: Circa 3 EUR höhere Fördersumme geht einher mit einer weiteren Mahlzeit
-\item Entdeckerfonds ohne Ausreißer: Circa 3000 EUR höhere Fördersumme geht einher mit einem weiteren Ausflug
-\item Selbstwertgefühl \& die Alltagskompetenzen: kein Zusammenhang mit Fördersumme
-\end{itemize}
-
-\end{frame}
-
-\subsection{Gesundheit}
-
-\begin{frame}[fragile]
-\frametitle{Fragestellungen, Assoziationen zwischen:}
-\begin{itemize}
-\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
-\begin{itemize}
-\item Anteil an Begünstigten, die seltener krank sind
-\item Anteil an Begünstigten, die ihr Ernährungswissen erweitert haben
-\item Anteil an Begünstigten, die gesunde Ernährung stärker wertschätzen
-\end{itemize}
-\item Schätzung mit WLS
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-lessIllDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-dietaryDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
-\begin{knitrout}\footnotesize
-\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
-
-{\centering \includegraphics[width=\maxwidth]{figure/beamer-appreciateDGEplot-1}
-
-}
-
-\end{knitrout}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable \glqq seltener krank\grqq: Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'seltener krank'}
-\begin{center}
-\scalebox{0.65}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$       & $0.46^{**}$ & $0.09$       & $0.39^{***}$ & $0.05$       \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.12)$     & $(0.07)$     \\
-DGECriteriaNoScaled & $0.33^{***}$ & $0.35^{*}$  & $0.25^{***}$ & $0.24$       & $0.18^{*}$   \\
-                    & $(0.08)$     & $(0.16)$    & $(0.07)$     & $(0.14)$     & $(0.07)$     \\
-ML1                 &              &             &              &              & $0.12^{*}$   \\
-                    &              &             &              &              & $(0.06)$     \\
-ML2                 &              &             &              &              & $0.27^{***}$ \\
-                    &              &             &              &              & $(0.06)$     \\
-\hline
-R$^2$               & 0.12         & 0.29        & 0.07         & 0.16         & 0.19         \\
-Adj. R$^2$          & 0.11         & 0.29        & 0.07         & 0.16         & 0.17         \\
-Num. obs.           & 121          & 120         & 177          & 177          & 161          \\
-RMSE                & 0.91         & 7.83        & 0.94         & 7.95         & 0.87         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries who are less frequently ill \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-LessIll}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Variable \glqq erweitertes Ernährungswissen\grqq: Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'erweitertes Ernährungswissen'}
-\begin{center}
-\scalebox{0.55}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $0.02$   & $0.08$   & $0.02$     & $0.21$   & $0.02$       \\
-                    & $(0.07)$ & $(0.19)$ & $(0.06)$   & $(0.18)$ & $(0.07)$     \\
-DGECriteriaNoScaled & $0.11$   & $-0.02$  & $0.12^{*}$ & $0.10$   & $-0.00$      \\
-                    & $(0.06)$ & $(0.12)$ & $(0.05)$   & $(0.14)$ & $(0.06)$     \\
-ML1                 &          &          &            &          & $0.26^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML2                 &          &          &            &          & $0.24^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-ML3                 &          &          &            &          & $0.37^{***}$ \\
-                    &          &          &            &          & $(0.06)$     \\
-\hline
-R$^2$               & 0.01     & 0.00     & 0.02       & 0.01     & 0.31         \\
-Adj. R$^2$          & 0.01     & -0.00    & 0.01       & 0.01     & 0.29         \\
-Num. obs.           & 214      & 212      & 275        & 275      & 161          \\
-RMSE                & 0.98     & 8.49     & 0.96       & 9.45     & 0.83         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with expanded dietary knowledge \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-DietaryKnowledge}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Variable \glqq Wertschätzung gesunder Ernährung\grqq: Zusammenhang mit DGE-Kriterium}
-
-\begin{table}
-\caption{Zusammenhang zwischen DGE-Kriterium und Variable 'Wertschätzung gesunder Ernährung'}
-\begin{center}
-\scalebox{0.5}{
-\begin{tabular}{l c c c c c }
-\hline
- & (1) & (2) & (3) & (4) & (5) \\
-\hline
-(Intercept)         & $-0.03$      & $0.26$   & $0.02$       & $0.37^{*}$ & $0.05$       \\
-                    & $(0.07)$     & $(0.18)$ & $(0.06)$     & $(0.17)$   & $(0.07)$     \\
-DGECriteriaNoScaled & $0.27^{***}$ & $-0.02$  & $0.25^{***}$ & $0.01$     & $0.03$       \\
-                    & $(0.07)$     & $(0.15)$ & $(0.06)$     & $(0.13)$   & $(0.06)$     \\
-ML1                 &              &          &              &            & $0.03$       \\
-                    &              &          &              &            & $(0.07)$     \\
-ML2                 &              &          &              &            & $0.47^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-ML3                 &              &          &              &            & $0.24^{***}$ \\
-                    &              &          &              &            & $(0.05)$     \\
-\hline
-R$^2$               & 0.06         & 0.00     & 0.06         & 0.00       & 0.37         \\
-Adj. R$^2$          & 0.06         & -0.00    & 0.06         & -0.00      & 0.35         \\
-Num. obs.           & 213          & 211      & 274          & 274        & 161          \\
-RMSE                & 1.02         & 8.61     & 1.01         & 9.00       & 0.82         \\
-\hline
-\multicolumn{6}{l}{\scriptsize{\parbox{\linewidth}
-{\vspace{2pt} Dependent variable: share of beneficiaries with increased appreciation for a healthy diet \\ DGECriteriaNo: index of healthy diet criteria fulfilled in organization's menu \\ Model (1): original data set, simple linear model, estimated with OLS \\ Model (2): original data set, simple linear model, estimated with WLS \\ Model (3): imputed data set, simple linear model, estimated with OLS \\ Model (4): imputed data set, simple linear model, estimated with WLS \\ Model (5): imputed data set, linear model with extracted factor scores as controls, estimated with OLS \\ All regressions are estimated with robust standard errors $^{***}p<0.001$, $^{**}p<0.01$, $^*p<0.05$.}}}
-\end{tabular}
-}
-\label{HealthRegressions-AppreciateHealthy}
-\end{center}
-\end{table}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Zusammenfassung der Ergebnisse}
-
-\begin{itemize}
-\item Einfaches lineares Modell, geschätzt mit OLS: Großer, teilweise signifikanter Zusammenhang zwischen DGE-Kriterium und gesundheitsrelevanten Variablen 
-\item Hinzunahme von extrahierten Faktoren als Kontrollen:
-\begin{itemize}
-\item Variable \glqq seltener krank\grqq: nach wie vor großer, statistisch signifikanter Koeffizient
-\item Variablen \glqq erweitertes Ernährungswissen\grqq und \grqq Wertschätzung gesunder Ernährung\glqq: kein Zusammenhang mehr erkennbar
-\end{itemize}
-\end{itemize}
-\end{frame}
 
@@
 \item Die Fragenbögen werden nicht direkt von den Kindern und Jugendlichen beantwortet, sondern von den Betreuern der geförderten Einrichtungen
-\item Die Skalierung der Zielvariable \glqq Selbstwertgefühl\grqq führt zu geringer Variation
+\item Die Skalierung der Zielvariable "Selbstwertgefühl" führt zu geringer Variation
 \item [$\Rightarrow$] Daher sollte dieses Ergebnis nicht überinterpretiert werden
-\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Statistisches Lob für CHILDREN}
-\begin{itemize}
-\item<1-> Erfassung vieler Variablen über die ganze Zeit
-\item<2-> Unveränderte Datenskala (alle bis keine)
-\item<3-> Erfassung von zwei Variablen sowohl bei Mittagstisch als auch bei Entdeckerfonds
-\item<4-> Fragebogen wird automatisch ausgefüllt $\Rightarrow$ wenige fehlende Werte
-\end{itemize}
-\end{frame}
-
-\begin{frame}[fragile]
-\frametitle{Empfehlungen für CHILDREN}
-\begin{itemize}
-\item[a)] Datenstruktur:
-\item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 
-\item[c)] Datenerhebung: Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
-\item[d)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
 \end{itemize}

### 2020-03-03 presentation.Rnw

@@
 \section{Partition}
+
 \begin{frame}[fragile]
@@
 \end{frame}
-
-\section{Effekte des Entdeckerfonds}
 
@@
 \begin{itemize}
-\item Standardisierten Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
+\item Standardisiertes Maß für gesundes Essen (DGE-Kriterium) und ausgewählte standardisierte gesundheitsrelevante Variablen
 \begin{itemize}
@@
 \item Elektronische Fragebögen und Datenerhebung
+\item Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
 \item[b)] Auswahl der Variablen: Ähnliche Variablen durch zugrundeliegende ersetzen, anhand von Faktoranalyse oder Partition 
-\item[c)] Datenerhebung: Ordinale Variablen an sich kein Problem, Ersetzung durch metrische (in Prozent) nur sinnvoll, wenn dadurch nicht häufiger fehlende Werte
-\item[d)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
+\item[c)] Interventionen: Noch stärkeres Gewicht auf gesunder Ernährung in Einrichtungen
 \end{itemize}

### 2020-03-15 ANALYSIS/data_example_presentation.R
UPDATE

@@ -3,11 +3,20 @@ library(dplyr)
 dataPraesi <- mergedData %>% filter(id == "103" | id == "112") %>% 
   dplyr::select(id, year, eatersPerMealNo, selfworth, tripsNo)
 
-dataPraesi <- dataPraesi[-c(1, 2, 3, 7, 8, 9, 10, 11, 15), ]
+dataPraesi <- dataPraesi[-c(1, 2, 3, 7, 8, 9, 10, 11, 15, 16), ]
 
 library(xtable)
 
-dataExample <- print(xtable(dataPraesi), include.rownames=FALSE)
-
+dataExample <- xtable(dataPraesi)
 
 saveRDS(dataExample, "./ANALYSIS/GRAPHS/PAPER/dataExample.Rds")
+
+print(xtable(dataExample, include.rownames = FALSE,
+             caption = "Beispielhafter Datensatz",
+             align = "lccccc"))
+
+
+print(xtable(dataExample), include.rownames = FALSE,
+      caption = "Beispielhafter Datensatz",
+      align = "lccccc",
+      label = "fundamentalDynamics")
